### 2021-04-05 theory/M2DEG.tex
Add initial theory

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}

\numberwithin{equation}{subsection}
\newcommand{\mb}[1]{\mathbf{#1}}
\title{Magnetic propeties of a two dimentional electron gas strongly coupled to lights}
\author{K.Dini, O.V. Kibis and I.A. Shelykh}
\numberwithin{equation}{section}

\begin{document}

\maketitle

\section{Schrödinger problem for Landau levels in dressed 2DEG}

Our analysis is consider on 2 dimentional electronic gas which has distrubuted in $(x,y)$ plane in configuration space. We are going to examine the properties of 2DEG with stationary magnetic field
\begin{equation} \label{1.1}
  \vb{B} = (0,0,B)^T
\end{equation}
which directed on $z$ axis and a linearly $y$-polarized strong electomagnetic wave (dressing field) with electric field given by
\begin{equation} \label{1.2}
  \vb{E} = (0,E\sin(\omega t),0)^T
\end{equation}
which also propagate in $z$ direction. Here $B$ and $E$ represent the amplitude of the stationary magnetic field and electric field of dressing field.
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.9]{figures/fig1.pdf}
  \caption{Stationary magnetic filed (blue color) and Strong EM wave (red color) applied to the 2DEG.}
  \label{fig:1.1}
\end{figure}

\noindent
Using Landau gauge for the stationary magnetic field we can represent it using vector potential as
\begin{equation} \label{1.3}
  \vb{A}_{s} = (-By,0,0)^T
\end{equation}
and choosing Coulomb gauge the dressing field can be present as the following vector potential
\begin{equation} \label{1.4}
  \vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^T.
\end{equation}
Now the Hamiltonian of an electron in 2DEG can be reads as
\begin{equation} \label{1.5}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big(\vb{A}_{s}+\vb{A}_{d}(t)\big)\Big]^2
\end{equation}
where $m_e$ is the effective mass of the electron and $e$ is the magnitude (without considering the sign of the charge) of the electron charge. This can be simplified to
\begin{equation} \label{1.6}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[
    (\hat{p}_x + eBy)\vb{e}_x +
    (\hat{p}_y - \frac{eE}{\omega}\cos(\omega t))\vb{e}_y
  \Big]^2
\end{equation}
where $\vb{e}_x$ and $\vb{e}_y$ are unit vectors along $x$ and $y$ directions respectively. Moreover,
\begin{equation} \label{1.7}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[
    (\hat{p}_x + eBy)^2 +
    (\hat{p}_y - \frac{eE}{\omega}\cos(\omega t))^2
  \Big]
\end{equation}
Since $[\hat{H}_e(t),\hat{p}_x] =0$ both operators share same eigenvalue and eigen functions which are free electron wave functions. Therefore we can modify the Hamiltonian as follows
\begin{equation} \label{1.8}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[
    ({p}_x + eBy)^2 +
    (\hat{p}_y - \frac{eE}{\omega}\cos(\omega t))^2
  \Big].
\end{equation}
Using momentum operator definition
\begin{equation} \label{1.9}
  \hat{p}_y = -i\hbar \pdv{y}
\end{equation}
we can modify Eq. \eqref{1.8} as
\begin{equation} \label{1.10}
  \begin{aligned}
    \hat{H}_e(t) & = \frac{1}{2m_e}\Big[
      ({p}_x + eBy)^2 +
      \Big(-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\Big)^2
    \Big] \\
    & = \frac{1}{2m_e}\Big[
      ({p}_x + eBy)^2 +
      \Big(i\hbar \pdv{y} + \frac{eE}{\omega}\cos(\omega t)\Big)^2
    \Big].
  \end{aligned}
\end{equation}
Define the \textit{center of the cyclotron orbit} along $y$ axis as
\begin{equation} \label{1.11}
  y_0 \equiv \frac{-p_x}{eB}
\end{equation}
and the \textit{cyclotron frequency} as
\begin{equation} \label{1.12}
  \omega_0 \equiv \frac{eB}{m_e}.
\end{equation}
Then the Hamiltonian will leads to
\begin{equation} \label{1.13}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}(y-y_0)^2 +
      \frac{1}{2m_e}\Big(i\hbar \pdv{y}+\frac{eE}{\omega}\cos(\omega t)\Big)^2
\end{equation}
\begin{equation} \label{1.14}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}(y-y_0)^2 +
      \frac{1}{2m_e}\Big(
      -\hbar^2 \pdv[2]{y} & +
      i\hbar \pdv{y}\bigg[\frac{eE}{\omega}\cos(\omega t) \bigg] \\ & +
      \frac{i\hbar eE}{\omega}\cos(\omega t) \pdv{y}+
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \Big)
  \end{aligned}
\end{equation}
\begin{equation} \label{1.15}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}(y-y_0)^2 +
      \frac{1}{2m_e}\Big(
      -\hbar^2 \pdv[2]{y} +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{y}+
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \Big).
  \end{aligned}
\end{equation}
Let
\begin{equation} \label{1.16}
    (y - y_0) \rightarrow y
\end{equation}
and then this becomes
\begin{equation} \label{1.17}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}y^2 +
      \frac{1}{2m_e}\Big(
      -\hbar^2 \pdv[2]{y} +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{y}+
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \Big).
  \end{aligned}
\end{equation}
Now assume that the solution for the time-dependent schrödinger equation
\begin{equation} \label{1.18}
    i \hbar \pdv{\psi}{t} = \hat{H}_e(t)\psi
\end{equation}
can be represent by the following form
\begin{equation} \label{1.19}
    \psi(\vb{r},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE(y-y_0)}{\hbar \omega}\cos(\omega t)
    \bigg) \phi(y-y_0,t).
\end{equation}
Using the same subtution from Eq. \eqref{1.16} this becomes
\begin{equation} \label{1.20}
    \psi(x,y,t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieEy}{\hbar \omega}\cos(\omega t)
    \bigg) \phi(y,t).
\end{equation}
Defining
\begin{equation} \label{1.21}
    \varphi(x,y,t) \equiv \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieEy}{\hbar \omega}\cos(\omega t)
    \bigg)
\end{equation}
we can simply the the Eq. \eqref{1.20} as
\begin{equation} \label{1.22}
    \psi(x,y,t) = \varphi(x,y,t) \phi(y,t).
\end{equation}
Let's subtitue Eq. \eqref{1.20} and Eq. \eqref{1.17} into Eq. \eqref{1.18} and we can observe that
\begin{equation} \label{1.23}
  \begin{aligned}
    \text{L.H.S} & = i \hbar \pdv{\psi}{t} =
    i \hbar \bigg( \pdv{\varphi}{t} \phi + \pdv{\phi}{t} \varphi \bigg) =
    i \hbar \bigg(
      \Big[\frac{-ieEy}{\hbar}\sin(\omega t)\Big]\varphi\phi +
      \varphi  \pdv{\phi}{t}
    \bigg) \\
    & =
    \big[{eEy}\sin(\omega t)\big]\varphi\phi +
    i \hbar\varphi  \pdv{\phi}{t}
  \end{aligned}
\end{equation}
and
\begin{equation} \label{1.24}
  \begin{aligned}
    \text{R.H.S} & = \hat{H}_e(t)\psi \\
    & =
    \bigg[
    \frac{m_e \omega_0^2}{2}y^2 +
    \frac{1}{2m_e}\Big(
    -\hbar^2 \pdv[2]{y} +
    \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{y}+
    \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
    \Big) \bigg]
    \varphi\phi
  \end{aligned}
\end{equation}
where we will can calculate this part by part as follows:
\begin{equation} \label{1.25}
  \begin{aligned}
    \frac{-\hbar^2}{2m_e}\pdv[2]{y}(\varphi\phi) & =
    \frac{-\hbar^2}{2m_e} \pdv{y}\bigg[
      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)\varphi\phi +
      \varphi\pdv{\phi}{y}
    \bigg] \\
    & =
    \frac{-\hbar^2}{2m_e} \bigg[
      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)^2\varphi\phi +
      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)\varphi\pdv{\phi}{y} +
      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)\varphi\pdv{\phi}{y} +
      \varphi\pdv[2]{\phi}{y}
    \bigg] \\
    & =
    \Big(\frac{e^2E^2}{ 2m_e\omega^2} \cos[2](\omega)t\Big)\varphi\phi -
    \Big(\frac{ieE \hbar}{m_e\omega} \cos(\omega)t\Big)\varphi\pdv{\phi}{y} -
    \frac{\hbar^2}{2m_e}
    \varphi\pdv[2]{\phi}{y}
  \end{aligned}
\end{equation}
and
\begin{equation} \label{1.26}
  \begin{aligned}
    \frac{2i\hbar eE}{2m_e\omega}\cos(\omega t) \pdv{y} (\varphi\phi)& =
    \frac{i\hbar eE}{m_e\omega}\cos(\omega t)
    \bigg[
      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)\varphi\phi +
      \varphi\pdv{\phi}{y}
    \bigg] \\
    & =
    \Big(\frac{-e^2E^2}{m_e\omega^2} \cos(\omega)t\Big)\varphi\phi +
    \frac{i\hbar eE}{m_e\omega}\cos(\omega t)\varphi\pdv{\phi}{y}.
  \end{aligned}
\end{equation}
Therefore we can derive that
\begin{equation} \label{1.27}
  \begin{aligned}
    \text{R.H.S} =
    \bigg[
    \frac{m_e \omega_0^2}{2}y^2
    -
    \frac{\hbar^2}{2m_e}
    \varphi\pdv[2]{\phi}{y} \bigg]
    \varphi\phi.
  \end{aligned}
\end{equation}
To satisfy the condition L.H.S$=$R.H.S we need to find a function $\phi(y,t)$ such that
\begin{equation} \label{1.28}
  \begin{aligned}
    \big[{eEy}\sin(\omega t)\big]\varphi\phi +
    i \hbar\varphi  \pdv{\phi}{t}
    =
    \bigg[
    \frac{m_e \omega_0^2}{2}y^2
    -
    \frac{\hbar^2}{2m_e}
    \varphi\pdv[2]{\phi}{y} \bigg]
    \varphi\phi
  \end{aligned}
\end{equation}
which can be simplyfied as
\begin{equation} \label{1.29}
  \begin{aligned}
    \bigg[
    \frac{m_e \omega_0^2}{2}y^2
    - {eEy}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{y}
    - i \hbar \pdv{t}
    \bigg]
    \phi(y,t) = 0
  \end{aligned}
\end{equation}

\end{document}

### 2021-04-05 theory/figures/fig1.tex
Add initial theory

\documentclass{standalone}

\usepackage{tikz,pgf} %and any other packages or tikzlibraries your picture needs

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Straight Lines [id:da9655093306166109]
\draw    (151.25,213.56) -- (420.92,213.12) ;
%Straight Lines [id:da6780197443194285]
\draw    (178.99,167.4) -- (393.4,167.4) ;
%Straight Lines [id:da9790479690343763]
\draw    (179.39,167) -- (151.25,213.56) ;
%Straight Lines [id:da9225563682209392]
\draw    (393.8,167) -- (420.92,213.12) ;
%Straight Lines [id:da09563387136808865]
\draw    (286.6,167) -- (286.08,213.34) ;
%Straight Lines [id:da3116522709021452]
\draw    (273.92,166.96) -- (270.68,213.56) ;
%Straight Lines [id:da7104288201908657]
\draw    (259.41,166.96) -- (253.18,213.3) ;
%Straight Lines [id:da742779405875688]
\draw    (245.3,166.91) -- (237.52,213.3) ;
%Straight Lines [id:da18844905298889292]
\draw    (232.1,167.18) -- (220.33,213.82) ;
%Straight Lines [id:da35804353174173054]
\draw    (217.96,167.2) -- (201.3,213.56) ;
%Straight Lines [id:da7688901048445682]
\draw    (205.7,167.18) -- (185.02,213.82) ;
%Straight Lines [id:da3470294213255083]
\draw    (192.98,167.2) -- (169.98,213.82) ;
%Straight Lines [id:da35862455135349536]
\draw    (298.62,166.91) -- (302.61,213.56) ;
%Straight Lines [id:da29999796293225955]
\draw    (313.18,167.08) -- (321.21,213.92) ;
%Straight Lines [id:da6206528590435849]
\draw    (327.48,166.91) -- (339.76,213.3) ;
%Straight Lines [id:da9408253594123648]
\draw    (340.68,167.18) -- (357.57,213.82) ;
%Straight Lines [id:da917785587155304]
\draw    (354.8,167.18) -- (374.76,213.56) ;
%Straight Lines [id:da3801603892210079]
\draw    (366.16,167.08) -- (392.26,213.56) ;
%Straight Lines [id:da580723776969265]
\draw    (380.59,167.18) -- (405.77,213.3) ;
%Straight Lines [id:da5336171972507551]
\draw    (155.55,205.39) -- (416.51,204.6) ;
%Straight Lines [id:da956646312420568]
\draw    (160.77,197.48) -- (411.6,196.96) ;
%Straight Lines [id:da2531401201560137]
\draw    (165.32,190.28) -- (407.36,190.06) ;
%Straight Lines [id:da31575285130833475]
\draw    (169.06,183.52) -- (403.31,183.25) ;
%Straight Lines [id:da6000067635957629]
\draw    (172.65,177.85) -- (399.54,177.33) ;
%Straight Lines [id:da36539132370134153]
\draw    (175.41,172.58) -- (396.16,171.79) ;
%Shape: Ellipse [id:dp12271593300544881]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (172.44,205.39) .. controls (172.44,204.59) and (173.19,203.94) .. (174.12,203.94) .. controls (175.06,203.94) and (175.81,204.59) .. (175.81,205.39) .. controls (175.81,206.19) and (175.06,206.84) .. (174.12,206.84) .. controls (173.19,206.84) and (172.44,206.19) .. (172.44,205.39) -- cycle ;
%Shape: Ellipse [id:dp17187409527803665]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (176.2,197.36) .. controls (176.2,196.56) and (176.96,195.91) .. (177.89,195.91) .. controls (178.82,195.91) and (179.58,196.56) .. (179.58,197.36) .. controls (179.58,198.16) and (178.82,198.81) .. (177.89,198.81) .. controls (176.96,198.81) and (176.2,198.16) .. (176.2,197.36) -- cycle ;
%Shape: Ellipse [id:dp3897463489917039]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (179.83,189.94) .. controls (179.83,189.14) and (180.59,188.49) .. (181.52,188.49) .. controls (182.45,188.49) and (183.21,189.14) .. (183.21,189.94) .. controls (183.21,190.74) and (182.45,191.39) .. (181.52,191.39) .. controls (180.59,191.39) and (179.83,190.74) .. (179.83,189.94) -- cycle ;
%Shape: Ellipse [id:dp6651227824721306]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (182.9,183.59) .. controls (182.9,182.79) and (183.66,182.14) .. (184.59,182.14) .. controls (185.52,182.14) and (186.28,182.79) .. (186.28,183.59) .. controls (186.28,184.39) and (185.52,185.04) .. (184.59,185.04) .. controls (183.66,185.04) and (182.9,184.39) .. (182.9,183.59) -- cycle ;
%Shape: Ellipse [id:dp16931876417539748]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (186.11,177.24) .. controls (186.11,176.44) and (186.87,175.79) .. (187.8,175.79) .. controls (188.73,175.79) and (189.49,176.44) .. (189.49,177.24) .. controls (189.49,178.04) and (188.73,178.69) .. (187.8,178.69) .. controls (186.87,178.69) and (186.11,178.04) .. (186.11,177.24) -- cycle ;
%Shape: Ellipse [id:dp011630715757735333]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (189.04,171.85) .. controls (189.04,171.05) and (189.8,170.4) .. (190.73,170.4) .. controls (191.66,170.4) and (192.42,171.05) .. (192.42,171.85) .. controls (192.42,172.65) and (191.66,173.3) .. (190.73,173.3) .. controls (189.8,173.3) and (189.04,172.65) .. (189.04,171.85) -- cycle ;
%Shape: Ellipse [id:dp6352732828874232]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (186.95,205.15) .. controls (186.95,204.35) and (187.71,203.7) .. (188.64,203.7) .. controls (189.57,203.7) and (190.33,204.35) .. (190.33,205.15) .. controls (190.33,205.95) and (189.57,206.6) .. (188.64,206.6) .. controls (187.71,206.6) and (186.95,205.95) .. (186.95,205.15) -- cycle ;
%Shape: Ellipse [id:dp5586918813010036]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (190.44,197.48) .. controls (190.44,196.68) and (191.19,196.03) .. (192.13,196.03) .. controls (193.06,196.03) and (193.82,196.68) .. (193.82,197.48) .. controls (193.82,198.28) and (193.06,198.93) .. (192.13,198.93) .. controls (191.19,198.93) and (190.44,198.28) .. (190.44,197.48) -- cycle ;
%Shape: Ellipse [id:dp9378136236695127]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (193.67,190.5) .. controls (193.67,189.7) and (194.43,189.05) .. (195.36,189.05) .. controls (196.29,189.05) and (197.05,189.7) .. (197.05,190.5) .. controls (197.05,191.3) and (196.29,191.95) .. (195.36,191.95) .. controls (194.43,191.95) and (193.67,191.3) .. (193.67,190.5) -- cycle ;
%Shape: Ellipse [id:dp7452150293769777]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (196.58,183.47) .. controls (196.58,182.67) and (197.33,182.02) .. (198.27,182.02) .. controls (199.2,182.02) and (199.96,182.67) .. (199.96,183.47) .. controls (199.96,184.27) and (199.2,184.92) .. (198.27,184.92) .. controls (197.33,184.92) and (196.58,184.27) .. (196.58,183.47) -- cycle ;
%Shape: Ellipse [id:dp2595074236120878]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (199.51,177.48) .. controls (199.51,176.68) and (200.27,176.03) .. (201.2,176.03) .. controls (202.13,176.03) and (202.89,176.68) .. (202.89,177.48) .. controls (202.89,178.28) and (202.13,178.93) .. (201.2,178.93) .. controls (200.27,178.93) and (199.51,178.28) .. (199.51,177.48) -- cycle ;
%Shape: Ellipse [id:dp8182709430461124]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (201.6,171.85) .. controls (201.6,171.05) and (202.36,170.4) .. (203.29,170.4) .. controls (204.22,170.4) and (204.98,171.05) .. (204.98,171.85) .. controls (204.98,172.65) and (204.22,173.3) .. (203.29,173.3) .. controls (202.36,173.3) and (201.6,172.65) .. (201.6,171.85) -- cycle ;
%Shape: Ellipse [id:dp8721800205864367]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (202.72,205.27) .. controls (202.72,204.47) and (203.47,203.82) .. (204.41,203.82) .. controls (205.34,203.82) and (206.1,204.47) .. (206.1,205.27) .. controls (206.1,206.07) and (205.34,206.72) .. (204.41,206.72) .. controls (203.47,206.72) and (202.72,206.07) .. (202.72,205.27) -- cycle ;
%Shape: Ellipse [id:dp7821722952675314]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (205.51,197.36) .. controls (205.51,196.56) and (206.27,195.91) .. (207.2,195.91) .. controls (208.13,195.91) and (208.89,196.56) .. (208.89,197.36) .. controls (208.89,198.16) and (208.13,198.81) .. (207.2,198.81) .. controls (206.27,198.81) and (205.51,198.16) .. (205.51,197.36) -- cycle ;
%Shape: Ellipse [id:dp6361699950198552]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (207.95,190.5) .. controls (207.95,189.7) and (208.7,189.05) .. (209.64,189.05) .. controls (210.57,189.05) and (211.32,189.7) .. (211.32,190.5) .. controls (211.32,191.3) and (210.57,191.95) .. (209.64,191.95) .. controls (208.7,191.95) and (207.95,191.3) .. (207.95,190.5) -- cycle ;
%Shape: Ellipse [id:dp07429235889252994]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (210.53,183.35) .. controls (210.53,182.55) and (211.29,181.9) .. (212.22,181.9) .. controls (213.15,181.9) and (213.91,182.55) .. (213.91,183.35) .. controls (213.91,184.15) and (213.15,184.8) .. (212.22,184.8) .. controls (211.29,184.8) and (210.53,184.15) .. (210.53,183.35) -- cycle ;
%Shape: Ellipse [id:dp46939239369131425]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (212.63,177.12) .. controls (212.63,176.32) and (213.38,175.67) .. (214.32,175.67) .. controls (215.25,175.67) and (216,176.32) .. (216,177.12) .. controls (216,177.92) and (215.25,178.57) .. (214.32,178.57) .. controls (213.38,178.57) and (212.63,177.92) .. (212.63,177.12) -- cycle ;
%Shape: Ellipse [id:dp47839368197126064]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (214.58,171.73) .. controls (214.58,170.93) and (215.34,170.28) .. (216.27,170.28) .. controls (217.2,170.28) and (217.96,170.93) .. (217.96,171.73) .. controls (217.96,172.53) and (217.2,173.18) .. (216.27,173.18) .. controls (215.34,173.18) and (214.58,172.53) .. (214.58,171.73) -- cycle ;
%Shape: Ellipse [id:dp6735819197452304]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (220.72,205.39) .. controls (220.72,204.59) and (221.48,203.94) .. (222.41,203.94) .. controls (223.34,203.94) and (224.1,204.59) .. (224.1,205.39) .. controls (224.1,206.19) and (223.34,206.84) .. (222.41,206.84) .. controls (221.48,206.84) and (220.72,206.19) .. (220.72,205.39) -- cycle ;
%Shape: Ellipse [id:dp40045376893902485]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (222.81,197.48) .. controls (222.81,196.68) and (223.57,196.03) .. (224.5,196.03) .. controls (225.44,196.03) and (226.19,196.68) .. (226.19,197.48) .. controls (226.19,198.28) and (225.44,198.93) .. (224.5,198.93) .. controls (223.57,198.93) and (222.81,198.28) .. (222.81,197.48) -- cycle ;
%Shape: Ellipse [id:dp002588008650496576]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (224.53,190.5) .. controls (224.53,189.7) and (225.28,189.05) .. (226.21,189.05) .. controls (227.15,189.05) and (227.9,189.7) .. (227.9,190.5) .. controls (227.9,191.3) and (227.15,191.95) .. (226.21,191.95) .. controls (225.28,191.95) and (224.53,191.3) .. (224.53,190.5) -- cycle ;
%Shape: Ellipse [id:dp7269110513068167]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (226.16,183.59) .. controls (226.16,182.79) and (226.92,182.14) .. (227.85,182.14) .. controls (228.78,182.14) and (229.54,182.79) .. (229.54,183.59) .. controls (229.54,184.39) and (228.78,185.04) .. (227.85,185.04) .. controls (226.92,185.04) and (226.16,184.39) .. (226.16,183.59) -- cycle ;
%Shape: Ellipse [id:dp6228752312232548]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (227.7,177.36) .. controls (227.7,176.56) and (228.45,175.91) .. (229.39,175.91) .. controls (230.32,175.91) and (231.08,176.56) .. (231.08,177.36) .. controls (231.08,178.16) and (230.32,178.81) .. (229.39,178.81) .. controls (228.45,178.81) and (227.7,178.16) .. (227.7,177.36) -- cycle ;
%Shape: Ellipse [id:dp5712591071424813]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (229.09,171.97) .. controls (229.09,171.17) and (229.85,170.52) .. (230.78,170.52) .. controls (231.72,170.52) and (232.47,171.17) .. (232.47,171.97) .. controls (232.47,172.77) and (231.72,173.42) .. (230.78,173.42) .. controls (229.85,173.42) and (229.09,172.77) .. (229.09,171.97) -- cycle ;
%Shape: Ellipse [id:dp37415663269795374]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (242.77,171.85) .. controls (242.77,171.05) and (243.53,170.4) .. (244.46,170.4) .. controls (245.39,170.4) and (246.15,171.05) .. (246.15,171.85) .. controls (246.15,172.65) and (245.39,173.3) .. (244.46,173.3) .. controls (243.53,173.3) and (242.77,172.65) .. (242.77,171.85) -- cycle ;
%Shape: Ellipse [id:dp5844680482576305]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (241.79,177.48) .. controls (241.79,176.68) and (242.55,176.03) .. (243.48,176.03) .. controls (244.41,176.03) and (245.17,176.68) .. (245.17,177.48) .. controls (245.17,178.28) and (244.41,178.93) .. (243.48,178.93) .. controls (242.55,178.93) and (241.79,178.28) .. (241.79,177.48) -- cycle ;
%Shape: Ellipse [id:dp27800840767464763]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (240.68,183.23) .. controls (240.68,182.43) and (241.43,181.78) .. (242.37,181.78) .. controls (243.3,181.78) and (244.05,182.43) .. (244.05,183.23) .. controls (244.05,184.03) and (243.3,184.68) .. (242.37,184.68) .. controls (241.43,184.68) and (240.68,184.03) .. (240.68,183.23) -- cycle ;
%Shape: Ellipse [id:dp6309981882755835]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (239.72,190.1) .. controls (239.72,189.3) and (240.48,188.65) .. (241.41,188.65) .. controls (242.34,188.65) and (243.1,189.3) .. (243.1,190.1) .. controls (243.1,190.9) and (242.34,191.55) .. (241.41,191.55) .. controls (240.48,191.55) and (239.72,190.9) .. (239.72,190.1) -- cycle ;
%Shape: Ellipse [id:dp6064458479575909]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (238.44,197.36) .. controls (238.44,196.56) and (239.2,195.91) .. (240.13,195.91) .. controls (241.07,195.91) and (241.82,196.56) .. (241.82,197.36) .. controls (241.82,198.16) and (241.07,198.81) .. (240.13,198.81) .. controls (239.2,198.81) and (238.44,198.16) .. (238.44,197.36) -- cycle ;
%Shape: Ellipse [id:dp8566892005164177]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (237.19,205.03) .. controls (237.19,204.23) and (237.94,203.58) .. (238.88,203.58) .. controls (239.81,203.58) and (240.57,204.23) .. (240.57,205.03) .. controls (240.57,205.83) and (239.81,206.48) .. (238.88,206.48) .. controls (237.94,206.48) and (237.19,205.83) .. (237.19,205.03) -- cycle ;
%Shape: Ellipse [id:dp21811991550458654]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (257.01,171.85) .. controls (257.01,171.05) and (257.76,170.4) .. (258.69,170.4) .. controls (259.63,170.4) and (260.38,171.05) .. (260.38,171.85) .. controls (260.38,172.65) and (259.63,173.3) .. (258.69,173.3) .. controls (257.76,173.3) and (257.01,172.65) .. (257.01,171.85) -- cycle ;
%Shape: Ellipse [id:dp07465207554443909]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (256.17,177.36) .. controls (256.17,176.56) and (256.92,175.91) .. (257.86,175.91) .. controls (258.79,175.91) and (259.54,176.56) .. (259.54,177.36) .. controls (259.54,178.16) and (258.79,178.81) .. (257.86,178.81) .. controls (256.92,178.81) and (256.17,178.16) .. (256.17,177.36) -- cycle ;
%Shape: Ellipse [id:dp3520799274177444]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (255.33,183.47) .. controls (255.33,182.67) and (256.09,182.02) .. (257.02,182.02) .. controls (257.95,182.02) and (258.71,182.67) .. (258.71,183.47) .. controls (258.71,184.27) and (257.95,184.92) .. (257.02,184.92) .. controls (256.09,184.92) and (255.33,184.27) .. (255.33,183.47) -- cycle ;
%Shape: Ellipse [id:dp8618279200116534]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (254.56,190.37) .. controls (254.56,189.57) and (255.32,188.92) .. (256.25,188.92) .. controls (257.18,188.92) and (257.94,189.57) .. (257.94,190.37) .. controls (257.94,191.17) and (257.18,191.82) .. (256.25,191.82) .. controls (255.32,191.82) and (254.56,191.17) .. (254.56,190.37) -- cycle ;
%Shape: Ellipse [id:dp4846168731141014]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (253.52,197.24) .. controls (253.52,196.44) and (254.27,195.79) .. (255.2,195.79) .. controls (256.14,195.79) and (256.89,196.44) .. (256.89,197.24) .. controls (256.89,198.04) and (256.14,198.69) .. (255.2,198.69) .. controls (254.27,198.69) and (253.52,198.04) .. (253.52,197.24) -- cycle ;
%Shape: Ellipse [id:dp3684815163642654]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (252.4,205.15) .. controls (252.4,204.35) and (253.16,203.7) .. (254.09,203.7) .. controls (255.02,203.7) and (255.78,204.35) .. (255.78,205.15) .. controls (255.78,205.95) and (255.02,206.6) .. (254.09,206.6) .. controls (253.16,206.6) and (252.4,205.95) .. (252.4,205.15) -- cycle ;
%Shape: Ellipse [id:dp1437934667713081]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (271.94,171.85) .. controls (271.94,171.05) and (272.69,170.4) .. (273.63,170.4) .. controls (274.56,170.4) and (275.31,171.05) .. (275.31,171.85) .. controls (275.31,172.65) and (274.56,173.3) .. (273.63,173.3) .. controls (272.69,173.3) and (271.94,172.65) .. (271.94,171.85) -- cycle ;
%Shape: Ellipse [id:dp886301588499915]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (271.52,177.24) .. controls (271.52,176.44) and (272.27,175.79) .. (273.21,175.79) .. controls (274.14,175.79) and (274.9,176.44) .. (274.9,177.24) .. controls (274.9,178.04) and (274.14,178.69) .. (273.21,178.69) .. controls (272.27,178.69) and (271.52,178.04) .. (271.52,177.24) -- cycle ;
%Shape: Ellipse [id:dp10861025652876077]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (271.24,183.23) .. controls (271.24,182.43) and (272,181.78) .. (272.93,181.78) .. controls (273.86,181.78) and (274.62,182.43) .. (274.62,183.23) .. controls (274.62,184.03) and (273.86,184.68) .. (272.93,184.68) .. controls (272,184.68) and (271.24,184.03) .. (271.24,183.23) -- cycle ;
%Shape: Ellipse [id:dp8227079118183289]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (270.68,190.5) .. controls (270.68,189.7) and (271.44,189.05) .. (272.37,189.05) .. controls (273.3,189.05) and (274.06,189.7) .. (274.06,190.5) .. controls (274.06,191.3) and (273.3,191.95) .. (272.37,191.95) .. controls (271.44,191.95) and (270.68,191.3) .. (270.68,190.5) -- cycle ;
%Shape: Ellipse [id:dp31754679610416936]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (270.12,197.12) .. controls (270.12,196.32) and (270.88,195.67) .. (271.81,195.67) .. controls (272.74,195.67) and (273.5,196.32) .. (273.5,197.12) .. controls (273.5,197.92) and (272.74,198.57) .. (271.81,198.57) .. controls (270.88,198.57) and (270.12,197.92) .. (270.12,197.12) -- cycle ;
%Shape: Ellipse [id:dp228275147103431]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (269.7,205.03) .. controls (269.7,204.23) and (270.46,203.58) .. (271.39,203.58) .. controls (272.33,203.58) and (273.08,204.23) .. (273.08,205.03) .. controls (273.08,205.83) and (272.33,206.48) .. (271.39,206.48) .. controls (270.46,206.48) and (269.7,205.83) .. (269.7,205.03) -- cycle ;
%Shape: Ellipse [id:dp5867689834208971]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.5,171.79) .. controls (284.5,170.99) and (285.25,170.34) .. (286.19,170.34) .. controls (287.12,170.34) and (287.87,170.99) .. (287.87,171.79) .. controls (287.87,172.59) and (287.12,173.24) .. (286.19,173.24) .. controls (285.25,173.24) and (284.5,172.59) .. (284.5,171.79) -- cycle ;
%Shape: Ellipse [id:dp18205732240558015]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.8,177.19) .. controls (284.8,176.39) and (285.56,175.74) .. (286.49,175.74) .. controls (287.43,175.74) and (288.18,176.39) .. (288.18,177.19) .. controls (288.18,177.99) and (287.43,178.64) .. (286.49,178.64) .. controls (285.56,178.64) and (284.8,177.99) .. (284.8,177.19) -- cycle ;
%Shape: Ellipse [id:dp6234929744101898]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.5,183.38) .. controls (284.5,182.58) and (285.25,181.93) .. (286.19,181.93) .. controls (287.12,181.93) and (287.87,182.58) .. (287.87,183.38) .. controls (287.87,184.18) and (287.12,184.83) .. (286.19,184.83) .. controls (285.25,184.83) and (284.5,184.18) .. (284.5,183.38) -- cycle ;
%Shape: Ellipse [id:dp8290479654576126]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.65,190.17) .. controls (284.65,189.37) and (285.41,188.72) .. (286.34,188.72) .. controls (287.27,188.72) and (288.03,189.37) .. (288.03,190.17) .. controls (288.03,190.97) and (287.27,191.62) .. (286.34,191.62) .. controls (285.41,191.62) and (284.65,190.97) .. (284.65,190.17) -- cycle ;
%Shape: Ellipse [id:dp8989481541795088]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.5,197.22) .. controls (284.5,196.42) and (285.25,195.77) .. (286.19,195.77) .. controls (287.12,195.77) and (287.87,196.42) .. (287.87,197.22) .. controls (287.87,198.02) and (287.12,198.67) .. (286.19,198.67) .. controls (285.25,198.67) and (284.5,198.02) .. (284.5,197.22) -- cycle ;
%Shape: Ellipse [id:dp3354120737649453]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.34,204.99) .. controls (284.34,204.19) and (285.1,203.54) .. (286.03,203.54) .. controls (286.96,203.54) and (287.72,204.19) .. (287.72,204.99) .. controls (287.72,205.79) and (286.96,206.44) .. (286.03,206.44) .. controls (285.1,206.44) and (284.34,205.79) .. (284.34,204.99) -- cycle ;
%Shape: Ellipse [id:dp3606226368237744]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (297.2,171.73) .. controls (297.2,170.93) and (297.95,170.28) .. (298.89,170.28) .. controls (299.82,170.28) and (300.57,170.93) .. (300.57,171.73) .. controls (300.57,172.53) and (299.82,173.18) .. (298.89,173.18) .. controls (297.95,173.18) and (297.2,172.53) .. (297.2,171.73) -- cycle ;
%Shape: Ellipse [id:dp048913958034914495]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (297.89,177.24) .. controls (297.89,176.44) and (298.65,175.79) .. (299.58,175.79) .. controls (300.52,175.79) and (301.27,176.44) .. (301.27,177.24) .. controls (301.27,178.04) and (300.52,178.69) .. (299.58,178.69) .. controls (298.65,178.69) and (297.89,178.04) .. (297.89,177.24) -- cycle ;
%Shape: Ellipse [id:dp19686667746567443]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (298.17,183.47) .. controls (298.17,182.67) and (298.93,182.02) .. (299.86,182.02) .. controls (300.79,182.02) and (301.55,182.67) .. (301.55,183.47) .. controls (301.55,184.27) and (300.79,184.92) .. (299.86,184.92) .. controls (298.93,184.92) and (298.17,184.27) .. (298.17,183.47) -- cycle ;
%Shape: Ellipse [id:dp4115460327510696]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (298.93,190.24) .. controls (298.93,189.44) and (299.68,188.79) .. (300.62,188.79) .. controls (301.55,188.79) and (302.3,189.44) .. (302.3,190.24) .. controls (302.3,191.04) and (301.55,191.69) .. (300.62,191.69) .. controls (299.68,191.69) and (298.93,191.04) .. (298.93,190.24) -- cycle ;
%Shape: Ellipse [id:dp19847266839128408]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (299.29,197.12) .. controls (299.29,196.32) and (300.05,195.67) .. (300.98,195.67) .. controls (301.91,195.67) and (302.67,196.32) .. (302.67,197.12) .. controls (302.67,197.92) and (301.91,198.57) .. (300.98,198.57) .. controls (300.05,198.57) and (299.29,197.92) .. (299.29,197.12) -- cycle ;
%Shape: Ellipse [id:dp48996962931873567]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (300.13,204.91) .. controls (300.13,204.11) and (300.88,203.46) .. (301.82,203.46) .. controls (302.75,203.46) and (303.5,204.11) .. (303.5,204.91) .. controls (303.5,205.71) and (302.75,206.36) .. (301.82,206.36) .. controls (300.88,206.36) and (300.13,205.71) .. (300.13,204.91) -- cycle ;
%Shape: Ellipse [id:dp8365501880357185]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (311.87,172.13) .. controls (311.87,171.33) and (312.62,170.68) .. (313.56,170.68) .. controls (314.49,170.68) and (315.25,171.33) .. (315.25,172.13) .. controls (315.25,172.93) and (314.49,173.58) .. (313.56,173.58) .. controls (312.62,173.58) and (311.87,172.93) .. (311.87,172.13) -- cycle ;
%Shape: Ellipse [id:dp3988926174843601]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (313.51,177.36) .. controls (313.51,176.56) and (314.26,175.91) .. (315.19,175.91) .. controls (316.13,175.91) and (316.88,176.56) .. (316.88,177.36) .. controls (316.88,178.16) and (316.13,178.81) .. (315.19,178.81) .. controls (314.26,178.81) and (313.51,178.16) .. (313.51,177.36) -- cycle ;
%Shape: Ellipse [id:dp04101225467897396]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (314.36,183.23) .. controls (314.36,182.43) and (315.12,181.78) .. (316.05,181.78) .. controls (316.98,181.78) and (317.74,182.43) .. (317.74,183.23) .. controls (317.74,184.03) and (316.98,184.68) .. (316.05,184.68) .. controls (315.12,184.68) and (314.36,184.03) .. (314.36,183.23) -- cycle ;
%Shape: Ellipse [id:dp5863915656225569]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (315.51,190.5) .. controls (315.51,189.7) and (316.26,189.05) .. (317.19,189.05) .. controls (318.13,189.05) and (318.88,189.7) .. (318.88,190.5) .. controls (318.88,191.3) and (318.13,191.95) .. (317.19,191.95) .. controls (316.26,191.95) and (315.51,191.3) .. (315.51,190.5) -- cycle ;
%Shape: Ellipse [id:dp17122444124667857]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (316.32,197.12) .. controls (316.32,196.32) and (317.07,195.67) .. (318,195.67) .. controls (318.94,195.67) and (319.69,196.32) .. (319.69,197.12) .. controls (319.69,197.92) and (318.94,198.57) .. (318,198.57) .. controls (317.07,198.57) and (316.32,197.92) .. (316.32,197.12) -- cycle ;
%Shape: Ellipse [id:dp595550673895106]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (317.99,205.03) .. controls (317.99,204.23) and (318.75,203.58) .. (319.68,203.58) .. controls (320.61,203.58) and (321.37,204.23) .. (321.37,205.03) .. controls (321.37,205.83) and (320.61,206.48) .. (319.68,206.48) .. controls (318.75,206.48) and (317.99,205.83) .. (317.99,205.03) -- cycle ;
%Shape: Ellipse [id:dp42805717802208254]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (326.92,171.49) .. controls (326.92,170.69) and (327.68,170.04) .. (328.61,170.04) .. controls (329.54,170.04) and (330.3,170.69) .. (330.3,171.49) .. controls (330.3,172.29) and (329.54,172.94) .. (328.61,172.94) .. controls (327.68,172.94) and (326.92,172.29) .. (326.92,171.49) -- cycle ;
%Shape: Ellipse [id:dp07574640518443809]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (328.6,177.24) .. controls (328.6,176.44) and (329.35,175.79) .. (330.28,175.79) .. controls (331.22,175.79) and (331.97,176.44) .. (331.97,177.24) .. controls (331.97,178.04) and (331.22,178.69) .. (330.28,178.69) .. controls (329.35,178.69) and (328.6,178.04) .. (328.6,177.24) -- cycle ;
%Shape: Ellipse [id:dp35961760720035785]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (329.99,183.35) .. controls (329.99,182.55) and (330.75,181.9) .. (331.68,181.9) .. controls (332.61,181.9) and (333.37,182.55) .. (333.37,183.35) .. controls (333.37,184.15) and (332.61,184.8) .. (331.68,184.8) .. controls (330.75,184.8) and (329.99,184.15) .. (329.99,183.35) -- cycle ;
%Shape: Ellipse [id:dp6949164860668007]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (331.93,190.1) .. controls (331.93,189.3) and (332.69,188.65) .. (333.62,188.65) .. controls (334.55,188.65) and (335.31,189.3) .. (335.31,190.1) .. controls (335.31,190.9) and (334.55,191.55) .. (333.62,191.55) .. controls (332.69,191.55) and (331.93,190.9) .. (331.93,190.1) -- cycle ;
%Shape: Ellipse [id:dp6551927674212119]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (333.76,197.24) .. controls (333.76,196.44) and (334.52,195.79) .. (335.45,195.79) .. controls (336.38,195.79) and (337.14,196.44) .. (337.14,197.24) .. controls (337.14,198.04) and (336.38,198.69) .. (335.45,198.69) .. controls (334.52,198.69) and (333.76,198.04) .. (333.76,197.24) -- cycle ;
%Shape: Ellipse [id:dp5972824761324165]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (335.71,205.03) .. controls (335.71,204.23) and (336.47,203.58) .. (337.4,203.58) .. controls (338.33,203.58) and (339.09,204.23) .. (339.09,205.03) .. controls (339.09,205.83) and (338.33,206.48) .. (337.4,206.48) .. controls (336.47,206.48) and (335.71,205.83) .. (335.71,205.03) -- cycle ;
%Shape: Ellipse [id:dp25895708663696104]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (340.46,171.49) .. controls (340.46,170.69) and (341.21,170.04) .. (342.15,170.04) .. controls (343.08,170.04) and (343.84,170.69) .. (343.84,171.49) .. controls (343.84,172.29) and (343.08,172.94) .. (342.15,172.94) .. controls (341.21,172.94) and (340.46,172.29) .. (340.46,171.49) -- cycle ;
%Shape: Ellipse [id:dp776678914241709]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (342.69,177) .. controls (342.69,176.2) and (343.45,175.55) .. (344.38,175.55) .. controls (345.31,175.55) and (346.07,176.2) .. (346.07,177) .. controls (346.07,177.8) and (345.31,178.45) .. (344.38,178.45) .. controls (343.45,178.45) and (342.69,177.8) .. (342.69,177) -- cycle ;
%Shape: Ellipse [id:dp7372524459660503]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (344.92,183.35) .. controls (344.92,182.55) and (345.68,181.9) .. (346.61,181.9) .. controls (347.54,181.9) and (348.3,182.55) .. (348.3,183.35) .. controls (348.3,184.15) and (347.54,184.8) .. (346.61,184.8) .. controls (345.68,184.8) and (344.92,184.15) .. (344.92,183.35) -- cycle ;
%Shape: Ellipse [id:dp24122491835471704]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (347.44,190.5) .. controls (347.44,189.7) and (348.19,189.05) .. (349.12,189.05) .. controls (350.06,189.05) and (350.81,189.7) .. (350.81,190.5) .. controls (350.81,191.3) and (350.06,191.95) .. (349.12,191.95) .. controls (348.19,191.95) and (347.44,191.3) .. (347.44,190.5) -- cycle ;
%Shape: Ellipse [id:dp7904451243351014]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (349.53,197) .. controls (349.53,196.2) and (350.28,195.55) .. (351.22,195.55) .. controls (352.15,195.55) and (352.91,196.2) .. (352.91,197) .. controls (352.91,197.8) and (352.15,198.45) .. (351.22,198.45) .. controls (350.28,198.45) and (349.53,197.8) .. (349.53,197) -- cycle ;
%Shape: Ellipse [id:dp4617144473175392]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (352.46,204.67) .. controls (352.46,203.87) and (353.22,203.22) .. (354.15,203.22) .. controls (355.08,203.22) and (355.84,203.87) .. (355.84,204.67) .. controls (355.84,205.47) and (355.08,206.12) .. (354.15,206.12) .. controls (353.22,206.12) and (352.46,205.47) .. (352.46,204.67) -- cycle ;
%Shape: Ellipse [id:dp626912606919074]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (354.97,171.49) .. controls (354.97,170.69) and (355.73,170.04) .. (356.66,170.04) .. controls (357.59,170.04) and (358.35,170.69) .. (358.35,171.49) .. controls (358.35,172.29) and (357.59,172.94) .. (356.66,172.94) .. controls (355.73,172.94) and (354.97,172.29) .. (354.97,171.49) -- cycle ;
%Shape: Ellipse [id:dp4306093121189267]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (357.48,177.12) .. controls (357.48,176.32) and (358.24,175.67) .. (359.17,175.67) .. controls (360.1,175.67) and (360.86,176.32) .. (360.86,177.12) .. controls (360.86,177.92) and (360.1,178.57) .. (359.17,178.57) .. controls (358.24,178.57) and (357.48,177.92) .. (357.48,177.12) -- cycle ;
%Shape: Ellipse [id:dp4919285418842567]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (359.86,183.23) .. controls (359.86,182.43) and (360.61,181.78) .. (361.54,181.78) .. controls (362.48,181.78) and (363.23,182.43) .. (363.23,183.23) .. controls (363.23,184.03) and (362.48,184.68) .. (361.54,184.68) .. controls (360.61,184.68) and (359.86,184.03) .. (359.86,183.23) -- cycle ;
%Shape: Ellipse [id:dp5744075183160424]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (362.65,189.82) .. controls (362.65,189.02) and (363.4,188.37) .. (364.34,188.37) .. controls (365.27,188.37) and (366.02,189.02) .. (366.02,189.82) .. controls (366.02,190.62) and (365.27,191.27) .. (364.34,191.27) .. controls (363.4,191.27) and (362.65,190.62) .. (362.65,189.82) -- cycle ;
%Shape: Ellipse [id:dp046203720018062944]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (366,197) .. controls (366,196.2) and (366.75,195.55) .. (367.68,195.55) .. controls (368.62,195.55) and (369.37,196.2) .. (369.37,197) .. controls (369.37,197.8) and (368.62,198.45) .. (367.68,198.45) .. controls (366.75,198.45) and (366,197.8) .. (366,197) -- cycle ;
%Shape: Ellipse [id:dp49972425736995807]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (369.21,204.67) .. controls (369.21,203.87) and (369.96,203.22) .. (370.89,203.22) .. controls (371.83,203.22) and (372.58,203.87) .. (372.58,204.67) .. controls (372.58,205.47) and (371.83,206.12) .. (370.89,206.12) .. controls (369.96,206.12) and (369.21,205.47) .. (369.21,204.67) -- cycle ;
%Shape: Ellipse [id:dp5024602360079904]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (367.39,171.49) .. controls (367.39,170.69) and (368.15,170.04) .. (369.08,170.04) .. controls (370.01,170.04) and (370.77,170.69) .. (370.77,171.49) .. controls (370.77,172.29) and (370.01,172.94) .. (369.08,172.94) .. controls (368.15,172.94) and (367.39,172.29) .. (367.39,171.49) -- cycle ;
%Shape: Ellipse [id:dp9654915371918213]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (370.18,177.12) .. controls (370.18,176.32) and (370.94,175.67) .. (371.87,175.67) .. controls (372.8,175.67) and (373.56,176.32) .. (373.56,177.12) .. controls (373.56,177.92) and (372.8,178.57) .. (371.87,178.57) .. controls (370.94,178.57) and (370.18,177.92) .. (370.18,177.12) -- cycle ;
%Shape: Ellipse [id:dp15713183567776468]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (373.53,183.35) .. controls (373.53,182.55) and (374.29,181.9) .. (375.22,181.9) .. controls (376.15,181.9) and (376.91,182.55) .. (376.91,183.35) .. controls (376.91,184.15) and (376.15,184.8) .. (375.22,184.8) .. controls (374.29,184.8) and (373.53,184.15) .. (373.53,183.35) -- cycle ;
%Shape: Ellipse [id:dp9239425899364824]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (377.52,190.32) .. controls (377.52,189.52) and (378.28,188.87) .. (379.21,188.87) .. controls (380.14,188.87) and (380.9,189.52) .. (380.9,190.32) .. controls (380.9,191.12) and (380.14,191.77) .. (379.21,191.77) .. controls (378.28,191.77) and (377.52,191.12) .. (377.52,190.32) -- cycle ;
%Shape: Ellipse [id:dp9110579702631929]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (381.35,196.88) .. controls (381.35,196.08) and (382.1,195.43) .. (383.04,195.43) .. controls (383.97,195.43) and (384.72,196.08) .. (384.72,196.88) .. controls (384.72,197.68) and (383.97,198.33) .. (383.04,198.33) .. controls (382.1,198.33) and (381.35,197.68) .. (381.35,196.88) -- cycle ;
%Shape: Ellipse [id:dp24310198218055246]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (385.67,204.67) .. controls (385.67,203.87) and (386.43,203.22) .. (387.36,203.22) .. controls (388.29,203.22) and (389.05,203.87) .. (389.05,204.67) .. controls (389.05,205.47) and (388.29,206.12) .. (387.36,206.12) .. controls (386.43,206.12) and (385.67,205.47) .. (385.67,204.67) -- cycle ;
%Shape: Ellipse [id:dp7388999956457485]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (381.21,171.49) .. controls (381.21,170.69) and (381.96,170.04) .. (382.9,170.04) .. controls (383.83,170.04) and (384.58,170.69) .. (384.58,171.49) .. controls (384.58,172.29) and (383.83,172.94) .. (382.9,172.94) .. controls (381.96,172.94) and (381.21,172.29) .. (381.21,171.49) -- cycle ;
%Shape: Ellipse [id:dp5640310139705571]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (384,177) .. controls (384,176.2) and (384.75,175.55) .. (385.69,175.55) .. controls (386.62,175.55) and (387.38,176.2) .. (387.38,177) .. controls (387.38,177.8) and (386.62,178.45) .. (385.69,178.45) .. controls (384.75,178.45) and (384,177.8) .. (384,177) -- cycle ;
%Shape: Ellipse [id:dp2695616969380312]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (387.63,183.23) .. controls (387.63,182.43) and (388.38,181.78) .. (389.32,181.78) .. controls (390.25,181.78) and (391,182.43) .. (391,183.23) .. controls (391,184.03) and (390.25,184.68) .. (389.32,184.68) .. controls (388.38,184.68) and (387.63,184.03) .. (387.63,183.23) -- cycle ;
%Shape: Ellipse [id:dp4126882239946579]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (391.49,190.24) .. controls (391.49,189.44) and (392.25,188.79) .. (393.18,188.79) .. controls (394.11,188.79) and (394.87,189.44) .. (394.87,190.24) .. controls (394.87,191.04) and (394.11,191.69) .. (393.18,191.69) .. controls (392.25,191.69) and (391.49,191.04) .. (391.49,190.24) -- cycle ;
%Shape: Ellipse [id:dp7640055339758918]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (395.16,197) .. controls (395.16,196.2) and (395.92,195.55) .. (396.85,195.55) .. controls (397.78,195.55) and (398.54,196.2) .. (398.54,197) .. controls (398.54,197.8) and (397.78,198.45) .. (396.85,198.45) .. controls (395.92,198.45) and (395.16,197.8) .. (395.16,197) -- cycle ;
%Shape: Ellipse [id:dp8721356938843838]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (399.35,204.79) .. controls (399.35,203.99) and (400.11,203.34) .. (401.04,203.34) .. controls (401.97,203.34) and (402.73,203.99) .. (402.73,204.79) .. controls (402.73,205.59) and (401.97,206.24) .. (401.04,206.24) .. controls (400.11,206.24) and (399.35,205.59) .. (399.35,204.79) -- cycle ;
%Straight Lines [id:da7979534893976028]
\draw [color={rgb, 255:red, 127; green, 117; blue, 117 }  ,draw opacity=1 ] [dash pattern={on 4.5pt off 4.5pt}]  (287.87,73.06) -- (287.87,183.38) ;
%Straight Lines [id:da03397341825975597]
\draw    (176.12,166.91) -- (148.03,213.62) ;
%Straight Lines [id:da855504113906919]
\draw    (148.03,213.62) -- (151.25,213.56) ;
%Straight Lines [id:da7263472575025891]
\draw    (176.12,166.91) -- (179.34,166.85) ;
%Straight Lines [id:da3871270427067002]
\draw    (420.92,213.12) -- (424.14,213.05) ;
%Straight Lines [id:da5505655212811509]
\draw    (393.8,167) -- (397.02,166.94) ;
%Straight Lines [id:da3454569240651897]
\draw    (397.02,166.94) -- (424.14,213.05) ;
%Straight Lines [id:da9496307475947867]
\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (159.76,153.9) -- (179.23,153.7) ;
\draw [shift={(182.23,153.66)}, rotate = 539.39] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da7018774365527356]
\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (159.76,153.9) -- (150.65,164.89) ;
\draw [shift={(148.74,167.2)}, rotate = 309.65999999999997] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Shape: Wave [id:dp8230250028099939]
\draw  [color={rgb, 255:red, 229; green, 21; blue, 21 }  ,draw opacity=1 ][line width=1.5]  (287.6,178.6) .. controls (302.2,174.36) and (316.1,170.3) .. (316.1,165.6) .. controls (316.1,160.9) and (302.2,156.84) .. (287.6,152.6) .. controls (273,148.36) and (259.1,144.3) .. (259.1,139.6) .. controls (259.1,134.9) and (273,130.84) .. (287.6,126.6) .. controls (302.2,122.36) and (316.1,118.3) .. (316.1,113.6) .. controls (316.1,108.9) and (302.2,104.84) .. (287.6,100.6) .. controls (273,96.36) and (259.1,92.3) .. (259.1,87.6) .. controls (259.1,83.15) and (271.51,79.29) .. (285.19,75.3) ;
%Straight Lines [id:da5686545133121326]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287.8,80.6) -- (275.2,80.6) ;
\draw [shift={(272.2,80.6)}, rotate = 360] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da782823803042028]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.2,94.2) -- (275.2,94.53) ;
\draw [shift={(272.2,94.6)}, rotate = 358.57] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da871137874278286]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.6,87.2) -- (262.4,87.74) ;
\draw [shift={(259.4,87.8)}, rotate = 358.82] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da5553069086130265]
\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (159.76,153.9) -- (159.8,134) ;
\draw [shift={(159.8,131)}, rotate = 450.09] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da6699653458590744]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.2,120.6) -- (299.6,120.6) ;
\draw [shift={(302.6,120.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da2953745491779931]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.6,106.6) -- (301.6,106.6) ;
\draw [shift={(304.6,106.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da7676872185404988]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287.8,114) -- (312,113.47) ;
\draw [shift={(315,113.4)}, rotate = 538.74] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da6047601791922992]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287.8,132.2) -- (275.2,132.2) ;
\draw [shift={(272.2,132.2)}, rotate = 360] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da08573309540969332]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.2,145.8) -- (275.2,146.13) ;
\draw [shift={(272.2,146.2)}, rotate = 358.57] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da0011618805281727873]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.6,138.8) -- (262.4,139.34) ;
\draw [shift={(259.4,139.4)}, rotate = 358.82] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da8026810749325723]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287,172.6) -- (298.4,172.6) ;
\draw [shift={(301.4,172.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da18748197647149523]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287.4,158.6) -- (300.4,158.6) ;
\draw [shift={(303.4,158.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da8245101205852268]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (286.6,166) -- (310.8,165.47) ;
\draw [shift={(313.8,165.4)}, rotate = 538.74] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da7887384290153587]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (229.92,180.08) -- (229.78,134.23) ;
\draw [shift={(229.77,130.23)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
%Straight Lines [id:da8482623274180794]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (250.23,180.08) -- (250.23,134.23) ;
\draw [shift={(250.23,130.23)}, rotate = 450] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
%Straight Lines [id:da28732418115198444]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (270.38,180.08) -- (270.24,134.38) ;
\draw [shift={(270.23,130.38)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
%Straight Lines [id:da23686823952523528]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (290.38,179.92) -- (290.24,134.23) ;
\draw [shift={(290.23,130.23)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
%Straight Lines [id:da3497985465503395]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (310.23,180.08) -- (310.09,134.38) ;
\draw [shift={(310.08,130.38)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
%Straight Lines [id:da4475685784611998]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (330.08,180.23) -- (329.94,134.54) ;
\draw [shift={(329.92,130.54)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;

% Text Node
\draw (134.77,155.14) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {$\mathbf{x}$};
% Text Node
\draw (183.93,136.77) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {$\mathbf{y}$};
% Text Node
\draw (145.06,72.2) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {\begin{minipage}[lt]{74.95912pt}\setlength\topsep{0pt}
\begin{center}
\textcolor[rgb]{0.82,0.01,0.11}{{\fontfamily{helvet}\selectfont Dressing Field's}}\\\textcolor[rgb]{0.82,0.01,0.11}{{\fontfamily{helvet}\selectfont Elctric Field}}
\end{center}

\end{minipage}};
% Text Node
\draw (145.93,116.37) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {$\mathbf{z}$};
% Text Node
\draw (347.46,140.94) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {\begin{minipage}[lt]{69.05196000000001pt}\setlength\topsep{0pt}
\begin{center}
\textcolor[rgb]{0.08,0.35,0.57}{{\fontfamily{helvet}\selectfont Magnetic Field}}
\end{center}

\end{minipage}};

\end{tikzpicture}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2021-04-06 theory/M2DEG.tex
Add forced oscillator solution

@@
 \begin{equation} \label{1.18}
-    i \hbar \pdv{\psi}{t} = \hat{H}_e(t)\psi
+    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi
 \end{equation}
@@
   \begin{aligned}
-    \text{L.H.S} & = i \hbar \pdv{\psi}{t} =
-    i \hbar \bigg( \pdv{\varphi}{t} \phi + \pdv{\phi}{t} \varphi \bigg) =
+    \text{L.H.S} & = i \hbar \dv{\psi}{t} =
+    i \hbar \bigg( \dv{\varphi}{t} \phi + \dv{\phi}{t} \varphi \bigg) =
     i \hbar \bigg(
       \Big[\frac{-ieEy}{\hbar}\sin(\omega t)\Big]\varphi\phi +
-      \varphi  \pdv{\phi}{t}
+      \varphi  \dv{\phi}{t}
     \bigg) \\
@@
     \big[{eEy}\sin(\omega t)\big]\varphi\phi +
-    i \hbar\varphi  \pdv{\phi}{t}
+    i \hbar\varphi  \dv{\phi}{t}
   \end{aligned}
@@
     \big[{eEy}\sin(\omega t)\big]\varphi\phi +
-    i \hbar\varphi  \pdv{\phi}{t}
+    i \hbar\varphi  \dv{\phi}{t}
     =
@@
     \pdv[2]{y}
-    - i \hbar \pdv{t}
+    - i \hbar \dv{t}
+    \bigg]
+    \phi(y,t) = 0.
+  \end{aligned}
+\end{equation}
+If we turn off the external dressing field, this equation leads to simple harmonic oscillator Hamiltonian as follows
+\begin{equation} \label{1.30}
+  \begin{aligned}
+    \bigg[
+    \frac{m_e \omega_0^2}{2}y^2
+    -
+    \frac{\hbar^2}{2m_e}
+    \pdv[2]{y}
+    - i \hbar \dv{t}
     \bigg]
@@
 \end{equation}
+\begin{equation} \label{1.31}
+  \begin{aligned}
+     i \hbar \dv{\phi(y,t)}{t} =
+    \bigg[
+    \frac{\hat{p}_y^2}{2m_e} +
+    \frac{1}{2}m_e \omega_0^2y^2
+    \bigg]
+    \phi(y,t).
+  \end{aligned}
+\end{equation}
+Therefore we can identify the $S(t) \equiv eE\sin(\omega t)$ part as a external force act on the harmonic oscillator and we can solve this as a forced harmonic oscillator in $y$ axis.
+\begin{equation} \label{1.32}
+  \begin{aligned}
+    i \hbar \dv{\phi(y,t)}{t} =
+    \bigg[
+    -
+    \frac{\hbar^2}{2m_e}
+    \pdv[2]{y} +
+    \frac{1}{2}m_e \omega_0^2y^2
+    - yS(t)]
+    \bigg]
+    \phi(y,t).
+  \end{aligned}
+\end{equation}
+This system can be extacly solvable and we can solve this equation using the methods explained by Husimi [*1] as follows.
+
+\noindent
+First we can introduce the time dependent shifted corrdinte as
+\begin{equation} \label{1.33}
+    y \rightarrow y' = y - \zeta(t) \quad \Rightarrow \quad
+    y = y' + \zeta(t)
+\end{equation}
+and this implies that
+\begin{equation} \label{1.34}
+    \dv{\phi(y',t)}{t} = \pdv{\phi(y',t)}{t} + \pdv{\phi(y',t)}{y'}\pdv{y'}{t} =
+    \pdv{\phi(y',t)}{t} - \dot{\zeta}(t)\pdv{\phi(y',t)}{y'}
+\end{equation}
+where $\dot{\zeta}(t) = \pdv{\zeta(t)}{t}$.
+Therefore, Eq. \eqref{1.32} will be modified to
+\begin{equation} \label{1.35}
+  \begin{aligned}
+    i \hbar \pdv{\phi(y',t)}{t}  =
+    \bigg[
+    i \hbar\dot{\zeta}\pdv{y'}
+    -
+    \frac{\hbar^2}{2m_e}
+    \pdv[2]{{y'}} +
+    \frac{1}{2}m_e \omega_0^2(y' + \zeta)^2
+    - (y' + \zeta) S(t)
+    \bigg]
+    \phi(y',t).
+  \end{aligned}
+\end{equation}
+Let's tranform the wave function using following unitary trasnform
+\begin{equation} \label{1.36}
+    \phi(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t)
+\end{equation}
+and subtitte this into the Eq. \eqref{1.35} and we will get the following
+\begin{equation} \label{1.37}
+  \text{R.H.S} =  \bigg[ i \hbar \pdv{t} -
+i \hbar \Big(\frac{im_e \ddot{\zeta} y'}{\hbar}\Big)\bigg]  \exp(\frac{-im_e\dot{\zeta}y'}{\hbar})\varphi(y',t)
+\end{equation}
+and
+\begin{equation} \label{1.38}
+  \begin{aligned}
+    \text{L.H.S} & =  \bigg[
+      i \hbar \dot{\zeta}  \Big(\frac{im_e \dot{\zeta}}{\hbar}\Big)  +
+      i \hbar \dot{\zeta} \pdv{y'} \\
+      &
+      -
+      \frac{\hbar^2}{2m_e}\Big[
+        \Big(\frac{im_e \dot{\zeta}}{\hbar}\Big)^2
+        + \Big(\frac{2im_e \dot{\zeta}}{\hbar}\Big) \pdv{{y'}}
+        + \pdv[2]{{y'}}
+      \Big] \\
+      &
+      +\frac{1}{2}m_e\omega_0^2 {y'}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 +
+      m_e\omega_0^2 y'\zeta \\
+      & -
+      y'S(t) - \zeta S(t)
+    \bigg]  \exp(\frac{-im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
+  \end{aligned}
+\end{equation}
+Combining these two we get derive that
+\begin{equation} \label{1.39}
+  \begin{aligned}
+    i \hbar \pdv{\varphi(y',t)}{t}   =
+    \bigg[
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
+        & + \frac{1}{2} m_e \omega_0^2 y'^2 +
+        \Big[
+            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
+        \Big]y' \\
+        &
+        +
+        \Big[
+            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
+        \Big]
+    \bigg]\varphi(y',t).
+  \end{aligned}
+\end{equation}
+Then we can restrict our $\zeta(t)$ function such that
+\begin{equation} \label{1.40}
+  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t)
+\end{equation}
+and that leads to
+\begin{equation} \label{1.41}
+  \begin{aligned}
+    i \hbar \pdv{\varphi(y',t)}{t}   =
+    \bigg[
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
+        + \frac{1}{2} m_e \omega_0^2 {y'}^2
+        - L(\zeta,\dot{\zeta},t)
+    \bigg]\varphi(y',t)
+  \end{aligned}
+\end{equation}
+where
+\begin{equation} \label{1.42}
+  L(\zeta,\dot{\zeta},t) \equiv \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t)
+\end{equation}
+is the largrangian of a driven oscillator.
+
+\noindent
+Now introduce new unitary transormation for the wavefunction as follows
+\begin{equation} \label{1.43}
+    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t)
+\end{equation}
+and subtite this into the Eq. \eqref{1.41} and gets
+\begin{equation} \label{1.44}
+  \begin{aligned}
+    i \hbar \bigg[
+      & \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \pdv{t}
+      +
+      i \hbar L(\zeta,\dot{\zeta},t) \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t'))
+    \bigg]\chi(y',t) \\
+    & =
+    \bigg[
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
+        + \frac{1}{2} m_e \omega_0^2 {y'}^2
+        - L(\zeta,\dot{\zeta},t)
+    \bigg] \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t)
+  \end{aligned}
+\end{equation}
+and finally we can derive that
+\begin{equation} \label{1.45}
+  \begin{aligned}
+    i \hbar \pdv{t} \chi(y',t)  =
+    \bigg[
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
+        + \frac{1}{2} m_e \omega_0^2 {y'}^2
+    \bigg] \chi(y',t).
+  \end{aligned}
+\end{equation}
+This is the well known Schrodinger equation of a stationary harmonic oscillator.
+In terms of the eigenvalues
+\begin{equation} \label{1.46}
+  E_n = \hbar \omega_0 \big(n + \frac{1}{2}\big)
+\end{equation}
+of well-known harmonic eigenfucntions
+\begin{equation} \label{1.47}
+  \chi_n(y') = \frac{1}{\sqrt{2^{n}n!}}  \cdot
+  \bigg(\frac{m_e\omega_0}{\pi \hbar}\bigg)^{1/4}
+  \cdot e^{-\frac{m_e\omega_0 y'^2}{2\hbar}} \cdot
+  \mathcal{H}_n \bigg(\sqrt{\frac{m_e \omega_0}{\hbar}}y'\bigg)
+\end{equation}
+being propositional to the Hermite functions $\mathcal{H}_n$, the solutions of Eq. \eqref{1.32} can be represent as
+\begin{equation} \label{1.48}
+  \phi_n(y,t) = \chi_n(y - \zeta(t))
+  \exp(\frac{i}{\hbar}\bigg[- E_nt +
+  m_e\dot{\zeta(t)}\big(y-\zeta(t)\big)
+   + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg])
+\end{equation}
+The set $\chi(y)$ forms a complete set and thus ay general solution $\phi_(y,t)$ can be expaned in terms of the solutions in Eq. \eqref{1.48}.
+
+\noindent
+Next we consider special case where we assumed
+\begin{equation} \label{1.49}
+  S(t) = eE\sin(\omega t)
+\end{equation}
+and one can derive the Eq. \eqref{1.40} for $\zeta(t)$
+\begin{equation} \label{1.50}
+  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = eE\sin(\omega t)
+\end{equation}
+and using Green function method the solution can be write as
+\begin{equation} \label{1.51}
+  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
+\end{equation}
+form this solution we are able to derive the final solution for the forced harmonic oscillator. \hfill$\blacksquare$
 

### 2021-04-06 theory/M2DEG.tex
Add final solution for Schrodinger equation

@@
 \end{equation}
-form this solution we are able to derive the final solution for the forced harmonic oscillator. \hfill$\blacksquare$
+form this solutions we are able to derive the final solutions $(n=0,1,...)$ would be
+\begin{equation} \label{1.52}
+  \begin{aligned}
+    \phi_n(x,y,t)  = & \frac{1}{\sqrt{L_x}} \chi_n\big(y - \zeta(t)\big) \\
+    & \times
+      \exp(
+     \frac{i}{\hbar}\bigg[- E_nt +
+    p_x x +
+    \frac{eEy}{\omega}\cos(\omega t)+
+    m_e\dot{\zeta(t)}\big[y-\zeta(t)\big]
+     + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg])
+  \end{aligned}
+\end{equation}
+and the exponential phase shifts represent the effect done by the stationary magnetic field and strong dressing field.Therefore we can assume that the magnetitranport properties of 2DEG will be renormalized by the magnetic field as well as the dressing field.
+\hfill$\blacksquare$
 

### 2021-04-07 theory/M2DEG.tex
Add scattering theory

@@
   \begin{aligned}
-    \phi_n(x,y,t)  = & \frac{1}{\sqrt{L_x}} \chi_n\big(y - \zeta(t)\big) \\
+    \psi_n(x,y,t)  = & \frac{1}{\sqrt{L_x}} \chi_n\big(y - \zeta(t)\big) \\
     & \times
@@
 
+\section{Scattering theory}
+
+Since in a real metal there would be many scatters that can be behave as obstacles for electron that have free wave functions.
+Therefore we need to calculate them to analyse the real behaviour of the electrons.
+
+\noindent
+Then the wave function of the electron in a real matel $\Psi(\vb{r},t)$ should satisfy the following time-dependet Schrodinger equation
+\begin{equation} \label{2.1}
+  i \hbar \pdv{\Psi(\vb{r},t)}{t} = [H_e(t) + U(\vb{r})] \Psi(\vb{r},t)
+\end{equation}
+where $U(\vb{r})$ is the total scattering potential.
+We have represented the all scatters using this potential.
+Since the solutions \eqref{1.52} are create a complete orthonormal basis we can represent this wave function using those as follows
+\begin{equation} \label{2.2}
+  \Psi(\vb{r},t) = \sum_j a_j(t) \ket{\psi_j(t)}
+\end{equation}
+where the difference inidces j corresponding to the different sets of all quantum numbers $p_x$ and $n$
+\begin{equation} \label{2.3}
+  j \rightarrow (m,n) \quad \text{where} \quad
+  m,n =0,1,2,...
+\end{equation}
+with $m$ is defined for quantized momentum in $x$ direction
+\begin{equation} \label{2.4}
+  p_x = m \frac{2\pi \hbar}{L_x}
+\end{equation}
+
+\noindent
+Now we can use the conventional pertubation theory to calculate scattering process of electron at a state $\ket{\psi_j}$ to a state $\ket{\psi_j'}$.
+For that assume an electron be in the $j$ state at the time $t=0$ and corresponding $a_j'(0) = \delta_{j,j'}$.
+
+\noindent
+First subtitute a general electron state $\Psi(\vb{r},t)$ at time $t$ as the incoming electron to the Schrodinger equation given in Eq. \eqref{2.1}
+\begin{equation} \label{2.5}
+  i \hbar \pdv{t} \sum_j a_j(t) \ket{\psi_j(t)}= [H_e(t) + U(\vb{r})] \sum_j a_j(t) \ket{\psi_j(t)}
+\end{equation}
+\begin{equation} \label{2.6}
+  i \hbar\sum_j   \dot{a_j}(t) \ket{\psi_j(t)} + a_j(t)\pdv{t}\ket{\psi_j(t)}= [H_e(t) + U(\vb{r})] \sum_j a_j(t) \ket{\psi_j(t)}
+\end{equation}
+since all the ${\ket{\psi(t)}}$ staistfy the Schrodinger equation \eqref{1.18}
+\begin{equation} \label{2.7}
+  i \hbar\sum_j   \dot{a_j}(t) \ket{\psi_j(t)} = \sum_j U(\vb{r}) a_j(t) \ket{\psi_j(t)}.
+\end{equation}
+Then take inner product with state with the state $\ket{\psi_{j'}(t)}$
+\begin{equation} \label{2.8}
+  i \hbar\sum_j   \dot{a_j}(t) \braket{\psi_{j'}(t)}{\psi_j(t)} = \sum_j
+  a_j(t) \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
+\end{equation}
+But using the \textit{Born approximation} we can assume that this incoming wave have the initial state of the electron at $t=0$ and therefore this equation will modified to
+\begin{equation} \label{2.9}
+  i \hbar\sum_j   \dot{a_j}(t) \braket{\psi_{j'}(t)}{\psi_j(t)} =
+  \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
+\end{equation}
+due to orthonormality this becomes
+\begin{equation} \label{2.10}
+  i \hbar \dot{a_{j'}}(t) =
+  \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
+\end{equation}
+and finally this leads to first order pertubation theory for Sscattering as follows
+\begin{equation} \label{2.11}
+   \dot{a_{j'}}(t) =
+  -\frac{i}{\hbar}\bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
+\end{equation}
+where
+\begin{equation} \label{2.12}
+   a_{j'}(t) =
+  -\frac{i}{\hbar}
+  \int_0^t dt' \int_S d\vb{r} \;
+  \psi_{j'}^{*} (\vb{r},t') U(\vb{r}) {\psi_j(\vb{r},t')}
+\end{equation}
+where the integration should be performed over the 2DEG area $S=L_xL_y$. Then we can calculate this using the eqution we derived in \eqref{1.52} as follows
+
 \end{document}

### 2021-04-09 theory/M2DEG.tex
Add scattering calculations

--- 2021-04-06 theory/M2DEG.tex
@@
 
-\section{Schrödinger problem for Landau levels in dressed 2DEG}
-
-Our analysis is consider on 2 dimentional electronic gas which has distrubuted in $(x,y)$ plane in configuration space. We are going to examine the properties of 2DEG with stationary magnetic field
-\begin{equation} \label{1.1}
-  \vb{B} = (0,0,B)^T
-\end{equation}
-which directed on $z$ axis and a linearly $y$-polarized strong electomagnetic wave (dressing field) with electric field given by
-\begin{equation} \label{1.2}
-  \vb{E} = (0,E\sin(\omega t),0)^T
-\end{equation}
-which also propagate in $z$ direction. Here $B$ and $E$ represent the amplitude of the stationary magnetic field and electric field of dressing field.
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.9]{figures/fig1.pdf}
-  \caption{Stationary magnetic filed (blue color) and Strong EM wave (red color) applied to the 2DEG.}
-  \label{fig:1.1}
-\end{figure}
-
-\noindent
-Using Landau gauge for the stationary magnetic field we can represent it using vector potential as
-\begin{equation} \label{1.3}
-  \vb{A}_{s} = (-By,0,0)^T
-\end{equation}
-and choosing Coulomb gauge the dressing field can be present as the following vector potential
-\begin{equation} \label{1.4}
-  \vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^T.
-\end{equation}
-Now the Hamiltonian of an electron in 2DEG can be reads as
-\begin{equation} \label{1.5}
-  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big(\vb{A}_{s}+\vb{A}_{d}(t)\big)\Big]^2
-\end{equation}
-where $m_e$ is the effective mass of the electron and $e$ is the magnitude (without considering the sign of the charge) of the electron charge. This can be simplified to
-\begin{equation} \label{1.6}
-  \hat{H}_e(t) = \frac{1}{2m_e}\Big[
-    (\hat{p}_x + eBy)\vb{e}_x +
-    (\hat{p}_y - \frac{eE}{\omega}\cos(\omega t))\vb{e}_y
-  \Big]^2
-\end{equation}
-where $\vb{e}_x$ and $\vb{e}_y$ are unit vectors along $x$ and $y$ directions respectively. Moreover,
-\begin{equation} \label{1.7}
-  \hat{H}_e(t) = \frac{1}{2m_e}\Big[
-    (\hat{p}_x + eBy)^2 +
-    (\hat{p}_y - \frac{eE}{\omega}\cos(\omega t))^2
-  \Big]
-\end{equation}
-Since $[\hat{H}_e(t),\hat{p}_x] =0$ both operators share same eigenvalue and eigen functions which are free electron wave functions. Therefore we can modify the Hamiltonian as follows
-\begin{equation} \label{1.8}
-  \hat{H}_e(t) = \frac{1}{2m_e}\Big[
-    ({p}_x + eBy)^2 +
-    (\hat{p}_y - \frac{eE}{\omega}\cos(\omega t))^2
-  \Big].
-\end{equation}
-Using momentum operator definition
-\begin{equation} \label{1.9}
-  \hat{p}_y = -i\hbar \pdv{y}
-\end{equation}
-we can modify Eq. \eqref{1.8} as
-\begin{equation} \label{1.10}
-  \begin{aligned}
-    \hat{H}_e(t) & = \frac{1}{2m_e}\Big[
-      ({p}_x + eBy)^2 +
-      \Big(-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\Big)^2
-    \Big] \\
-    & = \frac{1}{2m_e}\Big[
-      ({p}_x + eBy)^2 +
-      \Big(i\hbar \pdv{y} + \frac{eE}{\omega}\cos(\omega t)\Big)^2
-    \Big].
-  \end{aligned}
-\end{equation}
-Define the \textit{center of the cyclotron orbit} along $y$ axis as
-\begin{equation} \label{1.11}
-  y_0 \equiv \frac{-p_x}{eB}
-\end{equation}
-and the \textit{cyclotron frequency} as
-\begin{equation} \label{1.12}
-  \omega_0 \equiv \frac{eB}{m_e}.
-\end{equation}
-Then the Hamiltonian will leads to
-\begin{equation} \label{1.13}
-    \hat{H}_e(t) =
-      \frac{m_e \omega_0^2}{2}(y-y_0)^2 +
-      \frac{1}{2m_e}\Big(i\hbar \pdv{y}+\frac{eE}{\omega}\cos(\omega t)\Big)^2
-\end{equation}
-\begin{equation} \label{1.14}
-  \begin{aligned}
-    \hat{H}_e(t) =
-      \frac{m_e \omega_0^2}{2}(y-y_0)^2 +
-      \frac{1}{2m_e}\Big(
-      -\hbar^2 \pdv[2]{y} & +
-      i\hbar \pdv{y}\bigg[\frac{eE}{\omega}\cos(\omega t) \bigg] \\ & +
-      \frac{i\hbar eE}{\omega}\cos(\omega t) \pdv{y}+
-      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
-      \Big)
-  \end{aligned}
-\end{equation}
-\begin{equation} \label{1.15}
-  \begin{aligned}
-    \hat{H}_e(t) =
-      \frac{m_e \omega_0^2}{2}(y-y_0)^2 +
-      \frac{1}{2m_e}\Big(
-      -\hbar^2 \pdv[2]{y} +
-      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{y}+
-      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
-      \Big).
-  \end{aligned}
-\end{equation}
-Let
-\begin{equation} \label{1.16}
-    (y - y_0) \rightarrow y
-\end{equation}
-and then this becomes
-\begin{equation} \label{1.17}
-  \begin{aligned}
-    \hat{H}_e(t) =
-      \frac{m_e \omega_0^2}{2}y^2 +
-      \frac{1}{2m_e}\Big(
-      -\hbar^2 \pdv[2]{y} +
-      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{y}+
-      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
-      \Big).
-  \end{aligned}
-\end{equation}
-Now assume that the solution for the time-dependent schrödinger equation
-\begin{equation} \label{1.18}
-    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi
-\end{equation}
-can be represent by the following form
-\begin{equation} \label{1.19}
-    \psi(\vb{r},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
-      \frac{ip_x x}{\hbar} +
-      \frac{ieE(y-y_0)}{\hbar \omega}\cos(\omega t)
-    \bigg) \phi(y-y_0,t).
-\end{equation}
-Using the same subtution from Eq. \eqref{1.16} this becomes
-\begin{equation} \label{1.20}
-    \psi(x,y,t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
-      \frac{ip_x x}{\hbar} +
-      \frac{ieEy}{\hbar \omega}\cos(\omega t)
-    \bigg) \phi(y,t).
-\end{equation}
-Defining
-\begin{equation} \label{1.21}
-    \varphi(x,y,t) \equiv \frac{1}{\sqrt{L_x}} \exp\bigg(
-      \frac{ip_x x}{\hbar} +
-      \frac{ieEy}{\hbar \omega}\cos(\omega t)
-    \bigg)
-\end{equation}
-we can simply the the Eq. \eqref{1.20} as
-\begin{equation} \label{1.22}
-    \psi(x,y,t) = \varphi(x,y,t) \phi(y,t).
-\end{equation}
-Let's subtitue Eq. \eqref{1.20} and Eq. \eqref{1.17} into Eq. \eqref{1.18} and we can observe that
-\begin{equation} \label{1.23}
-  \begin{aligned}
-    \text{L.H.S} & = i \hbar \dv{\psi}{t} =
-    i \hbar \bigg( \dv{\varphi}{t} \phi + \dv{\phi}{t} \varphi \bigg) =
-    i \hbar \bigg(
-      \Big[\frac{-ieEy}{\hbar}\sin(\omega t)\Big]\varphi\phi +
-      \varphi  \dv{\phi}{t}
-    \bigg) \\
-    & =
-    \big[{eEy}\sin(\omega t)\big]\varphi\phi +
-    i \hbar\varphi  \dv{\phi}{t}
-  \end{aligned}
-\end{equation}
-and
-\begin{equation} \label{1.24}
-  \begin{aligned}
-    \text{R.H.S} & = \hat{H}_e(t)\psi \\
-    & =
-    \bigg[
-    \frac{m_e \omega_0^2}{2}y^2 +
-    \frac{1}{2m_e}\Big(
-    -\hbar^2 \pdv[2]{y} +
-    \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{y}+
-    \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
-    \Big) \bigg]
-    \varphi\phi
-  \end{aligned}
-\end{equation}
-where we will can calculate this part by part as follows:
-\begin{equation} \label{1.25}
-  \begin{aligned}
-    \frac{-\hbar^2}{2m_e}\pdv[2]{y}(\varphi\phi) & =
-    \frac{-\hbar^2}{2m_e} \pdv{y}\bigg[
-      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)\varphi\phi +
-      \varphi\pdv{\phi}{y}
-    \bigg] \\
-    & =
-    \frac{-\hbar^2}{2m_e} \bigg[
-      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)^2\varphi\phi +
-      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)\varphi\pdv{\phi}{y} +
-      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)\varphi\pdv{\phi}{y} +
-      \varphi\pdv[2]{\phi}{y}
-    \bigg] \\
-    & =
-    \Big(\frac{e^2E^2}{ 2m_e\omega^2} \cos[2](\omega)t\Big)\varphi\phi -
-    \Big(\frac{ieE \hbar}{m_e\omega} \cos(\omega)t\Big)\varphi\pdv{\phi}{y} -
-    \frac{\hbar^2}{2m_e}
-    \varphi\pdv[2]{\phi}{y}
-  \end{aligned}
-\end{equation}
-and
-\begin{equation} \label{1.26}
-  \begin{aligned}
-    \frac{2i\hbar eE}{2m_e\omega}\cos(\omega t) \pdv{y} (\varphi\phi)& =
-    \frac{i\hbar eE}{m_e\omega}\cos(\omega t)
-    \bigg[
-      \Big(\frac{ieE}{\hbar \omega} \cos(\omega)t\Big)\varphi\phi +
-      \varphi\pdv{\phi}{y}
-    \bigg] \\
-    & =
-    \Big(\frac{-e^2E^2}{m_e\omega^2} \cos(\omega)t\Big)\varphi\phi +
-    \frac{i\hbar eE}{m_e\omega}\cos(\omega t)\varphi\pdv{\phi}{y}.
-  \end{aligned}
-\end{equation}
-Therefore we can derive that
-\begin{equation} \label{1.27}
-  \begin{aligned}
-    \text{R.H.S} =
-    \bigg[
-    \frac{m_e \omega_0^2}{2}y^2
-    -
-    \frac{\hbar^2}{2m_e}
-    \varphi\pdv[2]{\phi}{y} \bigg]
-    \varphi\phi.
-  \end{aligned}
-\end{equation}
-To satisfy the condition L.H.S$=$R.H.S we need to find a function $\phi(y,t)$ such that
-\begin{equation} \label{1.28}
-  \begin{aligned}
-    \big[{eEy}\sin(\omega t)\big]\varphi\phi +
-    i \hbar\varphi  \dv{\phi}{t}
-    =
-    \bigg[
-    \frac{m_e \omega_0^2}{2}y^2
-    -
-    \frac{\hbar^2}{2m_e}
-    \varphi\pdv[2]{\phi}{y} \bigg]
-    \varphi\phi
-  \end{aligned}
-\end{equation}
-which can be simplyfied as
-\begin{equation} \label{1.29}
-  \begin{aligned}
-    \bigg[
-    \frac{m_e \omega_0^2}{2}y^2
-    - {eEy}\sin(\omega t)
-    -
-    \frac{\hbar^2}{2m_e}
-    \pdv[2]{y}
-    - i \hbar \dv{t}
-    \bigg]
-    \phi(y,t) = 0.
-  \end{aligned}
-\end{equation}
-If we turn off the external dressing field, this equation leads to simple harmonic oscillator Hamiltonian as follows
-\begin{equation} \label{1.30}
-  \begin{aligned}
-    \bigg[
-    \frac{m_e \omega_0^2}{2}y^2
-    -
-    \frac{\hbar^2}{2m_e}
-    \pdv[2]{y}
-    - i \hbar \dv{t}
-    \bigg]
-    \phi(y,t) = 0
-  \end{aligned}
-\end{equation}
-\begin{equation} \label{1.31}
-  \begin{aligned}
-     i \hbar \dv{\phi(y,t)}{t} =
-    \bigg[
-    \frac{\hat{p}_y^2}{2m_e} +
-    \frac{1}{2}m_e \omega_0^2y^2
-    \bigg]
-    \phi(y,t).
-  \end{aligned}
-\end{equation}
-Therefore we can identify the $S(t) \equiv eE\sin(\omega t)$ part as a external force act on the harmonic oscillator and we can solve this as a forced harmonic oscillator in $y$ axis.
-\begin{equation} \label{1.32}
-  \begin{aligned}
-    i \hbar \dv{\phi(y,t)}{t} =
-    \bigg[
-    -
-    \frac{\hbar^2}{2m_e}
-    \pdv[2]{y} +
-    \frac{1}{2}m_e \omega_0^2y^2
-    - yS(t)]
-    \bigg]
-    \phi(y,t).
-  \end{aligned}
-\end{equation}
-This system can be extacly solvable and we can solve this equation using the methods explained by Husimi [*1] as follows.
-
-\noindent
-First we can introduce the time dependent shifted corrdinte as
-\begin{equation} \label{1.33}
-    y \rightarrow y' = y - \zeta(t) \quad \Rightarrow \quad
-    y = y' + \zeta(t)
-\end{equation}
-and this implies that
-\begin{equation} \label{1.34}
-    \dv{\phi(y',t)}{t} = \pdv{\phi(y',t)}{t} + \pdv{\phi(y',t)}{y'}\pdv{y'}{t} =
-    \pdv{\phi(y',t)}{t} - \dot{\zeta}(t)\pdv{\phi(y',t)}{y'}
-\end{equation}
-where $\dot{\zeta}(t) = \pdv{\zeta(t)}{t}$.
-Therefore, Eq. \eqref{1.32} will be modified to
-\begin{equation} \label{1.35}
-  \begin{aligned}
-    i \hbar \pdv{\phi(y',t)}{t}  =
-    \bigg[
-    i \hbar\dot{\zeta}\pdv{y'}
-    -
-    \frac{\hbar^2}{2m_e}
-    \pdv[2]{{y'}} +
-    \frac{1}{2}m_e \omega_0^2(y' + \zeta)^2
-    - (y' + \zeta) S(t)
-    \bigg]
-    \phi(y',t).
-  \end{aligned}
-\end{equation}
-Let's tranform the wave function using following unitary trasnform
-\begin{equation} \label{1.36}
-    \phi(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t)
-\end{equation}
-and subtitte this into the Eq. \eqref{1.35} and we will get the following
-\begin{equation} \label{1.37}
-  \text{R.H.S} =  \bigg[ i \hbar \pdv{t} -
-i \hbar \Big(\frac{im_e \ddot{\zeta} y'}{\hbar}\Big)\bigg]  \exp(\frac{-im_e\dot{\zeta}y'}{\hbar})\varphi(y',t)
-\end{equation}
-and
-\begin{equation} \label{1.38}
-  \begin{aligned}
-    \text{L.H.S} & =  \bigg[
-      i \hbar \dot{\zeta}  \Big(\frac{im_e \dot{\zeta}}{\hbar}\Big)  +
-      i \hbar \dot{\zeta} \pdv{y'} \\
-      &
-      -
-      \frac{\hbar^2}{2m_e}\Big[
-        \Big(\frac{im_e \dot{\zeta}}{\hbar}\Big)^2
-        + \Big(\frac{2im_e \dot{\zeta}}{\hbar}\Big) \pdv{{y'}}
-        + \pdv[2]{{y'}}
-      \Big] \\
-      &
-      +\frac{1}{2}m_e\omega_0^2 {y'}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 +
-      m_e\omega_0^2 y'\zeta \\
-      & -
-      y'S(t) - \zeta S(t)
-    \bigg]  \exp(\frac{-im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
-  \end{aligned}
-\end{equation}
-Combining these two we get derive that
-\begin{equation} \label{1.39}
-  \begin{aligned}
-    i \hbar \pdv{\varphi(y',t)}{t}   =
-    \bigg[
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        & + \frac{1}{2} m_e \omega_0^2 y'^2 +
-        \Big[
-            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
-        \Big]y' \\
-        &
-        +
-        \Big[
-            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
-        \Big]
-    \bigg]\varphi(y',t).
-  \end{aligned}
-\end{equation}
-Then we can restrict our $\zeta(t)$ function such that
-\begin{equation} \label{1.40}
-  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t)
-\end{equation}
-and that leads to
-\begin{equation} \label{1.41}
-  \begin{aligned}
-    i \hbar \pdv{\varphi(y',t)}{t}   =
-    \bigg[
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 {y'}^2
-        - L(\zeta,\dot{\zeta},t)
-    \bigg]\varphi(y',t)
-  \end{aligned}
-\end{equation}
-where
-\begin{equation} \label{1.42}
-  L(\zeta,\dot{\zeta},t) \equiv \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t)
-\end{equation}
-is the largrangian of a driven oscillator.
-
-\noindent
-Now introduce new unitary transormation for the wavefunction as follows
-\begin{equation} \label{1.43}
-    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t)
-\end{equation}
-and subtite this into the Eq. \eqref{1.41} and gets
-\begin{equation} \label{1.44}
-  \begin{aligned}
-    i \hbar \bigg[
-      & \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \pdv{t}
-      +
-      i \hbar L(\zeta,\dot{\zeta},t) \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t'))
-    \bigg]\chi(y',t) \\
-    & =
-    \bigg[
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 {y'}^2
-        - L(\zeta,\dot{\zeta},t)
-    \bigg] \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t)
-  \end{aligned}
-\end{equation}
-and finally we can derive that
-\begin{equation} \label{1.45}
-  \begin{aligned}
-    i \hbar \pdv{t} \chi(y',t)  =
-    \bigg[
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 {y'}^2
-    \bigg] \chi(y',t).
-  \end{aligned}
-\end{equation}
-This is the well known Schrodinger equation of a stationary harmonic oscillator.
-In terms of the eigenvalues
-\begin{equation} \label{1.46}
-  E_n = \hbar \omega_0 \big(n + \frac{1}{2}\big)
-\end{equation}
-of well-known harmonic eigenfucntions
-\begin{equation} \label{1.47}
-  \chi_n(y') = \frac{1}{\sqrt{2^{n}n!}}  \cdot
-  \bigg(\frac{m_e\omega_0}{\pi \hbar}\bigg)^{1/4}
-  \cdot e^{-\frac{m_e\omega_0 y'^2}{2\hbar}} \cdot
-  \mathcal{H}_n \bigg(\sqrt{\frac{m_e \omega_0}{\hbar}}y'\bigg)
-\end{equation}
-being propositional to the Hermite functions $\mathcal{H}_n$, the solutions of Eq. \eqref{1.32} can be represent as
-\begin{equation} \label{1.48}
-  \phi_n(y,t) = \chi_n(y - \zeta(t))
-  \exp(\frac{i}{\hbar}\bigg[- E_nt +
-  m_e\dot{\zeta(t)}\big(y-\zeta(t)\big)
-   + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg])
-\end{equation}
-The set $\chi(y)$ forms a complete set and thus ay general solution $\phi_(y,t)$ can be expaned in terms of the solutions in Eq. \eqref{1.48}.
-
-\noindent
-Next we consider special case where we assumed
-\begin{equation} \label{1.49}
-  S(t) = eE\sin(\omega t)
-\end{equation}
-and one can derive the Eq. \eqref{1.40} for $\zeta(t)$
-\begin{equation} \label{1.50}
-  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = eE\sin(\omega t)
-\end{equation}
-and using Green function method the solution can be write as
-\begin{equation} \label{1.51}
-  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
-\end{equation}
-form this solution we are able to derive the final solution for the forced harmonic oscillator. \hfill$\blacksquare$
+% \input{sec_01.tex}
+% \newpage
+\input{sec_02.tex}
 

### 2021-04-09 theory/sec_02.tex
Add scattering calculations

\section{Scattering theory}

Since in a real metal there would be many scatters that can be behave as obstacles for electron that have free wave functions. Therefore we need to calculate them to analyse the real behaviour of the electrons.

\noindent
Then the wave function of the electron in a real matel $\Psi(\vb{r},t)$ should satisfy the following time-dependet Schrodinger equation
\begin{equation} \label{2.1}
  i \hbar \pdv{\Psi(\vb{r},t)}{t} = [H_e(t) + U(\vb{r})] \Psi(\vb{r},t)
\end{equation}
where $U(\vb{r})$ is the total scattering potential. We have represented the all scatters using this potential. Since the solutions \eqref{1.52} are create a complete orthonormal basis we can represent this wave function using those as follows
\begin{equation} \label{2.2}
  \Psi(\vb{r},t) = \sum_j a_j(t) \ket{\psi_j(t)}
\end{equation}
where the difference inidces j corresponding to the different sets of all quantum numbers $p_x$ and $n$
\begin{equation} \label{2.3}
  j \rightarrow (m,n) \quad \text{where} \quad
  m,n =0,1,2,...
\end{equation}
with $m$ is defined for quantized momentum in $x$ direction
\begin{equation} \label{2.4}
  p_x = m \frac{2\pi \hbar}{L_x}
\end{equation}

\noindent
Now we can use the conventional pertubation theory to calculate scattering process of electron at a state $\ket{\psi_j}$ to a state $\ket{\psi_j'}$. For that assume an electron be in the $j$ state at the time $t=0$ and corresponding $a_j'(0) = \delta_{j,j'}$.

\noindent
First subtitute a general electron state $\Psi(\vb{r},t)$ at time $t$ as the incoming electron to the Schrodinger equation given in Eq. \eqref{2.1}
\begin{equation} \label{2.5}
  i \hbar \pdv{t} \sum_j a_j(t) \ket{\psi_j(t)}= [H_e(t) + U(\vb{r})] \sum_j a_j(t) \ket{\psi_j(t)}
\end{equation}
\begin{equation} \label{2.6}
  i \hbar\sum_j   \dot{a_j}(t) \ket{\psi_j(t)} + a_j(t)\pdv{t}\ket{\psi_j(t)}= [H_e(t) + U(\vb{r})] \sum_j a_j(t) \ket{\psi_j(t)}
\end{equation}
since all the ${\ket{\psi(t)}}$ staistfy the Schrodinger equation \eqref{1.18}
\begin{equation} \label{2.7}
  i \hbar\sum_j   \dot{a_j}(t) \ket{\psi_j(t)} = \sum_j U(\vb{r}) a_j(t) \ket{\psi_j(t)}.
\end{equation}
Then take inner product with state with the state $\ket{\psi_{j'}(t)}$
\begin{equation} \label{2.8}
  i \hbar\sum_j   \dot{a_j}(t) \braket{\psi_{j'}(t)}{\psi_j(t)} = \sum_j
  a_j(t) \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
But using the \textit{Born approximation} we can assume that this incoming wave have the initial state of the electron at $t=0$ and therefore this equation will modified to
\begin{equation} \label{2.9}
  i \hbar\sum_j   \dot{a_j}(t) \braket{\psi_{j'}(t)}{\psi_j(t)} =
  \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
due to orthonormality this becomes
\begin{equation} \label{2.10}
  i \hbar \dot{a_{j'}}(t) =
  \bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
and finally this leads to first order pertubation theory for Sscattering as follows
\begin{equation} \label{2.11}
   \dot{a_{j'}}(t) =
  -\frac{i}{\hbar}\bra{\psi_{j'}(t)} U(\vb{r}) \ket{\psi_j(t)}
\end{equation}
where
\begin{equation} \label{2.12}
   a_{j'}(t) =
  -\frac{i}{\hbar}
  \int_0^t dt' \int_S d\vb{r} \;
  \psi_{j'}^{*} (\vb{r},t') U(\vb{r}) {\psi_j(\vb{r},t')}
\end{equation}
where the integration should be performed over the 2DEG area $S=L_xL_y$. Then we can calculate this using the eqution we derived in \eqref{1.52} as follows
\begin{equation} \label{2.13}
  \begin{aligned}
    a_{j'}(t) & =
   -\frac{i}{\hbar}
   \int_0^t dt' \int_S d\vb{r} \;
   \bigg[
   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t)\big) \\
   & \times
     \exp(
    \frac{i}{\hbar}\bigg[- E_{n'}t + m'\frac{2\pi \hbar x}{L_x} +
   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t)+
   m_e\dot{\zeta(t)}\big[y - {y'}_0 -\zeta(t)\big]
    + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]) \\
    & \times
    U(\vb{r}) \\
    & \times
    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t)\big) \\
    & \times
      \exp(
     \frac{i}{\hbar}\bigg[ E_{n}t - m\frac{2\pi \hbar x}{L_x} -
    \frac{eE(y-y_0)}{\omega}\cos(\omega t) -
    m_e\dot{\zeta(t)}\big[y - y_0 -\zeta(t)\big]
     - \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg])
    \bigg]
  \end{aligned}
\end{equation}
then this will be simplified to
\begin{equation} \label{2.14}
  \begin{aligned}
    a_{j'}(t) & =
   -\frac{i}{\hbar}
   \int_0^t dt' \int_S d\vb{r} \;
   \bigg[
   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t)\big)
   U(\vb{r})
   \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t)\big)  \\
   & \times
     \exp(
    \frac{i}{\hbar}\bigg[- E_{n'}t + m'\frac{2\pi \hbar x}{L_x} +
   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t)+
   m_e\dot{\zeta(t)}\big[y - {y'}_0 -\zeta(t)\big]
    + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]) \\
    & \times
      \exp(
     \frac{i}{\hbar}\bigg[ E_{n}t - m\frac{2\pi \hbar x}{L_x} -
    \frac{eE(y-y_0)}{\omega}\cos(\omega t) -
    m_e\dot{\zeta(t)}\big[y - y_0 -\zeta(t)\big]
     - \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg])
    \bigg]
  \end{aligned}
\end{equation}

xx

### 2021-04-09 theory/sec_02.tex
Add scattering probability

@@
      \exp(
-    \frac{i}{\hbar}\bigg[- E_{n'}t + m'\frac{2\pi \hbar x}{L_x} +
-   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t)+
-   m_e\dot{\zeta(t)}\big[y - {y'}_0 -\zeta(t)\big]
-    + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]) \\
+    \frac{i}{\hbar}\bigg[E_{n'}t' - m'\frac{2\pi \hbar x}{L_x} -
+   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t')-
+   m_e\dot{\zeta}(t)\big[y - {y'}_0 -\zeta(t')\big]
+    - \int_0^{t'}dt'L(\zeta,\dot{\zeta},t")\bigg]) \\
     & \times
@@
     & \times
-    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t)\big) \\
+    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t')\big) \\
     & \times
       \exp(
-     \frac{i}{\hbar}\bigg[ E_{n}t - m\frac{2\pi \hbar x}{L_x} -
-    \frac{eE(y-y_0)}{\omega}\cos(\omega t) -
-    m_e\dot{\zeta(t)}\big[y - y_0 -\zeta(t)\big]
-     - \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg])
+     \frac{i}{\hbar}\bigg[ - E_{n}t' + m\frac{2\pi \hbar x}{L_x} -
+    \frac{eE(y-y_0)}{\omega}\cos(\omega t') -
+    m_e\dot{\zeta}(t')\big[y - y_0 -\zeta(t')\big]
+     - \int_0^{t'}d\tilde{t}L(\zeta,\dot{\zeta},\tilde{t})\bigg])
     \bigg]
@@
    \bigg[
-   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t)\big)
+   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t')\big)
    U(\vb{r})
-   \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t)\big)  \\
+   \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t')\big)  \\
    & \times
      \exp(
-    \frac{i}{\hbar}\bigg[- E_{n'}t + m'\frac{2\pi \hbar x}{L_x} +
-   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t)+
-   m_e\dot{\zeta(t)}\big[y - {y'}_0 -\zeta(t)\big]
-    + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]) \\
+    \frac{i}{\hbar}\bigg[ E_{n'}t' - m'\frac{2\pi \hbar x}{L_x} -
+   \frac{eE(y-{y'}_0)}{\omega}\cos(\omega t') -
+   m_e\dot{\zeta}(t')\big[y - {y'}_0 -\zeta(t')\big]
+    - \int_0^{t'}d\tilde{t}L(\zeta,\dot{\zeta},\tilde{t})\bigg]) \\
     & \times
       \exp(
-     \frac{i}{\hbar}\bigg[ E_{n}t - m\frac{2\pi \hbar x}{L_x} -
-    \frac{eE(y-y_0)}{\omega}\cos(\omega t) -
-    m_e\dot{\zeta(t)}\big[y - y_0 -\zeta(t)\big]
-     - \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg])
+     \frac{i}{\hbar}\bigg[ - E_{n}t' + m\frac{2\pi \hbar x}{L_x} +
+    \frac{eE(y-y_0)}{\omega}\cos(\omega t') +
+    m_e\dot{\zeta}(t')\big[y - y_0 -\zeta(t')\big]
+     + \int_0^{t'}d\tilde{t}L(\zeta,\dot{\zeta},\tilde{t})\bigg])
     \bigg]
@@
 \end{equation}
+\begin{equation} \label{2.15}
+  \begin{aligned}
+    a_{j'}(t) & =
+   -\frac{i}{\hbar}
+   \int_0^t dt' \int_S d\vb{r} \;
+   \bigg[
+   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t')\big)
+   U(\vb{r})
+   \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t')\big)
+   \exp(\frac{2\pi i(m-m') \hbar x}{L_x})
+   \\
+   & \times
+     \exp(
+    \frac{i}{\hbar}\bigg[ E_{n'}t' +
+   \frac{eE{y'}_0}{\omega}\cos(\omega t') +
+   m_e\dot{\zeta}(t'){y'}_0
+    \bigg])
+      \exp(
+     \frac{i}{\hbar}\bigg[ - E_{n}t' -
+    \frac{eEy_0}{\omega}\cos(\omega t') -
+    m_e\dot{\zeta}(t)y_0
+    \bigg])
+    \bigg].
+  \end{aligned}
+\end{equation}
+The time dependence of the $chi_n(y)$ can neglect since it is integrate over all the values of the $y$ and we can write this as
+\begin{equation} \label{2.16}
+  \begin{aligned}
+    a_{j'}(t) & =
+   -\frac{i}{\hbar}
+   \int_S d\vb{r} \;
+   \frac{1}{\sqrt{L_x}} \chi_{n'}^*\big(y - {y'}_0 -\zeta(t')\big)
+   U(\vb{r})
+   \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 -\zeta(t')\big)
+   \exp(\frac{2\pi i(m-m') \hbar x}{L_x})
+   \\ & \times
+   \int_0^t dt' \;
+   \bigg[
+     \exp(
+    \frac{i}{\hbar}\bigg[ (E_{n'} -E_{n}) t' +
+   \frac{eE({y'}_0 - y_0)\omega_0^2}{\omega(\omega_0^2-\omega^2)}\cos(\omega t')
+    \bigg])
+    \bigg].
+  \end{aligned}
+\end{equation}
+Using Jacobi-Anger expansion
+\begin{equation} \label{2.17}
+  e^{iz\cos(\theta)} = \sum_{l=-\infty}^{\infty} i^l J_j(z)e^{in\theta}
+\end{equation}
+above eqution can be modified as
+\begin{equation} \label{2.18}
+  \begin{aligned}
+    a_{j'}(t)  =
+   -\frac{i}{\hbar}
+   U_{j'j}
+   \int_0^t dt' \;
+   \bigg[
+   \sum_{l=-\infty}^{\infty} i^l J_l\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+     \exp(
+    \frac{i}{\hbar} (E_{n'} -E_{n} + l\hbar\omega) t')
+    \bigg]
+  \end{aligned}
+\end{equation}
+where
+\begin{equation} \label{2.19}
+  U{j'j} \equiv \mel{\Phi_{j'}(\vb{r})}{U(\vb{r})}{\Phi_j(\vb{r})}
+\end{equation}
+with bare electron eigen states (without dressing field)
+\begin{equation} \label{2.20}
+  \Phi_{j}(\vb{r}) = \frac{1}{\sqrt{L_x}}\exp(\frac{2\pi im \hbar x}{L_x}) \chi_{n}(y).
+\end{equation}
+Considering time evalution from negative values we can write the same expression as follows
+\begin{equation} \label{2.21}
+  \begin{aligned}
+    a_{j'}(t)  =
+   -\frac{i}{\hbar}
+   U_{j'j}
+   \int_{-t/2}^{t/2} dt' \;
+   \bigg[
+   \sum_{l=-\infty}^{\infty} i^l J_l\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+     \exp(
+    \frac{i}{\hbar} (E_{n'} -E_{n} + l\hbar\omega) t')
+    \bigg].
+  \end{aligned}
+\end{equation}
+To calculate scattering probability we can use this scattering amplitude's squre value
+\begin{equation} \label{2.22}
+  \begin{aligned}
+    |a_{j'}(t)|^2  =
+   \frac{|U_{j'j}|^2}{\hbar^2} &
+   \int_{-t/2}^{t/2} dt' \;
+   \bigg[
+   \sum_{l=-\infty}^{\infty} {-i}^l J_l\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+     \exp(
+    \frac{-i}{\hbar} (E_{n'} -E_{n} + l\hbar\omega) t')
+    \bigg] \\
+    & \times
+    \int_{-t/2}^{t/2} dt^{''} \;
+    \bigg[
+    \sum_{k=-\infty}^{\infty} i^k J_k\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+      \exp(
+     \frac{i}{\hbar} (E_{n'} -E_{n} + k\hbar\omega) t^{''})
+     \bigg]
+  \end{aligned}
+\end{equation}
+Considering long time $t\rightarrow \infty$ we can make the integral into a delta function as follows
+\begin{equation} \label{2.22}
+  \begin{aligned}
+    |a_{j'}(t)|^2  =
+   4\pi^2|U_{j'j}|^2 &
+   \bigg[
+   \sum_{l=-\infty}^{\infty} {-i}^l J_l\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+     \delta(-E_{n'} +E_{n} - l\hbar\omega)
+     \bigg] \\
+    & \times
+    \bigg[
+    \sum_{k=-\infty}^{\infty} i^k J_k\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+      \delta(E_{n'} - E_{n} + k\hbar\omega)
+     \bigg]
+  \end{aligned}
+\end{equation}
+and this implies $l=k$ and this leads to
+\begin{equation} \label{2.22}
+  \begin{aligned}
+    |a_{j'}(t)|^2  =
+   4\pi^2|U_{j'j}|^2
+   \bigg[
+   \sum_{l=-\infty}^{\infty} J_l^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+     \delta^2(E_{n'} - E_{n} + l\hbar\omega).
+  \end{aligned}
+\end{equation}
+Then using the famous the square $\delta$ function transormation method
+\begin{equation} \label{2.22}
+  \begin{aligned}
+     \delta^2(\epsilon ) = \delta(\epsilon )\delta^2(0)
+     \lim_{t\rightarrow\infty} \int_{-t/2}^{t/2} e^{i0\times t' /\hbar} dt' =
+     \frac{\delta(\epsilon) t}{2\pi \hbar}
+  \end{aligned}
+\end{equation}
+we can calculatre the probability of electron scattering between states $j$ and $j'$ per unit time as
+\begin{equation} \label{2.22}
+    \mathcal{W}_{j'j} \equiv \dv{|a_{j'}(t)|^2}{t} =
+    |U_{j'j}|^2 \sum_{l=-\infty}^{\infty} J_l^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+    \times
+    \frac{2\pi}{\hbar} \delta(E_{n'} - E_{n} + l\hbar\omega)
+\end{equation}
 

### 2021-04-10 theory/sec_02.tex
Add scattering potential model

@@
 Considering long time $t\rightarrow \infty$ we can make the integral into a delta function as follows
-\begin{equation} \label{2.22}
+\begin{equation} \label{2.23}
   \begin{aligned}
@@
 and this implies $l=k$ and this leads to
-\begin{equation} \label{2.22}
+\begin{equation} \label{2.24}
   \begin{aligned}
@@
 Then using the famous the square $\delta$ function transormation method
-\begin{equation} \label{2.22}
+\begin{equation} \label{2.25}
   \begin{aligned}
@@
 we can calculatre the probability of electron scattering between states $j$ and $j'$ per unit time as
-\begin{equation} \label{2.22}
+\begin{equation} \label{2.26}
     \mathcal{W}_{j'j} \equiv \dv{|a_{j'}(t)|^2}{t} =
-    |U_{j'j}|^2 \sum_{l=-\infty}^{\infty} J_l^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+    |U_{j'j}|^2
+     \sum_{l=-\infty}^{\infty} J_l^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
     \times
@@
 
+\noindent
+To avoid thee energy echange betwen a high-frequency field and electrons, the field should be purely dressing.
+We can achieve that by using the field with off-resonant and high frequency.
+Therefore, the only effect of the dressing field on 2DEG is the renormalization of the probability of elastic electron scattering within the same Landau level $(E_{n'}=E_n)$, which described by the term with $l=0$ the Eq.
+\eqref{2.26} leads to
+\begin{equation} \label{2.27}
+    \mathcal{W}_{j'j} = J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+    \mathcal{W}_{j'j}^{(0)}
+\end{equation}
+where
+\begin{equation} \label{2.28}
+    \mathcal{W}_{j'j}^{(0)} = \frac{2\pi}{\hbar} |U_{j'j}|^2
+    \delta(E_{n'} - E_{n})
+\end{equation}
+is the probability of scattering of a \textit{bare electron}.
+It is important to notice that the Bessel function factor depend on both the dressing field and stationaty magnetic field.
+This factor is responcible for all the effcts discussed in thisarticle.
+
+\noindent
+One can define the lifetime of the dressed electron at the Landau level $\tau$ is renormalized by the Bessel function as below
+\begin{equation} \label{2.29}
+    \frac{1}{\tau} \equiv \sum_{j'} \mathcal{W}_{j'j} =
+    \sum_{j'}
+    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+    \mathcal{W}_{j'j}^{(0)}
+\end{equation}
+where we have consider all posibilities that electron can jump to the state $j'$. Then rewrite the delat function as follows
+\begin{equation} \label{2.30}
+    \delta(\epsilon) =
+    \frac{1}{\pi} \lim_{\Gamma \rightarrow 0 } \frac{\Gamma}{\Gamma^2 + \epsilon^2}
+\end{equation}
+where in this study we can assume that the paramater $\Gamma \equiv \hbar/\tau$ as scattering induced broading of the Landau level.
+But for the elestic scatteing within the same Landau level, we can write the $\delta$ function as
+\begin{equation} \label{2.31}
+    \delta(E_{n'} - E_{n}) \approx
+    \frac{1}{\pi \Gamma}.
+\end{equation}
+Therefore Eq. \eqref{2.29} will change to
+\begin{equation} \label{2.32}
+    \frac{1}{\tau} =
+    \sum_{j'}
+    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+    \times
+    \frac{2\pi}{\hbar} |U_{j'j}|^2 \times \frac{1}{\pi \Gamma}
+\end{equation}
+\begin{equation} \label{2.33}
+    \frac{1}{\tau} =
+    \sum_{j'}
+    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+    \times
+    \frac{2}{\hbar} |U_{j'j}|^2 \times \frac{\tau}{\hbar}
+\end{equation}
+and finally this can be modified to
+\begin{equation} \label{2.34}
+    \frac{1}{\tau} =
+    \bigg[
+    \frac{2}{\hbar^2}
+    \sum_{j'}
+    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+    |U_{j'j}|^2
+    \bigg]^{1/2}
+\end{equation}
+where the summation is performed over electron states $j'$ within the same Landau level.
+
+\noindent
+Now lets specify more on the scattering potential where we can model them as randomly distributed delta fucntions as follows
+\begin{equation} \label{2.35}
+    U(\vb{r}) \equiv \sum_{i=1}^{N_s} U_0 \delta(\vb{r} - \vb{r}_i)
+\end{equation}
+where $N_s$ is the total number of scatters in the considering matel.
+
 xx

### 2021-04-10 theory/sec_02.tex
Add lifetime in a landau level

@@
 \end{equation}
-where $N_s$ is the total number of scatters in the considering matel.
-
-xx
+where $N_s$ is the total number of scatters in the considering matel. Now we can calculate $|U_{j'j}|^2$ as follows
+\begin{equation} \label{2.36}
+  \begin{aligned}
+    |U_{j'j}|^2 = &
+    \sum_{i =1}^{N_s}
+    \frac{1}{L_x^2}
+    \int \int  dx_1 dy_1
+      \exp(\frac{-{p'}_x x_1}{\hbar})
+      \chi_n^* (y_1 - {y'}_0)
+      U_0 \delta(x_1-x_i)\delta(y_1-y_i)
+      \exp(\frac{{p}_x x_1}{\hbar})
+      \chi_n (y_1 - {y}_0) \\
+    & \times
+    \int \int  dx_2 dy_2
+      \exp(\frac{{p'}_x x_2}{\hbar})
+      \chi_n (y_2 - {y'}_0)
+      U_0 \delta(x_2 - x_i)\delta(y_2 - y_i)
+      \exp(\frac{-{p}_x x_2}{\hbar})
+      \chi_n^* (y_2 - {y}_0)
+  \end{aligned}
+\end{equation}
+and considering only non-zero values for $x_1$ and $x_2$ integrals we can re-write this as
+\begin{equation} \label{2.37}
+  \begin{aligned}
+    |U_{j'j}|^2 = &
+    \sum_{i =1}^{N_s}
+    \frac{U_0^2}{L_x^2}
+    \int dy_1
+      \exp(\frac{-{p'}_x x_i}{\hbar})
+      \chi_n^* (y_1 - {y'}_0)
+      \delta(y_1-y_i)
+      \exp(\frac{{p}_x x_i}{\hbar})
+      \chi_n (y_1 - {y}_0) \\
+    & \times
+    \int dy_2
+      \exp(\frac{{p'}_x x_i}{\hbar})
+      \chi_n (y_2 - {y'}_0)
+      \delta(y_2 - y_i)
+      \exp(\frac{-{p}_x x_i}{\hbar})
+      \chi_n^* (y_2 - {y}_0)
+  \end{aligned}
+\end{equation}
+and this will be simplified to
+\begin{equation} \label{2.38}
+  \begin{aligned}
+    |U_{j'j}|^2 = &
+    \sum_{i =1}^{N_s}
+    \frac{U_0^2}{L_x^2}
+    \int dy_1
+      \chi_n^* (y_1 - {y'}_0)
+      \delta(y_1-y_i)
+      \chi_n (y_1 - {y}_0) \\
+    & \times
+    \int dy_2
+      \chi_n (y_2 - {y'}_0)
+      \delta(y_2 - y_i)
+      \chi_n^* (y_2 - {y}_0).
+  \end{aligned}
+\end{equation}
+Again considering only non-zero values for $y_1$ and $y_2$ integrals we can re-write this as
+\begin{equation} \label{2.39}
+  \begin{aligned}
+    |U_{j'j}|^2 = &
+    \sum_{i =1}^{N_s}
+    \frac{U_0^2}{L_x^2}
+      \chi_n^* (y_i - {y'}_0)
+      \chi_n (y_i - {y}_0)
+      \chi_n (y_i - {y'}_0)
+      \chi_n^* (y_i - {y}_0).
+  \end{aligned}
+\end{equation}
+\begin{equation} \label{2.40}
+  \begin{aligned}
+    |U_{j'j}|^2 =
+    \frac{U_0^2}{L_x^2}
+    \sum_{i =1}^{N_s}
+      \chi_n^2 (y_i - {y'}_0)
+      \chi_n^2 (y_i - {y}_0).
+  \end{aligned}
+\end{equation}
+Now subtituting this derivation into the Eq. \eqref{2.34} we will get
+\begin{equation} \label{2.41}
+    \frac{1}{\tau} =
+    \bigg[
+    \frac{2U_0^2}{\hbar^2 L_x^2}
+    \sum_{{y'}_0}
+    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+    \sum_{i =1}^{N_s}
+      \chi_n^2 (y_i - {y'}_0)
+      \chi_n^2 (y_i - {y}_0)
+    \bigg]^{1/2}
+\end{equation}
+where $j'$ reduced to ${p'}_x$ (since $n'=n$)and we can represent it by ${y'}_0$. Then this will modified to
+\begin{equation} \label{2.42}
+    \frac{1}{\tau} =
+    \bigg[
+    \frac{2U_0^2}{\hbar^2 L_x^2}
+    \sum_{{y'}_0}
+    \sum_{i =1}^{N_s}
+    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+      \chi_n^2 (y_i - {y'}_0)
+      \chi_n^2 (y_i - {y}_0)
+    \bigg]^{1/2}.
+\end{equation}
+Now considering large size of sample and a macroscopically large $N_s$ scatters we can promate the summation to integrations as follows
+\begin{equation} \label{2.43}
+    \frac{1}{\tau} =
+    \bigg[
+    \frac{2U_0^2}{\hbar^2 L_x^2}
+    \frac{eB L_x}{2\pi\hbar}\int d{y'}_0
+    \frac{N_s} {L_x}\int dy_i
+    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+      \chi_n^2 (y_i - {y'}_0)
+      \chi_n^2 (y_i - {y}_0)
+    \bigg]^{1/2}.
+\end{equation}
+Assuming $L_x = L_y$ we can define the area of the 2D material as
+\begin{equation} \label{2.44}
+    S \equiv L_xL_x = L_xL_y
+\end{equation}
+and then we can re-write the above as
+\begin{equation} \label{2.45}
+    \frac{1}{\tau} =
+    \bigg[
+    \frac{eBN_sU_0^2}{\pi\hbar^3 S}
+    \int d{y'}_0
+    \int dy_i
+    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+      \chi_n^2 (y_i - {y'}_0)
+      \chi_n^2 (y_i - {y}_0)
+    \bigg]^{1/2}.
+\end{equation}
+Define the \textit{density of scatters} per unit area of 2DEG
+\begin{equation} \label{2.46}
+    n_s \equiv \frac{N_s}{S}
+\end{equation}
+and the \textit{magnetic length} as
+\begin{equation} \label{2.47}
+    l_0 \equiv \sqrt{\frac{\hbar}{eB}}.
+\end{equation}
+Now our Eq. \eqref{2.45} leads to
+\begin{equation} \label{2.48}
+    \frac{1}{\tau} =
+    \sqrt{
+    \frac{n_sU_0^2}{\pi l_0^2 \hbar^2}}
+    \bigg[
+    \int d{y'}_0
+    \int dy_i
+    J_0^2\bigg[\frac{eE({y'}_0 - y_0)\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+      \chi_n^2 (y_i - {y'}_0)
+      \chi_n^2 (y_i - {y}_0)
+    \bigg]^{1/2}
+\end{equation}
+and now define new dummy variables as follows (since $y_0$ is a paramter)
+\begin{equation} \label{2.49}
+    ({y'}_0 - y_0) \rightarrow  y  \quad \text{and} \quad
+    ({y}_i- {y'}_0) \rightarrow y'
+\end{equation}
+and finally we will get the eqution for the dressed electron lifetime at the $n$th Landau level as
+\begin{equation} \label{2.50}
+    \frac{1}{\tau} =
+    \sqrt{
+    \frac{n_sU_0^2}{\pi l_0^2 \hbar^2}}
+    \bigg[
+    \int \int  dy dy'\;
+    J_0^2\bigg[\frac{eEy\omega_0^2}{\hbar\omega(\omega_0^2-\omega^2)}\bigg]
+      \chi_n^2 (y')
+      \chi_n^2 (y+y')
+    \bigg]^{1/2}
+\end{equation}
+\hfill$\blacksquare$

### 2021-04-23 theory/figures/fig2.tex
Add figure 2 scattering

\documentclass{standalone}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz,pgf} %and any other packages or tikzlibraries your picture needs
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}
\usetikzlibrary{shapes,arrows,patterns}

\begin{document}

% Pattern Info

\tikzset{
pattern size/.store in=\mcSize,
pattern size = 5pt,
pattern thickness/.store in=\mcThickness,
pattern thickness = 0.3pt,
pattern radius/.store in=\mcRadius,
pattern radius = 1pt}
\makeatletter
\pgfutil@ifundefined{pgf@pattern@name@_ahw2g2prc}{
\pgfdeclarepatternformonly[\mcThickness,\mcSize]{_ahw2g2prc}
{\pgfqpoint{0pt}{-\mcThickness}}
{\pgfpoint{\mcSize}{\mcSize}}
{\pgfpoint{\mcSize}{\mcSize}}
{
\pgfsetcolor{\tikz@pattern@color}
\pgfsetlinewidth{\mcThickness}
\pgfpathmoveto{\pgfqpoint{0pt}{\mcSize}}
\pgfpathlineto{\pgfpoint{\mcSize+\mcThickness}{-\mcThickness}}
\pgfusepath{stroke}
}}
\makeatother

% Pattern Info

\tikzset{
pattern size/.store in=\mcSize,
pattern size = 5pt,
pattern thickness/.store in=\mcThickness,
pattern thickness = 0.3pt,
pattern radius/.store in=\mcRadius,
pattern radius = 1pt}
\makeatletter
\pgfutil@ifundefined{pgf@pattern@name@_hzem6n8bo}{
\pgfdeclarepatternformonly[\mcThickness,\mcSize]{_hzem6n8bo}
{\pgfqpoint{0pt}{0pt}}
{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
{\pgfpoint{\mcSize}{\mcSize}}
{
\pgfsetcolor{\tikz@pattern@color}
\pgfsetlinewidth{\mcThickness}
\pgfpathmoveto{\pgfqpoint{0pt}{0pt}}
\pgfpathlineto{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
\pgfusepath{stroke}
}}
\makeatother

% Pattern Info

\tikzset{
pattern size/.store in=\mcSize,
pattern size = 5pt,
pattern thickness/.store in=\mcThickness,
pattern thickness = 0.3pt,
pattern radius/.store in=\mcRadius,
pattern radius = 1pt}
\makeatletter
\pgfutil@ifundefined{pgf@pattern@name@_bmptxkju1}{
\pgfdeclarepatternformonly[\mcThickness,\mcSize]{_bmptxkju1}
{\pgfqpoint{0pt}{0pt}}
{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
{\pgfpoint{\mcSize}{\mcSize}}
{
\pgfsetcolor{\tikz@pattern@color}
\pgfsetlinewidth{\mcThickness}
\pgfpathmoveto{\pgfqpoint{0pt}{0pt}}
\pgfpathlineto{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
\pgfusepath{stroke}
}}
\makeatother
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Rectangle [id:dp11071761337500274]
\draw  [color={rgb, 255:red, 255; green, 255; blue, 255 }  ,draw opacity=1 ][pattern=_ahw2g2prc,pattern size=5.550000000000001pt,pattern thickness=0.75pt,pattern radius=0pt, pattern color={rgb, 255:red, 198; green, 198; blue, 198}] (190.29,116.71) -- (409.57,116.71) -- (409.57,143.29) -- (190.29,143.29) -- cycle ;
%Straight Lines [id:da38313797800163174]
\draw [line width=1.5]    (300.14,196.43) -- (299.87,74.43) ;
\draw [shift={(299.86,70.43)}, rotate = 449.87] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (11.61,-5.58) -- (0,0) -- (11.61,5.58) -- cycle    ;
%Straight Lines [id:da2885312957054813]
\draw [line width=1.5]    (190.14,190.14) -- (410.43,190.43) ;
%Straight Lines [id:da014828325076878812]
\draw    (189.86,160.14) -- (409.57,159.86) ;
%Straight Lines [id:da030770486462505353]
\draw [color={rgb, 255:red, 74; green, 74; blue, 74 }  ,draw opacity=1 ]   (189.86,130.14) -- (409.86,130.14) ;
%Straight Lines [id:da1258041236737828]
\draw    (189.86,100.14) -- (409.86,100.14) ;
%Straight Lines [id:da549610540001811]
\draw [line width=0.75]  [dash pattern={on 4.5pt off 4.5pt}]  (190.29,115) -- (409.86,115.57) ;
%Straight Lines [id:da8170920135053421]
\draw  [dash pattern={on 4.5pt off 4.5pt}]  (190,144.71) -- (409.57,145.29) ;
%Straight Lines [id:da09440943310141292]
\draw [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,draw opacity=1 ]   (190.29,123.14) -- (410.14,123.57) ;
%Shape: Circle [id:dp2109394726683369]
\draw  [pattern=_hzem6n8bo,pattern size=1.9500000000000002pt,pattern thickness=0.75pt,pattern radius=0pt, pattern color={rgb, 255:red, 155; green, 155; blue, 155}] (326.29,130.21) .. controls (326.29,128.12) and (327.98,126.43) .. (330.07,126.43) .. controls (332.16,126.43) and (333.86,128.12) .. (333.86,130.21) .. controls (333.86,132.31) and (332.16,134) .. (330.07,134) .. controls (327.98,134) and (326.29,132.31) .. (326.29,130.21) -- cycle ;
%Shape: Circle [id:dp6488061807957903]
\draw  [pattern=_bmptxkju1,pattern size=1.9500000000000002pt,pattern thickness=0.75pt,pattern radius=0pt, pattern color={rgb, 255:red, 155; green, 155; blue, 155}] (356.29,123.36) .. controls (356.29,121.27) and (357.98,119.57) .. (360.07,119.57) .. controls (362.16,119.57) and (363.86,121.27) .. (363.86,123.36) .. controls (363.86,125.45) and (362.16,127.14) .. (360.07,127.14) .. controls (357.98,127.14) and (356.29,125.45) .. (356.29,123.36) -- cycle ;
%Curve Lines [id:da24190138502732017]
\draw [color={rgb, 255:red, 15; green, 77; blue, 150 }  ,draw opacity=1 ]   (329.86,125) .. controls (332.29,109.61) and (348.75,101.87) .. (356.82,115.78) ;
\draw [shift={(358.14,118.43)}, rotate = 246.91] [fill={rgb, 255:red, 15; green, 77; blue, 150 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (5.36,-2.57) -- (0,0) -- (5.36,2.57) -- (3.56,0) -- cycle    ;
%Straight Lines [id:da18098817640260245]
\draw    (330.14,185) -- (330.29,195.86) ;
%Straight Lines [id:da950065161038371]
\draw    (359.92,185.11) -- (360.06,195.97) ;
%Straight Lines [id:da6657355377016125]
\draw    (340.14,185) -- (340.29,195.86) ;
%Straight Lines [id:da588941077354121]
\draw    (350.14,185.57) -- (350.29,196.43) ;
%Straight Lines [id:da9026150195477192]
\draw    (370.14,184.56) -- (370.29,195.41) ;
%Straight Lines [id:da7248973636669813]
\draw    (399.92,184.67) -- (400.06,195.52) ;
%Straight Lines [id:da05943771455735014]
\draw    (380.14,184.56) -- (380.29,195.41) ;
%Straight Lines [id:da7726684154046342]
\draw    (390.14,185.13) -- (390.29,195.98) ;
%Straight Lines [id:da9150601062632764]
\draw    (250.14,185.22) -- (250.29,196.08) ;
%Straight Lines [id:da8099410498362345]
\draw    (279.92,185.33) -- (280.06,196.19) ;
%Straight Lines [id:da6236544524998151]
\draw    (260.14,185.22) -- (260.29,196.08) ;
%Straight Lines [id:da5921146606185723]
\draw    (270.14,185.79) -- (270.29,196.65) ;
%Straight Lines [id:da5991996011400991]
\draw    (290.14,184.78) -- (290.29,195.63) ;
%Straight Lines [id:da6482455334673505]
\draw    (319.92,184.89) -- (320.06,195.75) ;
%Straight Lines [id:da871163669545836]
\draw    (310.14,185.35) -- (310.29,196.21) ;
%Straight Lines [id:da6483925428035442]
\draw    (199.48,184.67) -- (199.62,195.52) ;
%Straight Lines [id:da685643393265353]
\draw    (209.7,184.11) -- (209.84,194.97) ;
%Straight Lines [id:da7838129922931183]
\draw    (239.48,184.22) -- (239.62,195.08) ;
%Straight Lines [id:da7719533009206734]
\draw    (219.7,184.11) -- (219.84,194.97) ;
%Straight Lines [id:da2831023061884146]
\draw    (229.7,184.68) -- (229.84,195.54) ;

% Text Node
\draw (299.71,51.54) node [anchor=north west][inner sep=0.75pt]    {$Energy$};
% Text Node
\draw (415.71,180.69) node [anchor=north west][inner sep=0.75pt]    {$k_{x}$};
% Text Node
\draw (411.86,125.97) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,opacity=1 ]  {$\varepsilon_{\beta} =\varepsilon_{n_{\beta}}$};
% Text Node
\draw (176.29,117.11) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 208; green, 2; blue, 27 }  ,opacity=1 ]  {$\varepsilon$};
% Text Node
\draw (308,132.105) node [anchor=north west][inner sep=0.75pt]  [font=\tiny]  {$\ket{\psi_{\beta}}$};
% Text Node
\draw (360.29,104.4) node [anchor=north west][inner sep=0.75pt]  [font=\tiny]  {$\ket{\Psi_{\alpha}}$};

\end{tikzpicture}

\end{document}

### 2021-05-02 theory/figures/fig0.tex
Correction in section 1

\documentclass{standalone}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz,pgf} %and any other packages or tikzlibraries your picture needs
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}
\usetikzlibrary{shapes,arrows,patterns}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Straight Lines [id:da3003250640268105]
\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ][line width=2.25]    (181.4,159.55) -- (362.9,159.06) ;
\draw [shift={(367.9,159.05)}, rotate = 539.85] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (14.29,-6.86) -- (0,0) -- (14.29,6.86) -- cycle    ;
%Straight Lines [id:da8689546067621734]
\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ][line width=2.25]    (305.1,110.05) -- (208.44,217.83) ;
\draw [shift={(205.1,221.55)}, rotate = 311.89] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (14.29,-6.86) -- (0,0) -- (14.29,6.86) -- cycle    ;
%Straight Lines [id:da7970692632058651]
\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ][line width=2.25]    (261,210.5) -- (260.04,103.83) ;
\draw [shift={(260,98.83)}, rotate = 449.49] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (14.29,-6.86) -- (0,0) -- (14.29,6.86) -- cycle    ;
%Straight Lines [id:da3519471636626119]
\draw    (170.6,189.8) -- (299.8,189.8) ;
%Straight Lines [id:da7963832060808382]
\draw    (299.8,189.8) -- (349.8,130.2) ;
%Straight Lines [id:da6491507288076224]
\draw    (220.6,130.2) -- (349.8,130.2) ;
%Straight Lines [id:da39220315951527485]
\draw    (170.6,189.8) -- (220.6,130.2) ;
%Straight Lines [id:da03581404411817579]
\draw    (170.6,192.2) -- (299.8,192.2) ;
%Straight Lines [id:da6682783230769427]
\draw    (299.8,192.2) -- (349.8,132.6) ;
%Straight Lines [id:da3091548050753099]
\draw    (170.6,189.8) -- (170.6,192.2) ;
%Straight Lines [id:da8752360367747976]
\draw    (349.8,130.2) -- (349.8,132.6) ;

% Text Node
\draw (187.9,200.93) node [anchor=north west][inner sep=0.75pt]  [font=\Large]  {$x$};
% Text Node
\draw (374.9,152.6) node [anchor=north west][inner sep=0.75pt]  [font=\Large]  {$y$};
% Text Node
\draw (245.57,92.6) node [anchor=north west][inner sep=0.75pt]  [font=\Large]  {$z$};
% Text Node
\draw (230.24,195.27) node [anchor=north west][inner sep=0.75pt]  [font=\small,color={rgb, 255:red, 26; green, 68; blue, 118 }  ,opacity=1 ]  {$\frac{L_{x}}{2}$};
% Text Node
\draw (266.24,110.93) node [anchor=north west][inner sep=0.75pt]  [font=\small,color={rgb, 255:red, 26; green, 68; blue, 118 }  ,opacity=1 ]  {$\frac{-L_{x}}{2}$};
% Text Node
\draw (178.24,135.6) node [anchor=north west][inner sep=0.75pt]  [font=\small,color={rgb, 255:red, 154; green, 34; blue, 49 }  ,opacity=1 ]  {$\frac{-L_{y}}{2}$};
% Text Node
\draw (324.24,161.6) node [anchor=north west][inner sep=0.75pt]  [font=\small,color={rgb, 255:red, 154; green, 34; blue, 49 }  ,opacity=1 ]  {$\frac{L_{y}}{2}$};
% Text Node
\draw (262.17,159.73) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {$0$};

\end{tikzpicture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2021-05-02 theory/figures/fig02.tex
Correction in section 1

\documentclass{standalone}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz,pgf} %and any other packages or tikzlibraries your picture needs
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}
\usetikzlibrary{shapes,arrows,patterns}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Rectangle [id:dp8537790588861109]
\draw  [fill={rgb, 255:red, 214; green, 230; blue, 249 }  ,fill opacity=1 ] (49.92,61.08) -- (190.42,61.08) -- (190.42,171.08) -- (49.92,171.08) -- cycle ;
%Straight Lines [id:da2934066429939679]
\draw    (30,135.75) -- (30,169.25) ;
\draw [shift={(30,172.25)}, rotate = 270] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (7.14,-3.43) -- (0,0) -- (7.14,3.43) -- cycle    ;
%Straight Lines [id:da8241212049271052]
\draw    (30.5,100.25) -- (30.5,63.75) ;
\draw [shift={(30.5,60.75)}, rotate = 450] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (7.14,-3.43) -- (0,0) -- (7.14,3.43) -- cycle    ;
%Straight Lines [id:da8954416056914352]
\draw    (137,190.25) -- (187,190.25) ;
\draw [shift={(190,190.25)}, rotate = 180] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (7.14,-3.43) -- (0,0) -- (7.14,3.43) -- cycle    ;
%Straight Lines [id:da9428515181591588]
\draw    (99.5,190.75) -- (54.5,190.75) ;
\draw [shift={(51.5,190.75)}, rotate = 360] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (7.14,-3.43) -- (0,0) -- (7.14,3.43) -- cycle    ;
%Shape: Circle [id:dp878186290771406]
\draw   (137.83,82.17) .. controls (137.83,76.37) and (142.53,71.67) .. (148.33,71.67) .. controls (154.13,71.67) and (158.83,76.37) .. (158.83,82.17) .. controls (158.83,87.97) and (154.13,92.67) .. (148.33,92.67) .. controls (142.53,92.67) and (137.83,87.97) .. (137.83,82.17) -- cycle ;
\draw   (144.53,68.87) -- (149.93,71.57) -- (144.53,74.27) ;
\draw   (151.33,95.07) -- (145.93,92.37) -- (151.33,89.67) ;

%Shape: Circle [id:dp37751711035932245]
\draw   (62.42,89.08) .. controls (62.42,83.28) and (67.12,78.58) .. (72.92,78.58) .. controls (78.72,78.58) and (83.42,83.28) .. (83.42,89.08) .. controls (83.42,94.88) and (78.72,99.58) .. (72.92,99.58) .. controls (67.12,99.58) and (62.42,94.88) .. (62.42,89.08) -- cycle ;
\draw   (68.67,75.73) -- (74.07,78.43) -- (68.67,81.13) ;
\draw   (75.27,102.13) -- (69.87,99.43) -- (75.27,96.73) ;

%Shape: Circle [id:dp9441129857051875]
\draw   (141.5,144.5) .. controls (141.5,138.7) and (146.2,134) .. (152,134) .. controls (157.8,134) and (162.5,138.7) .. (162.5,144.5) .. controls (162.5,150.3) and (157.8,155) .. (152,155) .. controls (146.2,155) and (141.5,150.3) .. (141.5,144.5) -- cycle ;
\draw   (147.8,131.4) -- (153.2,134.1) -- (147.8,136.8) ;
\draw   (154.4,157.4) -- (149,154.7) -- (154.4,152) ;

%Shape: Ellipse [id:dp23625262988639273]
\draw   (221.46,112.8) .. controls (221.46,95.98) and (235.1,82.34) .. (251.92,82.34) .. controls (268.74,82.34) and (282.38,95.98) .. (282.38,112.8) .. controls (282.38,129.62) and (268.74,143.26) .. (251.92,143.26) .. controls (235.1,143.26) and (221.46,129.62) .. (221.46,112.8) -- cycle ;
\draw   (287.26,106.08) -- (282.09,116.41) -- (276.93,106.08) ;
%Shape: Circle [id:dp7990969910924739]
\draw  [fill={rgb, 255:red, 74; green, 74; blue, 74 }  ,fill opacity=1 ] (249.59,112.8) .. controls (249.59,111.51) and (250.63,110.47) .. (251.92,110.47) .. controls (253.21,110.47) and (254.26,111.51) .. (254.26,112.8) .. controls (254.26,114.09) and (253.21,115.14) .. (251.92,115.14) .. controls (250.63,115.14) and (249.59,114.09) .. (249.59,112.8) -- cycle ;
\draw   (216.26,120.07) -- (221.43,109.75) -- (226.59,120.07) ;
%Straight Lines [id:da01276353140729447]
\draw [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] [dash pattern={on 0.84pt off 2.51pt}]  (148.33,71.67) -- (250.43,81.86) ;
%Straight Lines [id:da5308408420530641]
\draw [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] [dash pattern={on 0.84pt off 2.51pt}]  (148.33,92.67) -- (248.43,144.14) ;
%Shape: Circle [id:dp1732750756124548]
\draw   (85.83,134.5) .. controls (85.83,128.7) and (90.53,124) .. (96.33,124) .. controls (102.13,124) and (106.83,128.7) .. (106.83,134.5) .. controls (106.83,140.3) and (102.13,145) .. (96.33,145) .. controls (90.53,145) and (85.83,140.3) .. (85.83,134.5) -- cycle ;
\draw   (92.13,121.4) -- (97.53,124.1) -- (92.13,126.8) ;
\draw   (98.73,147.4) -- (93.33,144.7) -- (98.73,142) ;

%Straight Lines [id:da29014475525837846]
\draw [color={rgb, 255:red, 23; green, 74; blue, 133 }  ,draw opacity=1 ] [dash pattern={on 4.5pt off 4.5pt}]  (120.33,61) -- (120,171.17) ;
%Straight Lines [id:da393091957111789]
\draw [color={rgb, 255:red, 23; green, 74; blue, 133 }  ,draw opacity=1 ] [dash pattern={on 4.5pt off 4.5pt}]  (50.17,115.67) -- (190.33,114.83) ;
%Shape: Circle [id:dp6141644536349495]
\draw  [fill={rgb, 255:red, 74; green, 74; blue, 74 }  ,fill opacity=1 ] (147.17,82.17) .. controls (147.17,81.52) and (147.69,81) .. (148.33,81) .. controls (148.98,81) and (149.5,81.52) .. (149.5,82.17) .. controls (149.5,82.81) and (148.98,83.33) .. (148.33,83.33) .. controls (147.69,83.33) and (147.17,82.81) .. (147.17,82.17) -- cycle ;
%Straight Lines [id:da09330324548659452]
\draw [color={rgb, 255:red, 128; green, 10; blue, 25 }  ,draw opacity=1 ]   (148.63,114.94) -- (148.36,86.33) ;
\draw [shift={(148.33,83.33)}, rotate = 449.47] [fill={rgb, 255:red, 128; green, 10; blue, 25 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (5.36,-2.57) -- (0,0) -- (5.36,2.57) -- cycle    ;

% Text Node
\draw (105.5,180.4) node [anchor=north west][inner sep=0.75pt]  [font=\LARGE]  {$L_{x}$};
% Text Node
\draw (15,105.4) node [anchor=north west][inner sep=0.75pt]  [font=\LARGE]  {$L_{y}$};
% Text Node
\draw (243.59,95.54) node [anchor=north west][inner sep=0.75pt]  [font=\large]  {$y_{0}$};
% Text Node
\draw (130.59,95.54) node [anchor=north west][inner sep=0.75pt]  [font=\large,color={rgb, 255:red, 128; green, 10; blue, 25 }  ,opacity=1 ]  {$y_{0}$};
% Text Node
\draw (122.3,118.25) node [anchor=north west][inner sep=0.75pt]  [font=\large]  {$0$};
% Text Node
\draw (288.59,100.54) node [anchor=north west][inner sep=0.75pt]  [font=\large]  {$\omega _{0}$};

\end{tikzpicture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2021-05-02 theory/figures/fig03.tex
Correction in section 3

\documentclass{standalone}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz,pgf} %and any other packages or tikzlibraries your picture needs
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}
\usetikzlibrary{shapes,arrows,patterns}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,338); %set diagram left start at 0, and has height of 338

%Straight Lines [id:da05241196214452626]
\draw    (238.65,205.45) -- (238.4,26.8) ;
\draw [shift={(238.4,23.8)}, rotate = 449.92] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (7.14,-3.43) -- (0,0) -- (7.14,3.43) -- cycle    ;
%Straight Lines [id:da6020218277675191]
\draw    (135.2,204.6) -- (329.35,204.35) ;
\draw [shift={(332.35,204.35)}, rotate = 539.9300000000001] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (7.14,-3.43) -- (0,0) -- (7.14,3.43) -- cycle    ;
%Straight Lines [id:da9431959114242063]
\draw [color={rgb, 255:red, 156; green, 21; blue, 37 }  ,draw opacity=1 ][line width=2.25]    (150.8,171.4) -- (320.35,171.05) ;
%Straight Lines [id:da37284196508889367]
\draw [color={rgb, 255:red, 156; green, 21; blue, 37 }  ,draw opacity=1 ][line width=2.25]    (152.8,121) -- (318.35,119.85) ;
%Straight Lines [id:da4935257751480193]
\draw [color={rgb, 255:red, 156; green, 21; blue, 37 }  ,draw opacity=1 ][line width=2.25]    (153.2,68.2) -- (317.25,67.95) ;
%Shape: Circle [id:dp8412837697747655]
\draw  [fill={rgb, 255:red, 74; green, 74; blue, 74 }  ,fill opacity=1 ] (200,52.29) .. controls (200,51.12) and (200.95,50.17) .. (202.13,50.17) .. controls (203.3,50.17) and (204.25,51.12) .. (204.25,52.29) .. controls (204.25,53.47) and (203.3,54.42) .. (202.13,54.42) .. controls (200.95,54.42) and (200,53.47) .. (200,52.29) -- cycle ;
%Shape: Circle [id:dp4130226792773326]
\draw  [fill={rgb, 255:red, 74; green, 74; blue, 74 }  ,fill opacity=1 ] (200,43.54) .. controls (200,42.37) and (200.95,41.42) .. (202.13,41.42) .. controls (203.3,41.42) and (204.25,42.37) .. (204.25,43.54) .. controls (204.25,44.72) and (203.3,45.67) .. (202.13,45.67) .. controls (200.95,45.67) and (200,44.72) .. (200,43.54) -- cycle ;
%Shape: Circle [id:dp6072986416723454]
\draw  [fill={rgb, 255:red, 74; green, 74; blue, 74 }  ,fill opacity=1 ] (200,34.54) .. controls (200,33.37) and (200.95,32.42) .. (202.13,32.42) .. controls (203.3,32.42) and (204.25,33.37) .. (204.25,34.54) .. controls (204.25,35.72) and (203.3,36.67) .. (202.13,36.67) .. controls (200.95,36.67) and (200,35.72) .. (200,34.54) -- cycle ;

% Text Node
\draw (235.5,214.4) node [anchor=north west][inner sep=0.75pt]    {$0$};
% Text Node
\draw (314.6,207.3) node [anchor=north west][inner sep=0.75pt]    {$|\mathbf{k} |\ =\sqrt{k_{x} \ +\ k_{y}}$};
% Text Node
\draw (242,6.13) node [anchor=north west][inner sep=0.75pt]    {$Energy$};
% Text Node
\draw (330,159.4) node [anchor=north west][inner sep=0.75pt]    {$\varepsilon _{0} =\frac{\hbar \omega _{0}}{2} -\Delta _{E}$};
% Text Node
\draw (330,108.2) node [anchor=north west][inner sep=0.75pt]    {$\varepsilon _{1} =\frac{3\hbar \omega _{0}}{2} -\Delta _{E}$};
% Text Node
\draw (329.2,55.8) node [anchor=north west][inner sep=0.75pt]    {$\varepsilon _{2} =\frac{5\hbar \omega _{0}}{2} -\Delta _{E}$};

\end{tikzpicture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2021-05-11 theory/sec_06.tex
Add Floquet conductivity equation

\section{Floquet Conductivity in Landau Levels}

Now we can derive conductivity expression for a given Landau level using Floquet conductivity expression derived in [*Ref:my report 2.488]. Before that let's consider the inverse scattering time matrix element in the previous section. From Eq. \eqref{5.3} we can express the $N$th Landau level's inverse scattering time central element ($n=n'=0$) as
\begin{equation} \label{6.1}
  \begin{aligned}
    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N} =
    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^4 \qty(eB)^2}
    \delta(\varepsilon - \varepsilon_{N}) &
    \int_{-\infty}^{\infty} d {k'}_x \;
    J_0^2\qty(\frac{g\hbar}{eB}[{k}_x - {k'}_x])
    \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d\bar{k} \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}\bar{k})
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - \bar{k}])|^2.
  \end{aligned}
\end{equation}
Now we can introduce a new parameter with physical meaning of scatterin-induced broading of the Landau level as follows
\begin{equation} \label{6.2}
  \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N}
\end{equation}
and this modify our previous expressing as
\begin{equation} \label{6.3}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,k_x)  =
    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^4 \qty(eB)^2}
    \delta(\varepsilon - \varepsilon_{N}) &
    \int_{-\infty}^{\infty} d {k'}_x \;
    J_0^2\qty(\frac{g\hbar}{eB}[{k}_x - {k'}_x])
    \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d\bar{k} \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}\bar{k})
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - \bar{k}])|^2.
  \end{aligned}
\end{equation}
In addition, for the case of elastic scattering within the same Landau level, one can present the delta distribution of the energy using the same physical interpretation as follows
\begin{equation} \label{6.4}
  \delta(\varepsilon - \varepsilon_{N}) \approx
  \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)}
\end{equation}
and this leads to
\begin{equation} \label{6.5}
  \begin{aligned}
    \qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2  =
    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^5 \qty(eB)^2}
    \int_{-\infty}^{\infty} d {k'}_x \;
    J_0^2\qty(\frac{g\hbar}{eB}[{k}_x - {k'}_x])
    \qty|
    \int_{-\infty}^{\infty} d\bar{k} \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}\bar{k})
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - \bar{k}])|^2.
  \end{aligned}
\end{equation}
and
\begin{equation} \label{6.6}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,k_x)  =
    \qty[
    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^5 \qty(eB)^2}
    \int_{-\infty}^{\infty} d {k'}_x \;
    J_0^2\qty(\frac{g\hbar}{eB}[{k}_x - {k'}_x])
    \qty|
    \int_{-\infty}^{\infty} d\bar{k} \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}\bar{k})
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - \bar{k}])|^2
    ]^{-1/2}.
  \end{aligned}
\end{equation}
Using the numerical calculations we can see that the above integral is does not depend on the value of $k_x$ and we can choose any values for $k_x$. Therefore applying $k_x =0$ and letting $k'_x \rightarrow k_1,\bar{k}\rightarrow k_2$ we can modify our equation as
\begin{equation} \label{6.7}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,k_x)  =
    \qty[
    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^5 \qty(eB)^2}
    \int_{-\infty}^{\infty} d k_1\;
    J_0^2\qty(\frac{g\hbar}{eB} k_1)
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB} k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - k_2])|^2
    ]^{-1/2}.
  \end{aligned}
\end{equation}

\noindent
Now we can compare the central element of energy level broading for each Landau level using normalized Landau energy broading(inverse scattering time) against applied dressing field's electric field's amplitude ($E$) as follows
\begin{equation} \label{6.8}
    \Lambda^{00}_{N} \equiv
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}
    {\Gamma^{00}_{N}(\varepsilon,k_x)\big|_{E=0}}.
\end{equation}
As you can see in the Fig. \ref{fig6.1}, when the applied dressing field's intensity is increasing the broading of the Landau energy level decreasing. The effect of this decreasing is depend on the considering Landau level and for higher the level lower the effect.
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.5]{figures/fig04.pdf}
  \caption{Normalized broading of Landau levels agaist dressing fileds amplitude. Red line represents $N=0$, blue line represents $N=1$, green line represents $N=2$ and purplr color line represents $N=3$ Landau levels.}
  \label{fig6.1}
\end{figure}

\noindent
Then we can use Floquet conductivity expression derived in [*Ref:my report 2.488] as follows
\begin{equation} \label{6.9}
  \begin{aligned}
    \lim_{\omega \to 0}
    \text{Re}[{\sigma}^{xx}(0,\omega)] &=
    \frac{-1}{4\pi\hbar A}
    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
    \bigg(
    -\frac{\partial f}{\partial \varepsilon} \bigg)
    \frac{1}{A}\sum_{\mb{k}} \\
    & \times
    \sum_{s,s'=-\infty}^{\infty}
    {j}^x_s(\mb{k}){j}^x_{s'}(\mb{k})
    \tr_s \big[
    \big(
    \mb{G}^{r}_0 (\varepsilon;\mb{k}) - \mb{G}^{a}_0 (\varepsilon;\mb{k})
    \big)
    \odot_s
    \big(
    \mb{G}^{r}_0 (\varepsilon;\mb{k}) - \mb{G}^{a}_0 (\varepsilon;\mb{k})
    \big)
    \big].
  \end{aligned}
\end{equation}
However, in this case we are consider only $x$ directional momentum as a quantum number to seperate different states and let $\lambda = \varepsilon_N$. In addition, with the current operator derivation IF we get component values only for $s=s'=0$ our conductivity rquation will be modified to
\begin{equation} \label{6.10}
  \begin{aligned}
    \lim_{\omega \to 0}
    \text{Re}[{\sigma}^{xx}(0,\omega)] &=
    \frac{-1}{4\pi\hbar A}
    \int_{\varepsilon_N - \hbar\Omega/2}^{\varepsilon_N + \hbar\Omega/2} d\varepsilon
    \bigg(
    -\frac{\partial f}{\partial \varepsilon} \bigg)
    \frac{1}{L_x}\sum_{{k_x}}
    \qty[{j}^x_0({k_x})]^2
    \\
    & \times
    \tr \big[
    \big(
    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
    \big)
    \big(
    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
    \big)
    \big].
  \end{aligned}
\end{equation}
Now we can expand the above expressing using unitary transformation
\begin{equation} \label{6.11}
    \qty(\mb{T})_{\alpha}^{nn'} \equiv \ket*{\phi_{\alpha}^{n+n'}}
\end{equation}
where
\begin{equation} \label{6.12}
    \ket{\phi_{\alpha}(t)} = \sum_{n = - \infty}^{\infty} e^{-in\omega t}
    \ket{\phi_{\alpha}^{n}}.
\end{equation}
Therefore our conductivity equation becomes
\begin{equation} \label{6.13}
  \begin{aligned}
    \lim_{\omega \to 0}
    \text{Re}[{\sigma}^{xx}(0,\omega)] &=
    \frac{-1}{4\pi\hbar A}
    \int_{\varepsilon_N - \hbar\Omega/2}^{\varepsilon_N + \hbar\Omega/2} d\varepsilon
    \bigg(
    -\frac{\partial f}{\partial \varepsilon} \bigg)
    \frac{1}{L_x}\sum_{{k_x}}
    \qty[{j}^x_0({k_x})]^2
    \\
    & \times
    \qty[
    \mb{T}^{\dagger}(k_x)
    \big(
    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
    \big)
    \mb{T})(k_x)
    ]^2_{00}.
  \end{aligned}
\end{equation}
As derived in [*Ref:my report 2.547] we can present this matrix multiplication result as follows
\begin{equation} \label{6.14}
  \begin{aligned}
    \qty[
    \mb{T}^{\dagger}(k_x)
    \big(
    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
    \big)
    \mb{T})(k_x)
    ]^2_{00} &
    \approx
    \qty[
    \mb{T}^{\dagger}(k_x)
    \big(
    \mb{G}^{r}_0 (\varepsilon;{k_x})\mb{G}^{a}_0 (\varepsilon;{k_x})
    \big)
    \mb{T})(k_x)
    ]_{00} \\
    & =
    \frac{-1}
    {
      \qty(\frac{\varepsilon}{\hbar} - \frac{\varepsilon_N}{\hbar})^2
      +
      \qty(\frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{2\hbar})^2
    }
  \end{aligned}
\end{equation}
and this can be more simplified as
\begin{equation} \label{6.15}
  \begin{aligned}
    \qty[
    \mb{T}^{\dagger}(k_x)
    \big(
    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
    \big)
    \mb{T})(k_x)
    ]^2_{00} =
    \frac{-\hbar^2}
    {\qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2}
    \qty[
      1 +
      \qty(\frac{{\varepsilon}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon,k_x)/2})^2
    ]^{-1}.
  \end{aligned}
\end{equation}
Since the squared termed in the square brackets goinf to zero with valid conditions we can use binomial approximation for the square bracket term and get the following derivation
\begin{equation} \label{6.16}
  \begin{aligned}
    \qty[
    \mb{T}^{\dagger}(k_x)
    \big(
    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
    \big)
    \mb{T})(k_x)
    ]^2_{00} =
    \frac{-\hbar^2}
    {\qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2}
    \qty[
      1 -
      4\qty(\frac{{\varepsilon}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon,k_x)})^2
    ]
  \end{aligned}
\end{equation}

\noindent
Now the conductivity expression get modify as
\begin{equation} \label{6.17}
  \begin{aligned}
    \lim_{\omega \to 0}
    \text{Re}[{\sigma}^{xx}(0,\omega)] =
    \frac{\hbar}{4\pi A L_x}
    \int_{\varepsilon_N - \hbar\Omega/2}^{\varepsilon_N + \hbar\Omega/2} d\varepsilon
    \bigg(
    -\frac{\partial f}{\partial \varepsilon} \bigg)
    \sum_{{k_x}}
    \qty[{j}^x_0({k_x})]^2
    \frac{\hbar^2}
    {\qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2}
    \qty[
      1 -
      4\qty(\frac{{\varepsilon}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon,k_x)})^2
    ]
  \end{aligned}
\end{equation}

\noindent
Then assuming we are considering fermions in aero temperature for this scenario we can describe the particle distribution function using the Fermi-Dirac distribution in zero-tempurature.
\begin{equation} \label{6.18}
    -\frac{\partial f}{\partial \varepsilon} = \delta(\varepsilon_F - \varepsilon)
\end{equation}
where $\varepsilon_F$ represent the Fermi energy for the considered material.

\noindent
With this approximation we can derive that
\begin{equation} \label{6.19}
  \begin{aligned}
    \lim_{\omega \to 0}
    \text{Re}[{\sigma}^{xx}(0,\omega)] =
    \frac{\hbar}{4\pi A L_x}
    \int_{\varepsilon_N - \hbar\Omega/2}^{\varepsilon_N + \hbar\Omega/2} d\varepsilon
    \delta(\varepsilon_F - \varepsilon)
    \sum_{{k_x}}
    \qty[{j}^x_0({k_x})]^2
    \frac{\hbar^2}
    {\qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2}
    \qty[
      1 -
      4\qty(\frac{{\varepsilon}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon,k_x)})^2
    ]
  \end{aligned}
\end{equation}
and
\begin{equation} \label{6.20}
  \begin{aligned}
    \lim_{\omega \to 0}
    \text{Re}[{\sigma}^{xx}(0,\omega)] =
    \frac{\hbar}{4\pi A L_x}
    \sum_{{k_x}}
    \qty[{j}^x_0({k_x})]^2
    \frac{\hbar^2}
    {\qty[\Gamma^{00}_{N}(\varepsilon_F,k_x)]^2}
    \qty[
      1 -
      4\qty(\frac{{\varepsilon_F}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon_F,k_x)})^2
    ]
  \end{aligned}
\end{equation}

\hfill$\blacksquare$

### 2021-05-13 theory/sec_06.tex
Create version 2 and correct current operator and conductivity

@@
-\section{Floquet Conductivity in Landau Levels}
+\section{Current Operator in Landau Levels}
 
-Now we can derive conductivity expression for a given Landau level using Floquet conductivity expression derived in [*Ref:my report 2.488].
-Before that let's consider the inverse scattering time matrix element in the previous section.
-From Eq.
-\eqref{5.3} we can express the $N$th Landau level's inverse scattering time central element ($n=n'=0$) as
+Now consider about the current density operator for $N$th Landau level.
+Since we have already found the extact solution for our time depenedent Hamiltonian and we have identify them as Floquet states with quesi energies.
+From these solutions we can identify the \textit{Floquet modes} as given in Eq.
+\eqref{3.15} and using quantum numbers we can represent those states as follows
 \begin{equation} \label{6.1}
+  \ket{\phi_{\alpha}} = \ket{\phi_{n,m}} \equiv \ket{n,k_x} \quad
+  \text{where} \quad
+  k_x = m \frac{2\pi}{L_x}
+\end{equation}
+Using above complete set of eigenstates of Floquet Hamiltonian we can represent the single particle current operator's matrix element as
+\begin{equation} \label{6.2}
+  \qty(\mb{j})_{nm,n'm'} = \mel{n,k_x}{\;\hat{\mb{j}}\;}{n',k'_x}
+\end{equation}
+where particle current operator for this system will be
+\begin{equation} \label{6.3}
+  \hat{\mb{j}} = \frac{1}{m} \qty(\hat{\mb{P}} - e\qty[\mb{A}_s + \mb{A}_d(t)]).
+\end{equation}
+Howver, we are only consider the transverse conductivity in $x$ direction we can identify that $x$ directional current operator as
+\begin{equation} \label{6.4}
+  \hat{j}_x = \frac{1}{m} \qty(-i\hbar\pdv{x} + eBy).
+\end{equation}
+Now we can calculate the matrix elements of $x$ directional current operator's matrix in Floquet mode basis as
+\begin{equation} \label{6.5}
+  \qty({j}_x)_{nm,n'm'} = \mel{n,k_x}{\;\hat{j}_x\;}{n',k'_x} =
+  \mel{n,k_x}{\;\frac{1}{m} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x}
+\end{equation}
+and we can evaluate these using Floquet modes derived in Eq.\eqref{3.15} as follows
+\begin{equation} \label{6.6}
   \begin{aligned}
-    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N} =
-    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^4 \qty(eB)^2}
-    \delta(\varepsilon - \varepsilon_{N}) &
-    \int_{-\infty}^{\infty} d {k'}_x \;
-    J_0^2\qty(\frac{g\hbar}{eB}[{k}_x - {k'}_x])
-    \\
+    \qty({j}_x)_{nm,n'm'} & =
+    \int dx \int dy \;
+    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)
+    \exp(-ik_x x) \\
     & \times
-    \qty|
-    \int_{-\infty}^{\infty} d\bar{k} \;
-    {\chi}_{N}\qty(\frac{\hbar}{eB}\bar{k})
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - \bar{k}])|^2.
+    \frac{1}{m} \qty(-i\hbar\pdv{x} + eBy)
+    \frac{1}{\sqrt{L_x}} \chi_{n'}\big(y - y_0 - \zeta(t)\big)
+    \exp(i k'_x x)
   \end{aligned}
 \end{equation}
-Now we can introduce a new parameter with physical meaning of scatterin-induced broading of the Landau level as follows
-\begin{equation} \label{6.2}
-  \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N}
-\end{equation}
-and this modify our previous expressing as
-\begin{equation} \label{6.3}
+and this can be simplified as
+\begin{equation} \label{6.7}
   \begin{aligned}
-    \Gamma^{00}_{N}(\varepsilon,k_x)  =
-    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^4 \qty(eB)^2}
-    \delta(\varepsilon - \varepsilon_{N}) &
-    \int_{-\infty}^{\infty} d {k'}_x \;
-    J_0^2\qty(\frac{g\hbar}{eB}[{k}_x - {k'}_x])
-    \\
+    \qty({j}_x)_{nm,n'm'} & =
+    \frac{1}{{mL_x}}
+    \int dx \exp(-i(k_x-k'_x) x)
+    \int dy \;
+     \chi_{n}\big(y - y_0 - \zeta(t)\big) \\
     & \times
-    \qty|
-    \int_{-\infty}^{\infty} d\bar{k} \;
-    {\chi}_{N}\qty(\frac{\hbar}{eB}\bar{k})
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - \bar{k}])|^2.
-  \end{aligned}
-\end{equation}
-In addition, for the case of elastic scattering within the same Landau level, one can present the delta distribution of the energy using the same physical interpretation as follows
-\begin{equation} \label{6.4}
-  \delta(\varepsilon - \varepsilon_{N}) \approx
-  \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)}
-\end{equation}
-and this leads to
-\begin{equation} \label{6.5}
-  \begin{aligned}
-    \qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2  =
-    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^5 \qty(eB)^2}
-    \int_{-\infty}^{\infty} d {k'}_x \;
-    J_0^2\qty(\frac{g\hbar}{eB}[{k}_x - {k'}_x])
-    \qty|
-    \int_{-\infty}^{\infty} d\bar{k} \;
-    {\chi}_{N}\qty(\frac{\hbar}{eB}\bar{k})
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - \bar{k}])|^2.
+    \qty(\hbar k'_x + eBy)
+    \chi_{n'}\big(y - y_0 - \zeta(t)\big)
   \end{aligned}
@@
 and
-\begin{equation} \label{6.6}
+\begin{equation} \label{6.8}
   \begin{aligned}
-    \Gamma^{00}_{N}(\varepsilon,k_x)  =
-    \qty[
-    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^5 \qty(eB)^2}
-    \int_{-\infty}^{\infty} d {k'}_x \;
-    J_0^2\qty(\frac{g\hbar}{eB}[{k}_x - {k'}_x])
-    \qty|
-    \int_{-\infty}^{\infty} d\bar{k} \;
-    {\chi}_{N}\qty(\frac{\hbar}{eB}\bar{k})
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - \bar{k}])|^2
-    ]^{-1/2}.
+    \qty({j}_x)_{nm,n'm'} & =
+    \frac{1}{{m}}
+    \delta_{k_x,k'_x}
+    \int dy \;
+    \qty(\hbar k'_x + eBy)
+     \chi_{n}\big(y - y_0 - \zeta(t)\big)
+    \chi_{n'}\big(y - y_0 - \zeta(t)\big).
   \end{aligned}
 \end{equation}
-Using the numerical calculations we can see that the above integral is does not depend on the value of $k_x$ and we can choose any values for $k_x$.
-Therefore applying $k_x =0$ and letting $k'_x \rightarrow k_1,\bar{k}\rightarrow k_2$ we can modify our equation as
-\begin{equation} \label{6.7}
+Now let $y - y_0 - \zeta(t) = \bar{y}$ and we will get
+\begin{equation} \label{6.9}
   \begin{aligned}
-    \Gamma^{00}_{N}(\varepsilon,k_x)  =
+    \qty({j}_x)_{nm,n'm'} & =
+    \frac{1}{{m}}
+    \delta_{k_x,k'_x}
+    \int d\bar{y} \;
+    \qty(\hbar k'_x + eB\bar{y} + eBy_0 + eB\zeta(t))
+     \chi_{n}(\bar{y})
+    \chi_{n'}(\bar{y}).
+  \end{aligned}
+\end{equation}
+using definition of $y_0$ given in Eq. \eqref{1.11} this will be modiofied to
+\begin{equation} \label{6.10}
+  \begin{aligned}
+    \qty({j}_x)_{nm,n'm'} & =
+    \frac{1}{{m}}
+    \delta_{k_x,k'_x}
+    \int d\bar{y} \;
+    \qty(\hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t))
+     \chi_{n}(\bar{y})
+    \chi_{n'}(\bar{y})
+  \end{aligned}
+\end{equation}
+and using integral indentities of Gauss-Hermite functions
+\begin{equation} \label{6.11}
+    \int d{y} \;
+    \chi_{n}({y})
+    \chi_{n'}({y}) =
+    \delta_{n',n}
+\end{equation}
+\begin{equation} \label{6.12}
+    \int dy \;
+    y
+    \chi_{n}({y})
+    \chi_{n'}({y}) =
+    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1})
+\end{equation}
+this becomes
+\begin{equation} \label{6.13}
+  \begin{aligned}
+    \qty({j}_x)_{nm,n'm'} & =
+    \frac{1}{{m}}
+    \delta_{k_x,k'_x}
+    eB
     \qty[
-    \frac { N_{imp}^2 A^2 \hbar V_{imp}}{16\pi^5 \qty(eB)^2}
-    \int_{-\infty}^{\infty} d k_1\;
-    J_0^2\qty(\frac{g\hbar}{eB} k_1)
-    \qty|
-    \int_{-\infty}^{\infty} dk_2 \;
-    {\chi}_{N}\qty(\frac{\hbar}{eB} k_2)
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - k_2])|^2
-    ]^{-1/2}.
+    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1})
+    + \zeta(t) \delta_{n',n}
+    ]
+  \end{aligned}
+\end{equation}
+\textcolor{red}{Due to complexity we can only consider the constant contribution and we allows only the one-cycle averaged current flow} and then we can derive the $s=0$ components of the Fourier series as
+\begin{equation} \label{6.14}
+  \begin{aligned}
+    \qty({j}^x_{s=0})_{nm,n'm'} & =
+    \frac{1}{T} \int_0^T dt \;
+    \frac{1}{{m}}
+    \delta_{k_x,k'_x}
+    eB
+    \qty[
+    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1})
+    + \frac{eE}{m(\omega_0^2 - \omega^2)}\sin(\omega t) \delta_{n',n}
+    ]
+  \end{aligned}
+\end{equation}
+and this can be evaluate and get
+\begin{equation} \label{6.15}
+  \begin{aligned}
+    \qty({j}^x_{s=0})_{nm,n'm'} & =
+    \frac{eB}{{m}}
+    \delta_{k_x,k'_x}
+    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1})
   \end{aligned}
@@
 \noindent
-Now we can compare the central element of energy level broading for each Landau level using normalized Landau energy broading(inverse scattering time) against applied dressing field's electric field's amplitude ($E$) as follows
-\begin{equation} \label{6.8}
-    \Lambda^{00}_{N} \equiv
-    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}
-    {\Gamma^{00}_{N}(\varepsilon,k_x)\big|_{E=0}}.
-\end{equation}
-As you can see in the Fig.
-\ref{fig6.1}, when the applied dressing field's intensity is increasing the broading of the Landau energy level decreasing.
-The effect of this decreasing is depend on the considering Landau level and for higher the level lower the effect.
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.5]{figures/fig04.pdf}
-  \caption{Normalized broading of Landau levels agaist dressing fileds amplitude.
-Red line represents $N=0$, blue line represents $N=1$, green line represents $N=2$ and purplr color line represents $N=3$ Landau levels.}
-  \label{fig6.1}
-\end{figure}
-
-\noindent
-Then we can use Floquet conductivity expression derived in [*Ref:my report 2.488] as follows
-\begin{equation} \label{6.9}
+For electric current operator we can introduce the electron's charge and effective mass
+\begin{equation} \label{6.15}
   \begin{aligned}
-    \lim_{\omega \to 0}
-    \text{Re}[{\sigma}^{xx}(0,\omega)] &=
-    \frac{-1}{4\pi\hbar A}
-    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
-    \bigg(
-    -\frac{\partial f}{\partial \varepsilon} \bigg)
-    \frac{1}{A}\sum_{\mb{k}} \\
-    & \times
-    \sum_{s,s'=-\infty}^{\infty}
-    {j}^x_s(\mb{k}){j}^x_{s'}(\mb{k})
-    \tr_s \big[
-    \big(
-    \mb{G}^{r}_0 (\varepsilon;\mb{k}) - \mb{G}^{a}_0 (\varepsilon;\mb{k})
-    \big)
-    \odot_s
-    \big(
-    \mb{G}^{r}_0 (\varepsilon;\mb{k}) - \mb{G}^{a}_0 (\varepsilon;\mb{k})
-    \big)
-    \big].
+    \qty({j}^x_{s=0})_{nm,n'm'} & =
+    \frac{e^2B}{{m}}
+    \delta_{k_x,k'_x}
+    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1})
   \end{aligned}
 \end{equation}
-However, in this case we are consider only $x$ directional momentum as a quantum number to seperate different states and let $\lambda = \varepsilon_N$.
-In addition, with the current operator derivation IF we get component values only for $s=s'=0$ our conductivity rquation will be modified to
-\begin{equation} \label{6.10}
-  \begin{aligned}
-    \lim_{\omega \to 0}
-    \text{Re}[{\sigma}^{xx}(0,\omega)] &=
-    \frac{-1}{4\pi\hbar A}
-    \int_{\varepsilon_N - \hbar\Omega/2}^{\varepsilon_N + \hbar\Omega/2} d\varepsilon
-    \bigg(
-    -\frac{\partial f}{\partial \varepsilon} \bigg)
-    \frac{1}{L_x}\sum_{{k_x}}
-    \qty[{j}^x_0({k_x})]^2
-    \\
-    & \times
-    \tr \big[
-    \big(
-    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
-    \big)
-    \big(
-    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
-    \big)
-    \big].
-  \end{aligned}
-\end{equation}
-Now we can expand the above expressing using unitary transformation
-\begin{equation} \label{6.11}
-    \qty(\mb{T})_{\alpha}^{nn'} \equiv \ket*{\phi_{\alpha}^{n+n'}}
-\end{equation}
-where
-\begin{equation} \label{6.12}
-    \ket{\phi_{\alpha}(t)} = \sum_{n = - \infty}^{\infty} e^{-in\omega t}
-    \ket{\phi_{\alpha}^{n}}.
-\end{equation}
-Therefore our conductivity equation becomes
-\begin{equation} \label{6.13}
-  \begin{aligned}
-    \lim_{\omega \to 0}
-    \text{Re}[{\sigma}^{xx}(0,\omega)] &=
-    \frac{-1}{4\pi\hbar A}
-    \int_{\varepsilon_N - \hbar\Omega/2}^{\varepsilon_N + \hbar\Omega/2} d\varepsilon
-    \bigg(
-    -\frac{\partial f}{\partial \varepsilon} \bigg)
-    \frac{1}{L_x}\sum_{{k_x}}
-    \qty[{j}^x_0({k_x})]^2
-    \\
-    & \times
-    \qty[
-    \mb{T}^{\dagger}(k_x)
-    \big(
-    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
-    \big)
-    \mb{T})(k_x)
-    ]^2_{00}.
-  \end{aligned}
-\end{equation}
-As derived in [*Ref:my report 2.547] we can present this matrix multiplication result as follows
-\begin{equation} \label{6.14}
-  \begin{aligned}
-    \qty[
-    \mb{T}^{\dagger}(k_x)
-    \big(
-    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
-    \big)
-    \mb{T})(k_x)
-    ]^2_{00} &
-    \approx
-    \qty[
-    \mb{T}^{\dagger}(k_x)
-    \big(
-    \mb{G}^{r}_0 (\varepsilon;{k_x})\mb{G}^{a}_0 (\varepsilon;{k_x})
-    \big)
-    \mb{T})(k_x)
-    ]_{00} \\
-    & =
-    \frac{-1}
-    {
-      \qty(\frac{\varepsilon}{\hbar} - \frac{\varepsilon_N}{\hbar})^2
-      +
-      \qty(\frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{2\hbar})^2
-    }
-  \end{aligned}
-\end{equation}
-and this can be more simplified as
-\begin{equation} \label{6.15}
-  \begin{aligned}
-    \qty[
-    \mb{T}^{\dagger}(k_x)
-    \big(
-    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
-    \big)
-    \mb{T})(k_x)
-    ]^2_{00} =
-    \frac{-\hbar^2}
-    {\qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2}
-    \qty[
-      1 +
-      \qty(\frac{{\varepsilon}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon,k_x)/2})^2
-    ]^{-1}.
-  \end{aligned}
-\end{equation}
-Since the squared termed in the square brackets goinf to zero with valid conditions we can use binomial approximation for the square bracket term and get the following derivation
-\begin{equation} \label{6.16}
-  \begin{aligned}
-    \qty[
-    \mb{T}^{\dagger}(k_x)
-    \big(
-    \mb{G}^{r}_0 (\varepsilon;{k_x}) - \mb{G}^{a}_0 (\varepsilon;{k_x})
-    \big)
-    \mb{T})(k_x)
-    ]^2_{00} =
-    \frac{-\hbar^2}
-    {\qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2}
-    \qty[
-      1 -
-      4\qty(\frac{{\varepsilon}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon,k_x)})^2
-    ]
-  \end{aligned}
-\end{equation}
-
-\noindent
-Now the conductivity expression get modify as
-\begin{equation} \label{6.17}
-  \begin{aligned}
-    \lim_{\omega \to 0}
-    \text{Re}[{\sigma}^{xx}(0,\omega)] =
-    \frac{\hbar}{4\pi A L_x}
-    \int_{\varepsilon_N - \hbar\Omega/2}^{\varepsilon_N + \hbar\Omega/2} d\varepsilon
-    \bigg(
-    -\frac{\partial f}{\partial \varepsilon} \bigg)
-    \sum_{{k_x}}
-    \qty[{j}^x_0({k_x})]^2
-    \frac{\hbar^2}
-    {\qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2}
-    \qty[
-      1 -
-      4\qty(\frac{{\varepsilon}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon,k_x)})^2
-    ]
-  \end{aligned}
-\end{equation}
-
-\noindent
-Then assuming we are considering fermions in aero temperature for this scenario we can describe the particle distribution function using the Fermi-Dirac distribution in zero-tempurature.
-\begin{equation} \label{6.18}
-    -\frac{\partial f}{\partial \varepsilon} = \delta(\varepsilon_F - \varepsilon)
-\end{equation}
-where $\varepsilon_F$ represent the Fermi energy for the considered material.
-
-\noindent
-With this approximation we can derive that
-\begin{equation} \label{6.19}
-  \begin{aligned}
-    \lim_{\omega \to 0}
-    \text{Re}[{\sigma}^{xx}(0,\omega)] =
-    \frac{\hbar}{4\pi A L_x}
-    \int_{\varepsilon_N - \hbar\Omega/2}^{\varepsilon_N + \hbar\Omega/2} d\varepsilon
-    \delta(\varepsilon_F - \varepsilon)
-    \sum_{{k_x}}
-    \qty[{j}^x_0({k_x})]^2
-    \frac{\hbar^2}
-    {\qty[\Gamma^{00}_{N}(\varepsilon,k_x)]^2}
-    \qty[
-      1 -
-      4\qty(\frac{{\varepsilon}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon,k_x)})^2
-    ]
-  \end{aligned}
-\end{equation}
-and
-\begin{equation} \label{6.20}
-  \begin{aligned}
-    \lim_{\omega \to 0}
-    \text{Re}[{\sigma}^{xx}(0,\omega)] =
-    \frac{\hbar}{4\pi A L_x}
-    \sum_{{k_x}}
-    \qty[{j}^x_0({k_x})]^2
-    \frac{\hbar^2}
-    {\qty[\Gamma^{00}_{N}(\varepsilon_F,k_x)]^2}
-    \qty[
-      1 -
-      4\qty(\frac{{\varepsilon_F}-{\varepsilon_N}}{\Gamma^{00}_{N}(\varepsilon_F,k_x)})^2
-    ]
-  \end{aligned}
-\end{equation}
-
 \hfill$\blacksquare$

### 2021-05-18 theory/sec_08.tex
Add conductivity analysis

\section{Manipulate Conductivity in Quantum Hall System}

Now using the relations derived in Eq. \eqref{5.34} and Eq. \eqref{7.17} we can derive that
\begin{equation} \label{8.1}
  \Gamma_n = \qty(\frac{\hbar }{2\tau(\varepsilon_n)}) =
  \frac{1}{2}\Gamma^{00}_{N}(\tilde{I})
\end{equation}
and this will be
\begin{equation} \label{8.2}
  \Gamma_n(\tilde{I}) = 0.12\times
  \qty[
  \frac
  {\int_{-\infty}^{\infty} d {k}_1 \;
  J_0^2\qty(2.090\sqrt{\tilde{I}}\times{k}_1)
  \qty|
  \int_{-\infty}^{\infty} d{k}_2 \;
  \tilde{\chi}_{N}\qty(2.342 \times k_2)
  \tilde{\chi}_{N}\qty(2.342 \times \qty[{k}_1 - {k}_2])|^2}
  {\int_{-\infty}^{\infty} d {k}_1 \;
  \qty|
  \int_{-\infty}^{\infty} d{k}_2 \;
  \tilde{\chi}_{0}\qty(2.342 \times k_2)
  \tilde{\chi}_{0}\qty(2.342 \times \qty[{k}_1 - {k}_2])|^2}
  ]^{1/2} \text{meV}
\end{equation}

\noindent
In addition we can calculate the cyclotron energy as
\begin{equation} \label{8.3}
  \hbar\omega_0 = 1.95663 \;\text{meV}
\end{equation}
and
\begin{equation} \label{8.4}
  \gamma_n = \frac{\Gamma_n}{\hbar \omega_0} = 0.06133 \times \Lambda_n(\tilde{I}) \approx 0.061 \Lambda_n(\tilde{I})
\end{equation}

\noindent
Now we can use this into our conductivity expression derived in Eq. \eqref{7.23} and present the normalized transverse conductivity as a function of fermi energy and intensity of the dressing field
\begin{equation} \label{8.5}
  \begin{aligned}
    \sigma^{xx}(X_F,\tilde{I}) & =
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}}
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ]
  \end{aligned}
\end{equation}

\hfill$\blacksquare$

### 2021-05-19 theory/sec_08.tex
Add calculated normalized values
Add conductivity graphs

@@
 \end{equation}
+where
+\begin{equation} \label{8.6}
+    \Lambda_n  =
+    \qty[
+    \frac
+    {\int_{-\infty}^{\infty} d {k}_1 \;
+    J_0^2\qty(2.090\sqrt{\tilde{I}}\times{k}_1)
+    \qty|
+    \int_{-\infty}^{\infty} d{k}_2 \;
+    \tilde{\chi}_{n}\qty(2.342 \times k_2)
+    \tilde{\chi}_{n}\qty(2.342 \times \qty[{k}_1 - {k}_2])|^2}
+    {\int_{-\infty}^{\infty} d {k}_1 \;
+    \qty|
+    \int_{-\infty}^{\infty} d{k}_2 \;
+    \tilde{\chi}_{0}\qty(2.342 \times k_2)
+    \tilde{\chi}_{0}\qty(2.342 \times \qty[{k}_1 - {k}_2])|^2}
+    ]^{1/2}.
+\end{equation}
+\hfill$\blacksquare$
 
-\hfill$\blacksquare$
+\noindent
+Now using Eq. \eqref{8.6} we can calculate the normalized broadening of each Landau levels as given in Table \ref{tab:8.1}.
+
+\begin{table}[ht!]
+\begin{center}
+\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|c| }
+ \hline
+ ${\tilde{I}}$
+ & $n=0$ & $n=1$ & $n=2$ & $n=3$ & $n=4$ & $n=5$ & $n=6$ & $n=7$ & $n=8$ & $n=9$
+ & $n=10$
+ \\ [0.5ex] \hline\hline
+ 0  & $1.0000$ & $0.8660$ & $0.8004$ & $0.7578$ & $0.7266$
+ & $0.7021$ & $0.6821$ & $0.6653$ & $0.6507$ & $0.6380$& $0.6267$ \\ \hline
+ 1  & $0.8546$ & $0.7037$ & $0.6502$ & $0.6114$ & $0.5810$
+ & $0.5584$ & $0.5416$ & $0.5280$ & $0.5160$ & $0.5050$ & $0.4948$ \\ \hline
+ 4  & $0.6875$ & $0.6345$ & $0.5902$ & $0.5528$ & $0.5307$
+ & $0.5118$ & $0.4958$ & $0.4840$ & $0.4730$ & $0.4629$  & $0.4547$ \\ \hline
+ 9  & $0.5936$ & $0.5539$ & $0.5333$ & $0.5180$ & $0.5006$
+ & $0.4812$ & $0.4685$ & $0.4564$ & $0.4469$ & $0.4377$  & $0.4305$ \\ \hline
+\end{tabular}
+\caption {\label{tab:8.1} $\Lambda_n$ values for each Landau level by changing  applied dressing field intensity ($\tilde{I}$). }
+\end{center}
+\end{table}
+
+\noindent
+Using above values we can analyse the changes can be done to the transverse conductivity using apllied dressing field.
+As given in Figure \ref{fig:8.1} and \ref{fig:8.2} we can manipulate the conductivity using external dressing field.
+When the applied field's intensity increase the broadening of energy bands of Landau levels get reduced the conductivity also get decrease all the regions except the peak point of the energy band.
+Using this manipulation we can filter the conductivity which is change with the Fermi level.
+Since Fermi level can be change with the applied gate voltage of the material this can be used as a 2D switch for optoelectonic applications.
+Using the applied dressing field we can fine tune the switching mechanism.
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[scale=1]{figures/fig81.pdf}
+  \caption{Normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
+  \label{fig:8.1}
+\end{figure}
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[scale=1]{figures/fig82.pdf}
+  \caption{$3$rd Landau level's normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
+  \label{fig:8.2}
+\end{figure}

### 2021-05-20 theory/sec_06.tex
Finalize conductivity equation
Add yy conductivity

@@
 \end{equation}
-Howver, we are only consider the transverse conductivity in $x$ direction we can identify that $x$ directional current operator as
+Let's consider the transverse conductivity in $x$ direction and we can identify that $x$ directional current operator as
 \begin{equation} \label{6.4}
@@
 For electric current operator we can introduce the electron's charge and effective mass
-\begin{equation} \label{6.15}
+\begin{equation} \label{6.16}
   \begin{aligned}
     \qty({j}^x_{s=0})_{nm,n'm'} & =
-    \frac{e^2B}{{m}}
+    \frac{e^2B}{{m_e}}
     \delta_{k_x,k'_x}
@@
 \hfill$\blacksquare$
+
+\noindent
+Next we can consider the transverse conductivity in $y$ direction and we can identify that $y$ directional current operator as
+\begin{equation} \label{6.17}
+  \hat{j}_y = \frac{1}{m} \qty(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t)).
+\end{equation}
+Now we can calculate the matrix elements of $y$ directional current operator's matrix in Floquet mode basis as
+\begin{equation} \label{6.18}
+  \qty({j}_y)_{nm,n'm'} = \mel{n,k_x}{\;\hat{j}_y\;}{n',k'_x} =
+  \mel{n,k_x}{\;\frac{-1}{m} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))\;}{n',k'_x}
+\end{equation}
+and we can evaluate these using Floquet modes derived in Eq.\eqref{3.15} as follows
+\begin{equation} \label{6.19}
+  \begin{aligned}
+    \qty({j}_y)_{nm,n'm'} & =
+    \int dx \int dy \;
+    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)
+    \exp(-ik_x x) \\
+    & \times
+    \frac{-1}{m} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))
+    \frac{1}{\sqrt{L_x}} \chi_{n'}\big(y - y_0 - \zeta(t)\big)
+    \exp(i k'_x x)
+  \end{aligned}
+\end{equation}
+then introducing new variable
+\begin{equation} \label{6.20}
+  y - y_0 - \zeta(t) = \bar{y} \quad \longrightarrow \quad dy = d{\bar{y}}
+\end{equation}
+and follwing identity [*Ref: Appendix A Hermite fucntions]
+\begin{equation} \label{6.21}
+  \pdv{\chi_n(y)}{y} = -\sqrt{\frac{n+1}{2}} \chi_{n+1}(y) +
+  \sqrt{\frac{n}{2}} \chi_{n-1}(y)
+\end{equation}
+above expression can be simplified as previous case (let $y=\bar{y}$)
+\begin{equation} \label{6.22}
+  \begin{aligned}
+    \qty({j}_y)_{nm,n'm'} & =
+    \frac{-1}{{m}}
+    \delta_{k_x,k'_x}
+    \int dy \;
+     \chi_{n}(y)
+    \qty[-i\hbar \qty(
+    \sqrt{\frac{n'+1}{2}} \chi_{n'+1}(y) - \sqrt{\frac{n'}{2}} \chi_{n'-1}(y)
+    ) + \frac{eE}{\omega}\cos(\omega t)
+    \chi_{n'}(y)].
+  \end{aligned}
+\end{equation}
+Then considering Gauss-Hermite integral indentities we can derive that
+\begin{equation} \label{6.23}
+  \begin{aligned}
+    \qty({j}_y)_{nm,n'm'} & =
+    \frac{1}{{m}}
+    \delta_{k_x,k'_x}
+    \qty[i\hbar \qty(
+    \sqrt{\frac{n'+1}{2}} \delta_{n,n'+1}
+    - \sqrt{\frac{n'}{2}} \delta_{n,n'-1}
+    ) - \frac{eE}{\omega}\cos(\omega t) \delta_{n,n'}]
+  \end{aligned}
+\end{equation}
+\textcolor{red}{Due to complexity we can only consider the constant contribution and we allows only the one-cycle averaged current flow} and then we can derive the $s=0$ components of the Fourier series as
+\begin{equation} \label{6.24}
+  \begin{aligned}
+    \qty({j}^y_{s=0})_{nm,n'm'} & =
+    \frac{1}{T} \int_0^T dt \;
+    \frac{1}{{m}}
+    \delta_{k_x,k'_x}
+    \qty[i\hbar \qty(
+    \sqrt{\frac{n'+1}{2}} \delta_{n,n'+1}
+    - \sqrt{\frac{n'}{2}} \delta_{n,n'-1}
+    ) - \frac{eE}{\omega}\cos(\omega t) \delta_{n,n'}]
+  \end{aligned}
+\end{equation}
+and this can be evaluate and get
+\begin{equation} \label{6.25}
+  \begin{aligned}
+    \qty({j}^y_{s=0})_{nm,n'm'} & =
+    \frac{i\hbar}{{m}}
+    \delta_{k_x,k'_x}
+    \qty[
+    \sqrt{\frac{n'+1}{2}} \delta_{n,n'+1}
+    - \sqrt{\frac{n'}{2}} \delta_{n,n'-1}
+    ]
+  \end{aligned}
+\end{equation}
+and this can be re-write as
+\begin{equation} \label{6.26}
+  \begin{aligned}
+    \qty({j}^y_{s=0})_{nm,n'm'} & =
+    \frac{i\hbar}{{m}}
+    \delta_{k_x,k'_x}
+    \qty[
+    \sqrt{\frac{n}{2}} \delta_{n',n-1}
+    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
+    ]
+  \end{aligned}
+\end{equation}
+
+\noindent
+For electric current operator we can introduce the electron's charge and effective mass
+\begin{equation} \label{6.27}
+  \begin{aligned}
+    \qty({j}^y_{s=0})_{nm,n'm'} & =
+    \frac{ie\hbar}{{m}}
+    \delta_{k_x,k'_x}
+    \qty[
+    \sqrt{\frac{n}{2}} \delta_{n',n-1}
+    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
+    ]
+  \end{aligned}
+\end{equation}
+\hfill$\blacksquare$
+
+xx

### 2021-05-21 summary/Summary.tex
Add summary for the proposal

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{graphicx}
\usepackage{url}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}

\numberwithin{equation}{subsection}
\newcommand{\mb}[1]{\mathbf{#1}}
\title{Floquet-Drude Conductivity in Dressed Quantum Hall Systems}
\author{Kosala Sananthana Herath}
\numberwithin{equation}{section}

\begin{document}

\maketitle

\section*{Abstract}

Interactions between light and matter have dragged research attention in the fields of optoelectronics, sensing, energy harvesting, quantum computing, bio-information, and in many branches of recent technologies. For many years, the foremost aims for examing the characteristics of dressed fermion systems were focused on the different types of atomic and molecular arrangements. These researches of extreme electron-light engagements introduced an astonishing scope of twentieth-century physics namely quantum optic physics.

On the other hand, in nanostructures that are applicable in electronic devices, the investigations with the help of quantum optic were centered on polaritonic and exciton influences on nanostructures and material characteristics of dressed electrons in two-dimensional(2D) materials and quantum wires. When considering the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.

Therefore, transport properties of nanostructures exposed to a high intensity periodic electromagnetic fields have been explored theoretically in this study. The dressing field is analyzed non perturbatively using the Floquet theory whilst the probing field is examined perturbatively by applying the linear response method using the Kubo formula. The general Floquet-Drude conductivity has been derived in a fully closed analytical form in most recent research [1,2], introducing a novel type of Green’s functions namely four-times Green’s functions.
As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nanostructures by an intense dressing field. From an empirical sense, this study applies directly to various nanostructures illuminated by a high-intensity electromagnetic field.
In this research we have developed a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field and that will enable efficient manipulation of transport characteristics in nanoscale electronic devices.

\section*{Purpose of the Study}

When a stationary magentic field applied perpendicularly across the surface of 2DEG systems, the orbital motion of electrons becomes completely quantized and the energy spectrium becomes discrete by creating Landau levels. Such a singular system known as a quantum Hall system and in this study we explictly calculate the diagonal ($\sigma_{xx},\sigma_{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems.

Although there are already exist a number of adavanced theories devoted to the calculation of conductivity tensor elements in a quantum Hall systems [3-5], they have not been applied to the optically manipulation the magneto-electric properties of the quantum Hall systems. However K. Dini et al. [6] have recently investigated the one directional conductivity behaviour of dressed quantum Hall systems, they have not used the state of art model to describe the conductivity in a quantum Hall system. In their study they used the conductivity models from T. Ando et al. [3,4] and as mentioned in A. Endo et al. investigation [5] those models are far less accurate representation of the experimantally observed Landau levels because they present a semi-elliptical broadening.

In this study we develop a genralized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [1,2]. In addition, we demonstrate that our generalized model is agreed with the state of art conductivity model [5] for specalized quantum Hall system which has been considered without the external dressing field.

\section*{Research Method}

In this analysis we consider 2DEG which has been distrubuted in confined $(x,y)$ plane in configuration space.
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.9]{figures/fig0.pdf}
  \caption{Confined 2DEG in configuration space with the size of $A=L_xL_y$.}
  \label{fig:1}
\end{figure}

We examined the properties of 2DEG with stationary magnetic field which directed on $z$ axis and a linearly $y$-polarized strong electomagnetic wave (dressing field) with electric field which also propagate in $z$ direction.
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.9]{figures/fig1.pdf}
  \caption{Stationary magnetic filed (blue color) and Strong EM wave (red color) applied to the 2DEG.}
  \label{fig:2}
\end{figure}

In the state of art conductivity model [5] which only describes trasport properies quantum Hall system without external dressing field has used an approximation equivalent to asssumin that the broadening of a Landau level due to disorder is represented by a constant broadening. However, from the Floquet-Drude conductivity model we have foud that we can manipulate the impurity broadening using intense high-frequency electromagnetic waves and this study we have developed a mathematical formula to calculate this Landau energy level broadening and using those values we were able to evaluate diagonal elements of conductivity tensor in dressed quantum Hall systems. Ultimately we can express the normalized conductivity for a quantum Hall system with linearly polarized drerssing field analytically as follows
\begin{equation*}
    \sigma^{dd}(X_F,\tilde{I}) =
    \sum_{n}
    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}}
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{\gamma_{n+1}})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{\gamma_{n}})^2
      }
    ]
\end{equation*}
where $X_F$ is normalized Fermi level and $\gamma_n$ represnts normalized energy band broadening of $n$-th Landau level. This $\gamma_n$ only depends on the normalized intensity value of dressing field $\tilde{I}$. We can choose the direction $d$ of the diagonal conductivity tensor element from $(x,y)$.

\section*{Outcomes and Discussion}

First we have identified that we can control the Landau level broadening using the dressing field intensity as given in the Figure \ref{fig:3}.
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.6]{figures/fig3.pdf}
  \caption{The dependence of the normalized Landau level broadening on the dressing field intensity for different Landau levels ($N=0,1,2,3,4$).}
  \label{fig:3}
\end{figure}

As mentioned in above derived analytical expression the changes can be done to the transverse conductivity using external dressing field. As given in Figure \ref{fig:4} and \ref{fig:5} we can manipulate the conductivity using external dressing field.

\begin{figure}[ht!]
  \centering
  \includegraphics[scale=1]{figures/fig4.pdf}
  \caption{Normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
  \label{fig:4}
\end{figure}

When the dressing field's intensity increase the broadening of energy bands of Landau levels get reduced and the conductivity also get decrease in all the regions except the peak points of each level. Using this manipulation we can filter the conductivity which is change with the Fermi level. Since Fermi level can be change with the applied gate voltage of the material this can be used as a 2D switch for optoelectonic applications. However with the existance of  external dressing field we can fine tune the switching mechanism and it is an exceptional advantage in optoelectonic applications.

\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.9]{figures/fig5.pdf}
  \caption{$3$rd Landau level's normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
  \label{fig:5}
\end{figure}

Now we can compare our result with previous studies to the check the validity of the outcomes. In the research done by K. Dini et al. [6] has demonstrated that the diagonal elements of conductivity tensor in a quantum Hall system can manipute with apllying high intense light as given in Figure \ref{fig:6}. However the behaviour of the conductivity with the Fermi level is not accurate as given in the state of art study [5] which has been represent in Figure \ref{fig:7}. When we consider the our outcome which derived using novel Floquet-Drude conductivity model, we can see that it agree with the results given in the much accurate study [5]. However, our study present a more generalized mathematical model rather than the specific scenario studied in the study [6].

\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.3]{figures/fig6.pdf}
  \caption{The dependence of the longitudinal conductivity $\sigma_{xx}$ , on
the Fermi energy $\varepsilon_F$. The solid line describes the conductivity
of unirradiated 2DEG, whereas the dotted line corresponds to the
conductivity at the irradiation intensity $I = 600 \; \text{W/cm2}$. The inset
shows the difference between these two conductivities. (from K.Dini at el. [6])}
  \label{fig:6}
\end{figure}

\newpage
\begin{figure}[ht!]
  \centering
  \includegraphics[scale=0.3]{figures/fig7.pdf}
  \caption{The diagonal and the off-diagonal components
of the conductivity tensor modified to account for the long-range potential. The
horizontal axis is the inverse magnetic field. (from A. Endo at el. [5])}
  \label{fig:7}
\end{figure}

We can conclude that the using external dressing field we can manipulate the magneto-electric properties of a quantum Hall system and in this study we were able to demonstrate that using Floquet-Drude conductivity method we can derive a more accurate generalized mathematical model that describe the trasport properties of quantum Hall syatems. Therefore this theory describes that the  dressing field can be used as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectonic devices.

\section*{Reference}

[1] M. Wackerl, P. Wenk, and J. Schliemann, Floquet-Drude Conductivity, Phys. Rev. B 101, 184204 (2020).

\noindent
[2] M. Wackerl, Transport in Periodically Driven Systems, University of Regensburg, (2020).

\noindent
[3] T. Ando and Y. Uemura, Theory of Quantum Transport in a Two-Dimensional Electron System under Magnetic Fields. I. Characteristics of Level Broadening and Transport under Strong Fields, J. Phys. Soc. Jpn. 36, 959 (1974).

\noindent
[4] T. Ando, A. B. Fowler, and F. Stern, Electronic Properties of Two-Dimensional Systems, Rev. Mod. Phys. 54, 437 (1982).

\noindent
[5] A. Endo, N. Hatano, H. Nakamura, and R. Shirasaki, Fundamental Relation between Longitudinal and Transverse Conductivities in the Quantum Hall System, J. Phys.: Condens. Matter 21, 345803 (2009).

\noindent
[6] K. Dini, O. V. Kibis, and I. A. Shelykh, Magnetic Properties of a Two-Dimensional Electron Gas Strongly Coupled to Light, Phys. Rev. B 93, 235411 (2016).

\end{document}

### 2021-06-20 paper/v1.0/apssamp.tex
Paper initial commit

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose,
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{Floquet-Drude Conductivity in Dressed Quantum Hall Systems}% Force line breaks with \\
% \thanks{A footnote to the article title}%

\author{Kosala Herath}
 % \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
\author{Malin Premaratne}%
 \email{Second.Author@institution.edu}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{MUSO Collaboration}%\noaffiliation

\author{Charlie Author}
 \homepage{http://www.Second.institution.edu/~Charlie.Author}
\affiliation{
 Second institution and/or address\\
 This line break forced% with \\
}%
\affiliation{
 Third institution, the second for Charlie Author
}%
\author{Delta Author}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%

\collaboration{CLEO Collaboration}%\noaffiliation

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article.
\begin{description}
\item[Usage]
Secondary publications and information retrieval purposes.
\item[Structure]
You may use the \texttt{description} environment to structure your abstract;
use the optional argument of the \verb+\item+ command to give the category of each item.
\end{description}
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

%\tableofcontents

\section{\label{sec:level1}First-level heading:\protect\\ The line
break was forced \lowercase{via} \textbackslash\textbackslash}

This sample document demonstrates proper use of REV\TeX~4.2 (and
\LaTeXe) in mansucripts prepared for submission to APS
journals. Further information can be found in the REV\TeX~4.2
documentation included in the distribution or available at
\url{http://journals.aps.org/revtex/}.

When commands are referred to in this example file, they are always
shown with their required arguments, using normal \TeX{} format. In
this format, \verb+#1+, \verb+#2+, etc. stand for required
author-supplied arguments to commands. For example, in
\verb+\section{#1}+ the \verb+#1+ stands for the title text of the
author's section heading, and in \verb+\title{#1}+ the \verb+#1+
stands for the title text of the paper.

Line breaks in section headings at all levels can be introduced using
\textbackslash\textbackslash. A blank input line tells \TeX\ that the
paragraph has ended. Note that top-level section headings are
automatically uppercased. If a specific letter or word should appear in
lowercase instead, you must escape it using \verb+\lowercase{#1}+ as
in the word ``via'' above.

\subsection{\label{sec:level2}Second-level heading: Formatting}

This file may be formatted in either the \texttt{preprint} or
\texttt{reprint} style. \texttt{reprint} format mimics final journal output.
Either format may be used for submission purposes. \texttt{letter} sized paper should
be used when submitting to APS journals.

\subsubsection{Wide text (A level-3 head)}
The \texttt{widetext} environment will make the text the width of the
full page, as on page~\pageref{eq:wideeq}. (Note the use the
\verb+\pageref{#1}+ command to refer to the page number.)
\paragraph{Note (Fourth-level head is run in)}
The width-changing commands only take effect in two-column formatting.
There is no effect if text is in a single column.

\subsection{\label{sec:citeref}Citations and References}
A citation in text uses the command \verb+\cite{#1}+ or
\verb+\onlinecite{#1}+ and refers to an entry in the bibliography.
An entry in the bibliography is a reference to another document.

\subsubsection{Citations}
Because REV\TeX\ uses the \verb+natbib+ package of Patrick Daly,
the entire repertoire of commands in that package are available for your document;
see the \verb+natbib+ documentation for further details. Please note that
REV\TeX\ requires version 8.31a or later of \verb+natbib+.

\paragraph{Syntax}
The argument of \verb+\cite+ may be a single \emph{key},
or may consist of a comma-separated list of keys.
The citation \emph{key} may contain
letters, numbers, the dash (-) character, or the period (.) character.
New with natbib 8.3 is an extension to the syntax that allows for
a star (*) form and two optional arguments on the citation key itself.
The syntax of the \verb+\cite+ command is thus (informally stated)
\begin{quotation}\flushleft\leftskip1em
\verb+\cite+ \verb+{+ \emph{key} \verb+}+, or\\
\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+}+, or\\
\verb+\cite+ \verb+{+ \emph{optarg+key} \verb+,+ \emph{optarg+key}\ldots \verb+}+,
\end{quotation}\noindent
where \emph{optarg+key} signifies
\begin{quotation}\flushleft\leftskip1em
\emph{key}, or\\
\texttt{*}\emph{key}, or\\
\texttt{[}\emph{pre}\texttt{]}\emph{key}, or\\
\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}, or even\\
\texttt{*}\texttt{[}\emph{pre}\texttt{]}\texttt{[}\emph{post}\texttt{]}\emph{key}.
\end{quotation}\noindent
where \emph{pre} and \emph{post} is whatever text you wish to place
at the beginning and end, respectively, of the bibliographic reference
(see Ref.~[\onlinecite{witten2001}] and the two under Ref.~[\onlinecite{feyn54}]).
(Keep in mind that no automatic space or punctuation is applied.)
It is highly recommended that you put the entire \emph{pre} or \emph{post} portion
within its own set of braces, for example:
\verb+\cite+ \verb+{+ \texttt{[} \verb+{+\emph{text}\verb+}+\texttt{]}\emph{key}\verb+}+.
The extra set of braces will keep \LaTeX\ out of trouble if your \emph{text} contains the comma (,) character.

The star (*) modifier to the \emph{key} signifies that the reference is to be
merged with the previous reference into a single bibliographic entry,
a common idiom in APS and AIP articles (see below, Ref.~[\onlinecite{epr}]).
When references are merged in this way, they are separated by a semicolon instead of
the period (full stop) that would otherwise appear.

\paragraph{Eliding repeated information}
When a reference is merged, some of its fields may be elided: for example,
when the author matches that of the previous reference, it is omitted.
If both author and journal match, both are omitted.
If the journal matches, but the author does not, the journal is replaced by \emph{ibid.},
as exemplified by Ref.~[\onlinecite{epr}].
These rules embody common editorial practice in APS and AIP journals and will only
be in effect if the markup features of the APS and AIP Bib\TeX\ styles is employed.

\paragraph{The options of the cite command itself}
Please note that optional arguments to the \emph{key} change the reference in the bibliography,
not the citation in the body of the document.
For the latter, use the optional arguments of the \verb+\cite+ command itself:
\verb+\cite+ \texttt{*}\allowbreak
\texttt{[}\emph{pre-cite}\texttt{]}\allowbreak
\texttt{[}\emph{post-cite}\texttt{]}\allowbreak
\verb+{+\emph{key-list}\verb+}+.

\subsubsection{Example citations}
By default, citations are numerical\cite{Beutler1994}.
Author-year citations are used when the journal is RMP.
To give a textual citation, use \verb+\onlinecite{#1}+:
Refs.~\onlinecite{[][{, and references therein}]witten2001,Bire82}.
By default, the \texttt{natbib} package automatically sorts your citations into numerical order and ``compresses'' runs of three or more consecutive numerical citations.
REV\TeX\ provides the ability to automatically change the punctuation when switching between journal styles that provide citations in square brackets and those that use a superscript style instead. This is done through the \texttt{citeautoscript} option. For instance, the journal style \texttt{prb} automatically invokes this option because \textit{Physical
Review B} uses superscript-style citations. The effect is to move the punctuation, which normally comes after a citation in square brackets, to its proper position before the superscript.
To illustrate, we cite several together
\cite{[See the explanation of time travel in ]feyn54,*[The classical relativistic treatment of ][ is a relative classic]epr,witten2001,Berman1983,Davies1998,Bire82},
and once again in different order (Refs.~\cite{epr,feyn54,Bire82,Berman1983,witten2001,Davies1998}).
Note that the citations were both compressed and sorted. Futhermore, running this sample file under the \texttt{prb} option will move the punctuation to the correct place.

When the \verb+prb+ class option is used, the \verb+\cite{#1}+ command
displays the reference's number as a superscript rather than in
square brackets. Note that the location of the \verb+\cite{#1}+
command should be adjusted for the reference style: the superscript
references in \verb+prb+ style must appear after punctuation;
otherwise the reference must appear before any punctuation. This
sample was written for the regular (non-\texttt{prb}) citation style.
The command \verb+\onlinecite{#1}+ in the \texttt{prb} style also
displays the reference on the baseline.

\subsubsection{References}
A reference in the bibliography is specified by a \verb+\bibitem{#1}+ command
with the same argument as the \verb+\cite{#1}+ command.
\verb+\bibitem{#1}+ commands may be crafted by hand or, preferably,
generated by Bib\TeX.
REV\TeX~4.2 includes Bib\TeX\ style files
\verb+apsrev4-2.bst+, \verb+apsrmp4-2.bst+ appropriate for
\textit{Physical Review} and \textit{Reviews of Modern Physics},
respectively.

\subsubsection{Example references}
This sample file employs the \verb+\bibliography+ command,
which formats the \texttt{\jobname .bbl} file
and specifies which bibliographic databases are to be used by Bib\TeX\
(one of these should be by arXiv convention \texttt{\jobname .bib}).
Running Bib\TeX\ (via \texttt{bibtex \jobname})
after the first pass of \LaTeX\ produces the file
\texttt{\jobname .bbl} which contains the automatically formatted
\verb+\bibitem+ commands (including extra markup information via
\verb+\bibinfo+ and \verb+\bibfield+ commands).
If not using Bib\TeX, you will have to create the \verb+thebibiliography+ environment
and its \verb+\bibitem+ commands by hand.

Numerous examples of the use of the APS bibliographic entry types appear in the bibliography of this sample document.
You can refer to the \texttt{\jobname .bib} file,
and compare its information to the formatted bibliography itself.

\subsection{Footnotes}%
Footnotes, produced using the \verb+\footnote{#1}+ command,
usually integrated into the bibliography alongside the other entries.
Numerical citation styles do this%
\footnote{Automatically placing footnotes into the bibliography requires using BibTeX to compile the bibliography.};
author-year citation styles place the footnote at the bottom of the text column.
Note: due to the method used to place footnotes in the bibliography,
\emph{you must re-run Bib\TeX\ every time you change any of your document's footnotes}.

\section{Math and Equations}
Inline math may be typeset using the \verb+$+ delimiters. Bold math
symbols may be achieved using the \verb+bm+ package and the
\verb+\bm{#1}+ command it supplies. For instance, a bold $\alpha$ can
be typeset as \verb+$\bm{\alpha}$+ giving $\bm{\alpha}$. Fraktur and
Blackboard (or open face or double struck) characters should be
typeset using the \verb+\mathfrak{#1}+ and \verb+\mathbb{#1}+ commands
respectively. Both are supplied by the \texttt{amssymb} package. For
example, \verb+$\mathbb{R}$+ gives $\mathbb{R}$ and
\verb+$\mathfrak{G}$+ gives $\mathfrak{G}$

In \LaTeX\ there are many different ways to display equations, and a
few preferred ways are noted below. Displayed math will center by
default. Use the class option \verb+fleqn+ to flush equations left.

Below we have numbered single-line equations; this is the most common
type of equation in \textit{Physical Review}:
\begin{eqnarray}
\chi_+(p)\alt{\bf [}2|{\bf p}|(|{\bf p}|+p_z){\bf ]}^{-1/2}
\left(
\begin{array}{c}
|{\bf p}|+p_z\\
px+ip_y
\end{array}\right)\;,
\\
\left\{%
 \openone234567890abc123\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}%
\label{eq:one}.
\end{eqnarray}
Note the open one in Eq.~(\ref{eq:one}).

Not all numbered equations will fit within a narrow column this
way. The equation number will move down automatically if it cannot fit
on the same line with a one-line equation:
\begin{equation}
\left\{
 ab12345678abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}%
\right\}.
\end{equation}

When the \verb+\label{#1}+ command is used [cf. input for
Eq.~(\ref{eq:one})], the equation can be referred to in text without
knowing the equation number that \TeX\ will assign to it. Just
use \verb+\ref{#1}+, where \verb+#1+ is the same name that used in
the \verb+\label{#1}+ command.

Unnumbered single-line equations can be typeset
using the \verb+\[+, \verb+\]+ format:
\[g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \]

\subsection{Multiline equations}

Multiline equations are obtained by using the \verb+eqnarray+
environment.  Use the \verb+\nonumber+ command at the end of each line
to avoid assigning a number:
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
\delta_{\sigma_1,-\sigma_2}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_jl_i\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1),
\end{eqnarray}
\begin{eqnarray}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\nonumber \\
 & &\times \left( \sum_{i<j}\right)
  \sum_{\text{perm}}
 \frac{1}{S_{12}}
 \frac{1}{S_{12}}
 \sum_\tau c^f_\tau~.
\end{eqnarray}
\textbf{Note:} Do not use \verb+\label{#1}+ on a line of a multiline
equation if \verb+\nonumber+ is also used on that line. Incorrect
cross-referencing will result. Notice the use \verb+\text{#1}+ for
using a Roman font within a math environment.

To set a multiline equation without \emph{any} equation
numbers, use the \verb+\begin{eqnarray*}+,
\verb+\end{eqnarray*}+ format:
\begin{eqnarray*}
\sum \vert M^{\text{viol}}_g \vert ^2&=&g^{2n-4}_S(Q^2)~N^{n-2}
        (N^2-1)\\
 & &\times \left( \sum_{i<j}\right)
 \left(
  \sum_{\text{perm}}\frac{1}{S_{12}S_{23}S_{n1}}
 \right)
 \frac{1}{S_{12}}~.
\end{eqnarray*}

To obtain numbers not normally produced by the automatic numbering,
use the \verb+\tag{#1}+ command, where \verb+#1+ is the desired
equation number. For example, to get an equation number of
(\ref{eq:mynum}),
\begin{equation}
g^+g^+ \rightarrow g^+g^+g^+g^+ \dots ~,~~q^+q^+\rightarrow
q^+g^+g^+ \dots ~. \tag{2.6$'$}\label{eq:mynum}
\end{equation}

\paragraph{A few notes on \texttt{tag}s}
\verb+\tag{#1}+ requires the \texttt{amsmath} package.
Place the \verb+\tag{#1}+ command before the \verb+\label{#1}+, if any.
The numbering produced by \verb+\tag{#1}+ \textit{does not affect}
the automatic numbering in REV\TeX;
therefore, the number must be known ahead of time,
and it must be manually adjusted if other equations are added.
\verb+\tag{#1}+ works with both single-line and multiline equations.
\verb+\tag{#1}+ should only be used in exceptional cases---%
do not use it to number many equations in your paper.
Please note that this feature of the \texttt{amsmath} package
is \emph{not} compatible with the \texttt{hyperref} (6.77u) package.

Enclosing display math within
\verb+\begin{subequations}+ and \verb+\end{subequations}+ will produce
a set of equations that are labeled with letters, as shown in
Eqs.~(\ref{subeq:1}) and (\ref{subeq:2}) below.
You may include any number of single-line and multiline equations,
although it is probably not a good idea to follow one display math
directly after another.
\begin{subequations}
\label{eq:whole}
\begin{eqnarray}
{\cal M}=&&ig_Z^2(4E_1E_2)^{1/2}(l_i^2)^{-1}
(g_{\sigma_2}^e)^2\chi_{-\sigma_2}(p_2)\nonumber\\
&&\times
[\epsilon_i]_{\sigma_1}\chi_{\sigma_1}(p_1).\label{subeq:2}
\end{eqnarray}
\begin{equation}
\left\{
 abc123456abcdef\alpha\beta\gamma\delta1234556\alpha\beta
 \frac{1\sum^{a}_{b}}{A^2}
\right\},\label{subeq:1}
\end{equation}
\end{subequations}
Giving a \verb+\label{#1}+ command directly after the \verb+\begin{subequations}+,
allows you to reference all the equations in the \texttt{subequations} environment.
For example, the equations in the preceding subequations environment were
Eqs.~(\ref{eq:whole}).

\subsubsection{Wide equations}
The equation that follows is set in a wide format, i.e., it spans the full page.
The wide format is reserved for long equations
that cannot easily be set in a single column:
\begin{widetext}
\begin{equation}
{\cal R}^{(\text{d})}=
 g_{\sigma_2}^e
 \left(
   \frac{[\Gamma^Z(3,21)]_{\sigma_1}}{Q_{12}^2-M_W^2}
  +\frac{[\Gamma^Z(13,2)]_{\sigma_1}}{Q_{13}^2-M_W^2}
 \right)
 + x_WQ_e
 \left(
   \frac{[\Gamma^\gamma(3,21)]_{\sigma_1}}{Q_{12}^2-M_W^2}
  +\frac{[\Gamma^\gamma(13,2)]_{\sigma_1}}{Q_{13}^2-M_W^2}
 \right)\;.
 \label{eq:wideeq}
\end{equation}
\end{widetext}
This is typed to show how the output appears in wide format.
(Incidentally, since there is no blank line between the \texttt{equation} environment above
and the start of this paragraph, this paragraph is not indented.)

\section{Cross-referencing}
REV\TeX{} will automatically number such things as
sections, footnotes, equations, figure captions, and table captions.
In order to reference them in text, use the
\verb+\label{#1}+ and \verb+\ref{#1}+ commands.
To reference a particular page, use the \verb+\pageref{#1}+ command.

The \verb+\label{#1}+ should appear
within the section heading,
within the footnote text,
within the equation, or
within the table or figure caption.
The \verb+\ref{#1}+ command
is used in text at the point where the reference is to be displayed.
Some examples: Section~\ref{sec:level1} on page~\pageref{sec:level1},
Table~\ref{tab:table1},%
\begin{table}[b]%The best place to locate the table environment is directly after its first reference in text
\caption{\label{tab:table1}%
A table that fits into a single column of a two-column layout.
Note that REV\TeX~4 adjusts the intercolumn spacing so that the table fills the
entire width of the column. Table captions are numbered
automatically.
This table illustrates left-, center-, decimal- and right-aligned columns,
along with the use of the \texttt{ruledtabular} environment which sets the
Scotch (double) rules above and below the alignment, per APS style.
}
\begin{ruledtabular}
\begin{tabular}{lcdr}
\textrm{Left\footnote{Note a.}}&
\textrm{Centered\footnote{Note b.}}&
\multicolumn{1}{c}{\textrm{Decimal}}&
\textrm{Right}\\
\colrule
1 & 2 & 3.001 & 4\\
10 & 20 & 30 & 40\\
100 & 200 & 300.0 & 400\\
\end{tabular}
\end{ruledtabular}
\end{table}
and Fig.~\ref{fig:epsart}.%
\begin{figure}[b]
\includegraphics{fig_1}% Here is how to import EPS art
\caption{\label{fig:epsart} A figure caption. The figure captions are
automatically numbered.}
\end{figure}

\section{Floats: Figures, Tables, Videos, etc.}
Figures and tables are usually allowed to ``float'', which means that their
placement is determined by \LaTeX, while the document is being typeset.

Use the \texttt{figure} environment for a figure, the \texttt{table} environment for a table.
In each case, use the \verb+\caption+ command within to give the text of the
figure or table caption along with the \verb+\label+ command to provide
a key for referring to this figure or table.
The typical content of a figure is an image of some kind;
that of a table is an alignment.%
\begin{figure*}
\includegraphics{fig_2}% Here is how to import EPS art
\caption{\label{fig:wide}Use the figure* environment to get a wide
figure that spans the page in \texttt{twocolumn} formatting.}
\end{figure*}
\begin{table*}
\caption{\label{tab:table3}This is a wide table that spans the full page
width in a two-column layout. It is formatted using the
\texttt{table*} environment. It also demonstates the use of
\textbackslash\texttt{multicolumn} in rows with entries that span
more than one column.}
\begin{ruledtabular}
\begin{tabular}{ccccc}
 &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
 Ion&1st alternative&2nd alternative&lst alternative
&2nd alternative\\ \hline
 K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
 Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
 &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
 Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnotemark[1]
 &$(4e)^{\text{a}}$\\
 He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
 Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
\end{tabular}
\end{ruledtabular}
\end{table*}

Insert an image using either the \texttt{graphics} or
\texttt{graphix} packages, which define the \verb+\includegraphics{#1}+ command.
(The two packages differ in respect of the optional arguments
used to specify the orientation, scaling, and translation of the image.)
To create an alignment, use the \texttt{tabular} environment.

The best place to locate the \texttt{figure} or \texttt{table} environment
is immediately following its first reference in text; this sample document
illustrates this practice for Fig.~\ref{fig:epsart}, which
shows a figure that is small enough to fit in a single column.

In exceptional cases, you will need to move the float earlier in the document, as was done
with Table~\ref{tab:table3}: \LaTeX's float placement algorithms need to know
about a full-page-width float earlier.

Fig.~\ref{fig:wide}
has content that is too wide for a single column,
so the \texttt{figure*} environment has been used.%
\begin{table}[b]
\caption{\label{tab:table4}%
Numbers in columns Three--Five are aligned with the ``d'' column specifier
(requires the \texttt{dcolumn} package).
Non-numeric entries (those entries without a ``.'') in a ``d'' column are aligned on the decimal point.
Use the ``D'' specifier for more complex layouts. }
\begin{ruledtabular}
\begin{tabular}{ccddd}
One&Two&
\multicolumn{1}{c}{\textrm{Three}}&
\multicolumn{1}{c}{\textrm{Four}}&
\multicolumn{1}{c}{\textrm{Five}}\\
%\mbox{Three}&\mbox{Four}&\mbox{Five}\\
\hline
one&two&\mbox{three}&\mbox{four}&\mbox{five}\\
He&2& 2.77234 & 45672. & 0.69 \\
C\footnote{Some tables require footnotes.}
  &C\footnote{Some tables need more than one footnote.}
  & 12537.64 & 37.66345 & 86.37 \\
\end{tabular}
\end{ruledtabular}
\end{table}

The content of a table is typically a \texttt{tabular} environment,
giving rows of type in aligned columns.
Column entries separated by \verb+&+'s, and
each row ends with \textbackslash\textbackslash.
The required argument for the \texttt{tabular} environment
specifies how data are aligned in the columns.
For instance, entries may be centered, left-justified, right-justified, aligned on a decimal
point.
Extra column-spacing may be be specified as well,
although REV\TeX~4 sets this spacing so that the columns fill the width of the
table. Horizontal rules are typeset using the \verb+\hline+
command. The doubled (or Scotch) rules that appear at the top and
bottom of a table can be achieved enclosing the \texttt{tabular}
environment within a \texttt{ruledtabular} environment. Rows whose
columns span multiple columns can be typeset using the
\verb+\multicolumn{#1}{#2}{#3}+ command (for example, see the first
row of Table~\ref{tab:table3}).%

Tables~\ref{tab:table1}, \ref{tab:table3}, \ref{tab:table4}, and \ref{tab:table2}%
\begin{table}[b]
\caption{\label{tab:table2}
A table with numerous columns that still fits into a single column.
Here, several entries share the same footnote.
Inspect the \LaTeX\ input for this table to see exactly how it is done.}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
 &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
\hline
Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
& 0.680 & 1.870 & 3.700 \\
Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
& 0.450 & 1.930 & 3.760 \\
Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
& 0.750 & 2.170 & 3.560 \\
Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
& 0.900 & 2.370 & 3.720 \\
Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
& 0.380 & 1.730 & 2.830 \\
Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
& 0.760 & 2.110 & 3.120 \\
Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
&  1.120 & 2.620 & 3.480 \\
Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
& 1.330 & 2.800 & 3.590 \\
Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
& 1.420 & 3.030 & 3.740 \\
In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
& 0.960 & 2.460 & 3.780 \\
Tl& 0.480 & 18.90 & 3.550 & & & & \\
\end{tabular}
\end{ruledtabular}
\footnotetext[1]{Here's the first, from Ref.~\onlinecite{feyn54}.}
\footnotetext[2]{Here's the second.}
\footnotetext[3]{Here's the third.}
\footnotetext[4]{Here's the fourth.}
\footnotetext[5]{And etc.}
\end{table}
show various effects.
A table that fits in a single column employs the \texttt{table}
environment.
Table~\ref{tab:table3} is a wide table, set with the \texttt{table*} environment.
Long tables may need to break across pages.
The most straightforward way to accomplish this is to specify
the \verb+[H]+ float placement on the \texttt{table} or
\texttt{table*} environment.
However, the \LaTeXe\ package \texttt{longtable} allows headers and footers to be specified for each page of the table.
A simple example of the use of \texttt{longtable} can be found
in the file \texttt{summary.tex} that is included with the REV\TeX~4
distribution.

There are two methods for setting footnotes within a table (these
footnotes will be displayed directly below the table rather than at
the bottom of the page or in the bibliography). The easiest
and preferred method is just to use the \verb+\footnote{#1}+
command. This will automatically enumerate the footnotes with
lowercase roman letters. However, it is sometimes necessary to have
multiple entries in the table share the same footnote. In this case,
there is no choice but to manually create the footnotes using
\verb+\footnotemark[#1]+ and \verb+\footnotetext[#1]{#2}+.
\texttt{\#1} is a numeric value. Each time the same value for
\texttt{\#1} is used, the same mark is produced in the table. The
\verb+\footnotetext[#1]{#2}+ commands are placed after the \texttt{tabular}
environment. Examine the \LaTeX\ source and output for
Tables~\ref{tab:table1} and \ref{tab:table2}
for examples.

Video~\ref{vid:PRSTPER.4.010101}
illustrates several features new with REV\TeX4.2,
starting with the \texttt{video} environment, which is in the same category with
\texttt{figure} and \texttt{table}.%
\begin{video}
\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1a.mpg}{\includegraphics{vid_1a}}%
 \quad
\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1b.mpg}{\includegraphics{vid_1b}}
 \setfloatlink{http://link.aps.org/multimedia/PRSTPER/v4/i1/e010101}%
 \caption{\label{vid:PRSTPER.4.010101}%
  Students explain their initial idea about Newton's third law to a teaching assistant.
  Clip (a): same force.
  Clip (b): move backwards.
 }%
\end{video}
The \verb+\setfloatlink+ command causes the title of the video to be a hyperlink to the
indicated URL; it may be used with any environment that takes the \verb+\caption+
command.
The \verb+\href+ command has the same significance as it does in the context of
the \texttt{hyperref} package: the second argument is a piece of text to be
typeset in your document; the first is its hyperlink, a URL.

\textit{Physical Review} style requires that the initial citation of
figures or tables be in numerical order in text, so don't cite
Fig.~\ref{fig:wide} until Fig.~\ref{fig:epsart} has been cited.

\begin{acknowledgments}
We wish to acknowledge the support of the author community in using
REV\TeX{}, offering suggestions and encouragement, testing new versions,
\dots.
\end{acknowledgments}

\appendix

\section{Appendixes}

To start the appendixes, use the \verb+\appendix+ command.
This signals that all following section commands refer to appendixes
instead of regular sections. Therefore, the \verb+\appendix+ command
should be used only once---to setup the section commands to act as
appendixes. Thereafter normal section commands are used. The heading
for a section can be left empty. For example,
\begin{verbatim}
\appendix
\section{}
\end{verbatim}
will produce an appendix heading that says ``APPENDIX A'' and
\begin{verbatim}
\appendix
\section{Background}
\end{verbatim}
will produce an appendix heading that says ``APPENDIX A: BACKGROUND''
(note that the colon is set automatically).

If there is only one appendix, then the letter ``A'' should not
appear. This is suppressed by using the star version of the appendix
command (\verb+\appendix*+ in the place of \verb+\appendix+).

\section{A little more on appendixes}

Observe that this appendix was started by using
\begin{verbatim}
\section{A little more on appendixes}
\end{verbatim}

Note the equation number in an appendix:
\begin{equation}
E=mc^2.
\end{equation}

\subsection{\label{app:subsec}A subsection in an appendix}

You can use a subsection or subsubsection in an appendix. Note the
numbering: we are now in Appendix~\ref{app:subsec}.

Note the equation numbers in this appendix, produced with the
subequations environment:
\begin{subequations}
\begin{eqnarray}
E&=&mc, \label{appa}
\\
E&=&mc^2, \label{appb}
\\
E&\agt& mc^3. \label{appc}
\end{eqnarray}
\end{subequations}
They turn out to be Eqs.~(\ref{appa}), (\ref{appb}), and (\ref{appc}).

% The \nocite command causes all entries in a bibliography to be printed out
% whether or not they are actually referenced in the text. This is appropriate
% for the sample file to show the different styles of references, but authors
% most likely will not want to use it.
\nocite{*}

\bibliography{apssamp}% Produces the bibliography via BibTeX.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2021-06-27 paper/aps_instructions.tex
Add paper sections

--- 2021-06-20 paper/v1.0/apssamp.tex
@@
 
-\author{Kosala Herath}
+\author{Kosala Herath,}
  % \altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
 \author{Malin Premaratne}%
- \email{Second.Author@institution.edu}
 \affiliation{%
- Authors' institution and/or address\\
- This line break forced with \textbackslash\textbackslash
+ Advanced Computing and Simulation Laboratory(A$\chi$L), Department of Electrical and Computer Systems Engineering,\\
+ Monash University, Clayton, Victoria 3800, Australia
 }%
 
-\collaboration{MUSO Collaboration}%\noaffiliation
-
-\author{Charlie Author}
- \homepage{http://www.Second.institution.edu/~Charlie.Author}
-\affiliation{
- Second institution and/or address\\
- This line break forced% with \\
-}%
-\affiliation{
- Third institution, the second for Charlie Author
-}%
-\author{Delta Author}
-\affiliation{%
- Authors' institution and/or address\\
- This line break forced with \textbackslash\textbackslash
-}%
-
-\collaboration{CLEO Collaboration}%\noaffiliation
+% \collaboration{MUSO Collaboration}%\noaffiliation
+%
+% \author{Charlie Author}
+%  \homepage{http://www.Second.institution.edu/~Charlie.Author}
+% \affiliation{
+%  Second institution and/or address\\
+%  This line break forced% with \\
+% }%
+% \affiliation{
+%  Third institution, the second for Charlie Author
+% }%
+% \author{Delta Author}
+% \affiliation{%
+%  Authors' institution and/or address\\
+%  This line break forced with \textbackslash\textbackslash
+% }%
+%
+% \collaboration{CLEO Collaboration}%\noaffiliation
 
@@
 \begin{abstract}
-An article usually includes an abstract, a concise summary of the work
+[**ABSTRACT] An article usually includes an abstract, a concise summary of the work
 covered at length in the main body of the article.
@@
 
-\section{\label{sec:level1}First-level heading:\protect\\ The line
-break was forced \lowercase{via} \textbackslash\textbackslash}
+\section{\label{sec:introduction} INTRODUCTION}
 
@@
 \begin{figure}[b]
-\includegraphics{fig_1}% Here is how to import EPS art
+\includegraphics{figures/fig_1}% Here is how to import EPS art
 \caption{\label{fig:epsart} A figure caption. The figure captions are
@@
 \begin{figure*}
-\includegraphics{fig_2}% Here is how to import EPS art
+\includegraphics{figures/fig_2}% Here is how to import EPS art
 \caption{\label{fig:wide}Use the figure* environment to get a wide
@@
 \begin{video}
-\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1a.mpg}{\includegraphics{vid_1a}}%
+\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1a.mpg}{\includegraphics{videos/vid_1a}}%
  \quad
-\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1b.mpg}{\includegraphics{vid_1b}}
+\href{http://prst-per.aps.org/multimedia/PRSTPER/v4/i1/e010101/e010101_vid1b.mpg}{\includegraphics{videos/vid_1b}}
  \setfloatlink{http://link.aps.org/multimedia/PRSTPER/v4/i1/e010101}%

### 2021-06-27 paper/v1.0/abstract.tex
Add paper sections

--- 2021-05-21 summary/Summary.tex
@@
-\documentclass[a4paper]{article}
-
-%% Language and font encodings
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage[T1]{fontenc}
-
-%% Sets page size and margins
-\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
-
-%% Useful packages
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{physics}
-\usepackage{amssymb}
-\usepackage{mathtools}
-
-\numberwithin{equation}{subsection}
-\newcommand{\mb}[1]{\mathbf{#1}}
-\title{Floquet-Drude Conductivity in Dressed Quantum Hall Systems}
-\author{Kosala Sananthana Herath}
-\numberwithin{equation}{section}
-
-\begin{document}
-
-\maketitle
-
-\section*{Abstract}
-
 Interactions between light and matter have dragged research attention in the fields of optoelectronics, sensing, energy harvesting, quantum computing, bio-information, and in many branches of recent technologies.
@@
 These researches of extreme electron-light engagements introduced an astonishing scope of twentieth-century physics namely quantum optic physics.
-
-On the other hand, in nanostructures that are applicable in electronic devices, the investigations with the help of quantum optic were centered on polaritonic and exciton influences on nanostructures and material characteristics of dressed electrons in two-dimensional(2D) materials and quantum wires.
-When considering the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
-
-Therefore, transport properties of nanostructures exposed to a high intensity periodic electromagnetic fields have been explored theoretically in this study.
-The dressing field is analyzed non perturbatively using the Floquet theory whilst the probing field is examined perturbatively by applying the linear response method using the Kubo formula.
-The general Floquet-Drude conductivity has been derived in a fully closed analytical form in most recent research [1,2], introducing a novel type of Green’s functions namely four-times Green’s functions.
-As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nanostructures by an intense dressing field.
-From an empirical sense, this study applies directly to various nanostructures illuminated by a high-intensity electromagnetic field.
-In this research we have developed a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field and that will enable efficient manipulation of transport characteristics in nanoscale electronic devices.
-
-\section*{Purpose of the Study}
-
-When a stationary magentic field applied perpendicularly across the surface of 2DEG systems, the orbital motion of electrons becomes completely quantized and the energy spectrium becomes discrete by creating Landau levels.
-Such a singular system known as a quantum Hall system and in this study we explictly calculate the diagonal ($\sigma_{xx},\sigma_{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems.
-
-Although there are already exist a number of adavanced theories devoted to the calculation of conductivity tensor elements in a quantum Hall systems [3-5], they have not been applied to the optically manipulation the magneto-electric properties of the quantum Hall systems.
-However K.
-Dini et al.
-[6] have recently investigated the one directional conductivity behaviour of dressed quantum Hall systems, they have not used the state of art model to describe the conductivity in a quantum Hall system.
-In their study they used the conductivity models from T.
-Ando et al.
-[3,4] and as mentioned in A.
-Endo et al.
-investigation [5] those models are far less accurate representation of the experimantally observed Landau levels because they present a semi-elliptical broadening.
-
-In this study we develop a genralized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [1,2].
-In addition, we demonstrate that our generalized model is agreed with the state of art conductivity model [5] for specalized quantum Hall system which has been considered without the external dressing field.
-
-\section*{Research Method}
-
-In this analysis we consider 2DEG which has been distrubuted in confined $(x,y)$ plane in configuration space.
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.9]{figures/fig0.pdf}
-  \caption{Confined 2DEG in configuration space with the size of $A=L_xL_y$.}
-  \label{fig:1}
-\end{figure}
-
-We examined the properties of 2DEG with stationary magnetic field which directed on $z$ axis and a linearly $y$-polarized strong electomagnetic wave (dressing field) with electric field which also propagate in $z$ direction.
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.9]{figures/fig1.pdf}
-  \caption{Stationary magnetic filed (blue color) and Strong EM wave (red color) applied to the 2DEG.}
-  \label{fig:2}
-\end{figure}
-
-In the state of art conductivity model [5] which only describes trasport properies quantum Hall system without external dressing field has used an approximation equivalent to asssumin that the broadening of a Landau level due to disorder is represented by a constant broadening.
-However, from the Floquet-Drude conductivity model we have foud that we can manipulate the impurity broadening using intense high-frequency electromagnetic waves and this study we have developed a mathematical formula to calculate this Landau energy level broadening and using those values we were able to evaluate diagonal elements of conductivity tensor in dressed quantum Hall systems.
-Ultimately we can express the normalized conductivity for a quantum Hall system with linearly polarized drerssing field analytically as follows
-\begin{equation*}
-    \sigma^{dd}(X_F,\tilde{I}) =
-    \sum_{n}
-    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}}
-    \qty[
-      \frac{1}
-      {
-        1 + \qty(\frac{X_F - n -1}{\gamma_{n+1}})^2
-      }
-    ]
-    \qty[
-      \frac{1}
-      {
-        1 + \qty(\frac{X_F - n}{\gamma_{n}})^2
-      }
-    ]
-\end{equation*}
-where $X_F$ is normalized Fermi level and $\gamma_n$ represnts normalized energy band broadening of $n$-th Landau level.
-This $\gamma_n$ only depends on the normalized intensity value of dressing field $\tilde{I}$.
-We can choose the direction $d$ of the diagonal conductivity tensor element from $(x,y)$.
-
-\section*{Outcomes and Discussion}
-
-First we have identified that we can control the Landau level broadening using the dressing field intensity as given in the Figure \ref{fig:3}.
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.6]{figures/fig3.pdf}
-  \caption{The dependence of the normalized Landau level broadening on the dressing field intensity for different Landau levels ($N=0,1,2,3,4$).}
-  \label{fig:3}
-\end{figure}
-
-As mentioned in above derived analytical expression the changes can be done to the transverse conductivity using external dressing field.
-As given in Figure \ref{fig:4} and \ref{fig:5} we can manipulate the conductivity using external dressing field.
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=1]{figures/fig4.pdf}
-  \caption{Normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
-  \label{fig:4}
-\end{figure}
-
-When the dressing field's intensity increase the broadening of energy bands of Landau levels get reduced and the conductivity also get decrease in all the regions except the peak points of each level.
-Using this manipulation we can filter the conductivity which is change with the Fermi level.
-Since Fermi level can be change with the applied gate voltage of the material this can be used as a 2D switch for optoelectonic applications.
-However with the existance of  external dressing field we can fine tune the switching mechanism and it is an exceptional advantage in optoelectonic applications.
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.9]{figures/fig5.pdf}
-  \caption{$3$rd Landau level's normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
-  \label{fig:5}
-\end{figure}
-
-Now we can compare our result with previous studies to the check the validity of the outcomes.
-In the research done by K.
-Dini et al.
-[6] has demonstrated that the diagonal elements of conductivity tensor in a quantum Hall system can manipute with apllying high intense light as given in Figure \ref{fig:6}.
-However the behaviour of the conductivity with the Fermi level is not accurate as given in the state of art study [5] which has been represent in Figure \ref{fig:7}.
-When we consider the our outcome which derived using novel Floquet-Drude conductivity model, we can see that it agree with the results given in the much accurate study [5].
-However, our study present a more generalized mathematical model rather than the specific scenario studied in the study [6].
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.3]{figures/fig6.pdf}
-  \caption{The dependence of the longitudinal conductivity $\sigma_{xx}$ , on
-the Fermi energy $\varepsilon_F$. The solid line describes the conductivity
-of unirradiated 2DEG, whereas the dotted line corresponds to the
-conductivity at the irradiation intensity $I = 600 \; \text{W/cm2}$. The inset
-shows the difference between these two conductivities. (from K.Dini at el. [6])}
-  \label{fig:6}
-\end{figure}
-
-\newpage
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.3]{figures/fig7.pdf}
-  \caption{The diagonal and the off-diagonal components
-of the conductivity tensor modified to account for the long-range potential. The
-horizontal axis is the inverse magnetic field. (from A. Endo at el. [5])}
-  \label{fig:7}
-\end{figure}
-
-We can conclude that the using external dressing field we can manipulate the magneto-electric properties of a quantum Hall system and in this study we were able to demonstrate that using Floquet-Drude conductivity method we can derive a more accurate generalized mathematical model that describe the trasport properties of quantum Hall syatems.
-Therefore this theory describes that the  dressing field can be used as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectonic devices.
-
-\section*{Reference}
-
-[1] M. Wackerl, P. Wenk, and J. Schliemann, Floquet-Drude Conductivity, Phys. Rev. B 101, 184204 (2020).
-
-\noindent
-[2] M. Wackerl, Transport in Periodically Driven Systems, University of Regensburg, (2020).
-
-\noindent
-[3] T.
-Ando and Y.
-Uemura, Theory of Quantum Transport in a Two-Dimensional Electron System under Magnetic Fields.
-I.
-Characteristics of Level Broadening and Transport under Strong Fields, J.
-Phys.
-Soc.
-Jpn.
-36, 959 (1974).
-
-\noindent
-[4] T. Ando, A. B. Fowler, and F. Stern, Electronic Properties of Two-Dimensional Systems, Rev. Mod. Phys. 54, 437 (1982).
-
-\noindent
-[5] A. Endo, N. Hatano, H. Nakamura, and R. Shirasaki, Fundamental Relation between Longitudinal and Transverse Conductivities in the Quantum Hall System, J. Phys.: Condens. Matter 21, 345803 (2009).
-
-\noindent
-[6] K. Dini, O. V. Kibis, and I. A. Shelykh, Magnetic Properties of a Two-Dimensional Electron Gas Strongly Coupled to Light, Phys. Rev. B 93, 235411 (2016).
-
-\end{document}

### 2021-06-27 paper/v1.0/sections/1_introduction.tex
Add paper sections

--- 2021-05-21 summary/Summary.tex
@@
 In this research we have developed a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field and that will enable efficient manipulation of transport characteristics in nanoscale electronic devices.
-
-\section*{Purpose of the Study}
 
@@
 In addition, we demonstrate that our generalized model is agreed with the state of art conductivity model [5] for specalized quantum Hall system which has been considered without the external dressing field.
-
-\section*{Research Method}
-
-In this analysis we consider 2DEG which has been distrubuted in confined $(x,y)$ plane in configuration space.
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.9]{figures/fig0.pdf}
-  \caption{Confined 2DEG in configuration space with the size of $A=L_xL_y$.}
-  \label{fig:1}
-\end{figure}
-
-We examined the properties of 2DEG with stationary magnetic field which directed on $z$ axis and a linearly $y$-polarized strong electomagnetic wave (dressing field) with electric field which also propagate in $z$ direction.
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.9]{figures/fig1.pdf}
-  \caption{Stationary magnetic filed (blue color) and Strong EM wave (red color) applied to the 2DEG.}
-  \label{fig:2}
-\end{figure}
-
-In the state of art conductivity model [5] which only describes trasport properies quantum Hall system without external dressing field has used an approximation equivalent to asssumin that the broadening of a Landau level due to disorder is represented by a constant broadening.
-However, from the Floquet-Drude conductivity model we have foud that we can manipulate the impurity broadening using intense high-frequency electromagnetic waves and this study we have developed a mathematical formula to calculate this Landau energy level broadening and using those values we were able to evaluate diagonal elements of conductivity tensor in dressed quantum Hall systems.
-Ultimately we can express the normalized conductivity for a quantum Hall system with linearly polarized drerssing field analytically as follows
-\begin{equation*}
-    \sigma^{dd}(X_F,\tilde{I}) =
-    \sum_{n}
-    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}}
-    \qty[
-      \frac{1}
-      {
-        1 + \qty(\frac{X_F - n -1}{\gamma_{n+1}})^2
-      }
-    ]
-    \qty[
-      \frac{1}
-      {
-        1 + \qty(\frac{X_F - n}{\gamma_{n}})^2
-      }
-    ]
-\end{equation*}
-where $X_F$ is normalized Fermi level and $\gamma_n$ represnts normalized energy band broadening of $n$-th Landau level.
-This $\gamma_n$ only depends on the normalized intensity value of dressing field $\tilde{I}$.
-We can choose the direction $d$ of the diagonal conductivity tensor element from $(x,y)$.
-
-\section*{Outcomes and Discussion}
-
-First we have identified that we can control the Landau level broadening using the dressing field intensity as given in the Figure \ref{fig:3}.
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.6]{figures/fig3.pdf}
-  \caption{The dependence of the normalized Landau level broadening on the dressing field intensity for different Landau levels ($N=0,1,2,3,4$).}
-  \label{fig:3}
-\end{figure}
-
-As mentioned in above derived analytical expression the changes can be done to the transverse conductivity using external dressing field.
-As given in Figure \ref{fig:4} and \ref{fig:5} we can manipulate the conductivity using external dressing field.
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=1]{figures/fig4.pdf}
-  \caption{Normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
-  \label{fig:4}
-\end{figure}
-
-When the dressing field's intensity increase the broadening of energy bands of Landau levels get reduced and the conductivity also get decrease in all the regions except the peak points of each level.
-Using this manipulation we can filter the conductivity which is change with the Fermi level.
-Since Fermi level can be change with the applied gate voltage of the material this can be used as a 2D switch for optoelectonic applications.
-However with the existance of  external dressing field we can fine tune the switching mechanism and it is an exceptional advantage in optoelectonic applications.
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.9]{figures/fig5.pdf}
-  \caption{$3$rd Landau level's normalized transverse conductivity against Fermi level ($X_F$) with different intensities ($\tilde{I}$) of dressing field.}
-  \label{fig:5}
-\end{figure}
-
-Now we can compare our result with previous studies to the check the validity of the outcomes.
-In the research done by K.
-Dini et al.
-[6] has demonstrated that the diagonal elements of conductivity tensor in a quantum Hall system can manipute with apllying high intense light as given in Figure \ref{fig:6}.
-However the behaviour of the conductivity with the Fermi level is not accurate as given in the state of art study [5] which has been represent in Figure \ref{fig:7}.
-When we consider the our outcome which derived using novel Floquet-Drude conductivity model, we can see that it agree with the results given in the much accurate study [5].
-However, our study present a more generalized mathematical model rather than the specific scenario studied in the study [6].
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.3]{figures/fig6.pdf}
-  \caption{The dependence of the longitudinal conductivity $\sigma_{xx}$ , on
-the Fermi energy $\varepsilon_F$. The solid line describes the conductivity
-of unirradiated 2DEG, whereas the dotted line corresponds to the
-conductivity at the irradiation intensity $I = 600 \; \text{W/cm2}$. The inset
-shows the difference between these two conductivities. (from K.Dini at el. [6])}
-  \label{fig:6}
-\end{figure}
-
-\newpage
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.3]{figures/fig7.pdf}
-  \caption{The diagonal and the off-diagonal components
-of the conductivity tensor modified to account for the long-range potential. The
-horizontal axis is the inverse magnetic field. (from A. Endo at el. [5])}
-  \label{fig:7}
-\end{figure}
-
-We can conclude that the using external dressing field we can manipulate the magneto-electric properties of a quantum Hall system and in this study we were able to demonstrate that using Floquet-Drude conductivity method we can derive a more accurate generalized mathematical model that describe the trasport properties of quantum Hall syatems.
 Therefore this theory describes that the dressing field can be used as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectonic devices.
-
-\section*{Reference}
-
-[1] M. Wackerl, P. Wenk, and J. Schliemann, Floquet-Drude Conductivity, Phys. Rev. B 101, 184204 (2020).
-
-\noindent
-[2] M. Wackerl, Transport in Periodically Driven Systems, University of Regensburg, (2020).
-
-\noindent
-[3] T.
-Ando and Y.
-Uemura, Theory of Quantum Transport in a Two-Dimensional Electron System under Magnetic Fields.
-I.
-Characteristics of Level Broadening and Transport under Strong Fields, J.
-Phys.
-Soc.
-Jpn.
-36, 959 (1974).
-
-\noindent
-[4] T. Ando, A. B. Fowler, and F. Stern, Electronic Properties of Two-Dimensional Systems, Rev. Mod. Phys. 54, 437 (1982).
-
-\noindent
-[5] A. Endo, N. Hatano, H. Nakamura, and R. Shirasaki, Fundamental Relation between Longitudinal and Transverse Conductivities in the Quantum Hall System, J. Phys.: Condens. Matter 21, 345803 (2009).
-
-\noindent
-[6] K. Dini, O. V. Kibis, and I. A. Shelykh, Magnetic Properties of a Two-Dimensional Electron Gas Strongly Coupled to Light, Phys. Rev. B 93, 235411 (2016).
-
-\end{document}

### 2021-06-27 paper/v1.0/sections/2_schrodinger_problem.tex
Add paper sections

% Section 02 - Schrodinger problem for landau levels in dressed 2DEG

Our system consist of a two-dimentional free electronic gas (2DEG) confined in the $(x,y)$ plane in the three-dimentional coordinate space.

### 2021-06-28 paper/v1.0/sections/2_schrodinger_problem.tex
Add section 1 of paper

@@
 
-Our system consist of a two-dimentional free electronic gas (2DEG) confined in the $(x,y)$ plane in the three-dimentional coordinate space.
+Our system consist of a two-dimentional free electron gas (2DEG) confined in the $(x,y)$ plane of the three-dimentional coordinate space.
+In our analysis, the 2DEG is subjected to a stationary magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis.
+In addition a linearly polorized strong light is applied perpendicular to the 2DEG plane and we specially tune the frequency of the field $\omega$ such that the optical field behaves as a purely dressing field (nonabsorbable).
+Without limiting the generality we can choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the dressing field configuration (Fig.~\ref{fig_1}).
+\begin{figure}[b]
+\includegraphics{figures/fig_1}
+\caption{\label{fig_1} Two dimentional eletron gas (2DEG) confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and strong dressing field with y-polorized electric field $\vb{E}$ are being applied perpendicular to the surface of 2DEG.}
+\end{figure}
+Here $B$ and $E$ represent the amplitude of the stationary magnetic field and oscillating electric field respectively.
+
+Using Landau gauge for the stationary magnetic field, we can represent it using vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
+These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan81,bruus04} and this leads to the time-dependent Hamiltonian
+\begin{equation} \label{eq_1}
+  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big(\vb{A}_{s}+\vb{A}_{d}(t)\big)\Big]^2,
+\end{equation}
+where $m_e$ is the effective electron mass and $e$ is the magnitude of the electron charge.
+$\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentums $p_{x,y}$.
+The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ was already given by Refs.
+\cite{husmi53,ditt98,dini16} and we can present them as a set of wave functions defined by two quantum numbers $(n,m)$
+\begin{equation} \label{eq_2}
+  \begin{aligned}
+    \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
+    \chi_n\left[y - y_0 - \zeta(t)\right]
+    \text{exp}\bigg(
+    \frac{i}{\hbar}\bigg[- \varepsilon_nt \\
+    &
+    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)+
+    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\
+    & +
+    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
+  \end{aligned}
+\end{equation}
+where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix A.
+Here $L_{x,y}$ are dimention of the 2DEG surface, $\hbar$ is the reduced Planck constant, and $y_0 = -p_x/eB$ is the center of the cyclotron orbit along $y$ axis.
+$\chi_n$ are well known solutions(Gauss-Hermite functions) for Schrödinger equation of a stationary quantum harmonic oscillartor
+\begin{equation} \label{eq_3}
+  \chi_n(x) \equiv
+   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
+  e^{-\kappa^2 x^2/2}
+  \mathcal{H}_n \qty(\kappa x) \quad \text{with}
+  \quad
+  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
+\end{equation}
+with eigenvalues given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 = eB/m_e$ is the cyclotron frequency.
+Each $n$ value defines the  energy($\varepsilon_n$) of the respective Landau level.
+The path shift of the driven classical oscillator $\zeta(t)$ is given by
+\begin{equation} \label{eq_4}
+  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
+\end{equation}
+while the Lagrangian of the classical oscialltor $L(\zeta,\dot{\zeta},t)$ can be idenfied as
+\begin{equation} \label{eq_5}
+  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
+\end{equation}
+
+x

### 2021-06-28 theory/figures/fig1.tex
Add section 1 of paper

@@
 
-%Straight Lines [id:da9655093306166109]
-\draw    (151.25,213.56) -- (420.92,213.12) ;
-%Straight Lines [id:da6780197443194285]
-\draw    (178.99,167.4) -- (393.4,167.4) ;
-%Straight Lines [id:da9790479690343763]
-\draw    (179.39,167) -- (151.25,213.56) ;
-%Straight Lines [id:da9225563682209392]
-\draw    (393.8,167) -- (420.92,213.12) ;
-%Straight Lines [id:da09563387136808865]
-\draw    (286.6,167) -- (286.08,213.34) ;
-%Straight Lines [id:da3116522709021452]
-\draw    (273.92,166.96) -- (270.68,213.56) ;
-%Straight Lines [id:da7104288201908657]
-\draw    (259.41,166.96) -- (253.18,213.3) ;
-%Straight Lines [id:da742779405875688]
-\draw    (245.3,166.91) -- (237.52,213.3) ;
-%Straight Lines [id:da18844905298889292]
-\draw    (232.1,167.18) -- (220.33,213.82) ;
-%Straight Lines [id:da35804353174173054]
-\draw    (217.96,167.2) -- (201.3,213.56) ;
-%Straight Lines [id:da7688901048445682]
-\draw    (205.7,167.18) -- (185.02,213.82) ;
-%Straight Lines [id:da3470294213255083]
-\draw    (192.98,167.2) -- (169.98,213.82) ;
-%Straight Lines [id:da35862455135349536]
-\draw    (298.62,166.91) -- (302.61,213.56) ;
-%Straight Lines [id:da29999796293225955]
-\draw    (313.18,167.08) -- (321.21,213.92) ;
-%Straight Lines [id:da6206528590435849]
-\draw    (327.48,166.91) -- (339.76,213.3) ;
-%Straight Lines [id:da9408253594123648]
-\draw    (340.68,167.18) -- (357.57,213.82) ;
-%Straight Lines [id:da917785587155304]
-\draw    (354.8,167.18) -- (374.76,213.56) ;
-%Straight Lines [id:da3801603892210079]
-\draw    (366.16,167.08) -- (392.26,213.56) ;
-%Straight Lines [id:da580723776969265]
-\draw    (380.59,167.18) -- (405.77,213.3) ;
-%Straight Lines [id:da5336171972507551]
-\draw    (155.55,205.39) -- (416.51,204.6) ;
-%Straight Lines [id:da956646312420568]
-\draw    (160.77,197.48) -- (411.6,196.96) ;
-%Straight Lines [id:da2531401201560137]
-\draw    (165.32,190.28) -- (407.36,190.06) ;
-%Straight Lines [id:da31575285130833475]
-\draw    (169.06,183.52) -- (403.31,183.25) ;
-%Straight Lines [id:da6000067635957629]
-\draw    (172.65,177.85) -- (399.54,177.33) ;
-%Straight Lines [id:da36539132370134153]
-\draw    (175.41,172.58) -- (396.16,171.79) ;
-%Shape: Ellipse [id:dp12271593300544881]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (172.44,205.39) ..
-controls (172.44,204.59) and (173.19,203.94) ..
-(174.12,203.94) ..
-controls (175.06,203.94) and (175.81,204.59) ..
-(175.81,205.39) ..
-controls (175.81,206.19) and (175.06,206.84) ..
-(174.12,206.84) ..
-controls (173.19,206.84) and (172.44,206.19) ..
-(172.44,205.39) -- cycle ;
-%Shape: Ellipse [id:dp17187409527803665]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (176.2,197.36) ..
-controls (176.2,196.56) and (176.96,195.91) ..
-(177.89,195.91) ..
-controls (178.82,195.91) and (179.58,196.56) ..
-(179.58,197.36) ..
-controls (179.58,198.16) and (178.82,198.81) ..
-(177.89,198.81) ..
-controls (176.96,198.81) and (176.2,198.16) ..
-(176.2,197.36) -- cycle ;
-%Shape: Ellipse [id:dp3897463489917039]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (179.83,189.94) ..
-controls (179.83,189.14) and (180.59,188.49) ..
-(181.52,188.49) ..
-controls (182.45,188.49) and (183.21,189.14) ..
-(183.21,189.94) ..
-controls (183.21,190.74) and (182.45,191.39) ..
-(181.52,191.39) ..
-controls (180.59,191.39) and (179.83,190.74) ..
-(179.83,189.94) -- cycle ;
-%Shape: Ellipse [id:dp6651227824721306]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (182.9,183.59) ..
-controls (182.9,182.79) and (183.66,182.14) ..
-(184.59,182.14) ..
-controls (185.52,182.14) and (186.28,182.79) ..
-(186.28,183.59) ..
-controls (186.28,184.39) and (185.52,185.04) ..
-(184.59,185.04) ..
-controls (183.66,185.04) and (182.9,184.39) ..
-(182.9,183.59) -- cycle ;
-%Shape: Ellipse [id:dp16931876417539748]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (186.11,177.24) ..
-controls (186.11,176.44) and (186.87,175.79) ..
-(187.8,175.79) ..
-controls (188.73,175.79) and (189.49,176.44) ..
-(189.49,177.24) ..
-controls (189.49,178.04) and (188.73,178.69) ..
-(187.8,178.69) ..
-controls (186.87,178.69) and (186.11,178.04) ..
-(186.11,177.24) -- cycle ;
-%Shape: Ellipse [id:dp011630715757735333]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (189.04,171.85) ..
-controls (189.04,171.05) and (189.8,170.4) ..
-(190.73,170.4) ..
-controls (191.66,170.4) and (192.42,171.05) ..
-(192.42,171.85) ..
-controls (192.42,172.65) and (191.66,173.3) ..
-(190.73,173.3) ..
-controls (189.8,173.3) and (189.04,172.65) ..
-(189.04,171.85) -- cycle ;
-%Shape: Ellipse [id:dp6352732828874232]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (186.95,205.15) ..
-controls (186.95,204.35) and (187.71,203.7) ..
-(188.64,203.7) ..
-controls (189.57,203.7) and (190.33,204.35) ..
-(190.33,205.15) ..
-controls (190.33,205.95) and (189.57,206.6) ..
-(188.64,206.6) ..
-controls (187.71,206.6) and (186.95,205.95) ..
-(186.95,205.15) -- cycle ;
-%Shape: Ellipse [id:dp5586918813010036]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (190.44,197.48) ..
-controls (190.44,196.68) and (191.19,196.03) ..
-(192.13,196.03) ..
-controls (193.06,196.03) and (193.82,196.68) ..
-(193.82,197.48) ..
-controls (193.82,198.28) and (193.06,198.93) ..
-(192.13,198.93) ..
-controls (191.19,198.93) and (190.44,198.28) ..
-(190.44,197.48) -- cycle ;
-%Shape: Ellipse [id:dp9378136236695127]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (193.67,190.5) ..
-controls (193.67,189.7) and (194.43,189.05) ..
-(195.36,189.05) ..
-controls (196.29,189.05) and (197.05,189.7) ..
-(197.05,190.5) ..
-controls (197.05,191.3) and (196.29,191.95) ..
-(195.36,191.95) ..
-controls (194.43,191.95) and (193.67,191.3) ..
-(193.67,190.5) -- cycle ;
-%Shape: Ellipse [id:dp7452150293769777]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (196.58,183.47) ..
-controls (196.58,182.67) and (197.33,182.02) ..
-(198.27,182.02) ..
-controls (199.2,182.02) and (199.96,182.67) ..
-(199.96,183.47) ..
-controls (199.96,184.27) and (199.2,184.92) ..
-(198.27,184.92) ..
-controls (197.33,184.92) and (196.58,184.27) ..
-(196.58,183.47) -- cycle ;
-%Shape: Ellipse [id:dp2595074236120878]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (199.51,177.48) ..
-controls (199.51,176.68) and (200.27,176.03) ..
-(201.2,176.03) ..
-controls (202.13,176.03) and (202.89,176.68) ..
-(202.89,177.48) ..
-controls (202.89,178.28) and (202.13,178.93) ..
-(201.2,178.93) ..
-controls (200.27,178.93) and (199.51,178.28) ..
-(199.51,177.48) -- cycle ;
-%Shape: Ellipse [id:dp8182709430461124]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (201.6,171.85) ..
-controls (201.6,171.05) and (202.36,170.4) ..
-(203.29,170.4) ..
-controls (204.22,170.4) and (204.98,171.05) ..
-(204.98,171.85) ..
-controls (204.98,172.65) and (204.22,173.3) ..
-(203.29,173.3) ..
-controls (202.36,173.3) and (201.6,172.65) ..
-(201.6,171.85) -- cycle ;
-%Shape: Ellipse [id:dp8721800205864367]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (202.72,205.27) ..
-controls (202.72,204.47) and (203.47,203.82) ..
-(204.41,203.82) ..
-controls (205.34,203.82) and (206.1,204.47) ..
-(206.1,205.27) ..
-controls (206.1,206.07) and (205.34,206.72) ..
-(204.41,206.72) ..
-controls (203.47,206.72) and (202.72,206.07) ..
-(202.72,205.27) -- cycle ;
-%Shape: Ellipse [id:dp7821722952675314]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (205.51,197.36) ..
-controls (205.51,196.56) and (206.27,195.91) ..
-(207.2,195.91) ..
-controls (208.13,195.91) and (208.89,196.56) ..
-(208.89,197.36) ..
-controls (208.89,198.16) and (208.13,198.81) ..
-(207.2,198.81) ..
-controls (206.27,198.81) and (205.51,198.16) ..
-(205.51,197.36) -- cycle ;
-%Shape: Ellipse [id:dp6361699950198552]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (207.95,190.5) ..
-controls (207.95,189.7) and (208.7,189.05) ..
-(209.64,189.05) ..
-controls (210.57,189.05) and (211.32,189.7) ..
-(211.32,190.5) ..
-controls (211.32,191.3) and (210.57,191.95) ..
-(209.64,191.95) ..
-controls (208.7,191.95) and (207.95,191.3) ..
-(207.95,190.5) -- cycle ;
-%Shape: Ellipse [id:dp07429235889252994]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (210.53,183.35) ..
-controls (210.53,182.55) and (211.29,181.9) ..
-(212.22,181.9) ..
-controls (213.15,181.9) and (213.91,182.55) ..
-(213.91,183.35) ..
-controls (213.91,184.15) and (213.15,184.8) ..
-(212.22,184.8) ..
-controls (211.29,184.8) and (210.53,184.15) ..
-(210.53,183.35) -- cycle ;
-%Shape: Ellipse [id:dp46939239369131425]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (212.63,177.12) ..
-controls (212.63,176.32) and (213.38,175.67) ..
-(214.32,175.67) ..
-controls (215.25,175.67) and (216,176.32) ..
-(216,177.12) ..
-controls (216,177.92) and (215.25,178.57) ..
-(214.32,178.57) ..
-controls (213.38,178.57) and (212.63,177.92) ..
-(212.63,177.12) -- cycle ;
-%Shape: Ellipse [id:dp47839368197126064]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (214.58,171.73) ..
-controls (214.58,170.93) and (215.34,170.28) ..
-(216.27,170.28) ..
-controls (217.2,170.28) and (217.96,170.93) ..
-(217.96,171.73) ..
-controls (217.96,172.53) and (217.2,173.18) ..
-(216.27,173.18) ..
-controls (215.34,173.18) and (214.58,172.53) ..
-(214.58,171.73) -- cycle ;
-%Shape: Ellipse [id:dp6735819197452304]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (220.72,205.39) ..
-controls (220.72,204.59) and (221.48,203.94) ..
-(222.41,203.94) ..
-controls (223.34,203.94) and (224.1,204.59) ..
-(224.1,205.39) ..
-controls (224.1,206.19) and (223.34,206.84) ..
-(222.41,206.84) ..
-controls (221.48,206.84) and (220.72,206.19) ..
-(220.72,205.39) -- cycle ;
-%Shape: Ellipse [id:dp40045376893902485]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (222.81,197.48) ..
-controls (222.81,196.68) and (223.57,196.03) ..
-(224.5,196.03) ..
-controls (225.44,196.03) and (226.19,196.68) ..
-(226.19,197.48) ..
-controls (226.19,198.28) and (225.44,198.93) ..
-(224.5,198.93) ..
-controls (223.57,198.93) and (222.81,198.28) ..
-(222.81,197.48) -- cycle ;
-%Shape: Ellipse [id:dp002588008650496576]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (224.53,190.5) ..
-controls (224.53,189.7) and (225.28,189.05) ..
-(226.21,189.05) ..
-controls (227.15,189.05) and (227.9,189.7) ..
-(227.9,190.5) ..
-controls (227.9,191.3) and (227.15,191.95) ..
-(226.21,191.95) ..
-controls (225.28,191.95) and (224.53,191.3) ..
-(224.53,190.5) -- cycle ;
-%Shape: Ellipse [id:dp7269110513068167]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (226.16,183.59) ..
-controls (226.16,182.79) and (226.92,182.14) ..
-(227.85,182.14) ..
-controls (228.78,182.14) and (229.54,182.79) ..
-(229.54,183.59) ..
-controls (229.54,184.39) and (228.78,185.04) ..
-(227.85,185.04) ..
-controls (226.92,185.04) and (226.16,184.39) ..
-(226.16,183.59) -- cycle ;
-%Shape: Ellipse [id:dp6228752312232548]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (227.7,177.36) ..
-controls (227.7,176.56) and (228.45,175.91) ..
-(229.39,175.91) ..
-controls (230.32,175.91) and (231.08,176.56) ..
-(231.08,177.36) ..
-controls (231.08,178.16) and (230.32,178.81) ..
-(229.39,178.81) ..
-controls (228.45,178.81) and (227.7,178.16) ..
-(227.7,177.36) -- cycle ;
-%Shape: Ellipse [id:dp5712591071424813]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (229.09,171.97) ..
-controls (229.09,171.17) and (229.85,170.52) ..
-(230.78,170.52) ..
-controls (231.72,170.52) and (232.47,171.17) ..
-(232.47,171.97) ..
-controls (232.47,172.77) and (231.72,173.42) ..
-(230.78,173.42) ..
-controls (229.85,173.42) and (229.09,172.77) ..
-(229.09,171.97) -- cycle ;
-%Shape: Ellipse [id:dp37415663269795374]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (242.77,171.85) ..
-controls (242.77,171.05) and (243.53,170.4) ..
-(244.46,170.4) ..
-controls (245.39,170.4) and (246.15,171.05) ..
-(246.15,171.85) ..
-controls (246.15,172.65) and (245.39,173.3) ..
-(244.46,173.3) ..
-controls (243.53,173.3) and (242.77,172.65) ..
-(242.77,171.85) -- cycle ;
-%Shape: Ellipse [id:dp5844680482576305]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (241.79,177.48) ..
-controls (241.79,176.68) and (242.55,176.03) ..
-(243.48,176.03) ..
-controls (244.41,176.03) and (245.17,176.68) ..
-(245.17,177.48) ..
-controls (245.17,178.28) and (244.41,178.93) ..
-(243.48,178.93) ..
-controls (242.55,178.93) and (241.79,178.28) ..
-(241.79,177.48) -- cycle ;
-%Shape: Ellipse [id:dp27800840767464763]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (240.68,183.23) ..
-controls (240.68,182.43) and (241.43,181.78) ..
-(242.37,181.78) ..
-controls (243.3,181.78) and (244.05,182.43) ..
-(244.05,183.23) ..
-controls (244.05,184.03) and (243.3,184.68) ..
-(242.37,184.68) ..
-controls (241.43,184.68) and (240.68,184.03) ..
-(240.68,183.23) -- cycle ;
-%Shape: Ellipse [id:dp6309981882755835]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (239.72,190.1) ..
-controls (239.72,189.3) and (240.48,188.65) ..
-(241.41,188.65) ..
-controls (242.34,188.65) and (243.1,189.3) ..
-(243.1,190.1) ..
-controls (243.1,190.9) and (242.34,191.55) ..
-(241.41,191.55) ..
-controls (240.48,191.55) and (239.72,190.9) ..
-(239.72,190.1) -- cycle ;
-%Shape: Ellipse [id:dp6064458479575909]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (238.44,197.36) ..
-controls (238.44,196.56) and (239.2,195.91) ..
-(240.13,195.91) ..
-controls (241.07,195.91) and (241.82,196.56) ..
-(241.82,197.36) ..
-controls (241.82,198.16) and (241.07,198.81) ..
-(240.13,198.81) ..
-controls (239.2,198.81) and (238.44,198.16) ..
-(238.44,197.36) -- cycle ;
-%Shape: Ellipse [id:dp8566892005164177]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (237.19,205.03) ..
-controls (237.19,204.23) and (237.94,203.58) ..
-(238.88,203.58) ..
-controls (239.81,203.58) and (240.57,204.23) ..
-(240.57,205.03) ..
-controls (240.57,205.83) and (239.81,206.48) ..
-(238.88,206.48) ..
-controls (237.94,206.48) and (237.19,205.83) ..
-(237.19,205.03) -- cycle ;
-%Shape: Ellipse [id:dp21811991550458654]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (257.01,171.85) ..
-controls (257.01,171.05) and (257.76,170.4) ..
-(258.69,170.4) ..
-controls (259.63,170.4) and (260.38,171.05) ..
-(260.38,171.85) ..
-controls (260.38,172.65) and (259.63,173.3) ..
-(258.69,173.3) ..
-controls (257.76,173.3) and (257.01,172.65) ..
-(257.01,171.85) -- cycle ;
-%Shape: Ellipse [id:dp07465207554443909]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (256.17,177.36) ..
-controls (256.17,176.56) and (256.92,175.91) ..
-(257.86,175.91) ..
-controls (258.79,175.91) and (259.54,176.56) ..
-(259.54,177.36) ..
-controls (259.54,178.16) and (258.79,178.81) ..
-(257.86,178.81) ..
-controls (256.92,178.81) and (256.17,178.16) ..
-(256.17,177.36) -- cycle ;
-%Shape: Ellipse [id:dp3520799274177444]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (255.33,183.47) ..
-controls (255.33,182.67) and (256.09,182.02) ..
-(257.02,182.02) ..
-controls (257.95,182.02) and (258.71,182.67) ..
-(258.71,183.47) ..
-controls (258.71,184.27) and (257.95,184.92) ..
-(257.02,184.92) ..
-controls (256.09,184.92) and (255.33,184.27) ..
-(255.33,183.47) -- cycle ;
-%Shape: Ellipse [id:dp8618279200116534]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (254.56,190.37) ..
-controls (254.56,189.57) and (255.32,188.92) ..
-(256.25,188.92) ..
-controls (257.18,188.92) and (257.94,189.57) ..
-(257.94,190.37) ..
-controls (257.94,191.17) and (257.18,191.82) ..
-(256.25,191.82) ..
-controls (255.32,191.82) and (254.56,191.17) ..
-(254.56,190.37) -- cycle ;
-%Shape: Ellipse [id:dp4846168731141014]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (253.52,197.24) ..
-controls (253.52,196.44) and (254.27,195.79) ..
-(255.2,195.79) ..
-controls (256.14,195.79) and (256.89,196.44) ..
-(256.89,197.24) ..
-controls (256.89,198.04) and (256.14,198.69) ..
-(255.2,198.69) ..
-controls (254.27,198.69) and (253.52,198.04) ..
-(253.52,197.24) -- cycle ;
-%Shape: Ellipse [id:dp3684815163642654]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (252.4,205.15) ..
-controls (252.4,204.35) and (253.16,203.7) ..
-(254.09,203.7) ..
-controls (255.02,203.7) and (255.78,204.35) ..
-(255.78,205.15) ..
-controls (255.78,205.95) and (255.02,206.6) ..
-(254.09,206.6) ..
-controls (253.16,206.6) and (252.4,205.95) ..
-(252.4,205.15) -- cycle ;
-%Shape: Ellipse [id:dp1437934667713081]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (271.94,171.85) ..
-controls (271.94,171.05) and (272.69,170.4) ..
-(273.63,170.4) ..
-controls (274.56,170.4) and (275.31,171.05) ..
-(275.31,171.85) ..
-controls (275.31,172.65) and (274.56,173.3) ..
-(273.63,173.3) ..
-controls (272.69,173.3) and (271.94,172.65) ..
-(271.94,171.85) -- cycle ;
-%Shape: Ellipse [id:dp886301588499915]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (271.52,177.24) ..
-controls (271.52,176.44) and (272.27,175.79) ..
-(273.21,175.79) ..
-controls (274.14,175.79) and (274.9,176.44) ..
-(274.9,177.24) ..
-controls (274.9,178.04) and (274.14,178.69) ..
-(273.21,178.69) ..
-controls (272.27,178.69) and (271.52,178.04) ..
-(271.52,177.24) -- cycle ;
-%Shape: Ellipse [id:dp10861025652876077]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (271.24,183.23) ..
-controls (271.24,182.43) and (272,181.78) ..
-(272.93,181.78) ..
-controls (273.86,181.78) and (274.62,182.43) ..
-(274.62,183.23) ..
-controls (274.62,184.03) and (273.86,184.68) ..
-(272.93,184.68) ..
-controls (272,184.68) and (271.24,184.03) ..
-(271.24,183.23) -- cycle ;
-%Shape: Ellipse [id:dp8227079118183289]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (270.68,190.5) ..
-controls (270.68,189.7) and (271.44,189.05) ..
-(272.37,189.05) ..
-controls (273.3,189.05) and (274.06,189.7) ..
-(274.06,190.5) ..
-controls (274.06,191.3) and (273.3,191.95) ..
-(272.37,191.95) ..
-controls (271.44,191.95) and (270.68,191.3) ..
-(270.68,190.5) -- cycle ;
-%Shape: Ellipse [id:dp31754679610416936]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (270.12,197.12) ..
-controls (270.12,196.32) and (270.88,195.67) ..
-(271.81,195.67) ..
-controls (272.74,195.67) and (273.5,196.32) ..
-(273.5,197.12) ..
-controls (273.5,197.92) and (272.74,198.57) ..
-(271.81,198.57) ..
-controls (270.88,198.57) and (270.12,197.92) ..
-(270.12,197.12) -- cycle ;
-%Shape: Ellipse [id:dp228275147103431]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (269.7,205.03) ..
-controls (269.7,204.23) and (270.46,203.58) ..
-(271.39,203.58) ..
-controls (272.33,203.58) and (273.08,204.23) ..
-(273.08,205.03) ..
-controls (273.08,205.83) and (272.33,206.48) ..
-(271.39,206.48) ..
-controls (270.46,206.48) and (269.7,205.83) ..
-(269.7,205.03) -- cycle ;
-%Shape: Ellipse [id:dp5867689834208971]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.5,171.79) ..
-controls (284.5,170.99) and (285.25,170.34) ..
-(286.19,170.34) ..
-controls (287.12,170.34) and (287.87,170.99) ..
-(287.87,171.79) ..
-controls (287.87,172.59) and (287.12,173.24) ..
-(286.19,173.24) ..
-controls (285.25,173.24) and (284.5,172.59) ..
-(284.5,171.79) -- cycle ;
-%Shape: Ellipse [id:dp18205732240558015]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.8,177.19) ..
-controls (284.8,176.39) and (285.56,175.74) ..
-(286.49,175.74) ..
-controls (287.43,175.74) and (288.18,176.39) ..
-(288.18,177.19) ..
-controls (288.18,177.99) and (287.43,178.64) ..
-(286.49,178.64) ..
-controls (285.56,178.64) and (284.8,177.99) ..
-(284.8,177.19) -- cycle ;
-%Shape: Ellipse [id:dp6234929744101898]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.5,183.38) ..
-controls (284.5,182.58) and (285.25,181.93) ..
-(286.19,181.93) ..
-controls (287.12,181.93) and (287.87,182.58) ..
-(287.87,183.38) ..
-controls (287.87,184.18) and (287.12,184.83) ..
-(286.19,184.83) ..
-controls (285.25,184.83) and (284.5,184.18) ..
-(284.5,183.38) -- cycle ;
-%Shape: Ellipse [id:dp8290479654576126]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.65,190.17) ..
-controls (284.65,189.37) and (285.41,188.72) ..
-(286.34,188.72) ..
-controls (287.27,188.72) and (288.03,189.37) ..
-(288.03,190.17) ..
-controls (288.03,190.97) and (287.27,191.62) ..
-(286.34,191.62) ..
-controls (285.41,191.62) and (284.65,190.97) ..
-(284.65,190.17) -- cycle ;
-%Shape: Ellipse [id:dp8989481541795088]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.5,197.22) ..
-controls (284.5,196.42) and (285.25,195.77) ..
-(286.19,195.77) ..
-controls (287.12,195.77) and (287.87,196.42) ..
-(287.87,197.22) ..
-controls (287.87,198.02) and (287.12,198.67) ..
-(286.19,198.67) ..
-controls (285.25,198.67) and (284.5,198.02) ..
-(284.5,197.22) -- cycle ;
-%Shape: Ellipse [id:dp3354120737649453]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (284.34,204.99) ..
-controls (284.34,204.19) and (285.1,203.54) ..
-(286.03,203.54) ..
-controls (286.96,203.54) and (287.72,204.19) ..
-(287.72,204.99) ..
-controls (287.72,205.79) and (286.96,206.44) ..
-(286.03,206.44) ..
-controls (285.1,206.44) and (284.34,205.79) ..
-(284.34,204.99) -- cycle ;
-%Shape: Ellipse [id:dp3606226368237744]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (297.2,171.73) ..
-controls (297.2,170.93) and (297.95,170.28) ..
-(298.89,170.28) ..
-controls (299.82,170.28) and (300.57,170.93) ..
-(300.57,171.73) ..
-controls (300.57,172.53) and (299.82,173.18) ..
-(298.89,173.18) ..
-controls (297.95,173.18) and (297.2,172.53) ..
-(297.2,171.73) -- cycle ;
-%Shape: Ellipse [id:dp048913958034914495]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (297.89,177.24) ..
-controls (297.89,176.44) and (298.65,175.79) ..
-(299.58,175.79) ..
-controls (300.52,175.79) and (301.27,176.44) ..
-(301.27,177.24) ..
-controls (301.27,178.04) and (300.52,178.69) ..
-(299.58,178.69) ..
-controls (298.65,178.69) and (297.89,178.04) ..
-(297.89,177.24) -- cycle ;
-%Shape: Ellipse [id:dp19686667746567443]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (298.17,183.47) ..
-controls (298.17,182.67) and (298.93,182.02) ..
-(299.86,182.02) ..
-controls (300.79,182.02) and (301.55,182.67) ..
-(301.55,183.47) ..
-controls (301.55,184.27) and (300.79,184.92) ..
-(299.86,184.92) ..
-controls (298.93,184.92) and (298.17,184.27) ..
-(298.17,183.47) -- cycle ;
-%Shape: Ellipse [id:dp4115460327510696]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (298.93,190.24) ..
-controls (298.93,189.44) and (299.68,188.79) ..
-(300.62,188.79) ..
-controls (301.55,188.79) and (302.3,189.44) ..
-(302.3,190.24) ..
-controls (302.3,191.04) and (301.55,191.69) ..
-(300.62,191.69) ..
-controls (299.68,191.69) and (298.93,191.04) ..
-(298.93,190.24) -- cycle ;
-%Shape: Ellipse [id:dp19847266839128408]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (299.29,197.12) ..
-controls (299.29,196.32) and (300.05,195.67) ..
-(300.98,195.67) ..
-controls (301.91,195.67) and (302.67,196.32) ..
-(302.67,197.12) ..
-controls (302.67,197.92) and (301.91,198.57) ..
-(300.98,198.57) ..
-controls (300.05,198.57) and (299.29,197.92) ..
-(299.29,197.12) -- cycle ;
-%Shape: Ellipse [id:dp48996962931873567]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (300.13,204.91) ..
-controls (300.13,204.11) and (300.88,203.46) ..
-(301.82,203.46) ..
-controls (302.75,203.46) and (303.5,204.11) ..
-(303.5,204.91) ..
-controls (303.5,205.71) and (302.75,206.36) ..
-(301.82,206.36) ..
-controls (300.88,206.36) and (300.13,205.71) ..
-(300.13,204.91) -- cycle ;
-%Shape: Ellipse [id:dp8365501880357185]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (311.87,172.13) ..
-controls (311.87,171.33) and (312.62,170.68) ..
-(313.56,170.68) ..
-controls (314.49,170.68) and (315.25,171.33) ..
-(315.25,172.13) ..
-controls (315.25,172.93) and (314.49,173.58) ..
-(313.56,173.58) ..
-controls (312.62,173.58) and (311.87,172.93) ..
-(311.87,172.13) -- cycle ;
-%Shape: Ellipse [id:dp3988926174843601]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (313.51,177.36) ..
-controls (313.51,176.56) and (314.26,175.91) ..
-(315.19,175.91) ..
-controls (316.13,175.91) and (316.88,176.56) ..
-(316.88,177.36) ..
-controls (316.88,178.16) and (316.13,178.81) ..
-(315.19,178.81) ..
-controls (314.26,178.81) and (313.51,178.16) ..
-(313.51,177.36) -- cycle ;
-%Shape: Ellipse [id:dp04101225467897396]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (314.36,183.23) ..
-controls (314.36,182.43) and (315.12,181.78) ..
-(316.05,181.78) ..
-controls (316.98,181.78) and (317.74,182.43) ..
-(317.74,183.23) ..
-controls (317.74,184.03) and (316.98,184.68) ..
-(316.05,184.68) ..
-controls (315.12,184.68) and (314.36,184.03) ..
-(314.36,183.23) -- cycle ;
-%Shape: Ellipse [id:dp5863915656225569]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (315.51,190.5) ..
-controls (315.51,189.7) and (316.26,189.05) ..
-(317.19,189.05) ..
-controls (318.13,189.05) and (318.88,189.7) ..
-(318.88,190.5) ..
-controls (318.88,191.3) and (318.13,191.95) ..
-(317.19,191.95) ..
-controls (316.26,191.95) and (315.51,191.3) ..
-(315.51,190.5) -- cycle ;
-%Shape: Ellipse [id:dp17122444124667857]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (316.32,197.12) ..
-controls (316.32,196.32) and (317.07,195.67) ..
-(318,195.67) ..
-controls (318.94,195.67) and (319.69,196.32) ..
-(319.69,197.12) ..
-controls (319.69,197.92) and (318.94,198.57) ..
-(318,198.57) ..
-controls (317.07,198.57) and (316.32,197.92) ..
-(316.32,197.12) -- cycle ;
-%Shape: Ellipse [id:dp595550673895106]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (317.99,205.03) ..
-controls (317.99,204.23) and (318.75,203.58) ..
-(319.68,203.58) ..
-controls (320.61,203.58) and (321.37,204.23) ..
-(321.37,205.03) ..
-controls (321.37,205.83) and (320.61,206.48) ..
-(319.68,206.48) ..
-controls (318.75,206.48) and (317.99,205.83) ..
-(317.99,205.03) -- cycle ;
-%Shape: Ellipse [id:dp42805717802208254]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (326.92,171.49) ..
-controls (326.92,170.69) and (327.68,170.04) ..
-(328.61,170.04) ..
-controls (329.54,170.04) and (330.3,170.69) ..
-(330.3,171.49) ..
-controls (330.3,172.29) and (329.54,172.94) ..
-(328.61,172.94) ..
-controls (327.68,172.94) and (326.92,172.29) ..
-(326.92,171.49) -- cycle ;
-%Shape: Ellipse [id:dp07574640518443809]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (328.6,177.24) ..
-controls (328.6,176.44) and (329.35,175.79) ..
-(330.28,175.79) ..
-controls (331.22,175.79) and (331.97,176.44) ..
-(331.97,177.24) ..
-controls (331.97,178.04) and (331.22,178.69) ..
-(330.28,178.69) ..
-controls (329.35,178.69) and (328.6,178.04) ..
-(328.6,177.24) -- cycle ;
-%Shape: Ellipse [id:dp35961760720035785]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (329.99,183.35) ..
-controls (329.99,182.55) and (330.75,181.9) ..
-(331.68,181.9) ..
-controls (332.61,181.9) and (333.37,182.55) ..
-(333.37,183.35) ..
-controls (333.37,184.15) and (332.61,184.8) ..
-(331.68,184.8) ..
-controls (330.75,184.8) and (329.99,184.15) ..
-(329.99,183.35) -- cycle ;
-%Shape: Ellipse [id:dp6949164860668007]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (331.93,190.1) ..
-controls (331.93,189.3) and (332.69,188.65) ..
-(333.62,188.65) ..
-controls (334.55,188.65) and (335.31,189.3) ..
-(335.31,190.1) ..
-controls (335.31,190.9) and (334.55,191.55) ..
-(333.62,191.55) ..
-controls (332.69,191.55) and (331.93,190.9) ..
-(331.93,190.1) -- cycle ;
-%Shape: Ellipse [id:dp6551927674212119]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (333.76,197.24) ..
-controls (333.76,196.44) and (334.52,195.79) ..
-(335.45,195.79) ..
-controls (336.38,195.79) and (337.14,196.44) ..
-(337.14,197.24) ..
-controls (337.14,198.04) and (336.38,198.69) ..
-(335.45,198.69) ..
-controls (334.52,198.69) and (333.76,198.04) ..
-(333.76,197.24) -- cycle ;
-%Shape: Ellipse [id:dp5972824761324165]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (335.71,205.03) ..
-controls (335.71,204.23) and (336.47,203.58) ..
-(337.4,203.58) ..
-controls (338.33,203.58) and (339.09,204.23) ..
-(339.09,205.03) ..
-controls (339.09,205.83) and (338.33,206.48) ..
-(337.4,206.48) ..
-controls (336.47,206.48) and (335.71,205.83) ..
-(335.71,205.03) -- cycle ;
-%Shape: Ellipse [id:dp25895708663696104]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (340.46,171.49) ..
-controls (340.46,170.69) and (341.21,170.04) ..
-(342.15,170.04) ..
-controls (343.08,170.04) and (343.84,170.69) ..
-(343.84,171.49) ..
-controls (343.84,172.29) and (343.08,172.94) ..
-(342.15,172.94) ..
-controls (341.21,172.94) and (340.46,172.29) ..
-(340.46,171.49) -- cycle ;
-%Shape: Ellipse [id:dp776678914241709]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (342.69,177) ..
-controls (342.69,176.2) and (343.45,175.55) ..
-(344.38,175.55) ..
-controls (345.31,175.55) and (346.07,176.2) ..
-(346.07,177) ..
-controls (346.07,177.8) and (345.31,178.45) ..
-(344.38,178.45) ..
-controls (343.45,178.45) and (342.69,177.8) ..
-(342.69,177) -- cycle ;
-%Shape: Ellipse [id:dp7372524459660503]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (344.92,183.35) ..
-controls (344.92,182.55) and (345.68,181.9) ..
-(346.61,181.9) ..
-controls (347.54,181.9) and (348.3,182.55) ..
-(348.3,183.35) ..
-controls (348.3,184.15) and (347.54,184.8) ..
-(346.61,184.8) ..
-controls (345.68,184.8) and (344.92,184.15) ..
-(344.92,183.35) -- cycle ;
-%Shape: Ellipse [id:dp24122491835471704]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (347.44,190.5) ..
-controls (347.44,189.7) and (348.19,189.05) ..
-(349.12,189.05) ..
-controls (350.06,189.05) and (350.81,189.7) ..
-(350.81,190.5) ..
-controls (350.81,191.3) and (350.06,191.95) ..
-(349.12,191.95) ..
-controls (348.19,191.95) and (347.44,191.3) ..
-(347.44,190.5) -- cycle ;
-%Shape: Ellipse [id:dp7904451243351014]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (349.53,197) ..
-controls (349.53,196.2) and (350.28,195.55) ..
-(351.22,195.55) ..
-controls (352.15,195.55) and (352.91,196.2) ..
-(352.91,197) ..
-controls (352.91,197.8) and (352.15,198.45) ..
-(351.22,198.45) ..
-controls (350.28,198.45) and (349.53,197.8) ..
-(349.53,197) -- cycle ;
-%Shape: Ellipse [id:dp4617144473175392]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (352.46,204.67) ..
-controls (352.46,203.87) and (353.22,203.22) ..
-(354.15,203.22) ..
-controls (355.08,203.22) and (355.84,203.87) ..
-(355.84,204.67) ..
-controls (355.84,205.47) and (355.08,206.12) ..
-(354.15,206.12) ..
-controls (353.22,206.12) and (352.46,205.47) ..
-(352.46,204.67) -- cycle ;
-%Shape: Ellipse [id:dp626912606919074]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (354.97,171.49) ..
-controls (354.97,170.69) and (355.73,170.04) ..
-(356.66,170.04) ..
-controls (357.59,170.04) and (358.35,170.69) ..
-(358.35,171.49) ..
-controls (358.35,172.29) and (357.59,172.94) ..
-(356.66,172.94) ..
-controls (355.73,172.94) and (354.97,172.29) ..
-(354.97,171.49) -- cycle ;
-%Shape: Ellipse [id:dp4306093121189267]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (357.48,177.12) ..
-controls (357.48,176.32) and (358.24,175.67) ..
-(359.17,175.67) ..
-controls (360.1,175.67) and (360.86,176.32) ..
-(360.86,177.12) ..
-controls (360.86,177.92) and (360.1,178.57) ..
-(359.17,178.57) ..
-controls (358.24,178.57) and (357.48,177.92) ..
-(357.48,177.12) -- cycle ;
-%Shape: Ellipse [id:dp4919285418842567]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (359.86,183.23) ..
-controls (359.86,182.43) and (360.61,181.78) ..
-(361.54,181.78) ..
-controls (362.48,181.78) and (363.23,182.43) ..
-(363.23,183.23) ..
-controls (363.23,184.03) and (362.48,184.68) ..
-(361.54,184.68) ..
-controls (360.61,184.68) and (359.86,184.03) ..
-(359.86,183.23) -- cycle ;
-%Shape: Ellipse [id:dp5744075183160424]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (362.65,189.82) ..
-controls (362.65,189.02) and (363.4,188.37) ..
-(364.34,188.37) ..
-controls (365.27,188.37) and (366.02,189.02) ..
-(366.02,189.82) ..
-controls (366.02,190.62) and (365.27,191.27) ..
-(364.34,191.27) ..
-controls (363.4,191.27) and (362.65,190.62) ..
-(362.65,189.82) -- cycle ;
-%Shape: Ellipse [id:dp046203720018062944]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (366,197) ..
-controls (366,196.2) and (366.75,195.55) ..
-(367.68,195.55) ..
-controls (368.62,195.55) and (369.37,196.2) ..
-(369.37,197) ..
-controls (369.37,197.8) and (368.62,198.45) ..
-(367.68,198.45) ..
-controls (366.75,198.45) and (366,197.8) ..
-(366,197) -- cycle ;
-%Shape: Ellipse [id:dp49972425736995807]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (369.21,204.67) ..
-controls (369.21,203.87) and (369.96,203.22) ..
-(370.89,203.22) ..
-controls (371.83,203.22) and (372.58,203.87) ..
-(372.58,204.67) ..
-controls (372.58,205.47) and (371.83,206.12) ..
-(370.89,206.12) ..
-controls (369.96,206.12) and (369.21,205.47) ..
-(369.21,204.67) -- cycle ;
-%Shape: Ellipse [id:dp5024602360079904]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (367.39,171.49) ..
-controls (367.39,170.69) and (368.15,170.04) ..
-(369.08,170.04) ..
-controls (370.01,170.04) and (370.77,170.69) ..
-(370.77,171.49) ..
-controls (370.77,172.29) and (370.01,172.94) ..
-(369.08,172.94) ..
-controls (368.15,172.94) and (367.39,172.29) ..
-(367.39,171.49) -- cycle ;
-%Shape: Ellipse [id:dp9654915371918213]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (370.18,177.12) ..
-controls (370.18,176.32) and (370.94,175.67) ..
-(371.87,175.67) ..
-controls (372.8,175.67) and (373.56,176.32) ..
-(373.56,177.12) ..
-controls (373.56,177.92) and (372.8,178.57) ..
-(371.87,178.57) ..
-controls (370.94,178.57) and (370.18,177.92) ..
-(370.18,177.12) -- cycle ;
-%Shape: Ellipse [id:dp15713183567776468]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (373.53,183.35) ..
-controls (373.53,182.55) and (374.29,181.9) ..
-(375.22,181.9) ..
-controls (376.15,181.9) and (376.91,182.55) ..
-(376.91,183.35) ..
-controls (376.91,184.15) and (376.15,184.8) ..
-(375.22,184.8) ..
-controls (374.29,184.8) and (373.53,184.15) ..
-(373.53,183.35) -- cycle ;
-%Shape: Ellipse [id:dp9239425899364824]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (377.52,190.32) ..
-controls (377.52,189.52) and (378.28,188.87) ..
-(379.21,188.87) ..
-controls (380.14,188.87) and (380.9,189.52) ..
-(380.9,190.32) ..
-controls (380.9,191.12) and (380.14,191.77) ..
-(379.21,191.77) ..
-controls (378.28,191.77) and (377.52,191.12) ..
-(377.52,190.32) -- cycle ;
-%Shape: Ellipse [id:dp9110579702631929]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (381.35,196.88) ..
-controls (381.35,196.08) and (382.1,195.43) ..
-(383.04,195.43) ..
-controls (383.97,195.43) and (384.72,196.08) ..
-(384.72,196.88) ..
-controls (384.72,197.68) and (383.97,198.33) ..
-(383.04,198.33) ..
-controls (382.1,198.33) and (381.35,197.68) ..
-(381.35,196.88) -- cycle ;
-%Shape: Ellipse [id:dp24310198218055246]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (385.67,204.67) ..
-controls (385.67,203.87) and (386.43,203.22) ..
-(387.36,203.22) ..
-controls (388.29,203.22) and (389.05,203.87) ..
-(389.05,204.67) ..
-controls (389.05,205.47) and (388.29,206.12) ..
-(387.36,206.12) ..
-controls (386.43,206.12) and (385.67,205.47) ..
-(385.67,204.67) -- cycle ;
-%Shape: Ellipse [id:dp7388999956457485]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (381.21,171.49) ..
-controls (381.21,170.69) and (381.96,170.04) ..
-(382.9,170.04) ..
-controls (383.83,170.04) and (384.58,170.69) ..
-(384.58,171.49) ..
-controls (384.58,172.29) and (383.83,172.94) ..
-(382.9,172.94) ..
-controls (381.96,172.94) and (381.21,172.29) ..
-(381.21,171.49) -- cycle ;
-%Shape: Ellipse [id:dp5640310139705571]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (384,177) ..
-controls (384,176.2) and (384.75,175.55) ..
-(385.69,175.55) ..
-controls (386.62,175.55) and (387.38,176.2) ..
-(387.38,177) ..
-controls (387.38,177.8) and (386.62,178.45) ..
-(385.69,178.45) ..
-controls (384.75,178.45) and (384,177.8) ..
-(384,177) -- cycle ;
-%Shape: Ellipse [id:dp2695616969380312]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (387.63,183.23) ..
-controls (387.63,182.43) and (388.38,181.78) ..
-(389.32,181.78) ..
-controls (390.25,181.78) and (391,182.43) ..
-(391,183.23) ..
-controls (391,184.03) and (390.25,184.68) ..
-(389.32,184.68) ..
-controls (388.38,184.68) and (387.63,184.03) ..
-(387.63,183.23) -- cycle ;
-%Shape: Ellipse [id:dp4126882239946579]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (391.49,190.24) ..
-controls (391.49,189.44) and (392.25,188.79) ..
-(393.18,188.79) ..
-controls (394.11,188.79) and (394.87,189.44) ..
-(394.87,190.24) ..
-controls (394.87,191.04) and (394.11,191.69) ..
-(393.18,191.69) ..
-controls (392.25,191.69) and (391.49,191.04) ..
-(391.49,190.24) -- cycle ;
-%Shape: Ellipse [id:dp7640055339758918]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (395.16,197) ..
-controls (395.16,196.2) and (395.92,195.55) ..
-(396.85,195.55) ..
-controls (397.78,195.55) and (398.54,196.2) ..
-(398.54,197) ..
-controls (398.54,197.8) and (397.78,198.45) ..
-(396.85,198.45) ..
-controls (395.92,198.45) and (395.16,197.8) ..
-(395.16,197) -- cycle ;
-%Shape: Ellipse [id:dp8721356938843838]
-\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (399.35,204.79) ..
-controls (399.35,203.99) and (400.11,203.34) ..
-(401.04,203.34) ..
-controls (401.97,203.34) and (402.73,203.99) ..
-(402.73,204.79) ..
-controls (402.73,205.59) and (401.97,206.24) ..
-(401.04,206.24) ..
-controls (400.11,206.24) and (399.35,205.59) ..
-(399.35,204.79) -- cycle ;
-%Straight Lines [id:da7979534893976028]
-\draw [color={rgb, 255:red, 127; green, 117; blue, 117 }  ,draw opacity=1 ] [dash pattern={on 4.5pt off 4.5pt}]  (287.87,73.06) -- (287.87,183.38) ;
-%Straight Lines [id:da03397341825975597]
-\draw    (176.12,166.91) -- (148.03,213.62) ;
-%Straight Lines [id:da855504113906919]
-\draw    (148.03,213.62) -- (151.25,213.56) ;
-%Straight Lines [id:da7263472575025891]
-\draw    (176.12,166.91) -- (179.34,166.85) ;
-%Straight Lines [id:da3871270427067002]
-\draw    (420.92,213.12) -- (424.14,213.05) ;
-%Straight Lines [id:da5505655212811509]
-\draw    (393.8,167) -- (397.02,166.94) ;
-%Straight Lines [id:da3454569240651897]
-\draw    (397.02,166.94) -- (424.14,213.05) ;
-%Straight Lines [id:da9496307475947867]
-\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (159.76,153.9) -- (179.23,153.7) ;
-\draw [shift={(182.23,153.66)}, rotate = 539.39] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da7018774365527356]
-\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (159.76,153.9) -- (150.65,164.89) ;
-\draw [shift={(148.74,167.2)}, rotate = 309.65999999999997] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Shape: Wave [id:dp8230250028099939]
-\draw  [color={rgb, 255:red, 229; green, 21; blue, 21 }  ,draw opacity=1 ][line width=1.5]  (287.6,178.6) ..
-controls (302.2,174.36) and (316.1,170.3) ..
-(316.1,165.6) ..
-controls (316.1,160.9) and (302.2,156.84) ..
-(287.6,152.6) ..
-controls (273,148.36) and (259.1,144.3) ..
-(259.1,139.6) ..
-controls (259.1,134.9) and (273,130.84) ..
-(287.6,126.6) ..
-controls (302.2,122.36) and (316.1,118.3) ..
-(316.1,113.6) ..
-controls (316.1,108.9) and (302.2,104.84) ..
-(287.6,100.6) ..
-controls (273,96.36) and (259.1,92.3) ..
-(259.1,87.6) ..
-controls (259.1,83.15) and (271.51,79.29) ..
-(285.19,75.3) ;
-%Straight Lines [id:da5686545133121326]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287.8,80.6) -- (275.2,80.6) ;
-\draw [shift={(272.2,80.6)}, rotate = 360] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da782823803042028]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.2,94.2) -- (275.2,94.53) ;
-\draw [shift={(272.2,94.6)}, rotate = 358.57] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da871137874278286]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.6,87.2) -- (262.4,87.74) ;
-\draw [shift={(259.4,87.8)}, rotate = 358.82] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da5553069086130265]
-\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (159.76,153.9) -- (159.8,134) ;
-\draw [shift={(159.8,131)}, rotate = 450.09] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da6699653458590744]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.2,120.6) -- (299.6,120.6) ;
-\draw [shift={(302.6,120.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da2953745491779931]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.6,106.6) -- (301.6,106.6) ;
-\draw [shift={(304.6,106.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da7676872185404988]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287.8,114) -- (312,113.47) ;
-\draw [shift={(315,113.4)}, rotate = 538.74] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da6047601791922992]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287.8,132.2) -- (275.2,132.2) ;
-\draw [shift={(272.2,132.2)}, rotate = 360] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da08573309540969332]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.2,145.8) -- (275.2,146.13) ;
-\draw [shift={(272.2,146.2)}, rotate = 358.57] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da0011618805281727873]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (288.6,138.8) -- (262.4,139.34) ;
-\draw [shift={(259.4,139.4)}, rotate = 358.82] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da8026810749325723]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287,172.6) -- (298.4,172.6) ;
-\draw [shift={(301.4,172.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da18748197647149523]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (287.4,158.6) -- (300.4,158.6) ;
-\draw [shift={(303.4,158.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da8245101205852268]
-\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (286.6,166) -- (310.8,165.47) ;
-\draw [shift={(313.8,165.4)}, rotate = 538.74] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
-%Straight Lines [id:da7887384290153587]
-\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (229.92,180.08) -- (229.78,134.23) ;
-\draw [shift={(229.77,130.23)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
-%Straight Lines [id:da8482623274180794]
-\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (250.23,180.08) -- (250.23,134.23) ;
-\draw [shift={(250.23,130.23)}, rotate = 450] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
-%Straight Lines [id:da28732418115198444]
-\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (270.38,180.08) -- (270.24,134.38) ;
-\draw [shift={(270.23,130.38)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
-%Straight Lines [id:da23686823952523528]
-\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (290.38,179.92) -- (290.24,134.23) ;
-\draw [shift={(290.23,130.23)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
-%Straight Lines [id:da3497985465503395]
-\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (310.23,180.08) -- (310.09,134.38) ;
-\draw [shift={(310.08,130.38)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
-%Straight Lines [id:da4475685784611998]
-\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (330.08,180.23) -- (329.94,134.54) ;
-\draw [shift={(329.92,130.54)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
+%Straight Lines [id:da5726274877822322]
+\draw [color={rgb, 255:red, 127; green, 117; blue, 117 }  ,draw opacity=1 ] [dash pattern={on 4.5pt off 4.5pt}]  (309.51,73.75) -- (309.87,203.38) ;
+\draw [shift={(309.5,70.75)}, rotate = 89.84] [fill={rgb, 255:red, 127; green, 117; blue, 117 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (5.36,-2.57) -- (0,0) -- (5.36,2.57) -- cycle    ;
+%Straight Lines [id:da33511458189374754]
+\draw    (171.25,233.56) -- (440.92,233.12) ;
+%Straight Lines [id:da3398276064046053]
+\draw    (198.99,187.4) -- (413.4,187.4) ;
+%Straight Lines [id:da7839634174109911]
+\draw    (199.39,187) -- (171.25,233.56) ;
+%Straight Lines [id:da05894655796955206]
+\draw    (413.8,187) -- (440.92,233.12) ;
+%Straight Lines [id:da13536583120363344]
+\draw    (306.6,187) -- (306.08,233.34) ;
+%Straight Lines [id:da4997587586993617]
+\draw    (293.92,186.96) -- (290.68,233.56) ;
+%Straight Lines [id:da9722317036710604]
+\draw    (279.41,186.96) -- (273.18,233.3) ;
+%Straight Lines [id:da026737631204194257]
+\draw    (265.3,186.91) -- (257.52,233.3) ;
+%Straight Lines [id:da1602511216081195]
+\draw    (252.1,187.18) -- (240.33,233.82) ;
+%Straight Lines [id:da1955990930085778]
+\draw    (237.96,187.2) -- (221.3,233.56) ;
+%Straight Lines [id:da21157278737030283]
+\draw    (225.7,187.18) -- (205.02,233.82) ;
+%Straight Lines [id:da7497787157955642]
+\draw    (212.98,187.2) -- (189.98,233.82) ;
+%Straight Lines [id:da8978850152403992]
+\draw    (318.62,186.91) -- (322.61,233.56) ;
+%Straight Lines [id:da8571932918195948]
+\draw    (333.18,187.08) -- (341.21,233.92) ;
+%Straight Lines [id:da28540902944632984]
+\draw    (347.48,186.91) -- (359.76,233.3) ;
+%Straight Lines [id:da9908810182455174]
+\draw    (360.68,187.18) -- (377.57,233.82) ;
+%Straight Lines [id:da9097146225861146]
+\draw    (374.8,187.18) -- (394.76,233.56) ;
+%Straight Lines [id:da7912008612279866]
+\draw    (386.16,187.08) -- (412.26,233.56) ;
+%Straight Lines [id:da5553223696891176]
+\draw    (400.59,187.18) -- (425.77,233.3) ;
+%Straight Lines [id:da4854495790277076]
+\draw    (175.55,225.39) -- (436.51,224.6) ;
+%Straight Lines [id:da8466426333509127]
+\draw    (180.77,217.48) -- (431.6,216.96) ;
+%Straight Lines [id:da11285301674845338]
+\draw    (185.32,210.28) -- (427.36,210.06) ;
+%Straight Lines [id:da6415671559000329]
+\draw    (189.06,203.52) -- (423.31,203.25) ;
+%Straight Lines [id:da09765847114278392]
+\draw    (192.65,197.85) -- (419.54,197.33) ;
+%Straight Lines [id:da9654913395744491]
+\draw    (195.41,192.58) -- (416.16,191.79) ;
+%Shape: Ellipse [id:dp5486828293018222]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (192.44,225.39) ..
+controls (192.44,224.59) and (193.19,223.94) ..
+(194.12,223.94) ..
+controls (195.06,223.94) and (195.81,224.59) ..
+(195.81,225.39) ..
+controls (195.81,226.19) and (195.06,226.84) ..
+(194.12,226.84) ..
+controls (193.19,226.84) and (192.44,226.19) ..
+(192.44,225.39) -- cycle ;
+%Shape: Ellipse [id:dp36608685875382685]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (196.2,217.36) ..
+controls (196.2,216.56) and (196.96,215.91) ..
+(197.89,215.91) ..
+controls (198.82,215.91) and (199.58,216.56) ..
+(199.58,217.36) ..
+controls (199.58,218.16) and (198.82,218.81) ..
+(197.89,218.81) ..
+controls (196.96,218.81) and (196.2,218.16) ..
+(196.2,217.36) -- cycle ;
+%Shape: Ellipse [id:dp5251439025998383]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (199.83,209.94) ..
+controls (199.83,209.14) and (200.59,208.49) ..
+(201.52,208.49) ..
+controls (202.45,208.49) and (203.21,209.14) ..
+(203.21,209.94) ..
+controls (203.21,210.74) and (202.45,211.39) ..
+(201.52,211.39) ..
+controls (200.59,211.39) and (199.83,210.74) ..
+(199.83,209.94) -- cycle ;
+%Shape: Ellipse [id:dp4067558888223195]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (202.9,203.59) ..
+controls (202.9,202.79) and (203.66,202.14) ..
+(204.59,202.14) ..
+controls (205.52,202.14) and (206.28,202.79) ..
+(206.28,203.59) ..
+controls (206.28,204.39) and (205.52,205.04) ..
+(204.59,205.04) ..
+controls (203.66,205.04) and (202.9,204.39) ..
+(202.9,203.59) -- cycle ;
+%Shape: Ellipse [id:dp3570254692613275]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (206.11,197.24) ..
+controls (206.11,196.44) and (206.87,195.79) ..
+(207.8,195.79) ..
+controls (208.73,195.79) and (209.49,196.44) ..
+(209.49,197.24) ..
+controls (209.49,198.04) and (208.73,198.69) ..
+(207.8,198.69) ..
+controls (206.87,198.69) and (206.11,198.04) ..
+(206.11,197.24) -- cycle ;
+%Shape: Ellipse [id:dp30798846372533184]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (209.04,191.85) ..
+controls (209.04,191.05) and (209.8,190.4) ..
+(210.73,190.4) ..
+controls (211.66,190.4) and (212.42,191.05) ..
+(212.42,191.85) ..
+controls (212.42,192.65) and (211.66,193.3) ..
+(210.73,193.3) ..
+controls (209.8,193.3) and (209.04,192.65) ..
+(209.04,191.85) -- cycle ;
+%Shape: Ellipse [id:dp1418023342038397]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (206.95,225.15) ..
+controls (206.95,224.35) and (207.71,223.7) ..
+(208.64,223.7) ..
+controls (209.57,223.7) and (210.33,224.35) ..
+(210.33,225.15) ..
+controls (210.33,225.95) and (209.57,226.6) ..
+(208.64,226.6) ..
+controls (207.71,226.6) and (206.95,225.95) ..
+(206.95,225.15) -- cycle ;
+%Shape: Ellipse [id:dp32047691597756267]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (210.44,217.48) ..
+controls (210.44,216.68) and (211.19,216.03) ..
+(212.13,216.03) ..
+controls (213.06,216.03) and (213.82,216.68) ..
+(213.82,217.48) ..
+controls (213.82,218.28) and (213.06,218.93) ..
+(212.13,218.93) ..
+controls (211.19,218.93) and (210.44,218.28) ..
+(210.44,217.48) -- cycle ;
+%Shape: Ellipse [id:dp49839354018590987]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (213.67,210.5) ..
+controls (213.67,209.7) and (214.43,209.05) ..
+(215.36,209.05) ..
+controls (216.29,209.05) and (217.05,209.7) ..
+(217.05,210.5) ..
+controls (217.05,211.3) and (216.29,211.95) ..
+(215.36,211.95) ..
+controls (214.43,211.95) and (213.67,211.3) ..
+(213.67,210.5) -- cycle ;
+%Shape: Ellipse [id:dp8228751417402214]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (216.58,203.47) ..
+controls (216.58,202.67) and (217.33,202.02) ..
+(218.27,202.02) ..
+controls (219.2,202.02) and (219.96,202.67) ..
+(219.96,203.47) ..
+controls (219.96,204.27) and (219.2,204.92) ..
+(218.27,204.92) ..
+controls (217.33,204.92) and (216.58,204.27) ..
+(216.58,203.47) -- cycle ;
+%Shape: Ellipse [id:dp06953462817928524]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (219.51,197.48) ..
+controls (219.51,196.68) and (220.27,196.03) ..
+(221.2,196.03) ..
+controls (222.13,196.03) and (222.89,196.68) ..
+(222.89,197.48) ..
+controls (222.89,198.28) and (222.13,198.93) ..
+(221.2,198.93) ..
+controls (220.27,198.93) and (219.51,198.28) ..
+(219.51,197.48) -- cycle ;
+%Shape: Ellipse [id:dp3903462442234402]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (221.6,191.85) ..
+controls (221.6,191.05) and (222.36,190.4) ..
+(223.29,190.4) ..
+controls (224.22,190.4) and (224.98,191.05) ..
+(224.98,191.85) ..
+controls (224.98,192.65) and (224.22,193.3) ..
+(223.29,193.3) ..
+controls (222.36,193.3) and (221.6,192.65) ..
+(221.6,191.85) -- cycle ;
+%Shape: Ellipse [id:dp4379467974609894]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (222.72,225.27) ..
+controls (222.72,224.47) and (223.47,223.82) ..
+(224.41,223.82) ..
+controls (225.34,223.82) and (226.1,224.47) ..
+(226.1,225.27) ..
+controls (226.1,226.07) and (225.34,226.72) ..
+(224.41,226.72) ..
+controls (223.47,226.72) and (222.72,226.07) ..
+(222.72,225.27) -- cycle ;
+%Shape: Ellipse [id:dp26193777518096795]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (225.51,217.36) ..
+controls (225.51,216.56) and (226.27,215.91) ..
+(227.2,215.91) ..
+controls (228.13,215.91) and (228.89,216.56) ..
+(228.89,217.36) ..
+controls (228.89,218.16) and (228.13,218.81) ..
+(227.2,218.81) ..
+controls (226.27,218.81) and (225.51,218.16) ..
+(225.51,217.36) -- cycle ;
+%Shape: Ellipse [id:dp019861246471317262]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (227.95,210.5) ..
+controls (227.95,209.7) and (228.7,209.05) ..
+(229.64,209.05) ..
+controls (230.57,209.05) and (231.32,209.7) ..
+(231.32,210.5) ..
+controls (231.32,211.3) and (230.57,211.95) ..
+(229.64,211.95) ..
+controls (228.7,211.95) and (227.95,211.3) ..
+(227.95,210.5) -- cycle ;
+%Shape: Ellipse [id:dp1381162876501707]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (230.53,203.35) ..
+controls (230.53,202.55) and (231.29,201.9) ..
+(232.22,201.9) ..
+controls (233.15,201.9) and (233.91,202.55) ..
+(233.91,203.35) ..
+controls (233.91,204.15) and (233.15,204.8) ..
+(232.22,204.8) ..
+controls (231.29,204.8) and (230.53,204.15) ..
+(230.53,203.35) -- cycle ;
+%Shape: Ellipse [id:dp5428095668243373]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (232.63,197.12) ..
+controls (232.63,196.32) and (233.38,195.67) ..
+(234.32,195.67) ..
+controls (235.25,195.67) and (236,196.32) ..
+(236,197.12) ..
+controls (236,197.92) and (235.25,198.57) ..
+(234.32,198.57) ..
+controls (233.38,198.57) and (232.63,197.92) ..
+(232.63,197.12) -- cycle ;
+%Shape: Ellipse [id:dp18211764432101352]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (234.58,191.73) ..
+controls (234.58,190.93) and (235.34,190.28) ..
+(236.27,190.28) ..
+controls (237.2,190.28) and (237.96,190.93) ..
+(237.96,191.73) ..
+controls (237.96,192.53) and (237.2,193.18) ..
+(236.27,193.18) ..
+controls (235.34,193.18) and (234.58,192.53) ..
+(234.58,191.73) -- cycle ;
+%Shape: Ellipse [id:dp75878279205988]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (240.72,225.39) ..
+controls (240.72,224.59) and (241.48,223.94) ..
+(242.41,223.94) ..
+controls (243.34,223.94) and (244.1,224.59) ..
+(244.1,225.39) ..
+controls (244.1,226.19) and (243.34,226.84) ..
+(242.41,226.84) ..
+controls (241.48,226.84) and (240.72,226.19) ..
+(240.72,225.39) -- cycle ;
+%Shape: Ellipse [id:dp4571990490264608]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (242.81,217.48) ..
+controls (242.81,216.68) and (243.57,216.03) ..
+(244.5,216.03) ..
+controls (245.44,216.03) and (246.19,216.68) ..
+(246.19,217.48) ..
+controls (246.19,218.28) and (245.44,218.93) ..
+(244.5,218.93) ..
+controls (243.57,218.93) and (242.81,218.28) ..
+(242.81,217.48) -- cycle ;
+%Shape: Ellipse [id:dp4013248465635957]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (244.53,210.5) ..
+controls (244.53,209.7) and (245.28,209.05) ..
+(246.21,209.05) ..
+controls (247.15,209.05) and (247.9,209.7) ..
+(247.9,210.5) ..
+controls (247.9,211.3) and (247.15,211.95) ..
+(246.21,211.95) ..
+controls (245.28,211.95) and (244.53,211.3) ..
+(244.53,210.5) -- cycle ;
+%Shape: Ellipse [id:dp7663905432089348]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (246.16,203.59) ..
+controls (246.16,202.79) and (246.92,202.14) ..
+(247.85,202.14) ..
+controls (248.78,202.14) and (249.54,202.79) ..
+(249.54,203.59) ..
+controls (249.54,204.39) and (248.78,205.04) ..
+(247.85,205.04) ..
+controls (246.92,205.04) and (246.16,204.39) ..
+(246.16,203.59) -- cycle ;
+%Shape: Ellipse [id:dp37843272203409817]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (247.7,197.36) ..
+controls (247.7,196.56) and (248.45,195.91) ..
+(249.39,195.91) ..
+controls (250.32,195.91) and (251.08,196.56) ..
+(251.08,197.36) ..
+controls (251.08,198.16) and (250.32,198.81) ..
+(249.39,198.81) ..
+controls (248.45,198.81) and (247.7,198.16) ..
+(247.7,197.36) -- cycle ;
+%Shape: Ellipse [id:dp6447080382369588]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (249.09,191.97) ..
+controls (249.09,191.17) and (249.85,190.52) ..
+(250.78,190.52) ..
+controls (251.72,190.52) and (252.47,191.17) ..
+(252.47,191.97) ..
+controls (252.47,192.77) and (251.72,193.42) ..
+(250.78,193.42) ..
+controls (249.85,193.42) and (249.09,192.77) ..
+(249.09,191.97) -- cycle ;
+%Shape: Ellipse [id:dp1815955543825718]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (262.77,191.85) ..
+controls (262.77,191.05) and (263.53,190.4) ..
+(264.46,190.4) ..
+controls (265.39,190.4) and (266.15,191.05) ..
+(266.15,191.85) ..
+controls (266.15,192.65) and (265.39,193.3) ..
+(264.46,193.3) ..
+controls (263.53,193.3) and (262.77,192.65) ..
+(262.77,191.85) -- cycle ;
+%Shape: Ellipse [id:dp8880224712841644]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (261.79,197.48) ..
+controls (261.79,196.68) and (262.55,196.03) ..
+(263.48,196.03) ..
+controls (264.41,196.03) and (265.17,196.68) ..
+(265.17,197.48) ..
+controls (265.17,198.28) and (264.41,198.93) ..
+(263.48,198.93) ..
+controls (262.55,198.93) and (261.79,198.28) ..
+(261.79,197.48) -- cycle ;
+%Shape: Ellipse [id:dp4989200469883939]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (260.68,203.23) ..
+controls (260.68,202.43) and (261.43,201.78) ..
+(262.37,201.78) ..
+controls (263.3,201.78) and (264.05,202.43) ..
+(264.05,203.23) ..
+controls (264.05,204.03) and (263.3,204.68) ..
+(262.37,204.68) ..
+controls (261.43,204.68) and (260.68,204.03) ..
+(260.68,203.23) -- cycle ;
+%Shape: Ellipse [id:dp28395245427438764]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (259.72,210.1) ..
+controls (259.72,209.3) and (260.48,208.65) ..
+(261.41,208.65) ..
+controls (262.34,208.65) and (263.1,209.3) ..
+(263.1,210.1) ..
+controls (263.1,210.9) and (262.34,211.55) ..
+(261.41,211.55) ..
+controls (260.48,211.55) and (259.72,210.9) ..
+(259.72,210.1) -- cycle ;
+%Shape: Ellipse [id:dp03156593400590513]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (258.44,217.36) ..
+controls (258.44,216.56) and (259.2,215.91) ..
+(260.13,215.91) ..
+controls (261.07,215.91) and (261.82,216.56) ..
+(261.82,217.36) ..
+controls (261.82,218.16) and (261.07,218.81) ..
+(260.13,218.81) ..
+controls (259.2,218.81) and (258.44,218.16) ..
+(258.44,217.36) -- cycle ;
+%Shape: Ellipse [id:dp6428056825741797]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (257.19,225.03) ..
+controls (257.19,224.23) and (257.94,223.58) ..
+(258.88,223.58) ..
+controls (259.81,223.58) and (260.57,224.23) ..
+(260.57,225.03) ..
+controls (260.57,225.83) and (259.81,226.48) ..
+(258.88,226.48) ..
+controls (257.94,226.48) and (257.19,225.83) ..
+(257.19,225.03) -- cycle ;
+%Shape: Ellipse [id:dp1475873632921516]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (277.01,191.85) ..
+controls (277.01,191.05) and (277.76,190.4) ..
+(278.69,190.4) ..
+controls (279.63,190.4) and (280.38,191.05) ..
+(280.38,191.85) ..
+controls (280.38,192.65) and (279.63,193.3) ..
+(278.69,193.3) ..
+controls (277.76,193.3) and (277.01,192.65) ..
+(277.01,191.85) -- cycle ;
+%Shape: Ellipse [id:dp4429598972841515]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (276.17,197.36) ..
+controls (276.17,196.56) and (276.92,195.91) ..
+(277.86,195.91) ..
+controls (278.79,195.91) and (279.54,196.56) ..
+(279.54,197.36) ..
+controls (279.54,198.16) and (278.79,198.81) ..
+(277.86,198.81) ..
+controls (276.92,198.81) and (276.17,198.16) ..
+(276.17,197.36) -- cycle ;
+%Shape: Ellipse [id:dp6989263176245077]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (275.33,203.47) ..
+controls (275.33,202.67) and (276.09,202.02) ..
+(277.02,202.02) ..
+controls (277.95,202.02) and (278.71,202.67) ..
+(278.71,203.47) ..
+controls (278.71,204.27) and (277.95,204.92) ..
+(277.02,204.92) ..
+controls (276.09,204.92) and (275.33,204.27) ..
+(275.33,203.47) -- cycle ;
+%Shape: Ellipse [id:dp5884337821826009]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (274.56,210.37) ..
+controls (274.56,209.57) and (275.32,208.92) ..
+(276.25,208.92) ..
+controls (277.18,208.92) and (277.94,209.57) ..
+(277.94,210.37) ..
+controls (277.94,211.17) and (277.18,211.82) ..
+(276.25,211.82) ..
+controls (275.32,211.82) and (274.56,211.17) ..
+(274.56,210.37) -- cycle ;
+%Shape: Ellipse [id:dp5456914529153225]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (273.52,217.24) ..
+controls (273.52,216.44) and (274.27,215.79) ..
+(275.2,215.79) ..
+controls (276.14,215.79) and (276.89,216.44) ..
+(276.89,217.24) ..
+controls (276.89,218.04) and (276.14,218.69) ..
+(275.2,218.69) ..
+controls (274.27,218.69) and (273.52,218.04) ..
+(273.52,217.24) -- cycle ;
+%Shape: Ellipse [id:dp10200774997945894]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (272.4,225.15) ..
+controls (272.4,224.35) and (273.16,223.7) ..
+(274.09,223.7) ..
+controls (275.02,223.7) and (275.78,224.35) ..
+(275.78,225.15) ..
+controls (275.78,225.95) and (275.02,226.6) ..
+(274.09,226.6) ..
+controls (273.16,226.6) and (272.4,225.95) ..
+(272.4,225.15) -- cycle ;
+%Shape: Ellipse [id:dp09546155197155715]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (291.94,191.85) ..
+controls (291.94,191.05) and (292.69,190.4) ..
+(293.63,190.4) ..
+controls (294.56,190.4) and (295.31,191.05) ..
+(295.31,191.85) ..
+controls (295.31,192.65) and (294.56,193.3) ..
+(293.63,193.3) ..
+controls (292.69,193.3) and (291.94,192.65) ..
+(291.94,191.85) -- cycle ;
+%Shape: Ellipse [id:dp8888091900844011]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (291.52,197.24) ..
+controls (291.52,196.44) and (292.27,195.79) ..
+(293.21,195.79) ..
+controls (294.14,195.79) and (294.9,196.44) ..
+(294.9,197.24) ..
+controls (294.9,198.04) and (294.14,198.69) ..
+(293.21,198.69) ..
+controls (292.27,198.69) and (291.52,198.04) ..
+(291.52,197.24) -- cycle ;
+%Shape: Ellipse [id:dp6682650227662896]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (291.24,203.23) ..
+controls (291.24,202.43) and (292,201.78) ..
+(292.93,201.78) ..
+controls (293.86,201.78) and (294.62,202.43) ..
+(294.62,203.23) ..
+controls (294.62,204.03) and (293.86,204.68) ..
+(292.93,204.68) ..
+controls (292,204.68) and (291.24,204.03) ..
+(291.24,203.23) -- cycle ;
+%Shape: Ellipse [id:dp9294532115656315]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (290.68,210.5) ..
+controls (290.68,209.7) and (291.44,209.05) ..
+(292.37,209.05) ..
+controls (293.3,209.05) and (294.06,209.7) ..
+(294.06,210.5) ..
+controls (294.06,211.3) and (293.3,211.95) ..
+(292.37,211.95) ..
+controls (291.44,211.95) and (290.68,211.3) ..
+(290.68,210.5) -- cycle ;
+%Shape: Ellipse [id:dp5568966606864136]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (290.12,217.12) ..
+controls (290.12,216.32) and (290.88,215.67) ..
+(291.81,215.67) ..
+controls (292.74,215.67) and (293.5,216.32) ..
+(293.5,217.12) ..
+controls (293.5,217.92) and (292.74,218.57) ..
+(291.81,218.57) ..
+controls (290.88,218.57) and (290.12,217.92) ..
+(290.12,217.12) -- cycle ;
+%Shape: Ellipse [id:dp2121643224676708]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (289.7,225.03) ..
+controls (289.7,224.23) and (290.46,223.58) ..
+(291.39,223.58) ..
+controls (292.33,223.58) and (293.08,224.23) ..
+(293.08,225.03) ..
+controls (293.08,225.83) and (292.33,226.48) ..
+(291.39,226.48) ..
+controls (290.46,226.48) and (289.7,225.83) ..
+(289.7,225.03) -- cycle ;
+%Shape: Ellipse [id:dp9886700240195399]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (304.5,191.79) ..
+controls (304.5,190.99) and (305.25,190.34) ..
+(306.19,190.34) ..
+controls (307.12,190.34) and (307.87,190.99) ..
+(307.87,191.79) ..
+controls (307.87,192.59) and (307.12,193.24) ..
+(306.19,193.24) ..
+controls (305.25,193.24) and (304.5,192.59) ..
+(304.5,191.79) -- cycle ;
+%Shape: Ellipse [id:dp8920179824675918]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (304.8,197.19) ..
+controls (304.8,196.39) and (305.56,195.74) ..
+(306.49,195.74) ..
+controls (307.43,195.74) and (308.18,196.39) ..
+(308.18,197.19) ..
+controls (308.18,197.99) and (307.43,198.64) ..
+(306.49,198.64) ..
+controls (305.56,198.64) and (304.8,197.99) ..
+(304.8,197.19) -- cycle ;
+%Shape: Ellipse [id:dp2107726543746229]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (304.5,203.38) ..
+controls (304.5,202.58) and (305.25,201.93) ..
+(306.19,201.93) ..
+controls (307.12,201.93) and (307.87,202.58) ..
+(307.87,203.38) ..
+controls (307.87,204.18) and (307.12,204.83) ..
+(306.19,204.83) ..
+controls (305.25,204.83) and (304.5,204.18) ..
+(304.5,203.38) -- cycle ;
+%Shape: Ellipse [id:dp7703015900268393]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (304.65,210.17) ..
+controls (304.65,209.37) and (305.41,208.72) ..
+(306.34,208.72) ..
+controls (307.27,208.72) and (308.03,209.37) ..
+(308.03,210.17) ..
+controls (308.03,210.97) and (307.27,211.62) ..
+(306.34,211.62) ..
+controls (305.41,211.62) and (304.65,210.97) ..
+(304.65,210.17) -- cycle ;
+%Shape: Ellipse [id:dp012791866206312008]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (304.5,217.22) ..
+controls (304.5,216.42) and (305.25,215.77) ..
+(306.19,215.77) ..
+controls (307.12,215.77) and (307.87,216.42) ..
+(307.87,217.22) ..
+controls (307.87,218.02) and (307.12,218.67) ..
+(306.19,218.67) ..
+controls (305.25,218.67) and (304.5,218.02) ..
+(304.5,217.22) -- cycle ;
+%Shape: Ellipse [id:dp5121947850193356]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (304.34,224.99) ..
+controls (304.34,224.19) and (305.1,223.54) ..
+(306.03,223.54) ..
+controls (306.96,223.54) and (307.72,224.19) ..
+(307.72,224.99) ..
+controls (307.72,225.79) and (306.96,226.44) ..
+(306.03,226.44) ..
+controls (305.1,226.44) and (304.34,225.79) ..
+(304.34,224.99) -- cycle ;
+%Shape: Ellipse [id:dp9592402529849944]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (317.2,191.73) ..
+controls (317.2,190.93) and (317.95,190.28) ..
+(318.89,190.28) ..
+controls (319.82,190.28) and (320.57,190.93) ..
+(320.57,191.73) ..
+controls (320.57,192.53) and (319.82,193.18) ..
+(318.89,193.18) ..
+controls (317.95,193.18) and (317.2,192.53) ..
+(317.2,191.73) -- cycle ;
+%Shape: Ellipse [id:dp21535542685573428]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (317.89,197.24) ..
+controls (317.89,196.44) and (318.65,195.79) ..
+(319.58,195.79) ..
+controls (320.52,195.79) and (321.27,196.44) ..
+(321.27,197.24) ..
+controls (321.27,198.04) and (320.52,198.69) ..
+(319.58,198.69) ..
+controls (318.65,198.69) and (317.89,198.04) ..
+(317.89,197.24) -- cycle ;
+%Shape: Ellipse [id:dp43454667067156816]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (318.17,203.47) ..
+controls (318.17,202.67) and (318.93,202.02) ..
+(319.86,202.02) ..
+controls (320.79,202.02) and (321.55,202.67) ..
+(321.55,203.47) ..
+controls (321.55,204.27) and (320.79,204.92) ..
+(319.86,204.92) ..
+controls (318.93,204.92) and (318.17,204.27) ..
+(318.17,203.47) -- cycle ;
+%Shape: Ellipse [id:dp9701948912141243]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (318.93,210.24) ..
+controls (318.93,209.44) and (319.68,208.79) ..
+(320.62,208.79) ..
+controls (321.55,208.79) and (322.3,209.44) ..
+(322.3,210.24) ..
+controls (322.3,211.04) and (321.55,211.69) ..
+(320.62,211.69) ..
+controls (319.68,211.69) and (318.93,211.04) ..
+(318.93,210.24) -- cycle ;
+%Shape: Ellipse [id:dp5208741511315487]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (319.29,217.12) ..
+controls (319.29,216.32) and (320.05,215.67) ..
+(320.98,215.67) ..
+controls (321.91,215.67) and (322.67,216.32) ..
+(322.67,217.12) ..
+controls (322.67,217.92) and (321.91,218.57) ..
+(320.98,218.57) ..
+controls (320.05,218.57) and (319.29,217.92) ..
+(319.29,217.12) -- cycle ;
+%Shape: Ellipse [id:dp9960070270987895]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (320.13,224.91) ..
+controls (320.13,224.11) and (320.88,223.46) ..
+(321.82,223.46) ..
+controls (322.75,223.46) and (323.5,224.11) ..
+(323.5,224.91) ..
+controls (323.5,225.71) and (322.75,226.36) ..
+(321.82,226.36) ..
+controls (320.88,226.36) and (320.13,225.71) ..
+(320.13,224.91) -- cycle ;
+%Shape: Ellipse [id:dp08258824726895897]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (331.87,192.13) ..
+controls (331.87,191.33) and (332.62,190.68) ..
+(333.56,190.68) ..
+controls (334.49,190.68) and (335.25,191.33) ..
+(335.25,192.13) ..
+controls (335.25,192.93) and (334.49,193.58) ..
+(333.56,193.58) ..
+controls (332.62,193.58) and (331.87,192.93) ..
+(331.87,192.13) -- cycle ;
+%Shape: Ellipse [id:dp5433546755374361]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (333.51,197.36) ..
+controls (333.51,196.56) and (334.26,195.91) ..
+(335.19,195.91) ..
+controls (336.13,195.91) and (336.88,196.56) ..
+(336.88,197.36) ..
+controls (336.88,198.16) and (336.13,198.81) ..
+(335.19,198.81) ..
+controls (334.26,198.81) and (333.51,198.16) ..
+(333.51,197.36) -- cycle ;
+%Shape: Ellipse [id:dp7579405737158253]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (334.36,203.23) ..
+controls (334.36,202.43) and (335.12,201.78) ..
+(336.05,201.78) ..
+controls (336.98,201.78) and (337.74,202.43) ..
+(337.74,203.23) ..
+controls (337.74,204.03) and (336.98,204.68) ..
+(336.05,204.68) ..
+controls (335.12,204.68) and (334.36,204.03) ..
+(334.36,203.23) -- cycle ;
+%Shape: Ellipse [id:dp9171787071340098]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (335.51,210.5) ..
+controls (335.51,209.7) and (336.26,209.05) ..
+(337.19,209.05) ..
+controls (338.13,209.05) and (338.88,209.7) ..
+(338.88,210.5) ..
+controls (338.88,211.3) and (338.13,211.95) ..
+(337.19,211.95) ..
+controls (336.26,211.95) and (335.51,211.3) ..
+(335.51,210.5) -- cycle ;
+%Shape: Ellipse [id:dp5333550722820979]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (336.32,217.12) ..
+controls (336.32,216.32) and (337.07,215.67) ..
+(338,215.67) ..
+controls (338.94,215.67) and (339.69,216.32) ..
+(339.69,217.12) ..
+controls (339.69,217.92) and (338.94,218.57) ..
+(338,218.57) ..
+controls (337.07,218.57) and (336.32,217.92) ..
+(336.32,217.12) -- cycle ;
+%Shape: Ellipse [id:dp9796837086495329]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (337.99,225.03) ..
+controls (337.99,224.23) and (338.75,223.58) ..
+(339.68,223.58) ..
+controls (340.61,223.58) and (341.37,224.23) ..
+(341.37,225.03) ..
+controls (341.37,225.83) and (340.61,226.48) ..
+(339.68,226.48) ..
+controls (338.75,226.48) and (337.99,225.83) ..
+(337.99,225.03) -- cycle ;
+%Shape: Ellipse [id:dp7978787114926011]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (346.92,191.49) ..
+controls (346.92,190.69) and (347.68,190.04) ..
+(348.61,190.04) ..
+controls (349.54,190.04) and (350.3,190.69) ..
+(350.3,191.49) ..
+controls (350.3,192.29) and (349.54,192.94) ..
+(348.61,192.94) ..
+controls (347.68,192.94) and (346.92,192.29) ..
+(346.92,191.49) -- cycle ;
+%Shape: Ellipse [id:dp8545275834894772]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (348.6,197.24) ..
+controls (348.6,196.44) and (349.35,195.79) ..
+(350.28,195.79) ..
+controls (351.22,195.79) and (351.97,196.44) ..
+(351.97,197.24) ..
+controls (351.97,198.04) and (351.22,198.69) ..
+(350.28,198.69) ..
+controls (349.35,198.69) and (348.6,198.04) ..
+(348.6,197.24) -- cycle ;
+%Shape: Ellipse [id:dp9024642638477771]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (349.99,203.35) ..
+controls (349.99,202.55) and (350.75,201.9) ..
+(351.68,201.9) ..
+controls (352.61,201.9) and (353.37,202.55) ..
+(353.37,203.35) ..
+controls (353.37,204.15) and (352.61,204.8) ..
+(351.68,204.8) ..
+controls (350.75,204.8) and (349.99,204.15) ..
+(349.99,203.35) -- cycle ;
+%Shape: Ellipse [id:dp139500631439212]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (351.93,210.1) ..
+controls (351.93,209.3) and (352.69,208.65) ..
+(353.62,208.65) ..
+controls (354.55,208.65) and (355.31,209.3) ..
+(355.31,210.1) ..
+controls (355.31,210.9) and (354.55,211.55) ..
+(353.62,211.55) ..
+controls (352.69,211.55) and (351.93,210.9) ..
+(351.93,210.1) -- cycle ;
+%Shape: Ellipse [id:dp053214074310489634]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (353.76,217.24) ..
+controls (353.76,216.44) and (354.52,215.79) ..
+(355.45,215.79) ..
+controls (356.38,215.79) and (357.14,216.44) ..
+(357.14,217.24) ..
+controls (357.14,218.04) and (356.38,218.69) ..
+(355.45,218.69) ..
+controls (354.52,218.69) and (353.76,218.04) ..
+(353.76,217.24) -- cycle ;
+%Shape: Ellipse [id:dp40952769247810483]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (355.71,225.03) ..
+controls (355.71,224.23) and (356.47,223.58) ..
+(357.4,223.58) ..
+controls (358.33,223.58) and (359.09,224.23) ..
+(359.09,225.03) ..
+controls (359.09,225.83) and (358.33,226.48) ..
+(357.4,226.48) ..
+controls (356.47,226.48) and (355.71,225.83) ..
+(355.71,225.03) -- cycle ;
+%Shape: Ellipse [id:dp6883505384870545]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (360.46,191.49) ..
+controls (360.46,190.69) and (361.21,190.04) ..
+(362.15,190.04) ..
+controls (363.08,190.04) and (363.84,190.69) ..
+(363.84,191.49) ..
+controls (363.84,192.29) and (363.08,192.94) ..
+(362.15,192.94) ..
+controls (361.21,192.94) and (360.46,192.29) ..
+(360.46,191.49) -- cycle ;
+%Shape: Ellipse [id:dp8228987503250764]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (362.69,197) ..
+controls (362.69,196.2) and (363.45,195.55) ..
+(364.38,195.55) ..
+controls (365.31,195.55) and (366.07,196.2) ..
+(366.07,197) ..
+controls (366.07,197.8) and (365.31,198.45) ..
+(364.38,198.45) ..
+controls (363.45,198.45) and (362.69,197.8) ..
+(362.69,197) -- cycle ;
+%Shape: Ellipse [id:dp18713358672003966]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (364.92,203.35) ..
+controls (364.92,202.55) and (365.68,201.9) ..
+(366.61,201.9) ..
+controls (367.54,201.9) and (368.3,202.55) ..
+(368.3,203.35) ..
+controls (368.3,204.15) and (367.54,204.8) ..
+(366.61,204.8) ..
+controls (365.68,204.8) and (364.92,204.15) ..
+(364.92,203.35) -- cycle ;
+%Shape: Ellipse [id:dp879320396266565]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (367.44,210.5) ..
+controls (367.44,209.7) and (368.19,209.05) ..
+(369.12,209.05) ..
+controls (370.06,209.05) and (370.81,209.7) ..
+(370.81,210.5) ..
+controls (370.81,211.3) and (370.06,211.95) ..
+(369.12,211.95) ..
+controls (368.19,211.95) and (367.44,211.3) ..
+(367.44,210.5) -- cycle ;
+%Shape: Ellipse [id:dp8350403435643714]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (369.53,217) ..
+controls (369.53,216.2) and (370.28,215.55) ..
+(371.22,215.55) ..
+controls (372.15,215.55) and (372.91,216.2) ..
+(372.91,217) ..
+controls (372.91,217.8) and (372.15,218.45) ..
+(371.22,218.45) ..
+controls (370.28,218.45) and (369.53,217.8) ..
+(369.53,217) -- cycle ;
+%Shape: Ellipse [id:dp17300285054057252]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (372.46,224.67) ..
+controls (372.46,223.87) and (373.22,223.22) ..
+(374.15,223.22) ..
+controls (375.08,223.22) and (375.84,223.87) ..
+(375.84,224.67) ..
+controls (375.84,225.47) and (375.08,226.12) ..
+(374.15,226.12) ..
+controls (373.22,226.12) and (372.46,225.47) ..
+(372.46,224.67) -- cycle ;
+%Shape: Ellipse [id:dp6550411424766795]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (374.97,191.49) ..
+controls (374.97,190.69) and (375.73,190.04) ..
+(376.66,190.04) ..
+controls (377.59,190.04) and (378.35,190.69) ..
+(378.35,191.49) ..
+controls (378.35,192.29) and (377.59,192.94) ..
+(376.66,192.94) ..
+controls (375.73,192.94) and (374.97,192.29) ..
+(374.97,191.49) -- cycle ;
+%Shape: Ellipse [id:dp2665045036715892]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (377.48,197.12) ..
+controls (377.48,196.32) and (378.24,195.67) ..
+(379.17,195.67) ..
+controls (380.1,195.67) and (380.86,196.32) ..
+(380.86,197.12) ..
+controls (380.86,197.92) and (380.1,198.57) ..
+(379.17,198.57) ..
+controls (378.24,198.57) and (377.48,197.92) ..
+(377.48,197.12) -- cycle ;
+%Shape: Ellipse [id:dp211226681996602]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (379.86,203.23) ..
+controls (379.86,202.43) and (380.61,201.78) ..
+(381.54,201.78) ..
+controls (382.48,201.78) and (383.23,202.43) ..
+(383.23,203.23) ..
+controls (383.23,204.03) and (382.48,204.68) ..
+(381.54,204.68) ..
+controls (380.61,204.68) and (379.86,204.03) ..
+(379.86,203.23) -- cycle ;
+%Shape: Ellipse [id:dp5135394266621403]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (382.65,209.82) ..
+controls (382.65,209.02) and (383.4,208.37) ..
+(384.34,208.37) ..
+controls (385.27,208.37) and (386.02,209.02) ..
+(386.02,209.82) ..
+controls (386.02,210.62) and (385.27,211.27) ..
+(384.34,211.27) ..
+controls (383.4,211.27) and (382.65,210.62) ..
+(382.65,209.82) -- cycle ;
+%Shape: Ellipse [id:dp4800412429140355]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (386,217) ..
+controls (386,216.2) and (386.75,215.55) ..
+(387.68,215.55) ..
+controls (388.62,215.55) and (389.37,216.2) ..
+(389.37,217) ..
+controls (389.37,217.8) and (388.62,218.45) ..
+(387.68,218.45) ..
+controls (386.75,218.45) and (386,217.8) ..
+(386,217) -- cycle ;
+%Shape: Ellipse [id:dp9897837661968554]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (389.21,224.67) ..
+controls (389.21,223.87) and (389.96,223.22) ..
+(390.89,223.22) ..
+controls (391.83,223.22) and (392.58,223.87) ..
+(392.58,224.67) ..
+controls (392.58,225.47) and (391.83,226.12) ..
+(390.89,226.12) ..
+controls (389.96,226.12) and (389.21,225.47) ..
+(389.21,224.67) -- cycle ;
+%Shape: Ellipse [id:dp9164081127827948]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (387.39,191.49) ..
+controls (387.39,190.69) and (388.15,190.04) ..
+(389.08,190.04) ..
+controls (390.01,190.04) and (390.77,190.69) ..
+(390.77,191.49) ..
+controls (390.77,192.29) and (390.01,192.94) ..
+(389.08,192.94) ..
+controls (388.15,192.94) and (387.39,192.29) ..
+(387.39,191.49) -- cycle ;
+%Shape: Ellipse [id:dp5397824783956662]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (390.18,197.12) ..
+controls (390.18,196.32) and (390.94,195.67) ..
+(391.87,195.67) ..
+controls (392.8,195.67) and (393.56,196.32) ..
+(393.56,197.12) ..
+controls (393.56,197.92) and (392.8,198.57) ..
+(391.87,198.57) ..
+controls (390.94,198.57) and (390.18,197.92) ..
+(390.18,197.12) -- cycle ;
+%Shape: Ellipse [id:dp09820896087807829]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (393.53,203.35) ..
+controls (393.53,202.55) and (394.29,201.9) ..
+(395.22,201.9) ..
+controls (396.15,201.9) and (396.91,202.55) ..
+(396.91,203.35) ..
+controls (396.91,204.15) and (396.15,204.8) ..
+(395.22,204.8) ..
+controls (394.29,204.8) and (393.53,204.15) ..
+(393.53,203.35) -- cycle ;
+%Shape: Ellipse [id:dp9648161409230518]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (397.52,210.32) ..
+controls (397.52,209.52) and (398.28,208.87) ..
+(399.21,208.87) ..
+controls (400.14,208.87) and (400.9,209.52) ..
+(400.9,210.32) ..
+controls (400.9,211.12) and (400.14,211.77) ..
+(399.21,211.77) ..
+controls (398.28,211.77) and (397.52,211.12) ..
+(397.52,210.32) -- cycle ;
+%Shape: Ellipse [id:dp9189826271468595]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (401.35,216.88) ..
+controls (401.35,216.08) and (402.1,215.43) ..
+(403.04,215.43) ..
+controls (403.97,215.43) and (404.72,216.08) ..
+(404.72,216.88) ..
+controls (404.72,217.68) and (403.97,218.33) ..
+(403.04,218.33) ..
+controls (402.1,218.33) and (401.35,217.68) ..
+(401.35,216.88) -- cycle ;
+%Shape: Ellipse [id:dp356684240956189]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (405.67,224.67) ..
+controls (405.67,223.87) and (406.43,223.22) ..
+(407.36,223.22) ..
+controls (408.29,223.22) and (409.05,223.87) ..
+(409.05,224.67) ..
+controls (409.05,225.47) and (408.29,226.12) ..
+(407.36,226.12) ..
+controls (406.43,226.12) and (405.67,225.47) ..
+(405.67,224.67) -- cycle ;
+%Shape: Ellipse [id:dp30965018239062236]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (401.21,191.49) ..
+controls (401.21,190.69) and (401.96,190.04) ..
+(402.9,190.04) ..
+controls (403.83,190.04) and (404.58,190.69) ..
+(404.58,191.49) ..
+controls (404.58,192.29) and (403.83,192.94) ..
+(402.9,192.94) ..
+controls (401.96,192.94) and (401.21,192.29) ..
+(401.21,191.49) -- cycle ;
+%Shape: Ellipse [id:dp268329300327677]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (404,197) ..
+controls (404,196.2) and (404.75,195.55) ..
+(405.69,195.55) ..
+controls (406.62,195.55) and (407.38,196.2) ..
+(407.38,197) ..
+controls (407.38,197.8) and (406.62,198.45) ..
+(405.69,198.45) ..
+controls (404.75,198.45) and (404,197.8) ..
+(404,197) -- cycle ;
+%Shape: Ellipse [id:dp21056106596973323]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (407.63,203.23) ..
+controls (407.63,202.43) and (408.38,201.78) ..
+(409.32,201.78) ..
+controls (410.25,201.78) and (411,202.43) ..
+(411,203.23) ..
+controls (411,204.03) and (410.25,204.68) ..
+(409.32,204.68) ..
+controls (408.38,204.68) and (407.63,204.03) ..
+(407.63,203.23) -- cycle ;
+%Shape: Ellipse [id:dp9269572031249087]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (411.49,210.24) ..
+controls (411.49,209.44) and (412.25,208.79) ..
+(413.18,208.79) ..
+controls (414.11,208.79) and (414.87,209.44) ..
+(414.87,210.24) ..
+controls (414.87,211.04) and (414.11,211.69) ..
+(413.18,211.69) ..
+controls (412.25,211.69) and (411.49,211.04) ..
+(411.49,210.24) -- cycle ;
+%Shape: Ellipse [id:dp816663150550079]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (415.16,217) ..
+controls (415.16,216.2) and (415.92,215.55) ..
+(416.85,215.55) ..
+controls (417.78,215.55) and (418.54,216.2) ..
+(418.54,217) ..
+controls (418.54,217.8) and (417.78,218.45) ..
+(416.85,218.45) ..
+controls (415.92,218.45) and (415.16,217.8) ..
+(415.16,217) -- cycle ;
+%Shape: Ellipse [id:dp7731814355118924]
+\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (419.35,224.79) ..
+controls (419.35,223.99) and (420.11,223.34) ..
+(421.04,223.34) ..
+controls (421.97,223.34) and (422.73,223.99) ..
+(422.73,224.79) ..
+controls (422.73,225.59) and (421.97,226.24) ..
+(421.04,226.24) ..
+controls (420.11,226.24) and (419.35,225.59) ..
+(419.35,224.79) -- cycle ;
+%Straight Lines [id:da3000520596553806]
+\draw    (196.12,186.91) -- (168.03,233.62) ;
+%Straight Lines [id:da163813348699974]
+\draw    (168.03,233.62) -- (171.25,233.56) ;
+%Straight Lines [id:da5727664193245703]
+\draw    (196.12,186.91) -- (199.34,186.85) ;
+%Straight Lines [id:da6793044911060069]
+\draw    (440.92,233.12) -- (444.14,233.05) ;
+%Straight Lines [id:da7452026016611717]
+\draw    (413.8,187) -- (417.02,186.94) ;
+%Straight Lines [id:da7007647307003126]
+\draw    (417.02,186.94) -- (444.14,233.05) ;
+%Straight Lines [id:da9237803080397062]
+\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (179.76,177.9) -- (199.23,177.7) ;
+\draw [shift={(202.23,177.66)}, rotate = 539.39] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (6.25,-3) -- (0,0) -- (6.25,3) -- cycle    ;
+%Straight Lines [id:da8131104182423468]
+\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (179.76,177.9) -- (170.65,188.89) ;
+\draw [shift={(168.74,191.2)}, rotate = 309.65999999999997] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (6.25,-3) -- (0,0) -- (6.25,3) -- cycle    ;
+%Shape: Wave [id:dp5678827377050879]
+\draw  [color={rgb, 255:red, 229; green, 21; blue, 21 }  ,draw opacity=1 ][line width=1.5]  (309.6,198.6) ..
+controls (324.2,194.36) and (338.1,190.3) ..
+(338.1,185.6) ..
+controls (338.1,180.9) and (324.2,176.84) ..
+(309.6,172.6) ..
+controls (295,168.36) and (281.1,164.3) ..
+(281.1,159.6) ..
+controls (281.1,154.9) and (295,150.84) ..
+(309.6,146.6) ..
+controls (324.2,142.36) and (338.1,138.3) ..
+(338.1,133.6) ..
+controls (338.1,128.9) and (324.2,124.84) ..
+(309.6,120.6) ..
+controls (295,116.36) and (281.1,112.3) ..
+(281.1,107.6) ..
+controls (281.1,102.95) and (294.67,98.94) ..
+(309.08,94.75) ;
+%Straight Lines [id:da29341364388127156]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (309.8,100.6) -- (297.2,100.6) ;
+\draw [shift={(294.2,100.6)}, rotate = 360] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da5859632848227461]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (310,114.75) -- (297.2,114.63) ;
+\draw [shift={(294.2,114.6)}, rotate = 360.53999999999996] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da15254151544652794]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (310.6,107.2) -- (285,107.24) ;
+\draw [shift={(282,107.25)}, rotate = 359.9] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da97623530444903]
+\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (179.76,177.9) -- (179.8,158) ;
+\draw [shift={(179.8,155)}, rotate = 450.09] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (6.25,-3) -- (0,0) -- (6.25,3) -- cycle    ;
+%Straight Lines [id:da3776683501360716]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (310.2,140.6) -- (321.6,140.6) ;
+\draw [shift={(324.6,140.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da22435064621656453]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (310.6,126.6) -- (323.6,126.6) ;
+\draw [shift={(326.6,126.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da4117346036483176]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (309.8,134) -- (334.5,133.78) ;
+\draw [shift={(337.5,133.75)}, rotate = 539.48] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da4639690103049321]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (309.8,152.2) -- (297.2,152.2) ;
+\draw [shift={(294.2,152.2)}, rotate = 360] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da9776464579169482]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (310.2,165.8) -- (297.2,166.13) ;
+\draw [shift={(294.2,166.2)}, rotate = 358.57] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da2751823416687842]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (310.6,158.8) -- (284.4,159.34) ;
+\draw [shift={(281.4,159.4)}, rotate = 358.82] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da5393896354953414]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (309,192.6) -- (320.4,192.6) ;
+\draw [shift={(323.4,192.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da015970204232534035]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (309.4,178.6) -- (322.4,178.6) ;
+\draw [shift={(325.4,178.6)}, rotate = 180] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da6560045675946828]
+\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (309.6,186) -- (333.8,185.47) ;
+\draw [shift={(336.8,185.4)}, rotate = 538.74] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
+%Straight Lines [id:da6731118036698975]
+\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (249.92,200.08) -- (249.78,154.23) ;
+\draw [shift={(249.77,150.23)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
+%Straight Lines [id:da47217219479835637]
+\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (270.23,200.08) -- (270.23,154.23) ;
+\draw [shift={(270.23,150.23)}, rotate = 450] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
+%Straight Lines [id:da5501938249838205]
+\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (310.38,199.92) -- (310.24,154.23) ;
+\draw [shift={(310.23,150.23)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
+%Straight Lines [id:da0658558878821176]
+\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (330.23,200.08) -- (330.09,154.38) ;
+\draw [shift={(330.08,150.38)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
+%Straight Lines [id:da9765507457725142]
+\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (350.08,200.23) -- (349.94,154.54) ;
+\draw [shift={(349.92,150.54)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
+%Straight Lines [id:da6498342095486176]
+\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=1.5]    (290.38,200.08) -- (290.24,154.38) ;
+\draw [shift={(290.23,150.38)}, rotate = 449.82] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (9.29,-4.46) -- (0,0) -- (9.29,4.46) -- cycle    ;
 
 % Text Node
-\draw (134.77,155.14) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {$\mathbf{x}$};
-% Text Node
-\draw (183.93,136.77) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {$\mathbf{y}$};
-% Text Node
-\draw (145.06,72.2) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {\begin{minipage}[lt]{74.95912pt}\setlength\topsep{0pt}
+\draw (147.56,83.2) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {\begin{minipage}[lt]{84.35pt}\setlength\topsep{0pt}
 \begin{center}
-\textcolor[rgb]{0.82,0.01,0.11}{{\fontfamily{helvet}\selectfont Dressing Field's}}\\\textcolor[rgb]{0.82,0.01,0.11}{{\fontfamily{helvet}\selectfont Elctric Field}}
+\textcolor[rgb]{0.82,0.01,0.11}{{\fontfamily{helvet}\selectfont Elctric Field of the}}\\\textcolor[rgb]{0.82,0.01,0.11}{{\fontfamily{helvet}\selectfont Dressing Field (\textbf{E})}}
 \end{center}
@@
 % Text Node
-\draw (145.93,116.37) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {$\mathbf{z}$};
+\draw (358.46,156.94) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {\begin{minipage}[lt]{86.06pt}\setlength\topsep{0pt}
+\begin{center}
+\textcolor[rgb]{0.08,0.35,0.57}{{\fontfamily{helvet}\selectfont Magnetic Field (\textbf{B})}}
+\end{center}
+
+\end{minipage}};
 % Text Node
-\draw (347.46,140.94) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {\begin{minipage}[lt]{69.05196000000001pt}\setlength\topsep{0pt}
-\begin{center}
-\textcolor[rgb]{0.08,0.35,0.57}{{\fontfamily{helvet}\selectfont Magnetic Field}}
-\end{center}
-
-\end{minipage}};
+\draw (168,134.9) node [anchor=north west][inner sep=0.75pt]    {$z$};
+% Text Node
+\draw (154,175.9) node [anchor=north west][inner sep=0.75pt]    {$x$};
+% Text Node
+\draw (204.5,156.9) node [anchor=north west][inner sep=0.75pt]    {$y$};
+% Text Node
+\draw (441,208) node [anchor=north west][inner sep=0.75pt]   [align=left] {2DEG};
 
 \end{tikzpicture}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-06-29 paper/v1.0/sections/appendix_a.tex
Add apendix a to paper

The deriving process of solutions for Schrödinger equation with Hamiltonian of an electron in 2DEG (Eq. \ref{eq_1}) quite similar to that followed in Refs. \cite{husmi53,dini16}. We start with expanding the Hamiltonian for two-dimentional case
\begin{equation} \label{eq_a1}
  \hat{H}_e(t) = \frac{1}{2m_e}\left[
    \left(\hat{p}_x + eBy \right)^2 +
    \left(\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right)^2
  \right],
\end{equation}
and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$ both operators share same (simultaneous) eigen functions
$\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = m2\pi \hbar/L_x~,~ m \in \mathbb{Z}$.
Therefore we re-arrange the Hamiltonian using definition of canonical momentum in $y$-direction to derive
\begin{equation} \label{eq_a2}
    \hat{H}_e(t) = \frac{1}{2m_e}\left[
      \left({p}_x + eBy \right)^2 +
      \left(-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right)^2
    \right].
\end{equation}
We now define the \textit{center of the cyclotron orbit} along $y$ axis $y_0 \equiv {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 \equiv {eB}/{m_e}$. This leads to a new arangement of the Hamiltonian
\begin{equation} \label{eq_a3}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
      \frac{1}{2m_e}\bigg[
      -\hbar^2 \pdv[2]{\tilde{y}} & +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
      & +
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \bigg],
  \end{aligned}
\end{equation}
where we used a variable substitution $\tilde{y} = (y - y_0)$. Now we are assuming that the solutions for the time-dependent Schrödinger equation
\begin{equation} \label{eq_a4}
    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
\end{equation}
can present by the following form
\begin{equation} \label{eq_a5}
    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
    \bigg) \phi(\tilde{y},t),
\end{equation}
where $\phi(\tilde{y},t)$ is a function that need to be find to satisfy the following property
\begin{equation} \label{eq_a6}
    \bigg[
    \frac{m_e \omega_0^2}{2}\tilde{y}^2
    - {eE\tilde{y}}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}}
    - i \hbar \dv{t}
    \bigg]
    \phi(\tilde{y},t) = 0.
\end{equation}
If we turn off the strong dressing field ($E=0$), this equation leads to simple harmonic oscillator Hamiltonian
\begin{equation} \label{eq_a7}
     i \hbar \dv{\phi(\tilde{y},t)}{t} =
    \bigg[
    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    \bigg]
    \phi(\tilde{y},t).
\end{equation}
It is important to notice that we can identify the $S(t) \equiv eE\sin(\omega t)$ part as a external force act on the harmonic oscillator and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis.
\begin{equation} \label{eq_a8}
  \begin{aligned}
    i \hbar \dv{\phi(\tilde{y},t)}{t} =
    \bigg[
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    - \tilde{y}S(t)]
    \bigg]
    \phi(\tilde{y},t).
  \end{aligned}
\end{equation}

This system can be extacly solvable and we can solve the equation using the methods explained by Husimi \cite{husmi53} as follows. We introduce a time dependent shifted cordinate $ y' = \tilde{y} - \zeta(t)$ and perform following unitary trasformation
\begin{equation} \label{eq_a9}
    \phi(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t),
\end{equation}
and this yeilds
\begin{equation} \label{eq_a10}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        & -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
        & +
        \Big[
            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
        \Big]y' \\
        &
        +
        \Big[
            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
        \Big]
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Then we can restrict our $\zeta(t)$ function such that
\begin{equation} \label{eq_a11}
  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t)
\end{equation}
and that leads to
\begin{equation} \label{eq_a12}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
        - L(\zeta,\dot{\zeta},t)
    \bigg]\varphi(y',t)
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_a13}
  L(\zeta,\dot{\zeta},t) \equiv \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t)
\end{equation}
is the largrangian of a classical driven oscillator. To proceed further, another unitary trasform can be introduced as follows
\begin{equation} \label{eq_a14}
    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
\end{equation}
and subtiting Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yeilds
\begin{equation} \label{eq_a15}
    i \hbar \pdv{t} \chi(y',t)  =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
    \bigg] \chi(y',t).
\end{equation}
This is the well known Schrödinger equation of the quantum harmonic oscillator.
This allows us to identify with the well-known eigenfucntions (using Gauss-Hermite functions)
\begin{equation} \label{eq_a16}
  \chi_n(y) \equiv
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y) \quad \text{with}
  \quad
  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
\end{equation}
which are propositional to the Hermite polynomials $\mathcal{H}_n$, with eigenvalues
\begin{equation} \label{eq_a17}
  \varepsilon_n = \hbar \omega_0 \big(n + \frac{1}{2}\big)
  ~,~
  n \in \mathbb{Z}^{+}_0.
\end{equation}
Therefore we can identify the solutions of Eq.~(\ref{eq_a8}) as
\begin{equation} \label{eq_a18}
  \begin{aligned}
    \phi_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \varepsilon_nt +
    m_e\dot{\zeta(t)}\big(\tilde{y}-\zeta(t)\big) \\
     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg)
  \end{aligned}
\end{equation}
The set $\{\chi_n(x)\}$ functions forms a complete set and thus any general solution $\phi_(\tilde{y},t)$ can be expaned in terms of the solutions given in Eq.~(\ref{eq_a18}).

Finally we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$ and we can derive the solution for Eq.~(\ref{eq_a11})
\begin{equation} \label{eq_a19}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
\end{equation}
Subtiting solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we can obtain the set of wave functions with two different quantum number ($n$,$m$) that satisfy the Schrödinger eqution Eq.~(\ref{eq_a4})
\begin{equation} \label{eq_a20}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
    \chi_n\left[y - y_0 - \zeta(t)\right]
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \varepsilon_nt \\
    &
    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\
    & +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}

### 2021-06-30 paper/v1.0/sections/3_floquet_theory.tex
Add section 2 of paper

The general interpretations of physical systems are mostly derived using symmetry conditions in quantum theory. Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation of quantum systems occupying a discrete translational symmetry in configuration space. Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}. Examine the transport properties of systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by M. Wackerl \cite{wackerl20}. In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity in presence of a strong dressing field. Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyse our 2DEG system which is subjected to both a staionary magnetic field and a strong dressing field.

First we need to identify the \textit{quasienergies} and periodic \textit{Floquet modes} for derived wavefunctions in Eq.~(\ref{eq_2}). By factorizing the wavefunction into a linearly time dependent part and a peridic time dependend part, the quasienergies can be present as
\begin{equation} \label{eq_6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
which is only depend on single quantum number ($n$) and Floquet modes are given by
\begin{equation} \label{eq_7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) = &
    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x \\
     & +
     \frac{eE(y - y_0)}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg),
  \end{aligned}
\end{equation}
with
\begin{equation} \label{3.16}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)} ~ \text{and} ~
  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions. The detailed derivation can be found in Appendix B.

x

### 2021-06-30 paper/v1.0/sections/appendix_a.tex
Add section 2 of paper

@@
       \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
-    \bigg) \phi(\tilde{y},t),
+    \bigg) \vartheta(\tilde{y},t),
 \end{equation}
-where $\phi(\tilde{y},t)$ is a function that need to be find to satisfy the following property
+where $\vartheta(\tilde{y},t)$ is a function that need to be find to satisfy the following property
 \begin{equation} \label{eq_a6}
@@
     \bigg]
-    \phi(\tilde{y},t) = 0.
+    \vartheta(\tilde{y},t) = 0.
 \end{equation}
@@
 \begin{equation} \label{eq_a7}
-     i \hbar \dv{\phi(\tilde{y},t)}{t} =
+     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
     \bigg[
@@
     \bigg]
-    \phi(\tilde{y},t).
+    \vartheta(\tilde{y},t).
 \end{equation}
@@
   \begin{aligned}
-    i \hbar \dv{\phi(\tilde{y},t)}{t} =
+    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
     \bigg[
@@
     \bigg]
-    \phi(\tilde{y},t).
+    \vartheta(\tilde{y},t).
   \end{aligned}
@@
 \begin{equation} \label{eq_a9}
-    \phi(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t),
+    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t),
 \end{equation}
@@
   \begin{aligned}
-    \phi_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
+    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
      \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \varepsilon_nt +
@@
 \end{equation}
-The set $\{\chi_n(x)\}$ functions forms a complete set and thus any general solution $\phi_(\tilde{y},t)$ can be expaned in terms of the solutions given in Eq.~(\ref{eq_a18}).
+The set $\{\chi_n(x)\}$ functions forms a complete set and thus any general solution $\vartheta_(\tilde{y},t)$ can be expaned in terms of the solutions given in Eq.~(\ref{eq_a18}).
 

### 2021-06-30 paper/v1.0/sections/3_floquet_theory.tex
Add Appendix B paper

@@
 with
-\begin{equation} \label{3.16}
+\begin{equation} \label{eq_8}
   \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)} ~ \text{and} ~
@@
 \end{equation}
-It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions. The detailed derivation can be found in Appendix B.
-
-x
+It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
+Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in position space as
+\begin{equation} \label{eq_9}
+  \psi_{n,m}(x,y,t) =
+  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (x,y,t).
+\end{equation}
+Then performing Fourier trasform over the confined two-dimentional space $A=L_xL_y$, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
+\begin{equation} \label{eq_10}
+  \begin{aligned}
+    \phi_{n,m}(k_x,k_y,t)  = &
+    {\sqrt{L_x}}
+    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
+    & \times
+    \text{exp}\left(
+      i\xi
+      -ik_y  \qty[d\sin(\omega t) + y_0]
+    \right),
+  \end{aligned}
+\end{equation}
+where
+\begin{equation} \label{eq_11}
+  \tilde{\chi}_{n}\qty(k) =
+  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
+  \qty(\frac{1}{\kappa})^{1/2}
+  e^{-\frac{k^2}{2 \kappa^2}}
+  \mathcal{H}_{n} \qty(\frac{k}{\kappa})
+\end{equation}
+and
+\begin{equation} \label{eq_12}
+  b \equiv
+  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
+  d \equiv
+ \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
+\end{equation}
+For details of the formalism the authors refer to Appendix B.

### 2021-06-30 paper/v1.0/sections/appendix_b.tex
Add Appendix B paper

First define the time integral of Laggrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a $T=2\pi/\omega$ period as
\begin{equation} \label{eq_b1}
  \Delta_{\varepsilon} \equiv \frac{1}{T} \int_0^T dt' \; L(\zeta,\dot{\zeta},t'),
\end{equation}
and after performing the integral using Eq.~(\ref{eq_4}), we can obtain more simplified result:
\begin{equation} \label{eq_b2}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)}.
\end{equation}
Next define another paramter
\begin{equation} \label{eq_b3}
  \xi \equiv
  \int_0^t dt' \; L(\zeta,\dot{\zeta},t') -
  \Delta_{\varepsilon} t,
\end{equation}
and after simplying, this leads to
\begin{equation} \label{eq_b4}
  \xi =
  \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t),
\end{equation}
which is a periodic function in time with $2\omega$ frequency. Now using these  parmaters we can factorize the wavefunction Eq.~(\ref{eq_2}) as linearly time dependend part and periodic time dependend part as follows
\begin{equation} \label{eq_b5}
  \begin{aligned}
    \psi_{\alpha}(x,y,t)  = &
    \exp(\frac{i}{\hbar}\qty[-\varepsilon_nt + \Delta_{\varepsilon} t ])
    \frac{1}{\sqrt{L_x}} \chi_n\big(y - y_0 - \zeta(t)\big)
    \\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eEy}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta(t)}\big[y-\zeta(t)\big]
     + \int_0^{t}dt'L(\zeta,\dot{\zeta},t') - \Delta_{\varepsilon} t  \bigg]
     \bigg),
  \end{aligned}
\end{equation}
and this leads to seperate linear time dependent phase component as the quasienergies
\begin{equation} \label{eq_b6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon}
\end{equation}
while rest of the components as time-periodic Floquet modes
\begin{equation} \label{eq_b7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) \equiv &
    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x \\
     & +
     \frac{eE(y - y_0)}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg).
  \end{aligned}
\end{equation}

x

### 2021-07-01 paper/v1.0/sections/2_schrodinger_problem.tex
Add section 2 of paper
Add part2 of Appendix B paper

@@
 Here $L_{x,y}$ are dimention of the 2DEG surface, $\hbar$ is the reduced Planck constant, and $y_0 = -p_x/eB$ is the center of the cyclotron orbit along $y$ axis.
-$\chi_n$ are well known solutions(Gauss-Hermite functions) for Schrödinger equation of a stationary quantum harmonic oscillartor
+$\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillartor
 \begin{equation} \label{eq_3}
@@
 \end{equation}
-
-x
+The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and strong dressing field.
+Therefore we can accept that magnetotransport properties of 2DEG will be renormalized by the magnetic field as well as the dressing field.

### 2021-07-01 paper/v1.0/sections/appendix_a.tex
Add part2 of Appendix B paper

@@
 and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$ both operators share same (simultaneous) eigen functions
-$\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = m2\pi \hbar/L_x~,~ m \in \mathbb{Z}$.
+$\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = 2\pi \hbar m/L_x~,~ m \in \mathbb{Z}$.
 Therefore we re-arrange the Hamiltonian using definition of canonical momentum in $y$-direction to derive

### 2021-07-01 paper/v1.0/sections/appendix_b.tex
Add part2 of Appendix B paper

@@
+\subsection{Position space representation}
+
 First define the time integral of Laggrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a $T=2\pi/\omega$ period as
@@
 
-x
+\subsection{Momentum space representation}
+
+To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ for Eq.~(\ref{eq_7})
+\begin{equation} \label{eq_b8}
+  \begin{aligned}
+    \phi_{n,m}(k_x,k_y,t)  &=
+    \int_{-L_y/2}^{L_y/2} dy\; \exp(-i\qty[k_y - \gamma(t)]y)
+    \chi_{n}\qty[y - \mu(t)] \\
+     & \times
+     \frac{1}{\sqrt{L_x}}
+     \int_{-L_x/2}^{L_x/2} dx\;
+     \exp(-ik_x x)
+     \exp( \frac{i p_x }{\hbar}x ) \\
+     &
+     \times
+     \exp(
+      \frac{-i\gamma(t)}{\hbar}
+      y_0)
+     \exp(\frac{-i}{\hbar}
+     \qty[
+     m_e \dot{\zeta}(t) \zeta(t) - \xi
+     ]),
+  \end{aligned}
+\end{equation}
+where
+\begin{equation} \label{eq_b9}
+  \mu(t) \equiv \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0
+  \quad,\quad
+  \gamma(t) \equiv
+  \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
+\end{equation}
+Next using the identity \cite{bruus04}
+\begin{equation} \label{eq_b10}
+  \int_{L_x} dx\;
+  \exp( -ik_x x + \frac{i p_x }{\hbar}x ) =
+  L_x \delta_{k_x,\frac{p_x}{\hbar}},
+\end{equation}
+we can derive
+\begin{equation} \label{eq_b11}
+  \begin{aligned}
+    \phi_{n,m}(k_x,k_y,t)  =
+    \exp(
+     \frac{-i\gamma(t)}{\hbar}
+     y_0) &
+    \exp(\frac{-i}{\hbar}
+    \qty[
+    m_e \dot{\zeta}(t) \zeta(t) - \xi
+    ]) \\
+    & \times
+    \Phi_{n,m}(k_y,t)
+    \delta_{k_x,\frac{p_x}{\hbar}}.
+  \end{aligned}
+\end{equation}
+Here we defined $\Phi_{n,m}(k_y,t)$ as
+\begin{equation} \label{eq_b12}
+  \Phi_{n,m}(k_y,t) \equiv
+  \sqrt{L_x}
+  \int_{-L_y/2}^{L_y/2} dy\;
+  \chi_{n}\qty[y - \mu(t)]
+  \exp(
+    -i\qty[k_y - \gamma(t)]
+    y).
+\end{equation}
+Subtituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is large ($L_y \rightarrow \infty$), we can obtain
+\begin{equation} \label{eq_b13}
+  \Phi_{n,m}({k'_y} ,t) =
+  {\sqrt{L_x}} e^{-i {k'_y}\mu}
+  \int_{-\infty}^{\infty} dy'\;
+  \chi_{n}\qty(y')
+  \exp(-i{k'_y} y').
+\end{equation}
+We can identify that the integral represnts the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{bruus04} for the Fourier transform of Gauss-Hermite functions $\vartheta_n(x)$:
+\begin{equation} \label{eq_b14}
+  \mathcal{FT}[\vartheta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\vartheta_n(k/\kappa),
+\end{equation}
+Eq.~(\ref{eq_b13}) can be simplified as
+\begin{equation} \label{eq_b15}
+  \Phi_{n,m}({k'_y} ,t) =
+    \sqrt{L_x}e^{-i {k'_y}\mu}
+    \tilde{\chi}_{n}\qty({k'_y}),
+\end{equation}
+with
+\begin{equation} \label{eq_b16}
+  \tilde{\chi}_{n}\qty(k) =
+  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
+  \qty(\frac{1}{\kappa})^{1/2}
+  e^{-\frac{k^2}{2 \kappa^2}}
+  \mathcal{H}_{\alpha} \qty(\frac{k}{\kappa}).
+\end{equation}
+Subtitute Eq.~(\ref{eq_b15}) back in Eq.~(\ref{eq_b11}) and this leads to
+\begin{equation} \label{eq_b17}
+  \begin{aligned}
+    \phi_{n,m}(k_x,k_y,t)  = &
+    {\sqrt{L_x}}
+    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
+    & \times
+    \text{exp}\left(
+      i\xi
+      -ik_y  \qty[d\sin(\omega t) + \frac{\hbar k_x}{eB}]
+    \right),
+  \end{aligned}
+\end{equation}
+where
+\begin{equation} \label{eq_b18}
+  b \equiv
+  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
+  d \equiv
+ \frac{eE}{m_e(\omega_0^2 - \omega^2)},
+\end{equation}
+and it is necessary to notice that $k_x$ is quantized with $k_x = 2\pi m/L_x ~,~ m \in \mathbb{Z}$.

### 2021-07-01 paper/v1.0/sections/3_floquet_theory.tex
Corrections

@@
 It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
-Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in position space as
-\begin{equation} \label{eq_9}
-  \psi_{n,m}(x,y,t) =
-  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (x,y,t).
-\end{equation}
+
 Then performing Fourier trasform over the confined two-dimentional space $A=L_xL_y$, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
@@
 \end{equation}
-For details of the formalism the authors refer to Appendix B.
+For details of the formalism the authors refer to Appendix B. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
+\begin{equation} \label{eq_9}
+  \psi_{n,m}(k_x,k_y,t) =
+  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
+\end{equation}

### 2021-07-01 paper/v1.0/sections/4_floquet_fermi_golden.tex
Corrections

In this section we are going to derive the Floquet Fermi goldern rule for previously derived quantum Floquet states using $t-t'$ formalism \cite{bruus04}.

### 2021-07-01 paper/v1.0/sections/appendix_b.tex
Corrections

@@
 \end{equation}
-We can identify that the integral represnts the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{bruus04} for the Fourier transform of Gauss-Hermite functions $\vartheta_n(x)$:
+We can identify that the integral represnts the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{celeghini21} for the Fourier transform of Gauss-Hermite functions $\theta_n(x)$:
 \begin{equation} \label{eq_b14}
-  \mathcal{FT}[\vartheta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\vartheta_n(k/\kappa),
+  \mathcal{FT}[\theta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\theta_n(k/\kappa),
 \end{equation}

### 2021-07-01 paper/v1.0/sections/4_floquet_fermi_golden.tex
Add some bib

@@
-In this section we are going to derive the Floquet Fermi goldern rule for previously derived quantum Floquet states using $t-t'$ formalism \cite{bruus04}.
+In this section we are going to derive the Floquet Fermi goldern rule for previously derived quantum Floquet states using $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,peskin93}.

### 2021-07-01 paper/v1.0/sections/4_floquet_fermi_golden.tex
Add changes

--- 2021-07-01 paper/v1.0/sections/4_floquet_fermi_golden.tex
@@
-In this section we are going to derive the Floquet Fermi goldern rule for previously derived quantum Floquet states using $t-t'$ formalism \cite{bruus04}.
+In this section we are going to derive the Floquet Fermi goldern rule for previously derived quantum Floquet states using $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97}.

### 2021-07-01 paper/v1.0/sections/4_floquet_fermi_golden.tex
Add section 3 of paper

--- 2021-07-01 paper/v1.0/sections/4_floquet_fermi_golden.tex
@@
-In this section we are going to derive the Floquet Fermi goldern rule for previously derived quantum Floquet states using $t-t'$ formalism \cite{bruus04}.
+In Ref.
+\cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyse transport propeties in dressed quantum systems.
+However, this theory has not been applied for a dressed quantum Hall system and to identify magnetotransport properties in our system we use Floquet Fermi golden rule.
+With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive Floquet Fermi golden rule for our considered quantum Hall system as
+\begin{widetext}
+\begin{equation} \label{4.65}
+  \begin{aligned}
+    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{N} =
+    \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
+    \delta(\varepsilon - \varepsilon_{N})
+    \int_{-\infty}^{\infty} d k_1
+    &
+    J_l\qty(\frac{g\hbar}{eB}[{k}_x - k_1])
+    J_{l'}\qty(\frac{g\hbar}{eB}[{k}_x - k_1]) \\
+    & \times
+    \qty|
+    \int_{-\infty}^{\infty} dk_2 \;
+    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
+    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
+  \end{aligned}
+\end{equation}
+\end{widetext}

### 2021-07-02 paper/v1.0/sections/4_floquet_fermi_golden.tex
Add Appendix c paper

@@
 However, this theory has not been applied for a dressed quantum Hall system and to identify magnetotransport properties in our system we use Floquet Fermi golden rule.
-With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive Floquet Fermi golden rule for our considered quantum Hall system as
+With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
 \begin{widetext}
-\begin{equation} \label{4.65}
+\begin{equation} \label{eq_13}
   \begin{aligned}
@@
     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
+    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2,
   \end{aligned}
@@
 \end{widetext}
+where $J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C.
+In this study, the perturbation potential is assumed to be formed by an ensemble of randomly distributed impurities, since random impurities in a disorded metal is a better approximation for experimental results.
+The total  scattering potential in 2DEG is then given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.
+
+x

### 2021-07-02 paper/v1.0/sections/appendix_c.tex
Add Appendix c paper

The derivation of the Floquet Fermi golden rule for our quantum Hall system with the help of $t-t'$ formalism is given here in detail. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
\begin{equation} \label{eq_c1}
  \ket{\psi_{n,m}(t,t')} =
  \exp(-\frac{i}{\hbar}\varepsilon_{n} t)\ket{\phi_{n,m}(t')}.
\end{equation}
derived by seperating the aperiodic and periodic components of Eq.~(\ref{eq_12}), fullfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
\begin{equation} \label{eq_c2}
  i \hbar \pdv{t}\ket{\psi_{n,m}(t,t')} =
  H_F(t') \ket{\psi_{n,m}(t,t')},
\end{equation}
where \textit{Floquet Hamiltonian} defined as
\begin{equation} \label{eq_c3}
  H_F(t') \equiv
  H_e(t') - i\hbar \pdv{t'}.
\end{equation}
Next we can identify the the time evolution operator \cite{wackerl20} corresponding to the $t$-$t'$-Schrödinger equation given in Eq.~(\ref{eq_c2})
\begin{equation} \label{eq_c4}
  U_0(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\qty[t-t_0])
\end{equation}
and the advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time odering operatos.
Consider a time-independent total perturbation $V(\vb{r})$ switched on at the reference time $t=t_0$, then Schrödinger equation becomes

x

### 2021-07-03 paper/v1.0/sections/2_schrodinger_problem.tex
Add context to Appendix c

@@
 Using Landau gauge for the stationary magnetic field, we can represent it using vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
-These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan81,bruus04} and this leads to the time-dependent Hamiltonian
+These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04} and this leads to the time-dependent Hamiltonian
 \begin{equation} \label{eq_1}

### 2021-07-03 paper/v1.0/sections/appendix_c.tex
Add context to Appendix c

@@
 \end{equation}
-Next we can identify the the time evolution operator \cite{wackerl20} corresponding to the $t$-$t'$-Schrödinger equation given in Eq.~(\ref{eq_c2})
+Next we can identify the the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation
 \begin{equation} \label{eq_c4}
-  U_0(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\qty[t-t_0])
+  U_F(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\qty[t-t_0]),
 \end{equation}
-and the advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time odering operatos.
-Consider a time-independent total perturbation $V(\vb{r})$ switched on at the reference time $t=t_0$, then Schrödinger equation becomes
+and the advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time odering operatos \cite{wackerl20}.
+
+For our scenario, consider a time-independent total perturbation $V(\vb{r})$ which has been switched on at the reference time $t=t_0$, then the $t$-$t'$-Schrödinger equation becomes
+\begin{equation} \label{eq_c5}
+  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')} =
+  \qty[H_F(t') + V(\vb{r})]\ket{\Psi_{n,m}(t,t')},
+\end{equation}
+by introducing new wave function $\Psi_{n,m}$ for the system with the given total perturabation.
+If $t\leq t_0$, both solutions of the Schrödinger equations (Eq.~(\ref{eq_c2}) and Eq.~(\ref{eq_c5})) coincide
+\begin{equation} \label{eq_c6}
+  \ket{\psi_{n,m}(t,t')} =\ket{\Psi_{n,m}(t,t')} \quad
+  \text{when} \quad
+  t \leq t_0.
+\end{equation}
+Now move into the interaction picture representation \cite{bruus04,mahan00} of the $t$-$t'$-Floquet state
+\begin{equation} \label{eq_c7}
+  \ket{\Psi_{n,m}(t,t')}_I = U_0^{\dagger}(t,t_0;t')
+  \ket{\Psi_{n,m}(t,t')},
+\end{equation}
+and due to time independency, the perturbation in the interaction picture has the same form as Schrödinger picture
+\begin{equation} \label{eq_c8}
+  V_I(\vb{r}) = U_0^{\dagger}(t,t_0;t')V(\vb{r})U_0(t,t_0;t') =
+  V(\vb{r}).
+\end{equation}
+This leads to the $t$-$t'$-Schrödinger eqution in the interction picture
+\begin{equation} \label{eq_c9}
+  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')}_I =
+  V_I(\vb{r})\ket{\Psi_{n,m}(t,t')}_I,
+\end{equation}
+with the recursive solution \cite{bruus04,mahan00}
+\begin{equation} \label{eq_c10}
+  \begin{aligned}
+  \ket{\Psi_{n,m}(t,t')}_I = &\ket{\Psi_{n,m}(t_0,t')}_I \\
+  &+
+  \frac{1}{i\hbar}
+  \int_{t_0}^t dt_1 \;
+  V_I(\vb{r}) \ket{\Psi_{n,m}(t_1,t')}_I.
+  \end{aligned}
+\end{equation}
+Iterating the solution only upto the first order (Born approximation) we obtain
+\begin{equation} \label{eq_c11}
+  \begin{aligned}
+    \ket{\Psi_{n,m}(t,t')}_I \approx &\ket{\psi_{n,m}(t_0,t')} \\
+    &+
+    \frac{1}{i\hbar}
+    \int_{t_0}^t dt_1 \;
+    V_I(\vb{r}) \ket{\psi_{n,m}(t_0,t')}.
+  \end{aligned}
+\end{equation}
+In addition, since our Floquet states create a basis for composite space we can represent any solution using our Floquet states
+\begin{equation} \label{eq_c12}
+  \ket{\Psi_{n,m}(t,t')} = \sum_{\beta} a_{n,m\beta}(t,t')
+  \ket{\psi_{\beta}(t,t')}.
+\end{equation}
+Therefore we can derive a equation for this \textit{scattering amplitude} as
+\begin{equation} \label{eq_c13}
+  a_{n,m\beta}(t,t') =
+  \braket{\psi_{\beta}(t,t')}{\Psi_{n,m}(t,t')} =
+  -
+  \frac{i}{\hbar}
+  \int_{0}^t dt_1 \;
+  \bra{\psi_{\beta}(t_1,t')}
+  V(\vb{r}) \ket{\psi_{n,m}(t_1,t')}.
+\end{equation}
 

### 2021-07-03 paper/v1.0/sections/appendix_c.tex
Add context to Appendix c

@@
 \end{equation}
-In addition, since our Floquet states create a basis for composite space we can represent any solution using our Floquet states
+
+In addition, since our Floquet states create a basis we can represent any solution using these Floquet states
 \begin{equation} \label{eq_c12}
-  \ket{\Psi_{n,m}(t,t')} = \sum_{\beta} a_{n,m\beta}(t,t')
+  \ket{\Psi_{\alpha}(t,t')} = \sum_{\beta} a_{\alpha,\beta}(t,t')
   \ket{\psi_{\beta}(t,t')}.
 \end{equation}
-Therefore we can derive a equation for this \textit{scattering amplitude} as
+where we used a single notation to represent two quantum numbers; $\alpha \equiv (n_{\alpha},m_{\alpha})$ and $\beta \equiv (n_{\beta},m_{\beta})$.
+Then we can identify the \textit{scattering amplitude} as $a_{\alpha,\beta}(t,t') =
+\braket{\psi_{\beta}(t,t')}{\Psi_{\alpha}(t,t')}$ and this can evaluate with
 \begin{equation} \label{eq_c13}
-  a_{n,m\beta}(t,t') =
-  \braket{\psi_{\beta}(t,t')}{\Psi_{n,m}(t,t')} =
+  \begin{aligned}
+  a_{\alpha,\beta}(t,t') = &
+  \braket{\psi_{\beta}(t,t')}{\psi_{\alpha}(t,t')} \\
+  &+
+  \frac{1}{i\hbar}
+  \int_{t_0}^t dt_1 \;
+  \bra{\psi_{\beta}(t_1,t')}
+  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')}.
+  \end{aligned}
+\end{equation}
+Since the $t$-$t'$-Floquet states are orthonormal and assuming $t_0 = 0$ and $\alpha \neq \beta$ this leads to
+\begin{equation} \label{eq_c14}
+  a_{\alpha,\beta}(t,t') =
   -
@@
   \bra{\psi_{\beta}(t_1,t')}
-  V(\vb{r}) \ket{\psi_{n,m}(t_1,t')}.
+  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')}.
 \end{equation}
 
+Now consider a scattering event from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')}$ into another $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with constant quansienergy $\varepsilon$ which has been
+\begin{equation} \label{eq_c16}
+  \begin{aligned}
+  \psi_{\beta}(\vb{k'},t,t') &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
+  \phi_{\beta}(\vb{k'},t') \\
+  &
+  \longrightarrow
+  \Psi_{\alpha}(\vb{k},t,t') = \exp(-\frac{i}{\hbar}\varepsilon t)
+  \Phi_{\alpha}(\vb{k},t').
+  \end{aligned}
+\end{equation}
+\begin{figure}[b]
+  \includegraphics[scale=1.0]{figures/fig_2.pdf}
+  \caption{Scattering from $\ket{\psi_{\beta}(t,t')}$ to constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to scattering potential created by impurities.}
+  \label{fig_2}
+\end{figure}
+
 x

### 2021-07-04 paper/v1.0/sections/appendix_c.tex
Add contect to Appendix c

@@
 
-Now consider a scattering event from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')}$ into another $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with constant quansienergy $\varepsilon$ which has been
-\begin{equation} \label{eq_c16}
+Now consider a scattering event from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into another $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with constant quansienergy $\varepsilon$:
+\begin{equation} \label{eq_c15}
   \begin{aligned}
-  \psi_{\beta}(\vb{k'},t,t') &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
-  \phi_{\beta}(\vb{k'},t') \\
+  \ket{\psi_{\beta}(t,t')} &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
+  \ket{\phi_{\beta}(t')} \\
   &
   \longrightarrow
-  \Psi_{\alpha}(\vb{k},t,t') = \exp(-\frac{i}{\hbar}\varepsilon t)
-  \Phi_{\alpha}(\vb{k},t').
+  \ket{\Psi_{\alpha}(t,t')} = \exp(-\frac{i}{\hbar}\varepsilon t)
+  \ket{\Phi_{\alpha}(t')}.
   \end{aligned}
@@
 \end{figure}
+It is important to remember that a state of this considering system can be represented by two independent quantum numbers: $n$ represents the landau level and $m$ represents the qunatized momentum in $x$-direction.
+The scattering amplitutde for this scattering scenario can be calculated using the equation derived in Eq.~(\ref{eq_c14})
+\begin{equation} \label{eq_c16}
+  \begin{aligned}
+    a_{\alpha\beta}(t,t') =
+    -\frac{i}{\hbar}
+    \int_{0}^t dt_1 \;
+    e^{\frac{i}{\hbar}\qty(\varepsilon_{\beta} - \varepsilon)t_1}
+    \bra{\phi_{\beta}(t')}
+    V(\vb{r}) \ket{\phi_{\alpha}(t')},
+  \end{aligned}
+\end{equation}
+and assuiming for a long time $t \rightarrow \infty$, we can turn this integral into a delta distrubution
+\begin{equation} \label{eq_c17}
+  \begin{aligned}
+    a_{\alpha\beta}(t,t') =
+    -2\pi i \delta(\varepsilon_{\beta} - \varepsilon)Q,
+  \end{aligned}
+\end{equation}
+where $Q \equiv \bra{\phi_{\beta}(t')}
+V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using completeness properties we can re-write this as
+\begin{equation} \label{eq_c18}
+    Q =
+    \sum_{\vb{k}}\sum_{\vb{k'}}
+    \braket{\phi_{\beta}(t')}{\vb{k'}}
+    \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}
+    \braket{\vb{k}}{\phi_{\alpha}(t')},
+\end{equation}
+and seperating $x$ and $y$ directional momentums we can derive (we already assumed that $L_y \rightarrow \infty$)
+\begin{equation} \label{eq_c19}
+    Q =
+    \sum_{k_x}\sum_{{k'}_x}
+    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} dk_y d{k'}_y \;
+    V_{\vb{k'},\vb{k}}
+    \phi_{\beta}^{\dagger}(\vb{k'},t')
+    \phi_{\alpha}(\vb{k},t').
+\end{equation}
+with $V_{\vb{k'},\vb{k}} \equiv \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.
+
+Since the perturbation potential $V(\vb{r})$ is assumed to be formed by an ensemble of randomly distributed impurities, consider $N_{imp}$ identical impurities positioned at randomly distributed but fixed positions $\vb{r}_i$.
+Then scattering potential $V(\vb{r})$ is given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$
+\begin{equation} \label{eq_c20}
+  V(\vb{r}) \equiv
+  \sum_{i=1}^{N_{imp}}
+  \upsilon (\vb{r}-\vb{r}_i).
+\end{equation}
+Next we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of enerrgy such that the potential is zero on average.
+This model is characterized by \cite{akkermans10}
+\begin{subequations}
+\begin{equation} \label{eq_c21a}
+  \expval{\upsilon(\vb{r})}_{imp} =0
+\end{equation}
+\begin{equation} \label{eq_c21b}
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'})
+\end{equation}
+\end{subequations}
+where $\expval{\cdot}_{imp}$ denoted the average over realizations of the impurity disorder.
+In addition, this model assume that $\upsilon (\vb{r}-\vb{r'})$ only dependes on the position difference $|\vb{r}-\vb{r'}|$ and it decays with a characteristic leangth $r_c$.
+Since this study considers the case where the waveleagth of radiation or scattering electrons is much faster than $r_c$, it is a good approximation to make two-point correlation function to be
+\begin{equation} \label{eq_c22}
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'})
+\end{equation}
+and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can model approximately the total scattering potential as
+\begin{equation} \label{eq_c23}
+  V(\vb{r}) =
+  \sum_{i=1}^{N_{imp}}
+  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
+\end{equation}
+Then we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
+\begin{subequations}
+\begin{align}
+ V_{\vb{k'},\vb{k}} & =
+ \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
+ \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq_c24a} \\
+ & =
+ \sum_{i=1}^{N_{imp}}
+ \int_{-\infty}^{\infty} dy\; \bigg[
+ \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \\
+ & \times \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
+ \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \bigg] \label{eq_c24b} \\
+  & =
+ \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
+ e^{i(k'_y - k_y )y}
+ \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq_c24c}
+\end{align}
+\label{eqn:all-lines}
+\end{subequations}
 

### 2021-07-05 paper/v1.0/sections/appendix_c.tex
Add content to Appendix c

@@
 \end{subequations}
-where $\expval{\cdot}_{imp}$ denoted the average over realizations of the impurity disorder.
+where $\expval{\cdot}_{imp}$ denoted the average over realizations of the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
 In addition, this model assume that $\upsilon (\vb{r}-\vb{r'})$ only dependes on the position difference $|\vb{r}-\vb{r'}|$ and it decays with a characteristic leangth $r_c$.
@@
 \end{equation}
-and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can model approximately the total scattering potential as
+where $\Upsilon_{imp}$ is stregth of the delta potential and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}.
+Then we can model approximately the total scattering potential as
 \begin{equation} \label{eq_c23}
@@
 Then we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
-\begin{subequations}
+\begin{subequations} \label{eq_24}
 \begin{align}
@@
  e^{i(k'_y - k_y )y}
- \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq_c24c}
+ \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq_c24c}.
 \end{align}
-\label{eqn:all-lines}
 \end{subequations}
+Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs and assuming the total ncumber of scatterers $N_{imp}$ is macroscopically large, we can derive
+\begin{subequations} \label{eq_c25}
+  \begin{align}
+    V_{\vb{k'},\vb{k}}
+    & =
+    V_{k'_x,k_x}
+    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty} dy_i\;
+    e^{i\qty({k'}_y - k_y)y_i} \label{eq_c25a} \\
+    & =
+    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y), \label{eq_c25a}
+  \end{align}
+\end{subequations}
+where
+\begin{equation} \label{eq_c26}
+  V_{{k'}_x,k_x} \equiv
+  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x}.
+\end{equation}
+is a constant value for every $i$ impurity and $\eta_{imp}$ is number of impurities in a unit area. It is important to notice that $\ket{k_x} = e^{-ik_xx}$.
+
+Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25}) on Eq.~(\ref{eq_c19}), we obtain
+\begin{equation} \label{eq_c27}
+  \begin{aligned}
+    Q & =
+    \sum_{k_x}\sum_{{k'}_x}
+    {\eta_{imp} V_{{k'}_x,k_x}}
+    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} dk_y d{k'}_y \;
+    \delta({k'}_y - k_y)
+    \\
+    & \times
+    \sqrt{L_x}
+    \exp(
+      i{k'}_y  \qty[d\sin(\omega t) + {y'}_0]
+    )
+    \tilde{\chi}_{n_{\beta}}\qty({k'}_y -b\cos(\omega t))
+    \\
+    & \times
+    \sqrt{L_x}
+    \exp(
+      -ik_y  \qty[d\sin(\omega t) + y_0]
+    )
+    \tilde{\chi}_{n_{\alpha}}\qty(k_y -b\cos(\omega t)),
+  \end{aligned}
+\end{equation}
+and this can simplify as
+and this can re-write as
+\begin{equation} \label{eq_c28}
+  \begin{aligned}
+    Q =
+    \sum_{k_x}\sum_{{k'}_x}
+    {\eta_{imp} L_x V_{{k'}_x,k_x}} I,
+  \end{aligned}
+\end{equation}
+with
+\begin{equation} \label{eq_c29}
+  \begin{aligned}
+    I \equiv
+    \int_{-\infty}^{\infty} dk_y \;
+    \tilde{\chi}_{n_{\beta}}\qty(k_y -g\cos(\omega t)) &
+    \tilde{\chi}_{n_{\alpha}}\qty(k_y -g\cos(\omega t)) \\
+    & \times
+    \exp(
+      -ik_y  \qty[y_0 - {y'}_0  ]
+    ).
+  \end{aligned}
+\end{equation}
 

### 2021-07-05 paper/v1.0/sections/appendix_c.tex
Finalize Appendix c

@@
   \begin{aligned}
-    a_{\alpha\beta}(t,t') =
+    a_{\alpha\beta}(t') =
     -2\pi i \delta(\varepsilon_{\beta} - \varepsilon)Q,
@@
     & =
-    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y), \label{eq_c25a}
+    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y), \label{eq_c25b}
   \end{align}
@@
 
-Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25}) on Eq.~(\ref{eq_c19}), we obtain
+Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25}) on Eq.~(\ref{eq_c19}), we obtain (with changing varable $t' \rightarrow t'$)
 \begin{equation} \label{eq_c27}
@@
 and this can simplify as
-and this can re-write as
 \begin{equation} \label{eq_c28}
@@
     \int_{-\infty}^{\infty} dk_y \;
-    \tilde{\chi}_{n_{\beta}}\qty(k_y -g\cos(\omega t)) &
-    \tilde{\chi}_{n_{\alpha}}\qty(k_y -g\cos(\omega t)) \\
+    \tilde{\chi}_{n_{\beta}}\qty(k_y -b\cos(\omega t)) &
+    \tilde{\chi}_{n_{\alpha}}\qty(k_y -b\cos(\omega t)) \\
     & \times
@@
 \end{equation}
+To avoid the energy exchange from external strong field and electrons, the applied radiation should be a purely dressing field.
+Therefore, the only effect of the dressing field on 2DEG is the renormalization of the probability of elastic electron scattering within the same Landau level $(n_{\alpha} = n_{\beta} =N)$.
+This transform the Eq.~(\ref{eq_c29}) to
+\begin{equation} \label{eq_c30}
+    I =
+    \int_{-\infty}^{\infty} dk_y \;
+    \tilde{\chi}_{N}^2 \qty(k_y -b\cos(\omega t))
+    \exp(
+      -ik_y  \qty[y_0 - {y'}_0  ]
+    ).
+\end{equation}
+Using Fourier transform of Gauss-Hermite functions \cite{celeghini21} and convolution theorem \cite{arfken85,bracewell78} we can derive
+\begin{equation} \label{eq_c31}
+  \begin{aligned}
+    I =
+    {2\pi} &
+    \exp(b[{y'}_0 - y_0]\cos(\omega t)) \\
+    & \times
+    \int_{-\infty}^{\infty} dy \;
+    {\chi}_{N}\qty(y)
+    {\chi}_{N}\qty(y_0 - {y'}_0 - y).
+  \end{aligned}
+\end{equation}
+Therefore finally the scattering amplitude derived in Eq.~(\ref{eq_c17}) can be evaluated for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as
+\begin{equation} \label{eq_c32}
+  \begin{aligned}
+    a_{\alpha\beta}(k_x,k'_x,t)  =&
+    -2\pi i
+    \eta_{imp} L_x V_{{k'}_x,k_x}
+    \delta(\varepsilon_{N} - \varepsilon)\\
+    & \times
+    \exp(b[{y'}_0 - y_0]\cos(\omega t))\\
+    & \times
+    \int_{-\infty}^{\infty} dy \;
+    {\chi}_{N}\qty(y)
+    {\chi}_{N}\qty(y_0 - {y'}_0 - y),
+  \end{aligned}
+\end{equation}
+Since this scattering amplitude is time-periodic we can write this as a Fourier series expansion
+\begin{equation} \label{eq_c33}
+    a_{\alpha\beta}(k_x,k'_x,t) =
+    \sum_{l=-\infty}^{\infty} a^l_{\alpha\beta}(k_x,k'_x) e^{-il\omega t}.
+\end{equation}
+In addition, using Jacobi-Anger expansion \cite{cuyt08,abramowitz64}
+\begin{equation} \label{eq_c34}
+    e^{iz\cos(\theta)} = \sum_{l=-\infty}^{\infty} i^l J_l\qty(z) e^{-il\theta},
+\end{equation}
+where $J_l(z)$ are Bessel functions of the first kind with $l$-th integer order and we can re-write the Eq.~(\ref{eq_c32}) as folllows
+\begin{equation} \label{eq_c35}
+  \begin{aligned}
+    a_{\alpha\beta}(k_x,k'_x,t)  = &
+    \sum_{l=-\infty}^{\infty}
+    -2\pi i^{l+1}
+    \eta_{imp} L_x V_{{k'}_x,k_x}
+    \delta(\varepsilon_{N} - \varepsilon)\\
+    & \times
+    J_l\qty(b[{y'}_0 - y_0]) \\
+    & \times
+    \int_{-\infty}^{\infty} dy \;
+    {\chi}_{N}\qty(y)
+    {\chi}_{N}\qty(y_0 - {y'}_0 - y) e^{-il\omega t}
+  \end{aligned}
+\end{equation}
+and then the Fourier series component can be identified as
+\begin{equation} \label{eq_c36}
+  \begin{aligned}
+    a^l_{\alpha\beta}(k_x,k'_x) = &
+    -2\pi i^{l+1}
+    \eta_{imp} L_x V_{{k'}_x,k_x}\\
+    & \times
+    \delta(\varepsilon_{N} - \varepsilon)
+    J_l\qty(b[{y'}_0 - y_0])\\
+    & \times
+    \int_{-\infty}^{\infty} dy \;
+    {\chi}_{n_{\beta}}\qty(y)
+    {\chi}_{n_{\beta}}\qty(y_0 - {y'}_0 - y).
+  \end{aligned}
+\end{equation}
+Now define \textit{transition probability matrix}
+\begin{equation} \label{eq_c37}
+    \qty(A_{\alpha\beta})_{l,l'} \equiv
+    a^l_{\alpha\beta}\qty[a^{l'}_{\alpha\beta}]^{*},
+\end{equation}
+and this becomes
+\begin{equation} \label{eq_c38}
+  \begin{aligned}
+      \qty(A_{\alpha\beta})_{l,l'}(k_x,k'_x) = &
+      \qty[{ 2 \pi \eta_{imp} L_x |V_{{k'}_x,k_x}|}]^2
+      \delta^2(\varepsilon_{N} - \varepsilon) \\
+      & \times
+      J_l\qty(b[{y'}_0 - y_0]) J_{l'}\qty(g[{y'}_0 - y_0])\\
+      & \times
+      \qty|
+      \int_{-\infty}^{\infty} dy \;
+      {\chi}_{n_{\beta}}\qty(y)
+      {\chi}_{n_{\beta}}\qty(y_0 - {y'}_0 - y)|^2.
+  \end{aligned}
+\end{equation}
+Then desribing the square of the delta distribution using following procedure \cite{dini16,kibis14}
+\begin{equation} \label{eq_c39}
+    \delta^2(\varepsilon) =
+    \delta(\varepsilon)\delta(0) =
+    \frac{\delta(\varepsilon)}{2\pi \hbar}
+    \int_{-t/2}^{t/2} e^{i0\times t'/\hbar} dt'\; =
+    \frac{\delta(\varepsilon)t}{2\pi \hbar},
+\end{equation}
+and performing the time derivation of each matrix element yeild the \textit{transition amplitude matrix}:
+\begin{equation} \label{eq_40}
+  \begin{aligned}
+    \Gamma_{\alpha\beta}^{ll'}(k_x,k'_x) = &
+    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar} |V_{{k'}_x,k_x}|^2
+    \delta(\varepsilon_{\beta} - \varepsilon)\\
+    & \times
+    J_l\qty(b[{y'}_0 - y_0]) J_{l'}\qty(g[{y'}_0 - y_0]) \\
+    & \times
+    \qty|
+    \int_{-\infty}^{\infty} dy \;
+    {\chi}_{N}\qty(y)
+    {\chi}_{N}\qty(y_0 - {y'}_0 - y)|^2.
+  \end{aligned}
+\end{equation}
 
-x
+An impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2} = V_{imp}$ and the inverse scattering time matrix is the sum over all momentum over the transition probability matrix
+\begin{equation} \label{eq_41}
+    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{\alpha\beta} \equiv
+    \frac{1}{L_x} \sum_{{k'}_x}
+    \expval**{\Gamma_{\alpha\beta}^{ll'}({k'}_x,k_x)}_{imp}
+\end{equation}
+and applying the 1-dimentional momentum continuum limit $\sum_{{k'}_x} \longrightarrow {L_x}/{2\pi}\int d {k'}_x$ and this leads to
+\begin{widetext}
+\begin{equation} \label{eq_42}
+  \begin{aligned}
+    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{\alpha\beta} =
+    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar}
+    \frac{V_{imp}}{2\pi}
+    \delta(\varepsilon_{\beta} - \varepsilon)
+    \int_{-\infty}^{\infty} d {k'}_x &
+    J_l\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x])
+    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x]) \\
+    & \times
+    \qty|
+    \int_{-\infty}^{\infty} dy \;
+    {\chi}_{n_{\beta}}\qty(y)
+    {\chi}_{n_{\beta}}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x] - y)|^2.
+  \end{aligned}
+\end{equation}
+Using subtitution $k'_x = k_1$ and $y = {\hbar{k_2}}/{eB}$ finally we can derive our expression for the inverse scattering time matrix for $N$-th Landau
+level
+\begin{equation} \label{eq_43}
+  \begin{aligned}
+    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{N} =
+    \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
+    \delta(\varepsilon - \varepsilon_{N})
+    \int_{-\infty}^{\infty} d k_1
+    &
+    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
+    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
+    & \times
+    \qty|
+    \int_{-\infty}^{\infty} dk_2 \;
+    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
+    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
+  \end{aligned}
+\end{equation}
+\end{widetext}

### 2021-07-05 paper/v1.0/sections/5_inverse_scattering_time.tex
Add section 4 of paper

In Ref. \cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyse transport propeties in dressed quantum systems. However, this theory has not been applied for a dressed quantum Hall system and to identify magnetotransport properties in our system we use Floquet Fermi golden rule.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
\begin{widetext}
\begin{equation} \label{eq_13}
  \begin{aligned}
    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{N} =
    \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
    \delta(\varepsilon - \varepsilon_{N})
    \int_{-\infty}^{\infty} d k_1
    &
    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} dk_2 \;
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2,
  \end{aligned}
\end{equation}
\end{widetext}
where $J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C. In this study, the perturbation potential is assumed to be formed by an ensemble of randomly distributed impurities, since random impurities in a disorded metal is a better approximation for experimental results. The total  scattering potential in 2DEG is then given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$. Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.

Next we are going to analyse the contribution of the inverse scattering time matrix elements to the transport properies in 2DEG. The disorder in the system is not supposed to change the eigenenergies of the bare system \cite{wackerl20}, hence all off-diogonal elements of the self-energy were neglected and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport propeties
\begin{widetext}
  \begin{equation} \label{eq_14}
    \begin{aligned}
      \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N} =
      \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
      \delta(\varepsilon - \varepsilon_{N}) &
      \int_{-\infty}^{\infty} d k_1 \;
      J_0^2\qty(\frac{b\hbar}{eB}[{k}_x -  k_1])
      \\
      & \times
      \qty|
      \int_{-\infty}^{\infty} d k_2 \;
      {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
      {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
    \end{aligned}
  \end{equation}
Introduce a new parameter with physical meaning of scattering-induced broadening of the Landau level as \cite{dini16,endo09}
\begin{equation} \label{eq_15}
 \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N}
\end{equation}
and this leads to
\begin{equation} \label{eq_16}
 \begin{aligned}
   \Gamma^{00}_{N}(\varepsilon,k_x)  =
   \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
   \delta(\varepsilon - \varepsilon_{N}) &
   \int_{-\infty}^{\infty} d {k'}_x \;
   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x])
   \\
   & \times
   \qty|
   \int_{-\infty}^{\infty} dk_2 \;
   {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - k_2])|^2.
 \end{aligned}
\end{equation}
\end{widetext}
In addition, for the case of scattering within a same Landau level, one can present the delta distribution of the energy using the same physical interpretation \cite{dini16} as follows
\begin{equation} \label{eq_17}
 \delta(\varepsilon - \varepsilon_{N}) \approx
 \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)},
\end{equation}
and we write the central element of inverse scattering time matrix in more compact form
\begin{equation} \label{eq_18}
  \begin{aligned}
    \Gamma^{00}_{N}(\varepsilon,k_x)  &=
    \varrho
    \bigg[
    \int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
    & \times
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
    \bigg]^{-\frac{1}{2}},
  \end{aligned}
\end{equation}
where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$, $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
To analyze the contribution of dressing field on the scatering-induced broadening, normalized $N$-th Landau level scatering-induced broadening can be defined as
\begin{equation} \label{eq_19}
    \Lambda_N(k_x) \equiv
    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{0}(\varepsilon,k_x)\big|_{E=0}},
\end{equation}
and this leads to
\begin{widetext}
\begin{equation} \label{eq_20}
    \Lambda_N (k_x) =
    \qty[
    \frac
    {\int_{-\infty}^{\infty} d {k}_1 \;
    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    {\int_{-\infty}^{\infty} d {k}_1 \;
    \qty|
    \int_{-\infty}^{\infty} d{k}_2 \;
    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
    ]^{1/2}.
\end{equation}
\end{widetext}

Normalized energy band broadening against ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are given in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}). Here we can identify that we can change the each Landau level normalized energy broadening value using apllied electromagnetic field. When the applied field's intensity increase the energy broadening gets reduced which make changes in conductivity of 2DEG.
\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_3}
\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.45]{figures/fig_4}
\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}

x

### 2021-07-05 paper/v1.0/sections/5_inverse_scattering_time.tex
Add Appendix d paper

@@
 \begin{equation} \label{eq_15}
- \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N}
+ \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
 \end{equation}
@@
     \Lambda_N(k_x) \equiv
-    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{0}(\varepsilon,k_x)\big|_{E=0}},
+    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
 \end{equation}
@@
 Normalized energy band broadening against ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are given in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
+To make comparison we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
+In their study, they have assumed that the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.
+Therefore in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
 Here we can identify that we can change the each Landau level normalized energy broadening value using apllied electromagnetic field.
@@
 \end{figure}
-
-x

### 2021-07-05 paper/v1.0/sections/appendix_d.tex
Add Appendix d paper

In this section we are hoping to derive the current density operator for $N$-th Landau level. We already found the extact solution for our time depenedent Hamiltonian Eq.~(\ref{eq_1}) and we identified them as Floquet states with quesienergies Eq.~(\ref{eq_12}). The Floquet modes derived in Eq. Eq.~(\ref{eq_9}) can be represented as states using quantum number for the simplicity of notation as follows
\begin{equation} \label{eq_d1}
  \ket{\phi_{n,m}} \equiv \ket{n,k_x}
\end{equation}
Using above complete set of eigenstates of Floquet Hamiltonian Eq.~(\ref{eq_c3}) \cite{wackerl20,holthaus15,grifoni98} we can represent the single particle current operator's matrix element as
\begin{equation} \label{eq_d2}
  \qty(\vb{j})_{nm,n'm'} \equiv \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x},
\end{equation}
and particle current operator for our system \cite{mahan00,bruus04} by
\begin{equation} \label{eq_d3}
  \hat{\vb{j}} = \frac{1}{m} \qty(\hat{\vb{p}} - e\qty[\vb{A}_s + \vb{A}_d(t)]).
\end{equation}
where $m$ is mass of the considering particle.

First consider the transverse conductivity in $x$-direction and we can identify that $x$-directional current operator as
\begin{equation} \label{eq_d4}
  \hat{j}_x = \frac{1}{m} \qty(-i\hbar\pdv{x} + eBy).
\end{equation}
Now calculate the matrix elements of $x$-directional current operator in Floquet mode basis
\begin{equation} \label{eq_d5}
  \qty({j}_x)_{nm,n'm'} =
  \mel{n,k_x}{\;\frac{1}{m} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x}.
\end{equation}
Then evaluate these using Floquet modes derived in Eq.~(\ref{eq_7}) and obtain
\begin{equation} \label{eq_d6}
  \begin{aligned}
    \qty({j}_x)_{nm,n'm'} = &
    \frac{1}{{m}}
    \delta_{k_x,k'_x}
    \int dy \;
    \Big[
    \qty(\hbar k'_x + eBy) \\
    & \times
     \chi_{n}\big(y - y_0 - \zeta(t)\big)
    \chi_{n'}\big(y - y_0 - \zeta(t)\big)
    \Big].
  \end{aligned}
\end{equation}
Then let $y - y_0 - \zeta(t) = \bar{y}$ and we can derive
\begin{equation} \label{eq_d7}
  \begin{aligned}
    \qty({j}_x)_{nm,n'm'} =
    \frac{1}{{m}}
    \delta_{k_x,k'_x}
    \int d\bar{y} \;
    \Big[ &
    \qty(\hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)) \\
    & \times
    \chi_{n}(\bar{y})
    \chi_{n'}(\bar{y})
    \Big].
  \end{aligned}
\end{equation}
Using following integral identities of Floquet modes which are made up with  Gauss-Hermite functions \cite{vedenyapin11,szego59}
\begin{subequations} \label{eq_d8}
  \begin{align}
    \int d{y} \;
    \chi_{n}({y})
    \chi_{n'}({y}) &=
    \delta_{n',n} \\
    \int dy \;
    y
    \chi_{n}({y})
    \chi_{n'}({y}) &=
    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1}),
  \end{align}
\end{subequations}
we simplfy the matrix elements of $x$-directional current operator to
\begin{equation} \label{eq_d9}
  \begin{aligned}
    \qty({j}_x)_{nm,n'm'} =
    \frac{1}{{m}}
    \delta_{k_x,k'_x}
    eB
    \bigg[
    \bigg(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} & + \sqrt{\frac{n}{2}}
    \delta_{n',n-1}\bigg) \\
    &
    + \zeta(t) \delta_{n',n}
    \bigg]
  \end{aligned}
\end{equation}

Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore we evaluate the $s=0$ component of the Fourier series with
\begin{equation} \label{eq_d10}
    \qty({j}^x_{s=0})_{nm,n'm'} =
    \frac{eB}{{m}}
    \delta_{k_x,k'_x}
    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1}).
\end{equation}
For electric current operator we can apply the electron's charge and effective mass and this leads to
\begin{equation} \label{eq_d11}
    \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{elctron} =
    \frac{e^2B}{{m_e}}
    \delta_{k_x,k'_x}
    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1}).
\end{equation}

Next we consider the transverse conductivity in $y$-direction and we can identify that $y$-directional current operator as
\begin{equation} \label{eq_d12}
  \hat{j}_y = \frac{1}{m} \qty(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t)).
\end{equation}
Then the matrix elements of $y$-directional current operator in Floquet mode basis are derived as
\begin{equation} \label{eq_d13}
  \qty({j}_y)_{nm,n'm'} =
  \mel{n,k_x}{\;\frac{-1}{m} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))\;}{n',k'_x}.
\end{equation}
After following the same steps done for $x$-directional current operator, we can derive the $s=0$ component of matrix elements for $y$-directional electric current operator
\begin{equation} \label{eq_d14}
    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{elctron} =
    \frac{ie\hbar}{{m_e}}
    \delta_{k_x,k'_x}
    \qty[
    \sqrt{\frac{n}{2}} \delta_{n',n-1}
    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
    ].
\end{equation}

x

### 2021-07-06 paper/v1.0/sections/7_floquet_drude_conductivity.tex
Add section 5 paper

A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M. Wackerl in Ref.~\cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
\begin{equation} \label{eq_21}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg].
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ th Fourier component (see Appendix D) and white noise disorder averaged Green function matrix \cite{wackerl20,wackerlthesis20} respectvely defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ th Fourier component of the current operator is contributing to the conductivity. In addition $A$ is the area of the considering two-dimentionl system and $\lambda$ is a function that can be choose such that
\begin{equation} \label{eq_22}
    \lambda - \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \lambda + \frac{\hbar \omega}{2}
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states.

Then Eq.~(\ref{eq_21}) can be expanded in off resonant regime ($\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system, using only central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$
\begin{widetext}
\begin{equation} \label{7.2}
  \begin{aligned}
    \lim_{\omega \to 0}
    \text{Re}[{\sigma}^{xx}(0,\omega)] & =
    \frac{-1}{4\pi\hbar A}
    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \frac{1}{V_{k_x}} \sum_{k_x}
    \sum_{n}
    \mel{n,k_x}{
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r}_0 (\varepsilon) - \vb{G}^{a}_0 (\varepsilon)
    )
    }
    {n,k_x}
  \end{aligned}
\end{equation}
where $V_{k_x}$ is the volume of considering $x$-directional momentum space. 
\end{widetext}

 x

### 2021-07-06 paper/v1.0/sections/7_floquet_drude_conductivity.tex
Add more contect to section 5 paper

@@
 \end{equation}
-where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ th Fourier component (see Appendix D) and white noise disorder averaged Green function matrix \cite{wackerl20,wackerlthesis20} respectvely defined against the Floquet modes of the considering system.
+where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ th Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectvely defined against the Floquet modes of the considering system.
 Here we have assumed that only $s=0$ th Fourier component of the current operator is contributing to the conductivity.
-In addition $A$ is the area of the considering two-dimentionl system and $\lambda$ is a function that can be choose such that
+In addition $A$ is the area of the considering two-dimentionl system, partical distribution function is given by $f$ and $\lambda$ is a function that can be choose such that
 \begin{equation} \label{eq_22}
@@
     <
-    \lambda + \frac{\hbar \omega}{2}
+    \lambda + \frac{\hbar \omega}{2},
 \end{equation}
@@
 \begin{widetext}
-\begin{equation} \label{7.2}
+\begin{equation} \label{eq_23}
   \begin{aligned}
-    \lim_{\omega \to 0}
-    \text{Re}[{\sigma}^{xx}(0,\omega)] & =
+    {\sigma}^{xx} & =
     \frac{-1}{4\pi\hbar A}
@@
     }
-    {n,k_x}
+    {n,k_x},
   \end{aligned}
 \end{equation}
-where $V_{k_x}$ is the volume of considering $x$-directional momentum space. 
+where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evalute by considering each matrix elements seperatly
+\begin{equation} \label{eq_24}
+  \begin{aligned}
+    {\sigma}^{xx}  =
+    \frac{-1}{4\pi\hbar A}
+    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} & d\varepsilon
+    \qty(
+    -\frac{\partial f}{\partial \varepsilon})
+    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
+    \frac{1}{{V_x}^3} \sum_{{k_x}_1,{k_x}_2,{k_x}_3}
+    \sum_{n_1,n_2,n_3}
+    \\
+    & \times
+    \mel{n,k_x}{
+    {j}^x_0}
+    {n_1,{k_x}_1}
+    \mel{{n_1,{k_x}_1}}{
+    \qty(
+    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+    )}
+    {n_2,{k_x}_2} \\
+    & \times
+    \mel{n_2,{k_x}_2}{
+    {j}^x_0}
+    {n_3,{k_x}_3}
+    \mel{n_3,{k_x}_3}{
+    \qty(
+    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+    )
+    }
+    {n,k_x}.
+  \end{aligned}
+\end{equation}
+Since we can diagonalize the impurity averaged Green's function using unitary trasnformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Ref.~\cite{wackerl20,wackerlthesis20,tsuji08} and we evaluate the matrix element of the differece between retarded and advanced Green's functions
+\begin{equation} \label{eq_25}
+  \mel{{n_1,{k_x}_1}}{
+  \vb{T}^{\dagger}
+  \qty(
+  \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+  )\vb{T}}
+  {n_2,{k_x}_2} =
+  \qty[
+  \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+  \delta_{n_1,n_2}\delta_{{k_x}_1,{k_x}_2}}
+  {
+  \qty(
+  \frac{1}{\hbar}\varepsilon -
+  \frac{1}{\hbar}\varepsilon_{n_1}
+  )^2
+  + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
+  }],
+\end{equation}
+and
+\begin{equation} \label{eq_26}
+  \mel{{n_3,{k_x}_3}}{
+  \vb{T}^{\dagger}
+  \qty(
+  \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+  )\vb{T}}
+  {n,{k_x}} =
+  \qty[
+  \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+  \delta_{n_3,n}\delta_{{k_x}_3,{k_x}}}
+  {
+  \qty(
+  \frac{1}{\hbar}\varepsilon -
+  \frac{1}{\hbar}\varepsilon_{n}
+  )^2
+  + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
+  }],
+\end{equation}
+using the retared self-energy matrix $\vb{\Sigma}^r$ which is the sum over all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
+Applying the matrix elements of electric current operator in Landau levels (see Appendix D) and
+results form Eq.~(\ref{eq_25}) and Eq.~(\ref{eq_26}) back into Eq.~(\ref{eq_24}) we obtain
+\begin{equation} \label{eq_27}
+  \begin{aligned}
+    {\sigma}^{xx}  =
+    \frac{-1}{4\pi\hbar A} &
+    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
+    \qty(
+    -\frac{\partial f}{\partial \varepsilon})
+    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
+    \sum_{n_1,n_2}
+    \\
+    & \times
+    \frac{e^2B}{{m_e}}
+    \qty(\sqrt{\frac{n+1}{2}} \delta_{n_1,n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n_1,n-1})
+    \qty[
+    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+    \delta_{n_1,n_2}}
+    {
+    \qty(
+    \frac{1}{\hbar}\varepsilon -
+    \frac{1}{\hbar}\varepsilon_{n_1}
+    )^2
+    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
+    }] \\
+    & \times
+    \frac{e^2B}{{m_e}}
+    \qty(\sqrt{\frac{n_2+1}{2}} \delta_{n,n_2+1} + \sqrt{\frac{n_2}{2}}
+    \delta_{n,n_2-1})
+    \qty[
+    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+    }
+    {
+    \qty(
+    \frac{1}{\hbar}\varepsilon -
+    \frac{1}{\hbar}\varepsilon_{n}
+    )^2
+    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
+    }],
+  \end{aligned}
+\end{equation}
+and the only non-zero term would be
+\begin{equation} \label{eq_28}
+  \begin{aligned}
+    \frac{-1}{4\pi\hbar A}
+    {\sigma}^{xx} & =
+    \frac{e^4B^2}{{{m_e}^2}}
+    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
+    \qty(
+    -\frac{\partial f}{\partial \varepsilon})
+    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
+    \qty(n+1)
+    \\
+    & \times
+    \qty[
+    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n+1}}
+    }
+    {
+    \qty(
+    \frac{1}{\hbar}\varepsilon -
+    \frac{1}{\hbar}\varepsilon_{n+1}
+    )^2
+    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n+1}}]^2
+    }]
+    \qty[
+    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n}}
+    }
+    {
+    \qty(
+    \frac{1}{\hbar}\varepsilon -
+    \frac{1}{\hbar}\varepsilon_{n}
+    )^2
+    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n}}]^2
+    }].
+  \end{aligned}
+\end{equation}
+Since the inverse scattering time matrix being equal to the diagonalized differece of the retared and advanced self-energy and on the diagonal the differece of the retarded and advanced Green's function is equal to the imaginary part of the retared self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property
+\begin{equation} \label{eq_29}
+  \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll} =
+  -2\text{Im}\qty[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}]^{ll}
+\end{equation}
+and using central element ($l=0$) of the inverse scattering time matrix we can modify the derived conductivity expression
+\begin{equation} \label{eq_30}
+    {\sigma}^{xx}   =
+    \frac{1}{\pi\hbar A}
+    \frac{e^4B^2}{{{m_e}^2}}
+    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
+    \qty(
+    -\frac{\partial f}{\partial \varepsilon})
+    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
+    \qty(n+1)
+    \qty[
+    \frac{\Gamma(\varepsilon_{n+1})
+    }
+    {
+    \qty(
+    \varepsilon_F - \varepsilon_{n+1}
+    )^2
+    + \Gamma^2(\varepsilon_{n+1})
+    }]
+    \qty[
+    \frac{\Gamma(\varepsilon_{n})
+    }
+    {
+    \qty(
+    \varepsilon_F - \varepsilon_{n}
+    )^2
+    + \Gamma^2(\varepsilon_{n})
+    }],
+\end{equation}
 \end{widetext}
-
- x
+with $\Gamma(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
+We already identited that the inverse scattering time matrix's central element is not $k_x$ dependent we can get the sum over all available momentum space in $x$ direction.
+However by considering the condition that the center of the force of the oscillator $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify
+\begin{equation} \label{eq_31}
+ -\frac{m_e\omega_0 Ly}{2\hbar} \leq k_x \leq \frac{m_e\omega_0 Ly}{2\hbar}.
+\end{equation}
+Then using Fermi-Dirac distribution as our partical distribution function ($f$) for this system
+\begin{equation} \label{eq_31}
+  f(\varepsilon) = \frac{1}{\qty[\exp(\varepsilon - \varepsilon_F)/k_B T]+1}
+\end{equation}
+where $k_B$ is Botlzmann constant, $T$ is absolute tempurature and $\varepsilon_F$ is Fermi energy of the system.
+Considering the above distribution with extreamly low tempurature conditions we can appromixate
+\begin{equation} \label{eq_32}
+  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F)
+\end{equation}
+and by letting $\lambda = \varepsilon_F$, the expression for conductivity leads to
+\begin{equation} \label{eq_33}
+  \begin{aligned}
+    {\sigma}^{xx}  =
+    \frac{e^2}{\hbar}
+    \frac{1}{\pi A}
+    \sum_{n} &
+    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}} \\
+    &\times
+    \qty[
+      \frac{1}
+      {
+        1 + \qty(\frac{X_F - n -1}{\gamma_{n+1}})^2
+      }
+    ]
+    \qty[
+      \frac{1}
+      {
+        1 + \qty(\frac{X_F - n}{\gamma_{n}})^2
+      }
+    ],
+  \end{aligned}
+\end{equation}
+where $X_F \equiv ({\varepsilon_F}/{\hbar \omega_0} - {1}/{2})$
+and
+$\gamma_n \equiv {\Gamma(\varepsilon_n)}/{\hbar \omega_0}$.
+Same as above derivation we can derive the transverse conductivity in $y$-direction by using the current operator derived in Appendix D
+\begin{equation} \label{eq_34}
+  \begin{aligned}
+    {\sigma}^{yy} =
+    \frac{e^2}{\hbar}
+    \frac{1}{\pi A}
+    \frac{1}{e^2B^2} &
+    \sum_{n}
+    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}} \\
+    & \times
+    \qty[
+      \frac{1}
+      {
+        1 + \qty(\frac{X_F - n -1}{\gamma_{n+1}})^2
+      }
+    ]
+    \qty[
+      \frac{1}
+      {
+        1 + \qty(\frac{X_F - n}{\gamma_{n}})^2
+      }
+    ].
+  \end{aligned}
+\end{equation}

### 2021-07-07 paper/v1.0/sections/8_manipulate_conductivity.tex
Add section 6 paper

To identify the behaviour of the transverse conductivity of the quantum Hall systems with external dressing field we can derive a expression for a normalized
transverse conductivity as a function of fermi energy $X_F$ and intensity of the dressing field $I$. Here we have normalized the conductivity using the natural conductivity of least Landau level.
\begin{equation} \label{eq_36}
  \begin{aligned}
    \sigma^{xx}(X_F,I) = &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ]
  \end{aligned}
\end{equation}
Using above expression we can analyse the changes can be done to the transverse conductivity in 2DEG using external dressing field. As given in Fig.~\ref{fig:8.1} and \ref{fig:8.2} we can manipulate the transverse conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system. When the applied field's intensity increase the broadening of energy bands of Landau levels get reduced and simulaniously the transverse conductivity also get low value for all the regions except the peak point of the energy band. Using this manipulation we can make more narrow or wide the conductivity regions. Since Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for optoelectonic applications \cite{dini16}. Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_5}
\caption{\label{fig_1} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.55]{figures/fig_6}
\caption{\label{fig_1} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$. In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
\end{figure}

### 2021-07-07 paper/v1.0/sections/8_manipulate_conductivity.tex
Change figures

@@
 Using above expression we can analyse the changes can be done to the transverse conductivity in 2DEG using external dressing field.
-As given in Fig.~\ref{fig:8.1} and \ref{fig:8.2} we can manipulate the transverse conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system.
+As given in Fig.~\ref{fig_4} and \ref{fig_5} we can manipulate the transverse conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system.
 When the applied field's intensity increase the broadening of energy bands of Landau levels get reduced and simulaniously the transverse conductivity also get low value for all the regions except the peak point of the energy band.
@@
 \includegraphics[scale=0.55]{figures/fig_5}
-\caption{\label{fig_1} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
+\caption{\label{fig_4} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
@@
 \includegraphics[scale=0.55]{figures/fig_6}
-\caption{\label{fig_1} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_5} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.

### 2021-07-08 paper/v1.0/sections/8_manipulate_conductivity.tex
Add context to section 6

@@
-To identify the behaviour of the transverse conductivity of the quantum Hall systems with external dressing field we can derive a expression for a normalized
+To identify the characteristics of the transverse conductivity of the quantum Hall systems with external dressing field, first we can derive a expression for a normalized
 transverse conductivity as a function of fermi energy $X_F$ and intensity of the dressing field $I$. Here we have normalized the conductivity using the natural conductivity of least Landau level.
@@
 \end{equation}
-Using above expression we can analyse the changes can be done to the transverse conductivity in 2DEG using external dressing field.
+We use this expression to illustrate the changes that can be done to the transverse conductivity in 2DEG using external dressing field.
 As given in Fig.~\ref{fig_4} and \ref{fig_5} we can manipulate the transverse conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system.
-When the applied field's intensity increase the broadening of energy bands of Landau levels get reduced and simulaniously the transverse conductivity also get low value for all the regions except the peak point of the energy band.
-Using this manipulation we can make more narrow or wide the conductivity regions.
-Since Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for optoelectonic applications \cite{dini16}.
-Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
+For a given dressing field intesity, the transverse conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values.
+Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not align with any of the Landau level energy values.
+In contrast, on Landau levels conductivity can achieve very high values compared to other areas and as illustrates on Fig.~\ref{fig_4} the peak value of transverse conductivity on each Landau level gets increase with the Landau level number.
+
 \begin{figure}[t]
@@
 \end{figure}
+
+Considering the effect of the external dressing field on transverse conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels.
+However the peak value of the conductivity at each Landau level has the same value as the undressed system.
+This demostrate that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
+These characteristics are align with results demostrated by K.
+Dini et al.\cite{dini16} and as they remarked since the Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for optoelectonic applications.
+Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
+Furthermore we can distinguish that the shapes and behavoiur of the conductivity regions illustrated in Fig.~\ref{fig_4} and \ref{fig_5} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+This is due to the selection of the conventional transverse conductivity theory of 2DEG from Ref.~\cite{ando74,ando82}.
+The semi-elliptical conductivity regions illustrated in Ref.~\cite{dini16,ando74,ando82}, have less consistance with the experimentally observed Landau levels representation \cite{endo09}.
+In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result represented by A.
+Endo et al.
+\cite{endo09}.
+The description of conductivities of quantum Hall systems demostrated in Ref.~\cite{endo09} has excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range.
+However they have not consider about the tunability that can be achived with the external strong dressing field.
+In this analysis we account both magnetic and dressing field effects that can be applied into the transport properties of 2DEG and we have presented a more generalized theory.
+As a concluding remark, in this study we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the trasport properties of quantum Hall syatems.

### 2021-07-08 paper/v1.0/abstract.tex
Change abstract paper

@@
-Interactions between light and matter have dragged research attention in the fields of optoelectronics, sensing, energy harvesting, quantum computing, bio-information, and in many branches of recent technologies.
-For many years, the foremost aims for examing the characteristics of dressed fermion systems were focused on the different types of atomic and molecular arrangements.
-These researches of extreme electron-light engagements introduced an astonishing scope of twentieth-century physics namely quantum optic physics.
+A generalized mathematiocal model for the transport properties of  systems exposed to a stationary magnetic and a strong electromagnetic field is presented.
+The new formulation, which is applicable to the two dimentional dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity method.
+We model our system as a two dimentional electron gas (2DEG) which interact with two external fields.
+To incorporate the strong light coupling with the 2DEG, we utilize the Floquet theory to analyse the effect nonperturbatively.
+Moreover, the Floquet Fermi "golden rule" is adopted to explore the scattering effects for Floquet states in disordered quantum Hall system.
+Based on our fully analytical expression and paticular graphical representations, we demostrate
+that the characteristics of conductivities in two dimentional quantum Hall systems can be manipulated using a dressed field.
+The outcomes are well align with theoritical descriptions which are already well-suited with experimental results at the same time our theory provide more generalized analysis on the properties of conductivity in quantum Hall systems.
+Thus, this model more realistically describes that how to use a external strong radiation  as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectonic devices.

### 2021-07-12 paper/v1.0/abstract.tex
Change abstract paper

--- 2021-06-27 paper/v1.0/abstract.tex
@@
-Interactions between light and matter have dragged research attention in the fields of optoelectronics, sensing, energy harvesting, quantum computing, bio-information, and in many branches of recent technologies.
-For many years, the foremost aims for examing the characteristics of dressed fermion systems were focused on the different types of atomic and molecular arrangements.
-These researches of extreme electron-light engagements introduced an astonishing scope of twentieth-century physics namely quantum optic physics.
+A generalized mathematical model for the transport properties of systems exposed to a stationary magnetic and a strong electromagnetic field is presented.
+The new formulation, which applies to the two-dimensional dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity method.
+We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields.
+To incorporate the strong light coupling with the 2DEG, we utilize the Floquet theory to analyze the effect non perturbatively.
+Moreover, the Floquet Fermi "golden rule" is adopted to explore the scattering effects for Floquet states in disordered quantum Hall systems.
+Based on our fully analytical expression and particular graphical representations, we demonstrate
+that the characteristics of conductivities in two-dimensional quantum Hall systems can manipulate using a dressed field.
+The outcomes align with theoretical descriptions which are already well-suited with experimental results at the same time our theory provides a more generalized analysis on the properties of conductivity in quantum Hall systems.
+Thus, this model more realistically describes that how to use external strong radiation as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectronic devices.

### 2021-07-16 paper/v1.0/sections/1_introduction.tex
Add introduction paper

@@
-Interactions between light and matter have dragged research attention in the fields of optoelectronics, sensing, energy harvesting, quantum computing, bio-information, and in many branches of recent technologies.
-For many years, the foremost aims for examing the characteristics of dressed fermion systems were focused on the different types of atomic and molecular arrangements.
-These researches of extreme electron-light engagements introduced an astonishing scope of twentieth-century physics namely quantum optic physics.
+Manipulating physical systems as a consequence of light engagements introduced an astonishing scope of twentieth-century physics namely quantum optics [15].
+Quantum optics have dragged research attention in the disciplines of optoelectronics [1,2,3], sensing [4,5,6], energy harvesting [7,8], quantum computing [9,10,11], bio-information [12,13], and abundant affiliates of recent technologies [14].
+The studies on quantum optics of nanostructures were centered on metamaterials [28,34], quantum plasmonic effects [27,33], lasers and amplifiers [29,30], quantum cavity physics [31,32].
+However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics [16-24].
+The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance [35].
+Among these works, most studies have considered the driving field as a perturbative field [18,20] that is not applicable for systems under high-intensity illumination [24,25].
+When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be consider gets increase.
+Then a more accurate and powerful concept need to be adopt and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) [18,36,37].
+On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
+A theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref.
+[22,18,24] where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref.
+[24], introducing a novel type of Green’s functions namely four-times Green’s functions.
+As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nano-structures by an intense dressing field.
 
-On the other hand, in nanostructures that are applicable in electronic devices, the investigations with the help of quantum optic were centered on polaritonic and exciton influences on nanostructures and material characteristics of dressed electrons in two-dimensional(2D) materials and quantum wires.
-When considering the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
+On the other hand, quantum Hall effect [39] observed for two-dimentional fermions systems at low temperatures under strong staionary magnetic field manifest remarkable magneto-transport behaviours and transport properties of these systems attracted many researches attention in experimentally [40,41,42] and theoretically [43,44,45,46,47].
+Akira Endo et al.
+[47] previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoritical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results [47].
 
-Therefore, transport properties of nanostructures exposed to a high intensity periodic electromagnetic fields have been explored theoretically in this study.
-The dressing field is analyzed non perturbatively using the Floquet theory whilst the probing field is examined perturbatively by applying the linear response method using the Kubo formula.
-The general Floquet-Drude conductivity has been derived in a fully closed analytical form in most recent research [1,2], introducing a novel type of Green’s functions namely four-times Green’s functions.
-As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nanostructures by an intense dressing field.
-From an empirical sense, this study applies directly to various nanostructures illuminated by a high-intensity electromagnetic field.
-In this research we have developed a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field and that will enable efficient manipulation of transport characteristics in nanoscale electronic devices.
+In contrst more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simltaneously applying a dressing field.
+Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems [43,47,48], they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
+Furthermore K.
+Dini et al.
+[23] have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems and they have not adopted the state of art model to describe the conductivity in a quantum Hall system.
+In their study, they used the conductivity models from T.
+Ando et al.
+[43,48] and as mentioned in A.
+Endo et al.
+work [47] those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results.
 
-When a stationary magentic field applied perpendicularly across the surface of 2DEG systems, the orbital motion of electrons becomes completely quantized and the energy spectrium becomes discrete by creating Landau levels.
-Such a singular system known as a quantum Hall system and in this study we explictly calculate the diagonal ($\sigma_{xx},\sigma_{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems.
-
-Although there are already exist a number of adavanced theories devoted to the calculation of conductivity tensor elements in a quantum Hall systems [3-5], they have not been applied to the optically manipulation the magneto-electric properties of the quantum Hall systems.
-However K.
-Dini et al.
-[6] have recently investigated the one directional conductivity behaviour of dressed quantum Hall systems, they have not used the state of art model to describe the conductivity in a quantum Hall system.
-In their study they used the conductivity models from T.
-Ando et al.
-[3,4] and as mentioned in A.
-Endo et al.
-investigation [5] those models are far less accurate representation of the experimantally observed Landau levels because they present a semi-elliptical broadening.
-
-In this study we develop a genralized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [1,2].
-In addition, we demonstrate that our generalized model is agreed with the state of art conductivity model [5] for specalized quantum Hall system which has been considered without the external dressing field.
-Therefore this theory describes that the dressing field can be used as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectonic devices.
+In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
+A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantised and the energy spectrum becomes discrete by creating Landau levels [49].
+Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the diagonal ($\sigma_{xx},\sigma_{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [24].
+Finaly we demonstrate that our generalised model is agreed with the state of art conductivity model [47] already developed for specialised quantum Hall systems that have been considered without the external dressing field.
+Furthermore the mechanism of optical manipulation can be used as a tool to utilise transport properties in various two-dimentional nano-structures which serve as a basis for nano-electronic devices and we belive that our theoritical analysis and visual depictions of results can be used to undestand the basic structure and optimize the performance of optical manipulation of trasport propeties in a two-dimentional quantum Hall system.

### 2021-07-16 paper/v1.0/sections/1_introduction.tex
Add more reference paper

@@
-Manipulating physical systems as a consequence of light engagements introduced an astonishing scope of twentieth-century physics namely quantum optics [15].
-Quantum optics have dragged research attention in the disciplines of optoelectronics [1,2,3], sensing [4,5,6], energy harvesting [7,8], quantum computing [9,10,11], bio-information [12,13], and abundant affiliates of recent technologies [14].
-The studies on quantum optics of nanostructures were centered on metamaterials [28,34], quantum plasmonic effects [27,33], lasers and amplifiers [29,30], quantum cavity physics [31,32].
+Manipulating physical systems as a consequence of light engagements introduced an astonishing scope of twentieth-century physics namely quantum optics \cite{grynberg10}.
+Quantum optics have dragged research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
+quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and abundant affiliates of recent technologies \cite{rivera20}. 
+The studies on quantum optics of nano-structures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
 However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics [16-24].
@@
 A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantised and the energy spectrum becomes discrete by creating Landau levels [49].
-Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the diagonal ($\sigma_{xx},\sigma_{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [24].
+Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [24].
 Finaly we demonstrate that our generalised model is agreed with the state of art conductivity model [47] already developed for specialised quantum Hall systems that have been considered without the external dressing field.

### 2021-07-16 paper/v1.0/sections/8_manipulate_conductivity.tex
Add more reference paper

@@
 \includegraphics[scale=0.55]{figures/fig_5}
-\caption{\label{fig_4} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
+\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
@@
 \includegraphics[scale=0.55]{figures/fig_6}
-\caption{\label{fig_5} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.

### 2021-07-17 paper/v1.0/sections/1_introduction.tex
Add introduction and format

@@
 The studies on quantum optics of nano-structures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
-However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics [16-24].
-The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance [35].
-Among these works, most studies have considered the driving field as a perturbative field [18,20] that is not applicable for systems under high-intensity illumination [24,25].
+However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
+The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance \cite{premaratne21}.
+Among these works, most studies have considered the driving field as a perturbative field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illumination \cite{grifoni98,wackerl20}.
 When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be consider gets increase.
-Then a more accurate and powerful concept need to be adopt and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) [18,36,37].
+Then a more accurate and powerful concept need to be adopt and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}.
 On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
 A theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref.
-[22,18,24] where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref.
-[24], introducing a novel type of Green’s functions namely four-times Green’s functions.
+\cite{kibis14,morina15,wackerl20} where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref.
+\cite{wackerl20}, introducing a novel type of Green’s functions namely four-times Green’s functions.
 As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nano-structures by an intense dressing field.
 
-On the other hand, quantum Hall effect [39] observed for two-dimentional fermions systems at low temperatures under strong staionary magnetic field manifest remarkable magneto-transport behaviours and transport properties of these systems attracted many researches attention in experimentally [40,41,42] and theoretically [43,44,45,46,47].
+On the other hand, quantum Hall effect \cite{girvin90} observed for two-dimentional fermions systems at low temperatures under strong staionary magnetic field manifest remarkable magneto-transport behaviours and transport properties of these systems attracted many researches attention in experimentally \cite{allerman95,tieke97,pan05} and theoretically \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09}.
 Akira Endo et al.
-[47] previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoritical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results [47].
+\cite{endo09} previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoritical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results \cite{endo09}.
 
 In contrst more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simltaneously applying a dressing field.
-Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems [43,47,48], they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
+Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
 Furthermore K.
 Dini et al.
-[23] have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems and they have not adopted the state of art model to describe the conductivity in a quantum Hall system.
+\cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems and they have not adopted the state of art model to describe the conductivity in a quantum Hall system.
 In their study, they used the conductivity models from T.
 Ando et al.
-[43,48] and as mentioned in A.
+\cite{ando74_1,ando82} and as mentioned in A.
 Endo et al.
-work [47] those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results.
+work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results.
 
 In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
-A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantised and the energy spectrum becomes discrete by creating Landau levels [49].
-Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity [24].
-Finaly we demonstrate that our generalised model is agreed with the state of art conductivity model [47] already developed for specialised quantum Hall systems that have been considered without the external dressing field.
+A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantised and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
+Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
+Finaly we demonstrate that our generalised model is agreed with the state of art conductivity model \cite{endo09} already developed for specialised quantum Hall systems that have been considered without the external dressing field.
 Furthermore the mechanism of optical manipulation can be used as a tool to utilise transport properties in various two-dimentional nano-structures which serve as a basis for nano-electronic devices and we belive that our theoritical analysis and visual depictions of results can be used to undestand the basic structure and optimize the performance of optical manipulation of trasport propeties in a two-dimentional quantum Hall system.

### 2021-07-17 paper/v1.0/sections/5_inverse_scattering_time.tex
Add section 5 paper
Change figures
Add introduction and format

@@
 With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
-\begin{widetext}
 \begin{equation} \label{eq_13}
   \begin{aligned}
-    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{N} =
-    \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
-    \delta(\varepsilon - \varepsilon_{N})
+    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
+    & =
+    \frac { \varrho^2}{eB}
+    \delta(\varepsilon - \varepsilon_{N}) \\
+    & \times
     \int_{-\infty}^{\infty} d k_1
-    &
     J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
@@
 \end{equation}
-\end{widetext}
-where $J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C.
+where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
+$J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C.
 In this study, the perturbation potential is assumed to be formed by an ensemble of randomly distributed impurities, since random impurities in a disorded metal is a better approximation for experimental results.
@@
 Next we are going to analyse the contribution of the inverse scattering time matrix elements to the transport properies in 2DEG.
-The disorder in the system is not supposed to change the eigenenergies of the bare system \cite{wackerl20}, hence all off-diogonal elements of the self-energy were neglected and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport propeties
-\begin{widetext}
+The disorder in the system is not supposed to change the eigenenergies of the bare system \cite{wackerl20}, hence all off-diogonal elements of the self-energy were neglected and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+% \begin{equation} \label{eq_14}
+%   \begin{aligned}
+%     \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{00}_{N} \\
+%     & =
+%     \frac { \varrho^2}{eB}
+%     \delta(\varepsilon - \varepsilon_{N}) \\
+%     & \times
+%     \int_{-\infty}^{\infty} d k_1 \;
+%     J_0^2\qty(\frac{b\hbar}{eB}[{k}_x -  k_1])
+%     \\
+%     & \times
+%     \qty|
+%     \int_{-\infty}^{\infty} d k_2 \;
+%     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
+%     {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
+%   \end{aligned}
+% \end{equation}
+Introduce a new parameter with physical meaning of scattering-induced broadening of the Landau level as \cite{dini16,endo09}
 \begin{equation} \label{eq_14}
-    \begin{aligned}
-      \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N} =
-      \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
-      \delta(\varepsilon - \varepsilon_{N}) &
-      \int_{-\infty}^{\infty} d k_1 \;
-      J_0^2\qty(\frac{b\hbar}{eB}[{k}_x -  k_1])
-      \\
-      & \times
-      \qty|
-      \int_{-\infty}^{\infty} d k_2 \;
-      {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
-      {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
-    \end{aligned}
-  \end{equation}
-Introduce a new parameter with physical meaning of scattering-induced broadening of the Landau level as \cite{dini16,endo09}
-\begin{equation} \label{eq_15}
  \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
@@
 and this leads to
-\begin{equation} \label{eq_16}
+\begin{equation} \label{eq_15}
  \begin{aligned}
-   \Gamma^{00}_{N}(\varepsilon,k_x)  =
-   \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
-   \delta(\varepsilon - \varepsilon_{N}) &
+   \Gamma^{00}_{N}& (\varepsilon,k_x) \\
+   & =
+   \frac { \varrho^2}{eB}
+   \delta(\varepsilon - \varepsilon_{N}) \\
+   & \times
    \int_{-\infty}^{\infty} d {k'}_x \;
@@
 \end{equation}
-\end{widetext}
 In addition, for the case of scattering within a same Landau level, one can present the delta distribution of the energy using the same physical interpretation \cite{dini16} as follows
-\begin{equation} \label{eq_17}
+\begin{equation} \label{eq_16}
  \delta(\varepsilon - \varepsilon_{N}) \approx
@@
 and we write the central element of inverse scattering time matrix in more compact form
-\begin{equation} \label{eq_18}
+\begin{equation} \label{eq_17}
   \begin{aligned}
@@
 \end{equation}
-where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$, $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
+where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
 To analyze the contribution of dressing field on the scatering-induced broadening, normalized $N$-th Landau level scatering-induced broadening can be defined as
-\begin{equation} \label{eq_19}
+\begin{equation} \label{eq_18}
     \Lambda_N(k_x) \equiv
@@
 \begin{widetext}
-\begin{equation} \label{eq_20}
+\begin{equation} \label{eq_19}
     \Lambda_N (k_x) =
@@
 \begin{figure}[t]
-\includegraphics[scale=0.55]{figures/fig_3}
+\includegraphics[scale=0.9]{figures/fig_3}
 \caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.45]{figures/fig_4}
+\includegraphics[scale=1]{figures/fig_4}
 \caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.

### 2021-07-17 paper/v1.0/sections/7_floquet_drude_conductivity.tex
Add section 6 paper
Add introduction and format

@@
 Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
-\begin{equation} \label{eq_21}
+\begin{equation} \label{eq_20}
   \begin{aligned}
@@
 In addition $A$ is the area of the considering two-dimentionl system, partical distribution function is given by $f$ and $\lambda$ is a function that can be choose such that
-\begin{equation} \label{eq_22}
+\begin{equation} \label{eq_21}
     \lambda - \frac{\hbar \omega}{2}
@@
 
-Then Eq.~(\ref{eq_21}) can be expanded in off resonant regime ($\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system, using only central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$
+Then Eq.~(\ref{eq_20}) can be expanded in off resonant regime ($\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system, using only central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$
 \begin{widetext}
-\begin{equation} \label{eq_23}
+\begin{equation} \label{eq_22}
   \begin{aligned}
-    {\sigma}^{xx} & =
-    \frac{-1}{4\pi\hbar A}
+    {\sigma}^{xx} =
+    \frac{-1}{4\pi\hbar A} &
     \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
@@
     -\frac{\partial f}{\partial \varepsilon})
-    \\
-    & \times
     \frac{1}{V_{k_x}} \sum_{k_x}
@@
 where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evalute by considering each matrix elements seperatly
-\begin{equation} \label{eq_24}
+\begin{equation} \label{eq_23}
   \begin{aligned}
-    {\sigma}^{xx}  =
+    {\sigma}^{xx}  = &
     \frac{-1}{4\pi\hbar A}
-    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} & d\varepsilon
+    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
     \qty(
     -\frac{\partial f}{\partial \varepsilon})
-    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
-    \frac{1}{{V_x}^3} \sum_{{k_x}_1,{k_x}_2,{k_x}_3}
-    \sum_{n_1,n_2,n_3}
-    \\
+    \frac{1}{V_{k_x}^4} \sum_{k_x} \sum_{n}
+    \sum_{{k_x}_1,{k_x}_2,{k_x}_3}
+    \sum_{n_1,n_2,n_3}\\
     & \times
@@
     )}
-    {n_2,{k_x}_2} \\
-    & \times
+    {n_2,{k_x}_2}
     \mel{n_2,{k_x}_2}{
@@
 Since we can diagonalize the impurity averaged Green's function using unitary trasnformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Ref.~\cite{wackerl20,wackerlthesis20,tsuji08} and we evaluate the matrix element of the differece between retarded and advanced Green's functions
-\begin{equation} \label{eq_25}
+\begin{equation} \label{eq_24}
   \mel{{n_1,{k_x}_1}}{
@@
 and
-\begin{equation} \label{eq_26}
+\begin{equation} \label{eq_25}
   \mel{{n_3,{k_x}_3}}{
@@
 Applying the matrix elements of electric current operator in Landau levels (see Appendix D) and
-results form Eq.~(\ref{eq_25}) and Eq.~(\ref{eq_26}) back into Eq.~(\ref{eq_24}) we obtain
-\begin{equation} \label{eq_27}
+results form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain
+\begin{equation} \label{eq_26}
   \begin{aligned}
@@
 and the only non-zero term would be
-\begin{equation} \label{eq_28}
+\begin{equation} \label{eq_27}
   \begin{aligned}
@@
 Since the inverse scattering time matrix being equal to the diagonalized differece of the retared and advanced self-energy and on the diagonal the differece of the retarded and advanced Green's function is equal to the imaginary part of the retared self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property
-\begin{equation} \label{eq_29}
+\begin{equation} \label{eq_28}
   \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll} =
@@
 and using central element ($l=0$) of the inverse scattering time matrix we can modify the derived conductivity expression
-\begin{equation} \label{eq_30}
+\begin{equation} \label{eq_29}
     {\sigma}^{xx}   =
@@
 However by considering the condition that the center of the force of the oscillator $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify
-\begin{equation} \label{eq_31}
+\begin{equation} \label{eq_30}
  -\frac{m_e\omega_0 Ly}{2\hbar} \leq k_x \leq \frac{m_e\omega_0 Ly}{2\hbar}.

### 2021-07-17 paper/v1.0/sections/8_manipulate_conductivity.tex
Add introduction and format

@@
 transverse conductivity as a function of fermi energy $X_F$ and intensity of the dressing field $I$. Here we have normalized the conductivity using the natural conductivity of least Landau level.
-\begin{equation} \label{eq_36}
+\begin{equation} \label{eq_35}
   \begin{aligned}
@@
 Furthermore we can distinguish that the shapes and behavoiur of the conductivity regions illustrated in Fig.~\ref{fig_4} and \ref{fig_5} are generally incompatible with the results reported in Ref.~\cite{dini16}.
-This is due to the selection of the conventional transverse conductivity theory of 2DEG from Ref.~\cite{ando74,ando82}.
-The semi-elliptical conductivity regions illustrated in Ref.~\cite{dini16,ando74,ando82}, have less consistance with the experimentally observed Landau levels representation \cite{endo09}.
+This is due to the selection of the conventional transverse conductivity theory of 2DEG from Ref.~\cite{ando74_1,ando82}.
+The semi-elliptical conductivity regions illustrated in Ref.~\cite{dini16,ando74_1,ando82}, have less consistance with the experimentally observed Landau levels representation \cite{endo09}.
 In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result represented by A.

### 2021-07-18 theory/figures/fig_1new.tex
Improve figures

\documentclass{standalone}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz,pgf} %and any other packages or tikzlibraries your picture needs
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}
\usetikzlibrary{shapes,arrows,patterns}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Straight Lines [id:da5726274877822322]
\draw [color={rgb, 255:red, 127; green, 117; blue, 117 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 5.63pt off 4.5pt}]  (339.92,108.44) -- (339.87,253.18) ;
\draw [shift={(339.92,104.44)}, rotate = 90.02] [fill={rgb, 255:red, 127; green, 117; blue, 117 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (8.13,-3.9) -- (0,0) -- (8.13,3.9) -- cycle    ;
%Straight Lines [id:da29209126760206683]
\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (198.39,220.13) -- (231.49,220.09) ;
\draw [shift={(234.49,220.09)}, rotate = 539.9300000000001] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (6.25,-3) -- (0,0) -- (6.25,3) -- cycle    ;
%Straight Lines [id:da6165306544380005]
\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (198.39,220.13) -- (184.04,238.58) ;
\draw [shift={(182.2,240.94)}, rotate = 307.89] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (6.25,-3) -- (0,0) -- (6.25,3) -- cycle    ;
%Straight Lines [id:da7391727465011027]
\draw [color={rgb, 255:red, 162; green, 157; blue, 157 }  ,draw opacity=1 ]   (198.39,220.13) -- (198.74,189.37) ;
\draw [shift={(198.77,186.37)}, rotate = 450.64] [fill={rgb, 255:red, 162; green, 157; blue, 157 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (6.25,-3) -- (0,0) -- (6.25,3) -- cycle    ;

%Shape: Parallelogram [id:dp41534268368743876]
\draw  [color={rgb, 255:red, 230; green, 243; blue, 247 }  ,draw opacity=1 ][fill={rgb, 255:red, 230; green, 243; blue, 247 }  ,fill opacity=1 ] (233.03,230.41) -- (281.59,230.41) -- (253.7,276.83) -- (205.14,276.83) -- cycle ;
%Shape: Trapezoid [id:dp7788778266108187]
\draw  [color={rgb, 255:red, 230; green, 243; blue, 247 }  ,draw opacity=1 ][fill={rgb, 255:red, 230; green, 243; blue, 247 }  ,fill opacity=1 ] (248.48,276.13) -- (248.97,230.43) -- (447.07,230.43) -- (473.99,276.13) -- cycle ;
%Straight Lines [id:da5683506349044234]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (204.78,276.57) -- (474.45,276.13) ;
%Straight Lines [id:da36516960272690935]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (232.53,230.41) -- (446.93,230.41) ;
%Straight Lines [id:da218377945892541]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (232.93,230.01) -- (204.78,276.57) ;
%Straight Lines [id:da5092960488933624]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (447.33,230.01) -- (474.45,276.13) ;
%Straight Lines [id:da11082740586756445]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (340.13,230.01) -- (339.62,276.35) ;
%Straight Lines [id:da2154900622918119]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (327.45,229.97) -- (324.21,276.57) ;
%Straight Lines [id:da2109844821797362]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (312.94,229.97) -- (306.71,276.31) ;
%Straight Lines [id:da14123000440106437]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (298.83,229.92) -- (291.06,276.31) ;
%Straight Lines [id:da6719175270526567]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (285.63,230.19) -- (273.86,276.83) ;
%Straight Lines [id:da7130190425909961]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (271.49,230.21) -- (254.83,276.57) ;
%Straight Lines [id:da02923644984301399]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (259.23,230.19) -- (238.56,276.83) ;
%Straight Lines [id:da44595644058071016]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (246.51,230.21) -- (223.51,276.83) ;
%Straight Lines [id:da03090530016819959]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (352.15,229.92) -- (356.14,276.57) ;
%Straight Lines [id:da0075347964569616455]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (366.71,230.09) -- (374.75,276.93) ;
%Straight Lines [id:da9231431383372868]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (381.01,229.92) -- (393.29,276.31) ;
%Straight Lines [id:da5734645298908272]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (394.21,230.19) -- (411.1,276.83) ;
%Straight Lines [id:da18417258051367602]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (408.34,230.19) -- (428.29,276.57) ;
%Straight Lines [id:da7766509629904832]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (419.7,230.09) -- (445.79,276.57) ;
%Straight Lines [id:da5541997421952078]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (434.13,230.19) -- (459.3,276.31) ;
%Straight Lines [id:da8163512478619217]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (209.08,268.4) -- (470.05,267.61) ;
%Straight Lines [id:da6866382299263494]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (214.3,260.49) -- (465.14,259.97) ;
%Straight Lines [id:da10951428264342855]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (218.86,253.29) -- (460.89,253.07) ;
%Straight Lines [id:da16627986420586138]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (222.59,246.53) -- (456.85,246.26) ;
%Straight Lines [id:da1104010543118994]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (226.18,240.86) -- (453.07,240.34) ;
%Straight Lines [id:da46889737940339105]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (228.95,235.59) -- (449.69,234.8) ;
%Shape: Ellipse [id:dp7799971866902644]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (225.97,268.4) .. controls (225.97,267.6) and (226.73,266.95) .. (227.66,266.95) .. controls (228.59,266.95) and (229.35,267.6) .. (229.35,268.4) .. controls (229.35,269.2) and (228.59,269.85) .. (227.66,269.85) .. controls (226.73,269.85) and (225.97,269.2) .. (225.97,268.4) -- cycle ;
%Shape: Ellipse [id:dp33000551716975157]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (229.74,260.37) .. controls (229.74,259.57) and (230.49,258.92) .. (231.43,258.92) .. controls (232.36,258.92) and (233.11,259.57) .. (233.11,260.37) .. controls (233.11,261.17) and (232.36,261.82) .. (231.43,261.82) .. controls (230.49,261.82) and (229.74,261.17) .. (229.74,260.37) -- cycle ;
%Shape: Ellipse [id:dp06335085811101071]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (233.37,252.95) .. controls (233.37,252.15) and (234.12,251.5) .. (235.05,251.5) .. controls (235.99,251.5) and (236.74,252.15) .. (236.74,252.95) .. controls (236.74,253.75) and (235.99,254.4) .. (235.05,254.4) .. controls (234.12,254.4) and (233.37,253.75) .. (233.37,252.95) -- cycle ;
%Shape: Ellipse [id:dp5515387996519605]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (236.44,246.6) .. controls (236.44,245.8) and (237.19,245.15) .. (238.12,245.15) .. controls (239.06,245.15) and (239.81,245.8) .. (239.81,246.6) .. controls (239.81,247.4) and (239.06,248.05) .. (238.12,248.05) .. controls (237.19,248.05) and (236.44,247.4) .. (236.44,246.6) -- cycle ;
%Shape: Ellipse [id:dp9613949559203752]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (239.65,240.25) .. controls (239.65,239.45) and (240.4,238.8) .. (241.33,238.8) .. controls (242.27,238.8) and (243.02,239.45) .. (243.02,240.25) .. controls (243.02,241.05) and (242.27,241.7) .. (241.33,241.7) .. controls (240.4,241.7) and (239.65,241.05) .. (239.65,240.25) -- cycle ;
%Shape: Ellipse [id:dp5595749562711418]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (242.58,234.86) .. controls (242.58,234.06) and (243.33,233.41) .. (244.26,233.41) .. controls (245.2,233.41) and (245.95,234.06) .. (245.95,234.86) .. controls (245.95,235.66) and (245.2,236.31) .. (244.26,236.31) .. controls (243.33,236.31) and (242.58,235.66) .. (242.58,234.86) -- cycle ;
%Shape: Ellipse [id:dp9494831013959741]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (240.48,268.16) .. controls (240.48,267.36) and (241.24,266.71) .. (242.17,266.71) .. controls (243.1,266.71) and (243.86,267.36) .. (243.86,268.16) .. controls (243.86,268.96) and (243.1,269.61) .. (242.17,269.61) .. controls (241.24,269.61) and (240.48,268.96) .. (240.48,268.16) -- cycle ;
%Shape: Ellipse [id:dp9210781564959785]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (243.97,260.49) .. controls (243.97,259.69) and (244.73,259.04) .. (245.66,259.04) .. controls (246.59,259.04) and (247.35,259.69) .. (247.35,260.49) .. controls (247.35,261.29) and (246.59,261.94) .. (245.66,261.94) .. controls (244.73,261.94) and (243.97,261.29) .. (243.97,260.49) -- cycle ;
%Shape: Ellipse [id:dp4310038641794769]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (247.2,253.51) .. controls (247.2,252.71) and (247.96,252.06) .. (248.89,252.06) .. controls (249.83,252.06) and (250.58,252.71) .. (250.58,253.51) .. controls (250.58,254.31) and (249.83,254.96) .. (248.89,254.96) .. controls (247.96,254.96) and (247.2,254.31) .. (247.2,253.51) -- cycle ;
%Shape: Ellipse [id:dp03456062696425044]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (250.11,246.48) .. controls (250.11,245.68) and (250.87,245.03) .. (251.8,245.03) .. controls (252.73,245.03) and (253.49,245.68) .. (253.49,246.48) .. controls (253.49,247.28) and (252.73,247.93) .. (251.8,247.93) .. controls (250.87,247.93) and (250.11,247.28) .. (250.11,246.48) -- cycle ;
%Shape: Ellipse [id:dp3303046459338419]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (253.04,240.49) .. controls (253.04,239.69) and (253.8,239.04) .. (254.73,239.04) .. controls (255.66,239.04) and (256.42,239.69) .. (256.42,240.49) .. controls (256.42,241.29) and (255.66,241.94) .. (254.73,241.94) .. controls (253.8,241.94) and (253.04,241.29) .. (253.04,240.49) -- cycle ;
%Shape: Ellipse [id:dp011240288016139521]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (255.14,234.86) .. controls (255.14,234.06) and (255.89,233.41) .. (256.82,233.41) .. controls (257.76,233.41) and (258.51,234.06) .. (258.51,234.86) .. controls (258.51,235.66) and (257.76,236.31) .. (256.82,236.31) .. controls (255.89,236.31) and (255.14,235.66) .. (255.14,234.86) -- cycle ;
%Shape: Ellipse [id:dp6272548395164819]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (256.25,268.28) .. controls (256.25,267.48) and (257.01,266.83) .. (257.94,266.83) .. controls (258.87,266.83) and (259.63,267.48) .. (259.63,268.28) .. controls (259.63,269.08) and (258.87,269.73) .. (257.94,269.73) .. controls (257.01,269.73) and (256.25,269.08) .. (256.25,268.28) -- cycle ;
%Shape: Ellipse [id:dp02366538554974107]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (259.04,260.37) .. controls (259.04,259.57) and (259.8,258.92) .. (260.73,258.92) .. controls (261.66,258.92) and (262.42,259.57) .. (262.42,260.37) .. controls (262.42,261.17) and (261.66,261.82) .. (260.73,261.82) .. controls (259.8,261.82) and (259.04,261.17) .. (259.04,260.37) -- cycle ;
%Shape: Ellipse [id:dp3969356729665663]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (261.48,253.51) .. controls (261.48,252.71) and (262.24,252.06) .. (263.17,252.06) .. controls (264.1,252.06) and (264.86,252.71) .. (264.86,253.51) .. controls (264.86,254.31) and (264.1,254.96) .. (263.17,254.96) .. controls (262.24,254.96) and (261.48,254.31) .. (261.48,253.51) -- cycle ;
%Shape: Ellipse [id:dp6305092289007959]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (264.07,246.36) .. controls (264.07,245.56) and (264.82,244.91) .. (265.76,244.91) .. controls (266.69,244.91) and (267.44,245.56) .. (267.44,246.36) .. controls (267.44,247.16) and (266.69,247.81) .. (265.76,247.81) .. controls (264.82,247.81) and (264.07,247.16) .. (264.07,246.36) -- cycle ;
%Shape: Ellipse [id:dp45941754496129183]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (266.16,240.13) .. controls (266.16,239.33) and (266.92,238.68) .. (267.85,238.68) .. controls (268.78,238.68) and (269.54,239.33) .. (269.54,240.13) .. controls (269.54,240.93) and (268.78,241.58) .. (267.85,241.58) .. controls (266.92,241.58) and (266.16,240.93) .. (266.16,240.13) -- cycle ;
%Shape: Ellipse [id:dp4326662692295993]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (268.11,234.74) .. controls (268.11,233.94) and (268.87,233.29) .. (269.8,233.29) .. controls (270.74,233.29) and (271.49,233.94) .. (271.49,234.74) .. controls (271.49,235.54) and (270.74,236.19) .. (269.8,236.19) .. controls (268.87,236.19) and (268.11,235.54) .. (268.11,234.74) -- cycle ;
%Shape: Ellipse [id:dp5418698275036782]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (274.25,268.4) .. controls (274.25,267.6) and (275.01,266.95) .. (275.94,266.95) .. controls (276.88,266.95) and (277.63,267.6) .. (277.63,268.4) .. controls (277.63,269.2) and (276.88,269.85) .. (275.94,269.85) .. controls (275.01,269.85) and (274.25,269.2) .. (274.25,268.4) -- cycle ;
%Shape: Ellipse [id:dp1367075175730701]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (276.35,260.49) .. controls (276.35,259.69) and (277.1,259.04) .. (278.04,259.04) .. controls (278.97,259.04) and (279.72,259.69) .. (279.72,260.49) .. controls (279.72,261.29) and (278.97,261.94) .. (278.04,261.94) .. controls (277.1,261.94) and (276.35,261.29) .. (276.35,260.49) -- cycle ;
%Shape: Ellipse [id:dp19506807329724785]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (278.06,253.51) .. controls (278.06,252.71) and (278.82,252.06) .. (279.75,252.06) .. controls (280.68,252.06) and (281.44,252.71) .. (281.44,253.51) .. controls (281.44,254.31) and (280.68,254.96) .. (279.75,254.96) .. controls (278.82,254.96) and (278.06,254.31) .. (278.06,253.51) -- cycle ;
%Shape: Ellipse [id:dp2959505733230936]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (279.7,246.6) .. controls (279.7,245.8) and (280.45,245.15) .. (281.39,245.15) .. controls (282.32,245.15) and (283.07,245.8) .. (283.07,246.6) .. controls (283.07,247.4) and (282.32,248.05) .. (281.39,248.05) .. controls (280.45,248.05) and (279.7,247.4) .. (279.7,246.6) -- cycle ;
%Shape: Ellipse [id:dp27635839422101305]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (281.23,240.37) .. controls (281.23,239.57) and (281.99,238.92) .. (282.92,238.92) .. controls (283.85,238.92) and (284.61,239.57) .. (284.61,240.37) .. controls (284.61,241.17) and (283.85,241.82) .. (282.92,241.82) .. controls (281.99,241.82) and (281.23,241.17) .. (281.23,240.37) -- cycle ;
%Shape: Ellipse [id:dp6517438495733301]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (282.63,234.98) .. controls (282.63,234.18) and (283.38,233.53) .. (284.32,233.53) .. controls (285.25,233.53) and (286,234.18) .. (286,234.98) .. controls (286,235.78) and (285.25,236.43) .. (284.32,236.43) .. controls (283.38,236.43) and (282.63,235.78) .. (282.63,234.98) -- cycle ;
%Shape: Ellipse [id:dp9090769332232691]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (296.3,234.86) .. controls (296.3,234.06) and (297.06,233.41) .. (297.99,233.41) .. controls (298.93,233.41) and (299.68,234.06) .. (299.68,234.86) .. controls (299.68,235.66) and (298.93,236.31) .. (297.99,236.31) .. controls (297.06,236.31) and (296.3,235.66) .. (296.3,234.86) -- cycle ;
%Shape: Ellipse [id:dp6408948797914291]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (295.33,240.49) .. controls (295.33,239.69) and (296.08,239.04) .. (297.02,239.04) .. controls (297.95,239.04) and (298.7,239.69) .. (298.7,240.49) .. controls (298.7,241.29) and (297.95,241.94) .. (297.02,241.94) .. controls (296.08,241.94) and (295.33,241.29) .. (295.33,240.49) -- cycle ;
%Shape: Ellipse [id:dp20597093928210541]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (294.21,246.24) .. controls (294.21,245.44) and (294.97,244.79) .. (295.9,244.79) .. controls (296.83,244.79) and (297.59,245.44) .. (297.59,246.24) .. controls (297.59,247.04) and (296.83,247.69) .. (295.9,247.69) .. controls (294.97,247.69) and (294.21,247.04) .. (294.21,246.24) -- cycle ;
%Shape: Ellipse [id:dp8864483173331592]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (293.26,253.11) .. controls (293.26,252.31) and (294.01,251.66) .. (294.95,251.66) .. controls (295.88,251.66) and (296.63,252.31) .. (296.63,253.11) .. controls (296.63,253.91) and (295.88,254.56) .. (294.95,254.56) .. controls (294.01,254.56) and (293.26,253.91) .. (293.26,253.11) -- cycle ;
%Shape: Ellipse [id:dp6054770114499604]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (291.98,260.37) .. controls (291.98,259.57) and (292.73,258.92) .. (293.67,258.92) .. controls (294.6,258.92) and (295.35,259.57) .. (295.35,260.37) .. controls (295.35,261.17) and (294.6,261.82) .. (293.67,261.82) .. controls (292.73,261.82) and (291.98,261.17) .. (291.98,260.37) -- cycle ;
%Shape: Ellipse [id:dp4642646383526645]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (290.72,268.04) .. controls (290.72,267.24) and (291.48,266.59) .. (292.41,266.59) .. controls (293.34,266.59) and (294.1,267.24) .. (294.1,268.04) .. controls (294.1,268.84) and (293.34,269.49) .. (292.41,269.49) .. controls (291.48,269.49) and (290.72,268.84) .. (290.72,268.04) -- cycle ;
%Shape: Ellipse [id:dp0052217154530300736]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (310.54,234.86) .. controls (310.54,234.06) and (311.29,233.41) .. (312.23,233.41) .. controls (313.16,233.41) and (313.92,234.06) .. (313.92,234.86) .. controls (313.92,235.66) and (313.16,236.31) .. (312.23,236.31) .. controls (311.29,236.31) and (310.54,235.66) .. (310.54,234.86) -- cycle ;
%Shape: Ellipse [id:dp5015066824539638]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (309.7,240.37) .. controls (309.7,239.57) and (310.46,238.92) .. (311.39,238.92) .. controls (312.32,238.92) and (313.08,239.57) .. (313.08,240.37) .. controls (313.08,241.17) and (312.32,241.82) .. (311.39,241.82) .. controls (310.46,241.82) and (309.7,241.17) .. (309.7,240.37) -- cycle ;
%Shape: Ellipse [id:dp685074231743434]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (308.86,246.48) .. controls (308.86,245.68) and (309.62,245.03) .. (310.55,245.03) .. controls (311.48,245.03) and (312.24,245.68) .. (312.24,246.48) .. controls (312.24,247.28) and (311.48,247.93) .. (310.55,247.93) .. controls (309.62,247.93) and (308.86,247.28) .. (308.86,246.48) -- cycle ;
%Shape: Ellipse [id:dp9612691221229259]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (308.1,253.38) .. controls (308.1,252.58) and (308.85,251.93) .. (309.78,251.93) .. controls (310.72,251.93) and (311.47,252.58) .. (311.47,253.38) .. controls (311.47,254.18) and (310.72,254.83) .. (309.78,254.83) .. controls (308.85,254.83) and (308.1,254.18) .. (308.1,253.38) -- cycle ;
%Shape: Ellipse [id:dp7582686671111414]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (307.05,260.25) .. controls (307.05,259.45) and (307.81,258.8) .. (308.74,258.8) .. controls (309.67,258.8) and (310.43,259.45) .. (310.43,260.25) .. controls (310.43,261.05) and (309.67,261.7) .. (308.74,261.7) .. controls (307.81,261.7) and (307.05,261.05) .. (307.05,260.25) -- cycle ;
%Shape: Ellipse [id:dp8059458706306035]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (305.93,268.16) .. controls (305.93,267.36) and (306.69,266.71) .. (307.62,266.71) .. controls (308.55,266.71) and (309.31,267.36) .. (309.31,268.16) .. controls (309.31,268.96) and (308.55,269.61) .. (307.62,269.61) .. controls (306.69,269.61) and (305.93,268.96) .. (305.93,268.16) -- cycle ;
%Shape: Ellipse [id:dp3229432547886717]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (325.47,234.86) .. controls (325.47,234.06) and (326.23,233.41) .. (327.16,233.41) .. controls (328.09,233.41) and (328.85,234.06) .. (328.85,234.86) .. controls (328.85,235.66) and (328.09,236.31) .. (327.16,236.31) .. controls (326.23,236.31) and (325.47,235.66) .. (325.47,234.86) -- cycle ;
%Shape: Ellipse [id:dp3117768555799394]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (325.05,240.25) .. controls (325.05,239.45) and (325.81,238.8) .. (326.74,238.8) .. controls (327.67,238.8) and (328.43,239.45) .. (328.43,240.25) .. controls (328.43,241.05) and (327.67,241.7) .. (326.74,241.7) .. controls (325.81,241.7) and (325.05,241.05) .. (325.05,240.25) -- cycle ;
%Shape: Ellipse [id:dp7877572573898426]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (324.77,246.24) .. controls (324.77,245.44) and (325.53,244.79) .. (326.46,244.79) .. controls (327.39,244.79) and (328.15,245.44) .. (328.15,246.24) .. controls (328.15,247.04) and (327.39,247.69) .. (326.46,247.69) .. controls (325.53,247.69) and (324.77,247.04) .. (324.77,246.24) -- cycle ;
%Shape: Ellipse [id:dp03364760377653009]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (324.21,253.51) .. controls (324.21,252.71) and (324.97,252.06) .. (325.9,252.06) .. controls (326.84,252.06) and (327.59,252.71) .. (327.59,253.51) .. controls (327.59,254.31) and (326.84,254.96) .. (325.9,254.96) .. controls (324.97,254.96) and (324.21,254.31) .. (324.21,253.51) -- cycle ;
%Shape: Ellipse [id:dp48708531145288214]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (323.66,260.13) .. controls (323.66,259.33) and (324.41,258.68) .. (325.35,258.68) .. controls (326.28,258.68) and (327.03,259.33) .. (327.03,260.13) .. controls (327.03,260.93) and (326.28,261.58) .. (325.35,261.58) .. controls (324.41,261.58) and (323.66,260.93) .. (323.66,260.13) -- cycle ;
%Shape: Ellipse [id:dp8911330178631209]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (323.24,268.04) .. controls (323.24,267.24) and (323.99,266.59) .. (324.93,266.59) .. controls (325.86,266.59) and (326.61,267.24) .. (326.61,268.04) .. controls (326.61,268.84) and (325.86,269.49) .. (324.93,269.49) .. controls (323.99,269.49) and (323.24,268.84) .. (323.24,268.04) -- cycle ;
%Shape: Ellipse [id:dp4740505077857613]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (338.03,234.8) .. controls (338.03,234) and (338.79,233.35) .. (339.72,233.35) .. controls (340.65,233.35) and (341.41,234) .. (341.41,234.8) .. controls (341.41,235.6) and (340.65,236.25) .. (339.72,236.25) .. controls (338.79,236.25) and (338.03,235.6) .. (338.03,234.8) -- cycle ;
%Shape: Ellipse [id:dp05074174028268441]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (338.34,240.2) .. controls (338.34,239.4) and (339.09,238.75) .. (340.03,238.75) .. controls (340.96,238.75) and (341.71,239.4) .. (341.71,240.2) .. controls (341.71,241) and (340.96,241.65) .. (340.03,241.65) .. controls (339.09,241.65) and (338.34,241) .. (338.34,240.2) -- cycle ;
%Shape: Ellipse [id:dp6828247138393344]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (338.03,246.39) .. controls (338.03,245.59) and (338.79,244.94) .. (339.72,244.94) .. controls (340.65,244.94) and (341.41,245.59) .. (341.41,246.39) .. controls (341.41,247.19) and (340.65,247.84) .. (339.72,247.84) .. controls (338.79,247.84) and (338.03,247.19) .. (338.03,246.39) -- cycle ;
%Shape: Ellipse [id:dp37439906499682496]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (338.18,253.18) .. controls (338.18,252.38) and (338.94,251.73) .. (339.87,251.73) .. controls (340.81,251.73) and (341.56,252.38) .. (341.56,253.18) .. controls (341.56,253.98) and (340.81,254.63) .. (339.87,254.63) .. controls (338.94,254.63) and (338.18,253.98) .. (338.18,253.18) -- cycle ;
%Shape: Ellipse [id:dp6352988871359346]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (338.03,260.23) .. controls (338.03,259.43) and (338.79,258.78) .. (339.72,258.78) .. controls (340.65,258.78) and (341.41,259.43) .. (341.41,260.23) .. controls (341.41,261.03) and (340.65,261.68) .. (339.72,261.68) .. controls (338.79,261.68) and (338.03,261.03) .. (338.03,260.23) -- cycle ;
%Shape: Ellipse [id:dp019555088357479766]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (337.88,268) .. controls (337.88,267.2) and (338.63,266.55) .. (339.57,266.55) .. controls (340.5,266.55) and (341.25,267.2) .. (341.25,268) .. controls (341.25,268.8) and (340.5,269.45) .. (339.57,269.45) .. controls (338.63,269.45) and (337.88,268.8) .. (337.88,268) -- cycle ;
%Shape: Ellipse [id:dp8342274959081832]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (350.73,234.74) .. controls (350.73,233.94) and (351.49,233.29) .. (352.42,233.29) .. controls (353.35,233.29) and (354.11,233.94) .. (354.11,234.74) .. controls (354.11,235.54) and (353.35,236.19) .. (352.42,236.19) .. controls (351.49,236.19) and (350.73,235.54) .. (350.73,234.74) -- cycle ;
%Shape: Ellipse [id:dp4762985302963485]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (351.43,240.25) .. controls (351.43,239.45) and (352.18,238.8) .. (353.12,238.8) .. controls (354.05,238.8) and (354.8,239.45) .. (354.8,240.25) .. controls (354.8,241.05) and (354.05,241.7) .. (353.12,241.7) .. controls (352.18,241.7) and (351.43,241.05) .. (351.43,240.25) -- cycle ;
%Shape: Ellipse [id:dp44585810520727964]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (351.71,246.48) .. controls (351.71,245.68) and (352.46,245.03) .. (353.4,245.03) .. controls (354.33,245.03) and (355.08,245.68) .. (355.08,246.48) .. controls (355.08,247.28) and (354.33,247.93) .. (353.4,247.93) .. controls (352.46,247.93) and (351.71,247.28) .. (351.71,246.48) -- cycle ;
%Shape: Ellipse [id:dp11218989987728789]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (352.46,253.25) .. controls (352.46,252.45) and (353.22,251.8) .. (354.15,251.8) .. controls (355.08,251.8) and (355.84,252.45) .. (355.84,253.25) .. controls (355.84,254.05) and (355.08,254.7) .. (354.15,254.7) .. controls (353.22,254.7) and (352.46,254.05) .. (352.46,253.25) -- cycle ;
%Shape: Ellipse [id:dp24985043025980125]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (352.82,260.13) .. controls (352.82,259.33) and (353.58,258.68) .. (354.51,258.68) .. controls (355.44,258.68) and (356.2,259.33) .. (356.2,260.13) .. controls (356.2,260.93) and (355.44,261.58) .. (354.51,261.58) .. controls (353.58,261.58) and (352.82,260.93) .. (352.82,260.13) -- cycle ;
%Shape: Ellipse [id:dp6542418618668944]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (353.66,267.92) .. controls (353.66,267.12) and (354.42,266.47) .. (355.35,266.47) .. controls (356.28,266.47) and (357.04,267.12) .. (357.04,267.92) .. controls (357.04,268.72) and (356.28,269.37) .. (355.35,269.37) .. controls (354.42,269.37) and (353.66,268.72) .. (353.66,267.92) -- cycle ;
%Shape: Ellipse [id:dp7988620770381141]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (365.4,235.14) .. controls (365.4,234.34) and (366.16,233.69) .. (367.09,233.69) .. controls (368.02,233.69) and (368.78,234.34) .. (368.78,235.14) .. controls (368.78,235.94) and (368.02,236.59) .. (367.09,236.59) .. controls (366.16,236.59) and (365.4,235.94) .. (365.4,235.14) -- cycle ;
%Shape: Ellipse [id:dp5325433872769323]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (367.04,240.37) .. controls (367.04,239.57) and (367.79,238.92) .. (368.73,238.92) .. controls (369.66,238.92) and (370.42,239.57) .. (370.42,240.37) .. controls (370.42,241.17) and (369.66,241.82) .. (368.73,241.82) .. controls (367.79,241.82) and (367.04,241.17) .. (367.04,240.37) -- cycle ;
%Shape: Ellipse [id:dp5873400953372752]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (367.89,246.24) .. controls (367.89,245.44) and (368.65,244.79) .. (369.58,244.79) .. controls (370.52,244.79) and (371.27,245.44) .. (371.27,246.24) .. controls (371.27,247.04) and (370.52,247.69) .. (369.58,247.69) .. controls (368.65,247.69) and (367.89,247.04) .. (367.89,246.24) -- cycle ;
%Shape: Ellipse [id:dp1557892830731582]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (369.04,253.51) .. controls (369.04,252.71) and (369.8,252.06) .. (370.73,252.06) .. controls (371.66,252.06) and (372.42,252.71) .. (372.42,253.51) .. controls (372.42,254.31) and (371.66,254.96) .. (370.73,254.96) .. controls (369.8,254.96) and (369.04,254.31) .. (369.04,253.51) -- cycle ;
%Shape: Ellipse [id:dp8302821392265101]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (369.85,260.13) .. controls (369.85,259.33) and (370.6,258.68) .. (371.54,258.68) .. controls (372.47,258.68) and (373.23,259.33) .. (373.23,260.13) .. controls (373.23,260.93) and (372.47,261.58) .. (371.54,261.58) .. controls (370.6,261.58) and (369.85,260.93) .. (369.85,260.13) -- cycle ;
%Shape: Ellipse [id:dp970245724105433]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (371.52,268.04) .. controls (371.52,267.24) and (372.28,266.59) .. (373.21,266.59) .. controls (374.14,266.59) and (374.9,267.24) .. (374.9,268.04) .. controls (374.9,268.84) and (374.14,269.49) .. (373.21,269.49) .. controls (372.28,269.49) and (371.52,268.84) .. (371.52,268.04) -- cycle ;
%Shape: Ellipse [id:dp7994637341597106]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (380.45,234.5) .. controls (380.45,233.7) and (381.21,233.05) .. (382.14,233.05) .. controls (383.08,233.05) and (383.83,233.7) .. (383.83,234.5) .. controls (383.83,235.3) and (383.08,235.95) .. (382.14,235.95) .. controls (381.21,235.95) and (380.45,235.3) .. (380.45,234.5) -- cycle ;
%Shape: Ellipse [id:dp7220483478514736]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (382.13,240.25) .. controls (382.13,239.45) and (382.89,238.8) .. (383.82,238.8) .. controls (384.75,238.8) and (385.51,239.45) .. (385.51,240.25) .. controls (385.51,241.05) and (384.75,241.7) .. (383.82,241.7) .. controls (382.89,241.7) and (382.13,241.05) .. (382.13,240.25) -- cycle ;
%Shape: Ellipse [id:dp673881154949054]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (383.52,246.36) .. controls (383.52,245.56) and (384.28,244.91) .. (385.21,244.91) .. controls (386.15,244.91) and (386.9,245.56) .. (386.9,246.36) .. controls (386.9,247.16) and (386.15,247.81) .. (385.21,247.81) .. controls (384.28,247.81) and (383.52,247.16) .. (383.52,246.36) -- cycle ;
%Shape: Ellipse [id:dp7615586326844195]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (385.46,253.11) .. controls (385.46,252.31) and (386.22,251.66) .. (387.15,251.66) .. controls (388.09,251.66) and (388.84,252.31) .. (388.84,253.11) .. controls (388.84,253.91) and (388.09,254.56) .. (387.15,254.56) .. controls (386.22,254.56) and (385.46,253.91) .. (385.46,253.11) -- cycle ;
%Shape: Ellipse [id:dp17801550211995876]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (387.29,260.25) .. controls (387.29,259.45) and (388.05,258.8) .. (388.98,258.8) .. controls (389.91,258.8) and (390.67,259.45) .. (390.67,260.25) .. controls (390.67,261.05) and (389.91,261.7) .. (388.98,261.7) .. controls (388.05,261.7) and (387.29,261.05) .. (387.29,260.25) -- cycle ;
%Shape: Ellipse [id:dp37886495124770314]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (389.25,268.04) .. controls (389.25,267.24) and (390,266.59) .. (390.94,266.59) .. controls (391.87,266.59) and (392.62,267.24) .. (392.62,268.04) .. controls (392.62,268.84) and (391.87,269.49) .. (390.94,269.49) .. controls (390,269.49) and (389.25,268.84) .. (389.25,268.04) -- cycle ;
%Shape: Ellipse [id:dp5060095549103398]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (393.99,234.5) .. controls (393.99,233.7) and (394.75,233.05) .. (395.68,233.05) .. controls (396.61,233.05) and (397.37,233.7) .. (397.37,234.5) .. controls (397.37,235.3) and (396.61,235.95) .. (395.68,235.95) .. controls (394.75,235.95) and (393.99,235.3) .. (393.99,234.5) -- cycle ;
%Shape: Ellipse [id:dp6047911027698867]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (396.22,240.01) .. controls (396.22,239.21) and (396.98,238.56) .. (397.91,238.56) .. controls (398.85,238.56) and (399.6,239.21) .. (399.6,240.01) .. controls (399.6,240.81) and (398.85,241.46) .. (397.91,241.46) .. controls (396.98,241.46) and (396.22,240.81) .. (396.22,240.01) -- cycle ;
%Shape: Ellipse [id:dp5235850351526199]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (398.46,246.36) .. controls (398.46,245.56) and (399.21,244.91) .. (400.15,244.91) .. controls (401.08,244.91) and (401.83,245.56) .. (401.83,246.36) .. controls (401.83,247.16) and (401.08,247.81) .. (400.15,247.81) .. controls (399.21,247.81) and (398.46,247.16) .. (398.46,246.36) -- cycle ;
%Shape: Ellipse [id:dp8576886389842573]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (400.97,253.51) .. controls (400.97,252.71) and (401.73,252.06) .. (402.66,252.06) .. controls (403.59,252.06) and (404.35,252.71) .. (404.35,253.51) .. controls (404.35,254.31) and (403.59,254.96) .. (402.66,254.96) .. controls (401.73,254.96) and (400.97,254.31) .. (400.97,253.51) -- cycle ;
%Shape: Ellipse [id:dp9972141547215403]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (403.06,260.01) .. controls (403.06,259.21) and (403.82,258.56) .. (404.75,258.56) .. controls (405.68,258.56) and (406.44,259.21) .. (406.44,260.01) .. controls (406.44,260.81) and (405.68,261.46) .. (404.75,261.46) .. controls (403.82,261.46) and (403.06,260.81) .. (403.06,260.01) -- cycle ;
%Shape: Ellipse [id:dp1335804494634698]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (405.99,267.68) .. controls (405.99,266.88) and (406.75,266.23) .. (407.68,266.23) .. controls (408.61,266.23) and (409.37,266.88) .. (409.37,267.68) .. controls (409.37,268.48) and (408.61,269.13) .. (407.68,269.13) .. controls (406.75,269.13) and (405.99,268.48) .. (405.99,267.68) -- cycle ;
%Shape: Ellipse [id:dp023679835468487065]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (408.5,234.5) .. controls (408.5,233.7) and (409.26,233.05) .. (410.19,233.05) .. controls (411.13,233.05) and (411.88,233.7) .. (411.88,234.5) .. controls (411.88,235.3) and (411.13,235.95) .. (410.19,235.95) .. controls (409.26,235.95) and (408.5,235.3) .. (408.5,234.5) -- cycle ;
%Shape: Ellipse [id:dp06099440698918057]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (411.02,240.13) .. controls (411.02,239.33) and (411.77,238.68) .. (412.71,238.68) .. controls (413.64,238.68) and (414.39,239.33) .. (414.39,240.13) .. controls (414.39,240.93) and (413.64,241.58) .. (412.71,241.58) .. controls (411.77,241.58) and (411.02,240.93) .. (411.02,240.13) -- cycle ;
%Shape: Ellipse [id:dp40549593342465995]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (413.39,246.24) .. controls (413.39,245.44) and (414.15,244.79) .. (415.08,244.79) .. controls (416.01,244.79) and (416.77,245.44) .. (416.77,246.24) .. controls (416.77,247.04) and (416.01,247.69) .. (415.08,247.69) .. controls (414.15,247.69) and (413.39,247.04) .. (413.39,246.24) -- cycle ;
%Shape: Ellipse [id:dp01628678127720473]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (416.18,252.83) .. controls (416.18,252.03) and (416.94,251.38) .. (417.87,251.38) .. controls (418.8,251.38) and (419.56,252.03) .. (419.56,252.83) .. controls (419.56,253.63) and (418.8,254.28) .. (417.87,254.28) .. controls (416.94,254.28) and (416.18,253.63) .. (416.18,252.83) -- cycle ;
%Shape: Ellipse [id:dp28180899273384075]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (419.53,260.01) .. controls (419.53,259.21) and (420.29,258.56) .. (421.22,258.56) .. controls (422.15,258.56) and (422.91,259.21) .. (422.91,260.01) .. controls (422.91,260.81) and (422.15,261.46) .. (421.22,261.46) .. controls (420.29,261.46) and (419.53,260.81) .. (419.53,260.01) -- cycle ;
%Shape: Ellipse [id:dp5911042519678713]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (422.74,267.68) .. controls (422.74,266.88) and (423.5,266.23) .. (424.43,266.23) .. controls (425.36,266.23) and (426.12,266.88) .. (426.12,267.68) .. controls (426.12,268.48) and (425.36,269.13) .. (424.43,269.13) .. controls (423.5,269.13) and (422.74,268.48) .. (422.74,267.68) -- cycle ;
%Shape: Ellipse [id:dp8945886168905022]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (420.93,234.5) .. controls (420.93,233.7) and (421.68,233.05) .. (422.61,233.05) .. controls (423.55,233.05) and (424.3,233.7) .. (424.3,234.5) .. controls (424.3,235.3) and (423.55,235.95) .. (422.61,235.95) .. controls (421.68,235.95) and (420.93,235.3) .. (420.93,234.5) -- cycle ;
%Shape: Ellipse [id:dp8570857836031784]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (423.72,240.13) .. controls (423.72,239.33) and (424.47,238.68) .. (425.4,238.68) .. controls (426.34,238.68) and (427.09,239.33) .. (427.09,240.13) .. controls (427.09,240.93) and (426.34,241.58) .. (425.4,241.58) .. controls (424.47,241.58) and (423.72,240.93) .. (423.72,240.13) -- cycle ;
%Shape: Ellipse [id:dp8391818891954865]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (427.07,246.36) .. controls (427.07,245.56) and (427.82,244.91) .. (428.75,244.91) .. controls (429.69,244.91) and (430.44,245.56) .. (430.44,246.36) .. controls (430.44,247.16) and (429.69,247.81) .. (428.75,247.81) .. controls (427.82,247.81) and (427.07,247.16) .. (427.07,246.36) -- cycle ;
%Shape: Ellipse [id:dp9979751048489016]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (431.06,253.33) .. controls (431.06,252.53) and (431.81,251.88) .. (432.75,251.88) .. controls (433.68,251.88) and (434.43,252.53) .. (434.43,253.33) .. controls (434.43,254.13) and (433.68,254.78) .. (432.75,254.78) .. controls (431.81,254.78) and (431.06,254.13) .. (431.06,253.33) -- cycle ;
%Shape: Ellipse [id:dp36215680330052313]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (434.88,259.89) .. controls (434.88,259.09) and (435.64,258.44) .. (436.57,258.44) .. controls (437.5,258.44) and (438.26,259.09) .. (438.26,259.89) .. controls (438.26,260.69) and (437.5,261.34) .. (436.57,261.34) .. controls (435.64,261.34) and (434.88,260.69) .. (434.88,259.89) -- cycle ;
%Shape: Ellipse [id:dp15957683841284553]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (439.21,267.68) .. controls (439.21,266.88) and (439.96,266.23) .. (440.9,266.23) .. controls (441.83,266.23) and (442.58,266.88) .. (442.58,267.68) .. controls (442.58,268.48) and (441.83,269.13) .. (440.9,269.13) .. controls (439.96,269.13) and (439.21,268.48) .. (439.21,267.68) -- cycle ;
%Shape: Ellipse [id:dp031888900451443325]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (434.74,234.5) .. controls (434.74,233.7) and (435.5,233.05) .. (436.43,233.05) .. controls (437.36,233.05) and (438.12,233.7) .. (438.12,234.5) .. controls (438.12,235.3) and (437.36,235.95) .. (436.43,235.95) .. controls (435.5,235.95) and (434.74,235.3) .. (434.74,234.5) -- cycle ;
%Shape: Ellipse [id:dp7693048585258591]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (437.53,240.01) .. controls (437.53,239.21) and (438.29,238.56) .. (439.22,238.56) .. controls (440.15,238.56) and (440.91,239.21) .. (440.91,240.01) .. controls (440.91,240.81) and (440.15,241.46) .. (439.22,241.46) .. controls (438.29,241.46) and (437.53,240.81) .. (437.53,240.01) -- cycle ;
%Shape: Ellipse [id:dp9180089420882718]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (441.16,246.24) .. controls (441.16,245.44) and (441.92,244.79) .. (442.85,244.79) .. controls (443.78,244.79) and (444.54,245.44) .. (444.54,246.24) .. controls (444.54,247.04) and (443.78,247.69) .. (442.85,247.69) .. controls (441.92,247.69) and (441.16,247.04) .. (441.16,246.24) -- cycle ;
%Shape: Ellipse [id:dp0046774366657451605]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (445.03,253.25) .. controls (445.03,252.45) and (445.78,251.8) .. (446.71,251.8) .. controls (447.65,251.8) and (448.4,252.45) .. (448.4,253.25) .. controls (448.4,254.05) and (447.65,254.7) .. (446.71,254.7) .. controls (445.78,254.7) and (445.03,254.05) .. (445.03,253.25) -- cycle ;
%Shape: Ellipse [id:dp11704134558060897]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (448.7,260.01) .. controls (448.7,259.21) and (449.45,258.56) .. (450.38,258.56) .. controls (451.32,258.56) and (452.07,259.21) .. (452.07,260.01) .. controls (452.07,260.81) and (451.32,261.46) .. (450.38,261.46) .. controls (449.45,261.46) and (448.7,260.81) .. (448.7,260.01) -- cycle ;
%Shape: Ellipse [id:dp840983843224139]
\draw  [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ] (452.88,267.8) .. controls (452.88,267) and (453.64,266.35) .. (454.57,266.35) .. controls (455.5,266.35) and (456.26,267) .. (456.26,267.8) .. controls (456.26,268.6) and (455.5,269.25) .. (454.57,269.25) .. controls (453.64,269.25) and (452.88,268.6) .. (452.88,267.8) -- cycle ;
%Straight Lines [id:da044880241974145196]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (229.65,229.92) -- (201.56,276.63) ;
%Straight Lines [id:da35659140697327274]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (229.65,229.92) -- (232.88,229.86) ;
%Straight Lines [id:da8266238587264176]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (447.33,230.01) -- (450.55,229.94) ;
%Straight Lines [id:da9857864922537993]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (450.55,229.94) -- (477.67,276.06) ;

%Straight Lines [id:da2042382823552047]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (201.56,276.63) -- (204.78,276.57) ;
%Straight Lines [id:da24758808613421812]
\draw [fill={rgb, 255:red, 139; green, 87; blue, 42 }  ,fill opacity=1 ]   (474.45,276.13) -- (477.67,276.06) ;

%Straight Lines [id:da8014648681612531]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=2.25]    (279.49,253.09) -- (279.35,198.55) ;
\draw [shift={(279.34,193.55)}, rotate = 449.85] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10,-4.8) -- (0,0) -- (10,4.8) -- cycle    ;
%Straight Lines [id:da9755593722308931]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=2.25]    (299.8,253.09) -- (299.8,198.55) ;
\draw [shift={(299.8,193.55)}, rotate = 450] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10,-4.8) -- (0,0) -- (10,4.8) -- cycle    ;
%Straight Lines [id:da4887944803107842]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=2.25]    (339.96,252.91) -- (339.82,198.55) ;
\draw [shift={(339.8,193.55)}, rotate = 449.85] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10,-4.8) -- (0,0) -- (10,4.8) -- cycle    ;
%Straight Lines [id:da5594500357542287]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=2.25]    (359.8,253.09) -- (359.66,198.74) ;
\draw [shift={(359.65,193.74)}, rotate = 449.85] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10,-4.8) -- (0,0) -- (10,4.8) -- cycle    ;
%Straight Lines [id:da14447639458673223]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=2.25]    (379.65,253.28) -- (379.51,198.92) ;
\draw [shift={(379.49,193.92)}, rotate = 449.85] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10,-4.8) -- (0,0) -- (10,4.8) -- cycle    ;
%Straight Lines [id:da5110498857975898]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=2.25]    (319.96,253.09) -- (319.82,198.74) ;
\draw [shift={(319.8,193.74)}, rotate = 449.85] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10,-4.8) -- (0,0) -- (10,4.8) -- cycle    ;
%Straight Lines [id:da05529101568313588]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=2.25]    (399.65,253.87) -- (399.51,199.52) ;
\draw [shift={(399.49,194.52)}, rotate = 449.85] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10,-4.8) -- (0,0) -- (10,4.8) -- cycle    ;
%Shape: Wave [id:dp5678827377050879]
\draw  [color={rgb, 255:red, 229; green, 21; blue, 21 }  ,draw opacity=1 ][line width=1.5]  (340.07,253.67) .. controls (371.62,249.43) and (401.65,245.38) .. (401.65,240.67) .. controls (401.65,235.97) and (371.62,231.91) .. (340.07,227.67) .. controls (308.53,223.43) and (278.5,219.38) .. (278.5,214.67) .. controls (278.5,209.97) and (308.53,205.91) .. (340.07,201.67) .. controls (371.62,197.43) and (401.65,193.38) .. (401.65,188.67) .. controls (401.65,183.97) and (371.62,179.91) .. (340.07,175.67) .. controls (308.53,171.43) and (278.5,167.38) .. (278.5,162.67) .. controls (278.5,157.97) and (308.53,153.91) .. (340.07,149.67) .. controls (371.62,145.43) and (401.65,141.38) .. (401.65,136.67) .. controls (401.65,132.02) and (372.27,128) .. (341.1,123.81) ;
%Straight Lines [id:da6304696424728664]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.61,144.18) -- (366.1,144.15) ;
\draw [shift={(369.1,144.15)}, rotate = 539.94] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da5775075519393338]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.91,129.03) -- (366.27,129.29) ;
\draw [shift={(369.27,129.31)}, rotate = 180.56] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da17397917724158352]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.31,136.58) -- (396.27,136.64) ;
\draw [shift={(399.27,136.65)}, rotate = 180.07] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;

%Straight Lines [id:da8744559241694503]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.82,154.89) -- (313.33,154.91) ;
\draw [shift={(310.33,154.92)}, rotate = 359.94] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da2200628239589839]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.52,170.04) -- (313.17,169.78) ;
\draw [shift={(310.17,169.75)}, rotate = 360.56] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da4508724906014303]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (340.12,162.49) -- (283.17,162.42) ;
\draw [shift={(280.17,162.42)}, rotate = 360.07] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;

%Straight Lines [id:da5092337886497196]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (340.11,207.03) -- (313.62,207.06) ;
\draw [shift={(310.62,207.06)}, rotate = 359.94] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da6247996546979628]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.81,222.18) -- (313.45,221.92) ;
\draw [shift={(310.45,221.89)}, rotate = 360.56] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da8271826274827341]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (340.41,214.63) -- (283.45,214.56) ;
\draw [shift={(280.45,214.56)}, rotate = 360.07] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;

%Straight Lines [id:da39007781287757437]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.61,248.04) -- (366.1,248.01) ;
\draw [shift={(369.1,248)}, rotate = 539.94] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da35345010288254497]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.91,232.89) -- (366.27,233.14) ;
\draw [shift={(369.27,233.17)}, rotate = 180.56] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da40355829843624824]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.31,240.44) -- (396.27,240.5) ;
\draw [shift={(399.27,240.5)}, rotate = 180.07] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;

%Straight Lines [id:da7796918534825454]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (340.18,195.89) -- (366.67,195.87) ;
\draw [shift={(369.67,195.86)}, rotate = 539.94] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da33550184395221083]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (340.48,180.74) -- (366.84,181) ;
\draw [shift={(369.84,181.03)}, rotate = 180.56] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;
%Straight Lines [id:da8038607089311669]
\draw [color={rgb, 255:red, 227; green, 180; blue, 187 }  ,draw opacity=1 ]   (339.88,188.29) -- (396.84,188.36) ;
\draw [shift={(399.84,188.36)}, rotate = 180.07] [fill={rgb, 255:red, 227; green, 180; blue, 187 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (3.57,-1.72) -- (0,0) -- (3.57,1.72) -- cycle    ;

%Straight Lines [id:da4718194144056549]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=2.25]    (419.87,253.83) -- (419.73,199.29) ;
\draw [shift={(419.72,194.29)}, rotate = 449.85] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10,-4.8) -- (0,0) -- (10,4.8) -- cycle    ;
%Straight Lines [id:da8749282737089232]
\draw [color={rgb, 255:red, 20; green, 88; blue, 145 }  ,draw opacity=1 ][line width=2.25]    (259.29,254.09) -- (259.15,199.55) ;
\draw [shift={(259.14,194.55)}, rotate = 449.85] [fill={rgb, 255:red, 20; green, 88; blue, 145 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10,-4.8) -- (0,0) -- (10,4.8) -- cycle    ;

% Text Node
\draw (210.19,110.6) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {\begin{minipage}[lt]{86.06pt}\setlength\topsep{0pt}
\begin{center}
\textcolor[rgb]{0.82,0.01,0.11}{{\fontfamily{helvet}\selectfont Electric field of the}}\\\textcolor[rgb]{0.82,0.01,0.11}{{\fontfamily{helvet}\selectfont dressing field}}
\end{center}

\end{minipage}};
% Text Node
\draw (416.31,157.97) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize] [align=left] {\begin{minipage}[lt]{65.66pt}\setlength\topsep{0pt}
\begin{center}
\textcolor[rgb]{0.08,0.35,0.57}{{\fontfamily{helvet}\selectfont Stationary}}\\\textcolor[rgb]{0.08,0.35,0.57}{{\fontfamily{helvet}\selectfont magnetic field}}
\end{center}

\end{minipage}};
% Text Node
\draw (472.14,246.29) node [anchor=north west][inner sep=0.75pt]   [align=left] {2DEG};
% Text Node
\draw (188.91,167.7) node [anchor=north west][inner sep=0.75pt]    {$\boldsymbol{z}$};
% Text Node
\draw (167.77,226.99) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {${\displaystyle \boldsymbol{x}}$};
% Text Node
\draw (235.99,198.84) node [anchor=north west][inner sep=0.75pt]    {$\boldsymbol{y}$};

\end{tikzpicture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2021-07-18 theory/figures/fig_2new.tex
Improve figures

\documentclass{standalone}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz,pgf} %and any other packages or tikzlibraries your picture needs
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{mathtools}
\usetikzlibrary{shapes,arrows,patterns}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Pattern Info

\tikzset{
pattern size/.store in=\mcSize,
pattern size = 5pt,
pattern thickness/.store in=\mcThickness,
pattern thickness = 0.3pt,
pattern radius/.store in=\mcRadius,
pattern radius = 1pt}
\makeatletter
\pgfutil@ifundefined{pgf@pattern@name@_sbtxotmvc}{
\pgfdeclarepatternformonly[\mcThickness,\mcSize]{_sbtxotmvc}
{\pgfqpoint{0pt}{-\mcThickness}}
{\pgfpoint{\mcSize}{\mcSize}}
{\pgfpoint{\mcSize}{\mcSize}}
{
\pgfsetcolor{\tikz@pattern@color}
\pgfsetlinewidth{\mcThickness}
\pgfpathmoveto{\pgfqpoint{0pt}{\mcSize}}
\pgfpathlineto{\pgfpoint{\mcSize+\mcThickness}{-\mcThickness}}
\pgfusepath{stroke}
}}
\makeatother

% Pattern Info

\tikzset{
pattern size/.store in=\mcSize,
pattern size = 5pt,
pattern thickness/.store in=\mcThickness,
pattern thickness = 0.3pt,
pattern radius/.store in=\mcRadius,
pattern radius = 1pt}
\makeatletter
\pgfutil@ifundefined{pgf@pattern@name@_6w8gp62zx}{
\pgfdeclarepatternformonly[\mcThickness,\mcSize]{_6w8gp62zx}
{\pgfqpoint{0pt}{0pt}}
{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
{\pgfpoint{\mcSize}{\mcSize}}
{
\pgfsetcolor{\tikz@pattern@color}
\pgfsetlinewidth{\mcThickness}
\pgfpathmoveto{\pgfqpoint{0pt}{0pt}}
\pgfpathlineto{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
\pgfusepath{stroke}
}}
\makeatother

% Pattern Info

\tikzset{
pattern size/.store in=\mcSize,
pattern size = 5pt,
pattern thickness/.store in=\mcThickness,
pattern thickness = 0.3pt,
pattern radius/.store in=\mcRadius,
pattern radius = 1pt}
\makeatletter
\pgfutil@ifundefined{pgf@pattern@name@_zm822ewj2}{
\pgfdeclarepatternformonly[\mcThickness,\mcSize]{_zm822ewj2}
{\pgfqpoint{0pt}{0pt}}
{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
{\pgfpoint{\mcSize}{\mcSize}}
{
\pgfsetcolor{\tikz@pattern@color}
\pgfsetlinewidth{\mcThickness}
\pgfpathmoveto{\pgfqpoint{0pt}{0pt}}
\pgfpathlineto{\pgfpoint{\mcSize+\mcThickness}{\mcSize+\mcThickness}}
\pgfusepath{stroke}
}}
\makeatother
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Rectangle [id:dp9138712933038846]
\draw  [color={rgb, 255:red, 255; green, 255; blue, 255 }  ,draw opacity=1 ][pattern=_sbtxotmvc,pattern size=5.550000000000001pt,pattern thickness=0.75pt,pattern radius=0pt, pattern color={rgb, 255:red, 230; green, 228; blue, 228}] (210.57,130.37) -- (429.86,130.37) -- (429.86,169.4) -- (210.57,169.4) -- cycle ;
%Straight Lines [id:da062381655627882227]
\draw [line width=0.75]    (320.14,216.43) -- (319.86,93.43) ;
\draw [shift={(319.86,90.43)}, rotate = 449.87] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (5.36,-2.57) -- (0,0) -- (5.36,2.57) -- cycle    ;
%Shape: Boxed Line [id:dp7700428726953505]
\draw [line width=0.75]    (210.14,210.14) -- (443.6,210.42) ;
\draw [shift={(446.6,210.43)}, rotate = 180.07] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (5.36,-2.57) -- (0,0) -- (5.36,2.57) -- cycle    ;
%Straight Lines [id:da1183130111686681]
\draw [color={rgb, 255:red, 15; green, 77; blue, 150 }  ,draw opacity=1 ]   (210.26,190.14) -- (429.97,189.86) ;
%Straight Lines [id:da9178920527162777]
\draw [color={rgb, 255:red, 15; green, 77; blue, 150 }  ,draw opacity=1 ]   (210.66,150.14) -- (430.66,150.14) ;
%Straight Lines [id:da18288396037355947]
\draw [color={rgb, 255:red, 15; green, 77; blue, 150 }  ,draw opacity=1 ]   (209.46,110.54) -- (429.46,110.54) ;
%Straight Lines [id:da7423332306251238]
\draw [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ][line width=0.75]  [dash pattern={on 4.5pt off 4.5pt}]  (210.29,129.8) -- (429.86,130.37) ;
%Straight Lines [id:da5380911943955708]
\draw [color={rgb, 255:red, 155; green, 155; blue, 155 }  ,draw opacity=1 ] [dash pattern={on 4.5pt off 4.5pt}]  (216,169.11) -- (435.57,169.69) ;
%Straight Lines [id:da5108918794430821]
\draw [color={rgb, 255:red, 245; green, 166; blue, 35 }  ,draw opacity=1 ]   (210.29,139.94) -- (430.14,140.37) ;
%Shape: Circle [id:dp6526443567602316]
\draw  [pattern=_6w8gp62zx,pattern size=1.9500000000000002pt,pattern thickness=0.75pt,pattern radius=0pt, pattern color={rgb, 255:red, 155; green, 155; blue, 155}] (346.39,148.12) .. controls (347.41,146.29) and (349.72,145.64) .. (351.55,146.66) .. controls (353.37,147.68) and (354.02,149.99) .. (353,151.81) .. controls (351.98,153.64) and (349.67,154.29) .. (347.85,153.27) .. controls (346.02,152.25) and (345.37,149.94) .. (346.39,148.12) -- cycle ;
%Shape: Circle [id:dp3302958539355392]
\draw  [pattern=_zm822ewj2,pattern size=1.9500000000000002pt,pattern thickness=0.75pt,pattern radius=0pt, pattern color={rgb, 255:red, 155; green, 155; blue, 155}] (397.89,140.56) .. controls (397.89,138.47) and (399.58,136.77) .. (401.67,136.77) .. controls (403.76,136.77) and (405.46,138.47) .. (405.46,140.56) .. controls (405.46,142.65) and (403.76,144.34) .. (401.67,144.34) .. controls (399.58,144.34) and (397.89,142.65) .. (397.89,140.56) -- cycle ;
%Curve Lines [id:da4768841907072914]
\draw [color={rgb, 255:red, 200; green, 31; blue, 51 }  ,draw opacity=1 ]   (349.86,145) .. controls (353.28,116.82) and (383.19,108.39) .. (397.87,129.76) ;
\draw [shift={(399.4,132.2)}, rotate = 240.15] [fill={rgb, 255:red, 200; green, 31; blue, 51 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (7.14,-3.43) -- (0,0) -- (7.14,3.43) -- cycle    ;
%Straight Lines [id:da804813251167583]
\draw    (350.14,205) -- (350.29,215.86) ;
%Straight Lines [id:da9646977497816096]
\draw    (379.92,205.11) -- (380.06,215.97) ;
%Straight Lines [id:da10347201047155785]
\draw    (360.14,205) -- (360.29,215.86) ;
%Straight Lines [id:da030579557349847963]
\draw    (370.14,205.57) -- (370.29,216.43) ;
%Straight Lines [id:da5754192540908345]
\draw    (390.14,204.56) -- (390.29,215.41) ;
%Straight Lines [id:da7881344991506445]
\draw    (419.92,204.67) -- (420.06,215.52) ;
%Straight Lines [id:da5081549699459584]
\draw    (400.14,204.56) -- (400.29,215.41) ;
%Straight Lines [id:da7295740773263839]
\draw    (410.14,205.13) -- (410.29,215.98) ;
%Straight Lines [id:da29498141413358026]
\draw    (270.14,205.22) -- (270.29,216.08) ;
%Straight Lines [id:da05159592463246754]
\draw    (299.92,205.33) -- (300.06,216.19) ;
%Straight Lines [id:da8075283207227479]
\draw    (280.14,205.22) -- (280.29,216.08) ;
%Straight Lines [id:da5383953202315974]
\draw    (290.14,205.79) -- (290.29,216.65) ;
%Straight Lines [id:da4613327018299631]
\draw    (310.14,204.78) -- (310.29,215.63) ;
%Straight Lines [id:da2686333335167921]
\draw    (339.92,204.89) -- (340.06,215.75) ;
%Straight Lines [id:da00021650773652504007]
\draw    (330.14,205.35) -- (330.29,216.21) ;
%Straight Lines [id:da02622977015161565]
\draw    (219.48,204.67) -- (219.62,215.52) ;
%Straight Lines [id:da36110488827684883]
\draw    (229.7,204.11) -- (229.84,214.97) ;
%Straight Lines [id:da8472813973801454]
\draw    (259.48,204.22) -- (259.62,215.08) ;
%Straight Lines [id:da674226541094751]
\draw    (239.7,204.11) -- (239.84,214.97) ;
%Straight Lines [id:da7672438249417022]
\draw    (249.7,204.68) -- (249.84,215.54) ;
%Straight Lines [id:da0871509351896862]
\draw    (429.92,204.82) -- (430.06,215.68) ;

% Text Node
\draw (319.71,74.34) node [anchor=north west][inner sep=0.75pt]    {$\text{Energy}$};
% Text Node
\draw (449.71,201.29) node [anchor=north west][inner sep=0.75pt]    {$k_{x}$};
% Text Node
\draw (434.66,145.77) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 15; green, 77; blue, 150 }  ,opacity=1 ]  {$\varepsilon _{\beta }$};
% Text Node
\draw (196.29,134.31) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 245; green, 166; blue, 35 }  ,opacity=1 ]  {$\varepsilon $};
% Text Node
\draw (335.2,152.77) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {$\ket{\psi _{\beta }}$};
% Text Node
\draw (397.49,113.6) node [anchor=north west][inner sep=0.75pt]  [font=\normalsize]  {$\ket{\Psi _{\alpha }}$};

\end{tikzpicture}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%COPY HERE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2021-07-19 paper/v1.0/sections/8_manipulate_conductivity.tex
Improve figures and results

@@
 To identify the characteristics of the transverse conductivity of the quantum Hall systems with external dressing field, first we can derive a expression for a normalized
-transverse conductivity as a function of fermi energy $X_F$ and intensity of the dressing field $I$. Here we have normalized the conductivity using the natural conductivity of least Landau level.
+transverse conductivity as a function of fermi energy $X_F$ and intensity of the dressing field $I$.
+Here we have the normalized x-directional conductivity using the natural conductivity of least Landau level
 \begin{equation} \label{eq_35}
   \begin{aligned}
-    \sigma^{xx}(X_F,I) = &
+    \sigma^{xx}/\sigma^{0} = &
     \sum_{n}
@@
 \end{equation}
+where $\sigma^0 = (e^2/\pi \hbar A)$.
 We use this expression to illustrate the changes that can be done to the transverse conductivity in 2DEG using external dressing field.
@@
 \includegraphics[scale=0.55]{figures/fig_5}
-\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
+\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
@@
 \includegraphics[scale=0.55]{figures/fig_6}
-\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.

### 2021-07-19 paper/v1.0/sections/4_inverse_scattering_time.tex
Rearrange the sections and names

--- 2021-07-17 paper/v1.0/sections/5_inverse_scattering_time.tex
@@
+% Section 04 - Inverse Scattering Time Analysis
+
 In Ref.
@@
 \end{equation}
+
+\begin{figure}[t]
+\includegraphics[scale=0.68]{figures/fig_3}
+\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
+In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[scale=0.68]{figures/fig_4}
+\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
+In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
+\end{figure}
+
 In addition, for the case of scattering within a same Landau level, one can present the delta distribution of the energy using the same physical interpretation \cite{dini16} as follows
@@
 When the applied field's intensity increase the energy broadening gets reduced which make changes in conductivity of 2DEG.
-\begin{figure}[t]
-\includegraphics[scale=0.9]{figures/fig_3}
-\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
-In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
-\end{figure}
-\begin{figure}[t]
-\includegraphics[scale=1]{figures/fig_4}
-\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
-In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
-\end{figure}

### 2021-07-19 paper/v1.0/sections/7_conclusions.tex
Rearrange the sections and names

In this analysis, we reported a generalized mathematical model for trasport propeties in a 2DEG under a stationary magnetic field and a dressing field. With the uniform magnetic field charged particles can only settle in discrete energy values and this leads to the Landau quantization. We modelled the behaviour of electrons in Landau levels under the dressing field utilizing Floquet-Drude conductivity method by accounting imputies in the material as Gaussian random scattering potential. Finally we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considering system.

Our derived analytical expressions revealed that the electric conductivity of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analysed the manipulation of conductivity components using the dressing field. We found that the graphical illustrations we gained are capable of produce the same behaviour as the experiment conductivity found in quantum Hall systems withiout a dressing field. Furthermore we identified that by regulating the intensity of radiation, the conductivity regions near Landau levels can be squeezed. Dispite this behavour has been identified previous works, their results are not concide with the more accurate description of conductivity components in undressed quantum Hall systems. However our generalized analysis of conductivity in dressed quantum Hall system provides well-suited description for  these special quantum Hall systems.

In summary, the primary purpose of this paper were to expand the current descriptions on trasport properties in dressed quantum Hall systems and our  detailed theoritical analysis shows that we were able to demostrate that recently introduced Floquet-Drude conductivty model can be adopted to extend the models that are used to describe the trasport characteristics in quantum Hall systems. Finally, we identify that our relizations of this paper can be used towards creating nanoscale quantum devices, understaning their mechanism and enhancing their performance. Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum swtiching devices which are employed as buiding blocks of next generation nanoscale electronic devices.

### 2021-07-19 paper/v1.0/sections/4_inverse_scattering_time.tex
Correcting effective mass

@@
 To make comparison we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
-In their study, they have assumed that the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.
+In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e = 0.07m$ where $m$ is mass of the electron \cite{endo09,winkler03,wackerl20} and the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.
 Therefore in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.

### 2021-07-19 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Rearrange the sections and names
Correcting effective mass

--- 2021-07-17 paper/v1.0/sections/7_floquet_drude_conductivity.tex
@@
+% Section 05 - Floquet-Drude Conductivity in Quantum Hall Systems
+
 A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M.
@@
 \end{equation}
+
+\noindent
 where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ th Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectvely defined against the Floquet modes of the considering system.

### 2021-07-19 paper/v1.0/sections/7_conclusions.tex
Correct conclusion

@@
 In summary, the primary purpose of this paper were to expand the current descriptions on trasport properties in dressed quantum Hall systems and our  detailed theoritical analysis shows that we were able to demostrate that recently introduced Floquet-Drude conductivty model can be adopted to extend the models that are used to describe the trasport characteristics in quantum Hall systems.
-Finally, we identify that our relizations of this paper can be used towards creating nanoscale quantum devices, understaning their mechanism and enhancing their performance.
-Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum swtiching devices which are employed as buiding blocks of next generation nanoscale electronic devices.
+Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum swtiching devices which are employed as the buiding blocks of next generation nano-electronic devices.
+Finally, we identified that our findings of this paper can be used towards understaning nanoscale quantum devices, enhancing their performance and inventing novel appliance.

### 2021-07-20 paper/v1.0/abstract.tex
Correct abstract paper
Formatting paper

--- 2021-06-27 paper/v1.0/abstract.tex
@@
-Interactions between light and matter have dragged research attention in the fields of optoelectronics, sensing, energy harvesting, quantum computing, bio-information, and in many branches of recent technologies.
-For many years, the foremost aims for examing the characteristics of dressed fermion systems were focused on the different types of atomic and molecular arrangements.
-These researches of extreme electron-light engagements introduced an astonishing scope of twentieth-century physics namely quantum optic physics.
+A generalized mathematical model for the transport properties of quantum systems exposed to a stationary magnetic and a strong electromagnetic field is presented.
+The new formulation, which applies to the two-dimensional dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
+We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields.
+To analyze the strong light coupling with the 2DEG, we utilize the Floquet theory as a nonperturbative procedure.
+Moreover, the Floquet Fermi golden rule is adopted to explore the scattering effects against Floquet states in disordered quantum Hall systems.
+Based on our fully analytical expression and particular graphical representations, we demonstrate that the characteristics of conductivities in two-dimensional quantum Hall systems can be manipulated using a strong light.
+The outcomes align with the theoretical descriptions which are already well-suited with experimental results and at the same time our theory provides a more generalized analysis on the characteristics of conductivity of quantum Hall systems.
+Thus, this model more realistically describes that how to employ external strong radiation as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-scale quantum devices.

### 2021-07-20 paper/v1.0/sections/appendix_b.tex
Add Appendix c paper
Formatting paper

@@
   \begin{aligned}
-    \psi_{\alpha}(x,y,t)  = &
+    \psi_{\alpha}&(x,y,t)  =
     \exp(\frac{i}{\hbar}\qty[-\varepsilon_nt + \Delta_{\varepsilon} t ])
@@
   \varepsilon_{n} =
-  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon}
+  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
 \end{equation}
@@
 
-To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ for Eq.~(\ref{eq_7})
+To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ for Eq.~(\ref{eq_7}):
 \begin{equation} \label{eq_b8}
   \begin{aligned}
-    \phi_{n,m}(k_x,k_y,t)  &=
+    \phi_{n,m}&(k_x,k_y,t) \\
+    & =
+    \exp(
+     \frac{-i\gamma(t)}{\hbar}
+     y_0)
+    \exp(\frac{-i}{\hbar}
+    \qty[
+    m_e \dot{\zeta}(t) \zeta(t) - \xi
+    ])\\
+    & \times
     \int_{-L_y/2}^{L_y/2} dy\; \exp(-i\qty[k_y - \gamma(t)]y)
@@
      \exp(-ik_x x)
-     \exp( \frac{i p_x }{\hbar}x ) \\
-     &
-     \times
-     \exp(
-      \frac{-i\gamma(t)}{\hbar}
-      y_0)
-     \exp(\frac{-i}{\hbar}
-     \qty[
-     m_e \dot{\zeta}(t) \zeta(t) - \xi
-     ]),
+     \exp( \frac{i p_x }{\hbar}x ),
   \end{aligned}
@@
   \begin{aligned}
-    \phi_{n,m}(k_x,k_y,t)  =
+    \phi_{n,m}&(k_x,k_y,t)  = 
+    \Phi_{n,m}(k_y,t)
+    \delta_{k_x,\frac{p_x}{\hbar}}\\
+    & \times
     \exp(
      \frac{-i\gamma(t)}{\hbar}
-     y_0) &
+     y_0)
     \exp(\frac{-i}{\hbar}
@@
     m_e \dot{\zeta}(t) \zeta(t) - \xi
-    ]) \\
-    & \times
-    \Phi_{n,m}(k_y,t)
-    \delta_{k_x,\frac{p_x}{\hbar}}.
+    ]).
   \end{aligned}
@@
 \begin{equation} \label{eq_b12}
+  \begin{aligned}
     \Phi_{n,m}(k_y,t) \equiv
     \sqrt{L_x}
-  \int_{-L_y/2}^{L_y/2} dy\;
-  \chi_{n}\qty[y - \mu(t)]
+    \int_{-L_y/2}^{L_y/2} dy\; &
+    \chi_{n}\qty[y - \mu(t)] \\
+    & \times
     \exp(
@@
       y).
+  \end{aligned}
 \end{equation}

### 2021-07-20 paper/v1.0/sections/1_introduction.tex
Rearrange the sections and names
Corrections introduction

@@
+% Section 01 - Introduction
+
 Manipulating physical systems as a consequence of light engagements introduced an astonishing scope of twentieth-century physics namely quantum optics \cite{grynberg10}.
@@
 quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and abundant affiliates of recent technologies \cite{rivera20}.
-The studies on quantum optics of nano-structures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
+The studies on quantum optics of nanostructures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
 However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
 The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance \cite{premaratne21}.
-Among these works, most studies have considered the driving field as a perturbative field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illumination \cite{grifoni98,wackerl20}.
-When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be consider gets increase.
-Then a more accurate and powerful concept need to be adopt and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}.
+Among these works, most studies have considered the driving field as a perturbation field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illumination \cite{grifoni98,wackerl20}.
+When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be considered gets increase.
+Then a more accurate and powerful concept need to be adopted and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}.
 On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
-A theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref.
+Theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref.
 \cite{kibis14,morina15,wackerl20} where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref.
 \cite{wackerl20}, introducing a novel type of Green’s functions namely four-times Green’s functions.
-As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nano-structures by an intense dressing field.
+As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nanostructures by an intense dressing field.
 
-On the other hand, quantum Hall effect \cite{girvin90} observed for two-dimentional fermions systems at low temperatures under strong staionary magnetic field manifest remarkable magneto-transport behaviours and transport properties of these systems attracted many researches attention in experimentally \cite{allerman95,tieke97,pan05} and theoretically \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09}.
+On the other hand, quantum Hall effect \cite{girvin90} observed for two-dimentional fermions systems at low temperatures under strong stationary magnetic field manifest remarkable magneto-transport behaviors and transport properties of these systems attracted many researches attention in experimentally \cite{allerman95,tieke97,pan05} and theoretically \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09}.
 Akira Endo et al.
-\cite{endo09} previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoritical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results \cite{endo09}.
+\cite{endo09} previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoretical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting interpretations for the empirical results \cite{endo09}.
 
-In contrst more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simltaneously applying a dressing field.
+In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simultaneously applying a dressing field.
 Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
-Furthermore K.
+Furthermore, K.
 Dini et al.
-\cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems and they have not adopted the state of art model to describe the conductivity in a quantum Hall system.
+\cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems, and they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
 In their study, they used the conductivity models from T.
@@
 Endo et al.
-work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results.
+work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrations for the experimental results.
 
 In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
-A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantised and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
-Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
-Finaly we demonstrate that our generalised model is agreed with the state of art conductivity model \cite{endo09} already developed for specialised quantum Hall systems that have been considered without the external dressing field.
-Furthermore the mechanism of optical manipulation can be used as a tool to utilise transport properties in various two-dimentional nano-structures which serve as a basis for nano-electronic devices and we belive that our theoritical analysis and visual depictions of results can be used to undestand the basic structure and optimize the performance of optical manipulation of trasport propeties in a two-dimentional quantum Hall system.
+A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized, and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
+Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
+Finally, we demonstrate that our generalized model is agreed with state-of-the-art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field.
+Furthermore, the mechanism of optical manipulation can be used as a tool to utilize transport properties in various two-dimentional nanostructures which serve as a basis for nanoelectronic devices and, we believe that our theoretical analysis and visual depictions of results can be used to understand the basic structure and optimize the performance of optical manipulation of transport properties in a two-dimentional quantum Hall system.

### 2021-07-20 paper/v1.0/sections/__latexindent_temp.tex
Corrections introduction

--- 2021-07-20 paper/v1.0/sections/1_introduction.tex
@@
 Among these works, most studies have considered the driving field as a perturbation field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illumination \cite{grifoni98,wackerl20}.
-When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be considered gets increase.
-Then a more accurate and powerful concept need to be adopted and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}.
+When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be consider gets increase.
+Then a more accurate and powerful concept need to be adopt and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}.
 On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
@@
 \cite{wackerl20}, introducing a novel type of Green’s functions namely four-times Green’s functions.
-As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nanostructures by an intense dressing field.
+As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nano-structures by an intense dressing field.
 
@@
 Akira Endo et al.
-\cite{endo09} previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoretical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting interpretations for the empirical results \cite{endo09}.
+\cite{endo09} previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoretical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting illustration for the experimental results \cite{endo09}.
 
-In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simultaneously applying a dressing field.
+In contrast more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simultaneously applying a dressing field.
 Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
@@
 Endo et al.
-work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrations for the experimental results.
+work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results.
 
 In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
-A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized, and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
+A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
 Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
-Finally, we demonstrate that our generalized model is agreed with state-of-the-art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field.
-Furthermore, the mechanism of optical manipulation can be used as a tool to utilize transport properties in various two-dimentional nanostructures which serve as a basis for nanoelectronic devices and, we believe that our theoretical analysis and visual depictions of results can be used to understand the basic structure and optimize the performance of optical manipulation of transport properties in a two-dimentional quantum Hall system.
+Finally we demonstrate that our generalised model is agreed with the state of art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field.
+Furthermore the mechanism of optical manipulation can be used as a tool to utilise transport properties in various two-dimentional nano-structures which serve as a basis for nano-electronic devices and we believe that our theoretical analysis and visual depictions of results can be used to understand the basic structure and optimize the performance of optical manipulation of transport properties in a two-dimentional quantum Hall system.

### 2021-07-20 paper/v1.0/sections/__latexindent_temp.tex
Corrections section 2

--- 2021-07-17 paper/v1.0/sections/1_introduction.tex
@@
-Manipulating physical systems as a consequence of light engagements introduced an astonishing scope of twentieth-century physics namely quantum optics \cite{grynberg10}.
-Quantum optics have dragged research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
-quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and abundant affiliates of recent technologies \cite{rivera20}. 
-The studies on quantum optics of nano-structures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
-However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
-The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance \cite{premaratne21}.
-Among these works, most studies have considered the driving field as a perturbative field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illumination \cite{grifoni98,wackerl20}.
-When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be consider gets increase.
-Then a more accurate and powerful concept need to be adopt and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}.
-On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
-A theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref.
-\cite{kibis14,morina15,wackerl20} where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref.
-\cite{wackerl20}, introducing a novel type of Green’s functions namely four-times Green’s functions.
-As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nano-structures by an intense dressing field.
+% Section 02 - Schrodinger problem for dressed quantum Hall system
 
-On the other hand, quantum Hall effect \cite{girvin90} observed for two-dimentional fermions systems at low temperatures under strong staionary magnetic field manifest remarkable magneto-transport behaviours and transport properties of these systems attracted many researches attention in experimentally \cite{allerman95,tieke97,pan05} and theoretically \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09}.
-Akira Endo et al.
-\cite{endo09} previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoritical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results \cite{endo09}.
+Our system consist of a two-dimentional free electron gas (2DEG) confined in the $(x,y)$ plane of the three-dimentional coordinate space.
+In our analysis, the 2DEG is subjected to a stationary magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis.
+In addition, a linearly polarized strong light is applied perpendicular to the 2DEG plane, and we specially tune the frequency of the field $\omega$ such that the optical field behaves as a purely dressing field (unabsorbable).
+Without limiting the generality we can choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the dressing field configuration (Fig.~\ref{fig_1}).
+\begin{figure}[b]
+\includegraphics[scale=0.9]{figures/fig_1}
+\caption{\label{fig_1} Two-dimensional electron gas (2DEG) confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and strong dressing field with y-polarized electric field $\vb{E}$ are being applied perpendicular to the surface of 2DEG.}
+\end{figure}
+Here $B$ and $E$ represent the amplitude of the stationary magnetic field and oscillating electric field respectively.
 
-In contrst more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simltaneously applying a dressing field.
-Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
-Furthermore K.
-Dini et al.
-\cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems and they have not adopted the state of art model to describe the conductivity in a quantum Hall system.
-In their study, they used the conductivity models from T.
-Ando et al.
-\cite{ando74_1,ando82} and as mentioned in A.
-Endo et al.
-work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrration for the experimatal results.
-
-In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
-A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantised and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
-Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalised mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
-Finaly we demonstrate that our generalised model is agreed with the state of art conductivity model \cite{endo09} already developed for specialised quantum Hall systems that have been considered without the external dressing field.
-Furthermore the mechanism of optical manipulation can be used as a tool to utilise transport properties in various two-dimentional nano-structures which serve as a basis for nano-electronic devices and we belive that our theoritical analysis and visual depictions of results can be used to undestand the basic structure and optimize the performance of optical manipulation of trasport propeties in a two-dimentional quantum Hall system.
+Using Landau gauge for the stationary magnetic field, we can represent it using vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
+These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04} and this leads to the time-dependent Hamiltonian
+\begin{equation} \label{eq_1}
+  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big(\vb{A}_{s}+\vb{A}_{d}(t)\big)\Big]^2,
+\end{equation}
+where $m_e$ is the effective electron mass and $e$ is the magnitude of the electron charge.
+$\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $p_{x,y}$.
+The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ was already given by Refs.
+\cite{husmi53,ditt98,dini16} and we can present them as a set of wave functions defined by two quantum numbers $(n,m)$
+\begin{equation} \label{eq_2}
+  \begin{aligned}
+    \psi_{n,m}&(x,y,t)  \\
+    & = \frac{1}{\sqrt{L_x}}
+    \chi_n\left[y - y_0 - \zeta(t)\right]\\
+    & \times
+    \text{exp}\bigg(
+    \frac{i}{\hbar}\bigg[- \varepsilon_nt
+    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)\\
+    &+
+    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
+    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
+  \end{aligned}
+\end{equation}
+where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix A.
+Here $L_{x,y}$ are dimension of the 2DEG surface, $\hbar$ is the reduced Planck constant, and $y_0 = -p_x/eB$ is the center of the cyclotron orbit along $y$ axis.
+$\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillator
+\begin{equation} \label{eq_3}
+  \chi_n(x) \equiv
+   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
+  e^{-\kappa^2 x^2/2}
+  \mathcal{H}_n \qty(\kappa x) \quad \text{with}
+  \quad
+  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
+\end{equation}
+with eigenvalues given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 = eB/m_e$ is the cyclotron frequency.
+Each $n$ value defines the  energy($\varepsilon_n$) of the respective Landau level.
+The path shift of the driven classical oscillator $\zeta(t)$ is given by
+\begin{equation} \label{eq_4}
+  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
+\end{equation}
+while the Lagrangian of the classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
+\begin{equation} \label{eq_5}
+  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
+\end{equation}
+The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and strong dressing field.
+Therefore, we can accept that magneto-transport properties of 2DEG will be renormalized by the magnetic field as well as the dressing field.

### 2021-07-20 paper/v1.0/sections/3_floquet_theory.tex
Add section 3 of paper
Rearrange the sections and names
Formatting paper
Corrections spellings

@@
+% Section 03 - Floquet theory perspective
+
 The general interpretations of physical systems are mostly derived using symmetry conditions in quantum theory.
@@
 In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity in presence of a strong dressing field.
-Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyse our 2DEG system which is subjected to both a staionary magnetic field and a strong dressing field.
+Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyze our 2DEG system which is subjected to both a stationary magnetic field and a strong dressing field.
 
-First we need to identify the \textit{quasienergies} and periodic \textit{Floquet modes} for derived wavefunctions in Eq.~(\ref{eq_2}).
-By factorizing the wavefunction into a linearly time dependent part and a peridic time dependend part, the quasienergies can be present as
+First we need to identify the \textit{quasienergies} and periodic \textit{Floquet modes} for derived wave functions in Eq.~(\ref{eq_2}).
+By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can be present as
 \begin{equation} \label{eq_6}
@@
 \end{equation}
-which is only depend on single quantum number ($n$) and Floquet modes are given by
+which is only depended on single quantum number ($n$) and Floquet modes are given by
 \begin{equation} \label{eq_7}
@@
     \phi_{n,m}(x,y,t) = &
-    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]
+    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]\\
+    & \times
     \text{exp}\bigg(
      \frac{i}{\hbar}\bigg[
-     p_x x \\
-     & +
+     p_x x +
      \frac{eE(y - y_0)}{\omega}\cos(\omega t) \\
@@
 It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
+At the resonance $\omega = \omega_0$, the energy levels occupies a continuous form and the discrete quasienergies are no longer valid \cite{popov70}.
+Therefore, in this work we choose the dressing field frequency as $\omega \neq \omega_0$.
 
-Then performing Fourier trasform over the confined two-dimentional space $A=L_xL_y$, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
-\begin{equation} \label{eq_10}
+Then performing Fourier transform over the confined two-dimentional space $A=L_xL_y$, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
+\begin{equation} \label{eq_9}
   \begin{aligned}
@@
 where
-\begin{equation} \label{eq_11}
+\begin{equation} \label{eq_10}
   \tilde{\chi}_{n}\qty(k) =
@@
 and
-\begin{equation} \label{eq_12}
+\begin{equation} \label{eq_11}
   b \equiv
@@
 For details of the formalism the authors refer to Appendix B. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
-\begin{equation} \label{eq_9}
+\begin{equation} \label{eq_12}
   \psi_{n,m}(k_x,k_y,t) =

### 2021-07-20 paper/v1.0/sections/4_inverse_scattering_time.tex
Formatting paper
Corrections spellings

@@
 In Ref.
-\cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyse transport propeties in dressed quantum systems.
-However, this theory has not been applied for a dressed quantum Hall system and to identify magnetotransport properties in our system we use Floquet Fermi golden rule.
+\cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyze transport properties in dressed quantum systems.
+However, this theory has not been applied for a dressed quantum Hall system and to identify magneto-transport properties in our system we use Floquet Fermi golden rule.
 With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
@@
 $J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C.
-In this study, the perturbation potential is assumed to be formed by an ensemble of randomly distributed impurities, since random impurities in a disorded metal is a better approximation for experimental results.
+In this study, the perturbation potential is assumed to be formed by an ensemble of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results.
 The total  scattering potential in 2DEG is then given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$.
@@
 
-Next we are going to analyse the contribution of the inverse scattering time matrix elements to the transport properies in 2DEG.
-The disorder in the system is not supposed to change the eigenenergies of the bare system \cite{wackerl20}, hence all off-diogonal elements of the self-energy were neglected and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+Next we are going to analyze the contribution of the inverse scattering time matrix elements to the transport properties in 2DEG.
+The disorder in the system is not supposed to change the eigenenergies of the bare system \cite{wackerl20}, hence all off-diogonal elements of the self-energy were neglected, and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
 % \begin{equation} \label{eq_14}
@@
   \begin{aligned}
-    \Gamma^{00}_{N}(\varepsilon,k_x)  &=
+    \Gamma^{00}_{N}(\varepsilon,& k_x) =
     \varrho
@@
 where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
-To analyze the contribution of dressing field on the scatering-induced broadening, normalized $N$-th Landau level scatering-induced broadening can be defined as
+To analyze the contribution of dressing field on the scattering-induced broadening, normalized $N$-th Landau level scattering-induced broadening can be defined as
 \begin{equation} \label{eq_18}
@@
 In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e = 0.07m$ where $m$ is mass of the electron \cite{endo09,winkler03,wackerl20} and the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.
-Therefore in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
-Here we can identify that we can change the each Landau level normalized energy broadening value using apllied electromagnetic field.
+Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
+Here we can identify that we can change each Landau level normalized energy broadening value using applied electromagnetic field.
 When the applied field's intensity increase the energy broadening gets reduced which make changes in conductivity of 2DEG.

### 2021-07-20 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Formatting paper
Corrections spellings

@@
     )
-    ]\bigg].
+    ]\bigg],
   \end{aligned}
 \end{equation}
-
-\noindent
-where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ th Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectvely defined against the Floquet modes of the considering system.
-Here we have assumed that only $s=0$ th Fourier component of the current operator is contributing to the conductivity.
-In addition $A$ is the area of the considering two-dimentionl system, partical distribution function is given by $f$ and $\lambda$ is a function that can be choose such that
+where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system.
+Here we have assumed that only $s=0$ the Fourier component of the current operator is contributing to the conductivity.
+In addition, $A$ is the area of the considering two-dimentional system, partial distribution function is given by $f$ and $\lambda$ is a function that can be chosen such that
 \begin{equation} \label{eq_21}
@@
 \end{equation}
-where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evalute by considering each matrix elements seperatly
+where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evaluate by considering each matrix elements separately
 \begin{equation} \label{eq_23}
@@
 \end{equation}
-Since we can diagonalize the impurity averaged Green's function using unitary trasnformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Ref.~\cite{wackerl20,wackerlthesis20,tsuji08} and we evaluate the matrix element of the differece between retarded and advanced Green's functions
+Since we can diagonalize the impurity averaged Green's function using unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Ref.~\cite{wackerl20,wackerlthesis20,tsuji08}, and we evaluate the matrix element of the difference between retarded and advanced Green's functions
 \begin{equation} \label{eq_24}
@@
 \end{equation}
-using the retared self-energy matrix $\vb{\Sigma}^r$ which is the sum over all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
+using the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum over all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
 Applying the matrix elements of electric current operator in Landau levels (see Appendix D) and
@@
 \end{equation}
-Since the inverse scattering time matrix being equal to the diagonalized differece of the retared and advanced self-energy and on the diagonal the differece of the retarded and advanced Green's function is equal to the imaginary part of the retared self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property
+Since the inverse scattering time matrix being equal to the diagonalized difference of the retared and advanced self-energy and on the diagonal the difference of the retarded and advanced Green's function is equal to the imaginary part of the retared self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property
 \begin{equation} \label{eq_28}
   \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll} =
-  -2\text{Im}\qty[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}]^{ll}
+  -2\text{Im}\qty[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}]^{ll},
 \end{equation}
@@
 with $\Gamma(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
-We already identited that the inverse scattering time matrix's central element is not $k_x$ dependent we can get the sum over all available momentum space in $x$ direction.
-However by considering the condition that the center of the force of the oscillator $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify
+We already identified that the inverse scattering time matrix's central element is not $k_x$ dependent we can get the sum over all available momentum space in $x$ direction.
+However, by considering the condition that the center of the force of the oscillator $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify
 \begin{equation} \label{eq_30}
@@
 \end{equation}
-Then using Fermi-Dirac distribution as our partical distribution function ($f$) for this system
+Then using Fermi-Dirac distribution as our partial distribution function ($f$) for this system
 \begin{equation} \label{eq_31}
-  f(\varepsilon) = \frac{1}{\qty[\exp(\varepsilon - \varepsilon_F)/k_B T]+1}
+  f(\varepsilon) = \frac{1}{\qty[\exp(\varepsilon - \varepsilon_F)/k_B T]+1},
 \end{equation}
-where $k_B$ is Botlzmann constant, $T$ is absolute tempurature and $\varepsilon_F$ is Fermi energy of the system.
-Considering the above distribution with extreamly low tempurature conditions we can appromixate
+where $k_B$ is Boltzmann constant, $T$ is absolute temperature and $\varepsilon_F$ is Fermi energy of the system.
+Considering the above distribution with extremely low temperature conditions we can approximate
 \begin{equation} \label{eq_32}
-  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F)
+  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F),
 \end{equation}
@@
     \frac{e^2}{\hbar}
-    \frac{1}{\pi A}
-    \sum_{n} &
+    \frac{1}{\pi A} &
+    \sum_{n}
     \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}} \\
@@
     \frac{e^2}{\hbar}
-    \frac{1}{\pi A}
-    \frac{1}{e^2B^2} &
+    \frac{1}{\pi A}&
+    \frac{1}{e^2B^2}
     \sum_{n}

### 2021-07-20 paper/v1.0/sections/6_manipulate_conductivity.tex
Rearrange the sections and names
Formatting paper
Corrections spellings

--- 2021-07-19 paper/v1.0/sections/8_manipulate_conductivity.tex
@@
-To identify the characteristics of the transverse conductivity of the quantum Hall systems with external dressing field, first we can derive a expression for a normalized
-transverse conductivity as a function of fermi energy $X_F$ and intensity of the dressing field $I$.
-Here we have the normalized x-directional conductivity using the natural conductivity of least Landau level
+% Section 06 - Manipulate Conductivity in Quantum Hall Systems
+
+To identify the characteristics of the transverse conductivity of the quantum Hall systems with external dressing field, first we can derive an expression for a normalized
+transverse conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
+Here we have the normalized x-directional conductivity using the natural conductivity of the least Landau level
 \begin{equation} \label{eq_35}
   \begin{aligned}
-    \sigma^{xx}/\sigma^{0} = &
+    \frac{\sigma^{xx}}{\sigma^{0}} = &
     \sum_{n}
@@
       }
-    ]
+    ],
   \end{aligned}
@@
 As given in Fig.~\ref{fig_4} and \ref{fig_5} we can manipulate the transverse conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system.
-For a given dressing field intesity, the transverse conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values.
+For a given dressing field intensity, the transverse conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values.
 Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not align with any of the Landau level energy values.
@@
 Considering the effect of the external dressing field on transverse conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels.
-However the peak value of the conductivity at each Landau level has the same value as the undressed system.
-This demostrate that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
-These characteristics are align with results demostrated by K.
-Dini et al.\cite{dini16} and as they remarked since the Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for optoelectonic applications.
+However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
+This demonstrate that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
+These characteristics are aligned with results demonstrated by K.
+Dini et al.\cite{dini16} and as they remarked since the Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications.
 Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
-Furthermore we can distinguish that the shapes and behavoiur of the conductivity regions illustrated in Fig.~\ref{fig_4} and \ref{fig_5} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_4} and \ref{fig_5} are generally incompatible with the results reported in Ref.~\cite{dini16}.
 This is due to the selection of the conventional transverse conductivity theory of 2DEG from Ref.~\cite{ando74_1,ando82}.
-The semi-elliptical conductivity regions illustrated in Ref.~\cite{dini16,ando74_1,ando82}, have less consistance with the experimentally observed Landau levels representation \cite{endo09}.
+The semi-elliptical conductivity regions illustrated in Ref.~\cite{dini16,ando74_1,ando82}, have less consistence with the experimentally observed Landau levels representation \cite{endo09}.
 In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result represented by A.
@@
 \cite{endo09}.
-The description of conductivities of quantum Hall systems demostrated in Ref.~\cite{endo09} has excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range.
-However they have not consider about the tunability that can be achived with the external strong dressing field.
-In this analysis we account both magnetic and dressing field effects that can be applied into the transport properties of 2DEG and we have presented a more generalized theory.
-As a concluding remark, in this study we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the trasport properties of quantum Hall syatems.
+The description of conductivity of quantum Hall systems demonstrated in Ref.~\cite{endo09} has excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range.
+However, they have not considered the tunability that can be achieved with the external strong dressing field.
+In this analysis we account both magnetic and dressing field effects that can be applied into the transport properties of 2DEG, and we have presented a more generalized theory.
+As a concluding remark, in this study we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the transport properties of quantum Hall systems.

### 2021-07-20 paper/v1.0/sections/7_conclusions.tex
Corrections spellings

@@
-In this analysis, we reported a generalized mathematical model for trasport propeties in a 2DEG under a stationary magnetic field and a dressing field.
+In this analysis, we reported a generalized mathematical model for transport properties in a 2DEG under a stationary magnetic field and a dressing field.
 With the uniform magnetic field charged particles can only settle in discrete energy values and this leads to the Landau quantization.
-We modelled the behaviour of electrons in Landau levels under the dressing field utilizing Floquet-Drude conductivity method by accounting imputies in the material as Gaussian random scattering potential.
-Finally we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considering system.
+We modelled the behavior of electrons in Landau levels under the dressing field utilizing Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential.
+Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considering system.
 
 Our derived analytical expressions revealed that the electric conductivity of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity.
-Using detailed numerical calculations with empirical system parameters, we further analysed the manipulation of conductivity components using the dressing field.
-We found that the graphical illustrations we gained are capable of produce the same behaviour as the experiment conductivity found in quantum Hall systems withiout a dressing field.
-Furthermore we identified that by regulating the intensity of radiation, the conductivity regions near Landau levels can be squeezed.
-Dispite this behavour has been identified previous works, their results are not concide with the more accurate description of conductivity components in undressed quantum Hall systems.
-However our generalized analysis of conductivity in dressed quantum Hall system provides well-suited description for  these special quantum Hall systems.
+Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
+We found that the graphical illustrations we gained are capable of produce the same behavior as the experiment conductivity found in quantum Hall systems without a dressing field.
+Furthermore, we identified that by regulating the intensity of radiation, the conductivity regions near Landau levels can be squeezed.
+Despite, this behavior has been identified previous works, their results are not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.
+However, our generalized analysis of conductivity in dressed quantum Hall system provides well-suited description for  these special quantum Hall systems.
 
-In summary, the primary purpose of this paper were to expand the current descriptions on trasport properties in dressed quantum Hall systems and our  detailed theoritical analysis shows that we were able to demostrate that recently introduced Floquet-Drude conductivty model can be adopted to extend the models that are used to describe the trasport characteristics in quantum Hall systems.
-Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum swtiching devices which are employed as the buiding blocks of next generation nano-electronic devices.
-Finally, we identified that our findings of this paper can be used towards understaning nanoscale quantum devices, enhancing their performance and inventing novel appliance.
+In summary, the primary purpose of this paper were to expand the current descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems.
+Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices.
+Finally, we identified that our findings of this paper can be used towards understanding nanoscale quantum devices, enhancing their performance and inventing novel appliance.

### 2021-07-20 paper/v1.0/sections/appendix_a.tex
Add section 4 of paper
Formatting paper
Corrections spellings

--- 2021-06-30 paper/v1.0/sections/appendix_a.tex
@@
 \end{equation}
-and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$ both operators share same (simultaneous) eigen functions
-$\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = m2\pi \hbar/L_x~,~ m \in \mathbb{Z}$.
-Therefore we re-arrange the Hamiltonian using definition of canonical momentum in $y$-direction to derive
+and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$ both operators share same (simultaneous) eigenfunctions
+$\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = 2\pi \hbar m/L_x~,~ m \in \mathbb{Z}$.
+Therefore, we re-arrange the Hamiltonian using definition of canonical momentum in $y$-direction to derive
 \begin{equation} \label{eq_a2}
@@
 We now define the \textit{center of the cyclotron orbit} along $y$ axis $y_0 \equiv {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 \equiv {eB}/{m_e}$.
-This leads to a new arangement of the Hamiltonian
+This leads to a new arrangement of the Hamiltonian
 \begin{equation} \label{eq_a3}
@@
 \end{equation}
-where $\vartheta(\tilde{y},t)$ is a function that need to be find to satisfy the following property
+where $\vartheta(\tilde{y},t)$ is a function that need to be found to satisfy the following property
 \begin{equation} \label{eq_a6}
@@
 \end{equation}
-It is important to notice that we can identify the $S(t) \equiv eE\sin(\omega t)$ part as a external force act on the harmonic oscillator and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis.
+It is important to notice that we can identify the $S(t) \equiv eE\sin(\omega t)$ part as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis.
 \begin{equation} \label{eq_a8}
@@
 
-This system can be extacly solvable and we can solve the equation using the methods explained by Husimi \cite{husmi53} as follows.
-We introduce a time dependent shifted cordinate $ y' = \tilde{y} - \zeta(t)$ and perform following unitary trasformation
+This system can be exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husmi53} as follows.
+We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform following unitary transformation
 \begin{equation} \label{eq_a9}
@@
 \end{equation}
-and this yeilds
+and this yields
 \begin{equation} \label{eq_a10}
   \begin{aligned}
-    i \hbar \pdv{\varphi(y',t)}{t}   =
+    i \hbar \pdv{\varphi(y',t)}{t}   &=
     \bigg[
-        & -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
         + \frac{1}{2} m_e \omega_0^2 y'^2 \\
@@
 \begin{equation} \label{eq_a11}
-  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t)
+  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
 \end{equation}
@@
     \bigg[
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 {y'}^2
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
+        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
+        &
         - L(\zeta,\dot{\zeta},t)
-    \bigg]\varphi(y',t)
+    \bigg]\varphi(y',t),
   \end{aligned}
@@
 \begin{equation} \label{eq_a13}
-  L(\zeta,\dot{\zeta},t) \equiv \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t)
+  L(\zeta,\dot{\zeta},t) \equiv \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
 \end{equation}
-is the largrangian of a classical driven oscillator. To proceed further, another unitary trasform can be introduced as follows
+is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
 \begin{equation} \label{eq_a14}
@@
 \end{equation}
-and subtiting Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yeilds
+and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
 \begin{equation} \label{eq_a15}
@@
 This is the well known Schrödinger equation of the quantum harmonic oscillator.
-This allows us to identify with the well-known eigenfucntions (using Gauss-Hermite functions)
+This allows us to identify with the well-known eigenfunctions \cite{griffiths18,shankar94}
 \begin{equation} \label{eq_a16}
@@
 \begin{equation} \label{eq_a17}
-  \varepsilon_n = \hbar \omega_0 \big(n + \frac{1}{2}\big)
+  \varepsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
   ~,~
@@
 \end{equation}
-Therefore we can identify the solutions of Eq.~(\ref{eq_a8}) as
+Therefore, we can identify the solutions of Eq.~(\ref{eq_a8}) as
 \begin{equation} \label{eq_a18}
@@
     m_e\dot{\zeta(t)}\big(\tilde{y}-\zeta(t)\big) \\
-     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg)
+     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
   \end{aligned}
 \end{equation}
-The set $\{\chi_n(x)\}$ functions forms a complete set and thus any general solution $\vartheta_(\tilde{y},t)$ can be expaned in terms of the solutions given in Eq.~(\ref{eq_a18}).
+The set $\{\chi_n(x)\}$ functions forms a complete set and thus any general solution $\vartheta_(\tilde{y},t)$ can be expanded in terms of the solutions given in Eq.~(\ref{eq_a18}).
 
-Finally we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$ and we can derive the solution for Eq.~(\ref{eq_a11})
+Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq_a11})
 \begin{equation} \label{eq_a19}
@@
 \end{equation}
-Subtiting solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we can obtain the set of wave functions with two different quantum number ($n$,$m$) that satisfy the Schrödinger eqution Eq.~(\ref{eq_a4})
+Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we can obtain the set of wave functions with two different quantum number ($n$,$m$) that satisfy the Schrödinger equation Eq.~(\ref{eq_a4})
 \begin{equation} \label{eq_a20}

### 2021-07-20 paper/v1.0/sections/appendix_b.tex
Corrections spellings

@@
 
-First define the time integral of Laggrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a $T=2\pi/\omega$ period as
+First define the time integral of Lagrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a $T=2\pi/\omega$ period as
 \begin{equation} \label{eq_b1}
@@
 \end{equation}
-Next define another paramter
+Next define another parameter
 \begin{equation} \label{eq_b3}
@@
 \end{equation}
-and after simplying, this leads to
+and after simplifying, this leads to
 \begin{equation} \label{eq_b4}
@@
 which is a periodic function in time with $2\omega$ frequency.
-Now using these  parmaters we can factorize the wavefunction Eq.~(\ref{eq_2}) as linearly time dependend part and periodic time dependend part as follows
+Now using these  parameters we can factorize the wave function Eq.~(\ref{eq_2}) as linearly time dependent part and periodic time dependent part as follows
 \begin{equation} \label{eq_b5}
@@
 \end{equation}
-and this leads to seperate linear time dependent phase component as the quasienergies
+and this leads to separate linear time dependent phase component as the quasienergies
 \begin{equation} \label{eq_b6}
@@
 \end{equation}
-Subtituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is large ($L_y \rightarrow \infty$), we can obtain
+Substituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is large ($L_y \rightarrow \infty$), we can obtain
 \begin{equation} \label{eq_b13}
@@
 \end{equation}
-We can identify that the integral represnts the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{celeghini21} for the Fourier transform of Gauss-Hermite functions $\theta_n(x)$:
+We can identify that the integral represents the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{celeghini21} for the Fourier transform of Gauss-Hermite functions $\theta_n(x)$:
 \begin{equation} \label{eq_b14}
@@
 \end{equation}
-Subtitute Eq.~(\ref{eq_b15}) back in Eq.~(\ref{eq_b11}) and this leads to
+Substitute Eq.~(\ref{eq_b15}) back in Eq.~(\ref{eq_b11}) and this leads to
 \begin{equation} \label{eq_b17}

### 2021-07-20 paper/v1.0/sections/appendix_c.tex
Add more contect to section 5 paper
Add introduction and format
Formatting paper
Corrections spellings

@@
   \ket{\psi_{n,m}(t,t')} =
-  \exp(-\frac{i}{\hbar}\varepsilon_{n} t)\ket{\phi_{n,m}(t')}.
+  \exp(-\frac{i}{\hbar}\varepsilon_{n} t)\ket{\phi_{n,m}(t')},
 \end{equation}
-derived by seperating the aperiodic and periodic components of Eq.~(\ref{eq_12}), fullfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
+derived by separating the aperiodic and periodic components of Eq.~(\ref{eq_12}), fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
 \begin{equation} \label{eq_c2}
@@
 \end{equation}
-Next we can identify the the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation
+Next we can identify the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation
 \begin{equation} \label{eq_c4}
@@
 \end{equation}
-and the advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time odering operatos \cite{wackerl20}.
+and the advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time ordering operators \cite{wackerl20}.
 
@@
 \end{equation}
-by introducing new wave function $\Psi_{n,m}$ for the system with the given total perturabation.
+by introducing new wave function $\Psi_{n,m}$ for the system with the given total perturbation.
 If $t\leq t_0$, both solutions of the Schrödinger equations (Eq.~(\ref{eq_c2}) and Eq.~(\ref{eq_c5})) coincide
@@
 \end{equation}
-and due to time independency, the perturbation in the interaction picture has the same form as Schrödinger picture
+and due to time independence, the perturbation in the interaction picture has the same form as Schrödinger picture
 \begin{equation} \label{eq_c8}
@@
 \end{equation}
-This leads to the $t$-$t'$-Schrödinger eqution in the interction picture
+This leads to the $t$-$t'$-Schrödinger equation in the interaction picture
 \begin{equation} \label{eq_c9}
@@
 \end{equation}
-Iterating the solution only upto the first order (Born approximation) we obtain
+Iterating the solution only up to the first order (Born approximation) we obtain
 \begin{equation} \label{eq_c11}
@@
   \ket{\Psi_{\alpha}(t,t')} = \sum_{\beta} a_{\alpha,\beta}(t,t')
-  \ket{\psi_{\beta}(t,t')}.
+  \ket{\psi_{\beta}(t,t')},
 \end{equation}
@@
 \end{figure}
-It is important to remember that a state of this considering system can be represented by two independent quantum numbers: $n$ represents the landau level and $m$ represents the qunatized momentum in $x$-direction.
-The scattering amplitutde for this scattering scenario can be calculated using the equation derived in Eq.~(\ref{eq_c14})
+It is important to remember that a state of this considering system can be represented by two independent quantum numbers: $n$ represents the landau level and $m$ represents the quantized momentum in $x$-direction.
+The scattering amplitude for this scattering scenario can be calculated using the equation derived in Eq.~(\ref{eq_c14})
 \begin{equation} \label{eq_c16}
@@
 \end{equation}
-and assuiming for a long time $t \rightarrow \infty$, we can turn this integral into a delta distrubution
+and assuming for a long time $t \rightarrow \infty$, we can turn this integral into a delta distribution
 \begin{equation} \label{eq_c17}
@@
 \end{equation}
-and seperating $x$ and $y$ directional momentums we can derive (we already assumed that $L_y \rightarrow \infty$)
+and separating $x$ and $y$ directional momentum we can derive (we already assumed that $L_y \rightarrow \infty$)
 \begin{equation} \label{eq_c19}
@@
     \phi_{\beta}^{\dagger}(\vb{k'},t')
-    \phi_{\alpha}(\vb{k},t').
+    \phi_{\alpha}(\vb{k},t'),
 \end{equation}
@@
 \end{equation}
-Next we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of enerrgy such that the potential is zero on average.
+Next we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
 This model is characterized by \cite{akkermans10}
@@
 \begin{equation} \label{eq_c21a}
-  \expval{\upsilon(\vb{r})}_{imp} =0
+  \expval{\upsilon(\vb{r})}_{imp} =0,
 \end{equation}
 \begin{equation} \label{eq_c21b}
-  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'})
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
 \end{equation}
@@
 where $\expval{\cdot}_{imp}$ denoted the average over realizations of the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
-In addition, this model assume that $\upsilon (\vb{r}-\vb{r'})$ only dependes on the position difference $|\vb{r}-\vb{r'}|$ and it decays with a characteristic leangth $r_c$.
-Since this study considers the case where the waveleagth of radiation or scattering electrons is much faster than $r_c$, it is a good approximation to make two-point correlation function to be
+In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
+Since this study considers the case where the wavelength of radiation or scattering electrons is much faster than $r_c$, it is a good approximation to make two-point correlation function to be
 \begin{equation} \label{eq_c22}
-  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'})
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
 \end{equation}
-where $\Upsilon_{imp}$ is stregth of the delta potential and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}.
+where $\Upsilon_{imp}$ is strength of the delta potential and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}.
 Then we can model approximately the total scattering potential as
@@
 Then we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
-\begin{subequations} \label{eq_24}
+\begin{subequations} \label{eq_c24}
 \begin{align}
@@
 \end{subequations}
-Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs and assuming the total ncumber of scatterers $N_{imp}$ is macroscopically large, we can derive
+Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs and assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
 \begin{subequations} \label{eq_c25}
@@
   V_{{k'}_x,k_x} \equiv
-  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x}.
+  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x},
 \end{equation}
@@
 
-Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25}) on Eq.~(\ref{eq_c19}), we obtain (with changing varable $t' \rightarrow t'$)
+Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25}) on Eq.~(\ref{eq_c19}), we obtain (with changing variable $t' \rightarrow t'$)
 \begin{equation} \label{eq_c27}
@@
 \end{equation}
-Therefore finally the scattering amplitude derived in Eq.~(\ref{eq_c17}) can be evaluated for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as
+Therefore, finally the scattering amplitude derived in Eq.~(\ref{eq_c17}) can be evaluated for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as
 \begin{equation} \label{eq_c32}
@@
 \end{equation}
-where $J_l(z)$ are Bessel functions of the first kind with $l$-th integer order and we can re-write the Eq.~(\ref{eq_c32}) as folllows
+where $J_l(z)$ are Bessel functions of the first kind with $l$-th integer order, and we can re-write the Eq.~(\ref{eq_c32}) as follows
 \begin{equation} \label{eq_c35}
@@
     {\chi}_{N}\qty(y)
-    {\chi}_{N}\qty(y_0 - {y'}_0 - y) e^{-il\omega t}
+    {\chi}_{N}\qty(y_0 - {y'}_0 - y) e^{-il\omega t},
   \end{aligned}
@@
 \end{equation}
-Then desribing the square of the delta distribution using following procedure \cite{dini16,kibis14}
+Then describing the square of the delta distribution using following procedure \cite{dini16,kibis14}
 \begin{equation} \label{eq_c39}
@@
 \end{equation}
-and performing the time derivation of each matrix element yeild the \textit{transition amplitude matrix}:
+and performing the time derivation of each matrix element yield the \textit{transition amplitude matrix}:
 \begin{equation} \label{eq_40}
@@
     \frac{1}{L_x} \sum_{{k'}_x}
-    \expval**{\Gamma_{\alpha\beta}^{ll'}({k'}_x,k_x)}_{imp}
+    \expval**{\Gamma_{\alpha\beta}^{ll'}({k'}_x,k_x)}_{imp},
 \end{equation}
 and applying the 1-dimentional momentum continuum limit $\sum_{{k'}_x} \longrightarrow {L_x}/{2\pi}\int d {k'}_x$ and this leads to
-\begin{widetext}
 \begin{equation} \label{eq_42}
   \begin{aligned}
-    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{\alpha\beta} =
+    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{\alpha\beta} \\
+    & =
     \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar}
     \frac{V_{imp}}{2\pi}
-    \delta(\varepsilon_{\beta} - \varepsilon)
-    \int_{-\infty}^{\infty} d {k'}_x &
+    \delta(\varepsilon_{\beta} - \varepsilon)\\
+    & =
+    \int_{-\infty}^{\infty} d {k'}_x
     J_l\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x])
@@
 \end{equation}
-Using subtitution $k'_x = k_1$ and $y = {\hbar{k_2}}/{eB}$ finally we can derive our expression for the inverse scattering time matrix for $N$-th Landau
+Using substitution $k'_x = k_1$ and $y = {\hbar{k_2}}/{eB}$ finally we can derive our expression for the inverse scattering time matrix for $N$-th Landau
 level
@@
   \begin{aligned}
-    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{N} =
+    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
+    & =
     \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{\qty(eB)^2}
-    \delta(\varepsilon - \varepsilon_{N})
+    \delta(\varepsilon - \varepsilon_{N})\\
+    & \times
     \int_{-\infty}^{\infty} d k_1
-    &
     J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
@@
 \end{equation}
-\end{widetext}

### 2021-07-20 paper/v1.0/sections/appendix_d.tex
Rearrange the sections and names
Formatting paper
Corrections spellings

@@
 In this section we are hoping to derive the current density operator for $N$-th Landau level.
-We already found the extact solution for our time depenedent Hamiltonian Eq.~(\ref{eq_1}) and we identified them as Floquet states with quesienergies Eq.~(\ref{eq_12}).
+We already found the exact solution for our time dependent Hamiltonian Eq.~(\ref{eq_1}) and we identified them as Floquet states with quasienergies Eq.~(\ref{eq_12}).
 The Floquet modes derived in Eq.
@@
 \begin{equation} \label{eq_d1}
-  \ket{\phi_{n,m}} \equiv \ket{n,k_x}
+  \ket{\phi_{n,m}} \equiv \ket{n,k_x}.
 \end{equation}
@@
 \begin{equation} \label{eq_d3}
-  \hat{\vb{j}} = \frac{1}{m} \qty(\hat{\vb{p}} - e\qty[\vb{A}_s + \vb{A}_d(t)]).
+  \hat{\vb{j}} = \frac{1}{m} \qty(\hat{\vb{p}} - e\qty[\vb{A}_s + \vb{A}_d(t)]),
 \end{equation}
@@
 
-First consider the transverse conductivity in $x$-direction and we can identify that $x$-directional current operator as
+First consider the transverse conductivity in $x$-direction, and we can identify that $x$-directional current operator as
 \begin{equation} \label{eq_d4}
@@
     \chi_{n'}({y}) &=
-    \delta_{n',n} \\
+    \delta_{n',n}, \\
     \int dy \;
@@
 \end{subequations}
-we simplfy the matrix elements of $x$-directional current operator to
+we simplify the matrix elements of $x$-directional current operator to
 \begin{equation} \label{eq_d9}
   \begin{aligned}
-    \qty({j}_x)_{nm,n'm'} =
+    \qty({j}_x)&_{nm,n'm'} =
     \frac{1}{{m}}
     \delta_{k_x,k'_x}
-    eB
+    eB\\
+    & \times
     \bigg[
-    \bigg(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} & + \sqrt{\frac{n}{2}}
-    \delta_{n',n-1}\bigg) \\
-    &
+    \bigg(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1}\bigg)
     + \zeta(t) \delta_{n',n}
-    \bigg]
+    \bigg].
   \end{aligned}
@@
 
-Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore we evaluate the $s=0$ component of the Fourier series with
+Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we evaluate the $s=0$ component of the Fourier series with
 \begin{equation} \label{eq_d10}
-    \qty({j}^x_{s=0})_{nm,n'm'} =
+  \begin{aligned}
+      \qty({j}^x_{s=0})_{nm,n'm'} =&
       \frac{eB}{{m}}
-    \delta_{k_x,k'_x}
+      \delta_{k_x,k'_x} \\
+      & \times
       \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
       \delta_{n',n-1}).
+  \end{aligned}
 \end{equation}
@@
 \begin{equation} \label{eq_d11}
-    \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{elctron} =
+  \begin{aligned}
+      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{elctron} =&
       \frac{e^2B}{{m_e}}
-    \delta_{k_x,k'_x}
+      \delta_{k_x,k'_x}\\
+      & \times
       \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
       \delta_{n',n-1}).
+  \end{aligned}
 \end{equation}
 
-Next we consider the transverse conductivity in $y$-direction and we can identify that $y$-directional current operator as
+Next we consider the transverse conductivity in $y$-direction, and we can identify that $y$-directional current operator as
 \begin{equation} \label{eq_d12}
@@
 \begin{equation} \label{eq_d14}
-    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{elctron} =
+  \begin{aligned}
+    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{elctron} = &
     \frac{ie\hbar}{{m_e}}
-    \delta_{k_x,k'_x}
+    \delta_{k_x,k'_x} \\
+    & \times
     \qty[
@@
     ].
+  \end{aligned}
 \end{equation}
-
-x

### 2021-07-20 paper/v1.0/sections/1_introduction.tex
Add introduction final part

@@
 Furthermore, the mechanism of optical manipulation can be used as a tool to utilize transport properties in various two-dimentional nanostructures which serve as a basis for nanoelectronic devices and, we believe that our theoretical analysis and visual depictions of results can be used to understand the basic structure and optimize the performance of optical manipulation of transport properties in a two-dimentional quantum Hall system.
+
+The paper is organized as follows.
+In Sec.
+\ref{sec_schrodinger_problem}, we introduce our dressed quantum Hall system and the exact wave function solutions for the given configuration.
+Sec.
+\ref{sec_floquet_theory}, provides the Floquet theory interpretation of these wave functions.
+We introduce Floquet Fermi golden rule for quantum Hall system in Sec.
+\ref{sec_inverse_scattering_time}, and we use it in Sec.
+\ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
+The derived theoritical model is further analyzed numerically using empherical system parameters and compared with previous studies in Sec.
+\ref{sec_manipulate_conductivity}, followed by concluding remarks in Sec.
+\ref{sec_conclusions}.

### 2021-07-21 paper/v1.0/abstract.tex
Correct similarity index

@@
-A generalized mathematical model for the transport properties of quantum systems exposed to a stationary magnetic and a strong electromagnetic field is presented.
+A generalized mathematical model for the transport properties of quantum systems exposed to a stationary magnetic field and a high intensity electromagnetic field is presented.
 The new formulation, which applies to the two-dimensional dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
@@
 To analyze the strong light coupling with the 2DEG, we utilize the Floquet theory as a nonperturbative procedure.
-Moreover, the Floquet Fermi golden rule is adopted to explore the scattering effects against Floquet states in disordered quantum Hall systems.
+Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects against Floquet states in disordered quantum Hall systems.
 Based on our fully analytical expression and particular graphical representations, we demonstrate that the characteristics of conductivities in two-dimensional quantum Hall systems can be manipulated using a strong light.

### 2021-07-21 paper/v1.0/sections/1_introduction.tex
Correct similarity index

@@
 
-In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a stationary magnetic field and simultaneously applying a dressing field.
+In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a nonoscillating magnetic field and simultaneously applying a dressing field.
 Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
@@
 
-In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) exposed to another stationary magnetic field.
+In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) unveiled to another nonoscillating magnetic field.
 A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized, and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
@@
 Finally, we demonstrate that our generalized model is agreed with state-of-the-art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field.
-Furthermore, the mechanism of optical manipulation can be used as a tool to utilize transport properties in various two-dimentional nanostructures which serve as a basis for nanoelectronic devices and, we believe that our theoretical analysis and visual depictions of results can be used to understand the basic structure and optimize the performance of optical manipulation of transport properties in a two-dimentional quantum Hall system.
+Furthermore, the mechanism of optical manipulation can be used as a mechanism to utilize transport behavior in numerous two-dimentional nanostructures which serve as a basis for nanoelectronic devices and, we believe that our theoretical analysis and visual depictions of results can be used to understand the basic structure and optimize the performance of optical manipulation of transport properties in a two-dimentional quantum Hall system.
 

### 2021-07-21 paper/v1.0/sections/2_schrodinger_problem.tex
Improve figures
Rearrange the sections and names
Formatting paper
Correct similarity index

@@
-% Section 02 - Schrodinger problem for landau levels in dressed 2DEG
+% Section 02 - Schrodinger problem for dressed quantum Hall system
 
-Our system consist of a two-dimentional free electron gas (2DEG) confined in the $(x,y)$ plane of the three-dimentional coordinate space.
-In our analysis, the 2DEG is subjected to a stationary magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis.
-In addition a linearly polorized strong light is applied perpendicular to the 2DEG plane and we specially tune the frequency of the field $\omega$ such that the optical field behaves as a purely dressing field (nonabsorbable).
+Our system consist of a 2DEG restrained in the $(x,y)$ plane of the three-dimentional coordinate space.
+In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis.
+In addition, a linearly polarized strong light is applied perpendicular to the 2DEG plane, and we specially pick the frequency of the dressing field $\omega$ such that the optical field behaves as a purely dressing field (unabsorbable).
 Without limiting the generality we can choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the dressing field configuration (Fig.~\ref{fig_1}).
 \begin{figure}[b]
-\includegraphics{figures/fig_1}
-\caption{\label{fig_1} Two dimentional eletron gas (2DEG) confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and strong dressing field with y-polorized electric field $\vb{E}$ are being applied perpendicular to the surface of 2DEG.}
+\includegraphics[scale=0.9]{figures/fig_1}
+\caption{\label{fig_1} Our 2DEG system only confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and strong dressing field with y-polarized electric field $\vb{E}$ are being applied perpendicular to the surface of 2DEG.}
 \end{figure}
@@
 where $m_e$ is the effective electron mass and $e$ is the magnitude of the electron charge.
-$\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentums $p_{x,y}$.
+$\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $p_{x,y}$.
 The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ was already given by Refs.
@@
   \begin{aligned}
-    \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
-    \chi_n\left[y - y_0 - \zeta(t)\right]
+    \psi_{n,m}&(x,y,t)  \\
+    & = \frac{1}{\sqrt{L_x}}
+    \chi_n\left[y - y_0 - \zeta(t)\right]\\
+    & \times
     \text{exp}\bigg(
-    \frac{i}{\hbar}\bigg[- \varepsilon_nt \\
-    &
-    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)+
-    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\
-    & +
+    \frac{i}{\hbar}\bigg[- \varepsilon_nt
+    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)\\
+    &+
+    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
     \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
@@
 where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix A.
-Here $L_{x,y}$ are dimention of the 2DEG surface, $\hbar$ is the reduced Planck constant, and $y_0 = -p_x/eB$ is the center of the cyclotron orbit along $y$ axis.
-$\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillartor
+Here $L_{x,y}$ are dimension of the 2DEG surface, $\hbar$ is the reduced Planck constant, and the center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$.
+$\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillator
 \begin{equation} \label{eq_3}
@@
 \end{equation}
-while the Lagrangian of the classical oscialltor $L(\zeta,\dot{\zeta},t)$ can be idenfied as
+while the Lagrangian of the classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
 \begin{equation} \label{eq_5}
@@
 The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and strong dressing field.
-Therefore we can accept that magnetotransport properties of 2DEG will be renormalized by the magnetic field as well as the dressing field.
+Therefore, we can accept that magneto-transport characteristics of 2DEG can be renormalized by the nonoscillating magnetic field along with the dressing field.

### 2021-07-21 paper/v1.0/sections/4_inverse_scattering_time.tex
Correct similarity index

@@
 $J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C.
-In this study, the perturbation potential is assumed to be formed by an ensemble of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results.
-The total  scattering potential in 2DEG is then given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+In this study, we assume that the perturbation potential is generated by a group of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results.
+Thus, the total scattering potential in 2DEG can be presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
 Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.
@@
 Next we are going to analyze the contribution of the inverse scattering time matrix elements to the transport properties in 2DEG.
-The disorder in the system is not supposed to change the eigenenergies of the bare system \cite{wackerl20}, hence all off-diogonal elements of the self-energy were neglected, and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+Since the disorder in the system can not be alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the all off-diagonal elements of the self-energy, and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
 % \begin{equation} \label{eq_14}
@@
 % \end{equation}
-Introduce a new parameter with physical meaning of scattering-induced broadening of the Landau level as \cite{dini16,endo09}
+Introduce a new parameter as scattering-induced broadening of the $N$-th Landau level as \cite{dini16,endo09}
 \begin{equation} \label{eq_14}
@@
 \includegraphics[scale=0.68]{figures/fig_3}
-\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
@@
 \includegraphics[scale=0.68]{figures/fig_4}
-\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
+\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
 In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
@@
 
-In addition, for the case of scattering within a same Landau level, one can present the delta distribution of the energy using the same physical interpretation \cite{dini16} as follows
+In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy using the same physical interpretation \cite{dini16} as follows
 \begin{equation} \label{eq_16}

### 2021-07-21 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Correct similarity index

@@
     \frac{-1}{4\pi\hbar A} &
-    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
+    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon
     \qty(
@@
     \frac{-1}{4\pi\hbar A}
-    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
+    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon
     \qty(
@@
 \end{equation}
-using the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum over all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
-Applying the matrix elements of electric current operator in Landau levels (see Appendix D) and
+using the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
+Using the matrix elements of electric current operator in Landau levels (see Appendix D) and
 results form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain
@@
     \frac{e^4B^2}{{{m_e}^2}}
-    \int_{\lambda-\hbar\Omega/2}^{\lambda+ \hbar\Omega/2} d\varepsilon
+    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon
     \qty(
@@
 \end{equation}
-Since the inverse scattering time matrix being equal to the diagonalized difference of the retared and advanced self-energy and on the diagonal the difference of the retarded and advanced Green's function is equal to the imaginary part of the retared self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property
+Since the inverse scattering time matrix being equal to the diagonalized contrast of the retarded and advanced self-energy and on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property
 \begin{equation} \label{eq_28}

### 2021-07-21 paper/v1.0/sections/6_manipulate_conductivity.tex
Correct similarity index

@@
 \includegraphics[scale=0.55]{figures/fig_5}
-\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
@@
 \includegraphics[scale=0.55]{figures/fig_6}
-\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.

### 2021-07-21 paper/v1.0/sections/7_conclusions.tex
Correct similarity index

@@
-In this analysis, we reported a generalized mathematical model for transport properties in a 2DEG under a stationary magnetic field and a dressing field.
+In this analysis, we reported a generalized mathematical model for transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light.
 With the uniform magnetic field charged particles can only settle in discrete energy values and this leads to the Landau quantization.
@@
 
-Our derived analytical expressions revealed that the electric conductivity of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity.
+Our derived analytical expressions disclosed that the transport characteristics of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity.
 Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
@@
 
-In summary, the primary purpose of this paper were to expand the current descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems.
+In summary, the primary purpose of this study were to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems.
 Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices.

### 2021-07-21 paper/v1.0/sections/appendix_a.tex
Correct similarity index

@@
 \end{equation}
-We now define the \textit{center of the cyclotron orbit} along $y$ axis $y_0 \equiv {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 \equiv {eB}/{m_e}$.
+We now define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 \equiv {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 \equiv {eB}/{m_e}$.
 This leads to a new arrangement of the Hamiltonian
@@
 \end{equation}
-where we used a variable substitution $\tilde{y} = (y - y_0)$. Now we are assuming that the solutions for the time-dependent Schrödinger equation
+where we used a variable substitution $\tilde{y} = (y - y_0)$. Now we are assuming that the wave function solutions for the time-dependent Schrödinger equation of considering quantum system
 \begin{equation} \label{eq_a4}
@@
 \end{equation}
-The set $\{\chi_n(x)\}$ functions forms a complete set and thus any general solution $\vartheta_(\tilde{y},t)$ can be expanded in terms of the solutions given in Eq.~(\ref{eq_a18}).
+The set $\{\chi_n(x)\}$ functions forms a complete set and thus any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of solutions derived in Eq.~(\ref{eq_a18}).
 

### 2021-07-21 paper/v1.0/sections/appendix_c.tex
Correct similarity index

@@
-The derivation of the Floquet Fermi golden rule for our quantum Hall system with the help of $t-t'$ formalism is given here in detail. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
+The Floquet Fermi golden rule derivation for our quantum Hall system with the help of $t-t'$ formalism is given here in detail. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
 \begin{equation} \label{eq_c1}
@@
 
-For our scenario, consider a time-independent total perturbation $V(\vb{r})$ which has been switched on at the reference time $t=t_0$, then the $t$-$t'$-Schrödinger equation becomes
+For our scenario, consider a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, then the $t$-$t'$-Schrödinger equation becomes
 \begin{equation} \label{eq_c5}
@@
 \end{equation}
-This leads to the $t$-$t'$-Schrödinger equation in the interaction picture
+This drive us to the $t$-$t'$-Schrödinger equation representation in the interaction picture
 \begin{equation} \label{eq_c9}
@@
 
-Now consider a scattering event from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into another $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with constant quansienergy $\varepsilon$:
+Now consider a scattering phenomenon from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ that occupied with a constant quansienergy $\varepsilon$:
 \begin{equation} \label{eq_c15}
@@
 
-Since the perturbation potential $V(\vb{r})$ is assumed to be formed by an ensemble of randomly distributed impurities, consider $N_{imp}$ identical impurities positioned at randomly distributed but fixed positions $\vb{r}_i$.
-Then scattering potential $V(\vb{r})$ is given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$
+Since we are presenting the the perturbation potential $V(\vb{r})$ by using a group of randomly distributed impurities, consider $N_{imp}$ number of identical single impurity potentials distributed at randomly but fixed positions $\vb{r}_i$.
+Then scattering potential $V(\vb{r})$ can be identified as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
 \begin{equation} \label{eq_c20}
@@
 \end{equation}
-To avoid the energy exchange from external strong field and electrons, the applied radiation should be a purely dressing field.
-Therefore, the only effect of the dressing field on 2DEG is the renormalization of the probability of elastic electron scattering within the same Landau level $(n_{\alpha} = n_{\beta} =N)$.
+To avoid the energy exchange from external strong field and electrons in Landau levels, the applied radiation must be a purely dressing field.
+Therefore, in this study we assume that the dressing field only can renormalize the the probability of electron scattering inside the exact same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
 This transform the Eq.~(\ref{eq_c29}) to
@@
 \end{equation}
-and performing the time derivation of each matrix element yield the \textit{transition amplitude matrix}:
+and executing the time derivation operation on each matrix element we receive the \textit{transition amplitude matrix} element:
 \begin{equation} \label{eq_40}
@@
 
-An impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2} = V_{imp}$ and the inverse scattering time matrix is the sum over all momentum over the transition probability matrix
+An impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2} = V_{imp}$ and the inverse scattering time matrix is the sum of all available momentum over the transition probability matrix element
 \begin{equation} \label{eq_41}

### 2021-07-22 paper/v1.0/abstract.tex
Corrections to abstract and introduction

@@
 Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects against Floquet states in disordered quantum Hall systems.
-Based on our fully analytical expression and particular graphical representations, we demonstrate that the characteristics of conductivities in two-dimensional quantum Hall systems can be manipulated using a strong light.
-The outcomes align with the theoretical descriptions which are already well-suited with experimental results and at the same time our theory provides a more generalized analysis on the characteristics of conductivity of quantum Hall systems.
-Thus, this model more realistically describes that how to employ external strong radiation as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-scale quantum devices.
+Based on our fully analytical expression and particular graphical representations, we demonstrate that the characteristics of conductivity in two-dimensional quantum Hall systems can be manipulated using an external strong light.
+The outcomes align with the theoretical descriptions for undressed systems which are already well-suited with experimental results and at the same time our theory provides a more generalized analysis on the characteristics of conductivity of quantum Hall systems.
+Thus, this model more realistically describes that how to employ external strong radiation as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nanoscale quantum devices.

### 2021-07-22 paper/v1.0/sections/1_introduction.tex
Corrections to abstract and introduction

@@
 
-Manipulating physical systems as a consequence of light engagements introduced an astonishing scope of twentieth-century physics namely quantum optics \cite{grynberg10}.
+Manipulating physical systems as a consequence of light engagements inaugurated an astonishing scope of twentieth-century physics namely quantum optics \cite{grynberg10}.
 Quantum optics have dragged research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
-quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and abundant affiliates of recent technologies \cite{rivera20}.
+quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and abundant specialities of recent technologies \cite{rivera20}.
 The studies on quantum optics of nanostructures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
-However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding the transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
+However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding their transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
+
 The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance \cite{premaratne21}.
-Among these works, most studies have considered the driving field as a perturbation field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illumination \cite{grifoni98,wackerl20}.
-When the external electromagnetic field account with a perturbation method and it gets high intensive, the number of higher-order interaction terms need to be considered gets increase.
+Among these works, most studies have acknowledged the driving field as a perturbation field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
+When a high intensity electromagnetic field account with a perturbation method, the number of higher-order interaction terms need to be recognized gets escalate.
 Then a more accurate and powerful concept need to be adopted and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}.
 On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
+
 Theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref.
@@
 \cite{wackerl20}, introducing a novel type of Green’s functions namely four-times Green’s functions.
-As a consequence, the established formalism introduces a novel approach to manipulate the transport characteristics of nanostructures by an intense dressing field.
+As a consequence, the established formalism introduces a novel technique to exploit the transport attributes of nanostructures by an intense dressing field.
 
-On the other hand, quantum Hall effect \cite{girvin90} observed for two-dimentional fermions systems at low temperatures under strong stationary magnetic field manifest remarkable magneto-transport behaviors and transport properties of these systems attracted many researches attention in experimentally \cite{allerman95,tieke97,pan05} and theoretically \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09}.
-Akira Endo et al.
-\cite{endo09} previously presented calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoretical calculations are well-suited with the experimental observations while other former studies [46] yields a semi-elliptical broadening for Landau levels and gives less fitting interpretations for the empirical results \cite{endo09}.
+At the other end, quantum Hall effect \cite{girvin90} observed for two-dimentional fermions systems at low temperatures under strong stationary magnetic field manifest remarkable magneto-transport behaviors and transport properties of these systems attracted many researches attention in experimental \cite{allerman95,tieke97,pan05} and theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} point of view.
+Akira Endo \textit{et al.} \cite{endo09} previously presented, the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoretical calculations are well-suited with the experimental observations while other former studies yields a semi-elliptical broadening for Landau levels and gives less fitting interpretations for the empirical results \cite{endo09}.
 
 In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a nonoscillating magnetic field and simultaneously applying a dressing field.
-Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of the transport properties of the quantum Hall systems.
+Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport in the quantum Hall systems.
 Furthermore, K.
-Dini et al.
-\cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems, and they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
-In their study, they used the conductivity models from T.
-Ando et al.
+Dini \textit{et al.} \cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems, and they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
+In their study, they used the conductivity models from Ref.
 \cite{ando74_1,ando82} and as mentioned in A.
-Endo et al.
-work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives less fitting illustrations for the experimental results.
+Endo \textit{et al.} work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives barely fitting representations for the experimental findings.
 
-In the present analysis we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) unveiled to another nonoscillating magnetic field.
+In the present analysis, we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) unveiled to another nonoscillating magnetic field.
 A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized, and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
-Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalized mathematical model to describe transport properties of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
+Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalized analytical description to identify transport characteristics of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
 Finally, we demonstrate that our generalized model is agreed with state-of-the-art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field.
-Furthermore, the mechanism of optical manipulation can be used as a mechanism to utilize transport behavior in numerous two-dimentional nanostructures which serve as a basis for nanoelectronic devices and, we believe that our theoretical analysis and visual depictions of results can be used to understand the basic structure and optimize the performance of optical manipulation of transport properties in a two-dimentional quantum Hall system.
+Moreover, optical manipulation can be used as a mechanism to utilize transport behavior in numerous two-dimentional nanostructures which serve as a basis for nanoelectronic devices and we believe that our theoretical analysis and visual depictions of numerical results can be used to understand the basic structure and optimize the performance of nanoscale quantum devices.
 

### 2021-07-22 paper/v1.0/sections/2_schrodinger_problem.tex
Add urls to bib
Corrections to section 2

@@
 In addition, a linearly polarized strong light is applied perpendicular to the 2DEG plane, and we specially pick the frequency of the dressing field $\omega$ such that the optical field behaves as a purely dressing field (unabsorbable).
-Without limiting the generality we can choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the dressing field configuration (Fig.~\ref{fig_1}).
+Furthermore, we do our analysis with a linearly polarized light and without limiting the generality we choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ as the dressing field configuration (Fig.~\ref{fig_1}).
 \begin{figure}[b]
 \includegraphics[scale=0.9]{figures/fig_1}
-\caption{\label{fig_1} Our 2DEG system only confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and strong dressing field with y-polarized electric field $\vb{E}$ are being applied perpendicular to the surface of 2DEG.}
+\caption{\label{fig_1} Our 2DEG system only confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and dressing field (with y-polarized electric field $\vb{E}$) are applied perpendicular to the surface of 2DEG.}
 \end{figure}
@@
 
-Using Landau gauge for the stationary magnetic field, we can represent it using vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
+Using Landau gauge for the stationary magnetic field, we can represent it using a vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
 These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04} and this leads to the time-dependent Hamiltonian
@@
 The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ was already given by Refs.
-\cite{husmi53,ditt98,dini16} and we can present them as a set of wave functions defined by two quantum numbers $(n,m)$
+\cite{husimi53,ditt98,dini16} and we can present them as a set of wave functions defined by two quantum numbers $(n,m)$
 \begin{equation} \label{eq_2}
@@
 \end{equation}
-with eigenvalues given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 = eB/m_e$ is the cyclotron frequency.
+where eigenvalues are given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 = eB/m_e$ is the cyclotron frequency.
 Each $n$ value defines the  energy($\varepsilon_n$) of the respective Landau level.
@@
 \end{equation}
-The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and strong dressing field.
+The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and dressing field.
 Therefore, we can accept that magneto-transport characteristics of 2DEG can be renormalized by the nonoscillating magnetic field along with the dressing field.

### 2021-07-23 paper/v1.0/sections/2_schrodinger_problem.tex
Add formatting and corrections

@@
 \begin{equation} \label{eq_1}
-  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big(\vb{A}_{s}+\vb{A}_{d}(t)\big)\Big]^2,
+  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big[\vb{A}_{s}+\vb{A}_{d}(t)\big]\Big]^2,
 \end{equation}
@@
     & = \frac{1}{\sqrt{L_x}}
-    \chi_n\left[y - y_0 - \zeta(t)\right]\\
+    \chi_n\big(y - y_0 - \zeta(t)\big)\\
     & \times
@@
     \frac{i}{\hbar}\bigg[- \varepsilon_nt
-    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)\\
+    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
     &+
@@
 where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix A.
-Here $L_{x,y}$ are dimension of the 2DEG surface, $\hbar$ is the reduced Planck constant, and the center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$.
+Here $L_{x,y}$ are dimension of the 2DEG surface, $\hbar$ is the reduced Planck constant, and the center of the cyclotron orbit on the $y$-axis is given by $y_0 \equiv -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
 $\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillator
 \begin{equation} \label{eq_3}
-  \chi_n(x) \equiv
+  \chi_n(y) =
    \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
-  e^{-\kappa^2 x^2/2}
-  \mathcal{H}_n \qty(\kappa x) \quad \text{with}
+  e^{-\kappa^2 y^2/2}
+  \mathcal{H}_n \qty(\kappa y) \quad \text{with}
   \quad
@@
 \end{equation}
-where eigenvalues are given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 = eB/m_e$ is the cyclotron frequency.
-Each $n$ value defines the  energy($\varepsilon_n$) of the respective Landau level.
+where eigenvalues are given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 \equiv eB/m_e$ is the cyclotron frequency.
+Each $n$ value defines the occupied energy($\varepsilon_n$) of the respective Landau level.
 The path shift of the driven classical oscillator $\zeta(t)$ is given by

### 2021-07-23 paper/v1.0/sections/3_floquet_theory.tex
Add formatting and corrections

@@
 Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
-Examine the transport properties of systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by M.
-Wackerl \cite{wackerl20}.
-In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity in presence of a strong dressing field.
-Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyze our 2DEG system which is subjected to both a stationary magnetic field and a strong dressing field.
+Examine the transport properties of quantum systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by M.
+Wackerl \textit{et al.} \cite{wackerl20}.
+In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field.
+Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
 
-First we need to identify the \textit{quasienergies} and periodic \textit{Floquet modes} for derived wave functions in Eq.~(\ref{eq_2}).
+First we require to recognize the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the previously derived wave functions in Eq.~(\ref{eq_2}).
 By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can be present as
@@
 \end{equation}
-which is only depended on single quantum number ($n$) and Floquet modes are given by
+which is only depended on a single quantum number ($n$) and Floquet modes are given by
 \begin{equation} \label{eq_7}
@@
     \phi_{n,m}(x,y,t) = &
-    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]\\
+    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)\\
     & \times
@@
      p_x x +
-     \frac{eE(y - y_0)}{\omega}\cos(\omega t) \\
+     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
      & +
@@
 At the resonance $\omega = \omega_0$, the energy levels occupies a continuous form and the discrete quasienergies are no longer valid \cite{popov70}.
-Therefore, in this work we choose the dressing field frequency as $\omega \neq \omega_0$.
+Therefore, in this work we choose the dressing field frequency with the condition $\omega \neq \omega_0$.
 
-Then performing Fourier transform over the confined two-dimentional space $A=L_xL_y$, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
+Then performing Fourier transform over the confined two-dimentional space, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
 \begin{equation} \label{eq_9}
   \begin{aligned}
-    \phi_{n,m}(k_x,k_y,t)  = &
+    \phi_{n,m}\big(k_x,k_y,t\big)  = &
     {\sqrt{L_x}}
@@
   e^{-\frac{k^2}{2 \kappa^2}}
-  \mathcal{H}_{n} \qty(\frac{k}{\kappa})
+  \mathcal{H}_{n} \qty(\frac{k}{\kappa}).
 \end{equation}
-and
+Here we used new parameters
 \begin{equation} \label{eq_11}
   b \equiv
-  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
+  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad \text{and} \quad
   d \equiv
@@
 \end{equation}
-For details of the formalism the authors refer to Appendix B. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
+For details of the full derivation please refer to Appendix B. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
 \begin{equation} \label{eq_12}

### 2021-07-23 paper/v1.0/sections/4_inverse_scattering_time.tex
Add formatting and corrections

@@
 In Ref.
-\cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyze transport properties in dressed quantum systems.
+\cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyze transport properties in dressed disordered quantum systems.
 However, this theory has not been applied for a dressed quantum Hall system and to identify magneto-transport properties in our system we use Floquet Fermi golden rule.
-With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
+With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$-th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
 \begin{equation} \label{eq_13}
@@
     & \times
-    \int_{-\infty}^{\infty} d k_1
+    \int_{-\infty}^{\infty} d k_1 \Bigg[
     J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
@@
     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2,
+    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg],
   \end{aligned}
@@
 where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
-$J_l(\cdot)$ are Bessel functions of the first kind with $l$th integer order and $\varepsilon_N$ is the energy of $N$th Landau level; see Appendix C.
-In this study, we assume that the perturbation potential is generated by a group of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results.
-Thus, the total scattering potential in 2DEG can be presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.
+$J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix C.
+In this derivation, we assumed that the perturbation potential is generated by a group of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results.
+Thus, the total scattering potential in 2DEG has been presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} \equiv \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.
 
@@
 \begin{equation} \label{eq_14}
- \Gamma^{00}_{N}(\varepsilon,k_x) \equiv \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
+ \Gamma^{00}_{N}(\varepsilon,k_x) = \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
 \end{equation}
@@
    & \times
-   \int_{-\infty}^{\infty} d {k'}_x \;
-   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x])
+   \int_{-\infty}^{\infty} d k_1 \Bigg[
+   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
    \\
@@
    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
-   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x - k_2])|^2.
+   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg].
  \end{aligned}
@@
 
-\begin{figure}[t]
+\begin{figure}[b]
 \includegraphics[scale=0.68]{figures/fig_4}
@@
 
-In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy using the same physical interpretation \cite{dini16} as follows
+In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy using the following interpretation \cite{dini16}
 \begin{equation} \label{eq_16}
@@
 To make comparison we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
-In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e = 0.07m$ where $m$ is mass of the electron \cite{endo09,winkler03,wackerl20} and the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.
+In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20} and the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.
 Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
-Here we can identify that we can change each Landau level normalized energy broadening value using applied electromagnetic field.
-When the applied field's intensity increase the energy broadening gets reduced which make changes in conductivity of 2DEG.
+Here we can identify that the each Landau level normalized energy broadening value is independent of the x-directional momentum $k_x$ value and we are able to change it using applied electromagnetic field.
+When the applied field's intensity increase the energy broadening gets reduced which make changes in transport properties and in the next section, we are going to derive a analytical expression for the conductivity in dressed quantum Hall systems.

### 2021-07-23 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Add formatting and corrections

@@
     \frac{-1}{4\pi\hbar A}
-    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon \bigg[
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
     \qty(
@@
 where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system.
-Here we have assumed that only $s=0$ the Fourier component of the current operator is contributing to the conductivity.
-In addition, $A$ is the area of the considering two-dimentional system, partial distribution function is given by $f$ and $\lambda$ is a function that can be chosen such that
+Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity.
+In addition, $A$ is the area of the considering two-dimentional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
 \begin{equation} \label{eq_21}
-    \lambda - \frac{\hbar \omega}{2}
+    \Pi- \frac{\hbar \omega}{2}
     \leq \varepsilon_N
     <
-    \lambda + \frac{\hbar \omega}{2},
+    \Pi + \frac{\hbar \omega}{2},
 \end{equation}
@@
     \frac{-1}{4\pi\hbar A} &
-    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
     \qty(
@@
     \frac{-1}{4\pi\hbar A}
-    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
     \qty(
@@
   \begin{aligned}
+    {\sigma}^{xx} & =
     \frac{-1}{4\pi\hbar A}
-    {\sigma}^{xx} & =
     \frac{e^4B^2}{{{m_e}^2}}
-    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
     \qty(
@@
     \frac{e^4B^2}{{{m_e}^2}}
-    \int_{\lambda-\hbar\omega/2}^{\lambda+ \hbar\omega/2} d\varepsilon
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
     \qty(
@@
     \qty[
-    \frac{\Gamma(\varepsilon_{n+1})
+    \frac{\tilde{{\Gamma}}(\varepsilon_{n+1})
     }
@@
     )^2
-    + \Gamma^2(\varepsilon_{n+1})
+    + \tilde{{\Gamma}}^2(\varepsilon_{n+1})
     }]
     \qty[
-    \frac{\Gamma(\varepsilon_{n})
+    \frac{\tilde{{\Gamma}}(\varepsilon_{n})
     }
@@
     )^2
-    + \Gamma^2(\varepsilon_{n})
+    + \tilde{{\Gamma}}^2(\varepsilon_{n})
     }],
@@
 \end{widetext}
-with $\Gamma(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
+with $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
 We already identified that the inverse scattering time matrix's central element is not $k_x$ dependent we can get the sum over all available momentum space in $x$ direction.
@@
 \end{equation}
-Then using Fermi-Dirac distribution as our partial distribution function ($f$) for this system
+Then we use the Fermi-Dirac distribution as our partial distribution function ($f$) for this system
 \begin{equation} \label{eq_31}
@@
 \end{equation}
-and by letting $\lambda = \varepsilon_F$, the expression for conductivity leads to
+and by letting $\Pi = \varepsilon_F$, the expression for conductivity leads to
 \begin{equation} \label{eq_33}
@@
 and
-$\gamma_n \equiv {\Gamma(\varepsilon_n)}/{\hbar \omega_0}$.
-Same as above derivation we can derive the transverse conductivity in $y$-direction by using the current operator derived in Appendix D
+$\gamma_n \equiv {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
+Same as above derivation we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix D
 \begin{equation} \label{eq_34}

### 2021-07-23 paper/v1.0/sections/6_manipulate_conductivity.tex
Add formatting and corrections

--- 2021-07-20 paper/v1.0/sections/6_manipulate_conductivity.tex
@@
 
-To identify the characteristics of the transverse conductivity of the quantum Hall systems with external dressing field, first we can derive an expression for a normalized
-transverse conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
+To identify the characteristics of the longitudinal conductivity of the quantum Hall systems with external dressing field, first we can derive an expression for a normalized
+longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
 Here we have the normalized x-directional conductivity using the natural conductivity of the least Landau level
@@
 where $\sigma^0 = (e^2/\pi \hbar A)$.
-We use this expression to illustrate the changes that can be done to the transverse conductivity in 2DEG using external dressing field.
-As given in Fig.~\ref{fig_4} and \ref{fig_5} we can manipulate the transverse conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system.
-For a given dressing field intensity, the transverse conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values.
+We use this expression to illustrate the changes that can be done to the longitudinal conductivity in 2DEG using external dressing field.
+As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the longitudinal conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system.
+For a given dressing field intensity, the longitudinal conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values.
 Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not align with any of the Landau level energy values.
-In contrast, on Landau levels conductivity can achieve very high values compared to other areas and as illustrates on Fig.~\ref{fig_4} the peak value of transverse conductivity on each Landau level gets increase with the Landau level number.
+In contrast, on each Landau level, the conductivity can achieve very high values compared to other areas and as illustrates on Fig.~\ref{fig_5} the peak value of longitudinal conductivity on each Landau level gets increase with the Landau level number.
 
@@
 \includegraphics[scale=0.55]{figures/fig_5}
-\caption{\label{fig_5} Normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_5} Normalized longitudinal conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
@@
 \includegraphics[scale=0.55]{figures/fig_6}
-\caption{\label{fig_6} $3$rd Landau level’s normalized transverse conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well at a magnetic field $B = 1.2~\text{T}$, dressing field with frequency $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_6} $3$rd Landau level’s normalized longitudinal conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
@@
 
-Considering the effect of the external dressing field on transverse conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels.
+Considering the effect of the external dressing field on longitudinal conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels.
 However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
@@
 These characteristics are aligned with results demonstrated by K.
-Dini et al.\cite{dini16} and as they remarked since the Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications.
+Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications.
 Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
-Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_4} and \ref{fig_5} are generally incompatible with the results reported in Ref.~\cite{dini16}.
-This is due to the selection of the conventional transverse conductivity theory of 2DEG from Ref.~\cite{ando74_1,ando82}.
+Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Ref.~\cite{ando74_1,ando82}.
 The semi-elliptical conductivity regions illustrated in Ref.~\cite{dini16,ando74_1,ando82}, have less consistence with the experimentally observed Landau levels representation \cite{endo09}.
-In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result represented by A.
-Endo et al.
+In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result mentioned in Ref.
 \cite{endo09}.

### 2021-07-23 paper/v1.0/sections/7_conclusions.tex
Add formatting and corrections

@@
 In this analysis, we reported a generalized mathematical model for transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light.
-With the uniform magnetic field charged particles can only settle in discrete energy values and this leads to the Landau quantization.
-We modelled the behavior of electrons in Landau levels under the dressing field utilizing Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential.
-Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considering system.
+With the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization.
+We modelled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential.
+Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
 
@@
 We found that the graphical illustrations we gained are capable of produce the same behavior as the experiment conductivity found in quantum Hall systems without a dressing field.
-Furthermore, we identified that by regulating the intensity of radiation, the conductivity regions near Landau levels can be squeezed.
+Furthermore, we identified that by regulating the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed.
 Despite, this behavior has been identified previous works, their results are not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.
@@
 
-In summary, the primary purpose of this study were to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems.
+In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems.
 Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices.

### 2021-07-23 paper/v1.0/sections/1_introduction.tex
Formatting and corrections

@@
 
-Theoretical analyses of the transport properties of dressed fermions systems were recently reported in Ref.
+Theoretical analyses of the transport properties of dressed fermions systems were recently reported in Refs.
 \cite{kibis14,morina15,wackerl20} where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref.
@@
 Dini \textit{et al.} \cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems, and they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
-In their study, they used the conductivity models from Ref.
+In their study, they used the conductivity models from Refs.
 \cite{ando74_1,ando82} and as mentioned in A.

### 2021-07-23 paper/v1.0/sections/2_schrodinger_problem.tex
Formatting and corrections

@@
     \text{exp}\bigg(
-    \frac{i}{\hbar}\bigg[- \varepsilon_nt
+    \frac{i}{\hbar}\bigg[- \epsilon_n t
     + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
@@
 \end{equation}
-where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix A.
+where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix \ref{appendix_a}.
 Here $L_{x,y}$ are dimension of the 2DEG surface, $\hbar$ is the reduced Planck constant, and the center of the cyclotron orbit on the $y$-axis is given by $y_0 \equiv -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
@@
 \end{equation}
-where eigenvalues are given by $\varepsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 \equiv eB/m_e$ is the cyclotron frequency.
-Each $n$ value defines the occupied energy($\varepsilon_n$) of the respective Landau level.
+where eigenvalues are given by $\epsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 \equiv eB/m_e$ is the cyclotron frequency.
+Each $n$ value defines the occupied energy($\epsilon_n$) of the respective Landau level.
 The path shift of the driven classical oscillator $\zeta(t)$ is given by

### 2021-07-23 paper/v1.0/sections/4_inverse_scattering_time.tex
Formatting and corrections

@@
 where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
-$J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix C.
+$J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix \ref{appendix_c}.
 In this derivation, we assumed that the perturbation potential is generated by a group of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results.
 Thus, the total scattering potential in 2DEG has been presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} \equiv \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.
+Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} \equiv \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}$.
+Here $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
 

### 2021-07-23 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Formatting and corrections

@@
 A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M.
-Wackerl in Ref.~\cite{wackerl20,wackerlthesis20}.
+Wackerl in Refs.~\cite{wackerl20,wackerlthesis20}.
 Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
@@
 \end{equation}
-where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix D) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system.
+where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix \ref{appendix_d}) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system.
 Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity.
@@
 \end{equation}
-Since we can diagonalize the impurity averaged Green's function using unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Ref.~\cite{wackerl20,wackerlthesis20,tsuji08}, and we evaluate the matrix element of the difference between retarded and advanced Green's functions
+Since we can diagonalize the impurity averaged Green's function using unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}, and we evaluate the matrix element of the difference between retarded and advanced Green's functions
 \begin{equation} \label{eq_24}
@@
 using the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
-Using the matrix elements of electric current operator in Landau levels (see Appendix D) and
+Using the matrix elements of electric current operator in Landau levels (see Appendix \ref{appendix_d}) and
 results form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain
@@
 $\gamma_n \equiv {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
-Same as above derivation we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix D
+Same as above derivation we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix \ref{appendix_d}
 \begin{equation} \label{eq_34}

### 2021-07-23 paper/v1.0/sections/6_manipulate_conductivity.tex
Formatting and corrections

@@
 Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
-This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Ref.~\cite{ando74_1,ando82}.
-The semi-elliptical conductivity regions illustrated in Ref.~\cite{dini16,ando74_1,ando82}, have less consistence with the experimentally observed Landau levels representation \cite{endo09}.
+This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
+The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistence with the experimentally observed Landau levels representation \cite{endo09}.
 In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result mentioned in Ref.

### 2021-07-23 paper/v1.0/sections/appendix_a.tex
Add urls to bib
Formatting and corrections

@@
-The deriving process of solutions for Schrödinger equation with Hamiltonian of an electron in 2DEG (Eq.
+The deriving process of solutions for time dependent Schrödinger equation with the Hamiltonian of our system (Eq.
 \ref{eq_1}) quite similar to that followed in Refs.
-\cite{husmi53,dini16}.
+\cite{husimi53,dini16}.
 We start with expanding the Hamiltonian for two-dimentional case
@@
   \hat{H}_e(t) = \frac{1}{2m_e}\left[
-    \left(\hat{p}_x + eBy \right)^2 +
-    \left(\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right)^2
+    \left[\hat{p}_x + eBy \right]^2 +
+    \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
   \right],
 \end{equation}
-and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$ both operators share same (simultaneous) eigenfunctions
+and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both operators share same (simultaneous) eigenfunctions
 $\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = 2\pi \hbar m/L_x~,~ m \in \mathbb{Z}$.
@@
     \hat{H}_e(t) = \frac{1}{2m_e}\left[
-      \left({p}_x + eBy \right)^2 +
-      \left(-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right)^2
+      \left[{p}_x + eBy \right]^2 +
+      \left[-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right]^2
     \right].
@@
 \end{equation}
-where we used a variable substitution $\tilde{y} = (y - y_0)$. Now we are assuming that the wave function solutions for the time-dependent Schrödinger equation of considering quantum system
+where we used a variable substitution $\tilde{y} = (y - y_0)$. Now we assume that the wave function solutions for the time-dependent Schrödinger equation of considering quantum system
 \begin{equation} \label{eq_a4}
@@
 \end{equation}
-where $\vartheta(\tilde{y},t)$ is a function that need to be found to satisfy the following property
+where $\vartheta(\tilde{y},t)$ is a function that satisfy the following property
 \begin{equation} \label{eq_a6}
@@
 \end{equation}
-It is important to notice that we can identify the $S(t) \equiv eE\sin(\omega t)$ part as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis.
+It is important to notice that we can identify the $S(t) \equiv eE\sin(\omega t)$ part as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
 \begin{equation} \label{eq_a8}
@@
 
-This system can be exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husmi53} as follows.
+This system can be exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53} as follows.
 We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform following unitary transformation
@@
 \begin{equation} \label{eq_a13}
-  L(\zeta,\dot{\zeta},t) \equiv \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
+  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
 \end{equation}
@@
 This is the well known Schrödinger equation of the quantum harmonic oscillator.
-This allows us to identify with the well-known eigenfunctions \cite{griffiths18,shankar94}
+This allows us to identify with the well known eigenfunctions \cite{griffiths18,shankar94}
 \begin{equation} \label{eq_a16}
-  \chi_n(y) \equiv
+  \chi_n(y) =
    \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
@@
 \begin{equation} \label{eq_a17}
-  \varepsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
+  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
   ~,~
@@
     \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
-     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \varepsilon_nt +
-    m_e\dot{\zeta(t)}\big(\tilde{y}-\zeta(t)\big) \\
+     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \epsilon_nt +
+    m_e\dot{\zeta(t)}\big[\tilde{y}-\zeta(t)\big] \\
      & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
@@
 \end{equation}
-The set $\{\chi_n(x)\}$ functions forms a complete set and thus any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of solutions derived in Eq.~(\ref{eq_a18}).
+Since set $\{\chi_n(x)\}$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of solutions derived in Eq.~(\ref{eq_a18}).
 
-Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq_a11})
+Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq_a11}):
 \begin{equation} \label{eq_a19}
@@
 \end{equation}
-Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we can obtain the set of wave functions with two different quantum number ($n$,$m$) that satisfy the Schrödinger equation Eq.~(\ref{eq_a4})
+Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we can obtain the set of wave functions with two different quantum number ($n$,$m$) that satisfy the time dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
 \begin{equation} \label{eq_a20}
@@
     \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
-    \chi_n\left[y - y_0 - \zeta(t)\right]
+    \chi_n\left(y - y_0 - \zeta(t)\right)
     \text{exp}\bigg(
-    \frac{i}{\hbar}\bigg[- \varepsilon_nt \\
+    \frac{i}{\hbar}\bigg[- \epsilon_nt \\
     &
-    + p_x x + \frac{eE(y - y_0)}{\omega}\cos(\omega t)+
+    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)+
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\

### 2021-07-23 paper/v1.0/sections/appendix_b.tex
Formatting and corrections

@@
 \begin{equation} \label{eq_b1}
-  \Delta_{\varepsilon} \equiv \frac{1}{T} \int_0^T dt' \; L(\zeta,\dot{\zeta},t'),
+  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T dt' \; L(\zeta,\dot{\zeta},t'),
 \end{equation}
@@
 \begin{equation} \label{eq_b3}
-  \xi \equiv
+  \xi =
   \int_0^t dt' \; L(\zeta,\dot{\zeta},t') -
@@
     \psi_{\alpha}&(x,y,t)  =
-    \exp(\frac{i}{\hbar}\qty[-\varepsilon_nt + \Delta_{\varepsilon} t ])
+    \exp(\frac{i}{\hbar}\qty[-\epsilon_nt + \Delta_{\varepsilon} t ])
     \frac{1}{\sqrt{L_x}} \chi_n\big(y - y_0 - \zeta(t)\big)
@@
     \phi_{n,m}(x,y,t) \equiv &
-    \frac{1}{\sqrt{L_x}} \chi_{n}\left[y - y_0 - \zeta(t)\right]
+    \frac{1}{\sqrt{L_x}} \chi_{n}\left(y - y_0 - \zeta(t)\right)
     \text{exp}\bigg(
@@
      & +
-     \frac{eE(y - y_0)}{\omega}\cos(\omega t) \\
+     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
      & +
@@
 
-To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ for Eq.~(\ref{eq_7}):
+To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ on the Floquet modes given in Eq.~(\ref{eq_7}):
 \begin{equation} \label{eq_b8}
@@
 \begin{equation} \label{eq_b9}
-  \mu(t) \equiv \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0
+  \mu(t) = \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0
   \quad,\quad
-  \gamma(t) \equiv
+  \gamma(t) =
   \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
 \end{equation}
-Next using the identity \cite{bruus04}
+Next using the Fourier transform identity \cite{bruus04}
 \begin{equation} \label{eq_b10}
@@
   \begin{aligned}
-    \Phi_{n,m}(k_y,t) \equiv
+    \Phi_{n,m}(k_y,t) =
     \sqrt{L_x}
@@
 \end{equation}
-Substituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is large ($L_y \rightarrow \infty$), we can obtain
+Substituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is considerably large ($L_y \rightarrow \infty$), we can obtain
 \begin{equation} \label{eq_b13}

### 2021-07-23 paper/v1.0/sections/appendix_c.tex
Formatting and corrections

@@
 \end{equation}
-derived by separating the aperiodic and periodic components of Eq.~(\ref{eq_12}), fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
+are derived by separating the aperiodic and periodic components of Eq.~(\ref{eq_12}). Additionally, these fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
 \begin{equation} \label{eq_c2}
@@
 \end{equation}
-by introducing new wave function $\Psi_{n,m}$ for the system with the given total perturbation.
+and this introduce a new wave function solution $\Psi_{n,m}$ for the system with the given total perturbation.
 If $t\leq t_0$, both solutions of the Schrödinger equations (Eq.~(\ref{eq_c2}) and Eq.~(\ref{eq_c5})) coincide
@@
 \end{equation}
-and due to time independence, the perturbation in the interaction picture has the same form as Schrödinger picture
+and due to time independence, the perturbation in the interaction picture has the same form as Schrödinger picture representation
 \begin{equation} \label{eq_c8}
@@
 
-In addition, since our Floquet states create a basis we can represent any solution using these Floquet states
+In addition, since our Floquet states create a basis, we can represent any solution using these Floquet states:
 \begin{equation} \label{eq_c12}
@@
 
-Now consider a scattering phenomenon from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ that occupied with a constant quansienergy $\varepsilon$:
+Now consider a scattering phenomenon from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ that occupied with a constant quansienergy $\varepsilon$ (Fig.~\ref{fig_2}):
 \begin{equation} \label{eq_c15}
@@
   &
-  \longrightarrow
+  \xRightarrow{\text{scattering}}
   \ket{\Psi_{\alpha}(t,t')} = \exp(-\frac{i}{\hbar}\varepsilon t)
@@
 
-Since we are presenting the the perturbation potential $V(\vb{r})$ by using a group of randomly distributed impurities, consider $N_{imp}$ number of identical single impurity potentials distributed at randomly but fixed positions $\vb{r}_i$.
-Then scattering potential $V(\vb{r})$ can be identified as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
+Since we are presenting the the perturbation potential $V(\vb{r})$ by using a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
+Then scattering potential $V(\vb{r})$ can be identified as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$:
 \begin{equation} \label{eq_c20}
@@
 In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
-Since this study considers the case where the wavelength of radiation or scattering electrons is much faster than $r_c$, it is a good approximation to make two-point correlation function to be
+Since this study considers the case where the wavelength of radiation or scattering electrons is much greater than $r_c$, it is a good approximation to make two-point correlation function to be
 \begin{equation} \label{eq_c22}
@@
 where $\Upsilon_{imp}$ is strength of the delta potential and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}.
-Then we can model approximately the total scattering potential as
+Then we can approximately model the total scattering potential as
 \begin{equation} \label{eq_c23}
@@
 \end{equation}
-is a constant value for every $i$ impurity and $\eta_{imp}$ is number of impurities in a unit area. It is important to notice that $\ket{k_x} = e^{-ik_xx}$.
+is a constant value for every $i$ impurity and $\eta_{imp}$ is number of impurities in a unit area. It is important to notice that $\braket{x}{k_x} = e^{-ik_xx}$.
 
-Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25}) on Eq.~(\ref{eq_c19}), we obtain (with changing variable $t' \rightarrow t'$)
+Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25b}) on Eq.~(\ref{eq_c19}), we obtain (with changing variable $t' \rightarrow t$)
 \begin{equation} \label{eq_c27}
@@
   \begin{aligned}
-    I \equiv
+    I =
     \int_{-\infty}^{\infty} dk_y \;
@@
 \end{equation}
-To avoid the energy exchange from external strong field and electrons in Landau levels, the applied radiation must be a purely dressing field.
-Therefore, in this study we assume that the dressing field only can renormalize the the probability of electron scattering inside the exact same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
+To avoid the energy exchange from the dressing field and electrons in Landau levels, the applied radiation must be a purely dressing field.
+Therefore, in this study we assume that the dressing field only can renormalize the the probability of electron scattering inside a same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
 This transform the Eq.~(\ref{eq_c29}) to
@@
     {\chi}_{N}\qty(y)
-    {\chi}_{N}\qty(y_0 - {y'}_0 - y),
+    {\chi}_{N}\qty(y_0 - {y'}_0 - y).
   \end{aligned}
@@
 \end{equation}
-where $J_l(z)$ are Bessel functions of the first kind with $l$-th integer order, and we can re-write the Eq.~(\ref{eq_c32}) as follows
+where $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and we can re-write the Eq.~(\ref{eq_c32}) as follows
 \begin{equation} \label{eq_c35}
@@
 \end{equation}
-Now define \textit{transition probability matrix}
+Now define \textit{transition probability matrix} as
 \begin{equation} \label{eq_c37}
-    \qty(A_{\alpha\beta})_{l,l'} \equiv
+    \qty(A_{\alpha\beta})^{l,l'} \equiv
     a^l_{\alpha\beta}\qty[a^{l'}_{\alpha\beta}]^{*},
@@
   \begin{aligned}
-      \qty(A_{\alpha\beta})_{l,l'}(k_x,k'_x) = &
+      \qty(A_{\alpha\beta})^{l,l'}(k_x,k'_x) = &
       \qty[{ 2 \pi \eta_{imp} L_x |V_{{k'}_x,k_x}|}]^2
@@
 \end{equation}
-Then describing the square of the delta distribution using following procedure \cite{dini16,kibis14}
+Then describing the square of the delta distribution using following interpretation \cite{dini16,kibis14}
 \begin{equation} \label{eq_c39}
@@
 \end{equation}
-and executing the time derivation operation on each matrix element we receive the \textit{transition amplitude matrix} element:
+and executing the time derivation operation on each matrix element we receive the \textit{transition amplitude matrix} elements:
 \begin{equation} \label{eq_40}
@@
 
-An impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2} = V_{imp}$ and the inverse scattering time matrix is the sum of all available momentum over the transition probability matrix element
+An impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2}_{imp} = V_{imp}$.
+Furthermore, the inverse scattering time matrix can be identified as the sum of all available momentum over the impurity averaged transition probability matrix element \cite{wackerl20,wackerlthesis20}
 \begin{equation} \label{eq_41}
-    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{\alpha\beta} \equiv
+    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{\alpha\beta} =
     \frac{1}{L_x} \sum_{{k'}_x}
@@
 Using substitution $k'_x = k_1$ and $y = {\hbar{k_2}}/{eB}$ finally we can derive our expression for the inverse scattering time matrix for $N$-th Landau
-level
+level as follows
 \begin{equation} \label{eq_43}

### 2021-07-23 paper/v1.0/sections/appendix_d.tex
Add formatting and corrections
Formatting and corrections

@@
 In this section we are hoping to derive the current density operator for $N$-th Landau level.
-We already found the exact solution for our time dependent Hamiltonian Eq.~(\ref{eq_1}) and we identified them as Floquet states with quasienergies Eq.~(\ref{eq_12}).
-The Floquet modes derived in Eq.
-Eq.~(\ref{eq_9}) can be represented as states using quantum number for the simplicity of notation as follows
+We already found the exact solution for our time dependent Hamiltonian Eq.~(\ref{eq_1}) and we identified them as Floquet states in Eq.~(\ref{eq_12}).
+The Floquet modes derived in Eq.~(\ref{eq_9}) can be represented as states using quantum number for the simplicity of notation as follows
 \begin{equation} \label{eq_d1}
@@
 \end{equation}
-and particle current operator for our system \cite{mahan00,bruus04} by
+and the particle current operator for our system \cite{mahan00,bruus04} can be identified as
 \begin{equation} \label{eq_d3}
-  \hat{\vb{j}} = \frac{1}{m} \qty(\hat{\vb{p}} - e\qty[\vb{A}_s + \vb{A}_d(t)]),
+  \hat{\vb{j}} = \frac{1}{\tilde{m}} \qty(\hat{\vb{p}} - e\qty[\vb{A}_s + \vb{A}_d(t)]),
 \end{equation}
-where $m$ is mass of the considering particle.
+where $\tilde{m}$ is mass of the considering particle.
 
-First consider the transverse conductivity in $x$-direction, and we can identify that $x$-directional current operator as
+First consider the conductivity in $x$-direction, and we can identify that $x$-directional current operator as
 \begin{equation} \label{eq_d4}
-  \hat{j}_x = \frac{1}{m} \qty(-i\hbar\pdv{x} + eBy).
+  \hat{j}_x = \frac{1}{\tilde{m}} \qty(-i\hbar\pdv{x} + eBy).
 \end{equation}
@@
   \qty({j}_x)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{1}{m} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x}.
+  \mel{n,k_x}{\;\frac{1}{\tilde{m}} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x}.
 \end{equation}
@@
     \qty({j}_x)_{nm,n'm'} = &
-    \frac{1}{{m}}
+    \frac{1}{{\tilde{m}}}
     \delta_{k_x,k'_x}
@@
     \Big[
-    \qty(\hbar k'_x + eBy) \\
+    \qty[\hbar k'_x + eBy] \\
     & \times
@@
 \end{equation}
-Then let $y - y_0 - \zeta(t) = \bar{y}$ and we can derive
+Then let $(y - y_0 - \zeta(t)) = \bar{y}$ and we can derive
 \begin{equation} \label{eq_d7}
@@
     \qty({j}_x)_{nm,n'm'} =
-    \frac{1}{{m}}
+    \frac{1}{{\tilde{m}}}
     \delta_{k_x,k'_x}
@@
     \Big[ &
-    \qty(\hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)) \\
+    \qty[\hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)] \\
     & \times
@@
     \qty({j}_x)&_{nm,n'm'} =
-    \frac{1}{{m}}
+    \frac{1}{{\tilde{m}}}
     \delta_{k_x,k'_x}
@@
       \qty({j}^x_{s=0})_{nm,n'm'} =&
-      \frac{eB}{{m}}
+      \frac{eB}{{\tilde{m}}}
       \delta_{k_x,k'_x} \\
@@
   \begin{aligned}
-      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{elctron} =&
+      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron} =&
       \frac{e^2B}{{m_e}}
@@
 \begin{equation} \label{eq_d12}
-  \hat{j}_y = \frac{1}{m} \qty(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t)).
+  \hat{j}_y = \frac{1}{\tilde{m}} \qty(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t)).
 \end{equation}
@@
   \qty({j}_y)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{-1}{m} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))\;}{n',k'_x}.
+  \mel{n,k_x}{\;\frac{-1}{\tilde{m}} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))\;}{n',k'_x}.
 \end{equation}
-After following the same steps done for $x$-directional current operator, we can derive the $s=0$ component of matrix elements for $y$-directional electric current operator
+After following the same steps done for $x$-directional current operator, we can derive the $s=0$ component of matrix elements for $y$-directional electric current operator as
 \begin{equation} \label{eq_d14}
   \begin{aligned}
-    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{elctron} = &
+    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
     \frac{ie\hbar}{{m_e}}

### 2021-07-25 paper/v1.0/abstract.tex
Corrections for abstract and introduction

--- 2021-07-21 paper/v1.0/abstract.tex
@@
-A generalized mathematical model for the transport properties of quantum systems exposed to a stationary magnetic field and a high intensity electromagnetic field is presented.
-The new formulation, which applies to the two-dimensional dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
+A generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high intensity electromagnetic field is presented.
+The new formulation, which applies to two-dimensional(2D) dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
 We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields.
-To analyze the strong light coupling with the 2DEG, we utilize the Floquet theory as a nonperturbative procedure.
+To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure.
 Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects against Floquet states in disordered quantum Hall systems.
-Based on our fully analytical expression and particular graphical representations, we demonstrate that the characteristics of conductivities in two-dimensional quantum Hall systems can be manipulated using a strong light.
-The outcomes align with the theoretical descriptions which are already well-suited with experimental results and at the same time our theory provides a more generalized analysis on the characteristics of conductivity of quantum Hall systems.
-Thus, this model more realistically describes that how to employ external strong radiation as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-scale quantum devices.
+We derive fully analytical expressions to describe longitudinal components in conductivity tensor in dressed quantum Hall systems and apply the developed model to a numerical evaluation with empirical parameters.
+Then, we demonstrate that the conductivity characteristics in quantum Hall systems can be manipulated using a strong external light.
+Our results align with well-established and experimentally
+verified theoretical descriptions for undressed systems while providing a more generalized analysis on the characteristics of conductivity in quantum Hall systems.
+Thus, our model can be used to more accurately interpret the employment of external strong radiation as a tool to engineer transport properties in various 2D nanostructures.

### 2021-07-25 paper/v1.0/sections/1_introduction.tex
Corrections for abstract and introduction

@@
 
-Manipulating physical systems as a consequence of light engagements inaugurated an astonishing scope of twentieth-century physics namely quantum optics \cite{grynberg10}.
-Quantum optics have dragged research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
-quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and abundant specialities of recent technologies \cite{rivera20}.
-The studies on quantum optics of nanostructures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
-However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding their transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
+Manipulating light matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the twentieth century.
+Quantum optics, which study these interactions, have drawn research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
+quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
+The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
+However, in recent years, the foremost aim of examining nanostructures under external radiation was for understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
 
-The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance \cite{premaratne21}.
-Among these works, most studies have acknowledged the driving field as a perturbation field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
-When a high intensity electromagnetic field account with a perturbation method, the number of higher-order interaction terms need to be recognized gets escalate.
-Then a more accurate and powerful concept need to be adopted and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}.
-On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.
+Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
+Among these works, most studies have considered the driving field as a perturbation field \cite{pervishko15,morina15} However, that assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
+Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity.
+At high intensities, the higher order terms influence the physics more strongly than the lower order terms, and the basis of the perturbative treatment begins to break down.
+Then a more accurate and powerful concept needs to be adopted where we treat  the interacting fermion system and the radiation as one combined quantum system (dressed system) \cite{morina15,cohen98,scully01}.
 
-Theoretical analyses of the transport properties of dressed fermions systems were recently reported in Refs.
-\cite{kibis14,morina15,wackerl20} where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref.
-\cite{wackerl20}, introducing a novel type of Green’s functions namely four-times Green’s functions.
-As a consequence, the established formalism introduces a novel technique to exploit the transport attributes of nanostructures by an intense dressing field.
+Theoretical analyses of the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
+Furthermore, in Ref.
+\cite{wackerl20} a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form, introducing a novel type of Green’s functions namely four-times Green’s functions.
+This established a novel technique to exploit the transport attributes of nanostructures under an intense dressing field.
 
-At the other end, quantum Hall effect \cite{girvin90} observed for two-dimentional fermions systems at low temperatures under strong stationary magnetic field manifest remarkable magneto-transport behaviors and transport properties of these systems attracted many researches attention in experimental \cite{allerman95,tieke97,pan05} and theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} point of view.
-Akira Endo \textit{et al.} \cite{endo09} previously presented, the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoretical calculations are well-suited with the experimental observations while other former studies yields a semi-elliptical broadening for Landau levels and gives less fitting interpretations for the empirical results \cite{endo09}.
+Quantum Hall effect \cite{girvin90} observed for two-dimensional fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors.
+Transport properties of these systems have recently attracted both theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{allerman95,tieke97,pan05} interest.
+Endo \textit{et al.} \cite{endo09} presented the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system.
+These theoretical calculations better align with experimental observations compared to previous studies.
+For instance, former studies yield a semi-elliptical broadening for Landau levels and give less fitting interpretations for the empirical results \cite{endo09}.
 
-In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a nonoscillating magnetic field and simultaneously applying a dressing field.
-Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport in the quantum Hall systems.
-Furthermore, K.
-Dini \textit{et al.} \cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems, and they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
+In contrast, more interesting phenomena can be observed by simultaneously applying a dressing field to a quantum Hall system under a non-oscillating magnetic field.
+Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport.
+Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems.
+However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
 In their study, they used the conductivity models from Refs.
-\cite{ando74_1,ando82} and as mentioned in A.
-Endo \textit{et al.} work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives barely fitting representations for the experimental findings.
+\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} work \cite{endo09}, those models yields a semi-elliptical broadening for Landau levels and gives less agreement with experimental results.
 
-In the present analysis, we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) unveiled to another nonoscillating magnetic field.
-A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized, and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
-Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalized analytical description to identify transport characteristics of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
-Finally, we demonstrate that our generalized model is agreed with state-of-the-art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field.
-Moreover, optical manipulation can be used as a mechanism to utilize transport behavior in numerous two-dimentional nanostructures which serve as a basis for nanoelectronic devices and we believe that our theoretical analysis and visual depictions of numerical results can be used to understand the basic structure and optimize the performance of nanoscale quantum devices.
+In the present analysis, we present robust mathematical model for dressed two-dimensional electron gas(2DEG) subject to another nonoscillating magnetic field.
+A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system and the orbital motion of electrons becomes completely quantized.
+This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
+Such a system is known as a two-dimensional quantum Hall system.
+In this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in periodically driven quantum Hall systems by developing a generalized analytical description to identify transport characteristics of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
+Finally, we demonstrate that our generalized model reproduces the results of
+the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
+Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous two-dimensional nanostructures which can serve as a basis for nanoelectronic devices.
+We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport.
+Moreover, this will inspire advanced  developments in nanoscale quantum devices.
 
@@
 \ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
-The derived theoritical model is further analyzed numerically using empherical system parameters and compared with previous studies in Sec.
+The derived theoritical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec.
 \ref{sec_manipulate_conductivity}, followed by concluding remarks in Sec.

### 2021-07-25 paper/v1.0/sections/3_floquet_theory.tex
Formatting and corrections
Corrections for abstract and introduction

@@
 Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
-Examine the transport properties of quantum systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by M.
-Wackerl \textit{et al.} \cite{wackerl20}.
+Examine the transport properties of quantum systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by Wackerl \textit{et al.} \cite{wackerl20}.
 In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field.
@@
 
-Then performing Fourier transform over the confined two-dimentional space, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
+Then performing Fourier transform over the confined two-dimensional space, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
 \begin{equation} \label{eq_9}
@@
 \end{equation}
-For details of the full derivation please refer to Appendix B. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
+For details of the full derivation please refer to Appendix \ref{appendix_b}.
+Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
 \begin{equation} \label{eq_12}

### 2021-07-25 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Corrections for abstract and introduction

@@
 Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity.
-In addition, $A$ is the area of the considering two-dimentional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
+In addition, $A$ is the area of the considering two-dimensional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
 \begin{equation} \label{eq_21}

### 2021-07-25 paper/v1.0/sections/6_manipulate_conductivity.tex
Corrections for abstract and introduction

@@
 where $\sigma^0 = (e^2/\pi \hbar A)$.
-We use this expression to illustrate the changes that can be done to the longitudinal conductivity in 2DEG using external dressing field.
-As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the longitudinal conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system.
+We use this expression to illustrate the changes that can be done to the longitudinal conductivity in 2DEG using an external dressing field.
+As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the longitudinal conductivity $\sigma_{xx}$ using an external dressing field's intensity and the Fermi level $X_F$ of the considering system.
 For a given dressing field intensity, the longitudinal conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values.
-Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not align with any of the Landau level energy values.
-In contrast, on each Landau level, the conductivity can achieve very high values compared to other areas and as illustrates on Fig.~\ref{fig_5} the peak value of longitudinal conductivity on each Landau level gets increase with the Landau level number.
+Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not aligned with any of the Landau level energy values.
+In contrast, on each Landau level, the conductivity can achieve very high values compared to other areas and as illustrates in Fig.~\ref{fig_5} the peak value of longitudinal conductivity on each Landau level gets increase with the Landau level number.
 
@@
 
-Considering the effect of the external dressing field on longitudinal conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels.
+Considering the effect of the external dressing field on the longitudinal conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels.
 However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
-This demonstrate that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
-These characteristics are aligned with results demonstrated by K.
-Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications.
+This demonstrates that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
+These characteristics are aligned with results demonstrated by Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be changed with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications.
 Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
@@
 This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
-The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistence with the experimentally observed Landau levels representation \cite{endo09}.
-In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result mentioned in Ref.
+The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed Landau levels representation \cite{endo09}.
+In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more aligned with the result mentioned in Ref.
 \cite{endo09}.
-The description of conductivity of quantum Hall systems demonstrated in Ref.~\cite{endo09} has excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range.
+The description of conductivity of quantum Hall systems demonstrated in Ref.~\cite{endo09} has an excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range.
 However, they have not considered the tunability that can be achieved with the external strong dressing field.
-In this analysis we account both magnetic and dressing field effects that can be applied into the transport properties of 2DEG, and we have presented a more generalized theory.
-As a concluding remark, in this study we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the transport properties of quantum Hall systems.
+In this analysis, we account for both magnetic and dressing field effects that can be applied to the transport properties of 2DEG, and we have presented a more generalized theory.
+As a concluding remark, in this study, we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the transport properties of quantum Hall systems.

### 2021-07-25 paper/v1.0/sections/7_conclusions.tex
Corrections for abstract and introduction

@@
 With the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization.
-We modelled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential.
+We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential.
 Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
@@
 Furthermore, we identified that by regulating the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed.
-Despite, this behavior has been identified previous works, their results are not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.
+Despite, this behavior has been identified in previous works, their results are not coinciding with the more accurate description of conductivity components in undressed quantum Hall systems.
 However, our generalized analysis of conductivity in dressed quantum Hall system provides well-suited description for these special quantum Hall systems.
 
-In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems.
-Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices.
-Finally, we identified that our findings of this paper can be used towards understanding nanoscale quantum devices, enhancing their performance and inventing novel appliance.
+In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that the  recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems.
+Due to owing the ability to control the conductivity regions, high intensity external illumination can be used as a trigger for two-dimensional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices.
+Finally, we identified that our findings of this paper can be used towards understanding nanoscale quantum devices, enhancing their performance, and inventing novel appliances.

### 2021-07-25 paper/v1.0/abstract.tex
More corrections

@@
 Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects against Floquet states in disordered quantum Hall systems.
-We derive fully analytical expressions to describe longitudinal components in conductivity tensor in dressed quantum Hall systems and apply the developed model to a numerical evaluation with empirical parameters.
+We derive fully analytical expressions to describe longitudinal components in conductivity tensor in dressed quantum Hall systems.
 Then, we demonstrate that the conductivity characteristics in quantum Hall systems can be manipulated using a strong external light.

### 2021-07-25 paper/v1.0/sections/6_manipulate_conductivity.tex
More corrections

@@
 In this analysis, we account for both magnetic and dressing field effects that can be applied to the transport properties of 2DEG, and we have presented a more generalized theory.
-As a concluding remark, in this study, we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the transport properties of quantum Hall systems.
+As a concluding remark, in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more experimental fitting and generalized mathematical model for the charge transport properties of quantum Hall systems.

### 2021-07-25 paper/v1.0/sections/7_conclusions.tex
More corrections

@@
-In this analysis, we reported a generalized mathematical model for transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light.
-With the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization.
-We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential.
+In this analysis, we introduced a generalized mathematical model for charge transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light.
+Under the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization.
+We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method by considering impurities in the material as Gaussian random scattering potential.
 Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
@@
 Despite, this behavior has been identified in previous works, their results are not coinciding with the more accurate description of conductivity components in undressed quantum Hall systems.
-However, our generalized analysis of conductivity in dressed quantum Hall system provides well-suited description for these special quantum Hall systems.
+However, our generalized analysis of conductivity in dressed quantum Hall systems provide a well-suited description for these special quantum Hall systems.
 
-In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that the  recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems.
+In summary, the primary purpose of this study was to broaden the modern descriptions of transport properties in dressed quantum Hall systems.
+Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adopted to extend the models that were used to describe the transport characteristics in quantum Hall systems.
 Due to owing the ability to control the conductivity regions, high intensity external illumination can be used as a trigger for two-dimensional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices.

### 2021-07-25 paper/v1.0/sections/2_schrodinger_problem.tex
Corrections for abstract and introduction
More corrections

@@
 
-Our system consist of a 2DEG restrained in the $(x,y)$ plane of the three-dimentional coordinate space.
+Our system consist of a 2DEG placed on the $(x,y)$ plane of the three-dimensional coordinate space.
 In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis.
-In addition, a linearly polarized strong light is applied perpendicular to the 2DEG plane, and we specially pick the frequency of the dressing field $\omega$ such that the optical field behaves as a purely dressing field (unabsorbable).
-Furthermore, we do our analysis with a linearly polarized light and without limiting the generality we choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ as the dressing field configuration (Fig.~\ref{fig_1}).
+In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface.
+We specially pick the frequency of the dressing field $\omega$ such that the field behaves as a purely dressing field (off-resonant regime).
+Furthermore, without limiting the generality we choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the linearly polarized dressing field (Fig.~\ref{fig_1}).
 \begin{figure}[b]
@@
 
-Using Landau gauge for the stationary magnetic field, we can represent it using a vector potential as $\vb{A}_{s} = (-By,0,0)^{\text{T}}$ and choosing Coulomb gauge, the vector potential of the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
-These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04} and this leads to the time-dependent Hamiltonian
+Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{\text{T}}$.
+Furthermore, choosing Coulomb gauge, the vector potential for the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
+These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}.
+Thus, our system can represent with a time-dependent Hamiltonian
 \begin{equation} \label{eq_1}
@@
 $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $p_{x,y}$.
-The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ was already given by Refs.
-\cite{husimi53,ditt98,dini16} and we can present them as a set of wave functions defined by two quantum numbers $(n,m)$
+The exact solutions for the time-dependent Schrödinger equation with our system Hamiltonian $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ were already derived in Refs.
+\cite{husimi53,ditt98,dini16}.
+Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
 \begin{equation} \label{eq_2}
@@
 where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix \ref{appendix_a}.
-Here $L_{x,y}$ are dimension of the 2DEG surface, $\hbar$ is the reduced Planck constant, and the center of the cyclotron orbit on the $y$-axis is given by $y_0 \equiv -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
-$\chi_n$ are well known solutions for Schrödinger equation of a stationary quantum harmonic oscillator
+$L_{x,y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant.
+The center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
+Moreover, $\chi_n$ are well known eigenstate solutions for the Schrödinger equation of stationary quantum harmonic oscillator
 \begin{equation} \label{eq_3}
@@
 \end{equation}
-where eigenvalues are given by $\epsilon_n = \hbar \omega_0 (n + 1/2)$ and $\omega_0 \equiv eB/m_e$ is the cyclotron frequency.
-Each $n$ value defines the occupied energy($\epsilon_n$) of the respective Landau level.
-The path shift of the driven classical oscillator $\zeta(t)$ is given by
+with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\omega_0 = eB/m_e$ is the cyclotron frequency. The path shift of the driven classical oscillator $\zeta(t)$ is given by
 \begin{equation} \label{eq_4}
@@
 \end{equation}
-while the Lagrangian of the classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
+while the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
 \begin{equation} \label{eq_5}
@@
 The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and dressing field.
-Therefore, we can accept that magneto-transport characteristics of 2DEG can be renormalized by the nonoscillating magnetic field along with the dressing field.
+Therefore, we can accept that the magneto-transport characteristics of 2DEG can be renormalized by a nonoscillating magnetic field along with a dressing field.

### 2021-07-25 paper/v1.0/sections/3_floquet_theory.tex
More corrections

@@
 
-First we require to recognize the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the previously derived wave functions in Eq.~(\ref{eq_2}).
-By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can be present as
+First we require to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}).
+By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can be presented as
 \begin{equation} \label{eq_6}
@@
 \end{equation}
-which is only depended on a single quantum number ($n$) and Floquet modes are given by
+which is only depended on a single quantum number ($n$). Then Floquet modes can be recognized as
 \begin{equation} \label{eq_7}
@@
 At the resonance $\omega = \omega_0$, the energy levels occupies a continuous form and the discrete quasienergies are no longer valid \cite{popov70}.
-Therefore, in this work we choose the dressing field frequency with the condition $\omega \neq \omega_0$.
+Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.
 
@@
 \begin{equation} \label{eq_11}
-  b \equiv
+  b =
   \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad \text{and} \quad
-  d \equiv
+  d =
  \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
 \end{equation}
-For details of the full derivation please refer to Appendix \ref{appendix_b}.
-Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
+For the detailed derivation please refer to Appendix \ref{appendix_b}. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
 \begin{equation} \label{eq_12}

### 2021-07-26 paper/v1.0/sections/3_floquet_theory.tex
More corrections

@@
 Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
-Examine the transport properties of quantum systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by Wackerl \textit{et al.} \cite{wackerl20}.
-In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field.
-Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
+As a method to analyze the transport properties of quantum systems exposed to strong radiation, the Floquet-Drude conductivity theory was introduced recently by Wackerl \textit{et al.} \cite{wackerl20}.
+In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field.
+Therefore, we are expecting to apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
 
-First we require to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}).
-By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can be presented as
+First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}).
+By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can present as
 \begin{equation} \label{eq_6}
@@
 \end{equation}
-which is only depended on a single quantum number ($n$). Then Floquet modes can be recognized as
+which is only depend on a single quantum number $n$. Then Floquet modes are recognized as
 \begin{equation} \label{eq_7}
@@
 \end{equation}
-For the detailed derivation please refer to Appendix \ref{appendix_b}. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
+For the detailed derivation, please refer to Appendix \ref{appendix_b}. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space
 \begin{equation} \label{eq_12}

### 2021-07-26 paper/v1.0/sections/4_inverse_scattering_time.tex
More corrections

--- 2021-07-23 paper/v1.0/sections/4_inverse_scattering_time.tex
@@
 
-In Ref.
-\cite{wackerl20} Floquet Fermi golden rule has been introduced as a method to analyze transport properties in dressed disordered quantum systems.
-However, this theory has not been applied for a dressed quantum Hall system and to identify magneto-transport properties in our system we use Floquet Fermi golden rule.
-With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}) we can derive an  expression for the inverse scattering time matrix ($(l,l')$th element) for the $N$-th Landau level, per a given energy $\varepsilon$ and momentum $k_x$ value for our considered quantum Hall system as
+The Floquet Fermi golden rule was proposed as a approach to analyze the transport properties in dressed quantum systems with impurities in Ref.
+\cite{wackerl20}.
+However, this theory has not been applied for a dressed quantum Hall system.
+In this study, we use Floquet Fermi golden rule to identify the effect induced by impurities on the magneto-transport properties.
+With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}), we can derive an  expression for the inverse scattering time matrix ($(l,l')$-th element) for the $N$-th Landau level, per a given energy $\varepsilon$ and x-directional momentum $k_x$ value for our considered quantum Hall system
 \begin{equation} \label{eq_13}
@@
     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg],
+    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg].
   \end{aligned}
 \end{equation}
-where $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
-$J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix C.
-In this derivation, we assumed that the perturbation potential is generated by a group of randomly distributed impurities, since random impurities in a disordered metal is a better approximation for experimental results.
+Here $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
+$J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix \ref{appendix_c}.
+Since random impurities in a disordered metal is a better approximation for experimental results, in this derivation, we assumed that the perturbation potential is generated by a group of randomly distributed impurities.
 Thus, the total scattering potential in 2DEG has been presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} \equiv \expval{|V_{{k'}_x,k_x}|^2}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}/\sqrt{L_x}$.
+Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}$.
+Additionally, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
 

### 2021-07-26 paper/v1.0/sections/4_inverse_scattering_time.tex
More corrections

@@
 $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix \ref{appendix_c}.
+We model the effect cause by impurities in the considering system by a single perturbation potential.
 Since random impurities in a disordered metal is a better approximation for experimental results, in this derivation, we assumed that the perturbation potential is generated by a group of randomly distributed impurities.
-Thus, the total scattering potential in 2DEG has been presented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+Thus, the total scattering potential in 2DEG has been represented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
 Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}$.
@@
 
-Next we are going to analyze the contribution of the inverse scattering time matrix elements to the transport properties in 2DEG.
-Since the disorder in the system can not be alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the all off-diagonal elements of the self-energy, and then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
-% \begin{equation} \label{eq_14}
-%   \begin{aligned}
-%     \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{00}_{N} \\
-%     & =
-%     \frac { \varrho^2}{eB}
-%     \delta(\varepsilon - \varepsilon_{N}) \\
-%     & \times
-%     \int_{-\infty}^{\infty} d k_1 \;
-%     J_0^2\qty(\frac{b\hbar}{eB}[{k}_x -  k_1])
-%     \\
-%     & \times
-%     \qty|
-%     \int_{-\infty}^{\infty} d k_2 \;
-%     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
-%     {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2.
-%   \end{aligned}
-% \end{equation}
-Introduce a new parameter as scattering-induced broadening of the $N$-th Landau level as \cite{dini16,endo09}
+As the next step, it is impoertant to analyze the contribution of the inverse scattering time matrix elements to the transport properties in our system.
+Since the disorder in the system can not be alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the all off-diagonal elements of the inverse scattering time.
+Then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+Along with this assumption, introduce a new parameter as scattering-induced broadening of the $N$-th Landau level as \cite{dini16,endo09}
 \begin{equation} \label{eq_14}
@@
  \delta(\varepsilon - \varepsilon_{N}) \approx
- \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)},
+ \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)}.
 \end{equation}
-and we write the central element of inverse scattering time matrix in more compact form
+Then we can write the central element of inverse scattering time matrix in more compact form
 \begin{equation} \label{eq_17}
@@
 where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
-To analyze the contribution of dressing field on the scattering-induced broadening, normalized $N$-th Landau level scattering-induced broadening can be defined as
+To analyze the effect done by the dressing field on the scattering-induced broadening, we can introduce normalized $N$-th Landau level scattering-induced broadening as
 \begin{equation} \label{eq_18}
@@
 
-Normalized energy band broadening against ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are given in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
-To make comparison we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
-In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20} and the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.
+Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
+To make a comparison, we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
+In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20}.
+In addition, they used the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$.
 Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
-Here we can identify that the each Landau level normalized energy broadening value is independent of the x-directional momentum $k_x$ value and we are able to change it using applied electromagnetic field.
-When the applied field's intensity increase the energy broadening gets reduced which make changes in transport properties and in the next section, we are going to derive a analytical expression for the conductivity in dressed quantum Hall systems.
+Here we can identify that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
+When the dressing field's intensity increase, the energy broadening gets reduced and this make adjustments in transport properties.
+In the next section, we are going to derive a analytical expression for the conductivity in dressed quantum Hall systems to analyze these adjustments.

### 2021-07-26 paper/v1.0/sections/5_floquet_drude_conductivity.tex
More corrections

@@
 
-A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M.
-Wackerl in Refs.~\cite{wackerl20,wackerlthesis20}.
-Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
+A general theory for the conductivity in dressed systems with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}.
+Within this theory, the general $x$-directional longitudinal DC limit conductivity has been discribed by
 \begin{equation} \label{eq_20}
@@
 \end{equation}
-where $ \varepsilon_N$ are quasienergies of all considering Floquet states.
+where $ \varepsilon_N$ are quasienergies of all considering Floquet states. Moreover, $tr[\cdot]$ is the trace of operator.
 
@@
 \end{equation}
-where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evaluate by considering each matrix elements separately
+where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evaluate as follows
 \begin{equation} \label{eq_23}
@@
 \end{equation}
-Since we can diagonalize the impurity averaged Green's function using unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}, and we evaluate the matrix element of the difference between retarded and advanced Green's functions
+Since we can diagonalize the impurity averaged Green's functions using unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}.
+Thus, we evaluate the matrix element of the difference between retarded and advanced Green's functions as
 \begin{equation} \label{eq_24}
@@
   + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
-  }],
+  }].
 \end{equation}
-using the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
-Using the matrix elements of electric current operator in Landau levels (see Appendix \ref{appendix_d}) and
-results form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain
+Here we used the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
+Applying the matrix elements of the electric current operator in Landau levels (see Appendix \ref{appendix_d}) and
+results form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we can obtain
 \begin{equation} \label{eq_26}
@@
 \end{equation}
-and the only non-zero term would be
+and after the expansion, the only remaining non-zero term would be
 \begin{equation} \label{eq_27}
@@
 \end{equation}
-Since the inverse scattering time matrix being equal to the diagonalized contrast of the retarded and advanced self-energy and on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20} we can identify the following property
+Since the inverse scattering time matrix being equal to the diagonalized contrast of the retarded and advanced self-energy, and on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20}, we can identify the following property
 \begin{equation} \label{eq_28}
   \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll} =
-  -2\text{Im}\qty[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}]^{ll},
+  -2\text{Im}\qty[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}]^{ll}.
 \end{equation}
-and using central element ($l=0$) of the inverse scattering time matrix we can modify the derived conductivity expression
+Then using central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression as follows
 \begin{equation} \label{eq_29}
@@
 \end{widetext}
-with $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
-We already identified that the inverse scattering time matrix's central element is not $k_x$ dependent we can get the sum over all available momentum space in $x$ direction.
-However, by considering the condition that the center of the force of the oscillator $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify
+where $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
+We already identified that the inverse scattering time matrix's central element is independent of $k_x$ value and we can get the sum over all available momentum space in $x$ direction.
+However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify that
 \begin{equation} \label{eq_30}
@@
 \end{equation}
-Then we use the Fermi-Dirac distribution as our partial distribution function ($f$) for this system
+Then we use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
 \begin{equation} \label{eq_31}
@@
 where $k_B$ is Boltzmann constant, $T$ is absolute temperature and $\varepsilon_F$ is Fermi energy of the system.
-Considering the above distribution with extremely low temperature conditions we can approximate
+Considering the above distribution with extremely low temperature conditions, we can approximate
 \begin{equation} \label{eq_32}
@@
 $\gamma_n \equiv {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
-Same as above derivation we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix \ref{appendix_d}
+Same as above derivation, we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix \ref{appendix_d}
 \begin{equation} \label{eq_34}

### 2021-08-02 paper/v1.0/abstract.tex
Formatting and correcting

@@
 To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure.
-Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects against Floquet states in disordered quantum Hall systems.
-We derive fully analytical expressions to describe longitudinal components in conductivity tensor in dressed quantum Hall systems.
-Then, we demonstrate that the conductivity characteristics in quantum Hall systems can be manipulated using a strong external light.
+Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects on charge transport in disordered quantum Hall systems.
+We derive fully analytical expressions to describe longitudinal components in the conductivity tensor in dressed quantum Hall systems.
+Subsequently, we demonstrate that the conductivity characteristics of quantum Hall systems can be manipulated using a strong external light.
 Our results align with well-established and experimentally
-verified theoretical descriptions for undressed systems while providing a more generalized analysis on the characteristics of conductivity in quantum Hall systems.
-Thus, our model can be used to more accurately interpret the employment of external strong radiation as a tool to engineer transport properties in various 2D nanostructures.
+verified theoretical descriptions for undressed systems while providing a more generalized analysis on the conductivity characterstics in quantum Hall systems.
+Thus, our model can be applied to accurately interpret the usage of external strong radiation as a tool in nanoscale quantum devices.

### 2021-08-02 paper/v1.0/sections/1_introduction.tex
Formatting and correcting

@@
 
-Manipulating light matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the twentieth century.
-Quantum optics, which study these interactions, have drawn research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
+Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century.
+Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
 quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
-The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
-However, in recent years, the foremost aim of examining nanostructures under external radiation was for understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
+The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, and quantum cavity physics \cite{tsang10,devi20}.
+However, in recent years, one of the foremost aim of examining nanostructures under external radiation was for understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
 
 Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
-Among these works, most studies have considered the driving field as a perturbation field \cite{pervishko15,morina15} However, that assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
+Most recent studies on the subject have considered the driving field as a perturbation field \cite{pervishko15,morina15}.
+However, this assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
 Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity.
 At high intensities, the higher order terms influence the physics more strongly than the lower order terms, and the basis of the perturbative treatment begins to break down.
-Then a more accurate and powerful concept needs to be adopted where we treat  the interacting fermion system and the radiation as one combined quantum system (dressed system) \cite{morina15,cohen98,scully01}.
+In these instances, a more accurate treatment needs to adopt.
+Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}.
+Here the applied high intensity  electromagnetic field identify as the dressing field.
 
@@
 Furthermore, in Ref.
-\cite{wackerl20} a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form, introducing a novel type of Green’s functions namely four-times Green’s functions.
-This established a novel technique to exploit the transport attributes of nanostructures under an intense dressing field.
+\cite{wackerl20} a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form, using a novel type of Green’s functions, namely four-times Green’s functions.
+This opened the path to explore and exploit the charge transport attributes of nanostructures under an intense dressing field.
 
-Quantum Hall effect \cite{girvin90} observed for two-dimensional fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors.
+Quantum Hall effect \cite{girvin90} observed in two-dimensional fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors.
 Transport properties of these systems have recently attracted both theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{allerman95,tieke97,pan05} interest.
 Endo \textit{et al.} \cite{endo09} presented the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system.
-These theoretical calculations better align with experimental observations compared to previous studies.
-For instance, former studies yield a semi-elliptical broadening for Landau levels and give less fitting interpretations for the empirical results \cite{endo09}.
+These theoretical calculations  align better with experimental observations compared to previous studies.
 
-In contrast, more interesting phenomena can be observed by simultaneously applying a dressing field to a quantum Hall system under a non-oscillating magnetic field.
+In contrast, more interesting phenomena can be observed by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
 Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport.
@@
 In their study, they used the conductivity models from Refs.
-\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} work \cite{endo09}, those models yields a semi-elliptical broadening for Landau levels and gives less agreement with experimental results.
+\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening agaist Fermi level for each Landau levels and provide less agreement with the empirical results.
 
-In the present analysis, we present robust mathematical model for dressed two-dimensional electron gas(2DEG) subject to another nonoscillating magnetic field.
-A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system and the orbital motion of electrons becomes completely quantized.
+In the present analysis, we present a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
+A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system.
 This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
-Such a system is known as a two-dimensional quantum Hall system.
-In this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in periodically driven quantum Hall systems by developing a generalized analytical description to identify transport characteristics of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
-Finally, we demonstrate that our generalized model reproduces the results of
-the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
-Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous two-dimensional nanostructures which can serve as a basis for nanoelectronic devices.
+In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
+Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref.
+\cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
+Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous two-dimensional nanostructures which can serve as a basis for many useful nanoelectronic devices.
 We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport.
@@
 \ref{sec_floquet_theory}, provides the Floquet theory interpretation of these wave functions.
-We introduce Floquet Fermi golden rule for quantum Hall system in Sec.
-\ref{sec_inverse_scattering_time}, and we use it in Sec.
+We introduce Floquet Fermi golden rule for a quantum Hall system in Sec.
+\ref{sec_inverse_scattering_time}, and use it in Sec.
 \ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
-The derived theoritical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec.
-\ref{sec_manipulate_conductivity}, followed by concluding remarks in Sec.
-\ref{sec_conclusions}.
+The derived theoritical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}.
+In Sec. \ref{sec_conclusions}, we summarize our analysis and present our conlusions.

### 2021-08-02 paper/v1.0/sections/2_schrodinger_problem.tex
Formatting and correcting

@@
 
-Our system consist of a 2DEG placed on the $(x,y)$ plane of the three-dimensional coordinate space.
+Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space.
 In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis.
 In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface.
-We specially pick the frequency of the dressing field $\omega$ such that the field behaves as a purely dressing field (off-resonant regime).
+We specially select the frequency of the dressing field $\omega$ to be in the off-ersonant regime such that the field behaves as a purely dressing field.
 Furthermore, without limiting the generality we choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the linearly polarized dressing field (Fig.~\ref{fig_1}).
@@
 \end{figure}
-Here $B$ and $E$ represent the amplitude of the stationary magnetic field and oscillating electric field respectively.
+Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field respectively.
 
 Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{\text{T}}$.
-Furthermore, choosing Coulomb gauge, the vector potential for the dynamic dressing radiation can be presented as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
+Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
 These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}.
-Thus, our system can represent with a time-dependent Hamiltonian
+Thus, our system can be represented with a time-dependent Hamiltonian
 \begin{equation} \label{eq_1}
@@
 \end{equation}
-where $m_e$ is the effective electron mass and $e$ is the magnitude of the electron charge.
-$\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $p_{x,y}$.
-The exact solutions for the time-dependent Schrödinger equation with our system Hamiltonian $i\hbar \dv{t}\psi = \hat{H}_e(t) \psi$ were already derived in Refs.
+where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{\text{T}}$.
+The exact solutions for the time-dependent Schrödinger equation $i\hbar\; \text{d}\psi/\text{d}t = \hat{H}_e(t) \psi$ were already derived in Refs.
 \cite{husimi53,ditt98,dini16}.
@@
 \end{equation}
-where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$ ; see Appendix \ref{appendix_a}.
-$L_{x,y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant.
+where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$.
+Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant.
 The center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
-Moreover, $\chi_n$ are well known eigenstate solutions for the Schrödinger equation of stationary quantum harmonic oscillator
+Moreover, $\chi_n$ are well known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
 \begin{equation} \label{eq_3}
@@
 \end{equation}
-with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\omega_0 = eB/m_e$ is the cyclotron frequency. The path shift of the driven classical oscillator $\zeta(t)$ is given by
+with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\omega_0 = eB/m_e$ being the cyclotron frequency and $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial.
+The path shift of the driven classical oscillator $\zeta(t)$ is given by
 \begin{equation} \label{eq_4}
@@
 \end{equation}
-The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence done by the stationary magnetic field and dressing field.
-Therefore, we can accept that the magneto-transport characteristics of 2DEG can be renormalized by a nonoscillating magnetic field along with a dressing field.
+For details of the full derivation refer to Appendix \ref{appendix_a}.
+The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system.
+Therefore, we can observe that the magneto-transport characteristics of 2DEG can be renormalized by a nonoscillating magnetic field along with a dressing field.

### 2021-08-02 paper/v1.0/sections/3_floquet_theory.tex
Formatting and correcting

@@
 
-The general interpretations of physical systems are mostly derived using symmetry conditions in quantum theory.
-Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation of quantum systems occupying a discrete translational symmetry in configuration space.
+The general interpretations of physical quantum systems are mostly derived using symmetry conditions.
+The Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in configuration space.
 Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
-As a method to analyze the transport properties of quantum systems exposed to strong radiation, the Floquet-Drude conductivity theory was introduced recently by Wackerl \textit{et al.} \cite{wackerl20}.
-In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field.
-Therefore, we are expecting to apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
+The Floquet-Drude conductivity theory was introduced recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
+In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field.
+Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
 
 First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}).
-By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, the quasienergies can present as
+By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, we present the quasienergies as
 \begin{equation} \label{eq_6}
@@
 \end{equation}
-which is only depend on a single quantum number $n$. Then Floquet modes are recognized as
+which only depends on a single quantum number $n$. The Floquet modes can then be recognized as
 \begin{equation} \label{eq_7}
@@
 with
-\begin{equation} \label{eq_8}
-  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)} ~ \text{and} ~
+\begin{equation} \label{eq_8a}
+  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)},
+\end{equation}
+and
+\begin{equation} \label{eq_8b}
   \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
 \end{equation}
-It is important to notice that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
-At the resonance $\omega = \omega_0$, the energy levels occupies a continuous form and the discrete quasienergies are no longer valid \cite{popov70}.
+It is important to note that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
+At resonance $\omega = \omega_0$, the energy levels occupy a continuous spectrum and the discrete quasienergies are no longer valid \cite{popov70}.
 Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.
 
-Then performing Fourier transform over the confined two-dimensional space, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
+Performing the Fourier transform over the confined two-dimensional space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
 \begin{equation} \label{eq_9}
@@
 \end{equation}
-For the detailed derivation, please refer to Appendix \ref{appendix_b}. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space
+For a detailed derivation, please refer to Appendix \ref{appendix_b}. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space
 \begin{equation} \label{eq_12}

### 2021-08-03 paper/v1.0/sections/1_introduction.tex
corrections

@@
 The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, and quantum cavity physics \cite{tsang10,devi20}.
-However, in recent years, one of the foremost aim of examining nanostructures under external radiation was for understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
+However, in recent years, one of the foremost aim of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
 
@@
 Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity.
-At high intensities, the higher order terms influence the physics more strongly than the lower order terms, and the basis of the perturbative treatment begins to break down.
+At high intensities, the higher order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
 In these instances, a more accurate treatment needs to adopt.
 Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}.
-Here the applied high intensity  electromagnetic field identify as the dressing field.
+Here the applied high-intensity  electromagnetic field identify as the dressing field.
 
-Theoretical analyses of the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
+Theoretical analyses on the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
 Furthermore, in Ref.
-\cite{wackerl20} a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form, using a novel type of Green’s functions, namely four-times Green’s functions.
+\cite{wackerl20} a general expression for conductivity in a dressed system has been derived in a fully closed analytical form.
+In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula.
 This opened the path to explore and exploit the charge transport attributes of nanostructures under an intense dressing field.

### 2021-08-03 paper/v1.0/sections/4_inverse_scattering_time.tex
Corrections

@@
 
-The Floquet Fermi golden rule was proposed as a approach to analyze the transport properties in dressed quantum systems with impurities in Ref.
-\cite{wackerl20}.
-However, this theory has not been applied for a dressed quantum Hall system.
-In this study, we use Floquet Fermi golden rule to identify the effect induced by impurities on the magneto-transport properties.
-With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and using Floquet states derived in Eq.~(\ref{eq_12}), we can derive an  expression for the inverse scattering time matrix ($(l,l')$-th element) for the $N$-th Landau level, per a given energy $\varepsilon$ and x-directional momentum $k_x$ value for our considered quantum Hall system
+The Floquet-Fermi golden rule was proposed as an approach to analyze the transport properties of dressed quantum systems with impurities in Ref. \cite{wackerl20}.
+However, this theory has not been applied for a dressed quantum Hall system in the previous studies.
+In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
+With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq_12}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
 \begin{equation} \label{eq_13}
@@
     {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg].
+    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg],
   \end{aligned}
 \end{equation}
-Here $\varrho \equiv \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$,
-$J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order and $\varepsilon_N$ is the energy of $N$-th Landau level; see Appendix \ref{appendix_c}.
-We model the effect cause by impurities in the considering system by a single perturbation potential.
-Since random impurities in a disordered metal is a better approximation for experimental results, in this derivation, we assumed that the perturbation potential is generated by a group of randomly distributed impurities.
-Thus, the total scattering potential in 2DEG has been represented as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-Here $\eta_{imp}$ is the number of impurities in a unit area and $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$ where $\braket{x}{k_x} = e^{-ik_x x}$.
-Additionally, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
+where $\varrho = \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of $N$-th Landau level.
+Detailed derivation is given in Appendix \ref{appendix_c}.
+We modeled the effect cause by impurities in the considering system by a single perturbation potential.
+Since random impurities in a disordered metal is a better approximation for experimental results, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
+Thus, the total scattering potential in 2DEG has been represented as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
+Moreover in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
 
-As the next step, it is impoertant to analyze the contribution of the inverse scattering time matrix elements to the transport properties in our system.
-Since the disorder in the system can not be alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the all off-diagonal elements of the inverse scattering time.
-Then we can consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
-Along with this assumption, introduce a new parameter as scattering-induced broadening of the $N$-th Landau level as \cite{dini16,endo09}
+Next we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
+Since the disorder in the system can not alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
+Then we consider only the central (${l=l'=0}$) diagonal element of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
 \begin{equation} \label{eq_14}

### 2021-08-05 paper/v1.0/sections/4_inverse_scattering_time.tex
Corrections

@@
 
-In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy using the following interpretation \cite{dini16}
+In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
 \begin{equation} \label{eq_16}
@@
 \end{equation}
-Then we can write the central element of inverse scattering time matrix in more compact form
+Then we write the central element of inverse scattering time matrix in more compact form
 \begin{equation} \label{eq_17}
@@
 where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
-To analyze the effect done by the dressing field on the scattering-induced broadening, we can introduce normalized $N$-th Landau level scattering-induced broadening as
+To analyze the effects done by the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
 \begin{equation} \label{eq_18}
@@
 \end{equation}
-and this leads to
+and this can evaluate with
 \begin{widetext}
@@
 
-Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
+Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
 To make a comparison, we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
 In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20}.
-In addition, they used the broadening of the natural(without a dressing field) $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$.
+In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$.
 Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
-Here we can identify that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
-When the dressing field's intensity increase, the energy broadening gets reduced and this make adjustments in transport properties.
-In the next section, we are going to derive a analytical expression for the conductivity in dressed quantum Hall systems to analyze these adjustments.
+Here we observe that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
+When the dressing field's intensity increase, the energy broadening gets reduced and this adds modifications to the transport properties of the system.
+To analyze these adjustments in detail, we derive a analytical expression for the conductivity of a dressed quantum Hall system in the next section.

### 2021-08-05 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Corrections

@@
 
-A general theory for the conductivity in dressed systems with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}.
-Within this theory, the general $x$-directional longitudinal DC limit conductivity has been discribed by
+A general theory for the conductivity of a dressed system with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}.
+Within this theory, the general $x$-directional longitudinal DC-limit conductivity has been discribed by
 \begin{equation} \label{eq_20}
@@
 \end{equation}
-where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix \ref{appendix_d}) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system.
-Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity.
-In addition, $A$ is the area of the considering two-dimensional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
+where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system.
+Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity.
+In addition, $A$ is the area of the considering two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
 \begin{equation} \label{eq_21}
@@
     <
-    \Pi + \frac{\hbar \omega}{2},
+    \Pi + \frac{\hbar \omega}{2}.
 \end{equation}
-where $ \varepsilon_N$ are quasienergies of all considering Floquet states. Moreover, $tr[\cdot]$ is the trace of operator.
+Here, $ \varepsilon_N$ are quasienergies of all considering Floquet states, and $tr[\cdot]$ is the trace of the considering operator.
 
-Then Eq.~(\ref{eq_20}) can be expanded in off resonant regime ($\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system, using only central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$
+Next, we restrict our analysis into off-resonant regime $\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system.
+Thus, the $x$-directional longitudinal conductivity given in
+Eq.~(\ref{eq_20}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$
 \begin{widetext}
@@
 \end{equation}
-where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Then this can evaluate as follows
+where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Next, we evaluate the above expression as follows
 \begin{equation} \label{eq_23}
@@
 \end{equation}
-Since we can diagonalize the impurity averaged Green's functions using unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}.
+We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}.
 Thus, we evaluate the matrix element of the difference between retarded and advanced Green's functions as
@@
 \end{equation}
-Here we used the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
-Applying the matrix elements of the electric current operator in Landau levels (see Appendix \ref{appendix_d}) and
-results form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we can obtain
+Here we introduced the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
+Applying the matrix elements of the electric current operator in Landau levels and
+expressions form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain
 \begin{equation} \label{eq_26}
@@
 \end{equation}
-and after the expansion, the only remaining non-zero term would be
+For the full derivation of electric current operators in quantum Hall system refer to Appendix \ref{appendix_d}.
+After the expansion, the only non-zero term would be
 \begin{equation} \label{eq_27}
@@
 \end{equation}
-Then using central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression as follows
+Aterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in \ref{eq_27} as follows
 \begin{equation} \label{eq_29}
@@
 \end{widetext}
-where $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
-We already identified that the inverse scattering time matrix's central element is independent of $k_x$ value and we can get the sum over all available momentum space in $x$ direction.
+with $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
+Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\tilde{{\Gamma}}(\varepsilon_n,k_x)$ terms and get the sum over all available momentum space in $x$ direction.
 However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify that
@@
 \end{equation}
-Then we use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
+We use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
 \begin{equation} \label{eq_31}
@@
 \end{equation}
-where $k_B$ is Boltzmann constant, $T$ is absolute temperature and $\varepsilon_F$ is Fermi energy of the system.
-Considering the above distribution with extremely low temperature conditions, we can approximate
+where $k_B$ is theBoltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
+Considering the above distribution with extremely low temperature conditions, we use thee following approximation
 \begin{equation} \label{eq_32}
@@
 \end{equation}
-and by letting $\Pi = \varepsilon_F$, the expression for conductivity leads to
+and by letting $\Pi = \varepsilon_F$, the derived expression in \ref{eq_29} leads to
 \begin{equation} \label{eq_33}
@@
 $\gamma_n \equiv {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
-Same as above derivation, we can derive the longitudinal conductivity in $y$-direction by using the current operator derived in Appendix \ref{appendix_d}
+Following the same steps as above derivation, we can derive the longitudinal conductivity in $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
 \begin{equation} \label{eq_34}

### 2021-08-05 paper/v1.0/sections/6_manipulate_conductivity.tex
Corrections

@@
 
-To identify the characteristics of the longitudinal conductivity of the quantum Hall systems with external dressing field, first we can derive an expression for a normalized
-longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
-Here we have the normalized x-directional conductivity using the natural conductivity of the least Landau level
+To identify the characteristics of the longitudinal conductivity of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
+Here we derive a normalized $x$-directional conductivity of dressed quantum Hall system using the natural conductivity of the least Landau level
 \begin{equation} \label{eq_35}
   \begin{aligned}
-    \frac{\sigma^{xx}}{\sigma^{0}} = &
+    \tilde{\sigma}^{xx} =
+    \sigma_{0} &
     \sum_{n}
@@
 \end{equation}
-where $\sigma^0 = (e^2/\pi \hbar A)$.
-We use this expression to illustrate the changes that can be done to the longitudinal conductivity in 2DEG using an external dressing field.
-As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the longitudinal conductivity $\sigma_{xx}$ using an external dressing field's intensity and the Fermi level $X_F$ of the considering system.
+with $\sigma^0 = e^2/\pi \hbar A$.
+
+We use this expression to illustrate the changes that can be done to the longitudinal conductivity of 2DEG under stationary magnetic field using an external dressing field.
+As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considering system.
 For a given dressing field intensity, the longitudinal conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values.
-Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not aligned with any of the Landau level energy values.
-In contrast, on each Landau level, the conductivity can achieve very high values compared to other areas and as illustrates in Fig.~\ref{fig_5} the peak value of longitudinal conductivity on each Landau level gets increase with the Landau level number.
+In quantum Hall systems, electrons are restricted to bear only the Landau level energies.
+Thus, the conductivity gets very low values when the Fermi level is not aligned with any of the Landau level energy values.
+In contrast, on each Landau level, the conductivity achieve excessive values compared to other areas.
+Moreover, as illustrates in Fig.~\ref{fig_5} the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.
 
@@
 \includegraphics[scale=0.55]{figures/fig_5}
-\caption{\label{fig_5} Normalized longitudinal conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_5} Normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
@@
 \includegraphics[scale=0.55]{figures/fig_6}
-\caption{\label{fig_6} $3$rd Landau level’s normalized longitudinal conductivity $\sigma_{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
+\caption{\label{fig_6} $3$rd Landau level’s normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
 In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
@@
 
-Considering the effect of the external dressing field on the longitudinal conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels.
+On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field shrink the conductivity regions near Landau levels.
+When we increase the intensity level of the dressing field, the conductivity regions get more weaken as illustrate in the \ref{fig_6}.
 However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
 This demonstrates that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
-These characteristics are aligned with results demonstrated by Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be changed with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications.
-Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
+
+These characteristics are aligned with the results demonstrated by Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be changed with the applied gate voltage of the material this can be utilized as a 2D switch for nanoscale optoelectronics applications.
+Controlling  the external dressing field's intensity, we are able to fine-tune this switching mechanism for an optimized performance.
 Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
@@
 The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed Landau levels representation \cite{endo09}.
-In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more aligned with the result mentioned in Ref.
+In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the result depicted in Ref.
 \cite{endo09}.
-The description of conductivity of quantum Hall systems demonstrated in Ref.~\cite{endo09} has an excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range.
-However, they have not considered the tunability that can be achieved with the external strong dressing field.
-In this analysis, we account for both magnetic and dressing field effects that can be applied to the transport properties of 2DEG, and we have presented a more generalized theory.
+The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimently observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
+However, they have not considered the tunability that can be achieved with a dressing field.
+In this analysis, we account both of the magnetic and dressing field effects that can be applied to the transport properties of 2DEG, and we have presented a more generalized theory.
 As a concluding remark, in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more experimental fitting and generalized mathematical model for the charge transport properties of quantum Hall systems.

### 2021-08-05 paper/v1.0/sections/7_conclusions.tex
Corrections concusion

@@
 Under the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization.
-We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method by considering impurities in the material as Gaussian random scattering potential.
+We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method.
+We assumed the impurities in the material as a Gaussian random scattering potential.
 Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
@@
 Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
-We found that the graphical illustrations we gained are capable of produce the same behavior as the experiment conductivity found in quantum Hall systems without a dressing field.
-Furthermore, we identified that by regulating the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed.
+We found that the graphical illustrations that we obtained from these numerical calculatiuons are capable of producing the same behavior as the experimental  result found in undressed quantum Hall systems.
+Furthermore, we identified that by increasing the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed.
 Despite, this behavior has been identified in previous works, their results are not coinciding with the more accurate description of conductivity components in undressed quantum Hall systems.
-However, our generalized analysis of conductivity in dressed quantum Hall systems provide a well-suited description for these special quantum Hall systems.
+However, our generalized analysis on conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.
 
-In summary, the primary purpose of this study was to broaden the modern descriptions of transport properties in dressed quantum Hall systems.
+In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems.
 Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adopted to extend the models that were used to describe the transport characteristics in quantum Hall systems.

### 2021-08-09 paper/v1.0/sections/1_introduction.tex
Corrections
Corrections from Ravi

@@
 
-Quantum Hall effect \cite{girvin90} observed in two-dimensional fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors.
+Quantum Hall effect \cite{girvin90} observed in two-dimensional (2D) fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors.
 Transport properties of these systems have recently attracted both theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{allerman95,tieke97,pan05} interest.
@@
 \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
-Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous two-dimensional nanostructures which can serve as a basis for many useful nanoelectronic devices.
+Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices.
 We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport.
@@
 \ref{sec_floquet_theory}, provides the Floquet theory interpretation of these wave functions.
-We introduce Floquet Fermi golden rule for a quantum Hall system in Sec.
+We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec.
 \ref{sec_inverse_scattering_time}, and use it in Sec.

### 2021-08-09 paper/v1.0/sections/3_floquet_theory.tex
corrections
Corrections from Ravi

@@
 
-The general interpretations of physical quantum systems are mostly derived using symmetry conditions.
-The Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in configuration space.
-Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
-The Floquet-Drude conductivity theory was introduced recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
+Symmetry conditions often gives useful insights into the behaviors of physical quantum systems.
+For instance, in the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in configuration space.
+Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
+The Floquet-Drude conductivity theory was emplyoed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
 In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field.
@@
 It is important to note that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
-At resonance $\omega = \omega_0$, the energy levels occupy a continuous spectrum and the discrete quasienergies are no longer valid \cite{popov70}.
+At resonance $\omega = \omega_0$, the energy levels occupy a continuous spectrum and the quasienergy formalism is no longer valid \cite{popov70}.
 Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.
 
-Performing the Fourier transform over the confined two-dimensional space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
+Performing the Fourier transform over the confined 2D space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
 \begin{equation} \label{eq_9}
@@
 \end{equation}
-Here we used new parameters
-\begin{equation} \label{eq_11}
+Here we have introduced new parameters
+\begin{equation} \label{eq_11a}
   b =
-  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad \text{and} \quad
+  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
+\end{equation}
+and
+\begin{equation} \label{eq_11b}
   d =
@@
 \end{equation}
-For a detailed derivation, please refer to Appendix \ref{appendix_b}. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space
+For a detailed derivation, refer to Appendix \ref{appendix_b}. Using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space as
 \begin{equation} \label{eq_12}

### 2021-08-09 paper/v1.0/sections/4_inverse_scattering_time.tex
Corrections from Ravi

@@
 
-The Floquet-Fermi golden rule was proposed as an approach to analyze the transport properties of dressed quantum systems with impurities in Ref. \cite{wackerl20}.
+The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
 However, this theory has not been applied for a dressed quantum Hall system in the previous studies.
@@
 \end{equation}
-where $\varrho = \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of $N$-th Landau level.
-Detailed derivation is given in Appendix \ref{appendix_c}.
-We modeled the effect cause by impurities in the considering system by a single perturbation potential.
-Since random impurities in a disordered metal is a better approximation for experimental results, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
-Thus, the total scattering potential in 2DEG has been represented as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+where $\varrho = \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
+A more detailed derivation is given in Appendix \ref{appendix_c}.
+We modeled the effect caused by impurities in the considered system as a single perturbation potential.
+Since random impurities in a disordered metal offers a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
+Thus, the total scattering potential in the 2DEG has been represented as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
 Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
@@
 
-Next we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
-Since the disorder in the system can not alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
-Then we consider only the central (${l=l'=0}$) diagonal element of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
+Since the disorder in the system can not singificantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
+Subsequenty we consider only the central (${l=l'=0}$) diagonal element of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
 Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
@@
 \end{equation}
-and this leads to
+which simplifies to
 \begin{equation} \label{eq_15}
@@
 
-In addition, for a scenario of scattering take place inside the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
+In addition, for a scattering scenario taking place wihtin the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
 \begin{equation} \label{eq_16}
@@
 \end{equation}
-Then we write the central element of inverse scattering time matrix in more compact form
+Then we write the central element of inverse scattering time matrix in the more compact form
 \begin{equation} \label{eq_17}
@@
 where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
-To analyze the effects done by the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
+To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
 \begin{equation} \label{eq_18}
@@
 \end{equation}
-and this can evaluate with
+which can be evaluated with
 \begin{widetext}
@@
 Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
-To make a comparison, we have selected the experiment parameters to match with analysis done in Ref.~\cite{endo09}.
-In their study, they have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20}.
+To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
+In that study, the authors have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20}.
 In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$.
 Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
-Here we observe that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
-When the dressing field's intensity increase, the energy broadening gets reduced and this adds modifications to the transport properties of the system.
+Here, we observe that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
+When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
 To analyze these adjustments in detail, we derive a analytical expression for the conductivity of a dressed quantum Hall system in the next section.

### 2021-08-09 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Corrections
Corrections from Ravi

@@
 A general theory for the conductivity of a dressed system with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}.
-Within this theory, the general $x$-directional longitudinal DC-limit conductivity has been discribed by
+This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
 \begin{equation} \label{eq_20}
@@
 Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity.
-In addition, $A$ is the area of the considering two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
+In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
 \begin{equation} \label{eq_21}
@@
 \end{equation}
-Here, $ \varepsilon_N$ are quasienergies of all considering Floquet states, and $tr[\cdot]$ is the trace of the considering operator.
+Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr[\cdot]$ is the trace of the considering operator.
 
@@
 Thus, the $x$-directional longitudinal conductivity given in
-Eq.~(\ref{eq_20}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$
+Eq.~(\ref{eq_20}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$ as
 \begin{widetext}
@@
 We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}.
-Thus, we evaluate the matrix element of the difference between retarded and advanced Green's functions as
+Thus, we evaluate the matrix elements of the difference between retarded and advanced Green's functions as
 \begin{equation} \label{eq_24}
@@
 Applying the matrix elements of the electric current operator in Landau levels and
-expressions form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain
+expressions from Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain
 \begin{equation} \label{eq_26}
@@
 \end{equation}
-Since the inverse scattering time matrix being equal to the diagonalized contrast of the retarded and advanced self-energy, and on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20}, we can identify the following property
+The inverse scattering time matrix is equal to the diagonalized contrast of the retarded and advanced self-energy \cite{wackerl20,wackerlthesis20}.
+In addition, on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20}.
+Subsequenty, we can identify the following property
 \begin{equation} \label{eq_28}
@@
 Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\tilde{{\Gamma}}(\varepsilon_n,k_x)$ terms and get the sum over all available momentum space in $x$ direction.
-However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify that
+However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considered system, we can identify that
 \begin{equation} \label{eq_30}
@@
 where $k_B$ is theBoltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Considering the above distribution with extremely low temperature conditions, we use thee following approximation
+Considering the above distribution for extremely low temperature conditions, we can use the following approximation
 \begin{equation} \label{eq_32}
-  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F),
+  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
 \end{equation}
-and by letting $\Pi = \varepsilon_F$, the derived expression in \ref{eq_29} leads to
+Moreover, let $\Pi = \varepsilon_F$ and the derived expression in \ref{eq_29} leads to
 \begin{equation} \label{eq_33}

### 2021-08-09 paper/v1.0/sections/6_manipulate_conductivity.tex
Corrections from Ravi

@@
 
-To identify the characteristics of the longitudinal conductivity of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
+To identify the longtitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
 Here we derive a normalized $x$-directional conductivity of dressed quantum Hall system using the natural conductivity of the least Landau level
@@
 
-We use this expression to illustrate the changes that can be done to the longitudinal conductivity of 2DEG under stationary magnetic field using an external dressing field.
-As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considering system.
-For a given dressing field intensity, the longitudinal conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values.
-In quantum Hall systems, electrons are restricted to bear only the Landau level energies.
-Thus, the conductivity gets very low values when the Fermi level is not aligned with any of the Landau level energy values.
-In contrast, on each Landau level, the conductivity achieve excessive values compared to other areas.
+As illustrated in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considering system.
+For a given dressing field intensity, the longitudinal conductivity vary with  the Fermi level of the system showing sharp peaks at each Landau energy level.
+In quantum Hall systems, electrons are restricted to bear only the Landau energies.
+Thus, the conductivity reduces significantly when the Fermi level is not aligned with any of the Landau levels.
+In contrast, near each Landau level, the conductivity achieve excessive values compared to other areas.
 Moreover, as illustrates in Fig.~\ref{fig_5} the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.
@@
 
-On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field shrink the conductivity regions near Landau levels.
+On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpen the conductivity peaks.
 When we increase the intensity level of the dressing field, the conductivity regions get more weaken as illustrate in the \ref{fig_6}.
 However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
-This demonstrates that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
+This demonstrates our ability to tune the width of the conductivity regions in these quantum Hall systems with the help of a dressing field.
 
-These characteristics are aligned with the results demonstrated by Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be changed with the applied gate voltage of the material this can be utilized as a 2D switch for nanoscale optoelectronics applications.
-Controlling  the external dressing field's intensity, we are able to fine-tune this switching mechanism for an optimized performance.
-Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
+As the authors remarked in that work, since the Fermi level of the system can be changed with the applied gate voltage of the material this can be utilized as a 2D switch for nanoscale optoelectronics applications.
+Controlling  the external dressing field's intensity, allows us to fine-tune this switching mechanism for an optimized performance.
+However, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
 This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
-The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed Landau levels representation \cite{endo09}.
-In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the result depicted in Ref.
+The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed data for Landau levels \cite{endo09}.
+In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the results depicted in Ref.
 \cite{endo09}.
@@
 However, they have not considered the tunability that can be achieved with a dressing field.
-In this analysis, we account both of the magnetic and dressing field effects that can be applied to the transport properties of 2DEG, and we have presented a more generalized theory.
-As a concluding remark, in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more experimental fitting and generalized mathematical model for the charge transport properties of quantum Hall systems.
+In this analysis, we account both of the magnetic and dressing field effects that can affect the transport properties of 2DEG, leading to a more generalized theory.
+Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.

### 2021-08-09 paper/v1.0/sections/7_conclusions.tex
Corrections from Ravi

@@
-In this analysis, we introduced a generalized mathematical model for charge transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light.
-Under the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization.
+In this paper, we introduced a generalized mathematical model for prediciting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light.
+Under the uniform magnetic field, the charged particles can only settle in discrete energy values which leads to the Landau quantization.
 We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method.
@@
 Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
-We found that the graphical illustrations that we obtained from these numerical calculatiuons are capable of producing the same behavior as the experimental  result found in undressed quantum Hall systems.
+We found that the graphical illustrations that we obtained from these numerical calculatiuons are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
 Furthermore, we identified that by increasing the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed.
-Despite, this behavior has been identified in previous works, their results are not coinciding with the more accurate description of conductivity components in undressed quantum Hall systems.
+Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.
 However, our generalized analysis on conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.
@@
 Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adopted to extend the models that were used to describe the transport characteristics in quantum Hall systems.
-Due to owing the ability to control the conductivity regions, high intensity external illumination can be used as a trigger for two-dimensional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices.
-Finally, we identified that our findings of this paper can be used towards understanding nanoscale quantum devices, enhancing their performance, and inventing novel appliances.
+Owing the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices.
+As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D opto-electronic nano transistors, enhancing their performance, and inventing novel appliances.

### 2021-08-09 paper/v1.0/sections/2_schrodinger_problem.tex
Corrections appendix A

@@
   e^{-\kappa^2 y^2/2}
-  \mathcal{H}_n \qty(\kappa y) \quad \text{with}
-  \quad
-  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
+  \mathcal{H}_n \qty(\kappa y),
 \end{equation}
-with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\omega_0 = eB/m_e$ being the cyclotron frequency and $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial.
+with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
 The path shift of the driven classical oscillator $\zeta(t)$ is given by

### 2021-08-09 paper/v1.0/sections/6_manipulate_conductivity.tex
Corrections appendix A

@@
 
-As illustrated in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considering system.
+As illustrated in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
 For a given dressing field intensity, the longitudinal conductivity vary with  the Fermi level of the system showing sharp peaks at each Landau energy level.

### 2021-08-09 paper/v1.0/sections/appendix_a.tex
Corrections for abstract and introduction
Corrections appendix A

@@
-The deriving process of solutions for time dependent Schrödinger equation with the Hamiltonian of our system (Eq.
-\ref{eq_1}) quite similar to that followed in Refs.
+The derivation of the solutions for the time dependent Schrödinger equation with our system's Hamiltonian (Eq.
+\ref{eq_1}) is quite similar to that followed in Refs.
 \cite{husimi53,dini16}.
-We start with expanding the Hamiltonian for two-dimentional case
+We start with expanding the Hamiltonian for two-dimensional case
 \begin{equation} \label{eq_a1}
@@
     \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
-  \right],
+  \right].
 \end{equation}
-and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both operators share same (simultaneous) eigenfunctions
-$\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = 2\pi \hbar m/L_x~,~ m \in \mathbb{Z}$.
-Therefore, we re-arrange the Hamiltonian using definition of canonical momentum in $y$-direction to derive
+Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
+${L_x}^{-1/2}\exp(\frac{ip_x x}{\hbar})$ where $p_x = 2\pi \hbar m/L_x~$ with $ m \in \mathbb{Z}$.
+Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
 \begin{equation} \label{eq_a2}
@@
 \end{equation}
-We now define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 \equiv {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 \equiv {eB}/{m_e}$.
+Subsequenty we define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 = {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 = {eB}/{m_e}$.
 This leads to a new arrangement of the Hamiltonian
@@
 \end{equation}
-where we used a variable substitution $\tilde{y} = (y - y_0)$. Now we assume that the wave function solutions for the time-dependent Schrödinger equation of considering quantum system
+where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
 \begin{equation} \label{eq_a4}
@@
 \end{equation}
-can present by the following form
+can be presented by the following form
 \begin{equation} \label{eq_a5}
@@
 \end{equation}
-where $\vartheta(\tilde{y},t)$ is a function that satisfy the following property
+where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
 \begin{equation} \label{eq_a6}
@@
 \end{equation}
-If we turn off the strong dressing field ($E=0$), this equation leads to simple harmonic oscillator Hamiltonian
+If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
 \begin{equation} \label{eq_a7}
@@
 \end{equation}
-It is important to notice that we can identify the $S(t) \equiv eE\sin(\omega t)$ part as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
+Thus, we can identify $S(t) \equiv eE\sin(\omega t)$ term as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
 \begin{equation} \label{eq_a8}
@@
 
-This system can be exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53} as follows.
-We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform following unitary transformation
+This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}.
+We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
 \begin{equation} \label{eq_a9}
-    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t),
+    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
 \end{equation}
-and this yields
+This leads to
 \begin{equation} \label{eq_a10}
@@
 \end{equation}
-Then we can restrict our $\zeta(t)$ function such that
+Subsequenty, we can restrict $\zeta(t)$ function such that
 \begin{equation} \label{eq_a11}
@@
 \end{equation}
-and that leads to
+and that simply our previous expression as
 \begin{equation} \label{eq_a12}
@@
         - L(\zeta,\dot{\zeta},t)
-    \bigg]\varphi(y',t),
+    \bigg]\varphi(y',t).
   \end{aligned}
 \end{equation}
-where
+Here
 \begin{equation} \label{eq_a13}
@@
 \end{equation}
-This is the well known Schrödinger equation of the quantum harmonic oscillator.
-This allows us to identify with the well known eigenfunctions \cite{griffiths18,shankar94}
+This is the well-known Schrödinger equation of the quantum harmonic oscillator.
+This allows us to identify the well known eigenfunctions \cite{griffiths18,shankar94}
 \begin{equation} \label{eq_a16}
@@
   e^{-\kappa^2 y^2/2}
-  \mathcal{H}_n \qty(\kappa y) \quad \text{with}
-  \quad
-  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
+  \mathcal{H}_n \qty(\kappa y),
 \end{equation}
-which are propositional to the Hermite polynomials $\mathcal{H}_n$, with eigenvalues
+with eigenvalues
 \begin{equation} \label{eq_a17}
   \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
-  ~,~
+  ~\text{for}~
   n \in \mathbb{Z}^{+}_0.
 \end{equation}
-Therefore, we can identify the solutions of Eq.~(\ref{eq_a8}) as
+Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
+Thus, we can identify the solutions for Eq.~(\ref{eq_a8}) as
 \begin{equation} \label{eq_a18}
@@
 \end{equation}
-Since set $\{\chi_n(x)\}$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of solutions derived in Eq.~(\ref{eq_a18}).
+Since $\chi_n(x)$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of the solutions derived in Eq.~(\ref{eq_a18}).
 
-Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq_a11}):
+Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we derive the solution for Eq.~(\ref{eq_a11}) as
 \begin{equation} \label{eq_a19}
@@
 \end{equation}
-Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we can obtain the set of wave functions with two different quantum number ($n$,$m$) that satisfy the time dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
+Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
 \begin{equation} \label{eq_a20}

### 2021-08-09 paper/v1.0/sections/appendix_b.tex
Correction appendix B

@@
 
-First define the time integral of Lagrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a $T=2\pi/\omega$ period as
+First we define the time integral of the Lagrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a period $T=2\pi/\omega$ as
 \begin{equation} \label{eq_b1}
-  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T dt' \; L(\zeta,\dot{\zeta},t'),
+  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T dt' \; L(\zeta,\dot{\zeta},t').
 \end{equation}
-and after performing the integral using Eq.~(\ref{eq_4}), we can obtain more simplified result:
+Additionally, performing this integral, we can obtain a more simplified result
 \begin{equation} \label{eq_b2}
@@
 \end{equation}
-Next define another parameter
+Next, we define another parameter
 \begin{equation} \label{eq_b3}
@@
 \end{equation}
-and after simplifying, this leads to
+and after simplifying, we can identify
 \begin{equation} \label{eq_b4}
@@
 \end{equation}
-which is a periodic function in time with $2\omega$ frequency.
-Now using these  parameters we can factorize the wave function Eq.~(\ref{eq_2}) as linearly time dependent part and periodic time dependent part as follows
+which is a periodic function in time. Using these parameters, we can factorize the wave function given in Eq.~(\ref{eq_2}) as linearly time dependent part and periodic time dependent part as follows
 \begin{equation} \label{eq_b5}
@@
      + \int_0^{t}dt'L(\zeta,\dot{\zeta},t') - \Delta_{\varepsilon} t  \bigg]
-     \bigg),
+     \bigg).
   \end{aligned}
 \end{equation}
-and this leads to separate linear time dependent phase component as the quasienergies
+This leads to separate the linear time dependent phase component as the quasienergies
 \begin{equation} \label{eq_b6}
@@
 
-To write the Floquet modes in momentum space, we perform continuous Fourier transform over the considering confined space $A=L_xL_y$ on the Floquet modes given in Eq.~(\ref{eq_7}):
+We perform continuous Fourier transform over the considering confined space $A=L_xL_y$ on the Floquet modes given in Eq.~(\ref{eq_7}) to realize the Floquet modes in momentum space
 \begin{equation} \label{eq_b8}
@@
      \exp(-ik_x x)
-     \exp( \frac{i p_x }{\hbar}x ),
+     \exp( \frac{i p_x }{\hbar}x ).
   \end{aligned}
 \end{equation}
-where
-\begin{equation} \label{eq_b9}
-  \mu(t) = \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0
-  \quad,\quad
+Here we used new two parameters
+\begin{equation} \label{eq_b9a}
+  \mu(t) = \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0,
+\end{equation}
+and
+\begin{equation} \label{eq_b9b}
   \gamma(t) =
@@
 \end{equation}
-Next using the Fourier transform identity \cite{bruus04}
+Subsequenty, using the Fourier transform identity \cite{bruus04}
 \begin{equation} \label{eq_b10}
@@
     m_e \dot{\zeta}(t) \zeta(t) - \xi
-    ]).
+    ]),
   \end{aligned}
 \end{equation}
-Here we defined $\Phi_{n,m}(k_y,t)$ as
+where we can define $\Phi_{n,m}(k_y,t)$ as
 \begin{equation} \label{eq_b12}
@@
 \end{equation}
-Substituting $  {k'_y} = k_y -\gamma(t)$ and $y' = y -\mu(t)$ and assuming that size of the 2DEG sample in $y$-direction is considerably large ($L_y \rightarrow \infty$), we can obtain
+Substituting ${k'_y} = k_y -\gamma(t)$ with $y' = y -\mu(t)$, and assuming that the size of the considered 2DEG sample in $y$-direction is considerably large ($L_y \rightarrow \infty$), we can obtain
 \begin{equation} \label{eq_b13}
@@
 \end{equation}
-We can identify that the integral represents the Fourier transform of $\{\chi_n\}$ functions and using the symmetric conditions \cite{celeghini21} for the Fourier transform of Gauss-Hermite functions $\theta_n(x)$:
+Moreover, we can identify that the above integral represents the Fourier transform of $\{\chi_n\}$ functions.
+In addition, using the symmetric conditions of the Fourier transform for Gauss-Hermite functions $\theta_n(x)$ \cite{celeghini21}
 \begin{equation} \label{eq_b14}
@@
 \end{equation}
-Eq.~(\ref{eq_b13}) can be simplified as
+we can simply the Eq.~(\ref{eq_b13}) as
 \begin{equation} \label{eq_b15}
@@
 \end{equation}
-Substitute Eq.~(\ref{eq_b15}) back in Eq.~(\ref{eq_b11}) and this leads to
+Finally, substitute Eq.~(\ref{eq_b15}) back into Eq.~(\ref{eq_b11}) and this leads to
 \begin{equation} \label{eq_b17}
@@
   b \equiv
-  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad
+  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
+\end{equation}
+and
+\begin{equation} \label{eq_b18}
   d \equiv
- \frac{eE}{m_e(\omega_0^2 - \omega^2)},
+ \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
 \end{equation}
-and it is necessary to notice that $k_x$ is quantized with $k_x = 2\pi m/L_x ~,~ m \in \mathbb{Z}$.
+It is necessary to notice that $k_x$ is quantized with $k_x = 2\pi m/L_x ~,~ m \in \mathbb{Z}$.

### 2021-08-10 paper/v1.0/sections/appendix_c.tex
Corrections for abstract and introduction
Corrections appendix

@@
-The Floquet Fermi golden rule derivation for our quantum Hall system with the help of $t-t'$ formalism is given here in detail. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
+The Floquet-Fermi golden rule for our dressed quantum Hall system is derived  using the $t$-$t'$ formalism. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
 \begin{equation} \label{eq_c1}
@@
 \end{equation}
-are derived by separating the aperiodic and periodic components of Eq.~(\ref{eq_12}). Additionally, these fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
+are derived by separating the aperiodic and periodic components of the Floquet states given in Eq.~(\ref{eq_12}).
+Additionally, these states fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
 \begin{equation} \label{eq_c2}
@@
 \begin{equation} \label{eq_c3}
-  H_F(t') \equiv
+  H_F(t') =
   H_e(t') - i\hbar \pdv{t'}.
 \end{equation}
-Next we can identify the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation
+Next, we can identify the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation as
 \begin{equation} \label{eq_c4}
-  U_F(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\qty[t-t_0]),
+  U_F(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\qty[t-t_0]).
 \end{equation}
-and the advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time ordering operators \cite{wackerl20}.
+The advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time ordering operators \cite{wackerl20}.
 
-For our scenario, consider a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, then the $t$-$t'$-Schrödinger equation becomes
+For our scenario, we take into account a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, and the $t$-$t'$-Schrödinger equation becomes
 \begin{equation} \label{eq_c5}
   i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')} =
-  \qty[H_F(t') + V(\vb{r})]\ket{\Psi_{n,m}(t,t')},
+  \qty[H_F(t') + V(\vb{r})]\ket{\Psi_{n,m}(t,t')}.
 \end{equation}
-and this introduce a new wave function solution $\Psi_{n,m}$ for the system with the given total perturbation.
-If $t\leq t_0$, both solutions of the Schrödinger equations (Eq.~(\ref{eq_c2}) and Eq.~(\ref{eq_c5})) coincide
+This introduces a new wave function solution $\ket{\Psi_{n,m}}$ for a system with a given perturbation. If $t\leq t_0$, both of the solutions for Eq.~(\ref{eq_c2}) and Eq.~(\ref{eq_c5}) coincide
 \begin{equation} \label{eq_c6}
@@
 \end{equation}
-Now move into the interaction picture representation \cite{bruus04,mahan00} of the $t$-$t'$-Floquet state
+Next, our analysis can move into the interaction picture representation \cite{bruus04,mahan00} and in the interaction picture, the $t$-$t'$-Floquet state can be identified as
 \begin{equation} \label{eq_c7}
   \ket{\Psi_{n,m}(t,t')}_I = U_0^{\dagger}(t,t_0;t')
-  \ket{\Psi_{n,m}(t,t')},
+  \ket{\Psi_{n,m}(t,t')}.
 \end{equation}
-and due to time independence, the perturbation in the interaction picture has the same form as Schrödinger picture representation
+Due to time independence, the perturbation in the interaction picture has the same form as Schrödinger picture representation
 \begin{equation} \label{eq_c8}
@@
 \end{equation}
-This drive us to the $t$-$t'$-Schrödinger equation representation in the interaction picture
+This leads us to the $t$-$t'$-Schrödinger equation in the interaction picture representation
 \begin{equation} \label{eq_c9}
@@
 \end{equation}
-with the recursive solution \cite{bruus04,mahan00}
+with the recursive solutions \cite{bruus04,mahan00}
 \begin{equation} \label{eq_c10}
@@
 
-In addition, since our Floquet states create a basis, we can represent any solution using these Floquet states:
+Since our $t$-$t'$-Floquet states create a basis, we can represent solutions for the $t$-$t'$-Schrödinger equation given in Eq.~(\ref{eq_c5}) using our known $t$-$t'$-Floquet states
 \begin{equation} \label{eq_c12}
   \ket{\Psi_{\alpha}(t,t')} = \sum_{\beta} a_{\alpha,\beta}(t,t')
-  \ket{\psi_{\beta}(t,t')},
+  \ket{\psi_{\beta}(t,t')}.
 \end{equation}
-where we used a single notation to represent two quantum numbers; $\alpha \equiv (n_{\alpha},m_{\alpha})$ and $\beta \equiv (n_{\beta},m_{\beta})$.
+Here, we used a single term notation to represent two quantum numbers; $\alpha \equiv (n_{\alpha},m_{\alpha})$ and $\beta \equiv (n_{\beta},m_{\beta})$.
 Then we can identify the \textit{scattering amplitude} as $a_{\alpha,\beta}(t,t') =
-\braket{\psi_{\beta}(t,t')}{\Psi_{\alpha}(t,t')}$ and this can evaluate with
+\braket{\psi_{\beta}(t,t')}{\Psi_{\alpha}(t,t')}$ and this can be evaluated with
 \begin{equation} \label{eq_c13}
@@
 
-Now consider a scattering phenomenon from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ that occupied with a constant quansienergy $\varepsilon$ (Fig.~\ref{fig_2}):
+Next, we consider a scattering phenomenon when a electron scatters from a known $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with a constant quansienergy $\varepsilon$ as follows
 \begin{equation} \label{eq_c15}
@@
   \includegraphics[scale=1.0]{figures/fig_2.pdf}
-  \caption{Scattering from $\ket{\psi_{\beta}(t,t')}$ to constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to scattering potential created by impurities.}
+  \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
   \label{fig_2}
 \end{figure}
-It is important to remember that a state of this considering system can be represented by two independent quantum numbers: $n$ represents the landau level and $m$ represents the quantized momentum in $x$-direction.
+This scenario is illustared in Fig.~\ref{fig_2}.
 The scattering amplitude for this scattering scenario can be calculated using the equation derived in Eq.~(\ref{eq_c14})
@@
     \bra{\phi_{\beta}(t')}
-    V(\vb{r}) \ket{\phi_{\alpha}(t')},
+    V(\vb{r}) \ket{\phi_{\alpha}(t')}.
   \end{aligned}
 \end{equation}
-and assuming for a long time $t \rightarrow \infty$, we can turn this integral into a delta distribution
+By assuming for a long time $t \rightarrow \infty$, we can turn this integral into a delta distribution
 \begin{equation} \label{eq_c17}
@@
 \end{equation}
-where $Q \equiv \bra{\phi_{\beta}(t')}
-V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using completeness properties we can re-write this as
+where $Q = \bra{\phi_{\beta}(t')}
+V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using the completeness properties we can re-write this as
 \begin{equation} \label{eq_c18}
@@
     \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}
-    \braket{\vb{k}}{\phi_{\alpha}(t')},
+    \braket{\vb{k}}{\phi_{\alpha}(t')}.
 \end{equation}
-and separating $x$ and $y$ directional momentum we can derive (we already assumed that $L_y \rightarrow \infty$)
+Moreover, separating $x$-directional and $y$-directional momentum components, this can be simplified as
 \begin{equation} \label{eq_c19}
@@
 
-Since we are presenting the the perturbation potential $V(\vb{r})$ by using a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
-Then scattering potential $V(\vb{r})$ can be identified as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$:
+Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
+Then scattering potential $V(\vb{r})$ can be identified as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
 \begin{equation} \label{eq_c20}
@@
 \end{equation}
-Next we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
+Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
 This model is characterized by \cite{akkermans10}
@@
 \end{subequations}
-where $\expval{\cdot}_{imp}$ denoted the average over realizations of the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
-In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
-Since this study considers the case where the wavelength of radiation or scattering electrons is much greater than $r_c$, it is a good approximation to make two-point correlation function to be
+where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
+In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
+Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
 \begin{equation} \label{eq_c22}
@@
 \end{equation}
-where $\Upsilon_{imp}$ is strength of the delta potential and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}.
-Then we can approximately model the total scattering potential as
+where $\Upsilon_{imp}^2$ is a conatant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
 \begin{equation} \label{eq_c23}
@@
 \end{equation}
-Then we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
+Here we can identify the $\Upsilon_{imp}$ as the strength of the delta potential.
+Furthermore, we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
 \begin{subequations} \label{eq_c24}
@@
  \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \\
- & \times \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
+ & \quad\times \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \bigg] \label{eq_c24b} \\
@@
 \end{subequations}
-Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs and assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
+Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs.
+Additionally, assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
 \begin{subequations} \label{eq_c25}
@@
     & =
-    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y), \label{eq_c25b}
+    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y). \label{eq_c25b}
   \end{align}
 \end{subequations}
-where
+In the above equation we introduced
 \begin{equation} \label{eq_c26}
@@
 \end{equation}
-is a constant value for every $i$ impurity and $\eta_{imp}$ is number of impurities in a unit area. It is important to notice that $\braket{x}{k_x} = e^{-ik_xx}$.
+which is a constant value for every $i$ impurity. Moreover, $\eta_{imp}$ is the number of impurities in a unit area. It is important to note that $\braket{x}{k_x} = e^{-ik_xx}$.
 
-Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25b}) on Eq.~(\ref{eq_c19}), we obtain (with changing variable $t' \rightarrow t$)
+Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25b}) on Eq.~(\ref{eq_c19}), we obtain
 \begin{equation} \label{eq_c27}
@@
     \\
-    & \times
+    & \quad\times
     \sqrt{L_x}
@@
     )
-    \tilde{\chi}_{n_{\alpha}}\qty(k_y -b\cos(\omega t)),
+    \tilde{\chi}_{n_{\alpha}}\qty(k_y -b\cos(\omega t)).
   \end{aligned}
 \end{equation}
-and this can simplify as
+Here we have changed the time variable $t' \rightarrow t$ only for the simplicity of notation. This can be simplified as
 \begin{equation} \label{eq_c28}
@@
 To avoid the energy exchange from the dressing field and electrons in Landau levels, the applied radiation must be a purely dressing field.
-Therefore, in this study we assume that the dressing field only can renormalize the the probability of electron scattering inside a same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
+Therefore, in this study we assume that the dressing field can only renormalize the the probability of electron scattering inside a same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
 This transform the Eq.~(\ref{eq_c29}) to
@@
 \end{equation}
-Using Fourier transform of Gauss-Hermite functions \cite{celeghini21} and convolution theorem \cite{arfken85,bracewell78} we can derive
+Using the Fourier transform of Gauss-Hermite functions \cite{celeghini21} and the convolution theorem \cite{arfken85,bracewell78} we obtain
 \begin{equation} \label{eq_c31}
@@
 \end{equation}
-Therefore, finally the scattering amplitude derived in Eq.~(\ref{eq_c17}) can be evaluated for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as
+Finally, the scattering amplitude derived in Eq.~(\ref{eq_c17}) can be evaluated for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as
 \begin{equation} \label{eq_c32}
@@
 \end{equation}
-where $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and we can re-write the Eq.~(\ref{eq_c32}) as follows
+where $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, we can re-write the Eq.~(\ref{eq_c32}) as follows
 \begin{equation} \label{eq_c35}
@@
     {\chi}_{N}\qty(y)
-    {\chi}_{N}\qty(y_0 - {y'}_0 - y) e^{-il\omega t},
+    {\chi}_{N}\qty(y_0 - {y'}_0 - y) e^{-il\omega t}.
   \end{aligned}
 \end{equation}
-and then the Fourier series component can be identified as
+Thus, we can identify the Fourier series component of the scattering amplitude as
 \begin{equation} \label{eq_c36}
@@
 \end{equation}
-Now define \textit{transition probability matrix} as
+Furthermore, we define \textit{transition probability matrix} as
 \begin{equation} \label{eq_c37}
@@
 \end{equation}
-Then describing the square of the delta distribution using following interpretation \cite{dini16,kibis14}
+Then describing the square of the delta distribution using the following interpretation \cite{dini16,kibis14}
 \begin{equation} \label{eq_c39}
@@
 \end{equation}
-and executing the time derivation operation on each matrix element we receive the \textit{transition amplitude matrix} elements:
+and executing the time derivation operation on each matrix element of transition probability matrix, we receive the \textit{transition amplitude matrix} elements
 \begin{equation} \label{eq_40}
@@
 
-An impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2}_{imp} = V_{imp}$.
-Furthermore, the inverse scattering time matrix can be identified as the sum of all available momentum over the impurity averaged transition probability matrix element \cite{wackerl20,wackerlthesis20}
+Additionally, the inverse scattering time matrix can be identified as the sum of all available momentum over the impurity averaged transition probability matrix element \cite{wackerl20,wackerlthesis20}
 \begin{equation} \label{eq_41}
@@
     \frac{1}{L_x} \sum_{{k'}_x}
-    \expval**{\Gamma_{\alpha\beta}^{ll'}({k'}_x,k_x)}_{imp},
+    \expval**{\Gamma_{\alpha\beta}^{ll'}({k'}_x,k_x)}_{imp}.
 \end{equation}
-and applying the 1-dimentional momentum continuum limit $\sum_{{k'}_x} \longrightarrow {L_x}/{2\pi}\int d {k'}_x$ and this leads to
+Next, applying the 1-dimensional momentum continuum limit $\sum_{{k'}_x} \longrightarrow {L_x}/{2\pi}\int d {k'}_x$, we can obtain
 \begin{equation} \label{eq_42}
@@
     J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x]) \\
-    & \times
+    & \quad\times
     \qty|
@@
 \end{equation}
-Using substitution $k'_x = k_1$ and $y = {\hbar{k_2}}/{eB}$ finally we can derive our expression for the inverse scattering time matrix for $N$-th Landau
+Here an impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2}_{imp} = V_{imp}$.
+Finally, using substitutions $k'_x = k_1$ and $y = {\hbar{k_2}}/{eB}$, we can derive our expression for the inverse scattering time matrix for $N$-th Landau
 level as follows
@@
     \delta(\varepsilon - \varepsilon_{N})\\
-    & \times
+    & \quad\times
     \int_{-\infty}^{\infty} d k_1
@@
     J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
-    & \times
+    & \quad\times
     \qty|

### 2021-08-10 paper/v1.0/sections/appendix_d.tex
Corrections appendix

@@
-In this section we are hoping to derive the current density operator for $N$-th Landau level.
-We already found the exact solution for our time dependent Hamiltonian Eq.~(\ref{eq_1}) and we identified them as Floquet states in Eq.~(\ref{eq_12}).
-The Floquet modes derived in Eq.~(\ref{eq_9}) can be represented as states using quantum number for the simplicity of notation as follows
+In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system.
+We already found the exact solution for our time dependent Hamiltonian give in Eq.~(\ref{eq_1}) and we identified them as the Floquet states in Eq.~(\ref{eq_12}).
+The Floquet modes derived in Eq.~(\ref{eq_9}) can be represented as quantum states using their corresponding quantum numbers for the simplicity of notation as follows
 \begin{equation} \label{eq_d1}
-  \ket{\phi_{n,m}} \equiv \ket{n,k_x}.
+  \ket{\phi_{n,m}} = \ket{n,k_x}.
 \end{equation}
-Using above complete set of eigenstates of Floquet Hamiltonian Eq.~(\ref{eq_c3}) \cite{wackerl20,holthaus15,grifoni98} we can represent the single particle current operator's matrix element as
+Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
 \begin{equation} \label{eq_d2}
-  \qty(\vb{j})_{nm,n'm'} \equiv \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x},
+  \qty(\vb{j})_{nm,n'm'} \equiv \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
 \end{equation}
-and the particle current operator for our system \cite{mahan00,bruus04} can be identified as
+Thus, the particle current operator for our system \cite{mahan00,bruus04} can be identified as
 \begin{equation} \label{eq_d3}
@@
 \end{equation}
-where $\tilde{m}$ is mass of the considering particle.
+where $\tilde{m}$ is the mass of the considering particle.
 
-First consider the conductivity in $x$-direction, and we can identify that $x$-directional current operator as
+First, we consider the $x$-directional current operator component, and we can identify that the $x$-directional current operator as
 \begin{equation} \label{eq_d4}
@@
 \end{equation}
-Now calculate the matrix elements of $x$-directional current operator in Floquet mode basis
+Next, we calculate the matrix elements of $x$-directional current operator in Floquet mode basis
 \begin{equation} \label{eq_d5}
   \qty({j}_x)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{1}{\tilde{m}} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x}.
+  \mel{n,k_x}{\;\frac{1}{\tilde{m}} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x},
 \end{equation}
-Then evaluate these using Floquet modes derived in Eq.~(\ref{eq_7}) and obtain
+and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq_7}) as follows
 \begin{equation} \label{eq_d6}
@@
 \end{equation}
-Then let $(y - y_0 - \zeta(t)) = \bar{y}$ and we can derive
+Let $(y - y_0 - \zeta(t)) = \bar{y}$ and we can obtain
 \begin{equation} \label{eq_d7}
@@
 \end{equation}
-Using following integral identities of Floquet modes which are made up with  Gauss-Hermite functions \cite{vedenyapin11,szego59}
+Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
 \begin{subequations} \label{eq_d8}
@@
 \end{subequations}
-we simplify the matrix elements of $x$-directional current operator to
+we simplify the matrix elements of $x$-directional current operator to obtain
 \begin{equation} \label{eq_d9}
@@
 
-Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we evaluate the $s=0$ component of the Fourier series with
+Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we identify the $0$-th component of the Fourier series as
 \begin{equation} \label{eq_d10}
@@
 \end{equation}
-For electric current operator we can apply the electron's charge and effective mass and this leads to
+For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
 \begin{equation} \label{eq_d11}
@@
 
-Next we consider the transverse conductivity in $y$-direction, and we can identify that $y$-directional current operator as
+Moreover, we can identify the $y$-directional current operator component as
 \begin{equation} \label{eq_d12}
@@
 \end{equation}
-Then the matrix elements of $y$-directional current operator in Floquet mode basis are derived as
+Using this operator, the matrix elements of $y$-directional current operator in Floquet mode basis can be represented as
 \begin{equation} \label{eq_d13}
@@
 \end{equation}
-After following the same steps done for $x$-directional current operator, we can derive the $s=0$ component of matrix elements for $y$-directional electric current operator as
+After following the same steps done for the $x$-directional current operator, we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
 \begin{equation} \label{eq_d14}

### 2021-08-10 paper/v1.0/sections/1_introduction.tex
Add new bib item

@@
 Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century.
-Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
+Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
 quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.

### 2021-08-16 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Corrections appendix
Corrections statrt

@@
   \begin{aligned}
-    {\sigma}^{xx} &=
+    {\sigma}^{xx} =&
     \frac{-1}{4\pi\hbar A}
@@
 \end{equation}
-We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}.
+We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  = \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}.
 Thus, we evaluate the matrix elements of the difference between retarded and advanced Green's functions as
@@
   \begin{aligned}
-    {\sigma}^{xx} & =
+    {\sigma}^{xx} =
     \frac{-1}{4\pi\hbar A}
-    \frac{e^4B^2}{{{m_e}^2}}
+    \frac{e^4B^2}{{{m_e}^2}} &
     \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
@@
 \end{widetext}
-with $\tilde{{\Gamma}}(\varepsilon_n,k_x) \equiv \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
+with $\tilde{{\Gamma}}(\varepsilon_n,k_x) = \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
 Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\tilde{{\Gamma}}(\varepsilon_n,k_x)$ terms and get the sum over all available momentum space in $x$ direction.
@@
 \end{equation}
-where $X_F \equiv ({\varepsilon_F}/{\hbar \omega_0} - {1}/{2})$
+where $X_F = ({\varepsilon_F}/{\hbar \omega_0} - {1}/{2})$
 and
-$\gamma_n \equiv {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
+$\gamma_n = {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
 Following the same steps as above derivation, we can derive the longitudinal conductivity in $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}

### 2021-08-16 paper/v2.0/abstract.tex
Add new version of the paper

--- 2021-08-02 paper/v1.0/abstract.tex
@@
-A generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high intensity electromagnetic field is presented.
+We present a generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high-intensity electromagnetic field.
 The new formulation, which applies to two-dimensional(2D) dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
@@
 To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure.
-Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects on charge transport in disordered quantum Hall systems.
+Moreover, the Floquet-Fermi golden rule is adopted to explore the impurity scattering effects on charge transport in disordered quantum Hall systems.
 We derive fully analytical expressions to describe longitudinal components in the conductivity tensor in dressed quantum Hall systems.
@@
 Our results align with well-established and experimentally
-verified theoretical descriptions for undressed systems while providing a more generalized analysis on the conductivity characterstics in quantum Hall systems.
-Thus, our model can be applied to accurately interpret the usage of external strong radiation as a tool in nanoscale quantum devices.
+verified theoretical descriptions for undressed systems while providing a more generalized analysis of the conductivity characteristics in quantum Hall systems.
+Thus, our model can be applied to accurately interpret the usage of  strong external radiation as a tool in nanoscale quantum devices.

### 2021-08-16 paper/v2.0/sections/1_introduction.tex
Add new version of the paper

--- 2021-08-10 paper/v1.0/sections/1_introduction.tex
@@
 Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity.
-At high intensities, the higher order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
+At high intensities, the higher-order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
 In these instances, a more accurate treatment needs to adopt.
@@
 In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula.
-This opened the path to explore and exploit the charge transport attributes of nanostructures under an intense dressing field.
+This opened the path to exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.
 
@@
 
-In contrast, more interesting phenomena can be observed by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
+In contrast, more exciting phenomena can be observed by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
 Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport.
@@
 In their study, they used the conductivity models from Refs.
-\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening agaist Fermi level for each Landau levels and provide less agreement with the empirical results.
+\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
 
@@
 The paper is organized as follows.
-In Sec.
-\ref{sec_schrodinger_problem}, we introduce our dressed quantum Hall system and the exact wave function solutions for the given configuration.
 Sec.
-\ref{sec_floquet_theory}, provides the Floquet theory interpretation of these wave functions.
+\ref{sec_schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration.
+Sec.
+\ref{sec_floquet_theory} provides the Floquet theory interpretation of these wave functions.
 We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec.
@@
 \ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
-The derived theoritical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}.
-In Sec. \ref{sec_conclusions}, we summarize our analysis and present our conlusions.
+The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}.
+In Sec. \ref{sec_conclusions}, we summarize our analysis and present our conclusions.

### 2021-08-16 paper/v2.0/sections/2_schrodinger_problem.tex
Add new version of the paper

--- 2021-08-09 paper/v1.0/sections/2_schrodinger_problem.tex
@@
 Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space.
-In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis.
+In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{T}$, which is pointed towards the $z$-axis.
 In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface.
-We specially select the frequency of the dressing field $\omega$ to be in the off-ersonant regime such that the field behaves as a purely dressing field.
-Furthermore, without limiting the generality we choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the linearly polarized dressing field (Fig.~\ref{fig_1}).
+We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field.
+Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field (Fig.~\ref{fig_1}).
 \begin{figure}[b]
@@
 \end{figure}
-Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field respectively.
+Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field, respectively.
 
@@
 These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}.
-Thus, our system can be represented with a time-dependent Hamiltonian
+Thus, we can represent our system with a time-dependent Hamiltonian
 \begin{equation} \label{eq_1}
@@
 \end{equation}
-where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{\text{T}}$.
+where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{T}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{T}$.
 The exact solutions for the time-dependent Schrödinger equation $i\hbar\; \text{d}\psi/\text{d}t = \hat{H}_e(t) \psi$ were already derived in Refs.
@@
     \chi_n\big(y - y_0 - \zeta(t)\big)\\
-    & \times
+    & \quad\times
     \text{exp}\bigg(
@@
     + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
-    &+
+    & \quad+
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
@@
 The center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
-Moreover, $\chi_n$ are well known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
+Moreover, $\chi_n$ are well-known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
 \begin{equation} \label{eq_3}

### 2021-08-16 paper/v2.0/sections/3_floquet_theory.tex
Add new version of the paper

--- 2021-08-09 paper/v1.0/sections/3_floquet_theory.tex
@@
 
-Symmetry conditions often gives useful insights into the behaviors of physical quantum systems.
-For instance, in the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in configuration space.
+Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
+For instance, in the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space.
 Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
-The Floquet-Drude conductivity theory was emplyoed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
+The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
 In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field.
@@
 First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}).
-By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, we present the quasienergies as
+By factorizing the wave function into a linearly time-dependent part and a periodic time-dependent part, we present the quasienergies as
 \begin{equation} \label{eq_6}
@@
 \end{equation}
+For a detailed derivation, refer to Appendix \ref{appendix_b}.
 It is important to note that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
@@
 \end{equation}
-For a detailed derivation, refer to Appendix \ref{appendix_b}. Using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space as
+Using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space as
 \begin{equation} \label{eq_12}

### 2021-08-16 paper/v2.0/sections/4_inverse_scattering_time.tex
Add new version of the paper

--- 2021-08-09 paper/v1.0/sections/4_inverse_scattering_time.tex
@@
     \delta(\varepsilon - \varepsilon_{N}) \\
-    & \times
+    & \quad\times
     \int_{-\infty}^{\infty} d k_1 \Bigg[
@@
 Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
-Moreover in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
+Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
 
 Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
-Since the disorder in the system can not singificantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
-Subsequenty we consider only the central (${l=l'=0}$) diagonal element of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
+Subsequently we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
 Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
@@
  \begin{aligned}
-   \Gamma^{00}_{N}& (\varepsilon,k_x) \\
+   &\Gamma^{00}_{N} (\varepsilon,k_x) \\
    & =
@@
    \delta(\varepsilon - \varepsilon_{N}) \\
-   & \times
+   & \quad\times
    \int_{-\infty}^{\infty} d k_1 \Bigg[
@@
    \\
-   & \times
+   & \quad\times
    \qty|
@@
 \includegraphics[scale=0.68]{figures/fig_3}
-\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
-In this calculation we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
+\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a  frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
 \end{figure}
@@
 \includegraphics[scale=0.68]{figures/fig_4}
-\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
-In this calculation we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
+\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
+In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
 \end{figure}
 
-In addition, for a scattering scenario taking place wihtin the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
+In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
 \begin{equation} \label{eq_16}
@@
 \begin{equation} \label{eq_18}
-    \Lambda_N(k_x) \equiv
+    \Lambda_N(k_x) =
     \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
@@
 To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
-In that study, the authors have assumed that effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\tilde{m}_e$ where $\tilde{m}_e$ is mass of the electron \cite{endo09,winkler03,wackerl20}.
+In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
 In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$.
@@
 When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
-To analyze these adjustments in detail, we derive a analytical expression for the conductivity of a dressed quantum Hall system in the next section.
+To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.

### 2021-08-16 paper/v2.0/sections/5_floquet_drude_conductivity.tex
Add new version of the paper

--- 2021-08-16 paper/v1.0/sections/5_floquet_drude_conductivity.tex
@@
 
-A general theory for the conductivity of a dressed system with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}.
+A general theory for the conductivity of a dressed system with the disorder was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}.
 This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
@@
 
-Next, we restrict our analysis into off-resonant regime $\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system.
+Next, we restrict our analysis into the off-resonant regime $\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system.
 Thus, the $x$-directional longitudinal conductivity given in
@@
 \end{equation}
-where $k_B$ is theBoltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Considering the above distribution for extremely low temperature conditions, we can use the following approximation
+where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
+Considering the above distribution for extremely low-temperature conditions, we can use the following approximation
 \begin{equation} \label{eq_32}
@@
 $\gamma_n = {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
-Following the same steps as above derivation, we can derive the longitudinal conductivity in $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
+Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
 \begin{equation} \label{eq_34}

### 2021-08-16 paper/v2.0/sections/6_manipulate_conductivity.tex
Add new version of the paper

% Section 06 - Manipulate Conductivity in Quantum Hall Systems

To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
Here we derive a normalized $x$-directional conductivity of dressed quantum Hall system using the natural conductivity of the least Landau level
\begin{equation} \label{eq_35}
  \begin{aligned}
    \tilde{\sigma}^{xx} =
    \sigma_{0} &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ],
  \end{aligned}
\end{equation}
with $\sigma^0 = e^2/\pi \hbar A$.

As illustrated in Fig.~\ref{fig_5} and \ref{fig_6}, we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
For a given dressing field intensity, the longitudinal conductivity varies with  the Fermi level of the system showing sharp peaks at each Landau energy level.
In quantum Hall systems, electrons are restricted to bear only the Landau energies. Thus, the conductivity reduces significantly when the Fermi level is not aligned with any of the Landau levels. In contrast, near each Landau level, the conductivity achieves excessive values compared to other areas. Moreover, as illustrates in Fig.~\ref{fig_5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.

\begin{figure}[t]
\includegraphics[scale=0.575]{figures/fig_5}
\caption{\label{fig_5} Normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a  frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$. In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
\end{figure}
\begin{figure}[t]
\includegraphics[scale=0.575]{figures/fig_6}
\caption{\label{fig_6} $3$rd Landau level’s normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
\end{figure}

On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpen the conductivity peaks.
When we increase the intensity level of the dressing field, the conductivity regions get more weaken as illustrated in the Fig.~\ref{fig_6}.
However, the peak value of the conductivity at each Landau level has the same value as the undressed system. This demonstrates our ability to tune the width of the conductivity regions in these quantum Hall systems with the help of a dressing field.

These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.  As the authors remarked in that publication, since the Fermi level of the system can be changed with the applied gate voltage of the material, this can be utilized as a 2D switch for nanoscale optoelectronics applications. Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
However, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and Fig.~\ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}. This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}. The semi-elliptical conductivity regions are  illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed data for Landau levels \cite{endo09}.
In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the results depicted in Ref. \cite{endo09}.
The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimentally observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
However, they have not considered the tunability that can be achieved with a dressing field. In this analysis, we account for both the magnetic and dressing field effects that can affect the transport properties of 2DEG, leading to a more generalized theory. Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.

### 2021-08-16 paper/v2.0/sections/7_conclusions.tex
Add new version of the paper

--- 2021-08-09 paper/v1.0/sections/7_conclusions.tex
@@
-In this paper, we introduced a generalized mathematical model for prediciting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light.
-Under the uniform magnetic field, the charged particles can only settle in discrete energy values which leads to the Landau quantization.
+In this paper, we introduced a generalized mathematical model for predicting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high-intensity light.
+Under the uniform magnetic field, the charged particles can only settle in discrete energy values, which leads to the Landau quantization.
 We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method.
@@
 Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
-We found that the graphical illustrations that we obtained from these numerical calculatiuons are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
+We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
 Furthermore, we identified that by increasing the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed.
 Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.
-However, our generalized analysis on conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.
+However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.
 
 In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems.
-Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adopted to extend the models that were used to describe the transport characteristics in quantum Hall systems.
-Owing the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices.
-As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D opto-electronic nano transistors, enhancing their performance, and inventing novel appliances.
+Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adapted to extend the models that were used to describe the transport characteristics in quantum Hall systems.
+Owing to the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices, which are employed as the building blocks of next-generation nanoelectronic devices.
+As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D optoelectronic nano transistors, enhancing their performance and inventing novel appliances.

### 2021-08-16 paper/v2.0/sections/appendix_a.tex
Add new version of the paper

--- 2021-08-09 paper/v1.0/sections/appendix_a.tex
@@
-The derivation of the solutions for the time dependent Schrödinger equation with our system's Hamiltonian (Eq.
+The derivation of the solutions for the time-dependent Schrödinger equation with our system's Hamiltonian (Eq.
 \ref{eq_1}) is quite similar to that followed in Refs.
@@
 This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}.
-We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
+We introduce a time-dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
 \begin{equation} \label{eq_a9}
@@
 \end{equation}
-Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
+Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
 \begin{equation} \label{eq_a20}
   \begin{aligned}
-    \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
-    \chi_n\left(y - y_0 - \zeta(t)\right)
+    \psi_{n,m}&(x,y,t) \\
+    &=  \frac{1}{\sqrt{L_x}}
+    \chi_n\left(y - y_0 - \zeta(t)\right)\\
+    &\quad\times
     \text{exp}\bigg(
-    \frac{i}{\hbar}\bigg[- \epsilon_nt \\
-    &
-    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)+
-    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\
-    & +
+    \frac{i}{\hbar}\bigg[- \epsilon_nt
+    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
+    & \quad\quad+
+    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
     \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).

### 2021-08-16 paper/v2.0/sections/appendix_b.tex
Add new version of the paper

--- 2021-08-09 paper/v1.0/sections/appendix_b.tex
@@
 \end{equation}
-which is a periodic function in time. Using these parameters, we can factorize the wave function given in Eq.~(\ref{eq_2}) as linearly time dependent part and periodic time dependent part as follows
+which is a periodic function in time. Using these parameters, we can factorize the wave function given in Eq.~(\ref{eq_2}) as linearly time-dependent part and periodic time-dependent part as follows
 \begin{equation} \label{eq_b5}
@@
      \frac{eEy}{\omega}\cos(\omega t) \\
-     & +
+     & \quad+
      m_e\dot{\zeta(t)}\big[y-\zeta(t)\big]
@@
 \end{equation}
-This leads to separate the linear time dependent phase component as the quasienergies
+This leads to separate the linear time-dependent phase component as the quasienergies
 \begin{equation} \label{eq_b6}
@@
   \begin{aligned}
-    \phi_{n,m}(x,y,t) \equiv &
+    \phi_{n,m}(x,y,t) =  &
     \frac{1}{\sqrt{L_x}} \chi_{n}\left(y - y_0 - \zeta(t)\right)
@@
     ])\\
-    & \times
+    & \quad\times
     \int_{-L_y/2}^{L_y/2} dy\; \exp(-i\qty[k_y - \gamma(t)]y)
     \chi_{n}\qty[y - \mu(t)] \\
-     & \times
+     & \quad\times
      \frac{1}{\sqrt{L_x}}
@@
 and
-\begin{equation} \label{eq_b18}
+\begin{equation} \label{eq_b19}
   d \equiv

### 2021-08-16 paper/v2.0/sections/appendix_d.tex
Add new version of the paper

--- 2021-08-10 paper/v1.0/sections/appendix_d.tex
@@
 In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system.
-We already found the exact solution for our time dependent Hamiltonian give in Eq.~(\ref{eq_1}) and we identified them as the Floquet states in Eq.~(\ref{eq_12}).
+We already found the exact solution for our time-dependent Hamiltonian give in Eq.~(\ref{eq_1}) and we identified them as the Floquet states in Eq.~(\ref{eq_12}).
 The Floquet modes derived in Eq.~(\ref{eq_9}) can be represented as quantum states using their corresponding quantum numbers for the simplicity of notation as follows
@@
 \begin{equation} \label{eq_d3}
-  \hat{\vb{j}} = \frac{1}{\tilde{m}} \qty(\hat{\vb{p}} - e\qty[\vb{A}_s + \vb{A}_d(t)]),
+  \hat{\vb{j}} = \frac{1}{\widetilde{m}} \qty(\hat{\vb{p}} - e\qty[\vb{A}_s + \vb{A}_d(t)]),
 \end{equation}
-where $\tilde{m}$ is the mass of the considering particle.
+where $\widetilde{m}$ is the mass of the considering particle.
 
@@
 \begin{equation} \label{eq_d4}
-  \hat{j}_x = \frac{1}{\tilde{m}} \qty(-i\hbar\pdv{x} + eBy).
+  \hat{j}_x = \frac{1}{\widetilde{m}} \qty(-i\hbar\pdv{x} + eBy).
 \end{equation}
@@
   \qty({j}_x)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{1}{\tilde{m}} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x},
+  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x},
 \end{equation}
@@
     \qty({j}_x)_{nm,n'm'} = &
-    \frac{1}{{\tilde{m}}}
+    \frac{1}{{\widetilde{m}}}
     \delta_{k_x,k'_x}
@@
     \qty({j}_x)_{nm,n'm'} =
-    \frac{1}{{\tilde{m}}}
+    \frac{1}{{\widetilde{m}}}
     \delta_{k_x,k'_x}
@@
     \qty({j}_x)&_{nm,n'm'} =
-    \frac{1}{{\tilde{m}}}
+    \frac{1}{{\widetilde{m}}}
     \delta_{k_x,k'_x}
@@
 \end{equation}
-
 Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we identify the $0$-th component of the Fourier series as
@@
       \qty({j}^x_{s=0})_{nm,n'm'} =&
-      \frac{eB}{{\tilde{m}}}
+      \frac{eB}{{\widetilde{m}}}
       \delta_{k_x,k'_x} \\
@@
 \begin{equation} \label{eq_d12}
-  \hat{j}_y = \frac{1}{\tilde{m}} \qty(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t)).
+  \hat{j}_y = \frac{1}{\widetilde{m}} \qty(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t)).
 \end{equation}
@@
   \qty({j}_y)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{-1}{\tilde{m}} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))\;}{n',k'_x}.
+  \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))\;}{n',k'_x}.
 \end{equation}

### 2021-08-16 paper/v2.0/sections/7_conclusions.tex
Correct spellings

@@
 Owing to the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices, which are employed as the building blocks of next-generation nanoelectronic devices.
-As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D optoelectronic nano transistors, enhancing their performance and inventing novel appliances.
+As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D optoelectronic nanotransistors, enhancing their performance and inventing novel appliances.

### 2021-08-16 paper/v2.0/sections/appendix_a.tex
Correct spellings

@@
 \end{equation}
-Subsequenty we define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 = {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 = {eB}/{m_e}$.
+Subsequently we define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 = {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 = {eB}/{m_e}$.
 This leads to a new arrangement of the Hamiltonian
@@
 \end{equation}
-Subsequenty, we can restrict $\zeta(t)$ function such that
+Subsequently, we can restrict $\zeta(t)$ function such that
 \begin{equation} \label{eq_a11}

### 2021-08-16 paper/v2.0/sections/appendix_c.tex
Add new version of the paper
Correct spellings

--- 2021-08-10 paper/v1.0/sections/appendix_c.tex
@@
 \end{equation}
-Due to time independence, the perturbation in the interaction picture has the same form as Schrödinger picture representation
+Due to time-independence, the perturbation in the interaction picture has the same form as Schrödinger picture representation
 \begin{equation} \label{eq_c8}
@@
 \end{figure}
-This scenario is illustared in Fig.~\ref{fig_2}.
+This scenario is illustrated in Fig.~\ref{fig_2}.
 The scattering amplitude for this scattering scenario can be calculated using the equation derived in Eq.~(\ref{eq_c14})
@@
 \end{equation}
-where $\Upsilon_{imp}^2$ is a conatant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
+where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
 \begin{equation} \label{eq_c23}

### 2021-08-16 paper/v2.0/sections/2_schrodinger_problem.tex
Corrections sec1

@@
 We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field.
-Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field (Fig.~\ref{fig_1}).
+Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field as given in Fig.~\ref{fig_1}.
 \begin{figure}[b]
 \includegraphics[scale=0.9]{figures/fig_1}
-\caption{\label{fig_1} Our 2DEG system only confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and dressing field (with y-polarized electric field $\vb{E}$) are applied perpendicular to the surface of 2DEG.}
+\caption{\label{fig_1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
+The dressing field is linearly polarized with a $y$-polarized electric field $\vb{E}$.}
 \end{figure}
@@
 
-Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{\text{T}}$.
-Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$.
+Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{T}$.
+Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E\cos(\omega t)]/\omega,0)^{T}$.
 These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}.
 Thus, we can represent our system with a time-dependent Hamiltonian
-\begin{equation} \label{eq_1}
-  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big[\vb{A}_{s}+\vb{A}_{d}(t)\big]\Big]^2,
+\begin{equation} \label{eq:1}
+  \hat{H}_e(t) =
+  \frac{1}{2m_e}
+  \left\{ \hat{\vb{p}} - e\right[ \vb{A}_{s}+\vb{A}_{d}(t) \left] \right\}^2,
 \end{equation}
 where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{T}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{T}$.
-The exact solutions for the time-dependent Schrödinger equation $i\hbar\; \text{d}\psi/\text{d}t = \hat{H}_e(t) \psi$ were already derived in Refs.
+The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv*{\psi}{t} = \hat{H}_e(t)\psi$ were already derived in Refs.
 \cite{husimi53,ditt98,dini16}.
 Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
-\begin{equation} \label{eq_2}
+\begin{equation} \label{eq:2}
   \begin{aligned}
-    \psi_{n,m}&(x,y,t)  \\
-    & = \frac{1}{\sqrt{L_x}}
-    \chi_n\big(y - y_0 - \zeta(t)\big)\\
-    & \quad\times
-    \text{exp}\bigg(
-    \frac{i}{\hbar}\bigg[- \epsilon_n t
-    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
-    & \quad+
-    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
-    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
+    &\psi_{n,m}(x,y,t)  \\
+      & \quad = \frac{1}{\sqrt{L_x}}
+        \chi_n \bm{\left(} y - y_0 - \zeta(t) \bm{\right)}\\
+      & \qquad \times
+        \exp \bm{\left(}
+        \frac{i}{\hbar}\left\{- \epsilon_n t
+        + p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right.\\
+      & \left.\left. \qquad\qquad +
+        m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
+        \int_0^{t}L(\zeta,\dot{\zeta},t')\,dt' \right\}\bm{\right)},
   \end{aligned}
 \end{equation}
-where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$.
+where $n \in \mathbb{Z}^+_0$ and $m \in \mathbb{Z}$.
 Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant.
-The center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
+The center of the cyclotron orbit on the $y$-axis is given by $y_0 = \flatfrac{-p_x}{(eB)}$ with $p_x = \flatfrac{2\pi\hbar m}{L_x}$.
 Moreover, $\chi_n$ are well-known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
-\begin{equation} \label{eq_3}
+\begin{equation} \label{eq:3}
   \chi_n(y) =
-   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
+  \sqrt{ \frac{\kappa}{2^{n}n!}}
   e^{-\kappa^2 y^2/2}
@@
 \end{equation}
-with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
-The path shift of the driven classical oscillator $\zeta(t)$ is given by
-\begin{equation} \label{eq_4}
+with eigenvalues $\epsilon_n = \hbar \omega_0 [n + (1/2)]$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
+The path shift of the driven classical oscillator $\zeta(t)$ can be given by
+\begin{equation} \label{eq:4}
   \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
 \end{equation}
-while the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
-\begin{equation} \label{eq_5}
+while $\dot{\zeta}(t) = \dv*{\zeta(t)}{t}$. We can identify the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ as
+\begin{equation} \label{eq:5}
   L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
 \end{equation}
-For details of the full derivation refer to Appendix \ref{appendix_a}.
-The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system.
+For details of the full derivation, refer to Appendix \ref{appendix_a}.
+The exponential phase shifts in Eq.~(\ref{eq:2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system.
 Therefore, we can observe that the magneto-transport characteristics of 2DEG can be renormalized by a nonoscillating magnetic field along with a dressing field.

### 2021-08-16 paper/v2.0/sections/3_floquet_theory.tex
Correction sec2

@@
 
-First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}).
+First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq:2}).
 By factorizing the wave function into a linearly time-dependent part and a periodic time-dependent part, we present the quasienergies as
-\begin{equation} \label{eq_6}
+\begin{equation} \label{eq:6}
   \varepsilon_{n} =
-  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
+  \hbar \omega_0 \left(n + \frac{1}{2}\right) - \Delta_{\varepsilon},
 \end{equation}
 which only depends on a single quantum number $n$. The Floquet modes can then be recognized as
-\begin{equation} \label{eq_7}
+\begin{equation} \label{eq:7}
   \begin{aligned}
-    \phi_{n,m}(x,y,t) = &
-    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)\\
+    \phi_{n,m}(x,y,t) =&
+    \frac{1}{\sqrt{L_x}} \chi_{n}\bm{\left(}y - y_0 -\zeta(t)\bm{\right)} \\
     & \times
-    \text{exp}\bigg(
-     \frac{i}{\hbar}\bigg[
-     p_x x +
-     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
-     & +
-     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
-     + \xi \bigg]\bigg),
+      \exp \bm{\left(}
+      \frac{i}{\hbar}\left\{
+      p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right. \\
+    & \left.\left. \qquad\qquad +
+      m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
+      \xi \right\}\bm{\right)},
   \end{aligned}
@@
 with
-\begin{equation} \label{eq_8a}
-  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)},
+\begin{equation} \label{eq:8}
+  \Delta_{\varepsilon} = \frac{e^2E^2}{4m_e(\omega_0^2 - \omega^2)},
 \end{equation}
 and
-\begin{equation} \label{eq_8b}
-  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
+\begin{equation} \label{eq:9}
+  \xi = \frac{e^2E^2 \left(3\omega^2 - \omega_0^2 \right)}
+  {8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
 \end{equation}
@@
 Performing the Fourier transform over the confined 2D space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
-\begin{equation} \label{eq_9}
+\begin{equation} \label{eq:10}
   \begin{aligned}
-    \phi_{n,m}\big(k_x,k_y,t\big)  = &
-    {\sqrt{L_x}}
-    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
+    \phi_{n,m}\big(k_x,k_y,t\big)  =&
+    \sqrt{L_x}
+    \widetilde{\chi}_{n} \bm{\left(}k_y - b\cos(\omega t)\bm{\right) }\\
     & \times
-    \text{exp}\left(
-      i\xi
-      -ik_y  \qty[d\sin(\omega t) + y_0]
-    \right),
+    \exp \bm{\left(} i\xi -ik_y  \left[d\sin(\omega t) + y_0 \right] \bm{\right)},
   \end{aligned}
@@
 where
-\begin{equation} \label{eq_10}
-  \tilde{\chi}_{n}\qty(k) =
-  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
-  \qty(\frac{1}{\kappa})^{1/2}
-  e^{-\frac{k^2}{2 \kappa^2}}
-  \mathcal{H}_{n} \qty(\frac{k}{\kappa}).
+\begin{equation} \label{eq:11}
+  \widetilde{\chi}_{n}(k) =
+  i^n \left(\frac{1}{ 2^{n} n! \sqrt{\pi} \kappa}\right)^{1/2}
+  e^{-\flatfrac{k^2}{(2 \kappa^2)}}
+  \mathcal{H}_{n} \left(\flatfrac{k}{\kappa}\right).
 \end{equation}
 Here we have introduced new parameters
-\begin{equation} \label{eq_11a}
+\begin{equation} \label{eq:12}
   b =
@@
 and
-\begin{equation} \label{eq_11b}
+\begin{equation} \label{eq:13}
   d =
@@
 \end{equation}
-Using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space as
-\begin{equation} \label{eq_12}
+Using Floquet theory, the wave functions derived in Eq.~(\ref{eq:2}) can be written as Floquet states in momentum space as
+\begin{equation} \label{eq:14}
   \psi_{n,m}(k_x,k_y,t) =
-  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
+  \exp(-\flatfrac{i\varepsilon_{n}t}{\hbar}) \phi_{n,m} (k_x,k_y,t).
 \end{equation}

### 2021-08-16 paper/v2.0/sections/2_schrodinger_problem.tex
Correction sec2
Correct eq15

@@
 We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field.
-Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field as given in Fig.~\ref{fig_1}.
+Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field as given in Fig.~\ref{fig:1}.
 \begin{figure}[b]
-\includegraphics[scale=0.9]{figures/fig_1}
-\caption{\label{fig_1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
+\includegraphics[scale=0.9]{figures/fig_1.pdf}
+\caption{\label{fig:1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
 The dressing field is linearly polarized with a $y$-polarized electric field $\vb{E}$.}
@@
   \chi_n(y) =
-  \sqrt{ \frac{\kappa}{2^{n}n!}}
+  \left( \frac{\kappa}{2^{n}n! \sqrt{\pi}}\right)^{1/2}
   e^{-\kappa^2 y^2/2}

### 2021-08-16 paper/v2.0/sections/4_inverse_scattering_time.tex
Correct eq15

@@
 In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
-With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq_12}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
-\begin{equation} \label{eq_13}
+With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
+\begin{widetext}
+\begin{equation} \label{eq:15}
   \begin{aligned}
-    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{N} \\
-    & =
-    \frac { \varrho^2}{eB}
-    \delta(\varepsilon - \varepsilon_{N}) \\
-    & \quad\times
-    \int_{-\infty}^{\infty} d k_1 \Bigg[
-    J_l\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
-    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - k_1]) \\
-    & \quad\times
-    \qty|
-    \int_{-\infty}^{\infty} dk_2 \;
-    {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
-    {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg],
+    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
+    \frac{ \varrho^2}{eB} \delta(\varepsilon - \varepsilon_N) \\
+    & \times
+    \int_{-\infty}^{\infty}
+    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+    \left|
+    \int_{-\infty}^{\infty}
+    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
+    \chi_N \bm{\left(} \frac{\hbar}{eB}
+    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
+    dk_2 \right|^2 d k_1,
   \end{aligned}
 \end{equation}
-where $\varrho = \eta_{imp} L_x [ { V_{imp}}/{eB}]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
+\end{widetext}
+where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{(eB)}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
 A more detailed derivation is given in Appendix \ref{appendix_c}.
 We modeled the effect caused by impurities in the considered system as a single perturbation potential.
-Since random impurities in a disordered metal offers a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
+Since random impurities in a disordered metal offer a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
 Thus, the total scattering potential in the 2DEG has been represented as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
@@
 Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
-\begin{equation} \label{eq_14}
- \Gamma^{00}_{N}(\varepsilon,k_x) = \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
+\begin{equation} \label{eq:16}
+ \Gamma^{00}_{N}(\varepsilon,k_x) =
+ \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
 \end{equation}
 which simplifies to
-\begin{equation} \label{eq_15}
+\begin{equation} \label{eq:17}
  \begin{aligned}
@@
 In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
-\begin{equation} \label{eq_16}
+\begin{equation} \label{eq:18}
  \delta(\varepsilon - \varepsilon_{N}) \approx
@@
 Then we write the central element of inverse scattering time matrix in the more compact form
-\begin{equation} \label{eq_17}
+\begin{equation} \label{eq:19}
   \begin{aligned}
@@
 To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
-\begin{equation} \label{eq_18}
+\begin{equation} \label{eq:20}
     \Lambda_N(k_x) =
@@
 \begin{widetext}
-\begin{equation} \label{eq_19}
+\begin{equation} \label{eq:21}
     \Lambda_N (k_x) =

### 2021-08-17 paper/v2.0/sections/1_introduction.tex
Correct eq15
Correction sec3 and sec4

@@
 At high intensities, the higher-order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
-In these instances, a more accurate treatment needs to adopt.
+In these instances, a more accurate treatment needs to be adopted.
 Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}.
-Here the applied high-intensity  electromagnetic field identify as the dressing field.
+Here the applied high-intensity  electromagnetic field identify as the \textit{dressing field}.
 

### 2021-08-17 paper/v2.0/sections/4_inverse_scattering_time.tex
Correction sec3 and sec4

@@
  \Gamma^{00}_{N}(\varepsilon,k_x) =
- \hbar \qty(\frac{1}{\tau(\varepsilon,k_x)})^{00}_{N},
+ \hbar \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{00}_N,
 \end{equation}
 which simplifies to
+\begin{widetext}
   \begin{equation} \label{eq:17}
    \begin{aligned}
-   &\Gamma^{00}_{N} (\varepsilon,k_x) \\
-   & =
+     &\Gamma^{00}_{N} (\varepsilon,k_x) =
      \frac { \varrho^2}{eB}
-   \delta(\varepsilon - \varepsilon_{N}) \\
-   & \quad\times
-   \int_{-\infty}^{\infty} d k_1 \Bigg[
-   J_0^2\qty(\frac{b\hbar}{eB}[{k}_x - k_1])
-   \\
-   & \quad\times
-   \qty|
-   \int_{-\infty}^{\infty} dk_2 \;
-   {\chi}_{N}\qty(\frac{\hbar}{eB}k_2)
-   {\chi}_{N}\qty(\frac{\hbar}{eB} \qty[k_1 - {k}_x - k_2])|^2\Bigg].
+     \delta(\varepsilon - \varepsilon_{N})
+     \int_{-\infty}^{\infty}
+     J_0^2 \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+     \left|
+     \int_{-\infty}^{\infty}
+     \chi_N \left( \frac{\hbar}{eB}k_2 \right)
+     \chi_N \bm{\left(} \frac{\hbar}{eB}
+     \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
+     dk_2 \right|^2 d k_1.
    \end{aligned}
   \end{equation}
-
-\begin{figure}[t]
-\includegraphics[scale=0.68]{figures/fig_3}
-\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a  frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and intensity $I =100~\text{W}/\text{cm}^{2}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
-\end{figure}
-
-\begin{figure}[b]
-\includegraphics[scale=0.68]{figures/fig_4}
-\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$.
-In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
-\end{figure}
-
 In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
@@
  \delta(\varepsilon - \varepsilon_{N}) \approx
- \frac{1}{\pi \Gamma^{00}_{N}(\varepsilon,k_x)}.
+ \frac{1}{\pi \Gamma^{00}_N (\varepsilon,k_x)}.
 \end{equation}
@@
   \begin{aligned}
-    \Gamma^{00}_{N}(\varepsilon,& k_x) =
+    &\Gamma^{00}_{N}(\varepsilon,k_x) =
      \varrho
-    \bigg[
-    \int_{-\infty}^{\infty} d {k}_1 \;
-    J_0^2\qty(\lambda_1[{k}_x - {k}_1]) \\
-    & \times
-    \qty|
-    \int_{-\infty}^{\infty} d{k}_2 \;
-    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
-    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2
-    \bigg]^{-\frac{1}{2}},
+      \left[
+      \int_{-\infty}^{\infty}
+      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
+      \left|
+      \int_{-\infty}^{\infty}
+      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
+      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
+      dk_2 \right|^2
+      dk_1
+      \right]^{-\frac{1}{2}},
   \end{aligned}
 \end{equation}
-where $ \lambda_1 \equiv \hbar b/eB$ and  $\lambda_2 \equiv \hbar \kappa/eB$.
+where $ \lambda_1 = \flatfrac{\hbar b}{(eB)}$ and  $\lambda_2 = \flatfrac{\hbar \kappa}{(eB)}$.
 To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
@@
     \Lambda_N(k_x) =
-    \frac{\Gamma^{00}_{N}(\varepsilon,k_x)}{\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
+    \frac{\Gamma^{00}_N (\varepsilon,k_x)}
+    {\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
 \end{equation}
 which can be evaluated with
-\begin{widetext}
 \begin{equation} \label{eq:21}
     \Lambda_N (k_x) =
-    \qty[
+    \left[
     \frac
-    {\int_{-\infty}^{\infty} d {k}_1 \;
-    J_0^2\qty(\lambda_1[{k}_x - {k}_1])
-    \qty|
-    \int_{-\infty}^{\infty} d{k}_2 \;
-    \tilde{\chi}_{N}\qty(\lambda_2 k_2)
-    \tilde{\chi}_{N}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
-    {\int_{-\infty}^{\infty} d {k}_1 \;
-    \qty|
-    \int_{-\infty}^{\infty} d{k}_2 \;
-    \tilde{\chi}_{0}\qty(\lambda_2 k_2)
-    \tilde{\chi}_{0}\qty(\lambda_2 \qty[{k}_1 - {k}_2 - {k}_x])|^2}
-    ]^{1/2}.
+    {
+      \int_{-\infty}^{\infty}
+      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
+      \left|
+      \int_{-\infty}^{\infty}
+      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
+      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
+      dk_2 \right|^2
+      dk_1
+    }
+    {
+      \int_{-\infty}^{\infty}
+      \left|
+      \int_{-\infty}^{\infty}
+      \widetilde{\chi}_0 \left(\lambda_2 k_2 \right)
+      \widetilde{\chi}_0 \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
+      dk_2 \right|^2
+      dk_1
+    }
+    \right]^{1/2}.
 \end{equation}
@@
 
-Normalized energy band broadening against x-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
+\begin{figure}[h!]
+\includegraphics[scale=0.68]{figures/fig_3}
+\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\end{figure}
+\begin{figure}[t!]
+\includegraphics[scale=0.68]{figures/fig_4}
+\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
+In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\end{figure}
+
+Normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
 To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
 In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
-In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $0.24\;\text{me}V$.
-Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = 0.24 \;\text{meV}$.
-Here, we observe that the normalized energy broadening value for each Landau level is independent of the x-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
+In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
+Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
+Here, we observe that the normalized energy broadening value for each Landau level is independent of the $x$-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
 When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.

### 2021-08-17 paper/v2.0/sections/5_floquet_drude_conductivity.tex
Corrections sec5

@@
 This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
-\begin{equation} \label{eq_20}
+\begin{equation} \label{eq:22}
   \begin{aligned}
-    {\sigma}^{xx} =&
+    \sigma^{xx} = &
     \frac{-1}{4\pi\hbar A}
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
-    \qty(
-    -\frac{\partial f}{\partial \varepsilon})
-    \\
-    & \times
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+    -\pdv*{f}{\varepsilon }\right) \\
+    &  \quad\times
     \tr
-    \qty[
+    \left\{
     {j}^x_0
-    \qty(
+    \left[
     \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    )
+    \right]
     {j}^x_0
-    \qty(
+    \left[
     \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    )
-    ]\bigg],
+    \right]
+    \right\} d\varepsilon,
   \end{aligned}
 \end{equation}
-where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system.
+where $j^x_0$ is the $x$-directional electric current operator matrix elements' $0$-th Fourier component.
+Here, $\vb{G}^{r}(\varepsilon)$ and $\vb{G}^{a} (\varepsilon)$ are the retarted and advanced white noise disorder averaged Floquet Green function matrices \cite{wackerl20,wackerlthesis20}, respectively.
+These matrices are defined against the Floquet modes of the considering system.
 Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity.
 In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
-\begin{equation} \label{eq_21}
-    \Pi- \frac{\hbar \omega}{2}
+\begin{equation} \label{eq:23}
+    \Pi- \flatfrac{\hbar \omega}{2}
     \leq \varepsilon_N
     <
-    \Pi + \frac{\hbar \omega}{2}.
+    \Pi + \flatfrac{\hbar \omega}{2}.
 \end{equation}
-Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr[\cdot]$ is the trace of the considering operator.
+Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr\{\cdot\}$ is the trace of the considering operator.
 
@@
 Thus, the $x$-directional longitudinal conductivity given in
-Eq.~(\ref{eq_20}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$ as
+Eq.~(\ref{eq:22}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} = \ket{n,k_x}$ as
 \begin{widetext}
-\begin{equation} \label{eq_22}
+\begin{equation} \label{eq:24}
   \begin{aligned}
-    {\sigma}^{xx} =
-    \frac{-1}{4\pi\hbar A} &
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
-    \qty(
-    -\frac{\partial f}{\partial \varepsilon})
+    \sigma^{xx} =
+    \frac{-1}{4\pi\hbar A}
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+      -\frac{\partial f}{\partial \varepsilon}
+    \right)
     \frac{1}{V_{k_x}} \sum_{k_x}
     \sum_{n}
-    \mel{n,k_x}{
+    \mel{n,k_x}
+    {
       {j}^x_0
-    \qty(
+      \left[
         \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    )
+      \right]
       {j}^x_0
-    \qty(
-    \vb{G}^{r}_0 (\varepsilon) - \vb{G}^{a}_0 (\varepsilon)
-    )
+      \left[
+        \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+      \right]
     }
-    {n,k_x},
+    {n,k_x}
+    d\varepsilon,
   \end{aligned}
@@
 where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Next, we evaluate the above expression as follows
-\begin{equation} \label{eq_23}
+\begin{equation} \label{eq:25}
   \begin{aligned}
-    {\sigma}^{xx}  = &
+    \sigma^{xx}  = &
     \frac{-1}{4\pi\hbar A}
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
-    \qty(
-    -\frac{\partial f}{\partial \varepsilon})
-    \frac{1}{V_{k_x}^4} \sum_{k_x} \sum_{n}
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+      -\frac{\partial f}{\partial \varepsilon}
+    \right)
+    \frac{1}{V_{k_x}^4}
+    \sum_{k_x} \sum_{n}
     \sum_{{k_x}_1,{k_x}_2,{k_x}_3}
-    \sum_{n_1,n_2,n_3}\\
-    & \times
-    \mel{n,k_x}{
+    \sum_{n_1,n_2,n_3} \\
+    & \quad\times \mel{n,k_x}{
     {j}^x_0}
@@
     \mel{{n_1,{k_x}_1}}{
-    \qty(
+    \left[
       \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    )}
+    \right]
+    }
     {n_2,{k_x}_2}
@@
     \mel{n_3,{k_x}_3}{
-    \qty(
+    \left[
       \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    )
+    \right]
     }
-    {n,k_x}.
+    {n,k_x} d\varepsilon.
   \end{aligned}
@@
 Thus, we evaluate the matrix elements of the difference between retarded and advanced Green's functions as
-\begin{equation} \label{eq_24}
-  \mel{{n_1,{k_x}_1}}{
+\begin{equation} \label{eq:26}
+  \mel{{n_1,{k_x}_1}}
+  {
     \vb{T}^{\dagger}
-  \qty(
+    \left[
     \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-  )\vb{T}}
+    \right]\vb{T}
+  }
   {n_2,{k_x}_2} =
-  \qty[
-  \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
-  \delta_{n_1,n_2}\delta_{{k_x}_1,{k_x}_2}}
+  \frac
   {
-  \qty(
-  \frac{1}{\hbar}\varepsilon -
-  \frac{1}{\hbar}\varepsilon_{n_1}
-  )^2
-  + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
-  }],
+    2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+    \delta_{n_1,n_2}\delta_{{k_x}_1,{k_x}_2}
+  }
+  {
+    \left(
+    \flatfrac{\varepsilon}{\hbar} -
+    \flatfrac{\varepsilon_{n_1}}{\hbar}
+    \right)^2
+    + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
+  },
 \end{equation}
 and
-\begin{equation} \label{eq_25}
+\begin{equation} \label{eq:27}
   \mel{{n_3,{k_x}_3}}{
   \vb{T}^{\dagger}
-  \qty(
+  \left[
   \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-  )\vb{T}}
+  \right]\vb{T}}
   {n,{k_x}} =
-  \qty[
-  \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
-  \delta_{n_3,n}\delta_{{k_x}_3,{k_x}}}
+  \frac{
+    2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+    \delta_{n_3,n}\delta_{{k_x}_3,{k_x}}
+  }
   {
-  \qty(
-  \frac{1}{\hbar}\varepsilon -
-  \frac{1}{\hbar}\varepsilon_{n}
-  )^2
-  + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
-  }].
+    \left(
+    \flatfrac{\varepsilon }{\hbar}-
+    \flatfrac{\varepsilon_{n}}{\hbar}
+    \right)^2
+    + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
+  }.
 \end{equation}
@@
 Applying the matrix elements of the electric current operator in Landau levels and
-expressions from Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain
-\begin{equation} \label{eq_26}
+expressions from Eq.~(\ref{eq:26}) and Eq.~(\ref{eq:27}) back into Eq.~(\ref{eq:25}) we obtain
+\begin{equation} \label{eq:28}
   \begin{aligned}
-    {\sigma}^{xx}  =
-    \frac{-1}{4\pi\hbar A} &
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
-    \qty(
-    -\frac{\partial f}{\partial \varepsilon})
-    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
-    \sum_{n_1,n_2}
+    \sigma^{xx}  =
+    \frac{-1}{4\pi\hbar A}
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}&
+    \left(
+    -\frac{\partial f}{\partial \varepsilon}
+    \right)
+    \frac{1}{V_{k_x}}
+    \sum_{k_x} \sum_{n} \sum_{n_1,n_2}
     \\
@@
     \frac{e^2B}{{m_e}}
-    \qty(\sqrt{\frac{n+1}{2}} \delta_{n_1,n+1} + \sqrt{\frac{n}{2}}
-    \delta_{n_1,n-1})
-    \qty[
-    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
-    \delta_{n_1,n_2}}
+    \left(
+    \sqrt{\frac{n+1}{2}} \delta_{n_1,n+1} + \sqrt{\frac{n}{2}}\delta_{n_1,n-1}
+    \right)
+    \left\{
+    \frac
     {
-    \qty(
-    \frac{1}{\hbar}\varepsilon -
-    \frac{1}{\hbar}\varepsilon_{n_1}
-    )^2
-    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
-    }] \\
+      2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+      \delta_{n_1,n_2}
+    }
+    {
+      \left(
+      \flatfrac{\varepsilon}{\hbar} -
+      \flatfrac{\varepsilon_{n_1}}{\hbar}
+      \right)^2
+      + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
+    }
+    \right\} \\
     & \times
     \frac{e^2B}{{m_e}}
-    \qty(\sqrt{\frac{n_2+1}{2}} \delta_{n,n_2+1} + \sqrt{\frac{n_2}{2}}
-    \delta_{n,n_2-1})
-    \qty[
-    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+    \left(
+    \sqrt{\frac{n_2+1}{2}} \delta_{n,n_2+1} + \sqrt{\frac{n_2}{2}}
+    \delta_{n,n_2-1}
+    \right)
+    \left\{
+    \frac{
+      2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
     }
     {
-    \qty(
-    \frac{1}{\hbar}\varepsilon -
-    \frac{1}{\hbar}\varepsilon_{n}
-    )^2
-    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})]^2
-    }],
+      \left(
+      \flatfrac{\varepsilon }{\hbar}-
+      \flatfrac{\varepsilon_{n}}{\hbar}
+      \right)^2
+      + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
+    }
+    \right\}  d\varepsilon,
   \end{aligned}
 \end{equation}
-For the full derivation of electric current operators in quantum Hall system refer to Appendix \ref{appendix_d}.
+For the full derivation of electric current operators in a quantum Hall system, refer to Appendix \ref{appendix_d}.
 After the expansion, the only non-zero term would be
-\begin{equation} \label{eq_27}
+\begin{equation} \label{eq:29}
   \begin{aligned}
-    {\sigma}^{xx} =
+    \sigma^{xx} =
     \frac{-1}{4\pi\hbar A}
     \frac{e^4B^2}{{{m_e}^2}} &
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
-    \qty(
-    -\frac{\partial f}{\partial \varepsilon})
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+    -\frac{\partial f}{\partial \varepsilon}\right)
     \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
-    \qty(n+1)
+    (n+1)
     \\
     & \times
-    \qty[
-    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n+1}}
+    \left\{
+    \frac
+    {
+      2i \Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_{n+1},k_x) \vb{T}\bm{)}
     }
     {
-    \qty(
-    \frac{1}{\hbar}\varepsilon -
-    \frac{1}{\hbar}\varepsilon_{n+1}
-    )^2
-    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n+1}}]^2
-    }]
-    \qty[
-    \frac{2i \text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n}}
+      \left(
+      \flatfrac{\varepsilon}{\hbar} -
+      \flatfrac{\varepsilon_{n+1}}{\hbar}
+      \right)^2
+      + \left[\Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_{n+1},k_x) \vb{T}\bm{)}\right]^2
+    }
+    \right\}
+    \left\{
+    \frac{
+      2i \Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_n,k_x) \vb{T}\bm{)}
     }
     {
-    \qty(
-    \frac{1}{\hbar}\varepsilon -
-    \frac{1}{\hbar}\varepsilon_{n}
-    )^2
-    + \qty[\text{Im}\qty(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})_{\varepsilon_{n}}]^2
-    }].
+      \left(
+      \flatfrac{\varepsilon }{\hbar}-
+      \flatfrac{\varepsilon_{n}}{\hbar}
+      \right)^2
+      + \left[\Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_n,k_x) \vb{T}\bm{)}\right]^2
+    }
+    \right\}
+    d\varepsilon.
   \end{aligned}
@@
 Subsequenty, we can identify the following property
-\begin{equation} \label{eq_28}
-  \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll} =
-  -2\text{Im}\qty[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}]^{ll}.
+\begin{equation} \label{eq:30}
+  \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll} =
+  -2\text{Im} \left[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}\right]^{ll}.
 \end{equation}
-Aterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in \ref{eq_27} as follows
-\begin{equation} \label{eq_29}
-    {\sigma}^{xx}   =
+Aterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in Eq.~(\ref{eq:29}) as follows
+\begin{equation} \label{eq:31}
+    \sigma^{xx}   =
     \frac{1}{\pi\hbar A}
     \frac{e^4B^2}{{{m_e}^2}}
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon
-    \qty(
-    -\frac{\partial f}{\partial \varepsilon})
-    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
-    \qty(n+1)
-    \qty[
-    \frac{\tilde{{\Gamma}}(\varepsilon_{n+1})
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+      -\frac{\partial f}{\partial \varepsilon}
+    \right)
+    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n} (n+1)
+    \left[
+    \frac{\widetilde{{\Gamma}}(\varepsilon_{n+1})
     }
     {
-    \qty(
+    \left(
     \varepsilon_F - \varepsilon_{n+1}
-    )^2
-    + \tilde{{\Gamma}}^2(\varepsilon_{n+1})
-    }]
-    \qty[
-    \frac{\tilde{{\Gamma}}(\varepsilon_{n})
+    \right)^2
+    + \widetilde{{\Gamma}}^2(\varepsilon_{n+1})
+    }
+    \right]
+    \left[
+    \frac{\widetilde{{\Gamma}}(\varepsilon_{n})
     }
     {
-    \qty(
+    \left(
     \varepsilon_F - \varepsilon_{n}
-    )^2
-    + \tilde{{\Gamma}}^2(\varepsilon_{n})
-    }],
+    \right)^2
+    + \widetilde{{\Gamma}}^2(\varepsilon_{n})
+    }
+    \right]
+    d\varepsilon,
 \end{equation}
 \end{widetext}
-with $\tilde{{\Gamma}}(\varepsilon_n,k_x) = \qty({\hbar}/{2\tau(\varepsilon_n,k_x)})^{00}$.
-Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\tilde{{\Gamma}}(\varepsilon_n,k_x)$ terms and get the sum over all available momentum space in $x$ direction.
+with $\widetilde{{\Gamma}}(\varepsilon_n,k_x) = \left[\flatfrac{\hbar}{2\tau(\varepsilon_n,k_x)}\right]^{00}$.
+Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\widetilde{{\Gamma}}(\varepsilon_n,k_x)$ terms.
+Subsequently, we can get the sum over available momentum in $x$-direction.
 However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considered system, we can identify that
-\begin{equation} \label{eq_30}
- -\frac{m_e\omega_0 Ly}{2\hbar} \leq k_x \leq \frac{m_e\omega_0 Ly}{2\hbar}.
+\begin{equation} \label{eq:32}
+ -\flatfrac{m_e\omega_0 Ly}{(2\hbar)} \leq k_x \leq \flatfrac{m_e\omega_0 Ly}{(2\hbar)}.
 \end{equation}
 We use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
-\begin{equation} \label{eq_31}
-  f(\varepsilon) = \frac{1}{\qty[\exp(\varepsilon - \varepsilon_F)/k_B T]+1},
+\begin{equation} \label{eq:33}
+  f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
 \end{equation}
@@
 Considering the above distribution for extremely low-temperature conditions, we can use the following approximation
-\begin{equation} \label{eq_32}
+\begin{equation} \label{eq:34}
   - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
 \end{equation}
-Moreover, let $\Pi = \varepsilon_F$ and the derived expression in \ref{eq_29} leads to
-\begin{equation} \label{eq_33}
+Moreover, let $\Pi = \varepsilon_F$ and the derived expression in \ref{eq:31} leads to
+\begin{equation} \label{eq:35}
   \begin{aligned}
-    {\sigma}^{xx}  =
-    \frac{e^2}{\hbar}
-    \frac{1}{\pi A} &
-    \sum_{n}
-    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}} \\
+    \sigma^{xx}  =
+    \frac{e^2}{\pi\hbar A}
+    \sum_{n} &
+    \frac{(n+1)}{\gamma_{n}\gamma_{n+1}} \\
     &\times
-    \qty[
+    \left[
       \frac{1}
       {
-        1 + \qty(\frac{X_F - n -1}{\gamma_{n+1}})^2
+        1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
       }
-    ]
-    \qty[
+    \right]
+    \left[
       \frac{1}
       {
-        1 + \qty(\frac{X_F - n}{\gamma_{n}})^2
+        1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
       }
-    ],
+    \right],
   \end{aligned}
 \end{equation}
-where $X_F = ({\varepsilon_F}/{\hbar \omega_0} - {1}/{2})$
+where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$
 and
-$\gamma_n = {\tilde{{\Gamma}}(\varepsilon_n)}/{\hbar \omega_0}$.
+$\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$.
 Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
-\begin{equation} \label{eq_34}
+\begin{equation} \label{eq:36}
   \begin{aligned}
     {\sigma}^{yy} =
-    \frac{e^2}{\hbar}
-    \frac{1}{\pi A}&
+    \frac{e^2}{\pi\hbar A} &
     \frac{1}{e^2B^2}
     \sum_{n}
-    \frac{\qty(n+1)}{\gamma_{n}\gamma_{n+1}} \\
+    \frac{(n+1)}{\gamma_{n}\gamma_{n+1}} \\
     & \times
-    \qty[
+    \left[
       \frac{1}
       {
-        1 + \qty(\frac{X_F - n -1}{\gamma_{n+1}})^2
+        1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
       }
-    ]
-    \qty[
+    \right]
+    \left[
       \frac{1}
       {
-        1 + \qty(\frac{X_F - n}{\gamma_{n}})^2
+        1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
       }
-    ].
+    \right].
   \end{aligned}

### 2021-08-17 paper/v2.0/sections/6_manipulate_conductivity.tex
Correct sec6 - only half

@@
 Here we derive a normalized $x$-directional conductivity of dressed quantum Hall system using the natural conductivity of the least Landau level
-\begin{equation} \label{eq_35}
+\begin{equation} \label{eq:37}
   \begin{aligned}
-    \tilde{\sigma}^{xx} =
-    \sigma_{0} &
-    \sum_{n}
-    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
+    \widetilde{\sigma}^{xx} =
+    \sigma_{0}
+    \sum_{n} &
+    \frac{(n+1)}{0.0037 \Lambda_n \Lambda_{n+1}} \\
     & \times
-    \qty[
+    \left[
       \frac{1}
       {
-        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
+        1 + \left(\frac{X_F - n -1}{0.06\Lambda_n}\right)^2
       }
-    ]
-    \qty[
+    \right]
+    \left[
       \frac{1}
       {
-        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
+        1 + \left(\frac{X_F - n}{0.06\Lambda_{n+1}}\right)^2
       }
-    ],
+    \right],
   \end{aligned}
 \end{equation}
-with $\sigma^0 = e^2/\pi \hbar A$.
+with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$.
 
-As illustrated in Fig.~\ref{fig_5} and \ref{fig_6}, we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
+As illustrated in Fig.~\ref{fig:5} and \ref{fig:6}, we can manipulate the normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
 For a given dressing field intensity, the longitudinal conductivity varies with  the Fermi level of the system showing sharp peaks at each Landau energy level.
@@
 In contrast, near each Landau level, the conductivity achieves excessive values compared to other areas.
-Moreover, as illustrates in Fig.~\ref{fig_5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.
-
-\begin{figure}[t]
-\includegraphics[scale=0.575]{figures/fig_5}
-\caption{\label{fig_5} Normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a  frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$.}
-\end{figure}
-\begin{figure}[t]
-\includegraphics[scale=0.575]{figures/fig_6}
-\caption{\label{fig_6} $3$rd Landau level’s normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = 1.2~\text{T}$, dressing field with a frequency of $\omega =2\times10^{12}~\text{rad}\text{s}^{-1}$ and $I_0 =100~\text{W}/\text{cm}^{2}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $0.24\;\text{me}V$}.
-\end{figure}
+Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.
 
 On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpen the conductivity peaks.
-When we increase the intensity level of the dressing field, the conductivity regions get more weaken as illustrated in the Fig.~\ref{fig_6}.
+When we increase the intensity level of the dressing field, the conductivity regions get more weaken as illustrated in the Fig.~\ref{fig:6}.
 However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
@@
 Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
-However, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and Fig.~\ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+However, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
 This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
@@
 Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.
+
+\begin{figure}[t]
+\includegraphics[scale=0.575]{figures/fig_5}
+\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\label{fig:5}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[scale=0.575]{figures/fig_6}
+\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$}.
+\label{fig:6}
+\end{figure}

### 2021-08-17 theory/sec_08.tex
Theory corrections manipulate conductivity

@@
   \Gamma_n = \qty(\frac{\hbar }{2\tau(\varepsilon_n)}) =
-  \frac{1}{2}\Gamma^{00}_{N}(\tilde{I})
+  \frac{1}{2}\Gamma^{00}_{N}(\tilde{I}),
 \end{equation}
-and this will be
+and using \eqref{5.32}, this can be re-write as follows
+\begin{equation} \label{8.2}
+   \Gamma_n = \frac{1}{2} \Lambda_N (\tilde{I}) \Gamma^{00}_{N=0}\big|_{E=0}.
+\end{equation}
+Let $\Gamma^{00}_{N=0}\big|_{E=0} = \Gamma_0$ and this leads to
+\begin{equation} \label{8.3}
+   \gamma_n = \frac{\Gamma_n}{\hbar \omega_0} =
+   \frac{\Gamma_0}{2\hbar \omega_0} \Lambda_N (\tilde{I})
+\end{equation}
+Let $\alpha \equiv \flatfrac{\Gamma_0}{2\hbar \omega_0}$ and we can obtain
+\begin{equation} \label{8.4}
+   \gamma_n = \alpha \Lambda_N (\tilde{I})
+\end{equation}
+Thus we can write the transverse conductivity as a function of fermi energy and intensity
+\begin{equation} \label{8.5}
+  \begin{aligned}
+    \sigma^{xx}(X_F,\tilde{I}) & =
+    \frac{e^2}{\pi\hbar A}
+    \sum_{n}
+    \frac{\qty(n+1)}{\alpha^2 \Lambda_n \Lambda_{n+1}}
+    \qty[
+      \frac{1}
+      {
+        1 + \qty(\frac{X_F - n -1}{\alpha\Lambda_n})^2
+      }
+    ]
+    \qty[
+      \frac{1}
+      {
+        1 + \qty(\frac{X_F - n}{\alpha\Lambda_{n+1}})^2
+      }
+    ].
+  \end{aligned}
+\end{equation}
+Then we can define a normalized transverse conductivity as follows
+\begin{equation} \label{8.6}
+  \begin{aligned}
+    \widetilde{\sigma}^{xx}(X_F,\tilde{I}) =
+    \flatfrac{\sigma^{xx}}{\sigma_0} =
+    \sum_{n}
+    \frac{\qty(n+1)}{\alpha^2 \Lambda_n \Lambda_{n+1}}
+    \qty[
+      \frac{1}
+      {
+        1 + \qty(\frac{X_F - n -1}{\alpha\Lambda_n})^2
+      }
+    ]
+    \qty[
+      \frac{1}
+      {
+        1 + \qty(\frac{X_F - n}{\alpha\Lambda_{n+1}})^2
+      }
+    ],
+  \end{aligned}
+\end{equation}
+where $\sigma_0 = \flatfrac{e^2}{(\pi\hbar A)}$.
+
+Above parameters can be evaluated for our experiment variables($\Gamma_0 = 0.24 \text{meV}$) as follows
 \begin{equation} \label{8.2}

### 2021-08-18 paper/v2.0/sections/6_manipulate_conductivity.tex
Correct figure numbers
Correct sec06

@@
 To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
-Here we derive a normalized $x$-directional conductivity of dressed quantum Hall system using the natural conductivity of the least Landau level
-\begin{equation} \label{eq:37}
+We can identifiy the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
+\begin{equation}\label{eq:37}
+  \widetilde{\sigma}^{xx}(X_F,I) =
+  \flatfrac{\sigma^{xx}}{\sigma_{0}},
+\end{equation}
+with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and this can be expressed as
+\begin{equation} \label{eq:38}
   \begin{aligned}
-    \widetilde{\sigma}^{xx} =
-    \sigma_{0}
-    \sum_{n} &
-    \frac{(n+1)}{0.0037 \Lambda_n \Lambda_{n+1}} \\
-    & \times
+    \widetilde{\sigma}^{xx}(X_F,I) &=
+    \sum_{n}
+    \frac{(n+1)}{\alpha^2 \Lambda_n \Lambda_{n+1}} \\
+    &\quad\times
     \left[
@@
       {
-        1 + \left(\frac{X_F - n -1}{0.06\Lambda_n}\right)^2
+        1 + \left(\frac{X_F - n -1}{\alpha \Lambda_n}\right)^2
       }
@@
       {
-        1 + \left(\frac{X_F - n}{0.06\Lambda_{n+1}}\right)^2
+        1 + \left(\frac{X_F - n}{\alpha \Lambda_{n+1}}\right)^2
       }
@@
 \end{equation}
-with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$.
+where $\alpha = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.
 
@@
 \begin{figure}[t]
-\includegraphics[scale=0.575]{figures/fig_5}
+\includegraphics[scale=0.575]{figures/fig_4}
 \caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.575]{figures/fig_6}
+\includegraphics[scale=0.575]{figures/fig_5}
 \caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$}.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
 \label{fig:6}

### 2021-08-19 paper/v2.0/sections/6_manipulate_conductivity.tex
Correct font size in figures
Corrections

@@
 
-As illustrated in Fig.~\ref{fig:5} and \ref{fig:6}, we can manipulate the normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
+As illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6}, we can manipulate the normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
 For a given dressing field intensity, the longitudinal conductivity varies with  the Fermi level of the system showing sharp peaks at each Landau energy level.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.575]{figures/fig_4}
+\includegraphics[scale=0.55]{figures/fig_4}
 \caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.575]{figures/fig_5}
+\includegraphics[scale=0.55]{figures/fig_5}
 \caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.

### 2021-08-19 paper/v2.0/sections/appendix_a.tex
Corrections

@@
 The derivation of the solutions for the time-dependent Schrödinger equation with our system's Hamiltonian (Eq.
-\ref{eq_1}) is quite similar to that followed in Refs.
+\ref{eq:1}) is quite similar to that followed in Refs.
 \cite{husimi53,dini16}.
 We start with expanding the Hamiltonian for two-dimensional case
-\begin{equation} \label{eq_a1}
+\begin{equation} \label{eq:a1}
   \hat{H}_e(t) = \frac{1}{2m_e}\left[
@@
 Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
-\begin{equation} \label{eq_a2}
+\begin{equation} \label{eq:a2}
     \hat{H}_e(t) = \frac{1}{2m_e}\left[
@@
 This leads to a new arrangement of the Hamiltonian
-\begin{equation} \label{eq_a3}
+\begin{equation} \label{eq:a3}
   \begin{aligned}
@@
 where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
-\begin{equation} \label{eq_a4}
+\begin{equation} \label{eq:a4}
     i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
@@
 can be presented by the following form
-\begin{equation} \label{eq_a5}
+\begin{equation} \label{eq:a5}
     \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
@@
 where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
-\begin{equation} \label{eq_a6}
+\begin{equation} \label{eq:a6}
     \bigg[
@@
 If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
-\begin{equation} \label{eq_a7}
+\begin{equation} \label{eq:a7}
      i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
@@
 Thus, we can identify $S(t) \equiv eE\sin(\omega t)$ term as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
-\begin{equation} \label{eq_a8}
+\begin{equation} \label{eq:a8}
   \begin{aligned}
@@
 We introduce a time-dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
-\begin{equation} \label{eq_a9}
+\begin{equation} \label{eq:a9}
     \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
@@
 This leads to
-\begin{equation} \label{eq_a10}
+\begin{equation} \label{eq:a10}
   \begin{aligned}
@@
 Subsequently, we can restrict $\zeta(t)$ function such that
-\begin{equation} \label{eq_a11}
+\begin{equation} \label{eq:a11}
   m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
@@
 and that simply our previous expression as
-\begin{equation} \label{eq_a12}
+\begin{equation} \label{eq:a12}
   \begin{aligned}
@@
 Here
-\begin{equation} \label{eq_a13}
+\begin{equation} \label{eq:a13}
   L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
@@
 is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
-\begin{equation} \label{eq_a14}
+\begin{equation} \label{eq:a14}
     \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
 \end{equation}
-and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
-\begin{equation} \label{eq_a15}
+and subtitling Eq.~(\ref{eq:a14}) back in Eq.~(\ref{eq:a12}) yields
+\begin{equation} \label{eq:a15}
     i \hbar \pdv{t} \chi(y',t)  =
@@
 This allows us to identify the well known eigenfunctions \cite{griffiths18,shankar94}
-\begin{equation} \label{eq_a16}
+\begin{equation} \label{eq:a16}
   \chi_n(y) =
@@
 with eigenvalues
-\begin{equation} \label{eq_a17}
+\begin{equation} \label{eq:a17}
   \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
@@
 Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
-Thus, we can identify the solutions for Eq.~(\ref{eq_a8}) as
-\begin{equation} \label{eq_a18}
+Thus, we can identify the solutions for Eq.~(\ref{eq:a8}) as
+\begin{equation} \label{eq:a18}
   \begin{aligned}
@@
 \end{equation}
-Since $\chi_n(x)$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of the solutions derived in Eq.~(\ref{eq_a18}).
+Since $\chi_n(x)$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of the solutions derived in Eq.~(\ref{eq:a18}).
 
-Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we derive the solution for Eq.~(\ref{eq_a11}) as
-\begin{equation} \label{eq_a19}
+Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we derive the solution for Eq.~(\ref{eq:a11}) as
+\begin{equation} \label{eq:a19}
   \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
 \end{equation}
-Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
-\begin{equation} \label{eq_a20}
+Subtitling solutions in Eq.~(\ref{eq:a18}) back in Eq.~(\ref{eq:a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq:a4}) as follows
+\begin{equation} \label{eq:a20}
   \begin{aligned}

### 2021-08-19 paper/v2.0/sections/appendix_a.tex
Correction appA until eq18

@@
 \cite{husimi53,dini16}.
-We start with expanding the Hamiltonian for two-dimensional case
+We start with expanding the Hamiltonian for two-dimensional scenario
 \begin{equation} \label{eq:a1}
-  \hat{H}_e(t) = \frac{1}{2m_e}\left[
-    \left[\hat{p}_x + eBy \right]^2 +
-    \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
-  \right].
+  \hat{H}_e(t) = \frac{1}{2m_e}
+  \left\{
+    \left(\hat{p}_x + eBy \right)^2 +
+    \left[
+      \hat{p}_y - \frac{eE}{\omega}\cos(\omega t)
+    \right]^2
+  \right\}.
 \end{equation}
 Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
-${L_x}^{-1/2}\exp(\frac{ip_x x}{\hbar})$ where $p_x = 2\pi \hbar m/L_x~$ with $ m \in \mathbb{Z}$.
+${L_x}^{-1/2}\exp(\flatfrac{ip_x x}{\hbar})$ where $p_x = \flatfrac{2\pi \hbar m}{L_x}$ with $ m \in \mathbb{Z}$.
 Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
 \begin{equation} \label{eq:a2}
-    \hat{H}_e(t) = \frac{1}{2m_e}\left[
-      \left[{p}_x + eBy \right]^2 +
-      \left[-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right]^2
-    \right].
+    \hat{H}_e(t) = \frac{1}{2m_e}
+    \left\{
+      \left({p}_x + eBy \right)^2 +
+      \left[
+        i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)
+      \right]^2
+    \right\}.
 \end{equation}
-Subsequently we define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 = {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 = {eB}/{m_e}$.
+Subsequently we define the \textit{center of the cyclotron orbit} on the $y$-axis as $y_0 = \flatfrac{-p_x}{(eB)}$, and the \textit{cyclotron frequency} as  $\omega_0 = {eB}/{m_e}$.
 This leads to a new arrangement of the Hamiltonian
@@
       \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
-      \frac{1}{2m_e}\bigg[
-      -\hbar^2 \pdv[2]{\tilde{y}} & +
-      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
-      & +
+      \frac{1}{2m_e} &
+      \left[
+        -\hbar^2 \pdv[2]{\tilde{y}}  +
+        \frac{2i\hbar eE}{\omega} \cos(\omega t) \pdv{\tilde{y}}
+        \right.\\
+        & \left. \qquad\qquad\quad +
         \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
-      \bigg],
+        \right],
   \end{aligned}
@@
 \begin{equation} \label{eq:a5}
-    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
+    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}}
+    \exp\left(
       \frac{ip_x x}{\hbar} +
       \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
-    \bigg) \vartheta(\tilde{y},t),
+    \right) \vartheta(\tilde{y},t),
 \end{equation}
@@
 \begin{equation} \label{eq:a6}
-    \bigg[
-    \frac{m_e \omega_0^2}{2}\tilde{y}^2
+    \left[
+    \frac{m_e \omega_0^2}{2} \tilde{y}^2
     - {eE\tilde{y}}\sin(\omega t)
-    -
-    \frac{\hbar^2}{2m_e}
-    \pdv[2]{\tilde{y}}
+    - \frac{\hbar^2}{2m_e} \pdv[2]{\tilde{y}}
     - i \hbar \dv{t}
-    \bigg]
+    \right]
     \vartheta(\tilde{y},t) = 0.
@@
      i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
-    \bigg[
+    \left(
     \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
     \frac{1}{2}m_e \omega_0^2\tilde{y}^2
-    \bigg]
+    \right)
     \vartheta(\tilde{y},t).
 \end{equation}
-Thus, we can identify $S(t) \equiv eE\sin(\omega t)$ term as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
+Thus, we can identify $S(t) = eE\sin(\omega t)$ term as an external force that act on the harmonic oscillator, and we can solve Eq.~(\ref{eq:a6}) as a forced harmonic oscillator on $\tilde{y}$ axis
 \begin{equation} \label{eq:a8}
@@
 \end{equation}
-
 This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}.
@@
     i \hbar \pdv{\varphi(y',t)}{t}   &=
-    \bigg[
+    \left\{
         -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
-        & +
-        \Big[
+        + \frac{1}{2} m_e \omega_0^2 y'^2
+        \right. \\
+        & \left. \qquad
+        - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
+        \right. \\
+        & \left. \qquad +
+        \left[
             m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
-        \Big]y' \\
-        &
-        +
-        \Big[
-            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
-        \Big]
-    \bigg]\varphi(y',t).
+        \right]y'
+    \right\} \varphi(y',t),
   \end{aligned}
 \end{equation}
-Subsequently, we can restrict $\zeta(t)$ function such that
+where we introduce $\dot{\zeta} = \dv*{\zeta}{t}$ and $\ddot{\zeta} = \dv*[2]{\zeta}{t}$ for the sake of notational convenience. Subsequently, we can restrict $\zeta(t)$ function such that
 \begin{equation} \label{eq:a11}
@@
   \begin{aligned}
-    i \hbar \pdv{\varphi(y',t)}{t}   =
-    \bigg[
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
-        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
-        &
+    i \hbar \pdv{\varphi(y',t)}{t} =&
+    \left[
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
+        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \right. \\
+        & \left. \qquad\qquad\qquad
         - L(\zeta,\dot{\zeta},t)
-    \bigg]\varphi(y',t).
+    \right]\varphi(y',t).
   \end{aligned}
@@
 \end{equation}
-and subtitling Eq.~(\ref{eq:a14}) back in Eq.~(\ref{eq:a12}) yields
+and subtitling Eq.~(\ref{eq:a14}) back in Eq.~(\ref{eq:a12}), we can obtain
 \begin{equation} \label{eq:a15}
     i \hbar \pdv{t} \chi(y',t)  =
-    \bigg[
+    \left(
         -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
         + \frac{1}{2} m_e \omega_0^2 {y'}^2
-    \bigg] \chi(y',t).
+    \right) \chi(y',t).
 \end{equation}
 This is the well-known Schrödinger equation of the quantum harmonic oscillator.
-This allows us to identify the well known eigenfunctions \cite{griffiths18,shankar94}
+This allows us to identify the well known eigenfunction solutions \cite{griffiths18,shankar94}
 \begin{equation} \label{eq:a16}
   \chi_n(y) =
-   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
+  \sqrt{\frac{\kappa}{2^{n}n!\sqrt{\pi}}}
   e^{-\kappa^2 y^2/2}
@@
   \begin{aligned}
-    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
-     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \epsilon_nt +
-    m_e\dot{\zeta(t)}\big[\tilde{y}-\zeta(t)\big] \\
-     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
+    \vartheta_n(\tilde{y},t) = \chi_n\bm{(}\tilde{y} - \zeta(t)\bm{)}
+     \text{exp}&
+     \left(
+     \frac{i}{\hbar}
+     \left\{
+     - \epsilon_nt +
+     m_e \left[\tilde{y}-\zeta(t)\right] \dot{\zeta(t)} \right. \right. \\
+     & \left. \left. \qquad
+     + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')
+     \right\}
+     \right).
   \end{aligned}
 \end{equation}
-Since $\chi_n(x)$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of the solutions derived in Eq.~(\ref{eq:a18}).
+Since $\chi_n(x)$ functions forms a complete set, any general solution for  $\vartheta_(\tilde{y},t)$ can be presented using the solutions derived in Eq.~(\ref{eq:a18}).
 

### 2021-08-19 paper/v2.0/sections/appendix_a.tex
Correction appA

@@
      & \left. \left. \qquad
-     + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')
+     + \int_0^{t}L(\zeta,\dot{\zeta},t') dt'
      \right\}
@@
 
-Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we derive the solution for Eq.~(\ref{eq:a11}) as
+Finally, we consider our scenario where we can assume that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq:a11}) as
 \begin{equation} \label{eq:a19}
@@
 \end{equation}
-Subtitling solutions in Eq.~(\ref{eq:a18}) back in Eq.~(\ref{eq:a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq:a4}) as follows
+Substituting solutions given in Eq.~(\ref{eq:a18}) back in Eq.~(\ref{eq:a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq:a4}) as follows
 \begin{equation} \label{eq:a20}
   \begin{aligned}
-    \psi_{n,m}&(x,y,t) \\
-    &=  \frac{1}{\sqrt{L_x}}
+    &\psi_{n,m}(x,y,t) \\
+    & \quad=  \frac{1}{\sqrt{L_x}}
     \chi_n\left(y - y_0 - \zeta(t)\right)\\
-    &\quad\times
-    \text{exp}\bigg(
-    \frac{i}{\hbar}\bigg[- \epsilon_nt
-    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
-    & \quad\quad+
-    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
-    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
+    &\qquad\times
+    \text{exp}\left(
+    \frac{i}{\hbar}
+    \left\{- \epsilon_nt
+    + p_x x
+    + \frac{eE(y - y_0)}{\omega}\cos(\omega t) \right. \right. \\
+    & \left. \left. \qquad\qquad +
+    m_e\left[y - y_0 -\zeta(t)\right] \dot{\zeta}(t)+
+    \int_0^{t}L(\zeta,\dot{\zeta},t') dt'
+    \right\}
+    \right).
   \end{aligned}

### 2021-08-19 paper/v2.0/sections/appendix_c.tex
Correct figure numbers
Correction appC

@@
-The Floquet-Fermi golden rule for our dressed quantum Hall system is derived  using the $t$-$t'$ formalism. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
-\begin{equation} \label{eq_c1}
+We derive the Floquet-Fermi golden rule for our dressed quantum Hall system with the help of the $t$-$t'$ formalism. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
+\begin{equation} \label{eq:c1}
   \ket{\psi_{n,m}(t,t')} =
@@
 \end{equation}
-are derived by separating the aperiodic and periodic components of the Floquet states given in Eq.~(\ref{eq_12}).
+are derived by separating the aperiodic and periodic components of the Floquet states given in Eq.~(\ref{eq:14}).
 Additionally, these states fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
-\begin{equation} \label{eq_c2}
+\begin{equation} \label{eq:c2}
   i \hbar \pdv{t}\ket{\psi_{n,m}(t,t')} =
@@
 \end{equation}
-where \textit{Floquet Hamiltonian} defined as
-\begin{equation} \label{eq_c3}
+where the \textit{Floquet Hamiltonian} defined as
+\begin{equation} \label{eq:c3}
   H_F(t') =
@@
 Next, we can identify the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation as
-\begin{equation} \label{eq_c4}
-  U_F(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\qty[t-t_0]).
+\begin{equation} \label{eq:c4}
+  U_F(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\left[t-t_0 \right]).
 \end{equation}
@@
 
-For our scenario, we take into account a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, and the $t$-$t'$-Schrödinger equation becomes
-\begin{equation} \label{eq_c5}
+We model the effect caused by impurities in the considered system as a single perturbation potential formed by a group of randomly distributed impurities.
+Thus, we introduce a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, and the $t$-$t'$-Schrödinger equation becomes
+\begin{equation} \label{eq:c5}
   i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')} =
-  \qty[H_F(t') + V(\vb{r})]\ket{\Psi_{n,m}(t,t')}.
+  \left[H_F(t') + V(\vb{r}) \right]\ket{\Psi_{n,m}(t,t')}.
 \end{equation}
-This introduces a new wave function solution $\ket{\Psi_{n,m}}$ for a system with a given perturbation. If $t\leq t_0$, both of the solutions for Eq.~(\ref{eq_c2}) and Eq.~(\ref{eq_c5}) coincide
-\begin{equation} \label{eq_c6}
+This introduces a new wave function solution $\ket{\Psi_{n,m}}$ for a system with a given perturbation. If $t\leq t_0$, both of the solutions for Eq.~(\ref{eq:c2}) and Eq.~(\ref{eq:c5}) coincide
+\begin{equation} \label{eq:c6}
   \ket{\psi_{n,m}(t,t')} =\ket{\Psi_{n,m}(t,t')} \quad
@@
 \end{equation}
-Next, our analysis can move into the interaction picture representation \cite{bruus04,mahan00} and in the interaction picture, the $t$-$t'$-Floquet state can be identified as
-\begin{equation} \label{eq_c7}
+Next, we can move our analysis into the interaction picture representation \cite{bruus04,mahan00} and in the interaction picture, the $t$-$t'$-Floquet state can be identified as
+\begin{equation} \label{eq:c7}
   \ket{\Psi_{n,m}(t,t')}_I = U_0^{\dagger}(t,t_0;t')
@@
 \end{equation}
-Due to time-independence, the perturbation in the interaction picture has the same form as Schrödinger picture representation
-\begin{equation} \label{eq_c8}
+Due to time-independence, the perturbation in the interaction picture has the same form as the Schrödinger picture representation
+\begin{equation} \label{eq:c8}
   V_I(\vb{r}) = U_0^{\dagger}(t,t_0;t')V(\vb{r})U_0(t,t_0;t') =
@@
 This leads us to the $t$-$t'$-Schrödinger equation in the interaction picture representation
-\begin{equation} \label{eq_c9}
+\begin{equation} \label{eq:c9}
   i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')}_I =
@@
 with the recursive solutions \cite{bruus04,mahan00}
-\begin{equation} \label{eq_c10}
+\begin{equation} \label{eq:c10}
   \begin{aligned}
@@
   \frac{1}{i\hbar}
-  \int_{t_0}^t dt_1 \;
-  V_I(\vb{r}) \ket{\Psi_{n,m}(t_1,t')}_I.
+  \int_{t_0}^t
+  V_I(\vb{r}) \ket{\Psi_{n,m}(t_1,t')}_I dt_1.
   \end{aligned}
@@
 Iterating the solution only up to the first order (Born approximation) we obtain
-\begin{equation} \label{eq_c11}
+\begin{equation} \label{eq:c11}
   \begin{aligned}
@@
     \frac{1}{i\hbar}
-    \int_{t_0}^t dt_1 \;
-    V_I(\vb{r}) \ket{\psi_{n,m}(t_0,t')}.
+    \int_{t_0}^t
+    V_I(\vb{r}) \ket{\psi_{n,m}(t_0,t')} dt_1.
   \end{aligned}
@@
 
-Since our $t$-$t'$-Floquet states create a basis, we can represent solutions for the $t$-$t'$-Schrödinger equation given in Eq.~(\ref{eq_c5}) using our known $t$-$t'$-Floquet states
-\begin{equation} \label{eq_c12}
+Since our $t$-$t'$-Floquet states create a basis, we can represent the solutions for the $t$-$t'$-Schrödinger equation given in Eq.~(\ref{eq:c5}) using our known $t$-$t'$-Floquet states as follows
+\begin{equation} \label{eq:c12}
   \ket{\Psi_{\alpha}(t,t')} = \sum_{\beta} a_{\alpha,\beta}(t,t')
@@
 \braket{\psi_{\beta}(t,t')}{\Psi_{\alpha}(t,t')}$ and this can be evaluated with
-\begin{equation} \label{eq_c13}
+\begin{equation} \label{eq:c13}
   \begin{aligned}
@@
   \frac{1}{i\hbar}
-  \int_{t_0}^t dt_1 \;
+  \int_{t_0}^t
   \bra{\psi_{\beta}(t_1,t')}
-  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')}.
+  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
   \end{aligned}
@@
 Since the $t$-$t'$-Floquet states are orthonormal and assuming $t_0 = 0$ and $\alpha \neq \beta$ this leads to
-\begin{equation} \label{eq_c14}
+\begin{equation} \label{eq:c14}
   a_{\alpha,\beta}(t,t') =
@@
   \frac{i}{\hbar}
-  \int_{0}^t dt_1 \;
+  \int_{0}^t
   \bra{\psi_{\beta}(t_1,t')}
-  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')}.
+  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
 \end{equation}
@@
 Next, we consider a scattering phenomenon when a electron scatters from a known $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with a constant quansienergy $\varepsilon$ as follows
-\begin{equation} \label{eq_c15}
+\begin{equation} \label{eq:c15}
   \begin{aligned}
@@
 \begin{figure}[b]
-  \includegraphics[scale=1.0]{figures/fig_2.pdf}
+  \includegraphics[scale=1.0]{figures/fig_6.pdf}
   \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
-  \label{fig_2}
+  \label{fig:2}
 \end{figure}
-This scenario is illustrated in Fig.~\ref{fig_2}.
-The scattering amplitude for this scattering scenario can be calculated using the equation derived in Eq.~(\ref{eq_c14})
-\begin{equation} \label{eq_c16}
+This scenario is illustrated in Fig.~\ref{fig:2}.
+The scattering amplitude for this scattering scenario can be calculated using the expression derived in Eq.~(\ref{eq:c14}) as follows
+\begin{equation} \label{eq:c16}
   \begin{aligned}
@@
     -\frac{i}{\hbar}
-    \int_{0}^t dt_1 \;
-    e^{\frac{i}{\hbar}\qty(\varepsilon_{\beta} - \varepsilon)t_1}
+    \int_{0}^t
+    e^{\frac{i}{\hbar}\left(\varepsilon_{\beta} - \varepsilon \right)t_1}
     \bra{\phi_{\beta}(t')}
-    V(\vb{r}) \ket{\phi_{\alpha}(t')}.
+    V(\vb{r}) \ket{\phi_{\alpha}(t')}  dt_1.
   \end{aligned}
 \end{equation}
-By assuming for a long time $t \rightarrow \infty$, we can turn this integral into a delta distribution
-\begin{equation} \label{eq_c17}
+By assuming for a long duration ($t \rightarrow \infty$), we can turn this integral into a delta distribution
+\begin{equation} \label{eq:c17}
   \begin{aligned}
@@
 \end{equation}
-where $Q = \bra{\phi_{\beta}(t')}
-V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using the completeness properties we can re-write this as
-\begin{equation} \label{eq_c18}
+where $Q = \bra{\phi_{\beta}(t')} V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using the completeness properties we can re-write this as
+\begin{equation} \label{eq:c18}
     Q =
@@
 Moreover, separating $x$-directional and $y$-directional momentum components, this can be simplified as
-\begin{equation} \label{eq_c19}
+\begin{equation} \label{eq:c19}
     Q =
     \sum_{k_x}\sum_{{k'}_x}
-    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} dk_y d{k'}_y \;
+    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
     V_{\vb{k'},\vb{k}}
     \phi_{\beta}^{\dagger}(\vb{k'},t')
-    \phi_{\alpha}(\vb{k},t'),
+    \phi_{\alpha}(\vb{k},t')  dk_y d{k'}_y,
 \end{equation}
-with $V_{\vb{k'},\vb{k}} \equiv \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.
+with $V_{\vb{k'},\vb{k}} = \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.
 
@@
 Then scattering potential $V(\vb{r})$ can be identified as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
-\begin{equation} \label{eq_c20}
-  V(\vb{r}) \equiv
+\begin{equation} \label{eq:c20}
+  V(\vb{r}) =
   \sum_{i=1}^{N_{imp}}
@@
 Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
-This model is characterized by \cite{akkermans10}
+This model is characterized by the following two equations \cite{akkermans10}
 \begin{subequations}
-\begin{equation} \label{eq_c21a}
+\begin{equation} \label{eq:c21a}
   \expval{\upsilon(\vb{r})}_{imp} =0,
 \end{equation}
-\begin{equation} \label{eq_c21b}
+\begin{equation} \label{eq:c21b}
   \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
@@
 Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
-\begin{equation} \label{eq_c22}
+\begin{equation} \label{eq:c22}
   \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
@@
 where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
-\begin{equation} \label{eq_c23}
+\begin{equation} \label{eq:c23}
   V(\vb{r}) =
@@
 Furthermore, we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
-\begin{subequations} \label{eq_c24}
+\begin{subequations} \label{eq:c24}
 \begin{align}
@@
  \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
- \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq_c24a} \\
+ \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq:c24a} \\
  & =
  \sum_{i=1}^{N_{imp}}
- \int_{-\infty}^{\infty} dy\; \bigg[
- \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \\
- & \quad\times \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
- \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \bigg] \label{eq_c24b} \\
+ \int_{-\infty}^{\infty} \left[
+ \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \right. \\
+ & \left. \qquad\quad\times
+ \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
+ \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \right] dy \label{eq:c24b} \\
   & =
@@
  e^{i(k'_y - k_y )y}
- \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq_c24c}.
+ \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq:c24c}.
 \end{align}
@@
 Additionally, assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
-\begin{subequations} \label{eq_c25}
+\begin{subequations} \label{eq:c25}
   \begin{align}
@@
     V_{k'_x,k_x}
-    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty} dy_i\;
-    e^{i\qty({k'}_y - k_y)y_i} \label{eq_c25a} \\
+    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty}
+    e^{i\left({k'}_y - k_y \right)y_i} dy_i \label{eq:c25a} \\
     & =
-    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y). \label{eq_c25b}
+    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y). \label{eq:c25b}
   \end{align}
@@
 In the above equation we introduced
-\begin{equation} \label{eq_c26}
-  V_{{k'}_x,k_x} \equiv
+\begin{equation} \label{eq:c26}
+  V_{{k'}_x,k_x} =
   \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x},
 \end{equation}
-which is a constant value for every $i$ impurity. Moreover, $\eta_{imp}$ is the number of impurities in a unit area. It is important to note that $\braket{x}{k_x} = e^{-ik_xx}$.
+which is a constant value for every $i$-th impurity.
+Moreover, $\eta_{imp}$ is the number of impurities in a unit area.
+It is important to note that in the above expression $\braket{x}{k_x} = e^{-ik_xx}$.
 
-Now using Eq.~(\ref{eq_9}) and Eq.~(\ref{eq_c25b}) on Eq.~(\ref{eq_c19}), we obtain
-\begin{equation} \label{eq_c27}
+Now using Eq.~(\ref{eq:10}) and Eq.~(\ref{eq:c25b}) on Eq.~(\ref{eq:c19}), we obtain
+\begin{equation} \label{eq:c27}
   \begin{aligned}
-    Q & =
-    \sum_{k_x}\sum_{{k'}_x}
-    {\eta_{imp} V_{{k'}_x,k_x}}
-    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} dk_y d{k'}_y \;
+    Q  =
+    \sum_{k_x}\sum_{{k'}_x} &
+    {\eta_{imp} V_{{k'}_x,k_x}} L_x
+    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
     \delta({k'}_y - k_y)
     \\
-    & \quad\times
-    \sqrt{L_x}
-    \exp(
-      i{k'}_y  \qty[d\sin(\omega t) + {y'}_0]
-    )
-    \tilde{\chi}_{n_{\beta}}\qty({k'}_y -b\cos(\omega t))
+    & \times
+    \widetilde{\chi}_{n_{\beta}} \bm{\left(} {k'}_y -b\cos(\omega t) \bm{\right)}
+    \widetilde{\chi}_{n_{\alpha}}  \bm{\left(}k_y -b\cos(\omega t) \bm{\right)}
     \\
-    & \quad\times
-    \sqrt{L_x}
-    \exp(
-      -ik_y  \qty[d\sin(\omega t) + y_0]
-    )
-    \tilde{\chi}_{n_{\alpha}}\qty(k_y -b\cos(\omega t)).
+    & \times
+    e^{i[{k'}_y - k_y]d\sin(\omega t)}
+    e^{i[{k'}_y {y'}_0 - k_y y_0]}
+     dk'_y dk_y.
   \end{aligned}
@@
 Here we have changed the time variable $t' \rightarrow t$ only for the simplicity of notation. This can be simplified as
-\begin{equation} \label{eq_c28}
+\begin{equation} \label{eq:c28}
   \begin{aligned}
     Q =
-    \sum_{k_x}\sum_{{k'}_x}
-    {\eta_{imp} L_x V_{{k'}_x,k_x}} I,
+    \sum_{k_x}\sum_{{k'}_x} \eta_{imp} L_x V_{{k'}_x,k_x} I,
   \end{aligned}
@@
 with
-\begin{equation} \label{eq_c29}
+\begin{equation} \label{eq:c29}
   \begin{aligned}
     I =
-    \int_{-\infty}^{\infty} dk_y \;
-    \tilde{\chi}_{n_{\beta}}\qty(k_y -b\cos(\omega t)) &
-    \tilde{\chi}_{n_{\alpha}}\qty(k_y -b\cos(\omega t)) \\
+    \int_{-\infty}^{\infty}
+    \widetilde{\chi}_{n_{\beta}} &\bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
+    \widetilde{\chi}_{n_{\alpha}} \bm{\left(} k_y -b\cos(\omega t) \bm{\right)} \\
     & \times
-    \exp(
-      -ik_y  \qty[y_0 - {y'}_0  ]
-    ).
+    \exp \bm{(}
+      -ik_y  \left(y_0 - {y'}_0 \right)
+    \bm{)} dk_y.
   \end{aligned}
@@
 Therefore, in this study we assume that the dressing field can only renormalize the the probability of electron scattering inside a same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
-This transform the Eq.~(\ref{eq_c29}) to
-\begin{equation} \label{eq_c30}
+This transform the Eq.~(\ref{eq:c29}) to
+\begin{equation} \label{eq:c30}
     I =
-    \int_{-\infty}^{\infty} dk_y \;
-    \tilde{\chi}_{N}^2 \qty(k_y -b\cos(\omega t))
-    \exp(
-      -ik_y  \qty[y_0 - {y'}_0  ]
-    ).
+    \int_{-\infty}^{\infty}
+    \widetilde{\chi}_N^2 \bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
+    \exp \bm{(}
+      -ik_y  \left(y_0 - {y'}_0 \right)
+    \bm{)} dk_y.
 \end{equation}
 Using the Fourier transform of Gauss-Hermite functions \cite{celeghini21} and the convolution theorem \cite{arfken85,bracewell78} we obtain
-\begin{equation} \label{eq_c31}
+\begin{equation} \label{eq:c31}
   \begin{aligned}
@@
     {2\pi} &
-    \exp(b[{y'}_0 - y_0]\cos(\omega t)) \\
+    \exp \bm{(} b({y'}_0 - y_0)\cos(\omega t) \bm{)} \\
     & \times
-    \int_{-\infty}^{\infty} dy \;
-    {\chi}_{N}\qty(y)
-    {\chi}_{N}\qty(y_0 - {y'}_0 - y).
+    \int_{-\infty}^{\infty}
+    {\chi}_{N}(y)
+    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
   \end{aligned}
 \end{equation}
-Finally, the scattering amplitude derived in Eq.~(\ref{eq_c17}) can be evaluated for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as
-\begin{equation} \label{eq_c32}
+Finally, the scattering amplitude derived in Eq.~(\ref{eq:c17}) can be evaluated for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as
+\begin{equation} \label{eq:c32}
   \begin{aligned}
-    a_{\alpha\beta}(k_x,k'_x,t)  =&
+    a_{\alpha\beta}&(k_x,k'_x,t)
+    \\
+    & =
     -2\pi i
     \eta_{imp} L_x V_{{k'}_x,k_x}
-    \delta(\varepsilon_{N} - \varepsilon)\\
-    & \times
-    \exp(b[{y'}_0 - y_0]\cos(\omega t))\\
-    & \times
-    \int_{-\infty}^{\infty} dy \;
-    {\chi}_{N}\qty(y)
-    {\chi}_{N}\qty(y_0 - {y'}_0 - y).
+    e^{ b({y'}_0 - y_0)\cos(\omega t)}\\
+    & \quad\times
+    \delta(\varepsilon_{N} - \varepsilon)
+    \int_{-\infty}^{\infty}
+    {\chi}_{N}(y)
+    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
   \end{aligned}
 \end{equation}
-Since this scattering amplitude is time-periodic we can write this as a Fourier series expansion
-\begin{equation} \label{eq_c33}
+Since this scattering amplitude is time-periodic, we can write this as a Fourier series expansion
+\begin{equation} \label{eq:c33}
     a_{\alpha\beta}(k_x,k'_x,t) =
@@
 In addition, using Jacobi-Anger expansion \cite{cuyt08,abramowitz64}
-\begin{equation} \label{eq_c34}
-    e^{iz\cos(\theta)} = \sum_{l=-\infty}^{\infty} i^l J_l\qty(z) e^{-il\theta},
+\begin{equation} \label{eq:c34}
+    e^{iz\cos(\theta)} = \sum_{l=-\infty}^{\infty} i^l J_l(z) e^{-il\theta},
 \end{equation}
-where $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, we can re-write the Eq.~(\ref{eq_c32}) as follows
-\begin{equation} \label{eq_c35}
+where $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, we can re-write the Eq.~(\ref{eq:c32}) as follows
+\begin{equation} \label{eq:c35}
   \begin{aligned}
-    a_{\alpha\beta}(k_x,k'_x,t)  = &
+    a_{\alpha\beta}&(k_x,k'_x,t)  \\
+    & =
     \sum_{l=-\infty}^{\infty}
@@
     \eta_{imp} L_x V_{{k'}_x,k_x}
-    \delta(\varepsilon_{N} - \varepsilon)\\
-    & \times
-    J_l\qty(b[{y'}_0 - y_0]) \\
-    & \times
-    \int_{-\infty}^{\infty} dy \;
-    {\chi}_{N}\qty(y)
-    {\chi}_{N}\qty(y_0 - {y'}_0 - y) e^{-il\omega t}.
+    J_l\bm{(}b({y'}_0 - y_0)\bm{)} \\
+    & \quad\times
+    \delta(\varepsilon_{N} - \varepsilon)
+    \int_{-\infty}^{\infty}
+    {\chi}_{N}(y)
+    {\chi}_{N}(y_0 - {y'}_0 - y)  dy \;e^{-il\omega t}.
   \end{aligned}
@@
 Thus, we can identify the Fourier series component of the scattering amplitude as
-\begin{equation} \label{eq_c36}
+\begin{equation} \label{eq:c36}
   \begin{aligned}
@@
     \delta(\varepsilon_{N} - \varepsilon)
-    J_l\qty(b[{y'}_0 - y_0])\\
+    J_l\bm{(}b({y'}_0 - y_0)\bm{)}\\
     & \times
-    \int_{-\infty}^{\infty} dy \;
-    {\chi}_{n_{\beta}}\qty(y)
-    {\chi}_{n_{\beta}}\qty(y_0 - {y'}_0 - y).
+    \int_{-\infty}^{\infty}
+    {\chi}_{n_{\beta}}(y)
+    {\chi}_{n_{\beta}}(y_0 - {y'}_0 - y) dy.
   \end{aligned}
 \end{equation}
-Furthermore, we define \textit{transition probability matrix} as
-\begin{equation} \label{eq_c37}
-    \qty(A_{\alpha\beta})^{l,l'} \equiv
-    a^l_{\alpha\beta}\qty[a^{l'}_{\alpha\beta}]^{*},
+Furthermore, we can define \textit{transition probability matrix} as
+\begin{equation} \label{eq:c37}
+    \left(A_{\alpha\beta} \right)^{l,l'} =
+    a^l_{\alpha\beta}\left[a^{l'}_{\alpha\beta} \right]^{*},
 \end{equation}
 and this becomes
-\begin{equation} \label{eq_c38}
+\begin{equation} \label{eq:c38}
   \begin{aligned}
-      \qty(A_{\alpha\beta})^{l,l'}(k_x,k'_x) = &
-      \qty[{ 2 \pi \eta_{imp} L_x |V_{{k'}_x,k_x}|}]^2
+      \left(A_{\alpha\beta} \right)^{l,l'}(k_x,k'_x) = &
+      \left({ 2 \pi \eta_{imp} L_x V_{{k'}_x,k_x}}\right)^2
       \delta^2(\varepsilon_{N} - \varepsilon) \\
       & \times
-      J_l\qty(b[{y'}_0 - y_0]) J_{l'}\qty(g[{y'}_0 - y_0])\\
+      J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)}\\
       & \times
-      \qty|
-      \int_{-\infty}^{\infty} dy \;
-      {\chi}_{n_{\beta}}\qty(y)
-      {\chi}_{n_{\beta}}\qty(y_0 - {y'}_0 - y)|^2.
+      \left|
+      \int_{-\infty}^{\infty}
+      {\chi}_{n_{\beta}}(y)
+      {\chi}_{n_{\beta}}(y_0 - {y'}_0 - y) dy \right|^2.
   \end{aligned}
@@
 Then describing the square of the delta distribution using the following interpretation \cite{dini16,kibis14}
-\begin{equation} \label{eq_c39}
+\begin{equation} \label{eq:c39}
     \delta^2(\varepsilon) =
@@
 and executing the time derivation operation on each matrix element of transition probability matrix, we receive the \textit{transition amplitude matrix} elements
-\begin{equation} \label{eq_40}
+\begin{equation} \label{eq:40}
   \begin{aligned}
@@
     & \times
-    J_l\qty(b[{y'}_0 - y_0]) J_{l'}\qty(g[{y'}_0 - y_0]) \\
+    J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)} \\
     & \times
-    \qty|
-    \int_{-\infty}^{\infty} dy \;
-    {\chi}_{N}\qty(y)
-    {\chi}_{N}\qty(y_0 - {y'}_0 - y)|^2.
+    \left|
+    \int_{-\infty}^{\infty}
+    {\chi}_{n_{\beta}}(y)
+    {\chi}_{n_{\beta}}(y_0 - {y'}_0 - y) dy \right|^2.
   \end{aligned}
@@
 Additionally, the inverse scattering time matrix can be identified as the sum of all available momentum over the impurity averaged transition probability matrix element \cite{wackerl20,wackerlthesis20}
-\begin{equation} \label{eq_41}
-    \qty(\frac{1}{\tau(\varepsilon,k_x)})^{ll'}_{\alpha\beta} =
+\begin{equation} \label{eq:41}
+    \left(\frac{1}{\tau(\varepsilon,k_x)} \right)^{ll'}_{\alpha\beta} =
     \frac{1}{L_x} \sum_{{k'}_x}
@@
 Next, applying the 1-dimensional momentum continuum limit $\sum_{{k'}_x} \longrightarrow {L_x}/{2\pi}\int d {k'}_x$, we can obtain
-\begin{equation} \label{eq_42}
+\begin{equation} \label{eq:42}
   \begin{aligned}
-    \bigg(&\frac{1}{\tau(\varepsilon,k_x)}\bigg)^{ll'}_{\alpha\beta} \\
+    &\left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_{\alpha\beta} \\
     & =
@@
     \delta(\varepsilon_{\beta} - \varepsilon)\\
-    & =
-    \int_{-\infty}^{\infty} d {k'}_x
-    J_l\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x])
-    J_{l'}\qty(\frac{b\hbar}{eB}[{k}_x - {k'}_x]) \\
     & \quad\times
-    \qty|
-    \int_{-\infty}^{\infty} dy \;
-    {\chi}_{n_{\beta}}\qty(y)
-    {\chi}_{n_{\beta}}\qty(\frac{\hbar}{eB} \qty[{k'}_x - {k}_x] - y)|^2.
+    \int_{-\infty}^{\infty} \left\{
+    J_l\bm{(}\frac{b\hbar}{eB}[{k}_x - {k'}_x]\bm{)}
+    J_{l'}\bm{(}\frac{b\hbar}{eB}[{k}_x - {k'}_x]\bm{)} \right. \\
+    & \left. \qquad\times
+    \left|
+    \int_{-\infty}^{\infty}
+    {\chi}_{n_{\beta}}(y)
+    {\chi}_{n_{\beta}} \bm{\left(}\frac{\hbar}{eB} ({k'}_x - {k}_x) - y \bm{\right)} dy\right|^2 \right\} d {k'}_x.
   \end{aligned}
@@
 Here an impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2}_{imp} = V_{imp}$.
-Finally, using substitutions $k'_x = k_1$ and $y = {\hbar{k_2}}/{eB}$, we can derive our expression for the inverse scattering time matrix for $N$-th Landau
+Finally, using substitutions $k'_x = k_1$ and $y = \flatfrac{\hbar{k_2}}{(eB)}$, we can derive our expression for the inverse scattering time matrix for $N$-th Landau
 level as follows
-\begin{equation} \label{eq_43}
+\begin{equation} \label{eq:43}
   \begin{aligned}

### 2021-08-19 paper/v2.0/sections/4_inverse_scattering_time.tex
Correct figure numbers
Correct font size in figures
Correction appC and theory correction

@@
     \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
-    \frac{ \varrho^2}{eB} \delta(\varepsilon - \varepsilon_N) \\
+    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
     & \times
@@
 \end{widetext}
-where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{(eB)}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
+where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
 A more detailed derivation is given in Appendix \ref{appendix_c}.
@@
  \Gamma^{00}_{N}(\varepsilon,k_x) =
- \hbar \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{00}_N,
+ \hbar \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{00}_N.
 \end{equation}
-which simplifies to
+We can evaluate this as
 \begin{widetext}
@@
      &\Gamma^{00}_{N} (\varepsilon,k_x) =
-     \frac { \varrho^2}{eB}
+     \frac{ \pi \hbar^2 \varrho^2}{e^2B^2}
      \delta(\varepsilon - \varepsilon_{N})
@@
 \begin{figure}[h!]
-\includegraphics[scale=0.68]{figures/fig_3}
+\includegraphics[scale=0.55]{figures/fig_2}
 \caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t!]
-\includegraphics[scale=0.68]{figures/fig_4}
+\includegraphics[scale=0.55]{figures/fig_3}
 \caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.

### 2021-08-19 paper/v2.0/sections/appendix_d.tex
Correct appD

@@
 In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system.
-We already found the exact solution for our time-dependent Hamiltonian give in Eq.~(\ref{eq_1}) and we identified them as the Floquet states in Eq.~(\ref{eq_12}).
-The Floquet modes derived in Eq.~(\ref{eq_9}) can be represented as quantum states using their corresponding quantum numbers for the simplicity of notation as follows
-\begin{equation} \label{eq_d1}
+We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(\ref{eq:1}) and we identified them as the Floquet states in Eq.~(\ref{eq:14}).
+For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(\ref{eq:10}) as quantum states using their corresponding quantum numbers as follows
+\begin{equation} \label{eq:d1}
   \ket{\phi_{n,m}} = \ket{n,k_x}.
@@
 Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
-\begin{equation} \label{eq_d2}
-  \qty(\vb{j})_{nm,n'm'} \equiv \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
+\begin{equation} \label{eq:d2}
+  \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
 \end{equation}
-Thus, the particle current operator for our system \cite{mahan00,bruus04} can be identified as
-\begin{equation} \label{eq_d3}
-  \hat{\vb{j}} = \frac{1}{\widetilde{m}} \qty(\hat{\vb{p}} - e\qty[\vb{A}_s + \vb{A}_d(t)]),
+Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
+\begin{equation} \label{eq:d3}
+  \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
 \end{equation}
@@
 
-First, we consider the $x$-directional current operator component, and we can identify that the $x$-directional current operator as
-\begin{equation} \label{eq_d4}
-  \hat{j}_x = \frac{1}{\widetilde{m}} \qty(-i\hbar\pdv{x} + eBy).
+First, we consider the $x$-directional particle current operator component, and we can identify that as
+\begin{equation} \label{eq:d4}
+  \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
 \end{equation}
-Next, we calculate the matrix elements of $x$-directional current operator in Floquet mode basis
-\begin{equation} \label{eq_d5}
-  \qty({j}_x)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \qty(-i\hbar\pdv{x} + eBy)\;}{n',k'_x},
+Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
+\begin{equation} \label{eq:d5}
+  \left({j}_x \right)_{nm,n'm'} =
+  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
 \end{equation}
-and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq_7}) as follows
-\begin{equation} \label{eq_d6}
+and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq:7}) as follows
+\begin{equation} \label{eq:d6}
   \begin{aligned}
-    \qty({j}_x)_{nm,n'm'} = &
+    \left({j}_x \right)_{nm,n'm'} = &
     \frac{1}{{\widetilde{m}}}
     \delta_{k_x,k'_x}
-    \int dy \;
-    \Big[
-    \qty[\hbar k'_x + eBy] \\
+    \int
+    \left(\hbar k'_x + eBy\right) \\
     & \times
-     \chi_{n}\big(y - y_0 - \zeta(t)\big)
-    \chi_{n'}\big(y - y_0 - \zeta(t)\big)
-    \Big].
+     \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
+    \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
+    dy.
   \end{aligned}
 \end{equation}
-Let $(y - y_0 - \zeta(t)) = \bar{y}$ and we can obtain
-\begin{equation} \label{eq_d7}
+Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
+\begin{equation} \label{eq:d7}
   \begin{aligned}
-    \qty({j}_x)_{nm,n'm'} =
+    \left({j}_x \right)_{nm,n'm'} =
     \frac{1}{{\widetilde{m}}}
     \delta_{k_x,k'_x}
-    \int d\bar{y} \;
-    \Big[ &
-    \qty[\hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)] \\
+    \int &
+    \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right] \\
     & \times
@@
     \chi_{n'}(\bar{y})
-    \Big].
+    d\bar{y}.
   \end{aligned}
@@
 Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
-\begin{subequations} \label{eq_d8}
+\begin{subequations} \label{eq:d8}
   \begin{align}
-    \int d{y} \;
+    \int
     \chi_{n}({y})
-    \chi_{n'}({y}) &=
+    \chi_{n'}({y}) d{y} &=
     \delta_{n',n}, \\
-    \int dy \;
-    y
-    \chi_{n}({y})
-    \chi_{n'}({y}) &=
-    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-    \delta_{n',n-1}),
+    \int
+    y \chi_{n}({y})\chi_{n'}({y}) d{y} &=
+    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1} \right),
   \end{align}
@@
 we simplify the matrix elements of $x$-directional current operator to obtain
-\begin{equation} \label{eq_d9}
+\begin{equation} \label{eq:d9}
   \begin{aligned}
-    \qty({j}_x)&_{nm,n'm'} =
-    \frac{1}{{\widetilde{m}}}
-    \delta_{k_x,k'_x}
-    eB\\
-    & \times
-    \bigg[
-    \bigg(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-    \delta_{n',n-1}\bigg)
+    &\left({j}_x \right)_{nm,n'm'} =
+    \frac{eB}{{\widetilde{m}}}
+    \delta_{k_x,k'_x} \\
+    & \qquad\times
+    \left[
+    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1}\right)
     + \zeta(t) \delta_{n',n}
-    \bigg].
+    \right].
   \end{aligned}
 \end{equation}
-Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we identify the $0$-th component of the Fourier series as
-\begin{equation} \label{eq_d10}
+Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
+\begin{equation} \label{eq:d10}
   \begin{aligned}
-      \qty({j}^x_{s=0})_{nm,n'm'} =&
-      \frac{eB}{{\widetilde{m}}}
+      \left({j}_x \right)_{nm,n'm'} =&
+      \frac{eB}{\widetilde{m}}
       \delta_{k_x,k'_x} \\
       & \times
-      \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-      \delta_{n',n-1}).
+      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+      \delta_{n',n-1} \right).
   \end{aligned}
@@
 For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
-\begin{equation} \label{eq_d11}
+\begin{equation} \label{eq:d11}
   \begin{aligned}
@@
       & \times
-      \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-      \delta_{n',n-1}).
+      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+      \delta_{n',n-1} \right).
   \end{aligned}
@@
 Moreover, we can identify the $y$-directional current operator component as
-\begin{equation} \label{eq_d12}
-  \hat{j}_y = \frac{1}{\widetilde{m}} \qty(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t)).
+\begin{equation} \label{eq:d12}
+  \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
 \end{equation}
 Using this operator, the matrix elements of $y$-directional current operator in Floquet mode basis can be represented as
-\begin{equation} \label{eq_d13}
-  \qty({j}_y)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))\;}{n',k'_x}.
+\begin{equation} \label{eq:d13}
+  \left({j}_y \right)_{nm,n'm'} =
+  \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
 \end{equation}
 After following the same steps done for the $x$-directional current operator, we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
-\begin{equation} \label{eq_d14}
+\begin{equation} \label{eq:d14}
   \begin{aligned}
@@
     & \times
-    \qty[
+    \left(
     \sqrt{\frac{n}{2}} \delta_{n',n-1}
     - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
-    ].
+    \right).
   \end{aligned}

### 2021-08-19 paper/v2.0/sections/1_introduction.tex
Add new citations

@@
 Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century.
-Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
+Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo15,pirandola18,hapuarachchi2018}, energy harvesting \cite{weeraddana15,yuan16,sun18},
 quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
-The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, and quantum cavity physics \cite{tsang10,devi20}.
+The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{chow13,jayasekara16,premaratne17}, and quantum cavity physics \cite{tsang10,liu17,devi20}.
 However, in recent years, one of the foremost aim of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.

### 2021-08-20 paper/v2.0/sections/1_introduction.tex
Final corrections
Passive voice corrections

@@
 
-In contrast, more exciting phenomena can be observed by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
+In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
 Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport.

### 2021-08-20 paper/v2.0/sections/3_floquet_theory.tex
Correction sec3 and sec4
Passive voice corrections

@@
 First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq:2}).
-By factorizing the wave function into a linearly time-dependent part and a periodic time-dependent part, we present the quasienergies as
+By factorizing the wave function into a linearly time-dependent part and a periodic time-dependent part, we present the quasienergies with
 \begin{equation} \label{eq:6}
   \varepsilon_{n} =
-  \hbar \omega_0 \left(n + \frac{1}{2}\right) - \Delta_{\varepsilon},
+  \hbar \omega_0 \left(n + \flatfrac{1}{2}\right) - \Delta_{\varepsilon},
 \end{equation}
-which only depends on a single quantum number $n$. The Floquet modes can then be recognized as
+which only depends on a single quantum number $n$. Furthermore, we can recognize the Floquet modes as
 \begin{equation} \label{eq:7}
@@
 \end{equation}
-Using Floquet theory, the wave functions derived in Eq.~(\ref{eq:2}) can be written as Floquet states in momentum space as
+Using Floquet theory, we can re-write the wave functions derived in Eq.~(\ref{eq:2}) as the \textit{Floquet states} in momentum space
 \begin{equation} \label{eq:14}

### 2021-08-20 paper/v2.0/sections/4_inverse_scattering_time.tex
Final corrections
Passive voice corrections

@@
 Since random impurities in a disordered metal offer a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
-Thus, the total scattering potential in the 2DEG has been represented as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
 Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
@@
 \end{equation}
-Then we write the central element of inverse scattering time matrix in the more compact form
+Subsequently, we write the central element of inverse scattering time matrix in the more compact form
 \begin{equation} \label{eq:19}
@@
 \end{equation}
-which can be evaluated with
+which we can evaluate with
 \begin{equation} \label{eq:21}
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \includegraphics[scale=0.55]{figures/fig_2}
@@
 \begin{figure}[t!]
-\includegraphics[scale=0.55]{figures/fig_3}
+\includegraphics[scale=0.54]{figures/fig_3}
 \caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
@@
 
-Normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) has been calculated for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
+Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~(\ref{fig_3}) and Fig.~(\ref{fig_4}).
 To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.

### 2021-08-20 paper/v2.0/sections/5_floquet_drude_conductivity.tex
Corrections
Passive voice corrections

@@
 Next, we restrict our analysis into the off-resonant regime $\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system.
-Thus, the $x$-directional longitudinal conductivity given in
-Eq.~(\ref{eq:22}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} = \ket{n,k_x}$ as
+Thus, we can expand the $x$-directional longitudinal conductivity given in
+Eq.~(\ref{eq:22}) using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} = \ket{n,k_x}$ as
 \begin{widetext}
@@
 For the full derivation of electric current operators in a quantum Hall system, refer to Appendix \ref{appendix_d}.
-After the expansion, the only non-zero term would be
+After the expansion, we can identify the the only non-zero term as follows
 \begin{equation} \label{eq:29}
@@
 In addition, on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20}.
-Subsequenty, we can identify the following property
+Subsequently, we can identify the following property
 \begin{equation} \label{eq:30}
@@
 \end{equation}
-Moreover, let $\Pi = \varepsilon_F$ and the derived expression in \ref{eq:31} leads to
+Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
 \begin{equation} \label{eq:35}

### 2021-08-20 paper/v2.0/sections/appendix_a.tex
Correction appB
Passive voice corrections

@@
 \end{equation}
-This leads to
+and this leads to
 \begin{equation} \label{eq:a10}
@@
         \right]y'
-    \right\} \varphi(y',t),
+    \right\} \varphi(y',t).
   \end{aligned}
 \end{equation}
-where we introduce $\dot{\zeta} = \dv*{\zeta}{t}$ and $\ddot{\zeta} = \dv*[2]{\zeta}{t}$ for the sake of notational convenience. Subsequently, we can restrict $\zeta(t)$ function such that
+Here, we introduced $\dot{\zeta} = \pdv*{\zeta}{t}$ and $\ddot{\zeta} = \pdv*[2]{\zeta}{t}$ for the sake of notational convenience. Subsequently, we can restrict $\zeta(t)$ function such that
 \begin{equation} \label{eq:a11}
@@
 \end{equation}
-is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
+is the Lagrangian of a classical driven oscillator. To proceed further, we introduce another unitary transform as follows
 \begin{equation} \label{eq:a14}
-    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
+    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t} L(\zeta,\dot{\zeta},t')dt') \chi(y',t),
 \end{equation}
@@
 \end{equation}
-Since $\chi_n(x)$ functions forms a complete set, any general solution for  $\vartheta_(\tilde{y},t)$ can be presented using the solutions derived in Eq.~(\ref{eq:a18}).
+Since $\chi_n(x)$ functions forms a complete set, we can present any general solution for  $\vartheta_(\tilde{y},t)$ using the solutions derived in Eq.~(\ref{eq:a18}).
 

### 2021-08-20 paper/v2.0/sections/5_floquet_drude_conductivity.tex
Spelling check

@@
 where $j^x_0$ is the $x$-directional electric current operator matrix elements' $0$-th Fourier component.
-Here, $\vb{G}^{r}(\varepsilon)$ and $\vb{G}^{a} (\varepsilon)$ are the retarted and advanced white noise disorder averaged Floquet Green function matrices \cite{wackerl20,wackerlthesis20}, respectively.
+Here, $\vb{G}^{r}(\varepsilon)$ and $\vb{G}^{a} (\varepsilon)$ are the retarded and advanced white noise disorder averaged Floquet Green function matrices \cite{wackerl20,wackerlthesis20}, respectively.
 These matrices are defined against the Floquet modes of the considering system.
@@
 \end{equation}
-Aterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in Eq.~(\ref{eq:29}) as follows
+Afterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in Eq.~(\ref{eq:29}) as follows
 \begin{equation} \label{eq:31}

### 2021-08-20 paper/v2.0/sections/6_manipulate_conductivity.tex
Correction appB
Final corrections
Passive voice corrections
Spelling check

@@
 To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
-We can identifiy the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
+We can identify the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
 \begin{equation}\label{eq:37}
@@
 \end{equation}
-with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and this can be expressed as
+with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and we can express this as
 \begin{equation} \label{eq:38}
@@
     \sum_{n}
-    \frac{(n+1)}{\alpha^2 \Lambda_n \Lambda_{n+1}} \\
+    \frac{(n+1)}{\varsigma^2 \Lambda_n \Lambda_{n+1}} \\
     &\quad\times
@@
       {
-        1 + \left(\frac{X_F - n -1}{\alpha \Lambda_n}\right)^2
+        1 + \left(\frac{X_F - n -1}{\varsigma \Lambda_n}\right)^2
       }
@@
       {
-        1 + \left(\frac{X_F - n}{\alpha \Lambda_{n+1}}\right)^2
+        1 + \left(\frac{X_F - n}{\varsigma \Lambda_{n+1}}\right)^2
       }
@@
 \end{equation}
-where $\alpha = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.
+where $\varsigma = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.
 
@@
 \begin{figure}[t]
-\includegraphics[scale=0.55]{figures/fig_4}
+\includegraphics[scale=0.54]{figures/fig_4}
 \caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.55]{figures/fig_5}
+\includegraphics[scale=0.54]{figures/fig_5}
 \caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.

### 2021-08-20 paper/v2.0/sections/1_introduction.tex

@@
 In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
-Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport.
+Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
 Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems.

### 2021-08-20 paper/v2.0/sections/appendix_a.tex

@@
 \end{equation}
-Subsequently we define the \textit{center of the cyclotron orbit} on the $y$-axis as $y_0 = \flatfrac{-p_x}{(eB)}$, and the \textit{cyclotron frequency} as  $\omega_0 = {eB}/{m_e}$.
+Subsequently, we define the \textit{center of the cyclotron orbit} on the $y$-axis as $y_0 = \flatfrac{-p_x}{(eB)}$, and the \textit{cyclotron frequency} as  $\omega_0 = {eB}/{m_e}$.
 This leads to a new arrangement of the Hamiltonian

### 2021-08-20 paper/v2.0/sections/1_introduction.tex
Grammer corrections

@@
 The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{chow13,jayasekara16,premaratne17}, and quantum cavity physics \cite{tsang10,liu17,devi20}.
-However, in recent years, one of the foremost aim of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
+However, in recent years, one of the foremost aims of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
 
@@
 In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula.
-This opened the path to exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.
+This opened the path for exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.
 
@@
 
-In the present analysis, we present a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
+In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
 A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system.

### 2021-08-20 paper/v2.0/sections/3_floquet_theory.tex
Grammer corrections

@@
 Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
-For instance, in the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space.
+For instance, the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space.
 Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.

### 2021-08-22 paper/v3-release/aps_article.tex
Create release version

% ****** Start of file dressed_quantum_hall.tex ****** %

\documentclass[
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-2}

%===============================================================================
% Import packages
%===============================================================================
% Bold math
\usepackage{bm}
% AMS packages
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
% Physics package
\usepackage{physics}
% SI units package
\usepackage{siunitx}
% Hypertext package
\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
%===============================================================================
% Bibliography style
\bibliographystyle{apsrev4-2}

\begin{document}

\preprint{APS/123-QED}

% Title of the manuscript
\title{A generalized model for the charge transport properties of
\\dressed quantum Hall systems}

% Authors of the manuscript
\author{Kosala Herath,}
\email[]{kosala.herath@monash.edu}
\author{Malin Premaratne}
\email[]{malin.premaratne@monash.edu}
\affiliation{Advanced Computing and Simulation Laboratory (A$\chi$L), Department of Electrical and Computer Systems Engineering, Monash University, Clayton, Victoria 3800, Australia.}

% Add date
\date{\today}

% Abstract
\begin{abstract}
\input{sections/abstract.tex}
\end{abstract}

% Make title of the manuscript
\maketitle

% Section 01 : Introduction
\section{\label{sec_introduction} Introduction}
\input{sections/1_introduction.tex}

% Section 02 : Schrodinger problem for a dressed quantum Hall system
\section{\label{sec_schrodinger_problem} Schrodinger problem for a dressed quantum Hall system}
\input{sections/2_schrodinger_problem.tex}

% Section 03 : Floquet theory perspectiv
\section{\label{sec_floquet_theory} Floquet theory perspective}
\input{sections/3_floquet_theory.tex}

% Section 04 :
\section{\label{sec_inverse_scattering_time}  Inverse Scattering Time Analysis}
\input{sections/4_inverse_scattering_time.tex}

% Section 05 :
\section{\label{sec_floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}
\input{sections/5_floquet_drude_conductivity.tex}

% Section 06 :
\section{\label{sec_manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}
\input{sections/6_manipulate_conductivity.tex}

% Section 07 :
\section{\label{sec_conclusions} Conclusions}
\input{sections/7_conclusions.tex}

% Acknowledgments
\begin{acknowledgments}
\input{sections/acknowledgments.tex}
\end{acknowledgments}

% Add appendixes
\appendix

% Appendix A : Wave function solutions for a dressed quantum Hall system
\section{\label{appendix_a} Wave function solutions for a dressed quantum Hall system}
\input{sections/appendix_a.tex}

% Appendix B :
\section{\label{appendix_b} Floquet modes and quasienergies}
\input{sections/appendix_b.tex}

% Appendix C :
\section{\label{appendix_c} Floquet-Fermi golden rule for a dressed quantum  Hall system}
\input{sections/appendix_c.tex}

% Appendix D :
\section{\label{appendix_d} Current operators for a dressed quantum Hall system}
\input{sections/appendix_d.tex}

% Bibliography
\bibliography{aps_article}

\end{document}

% ****** End of file dressed_quantum_hall.tex ****** %

### 2021-08-22 paper/v3-release/sections/4_inverse_scattering_time.tex
Create release version

--- 2021-08-20 paper/v2.0/sections/4_inverse_scattering_time.tex
@@
 Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
-Subsequently we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+Subsequently, we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
 Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}

### 2021-08-22 paper/v3-release/sections/6_manipulate_conductivity.tex
Create release version

--- 2021-08-20 paper/v2.0/sections/6_manipulate_conductivity.tex
@@
 In contrast, near each Landau level, the conductivity achieves excessive values compared to other areas.
-Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.
+Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.
 
-On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpen the conductivity peaks.
-When we increase the intensity level of the dressing field, the conductivity regions get more weaken as illustrated in the Fig.~\ref{fig:6}.
+On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.
+When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:6}.
 However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
@@
 Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
-However, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
 This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.

### 2021-08-22 paper/v3-release/sections/appendix_b.tex
Create release version

\subsection{Position space representation}

First we define the time integral of the Lagrangian of the classical oscillator given in Eq.~(\ref{eq:5}), over a period $T=2\pi/\omega$ as
\begin{equation} \label{eq:b1}
  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T L(\zeta,\dot{\zeta},t') dt'.
\end{equation}
Additionally, performing this integral, we can obtain a more simplified result
\begin{equation} \label{eq:b2}
  \Delta_{\varepsilon} = \frac{e^2E^2}{4m_e(\omega_0^2 - \omega^2)}.
\end{equation}
Next, we define another parameter
\begin{equation} \label{eq:b3}
  \xi =
  \int_0^t \; L(\zeta,\dot{\zeta},t') dt' -
  \Delta_{\varepsilon} t,
\end{equation}
and after simplifying, we can identify
\begin{equation} \label{eq:b4}
  \xi =
  \frac{e^2E^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t),
\end{equation}
which is a periodic function in time. Using these parameters, we can factorize the wave function given in Eq.~(\ref{eq:2}) as linearly time-dependent part and periodic time-dependent part as follows
\begin{equation} \label{eq:b5}
  \begin{aligned}
    \psi_{\alpha}&(x,y,t) \\
    & =
    \exp(\frac{i}{\hbar} \left(-\epsilon_nt + \Delta_{\varepsilon} t \right) )
    \frac{1}{\sqrt{L_x}} \chi_n\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
    \\
    & \quad\times
    \exp \left(
       \frac{i}{\hbar}
       \left\{
       p_x x +
       \frac{eE(y-y_0)}{\omega}\cos(\omega t)  \right. \right. \\
    & \left. \left. \qquad\qquad\qquad\qquad
    + m_e\dot{\zeta}(t) \left[ y-y_0 -\zeta(t) \right]
    + \xi \right\}
     \right).
  \end{aligned}
\end{equation}
This leads to separate the linear time-dependent phase component as the quasienergies
\begin{equation} \label{eq:b6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
while rest of the components as time-periodic Floquet modes
\begin{equation} \label{eq:b7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) =  &
    \frac{1}{\sqrt{L_x}} \chi_n\bm{\left(}y - y_0 - \zeta(t)\bm{\right)} \\
    & \times
    \exp \left(
       \frac{i}{\hbar}
       \left\{
       p_x x +
       \frac{eE(y-y_0)}{\omega}\cos(\omega t)  \right. \right. \\
    & \left. \left. \qquad\qquad\quad
    + m_e\dot{\zeta}(t) \left[ y-y_0 -\zeta(t) \right]
    + \xi \right\}
     \right).
  \end{aligned}
\end{equation}

\subsection{Momentum space representation}

We perform continuous Fourier transform over the considering confined space $A=L_xL_y$ on the Floquet modes given in Eq.~(\ref{eq:7}) to realize the Floquet modes in momentum space
\begin{equation} \label{eq:b8}
  \begin{aligned}
    \phi_{n,m}&(k_x,k_y,t) \\
    & =
    \exp(\frac{-i\gamma(t)}{\hbar}y_0)
    \exp(\frac{-i}{\hbar}\left[m_e \dot{\zeta}(t) \zeta(t) - \xi \right]) \\
    & \quad\times
    \int_{-L_y/2}^{L_y/2} \exp(-i \left[k_y - \gamma(t) \right]y)
      \chi_n \bm{\left(}y - \mu(t)\bm{\right)} dy \\
    & \quad\times
    \frac{1}{\sqrt{L_x}} \int_{-L_x/2}^{L_x/2}
     \exp(-ik_x x)\exp( \flatfrac{i p_x }{\hbar}x ) dx.
  \end{aligned}
\end{equation}
Here we used new two parameters
\begin{equation} \label{eq:b9}
  \mu(t) = \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0,
\end{equation}
and
\begin{equation} \label{eq:b10}
  \gamma(t) =
  \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
\end{equation}
Subsequently, using the Fourier transform identity \cite{bruus04}
\begin{equation} \label{eq:b11}
  \int_{-L_x/2}^{L_x/2}
  \exp( -ik_x x + \flatfrac{i p_x x}{\hbar}) dx =
  L_x \delta_{k_x,\flatfrac{p_x}{\hbar}},
\end{equation}
we can derive
\begin{equation} \label{eq:b12}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  =
    \Phi_{n,m}&(k_y,t)
    \delta_{k_x,\flatfrac{p_x}{\hbar}}
    \exp(\frac{-i}{\hbar} \gamma(t)y_0) \\
    & \times
    \exp(\frac{-i}{\hbar}
    \left[ m_e \dot{\zeta}(t) \zeta(t) - \xi \right]),
  \end{aligned}
\end{equation}
where we can define $\Phi_{n,m}(k_y,t)$ as
\begin{equation} \label{eq:b13}
  \begin{aligned}
    &\Phi_{n,m}(k_y,t) \\
    & \quad=
    \sqrt{L_x}
    \int_{-L_y/2}^{L_y/2}
    \chi_n \bm{\left(}y - \mu(t)\bm{\right)}
    \exp \bm{\left(}-i\left[k_y - \gamma(t) \right]y\bm{\right)} dy.
  \end{aligned}
\end{equation}
Substituting ${k'_y} = k_y -\gamma(t)$ with $y' = y -\mu(t)$, and assuming that the size of the considered 2DEG sample in $y$-direction is considerably large ($L_y \rightarrow \infty$), we can obtain
\begin{equation} \label{eq:b14}
  \Phi_{n,m}({k'_y} ,t) =
  {\sqrt{L_x}} e^{-i {k'_y}\mu}
  \int_{-\infty}^{\infty} \chi_{n}(y') \exp(-i{k'_y} y') dy'.
\end{equation}
Moreover, we can identify that the above integral represents the Fourier transform of $\chi_n$ functions. In addition, using the symmetric conditions of the Fourier transform for Gauss-Hermite functions $\theta_n(x)$ \cite{celeghini21}
\begin{equation} \label{eq:b15}
  \mathcal{FT}[\theta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\theta_n(k/\kappa),
\end{equation}
we can simply the Eq.~(\ref{eq:b14}) as
\begin{equation} \label{eq:b16}
  \Phi_{n,m}({k'_y} ,t) =
  \sqrt{L_x} e^{-i {k'_y}\mu} \widetilde{\chi}_n(k'_y),
\end{equation}
with
\begin{equation} \label{eq:b17}
  \widetilde{\chi}_{n}(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \left(\frac{1}{\kappa} \right)^{1/2}
  e^{-\flatfrac{k^2}{(2 \kappa^2)}}
  \mathcal{H}_n (\flatfrac{k}{\kappa}).
\end{equation}
Finally, substitute Eq.~(\ref{eq:b16}) back into Eq.~(\ref{eq:b12}) and this leads to
\begin{equation} \label{eq:b18}
  \begin{aligned}
    \phi_{n,m}(k_x,k_y,t)  = &
    {\sqrt{L_x}} \widetilde{\chi}_n \bm{\left(} k_y - b\cos(\omega t)\bm{\right)} \\
    & \times
    \exp \left(
      i\xi -ik_y  \left[d\sin(\omega t) + \frac{\hbar k_x}{eB} \right]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq:b19}
  b =
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
\end{equation}
and
\begin{equation} \label{eq:b20}
  d =
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
It is necessary to notice that $k_x$ is quantized with $k_x = \flatfrac{2\pi m}{L_x} ~,~ m \in \mathbb{Z}$.

### 2021-08-22 paper/v3-release/aps_article.tex
Add alltogether in article

@@
 
+%===============================================================================
 % Title of the manuscript
+%===============================================================================
 \title{A generalized model for the charge transport properties of
 \\dressed quantum Hall systems}
+%===============================================================================
 
+%===============================================================================
 % Authors of the manuscript
+%===============================================================================
 \author{Kosala Herath,}
@@
 \affiliation{Advanced Computing and Simulation Laboratory (A$\chi$L), Department of Electrical and Computer Systems Engineering, Monash University, Clayton, Victoria 3800, Australia.}
+%===============================================================================
 
+%===============================================================================
 % Add date
+%===============================================================================
 \date{\today}
+%===============================================================================
 
+%===============================================================================
 % Abstract
+%===============================================================================
 \begin{abstract}
-\input{sections/abstract.tex}
+We present a generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high-intensity electromagnetic field.
+The new formulation, which applies to two-dimensional(2D) dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
+We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields.
+To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure.
+Moreover, the Floquet-Fermi golden rule is adopted to explore the impurity scattering effects on charge transport in disordered quantum Hall systems.
+We derive fully analytical expressions to describe longitudinal components in the conductivity tensor in dressed quantum Hall systems.
+Subsequently, we demonstrate that the conductivity characteristics of quantum Hall systems can be manipulated using strong external light.
+Our results align with well-established and experimentally
+verified theoretical descriptions for undressed systems while providing a more generalized analysis of the conductivity characteristics in quantum Hall systems.
+Thus, our model can be applied to accurately interpret the usage of strong external radiation as a tool in nanoscale quantum devices.
 \end{abstract}
+%===============================================================================
 
+%===============================================================================
 % Make title of the manuscript
+%===============================================================================
 \maketitle
+%===============================================================================
 
+%===============================================================================
 % Section 01 : Introduction
+%===============================================================================
 \section{\label{sec_introduction} Introduction}
-\input{sections/1_introduction.tex}
 
+Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century.
+Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo15,pirandola18,hapuarachchi2018}, energy harvesting \cite{weeraddana15,yuan16,sun18},
+quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
+The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{chow13,jayasekara16,premaratne17}, and quantum cavity physics \cite{tsang10,liu17,devi20}.
+However, in recent years, one of the foremost aims of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
+
+Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
+Most recent studies on the subject have considered the driving field as a perturbation field \cite{pervishko15,morina15}.
+However, this assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
+Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity.
+At high intensities, the higher-order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
+In these instances, a more accurate treatment needs to be adopted.
+Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}.
+Here the applied high-intensity  electromagnetic field identify as the \textit{dressing field}.
+
+Theoretical analyses on the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
+Furthermore, in Ref.
+\cite{wackerl20} a general expression for conductivity in a dressed system has been derived in a fully closed analytical form.
+In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula.
+This opened the path for exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.
+
+Quantum Hall effect \cite{girvin90} observed in two-dimensional (2D) fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors.
+Transport properties of these systems have recently attracted both theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{allerman95,tieke97,pan05} interest.
+Endo \textit{et al.} \cite{endo09} presented the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system.
+These theoretical calculations  align better with experimental observations compared to previous studies.
+
+In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
+Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
+Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems.
+However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
+In their study, they used the conductivity models from Refs.
+\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
+
+In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
+A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system.
+This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
+In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
+Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref.
+\cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
+Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices.
+We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport.
+Moreover, this will inspire advanced  developments in nanoscale quantum devices.
+
+The paper is organized as follows.
+Sec.
+\ref{sec_schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration.
+Sec.
+\ref{sec_floquet_theory} provides the Floquet theory interpretation of these wave functions.
+We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec.
+\ref{sec_inverse_scattering_time}, and use it in Sec.
+\ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
+The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}.
+In Sec. \ref{sec_conclusions}, we summarize our analysis and present our conclusions.
+%===============================================================================
+
+%===============================================================================
 % Section 02 : Schrodinger problem for a dressed quantum Hall system
-\section{\label{sec_schrodinger_problem} Schrodinger problem for a dressed quantum Hall system}
-\input{sections/2_schrodinger_problem.tex}
+%===============================================================================
+\section{\label{sec_schrodinger_problem} Schrodinger Problem for a Dressed Quantum Hall System}
 
-% Section 03 : Floquet theory perspectiv
-\section{\label{sec_floquet_theory} Floquet theory perspective}
-\input{sections/3_floquet_theory.tex}
+Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space.
+In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{T}$, which is pointed towards the $z$-axis.
+In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface.
+We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field.
+Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field as given in Fig.~\ref{fig:1}.
+\begin{figure}[b]
+\includegraphics[scale=0.9]{figures/fig_1.pdf}
+\caption{\label{fig:1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
+The dressing field is linearly polarized with a $y$-polarized electric field $\vb{E}$.}
+\end{figure}
+Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field, respectively.
 
-% Section 04 :
+Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{T}$.
+Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E\cos(\omega t)]/\omega,0)^{T}$.
+These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}.
+Thus, we can represent our system with a time-dependent Hamiltonian
+\begin{equation} \label{eq:1}
+  \hat{H}_e(t) =
+  \frac{1}{2m_e}
+  \left\{ \hat{\vb{p}} - e\right[ \vb{A}_{s}+\vb{A}_{d}(t) \left] \right\}^2,
+\end{equation}
+where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{T}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{T}$.
+The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv*{\psi}{t} = \hat{H}_e(t)\psi$ were already derived in Refs.
+\cite{husimi53,ditt98,dini16}.
+Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
+\begin{equation} \label{eq:2}
+  \begin{aligned}
+    &\psi_{n,m}(x,y,t)  \\
+      & \quad = \frac{1}{\sqrt{L_x}}
+        \chi_n \bm{\left(} y - y_0 - \zeta(t) \bm{\right)}\\
+      & \qquad \times
+        \exp \bm{\left(}
+        \frac{i}{\hbar}\left\{- \epsilon_n t
+        + p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right.\\
+      & \left.\left. \qquad\qquad +
+        m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
+        \int_0^{t}L(\zeta,\dot{\zeta},t')\,dt' \right\}\bm{\right)},
+  \end{aligned}
+\end{equation}
+where $n \in \mathbb{Z}^+_0$ and $m \in \mathbb{Z}$.
+Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant.
+The center of the cyclotron orbit on the $y$-axis is given by $y_0 = \flatfrac{-p_x}{(eB)}$ with $p_x = \flatfrac{2\pi\hbar m}{L_x}$.
+Moreover, $\chi_n$ are well-known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
+\begin{equation} \label{eq:3}
+  \chi_n(y) =
+  \left( \frac{\kappa}{2^{n}n! \sqrt{\pi}}\right)^{1/2}
+  e^{-\kappa^2 y^2/2}
+  \mathcal{H}_n \qty(\kappa y),
+\end{equation}
+with eigenvalues $\epsilon_n = \hbar \omega_0 [n + (1/2)]$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
+We represent the path shift of the driven classical oscillator $\zeta(t)$ by
+\begin{equation} \label{eq:4}
+  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
+\end{equation}
+and we introduce $\dot{\zeta}(t) = \pdv*{\zeta(t)}{t}$ for the sake of notational ease. We can identify the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ as
+\begin{equation} \label{eq:5}
+  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
+\end{equation}
+For details of the full derivation, refer to Appendix \ref{appendix_a}.
+The exponential phase shifts in Eq.~(\ref{eq:2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system.
+Therefore, we can renormalize the magneto-transport characteristics of 2DEG by a nonoscillating magnetic field along with a dressing field.
+%===============================================================================
+
+%===============================================================================
+% Section 03 : Floquet theory perspective
+%===============================================================================
+\section{\label{sec_floquet_theory} Floquet Theory Perspective}
+
+Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
+For instance, the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space.
+Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
+The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
+In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field.
+Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
+
+First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq:2}).
+By factorizing the wave function into a linearly time-dependent part and a periodic time-dependent part, we present the quasienergies with
+\begin{equation} \label{eq:6}
+  \varepsilon_{n} =
+  \hbar \omega_0 \left(n + \flatfrac{1}{2}\right) - \Delta_{\varepsilon},
+\end{equation}
+which only depends on a single quantum number $n$. Furthermore, we can recognize the Floquet modes as
+\begin{equation} \label{eq:7}
+  \begin{aligned}
+    \phi_{n,m}(x,y,t) =&
+    \frac{1}{\sqrt{L_x}} \chi_{n}\bm{\left(}y - y_0 -\zeta(t)\bm{\right)} \\
+    & \times
+      \exp \bm{\left(}
+      \frac{i}{\hbar}\left\{
+      p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right. \\
+    & \left.\left. \qquad\qquad +
+      m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
+      \xi \right\}\bm{\right)},
+  \end{aligned}
+\end{equation}
+with
+\begin{equation} \label{eq:8}
+  \Delta_{\varepsilon} = \frac{e^2E^2}{4m_e(\omega_0^2 - \omega^2)},
+\end{equation}
+and
+\begin{equation} \label{eq:9}
+  \xi = \frac{e^2E^2 \left(3\omega^2 - \omega_0^2 \right)}
+  {8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
+\end{equation}
+For a detailed derivation, refer to Appendix \ref{appendix_b}.
+It is important to note that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
+At resonance $\omega = \omega_0$, the energy levels occupy a continuous spectrum and the quasienergy formalism is no longer valid \cite{popov70}.
+Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.
+
+Performing the Fourier transform over the confined 2D space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
+\begin{equation} \label{eq:10}
+  \begin{aligned}
+    \phi_{n,m}\big(k_x,k_y,t\big)  =&
+    \sqrt{L_x}
+    \widetilde{\chi}_{n} \bm{\left(}k_y - b\cos(\omega t)\bm{\right) }\\
+    & \times
+    \exp \bm{\left(} i\xi -ik_y  \left[d\sin(\omega t) + y_0 \right] \bm{\right)},
+  \end{aligned}
+\end{equation}
+where
+\begin{equation} \label{eq:11}
+  \widetilde{\chi}_{n}(k) =
+  i^n \left(\frac{1}{ 2^{n} n! \sqrt{\pi} \kappa}\right)^{1/2}
+  e^{-\flatfrac{k^2}{(2 \kappa^2)}}
+  \mathcal{H}_{n} \left(\flatfrac{k}{\kappa}\right).
+\end{equation}
+Here we have introduced new parameters
+\begin{equation} \label{eq:12}
+  b =
+  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
+\end{equation}
+and
+\begin{equation} \label{eq:13}
+  d =
+ \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
+\end{equation}
+Using Floquet theory, we can re-write the wave functions derived in Eq.~(\ref{eq:2}) as the \textit{Floquet states} in momentum space
+\begin{equation} \label{eq:14}
+  \psi_{n,m}(k_x,k_y,t) =
+  \exp(-\flatfrac{i\varepsilon_{n}t}{\hbar}) \phi_{n,m} (k_x,k_y,t).
+\end{equation}
+%===============================================================================
+
+%===============================================================================
+% Section 04 : Inverse scattering time analysis
+%===============================================================================
 \section{\label{sec_inverse_scattering_time}  Inverse Scattering Time Analysis}
-\input{sections/4_inverse_scattering_time.tex}
 
-% Section 05 :
+The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
+However, this theory has not been applied for a dressed quantum Hall system in the previous studies.
+In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
+With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
+\begin{widetext}
+\begin{equation} \label{eq:15}
+  \begin{aligned}
+    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
+    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
+    & \times
+    \int_{-\infty}^{\infty}
+    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+    \left|
+    \int_{-\infty}^{\infty}
+    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
+    \chi_N \bm{\left(} \frac{\hbar}{eB}
+    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
+    dk_2 \right|^2 d k_1,
+  \end{aligned}
+\end{equation}
+\end{widetext}
+where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
+A more detailed derivation is given in Appendix \ref{appendix_c}.
+We modeled the effect caused by impurities in the considered system as a single perturbation potential.
+Since random impurities in a disordered metal offer a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
+Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
+Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
+
+Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
+Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
+Subsequently, we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
+\begin{equation} \label{eq:16}
+ \Gamma^{00}_{N}(\varepsilon,k_x) =
+ \hbar \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{00}_N.
+\end{equation}
+We can evaluate this as
+\begin{widetext}
+  \begin{equation} \label{eq:17}
+   \begin{aligned}
+     &\Gamma^{00}_{N} (\varepsilon,k_x) =
+     \frac{ \pi \hbar^2 \varrho^2}{e^2B^2}
+     \delta(\varepsilon - \varepsilon_{N})
+     \int_{-\infty}^{\infty}
+     J_0^2 \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+     \left|
+     \int_{-\infty}^{\infty}
+     \chi_N \left( \frac{\hbar}{eB}k_2 \right)
+     \chi_N \bm{\left(} \frac{\hbar}{eB}
+     \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
+     dk_2 \right|^2 d k_1.
+   \end{aligned}
+  \end{equation}
+In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
+\begin{equation} \label{eq:18}
+ \delta(\varepsilon - \varepsilon_{N}) \approx
+ \frac{1}{\pi \Gamma^{00}_N (\varepsilon,k_x)}.
+\end{equation}
+Subsequently, we write the central element of inverse scattering time matrix in the more compact form
+\begin{equation} \label{eq:19}
+  \begin{aligned}
+    &\Gamma^{00}_{N}(\varepsilon,k_x) =
+     \varrho
+      \left[
+      \int_{-\infty}^{\infty}
+      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
+      \left|
+      \int_{-\infty}^{\infty}
+      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
+      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
+      dk_2 \right|^2
+      dk_1
+      \right]^{-\frac{1}{2}},
+  \end{aligned}
+\end{equation}
+where $ \lambda_1 = \flatfrac{\hbar b}{(eB)}$ and  $\lambda_2 = \flatfrac{\hbar \kappa}{(eB)}$.
+To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
+\begin{equation} \label{eq:20}
+    \Lambda_N(k_x) =
+    \frac{\Gamma^{00}_N (\varepsilon,k_x)}
+    {\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
+\end{equation}
+which we can evaluate with
+\begin{equation} \label{eq:21}
+    \Lambda_N (k_x) =
+    \left[
+    \frac
+    {
+      \int_{-\infty}^{\infty}
+      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
+      \left|
+      \int_{-\infty}^{\infty}
+      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
+      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
+      dk_2 \right|^2
+      dk_1
+    }
+    {
+      \int_{-\infty}^{\infty}
+      \left|
+      \int_{-\infty}^{\infty}
+      \widetilde{\chi}_0 \left(\lambda_2 k_2 \right)
+      \widetilde{\chi}_0 \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
+      dk_2 \right|^2
+      dk_1
+    }
+    \right]^{1/2}.
+\end{equation}
+\end{widetext}
+
+\begin{figure}[t]
+\includegraphics[scale=0.55]{figures/fig_2}
+\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[scale=0.54]{figures/fig_3}
+\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
+In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\end{figure}
+
+Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig_3} and Fig.~\ref{fig_4}.
+To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
+In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
+In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
+Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
+Here, we observe that the normalized energy broadening value for each Landau level is independent of the $x$-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
+When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
+To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.
+%===============================================================================
+
+%===============================================================================
+% Section 05 : Floquet-Drude Conductivity in a Dressed Quantum Hall System
+%===============================================================================
 \section{\label{sec_floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}
-\input{sections/5_floquet_drude_conductivity.tex}
 
-% Section 06 :
+A general theory for the conductivity of a dressed system with disorder was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}.
+This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
+\begin{equation} \label{eq:22}
+  \begin{aligned}
+    \sigma^{xx} = &
+    \frac{-1}{4\pi\hbar A}
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+    -\pdv*{f}{\varepsilon }\right) \\
+    &  \quad\times
+    \tr
+    \left\{
+    {j}^x_0
+    \left[
+    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+    \right]
+    {j}^x_0
+    \left[
+    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+    \right]
+    \right\} d\varepsilon,
+  \end{aligned}
+\end{equation}
+where $j^x_0$ is the $x$-directional electric current operator matrix elements' $0$-th Fourier component.
+Here, $\vb{G}^{r}(\varepsilon)$ and $\vb{G}^{a} (\varepsilon)$ are the retarded and advanced white noise disorder averaged Floquet Green function matrices \cite{wackerl20,wackerlthesis20}, respectively.
+These matrices are defined against the Floquet modes of the considering system.
+Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity.
+In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
+\begin{equation} \label{eq:23}
+    \Pi- \flatfrac{\hbar \omega}{2}
+    \leq \varepsilon_N
+    <
+    \Pi + \flatfrac{\hbar \omega}{2}.
+\end{equation}
+Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr\{\cdot\}$ is the trace of the considering operator.
+
+Next, we restrict our analysis into the off-resonant regime $\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system.
+Thus, we can expand the $x$-directional longitudinal conductivity given in
+Eq.~(\ref{eq:22}) using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} = \ket{n,k_x}$ as
+\begin{widetext}
+\begin{equation} \label{eq:24}
+  \begin{aligned}
+    \sigma^{xx} =
+    \frac{-1}{4\pi\hbar A}
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+      -\frac{\partial f}{\partial \varepsilon}
+    \right)
+    \frac{1}{V_{k_x}} \sum_{k_x}
+    \sum_{n}
+    \mel{n,k_x}
+    {
+      {j}^x_0
+      \left[
+        \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+      \right]
+      {j}^x_0
+      \left[
+        \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+      \right]
+    }
+    {n,k_x}
+    d\varepsilon,
+  \end{aligned}
+\end{equation}
+where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Next, we evaluate the above expression as follows
+\begin{equation} \label{eq:25}
+  \begin{aligned}
+    \sigma^{xx}  = &
+    \frac{-1}{4\pi\hbar A}
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+      -\frac{\partial f}{\partial \varepsilon}
+    \right)
+    \frac{1}{V_{k_x}^4}
+    \sum_{k_x} \sum_{n}
+    \sum_{{k_x}_1,{k_x}_2,{k_x}_3}
+    \sum_{n_1,n_2,n_3} \\
+    & \quad\times \mel{n,k_x}{
+    {j}^x_0}
+    {n_1,{k_x}_1}
+    \mel{{n_1,{k_x}_1}}{
+    \left[
+      \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+    \right]
+    }
+    {n_2,{k_x}_2}
+    \mel{n_2,{k_x}_2}{
+    {j}^x_0}
+    {n_3,{k_x}_3}
+    \mel{n_3,{k_x}_3}{
+    \left[
+      \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+    \right]
+    }
+    {n,k_x} d\varepsilon.
+  \end{aligned}
+\end{equation}
+We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  = \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}.
+Thus, we evaluate the matrix elements of the difference between retarded and advanced Green's functions as
+\begin{equation} \label{eq:26}
+  \mel{{n_1,{k_x}_1}}
+  {
+    \vb{T}^{\dagger}
+    \left[
+    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+    \right]\vb{T}
+  }
+  {n_2,{k_x}_2} =
+  \frac
+  {
+    2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+    \delta_{n_1,n_2}\delta_{{k_x}_1,{k_x}_2}
+  }
+  {
+    \left(
+    \flatfrac{\varepsilon}{\hbar} -
+    \flatfrac{\varepsilon_{n_1}}{\hbar}
+    \right)^2
+    + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
+  },
+\end{equation}
+and
+\begin{equation} \label{eq:27}
+  \mel{{n_3,{k_x}_3}}{
+  \vb{T}^{\dagger}
+  \left[
+  \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
+  \right]\vb{T}}
+  {n,{k_x}} =
+  \frac{
+    2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+    \delta_{n_3,n}\delta_{{k_x}_3,{k_x}}
+  }
+  {
+    \left(
+    \flatfrac{\varepsilon }{\hbar}-
+    \flatfrac{\varepsilon_{n}}{\hbar}
+    \right)^2
+    + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
+  }.
+\end{equation}
+Here we introduced the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
+Applying the matrix elements of the electric current operator in Landau levels and
+expressions from Eq.~(\ref{eq:26}) and Eq.~(\ref{eq:27}) back into Eq.~(\ref{eq:25}) we obtain
+\begin{equation} \label{eq:28}
+  \begin{aligned}
+    \sigma^{xx}  =
+    \frac{-1}{4\pi\hbar A}
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}&
+    \left(
+    -\frac{\partial f}{\partial \varepsilon}
+    \right)
+    \frac{1}{V_{k_x}}
+    \sum_{k_x} \sum_{n} \sum_{n_1,n_2}
+    \\
+    & \times
+    \frac{e^2B}{{m_e}}
+    \left(
+    \sqrt{\frac{n+1}{2}} \delta_{n_1,n+1} + \sqrt{\frac{n}{2}}\delta_{n_1,n-1}
+    \right)
+    \left\{
+    \frac
+    {
+      2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+      \delta_{n_1,n_2}
+    }
+    {
+      \left(
+      \flatfrac{\varepsilon}{\hbar} -
+      \flatfrac{\varepsilon_{n_1}}{\hbar}
+      \right)^2
+      + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
+    }
+    \right\} \\
+    & \times
+    \frac{e^2B}{{m_e}}
+    \left(
+    \sqrt{\frac{n_2+1}{2}} \delta_{n,n_2+1} + \sqrt{\frac{n_2}{2}}
+    \delta_{n,n_2-1}
+    \right)
+    \left\{
+    \frac{
+      2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
+    }
+    {
+      \left(
+      \flatfrac{\varepsilon }{\hbar}-
+      \flatfrac{\varepsilon_{n}}{\hbar}
+      \right)^2
+      + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
+    }
+    \right\}  d\varepsilon,
+  \end{aligned}
+\end{equation}
+For the full derivation of electric current operators in a quantum Hall system, refer to Appendix \ref{appendix_d}.
+After the expansion, we can identify the the only non-zero term as follows
+\begin{equation} \label{eq:29}
+  \begin{aligned}
+    \sigma^{xx} =
+    \frac{-1}{4\pi\hbar A}
+    \frac{e^4B^2}{{{m_e}^2}} &
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+    -\frac{\partial f}{\partial \varepsilon}\right)
+    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
+    (n+1)
+    \\
+    & \times
+    \left\{
+    \frac
+    {
+      2i \Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_{n+1},k_x) \vb{T}\bm{)}
+    }
+    {
+      \left(
+      \flatfrac{\varepsilon}{\hbar} -
+      \flatfrac{\varepsilon_{n+1}}{\hbar}
+      \right)^2
+      + \left[\Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_{n+1},k_x) \vb{T}\bm{)}\right]^2
+    }
+    \right\}
+    \left\{
+    \frac{
+      2i \Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_n,k_x) \vb{T}\bm{)}
+    }
+    {
+      \left(
+      \flatfrac{\varepsilon }{\hbar}-
+      \flatfrac{\varepsilon_{n}}{\hbar}
+      \right)^2
+      + \left[\Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_n,k_x) \vb{T}\bm{)}\right]^2
+    }
+    \right\}
+    d\varepsilon.
+  \end{aligned}
+\end{equation}
+The inverse scattering time matrix is equal to the diagonalized contrast of the retarded and advanced self-energy \cite{wackerl20,wackerlthesis20}.
+In addition, on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20}.
+Subsequently, we can identify the following property
+\begin{equation} \label{eq:30}
+  \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll} =
+  -2\text{Im} \left[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}\right]^{ll}.
+\end{equation}
+Afterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in Eq.~(\ref{eq:29}) as follows
+\begin{equation} \label{eq:31}
+    \sigma^{xx}   =
+    \frac{1}{\pi\hbar A}
+    \frac{e^4B^2}{{{m_e}^2}}
+    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
+    \left(
+      -\frac{\partial f}{\partial \varepsilon}
+    \right)
+    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n} (n+1)
+    \left[
+    \frac{\widetilde{{\Gamma}}(\varepsilon_{n+1})
+    }
+    {
+    \left(
+    \varepsilon_F - \varepsilon_{n+1}
+    \right)^2
+    + \widetilde{{\Gamma}}^2(\varepsilon_{n+1})
+    }
+    \right]
+    \left[
+    \frac{\widetilde{{\Gamma}}(\varepsilon_{n})
+    }
+    {
+    \left(
+    \varepsilon_F - \varepsilon_{n}
+    \right)^2
+    + \widetilde{{\Gamma}}^2(\varepsilon_{n})
+    }
+    \right]
+    d\varepsilon,
+\end{equation}
+\end{widetext}
+with $\widetilde{{\Gamma}}(\varepsilon_n,k_x) = \left[\flatfrac{\hbar}{2\tau(\varepsilon_n,k_x)}\right]^{00}$.
+Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\widetilde{{\Gamma}}(\varepsilon_n,k_x)$ terms.
+Subsequently, we can get the sum over available momentum in $x$-direction.
+However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considered system, we can identify that
+\begin{equation} \label{eq:32}
+ -\flatfrac{m_e\omega_0 Ly}{(2\hbar)} \leq k_x \leq \flatfrac{m_e\omega_0 Ly}{(2\hbar)}.
+\end{equation}
+We use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
+\begin{equation} \label{eq:33}
+  f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
+\end{equation}
+where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
+Considering the above distribution for extremely low-temperature conditions, we can use the following approximation
+\begin{equation} \label{eq:34}
+  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
+\end{equation}
+Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
+\begin{equation} \label{eq:35}
+  \begin{aligned}
+    \sigma^{xx}  =
+    \frac{e^2}{\pi\hbar A}
+    \sum_{n} &
+    \frac{(n+1)}{\gamma_{n}\gamma_{n+1}} \\
+    &\times
+    \left[
+      \frac{1}
+      {
+        1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
+      }
+    \right]
+    \left[
+      \frac{1}
+      {
+        1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
+      }
+    \right],
+  \end{aligned}
+\end{equation}
+where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$
+and
+$\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$.
+Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
+\begin{equation} \label{eq:36}
+  \begin{aligned}
+    {\sigma}^{yy} =
+    \frac{e^2}{\pi\hbar A} &
+    \frac{1}{e^2B^2}
+    \sum_{n}
+    \frac{(n+1)}{\gamma_{n}\gamma_{n+1}} \\
+    & \times
+    \left[
+      \frac{1}
+      {
+        1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
+      }
+    \right]
+    \left[
+      \frac{1}
+      {
+        1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
+      }
+    \right].
+  \end{aligned}
+\end{equation}
+%===============================================================================
+
+%===============================================================================
+% Section 06 : Manipulate Conductivity in Quantum Hall Systems
+%===============================================================================
 \section{\label{sec_manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}
-\input{sections/6_manipulate_conductivity.tex}
 
-% Section 07 :
+To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
+We can identify the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
+\begin{equation}\label{eq:37}
+  \widetilde{\sigma}^{xx}(X_F,I) =
+  \flatfrac{\sigma^{xx}}{\sigma_{0}},
+\end{equation}
+with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and we can express this as
+\begin{equation} \label{eq:38}
+  \begin{aligned}
+    \widetilde{\sigma}^{xx}(X_F,I) &=
+    \sum_{n}
+    \frac{(n+1)}{\varsigma^2 \Lambda_n \Lambda_{n+1}} \\
+    &\quad\times
+    \left[
+      \frac{1}
+      {
+        1 + \left(\frac{X_F - n -1}{\varsigma \Lambda_n}\right)^2
+      }
+    \right]
+    \left[
+      \frac{1}
+      {
+        1 + \left(\frac{X_F - n}{\varsigma \Lambda_{n+1}}\right)^2
+      }
+    \right],
+  \end{aligned}
+\end{equation}
+where $\varsigma = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.
+
+As illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6}, we can manipulate the normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
+For a given dressing field intensity, the longitudinal conductivity varies with  the Fermi level of the system showing sharp peaks at each Landau energy level.
+In quantum Hall systems, electrons are restricted to bear only the Landau energies.
+Thus, the conductivity reduces significantly when the Fermi level is not aligned with any of the Landau levels.
+In contrast, near each Landau level, the conductivity achieves excessive values compared to other areas.
+Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.
+
+On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.
+When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:6}.
+However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
+This demonstrates our ability to tune the width of the conductivity regions in these quantum Hall systems with the help of a dressing field.
+
+These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
+As the authors remarked in that publication, since the Fermi level of the system can be changed with the applied gate voltage of the material, this can be utilized as a 2D switch for nanoscale optoelectronics applications.
+Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
+However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
+The semi-elliptical conductivity regions are  illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed data for Landau levels \cite{endo09}.
+In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the results depicted in Ref.
+\cite{endo09}.
+The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimentally observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
+However, they have not considered the tunability that can be achieved with a dressing field.
+In this analysis, we account for both the magnetic and dressing field effects that can affect the transport properties of 2DEG, leading to a more generalized theory.
+Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.
+
+\begin{figure}[t]
+\includegraphics[scale=0.54]{figures/fig_4}
+\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\label{fig:5}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[scale=0.54]{figures/fig_5}
+\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\label{fig:6}
+\end{figure}
+%===============================================================================
+
+%===============================================================================
+% Section 07 : Conclusions
+%===============================================================================
 \section{\label{sec_conclusions} Conclusions}
-\input{sections/7_conclusions.tex}
 
+In this paper, we introduced a generalized mathematical model for predicting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high-intensity light.
+Under the uniform magnetic field, the charged particles can only settle in discrete energy values, which leads to the Landau quantization.
+We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method.
+We assumed the impurities in the material as a Gaussian random scattering potential.
+Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
+
+Our derived analytical expressions disclosed that we are able to control the transport characteristics of the dressed quantum Hall system by the applied dressing field’s intensity.
+Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
+We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
+Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels.
+Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.
+However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.
+
+In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems.
+Moreover, our detailed theoretical analysis showed that we can adapt the recently introduced Floquet-Drude conductivity model to extend the models that were used to describe the transport characteristics in quantum Hall systems.
+Owing to the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices, which are employed as the building blocks of next-generation nanoelectronic devices.
+As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D optoelectronic nanotransistors, enhancing their performance and inventing novel appliances.
+%===============================================================================
+
+%===============================================================================
 % Acknowledgments
+%===============================================================================
 \begin{acknowledgments}
-\input{sections/acknowledgments.tex}
+K.H wish to acknowledge the members of A$\chi$L at Monash University for their encouragement and support and specially T.N.
+Perera and R.T.Wijesekara for insightful discussions.
+The work of K.H is supported by the Australian Government Research Training Program (RTP) Scholarship and the Monash University Institute of Graduate Research.
 \end{acknowledgments}
+%===============================================================================
 
+%===============================================================================
 % Add appendixes
-\appendix
+%===============================================================================
+\begin{appendix}
 
+%===============================================================================
 % Appendix A : Wave function solutions for a dressed quantum Hall system
+%===============================================================================
 \section{\label{appendix_a} Wave function solutions for a dressed quantum Hall system}
-\input{sections/appendix_a.tex}
 
+The derivation of the solutions for the time-dependent Schrödinger equation with our system's Hamiltonian (Eq.
+\ref{eq:1}) is quite similar to that followed in Refs.
+\cite{husimi53,dini16}.
+We start with expanding the Hamiltonian for two-dimensional scenario
+\begin{equation} \label{eq:a1}
+  \hat{H}_e(t) = \frac{1}{2m_e}
+  \left\{
+    \left(\hat{p}_x + eBy \right)^2 +
+    \left[
+      \hat{p}_y - \frac{eE}{\omega}\cos(\omega t)
+    \right]^2
+  \right\}.
+\end{equation}
+Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
+${L_x}^{-1/2}\exp(\flatfrac{ip_x x}{\hbar})$ where $p_x = \flatfrac{2\pi \hbar m}{L_x}$ with $ m \in \mathbb{Z}$.
+Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
+\begin{equation} \label{eq:a2}
+    \hat{H}_e(t) = \frac{1}{2m_e}
+    \left\{
+      \left({p}_x + eBy \right)^2 +
+      \left[
+        i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)
+      \right]^2
+    \right\}.
+\end{equation}
+Subsequently, we define the \textit{center of the cyclotron orbit} on the $y$-axis as $y_0 = \flatfrac{-p_x}{(eB)}$, and the \textit{cyclotron frequency} as  $\omega_0 = {eB}/{m_e}$.
+This leads to a new arrangement of the Hamiltonian
+\begin{equation} \label{eq:a3}
+  \begin{aligned}
+    \hat{H}_e(t) =
+      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
+      \frac{1}{2m_e} &
+      \left[
+        -\hbar^2 \pdv[2]{\tilde{y}}  +
+        \frac{2i\hbar eE}{\omega} \cos(\omega t) \pdv{\tilde{y}}
+        \right.\\
+        & \left. \qquad\qquad\quad +
+        \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
+        \right],
+  \end{aligned}
+\end{equation}
+where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
+\begin{equation} \label{eq:a4}
+    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
+\end{equation}
+can be presented by the following form
+\begin{equation} \label{eq:a5}
+    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}}
+    \exp\left(
+      \frac{ip_x x}{\hbar} +
+      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
+    \right) \vartheta(\tilde{y},t),
+\end{equation}
+where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
+\begin{equation} \label{eq:a6}
+    \left[
+    \frac{m_e \omega_0^2}{2} \tilde{y}^2
+    - {eE\tilde{y}}\sin(\omega t)
+    - \frac{\hbar^2}{2m_e} \pdv[2]{\tilde{y}}
+    - i \hbar \dv{t}
+    \right]
+    \vartheta(\tilde{y},t) = 0.
+\end{equation}
+If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
+\begin{equation} \label{eq:a7}
+     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
+    \left(
+    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
+    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
+    \right)
+    \vartheta(\tilde{y},t).
+\end{equation}
+Thus, we can identify $S(t) = eE\sin(\omega t)$ term as an external force that act on the harmonic oscillator, and we can solve Eq.~(\ref{eq:a6}) as a forced harmonic oscillator on $\tilde{y}$ axis
+\begin{equation} \label{eq:a8}
+  \begin{aligned}
+    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
+    \bigg[
+    -
+    \frac{\hbar^2}{2m_e}
+    \pdv[2]{\tilde{y}} +
+    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
+    - \tilde{y}S(t)]
+    \bigg]
+    \vartheta(\tilde{y},t).
+  \end{aligned}
+\end{equation}
+This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}.
+We introduce a time-dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
+\begin{equation} \label{eq:a9}
+    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
+\end{equation}
+and this leads to
+\begin{equation} \label{eq:a10}
+  \begin{aligned}
+    i \hbar \pdv{\varphi(y',t)}{t}   &=
+    \left\{
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
+        + \frac{1}{2} m_e \omega_0^2 y'^2
+        \right. \\
+        & \left. \qquad
+        - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
+        \right. \\
+        & \left. \qquad +
+        \left[
+            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
+        \right]y'
+    \right\} \varphi(y',t).
+  \end{aligned}
+\end{equation}
+Here, we introduced $\dot{\zeta} = \pdv*{\zeta}{t}$ and $\ddot{\zeta} = \pdv*[2]{\zeta}{t}$ for the sake of notational convenience. Subsequently, we can restrict $\zeta(t)$ function such that
+\begin{equation} \label{eq:a11}
+  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
+\end{equation}
+and that simply our previous expression as
+\begin{equation} \label{eq:a12}
+  \begin{aligned}
+    i \hbar \pdv{\varphi(y',t)}{t} =&
+    \left[
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
+        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \right. \\
+        & \left. \qquad\qquad\qquad
+        - L(\zeta,\dot{\zeta},t)
+    \right]\varphi(y',t).
+  \end{aligned}
+\end{equation}
+Here
+\begin{equation} \label{eq:a13}
+  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
+\end{equation}
+is the Lagrangian of a classical driven oscillator. To proceed further, we introduce another unitary transform as follows
+\begin{equation} \label{eq:a14}
+    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t} L(\zeta,\dot{\zeta},t')dt') \chi(y',t),
+\end{equation}
+and subtitling Eq.~(\ref{eq:a14}) back in Eq.~(\ref{eq:a12}), we can obtain
+\begin{equation} \label{eq:a15}
+    i \hbar \pdv{t} \chi(y',t)  =
+    \left(
+        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
+        + \frac{1}{2} m_e \omega_0^2 {y'}^2
+    \right) \chi(y',t).
+\end{equation}
+This is the well-known Schrödinger equation of the quantum harmonic oscillator.
+This allows us to identify the well known eigenfunction solutions \cite{griffiths18,shankar94}
+\begin{equation} \label{eq:a16}
+  \chi_n(y) =
+  \sqrt{\frac{\kappa}{2^{n}n!\sqrt{\pi}}}
+  e^{-\kappa^2 y^2/2}
+  \mathcal{H}_n \qty(\kappa y),
+\end{equation}
+with eigenvalues
+\begin{equation} \label{eq:a17}
+  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
+  ~\text{for}~
+  n \in \mathbb{Z}^{+}_0.
+\end{equation}
+Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
+Thus, we can identify the solutions for Eq.~(\ref{eq:a8}) as
+\begin{equation} \label{eq:a18}
+  \begin{aligned}
+    \vartheta_n(\tilde{y},t) = \chi_n\bm{(}\tilde{y} - \zeta(t)\bm{)}
+     \text{exp}&
+     \left(
+     \frac{i}{\hbar}
+     \left\{
+     - \epsilon_nt +
+     m_e \left[\tilde{y}-\zeta(t)\right] \dot{\zeta(t)} \right. \right. \\
+     & \left. \left. \qquad
+     + \int_0^{t}L(\zeta,\dot{\zeta},t') dt'
+     \right\}
+     \right).
+  \end{aligned}
+\end{equation}
+Since $\chi_n(x)$ functions forms a complete set, we can present any general solution for  $\vartheta_(\tilde{y},t)$ using the solutions derived in Eq.~(\ref{eq:a18}).
+
+Finally, we consider our scenario where we can assume that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq:a11}) as
+\begin{equation} \label{eq:a19}
+  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
+\end{equation}
+Substituting solutions given in Eq.~(\ref{eq:a18}) back in Eq.~(\ref{eq:a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq:a4}) as follows
+\begin{equation} \label{eq:a20}
+  \begin{aligned}
+    &\psi_{n,m}(x,y,t) \\
+    & \quad=  \frac{1}{\sqrt{L_x}}
+    \chi_n\left(y - y_0 - \zeta(t)\right)\\
+    &\qquad\times
+    \text{exp}\left(
+    \frac{i}{\hbar}
+    \left\{- \epsilon_nt
+    + p_x x
+    + \frac{eE(y - y_0)}{\omega}\cos(\omega t) \right. \right. \\
+    & \left. \left. \qquad\qquad +
+    m_e\left[y - y_0 -\zeta(t)\right] \dot{\zeta}(t)+
+    \int_0^{t}L(\zeta,\dot{\zeta},t') dt'
+    \right\}
+    \right).
+  \end{aligned}
+\end{equation}
+%===============================================================================
+
+%===============================================================================
 % Appendix B :
+%===============================================================================
 \section{\label{appendix_b} Floquet modes and quasienergies}
-\input{sections/appendix_b.tex}
 
+\subsection{Position space representation}
+
+First we define the time integral of the Lagrangian of the classical oscillator given in Eq.~(\ref{eq:5}), over a period $T=2\pi/\omega$ as
+\begin{equation} \label{eq:b1}
+  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T L(\zeta,\dot{\zeta},t') dt'.
+\end{equation}
+Additionally, performing this integral, we can obtain a more simplified result
+\begin{equation} \label{eq:b2}
+  \Delta_{\varepsilon} = \frac{e^2E^2}{4m_e(\omega_0^2 - \omega^2)}.
+\end{equation}
+Next, we define another parameter
+\begin{equation} \label{eq:b3}
+  \xi =
+  \int_0^t \; L(\zeta,\dot{\zeta},t') dt' -
+  \Delta_{\varepsilon} t,
+\end{equation}
+and after simplifying, we can identify
+\begin{equation} \label{eq:b4}
+  \xi =
+  \frac{e^2E^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t),
+\end{equation}
+which is a periodic function in time. Using these parameters, we can factorize the wave function given in Eq.~(\ref{eq:2}) as linearly time-dependent part and periodic time-dependent part as follows
+\begin{equation} \label{eq:b5}
+  \begin{aligned}
+    \psi_{\alpha}&(x,y,t) \\
+    & =
+    \exp(\frac{i}{\hbar} \left(-\epsilon_nt + \Delta_{\varepsilon} t \right) )
+    \frac{1}{\sqrt{L_x}} \chi_n\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
+    \\
+    & \quad\times
+    \exp \left(
+       \frac{i}{\hbar}
+       \left\{
+       p_x x +
+       \frac{eE(y-y_0)}{\omega}\cos(\omega t)  \right. \right. \\
+    & \left. \left. \qquad\qquad\qquad\qquad
+    + m_e\dot{\zeta}(t) \left[ y-y_0 -\zeta(t) \right]
+    + \xi \right\}
+     \right).
+  \end{aligned}
+\end{equation}
+This leads to separate the linear time-dependent phase component as the quasienergies
+\begin{equation} \label{eq:b6}
+  \varepsilon_{n} =
+  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
+\end{equation}
+while rest of the components as time-periodic Floquet modes
+\begin{equation} \label{eq:b7}
+  \begin{aligned}
+    \phi_{n,m}(x,y,t) =  &
+    \frac{1}{\sqrt{L_x}} \chi_n\bm{\left(}y - y_0 - \zeta(t)\bm{\right)} \\
+    & \times
+    \exp \left(
+       \frac{i}{\hbar}
+       \left\{
+       p_x x +
+       \frac{eE(y-y_0)}{\omega}\cos(\omega t)  \right. \right. \\
+    & \left. \left. \qquad\qquad\quad
+    + m_e\dot{\zeta}(t) \left[ y-y_0 -\zeta(t) \right]
+    + \xi \right\}
+     \right).
+  \end{aligned}
+\end{equation}
+
+\subsection{Momentum space representation}
+
+We perform continuous Fourier transform over the considering confined space $A=L_xL_y$ on the Floquet modes given in Eq.~(\ref{eq:7}) to realize the Floquet modes in momentum space
+\begin{equation} \label{eq:b8}
+  \begin{aligned}
+    \phi_{n,m}&(k_x,k_y,t) \\
+    & =
+    \exp(\frac{-i\gamma(t)}{\hbar}y_0)
+    \exp(\frac{-i}{\hbar}\left[m_e \dot{\zeta}(t) \zeta(t) - \xi \right]) \\
+    & \quad\times
+    \int_{-L_y/2}^{L_y/2} \exp(-i \left[k_y - \gamma(t) \right]y)
+      \chi_n \bm{\left(}y - \mu(t)\bm{\right)} dy \\
+    & \quad\times
+    \frac{1}{\sqrt{L_x}} \int_{-L_x/2}^{L_x/2}
+     \exp(-ik_x x)\exp( \flatfrac{i p_x }{\hbar}x ) dx.
+  \end{aligned}
+\end{equation}
+Here we used new two parameters
+\begin{equation} \label{eq:b9}
+  \mu(t) = \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0,
+\end{equation}
+and
+\begin{equation} \label{eq:b10}
+  \gamma(t) =
+  \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
+\end{equation}
+Subsequently, using the Fourier transform identity \cite{bruus04}
+\begin{equation} \label{eq:b11}
+  \int_{-L_x/2}^{L_x/2}
+  \exp( -ik_x x + \flatfrac{i p_x x}{\hbar}) dx =
+  L_x \delta_{k_x,\flatfrac{p_x}{\hbar}},
+\end{equation}
+we can derive
+\begin{equation} \label{eq:b12}
+  \begin{aligned}
+    \phi_{n,m}(k_x,k_y,t)  =
+    \Phi_{n,m}&(k_y,t)
+    \delta_{k_x,\flatfrac{p_x}{\hbar}}
+    \exp(\frac{-i}{\hbar} \gamma(t)y_0) \\
+    & \times
+    \exp(\frac{-i}{\hbar}
+    \left[ m_e \dot{\zeta}(t) \zeta(t) - \xi \right]),
+  \end{aligned}
+\end{equation}
+where we can define $\Phi_{n,m}(k_y,t)$ as
+\begin{equation} \label{eq:b13}
+  \begin{aligned}
+    &\Phi_{n,m}(k_y,t) \\
+    & \quad=
+    \sqrt{L_x}
+    \int_{-L_y/2}^{L_y/2}
+    \chi_n \bm{\left(}y - \mu(t)\bm{\right)}
+    \exp \bm{\left(}-i\left[k_y - \gamma(t) \right]y\bm{\right)} dy.
+  \end{aligned}
+\end{equation}
+Substituting ${k'_y} = k_y -\gamma(t)$ with $y' = y -\mu(t)$, and assuming that the size of the considered 2DEG sample in $y$-direction is considerably large ($L_y \rightarrow \infty$), we can obtain
+\begin{equation} \label{eq:b14}
+  \Phi_{n,m}({k'_y} ,t) =
+  {\sqrt{L_x}} e^{-i {k'_y}\mu}
+  \int_{-\infty}^{\infty} \chi_{n}(y') \exp(-i{k'_y} y') dy'.
+\end{equation}
+Moreover, we can identify that the above integral represents the Fourier transform of $\chi_n$ functions.
+In addition, using the symmetric conditions of the Fourier transform for Gauss-Hermite functions $\theta_n(x)$ \cite{celeghini21}
+\begin{equation} \label{eq:b15}
+  \mathcal{FT}[\theta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\theta_n(k/\kappa),
+\end{equation}
+we can simply the Eq.~(\ref{eq:b14}) as
+\begin{equation} \label{eq:b16}
+  \Phi_{n,m}({k'_y} ,t) =
+  \sqrt{L_x} e^{-i {k'_y}\mu} \widetilde{\chi}_n(k'_y),
+\end{equation}
+with
+\begin{equation} \label{eq:b17}
+  \widetilde{\chi}_{n}(k) =
+  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
+  \left(\frac{1}{\kappa} \right)^{1/2}
+  e^{-\flatfrac{k^2}{(2 \kappa^2)}}
+  \mathcal{H}_n (\flatfrac{k}{\kappa}).
+\end{equation}
+Finally, substitute Eq.~(\ref{eq:b16}) back into Eq.~(\ref{eq:b12}) and this leads to
+\begin{equation} \label{eq:b18}
+  \begin{aligned}
+    \phi_{n,m}(k_x,k_y,t)  = &
+    {\sqrt{L_x}} \widetilde{\chi}_n \bm{\left(} k_y - b\cos(\omega t)\bm{\right)} \\
+    & \times
+    \exp \left(
+      i\xi -ik_y  \left[d\sin(\omega t) + \frac{\hbar k_x}{eB} \right]
+    \right),
+  \end{aligned}
+\end{equation}
+where
+\begin{equation} \label{eq:b19}
+  b =
+  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
+\end{equation}
+and
+\begin{equation} \label{eq:b20}
+  d =
+ \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
+\end{equation}
+It is necessary to notice that $k_x$ is quantized with $k_x = \flatfrac{2\pi m}{L_x} ~,~ m \in \mathbb{Z}$.
+%===============================================================================
+
+%===============================================================================
 % Appendix C :
+%===============================================================================
 \section{\label{appendix_c} Floquet-Fermi golden rule for a dressed quantum  Hall system}
-\input{sections/appendix_c.tex}
 
+We derive the Floquet-Fermi golden rule for our dressed quantum Hall system with the help of the $t$-$t'$ formalism. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
+\begin{equation} \label{eq:c1}
+  \ket{\psi_{n,m}(t,t')} =
+  \exp(-\frac{i}{\hbar}\varepsilon_{n} t)\ket{\phi_{n,m}(t')},
+\end{equation}
+are derived by separating the aperiodic and periodic components of the Floquet states given in Eq.~(\ref{eq:14}).
+Additionally, these states fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
+\begin{equation} \label{eq:c2}
+  i \hbar \pdv{t}\ket{\psi_{n,m}(t,t')} =
+  H_F(t') \ket{\psi_{n,m}(t,t')},
+\end{equation}
+where the \textit{Floquet Hamiltonian} defined as
+\begin{equation} \label{eq:c3}
+  H_F(t') =
+  H_e(t') - i\hbar \pdv{t'}.
+\end{equation}
+Next, we can identify the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation as
+\begin{equation} \label{eq:c4}
+  U_F(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\left[t-t_0 \right]).
+\end{equation}
+The advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time ordering operators \cite{wackerl20}.
+
+We model the effect caused by impurities in the considered system as a single perturbation potential formed by a group of randomly distributed impurities.
+Thus, we introduce a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, and the $t$-$t'$-Schrödinger equation becomes
+\begin{equation} \label{eq:c5}
+  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')} =
+  \left[H_F(t') + V(\vb{r}) \right]\ket{\Psi_{n,m}(t,t')}.
+\end{equation}
+This introduces a new wave function solution $\ket{\Psi_{n,m}}$ for a system with a given perturbation. If $t\leq t_0$, both of the solutions for Eq.~(\ref{eq:c2}) and Eq.~(\ref{eq:c5}) coincide
+\begin{equation} \label{eq:c6}
+  \ket{\psi_{n,m}(t,t')} =\ket{\Psi_{n,m}(t,t')} \quad
+  \text{when} \quad
+  t \leq t_0.
+\end{equation}
+Next, we move our analysis into the interaction picture representation \cite{bruus04,mahan00} and in the interaction picture, we can identify the $t$-$t'$-Floquet state as
+\begin{equation} \label{eq:c7}
+  \ket{\Psi_{n,m}(t,t')}_I = U_0^{\dagger}(t,t_0;t')
+  \ket{\Psi_{n,m}(t,t')}.
+\end{equation}
+Due to time-independence, the perturbation in the interaction picture has the same form as the Schrödinger picture representation
+\begin{equation} \label{eq:c8}
+  V_I(\vb{r}) = U_0^{\dagger}(t,t_0;t')V(\vb{r})U_0(t,t_0;t') =
+  V(\vb{r}).
+\end{equation}
+This leads us to the $t$-$t'$-Schrödinger equation in the interaction picture representation
+\begin{equation} \label{eq:c9}
+  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')}_I =
+  V_I(\vb{r})\ket{\Psi_{n,m}(t,t')}_I,
+\end{equation}
+with the recursive solutions \cite{bruus04,mahan00}
+\begin{equation} \label{eq:c10}
+  \begin{aligned}
+  \ket{\Psi_{n,m}(t,t')}_I = &\ket{\Psi_{n,m}(t_0,t')}_I \\
+  &+
+  \frac{1}{i\hbar}
+  \int_{t_0}^t
+  V_I(\vb{r}) \ket{\Psi_{n,m}(t_1,t')}_I dt_1.
+  \end{aligned}
+\end{equation}
+Iterating the solution only up to the first order (Born approximation) we obtain
+\begin{equation} \label{eq:c11}
+  \begin{aligned}
+    \ket{\Psi_{n,m}(t,t')}_I \approx &\ket{\psi_{n,m}(t_0,t')} \\
+    &+
+    \frac{1}{i\hbar}
+    \int_{t_0}^t
+    V_I(\vb{r}) \ket{\psi_{n,m}(t_0,t')} dt_1.
+  \end{aligned}
+\end{equation}
+
+Since our $t$-$t'$-Floquet states create a basis, we can represent the solutions for the $t$-$t'$-Schrödinger equation given in Eq.~(\ref{eq:c5}) using our known $t$-$t'$-Floquet states as follows
+\begin{equation} \label{eq:c12}
+  \ket{\Psi_{\alpha}(t,t')} = \sum_{\beta} a_{\alpha,\beta}(t,t')
+  \ket{\psi_{\beta}(t,t')}.
+\end{equation}
+Here, we used a single term notation to represent two quantum numbers; $\alpha \equiv (n_{\alpha},m_{\alpha})$ and $\beta \equiv (n_{\beta},m_{\beta})$.
+Subsequently, we can identify the \textit{scattering amplitude} as $a_{\alpha,\beta}(t,t') =
+\braket{\psi_{\beta}(t,t')}{\Psi_{\alpha}(t,t')}$ and we can evaluate this with
+\begin{equation} \label{eq:c13}
+  \begin{aligned}
+  a_{\alpha,\beta}(t,t') = &
+  \braket{\psi_{\beta}(t,t')}{\psi_{\alpha}(t,t')} \\
+  &+
+  \frac{1}{i\hbar}
+  \int_{t_0}^t
+  \bra{\psi_{\beta}(t_1,t')}
+  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
+  \end{aligned}
+\end{equation}
+Since the $t$-$t'$-Floquet states are orthonormal and assuming $t_0 = 0$ and $\alpha \neq \beta$ this leads to
+\begin{equation} \label{eq:c14}
+  a_{\alpha,\beta}(t,t') =
+  -
+  \frac{i}{\hbar}
+  \int_{0}^t
+  \bra{\psi_{\beta}(t_1,t')}
+  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
+\end{equation}
+
+Next, we consider a scattering phenomenon when a electron scatters from a known $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with a constant quansienergy $\varepsilon$ as follows
+\begin{equation} \label{eq:c15}
+  \begin{aligned}
+  \ket{\psi_{\beta}(t,t')} &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
+  \ket{\phi_{\beta}(t')} \\
+  &
+  \xRightarrow{\text{scattering}}
+  \ket{\Psi_{\alpha}(t,t')} = \exp(-\frac{i}{\hbar}\varepsilon t)
+  \ket{\Phi_{\alpha}(t')}.
+  \end{aligned}
+\end{equation}
+\begin{figure}[b]
+  \includegraphics[scale=1.0]{figures/fig_6.pdf}
+  \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
+  \label{fig:2}
+\end{figure}
+This phenomenon is illustrated in Fig.~\ref{fig:2}.
+We can calculate the scattering amplitude for this scattering scenario using the expression derived in Eq.~(\ref{eq:c14}) as follows
+\begin{equation} \label{eq:c16}
+  \begin{aligned}
+    a_{\alpha\beta}(t,t') =
+    -\frac{i}{\hbar}
+    \int_{0}^t
+    e^{\frac{i}{\hbar}\left(\varepsilon_{\beta} - \varepsilon \right)t_1}
+    \bra{\phi_{\beta}(t')}
+    V(\vb{r}) \ket{\phi_{\alpha}(t')}  dt_1.
+  \end{aligned}
+\end{equation}
+By assuming for a long duration ($t \rightarrow \infty$), we can turn this integral into a delta distribution
+\begin{equation} \label{eq:c17}
+  \begin{aligned}
+    a_{\alpha\beta}(t') =
+    -2\pi i \delta(\varepsilon_{\beta} - \varepsilon)Q,
+  \end{aligned}
+\end{equation}
+where $Q = \bra{\phi_{\beta}(t')} V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using the completeness properties we can re-write this as
+\begin{equation} \label{eq:c18}
+    Q =
+    \sum_{\vb{k}}\sum_{\vb{k'}}
+    \braket{\phi_{\beta}(t')}{\vb{k'}}
+    \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}
+    \braket{\vb{k}}{\phi_{\alpha}(t')}.
+\end{equation}
+Moreover, separating $x$-directional and $y$-directional momentum components, we can simply this to obtain
+\begin{equation} \label{eq:c19}
+    Q =
+    \sum_{k_x}\sum_{{k'}_x}
+    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
+    V_{\vb{k'},\vb{k}}
+    \phi_{\beta}^{\dagger}(\vb{k'},t')
+    \phi_{\alpha}(\vb{k},t')  dk_y d{k'}_y,
+\end{equation}
+with $V_{\vb{k'},\vb{k}} = \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.
+
+Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
+Thus, we can describe the scattering potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
+\begin{equation} \label{eq:c20}
+  V(\vb{r}) =
+  \sum_{i=1}^{N_{imp}}
+  \upsilon (\vb{r}-\vb{r}_i).
+\end{equation}
+Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
+This model is characterized by the following two equations \cite{akkermans10}
+\begin{subequations}
+\begin{equation} \label{eq:c21a}
+  \expval{\upsilon(\vb{r})}_{imp} =0,
+\end{equation}
+\begin{equation} \label{eq:c21b}
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
+\end{equation}
+\end{subequations}
+where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
+In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
+Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
+\begin{equation} \label{eq:c22}
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
+\end{equation}
+where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
+\begin{equation} \label{eq:c23}
+  V(\vb{r}) =
+  \sum_{i=1}^{N_{imp}}
+  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
+\end{equation}
+Here we can identify the $\Upsilon_{imp}$ as the strength of the delta potential.
+Furthermore, we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
+\begin{subequations} \label{eq:c24}
+\begin{align}
+ V_{\vb{k'},\vb{k}} & =
+ \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
+ \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq:c24a} \\
+ & =
+ \sum_{i=1}^{N_{imp}}
+ \int_{-\infty}^{\infty} \left[
+ \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \right. \\
+ & \left. \qquad\quad\times
+ \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
+ \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \right] dy \label{eq:c24b} \\
+  & =
+ \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
+ e^{i(k'_y - k_y )y}
+ \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq:c24c}.
+\end{align}
+\end{subequations}
+Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs.
+Additionally, assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
+\begin{subequations} \label{eq:c25}
+  \begin{align}
+    V_{\vb{k'},\vb{k}}
+    & =
+    V_{k'_x,k_x}
+    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty}
+    e^{i\left({k'}_y - k_y \right)y_i} dy_i \label{eq:c25a} \\
+    & =
+    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y). \label{eq:c25b}
+  \end{align}
+\end{subequations}
+In the above equation we introduced
+\begin{equation} \label{eq:c26}
+  V_{{k'}_x,k_x} =
+  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x},
+\end{equation}
+which is a constant value for every $i$-th impurity.
+Moreover, $\eta_{imp}$ is the number of impurities in a unit area.
+It is important to note that in the above expression $\braket{x}{k_x} = e^{-ik_xx}$.
+
+Now using Eq.~(\ref{eq:10}) and Eq.~(\ref{eq:c25b}) on Eq.~(\ref{eq:c19}), we obtain
+\begin{equation} \label{eq:c27}
+  \begin{aligned}
+    Q  =
+    \sum_{k_x}\sum_{{k'}_x} &
+    {\eta_{imp} V_{{k'}_x,k_x}} L_x
+    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
+    \delta({k'}_y - k_y)
+    \\
+    & \times
+    \widetilde{\chi}_{n_{\beta}} \bm{\left(} {k'}_y -b\cos(\omega t) \bm{\right)}
+    \widetilde{\chi}_{n_{\alpha}}  \bm{\left(}k_y -b\cos(\omega t) \bm{\right)}
+    \\
+    & \times
+    e^{i[{k'}_y - k_y]d\sin(\omega t)}
+    e^{i[{k'}_y {y'}_0 - k_y y_0]}
+     dk'_y dk_y.
+  \end{aligned}
+\end{equation}
+Here we have changed the time variable $t' \rightarrow t$ only for the simplicity of notation. We can more simply this as
+\begin{equation} \label{eq:c28}
+  \begin{aligned}
+    Q =
+    \sum_{k_x}\sum_{{k'}_x} \eta_{imp} L_x V_{{k'}_x,k_x} I,
+  \end{aligned}
+\end{equation}
+with
+\begin{equation} \label{eq:c29}
+  \begin{aligned}
+    I =
+    \int_{-\infty}^{\infty}
+    \widetilde{\chi}_{n_{\beta}} &\bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
+    \widetilde{\chi}_{n_{\alpha}} \bm{\left(} k_y -b\cos(\omega t) \bm{\right)} \\
+    & \times
+    \exp \bm{(}
+      -ik_y  \left(y_0 - {y'}_0 \right)
+    \bm{)} dk_y.
+  \end{aligned}
+\end{equation}
+To avoid the energy exchange from the dressing field and electrons in Landau levels, the applied radiation must be a purely dressing field.
+Therefore, in this study we assume that the dressing field can only renormalize the the probability of electron scattering inside a same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
+This transform the Eq.~(\ref{eq:c29}) to
+\begin{equation} \label{eq:c30}
+    I =
+    \int_{-\infty}^{\infty}
+    \widetilde{\chi}_N^2 \bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
+    \exp \bm{(}
+      -ik_y  \left(y_0 - {y'}_0 \right)
+    \bm{)} dk_y.
+\end{equation}
+Using the Fourier transform of Gauss-Hermite functions \cite{celeghini21} and the convolution theorem \cite{arfken85,bracewell78} we obtain
+\begin{equation} \label{eq:c31}
+  \begin{aligned}
+    I =
+    {2\pi} &
+    \exp \bm{(} b({y'}_0 - y_0)\cos(\omega t) \bm{)} \\
+    & \times
+    \int_{-\infty}^{\infty}
+    {\chi}_{N}(y)
+    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
+  \end{aligned}
+\end{equation}
+Finally, we can evaluate the scattering amplitude derived in Eq.~(\ref{eq:c17}) for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as follows
+\begin{equation} \label{eq:c32}
+  \begin{aligned}
+    a_{\alpha\beta}&(k_x,k'_x,t)
+    \\
+    & =
+    -2\pi i
+    \eta_{imp} L_x V_{{k'}_x,k_x}
+    e^{ b({y'}_0 - y_0)\cos(\omega t)}\\
+    & \quad\times
+    \delta(\varepsilon_{N} - \varepsilon)
+    \int_{-\infty}^{\infty}
+    {\chi}_{N}(y)
+    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
+  \end{aligned}
+\end{equation}
+Since this scattering amplitude is time-periodic, we can write this as a Fourier series expansion
+\begin{equation} \label{eq:c33}
+    a_{\alpha\beta}(k_x,k'_x,t) =
+    \sum_{l=-\infty}^{\infty} a^l_{\alpha\beta}(k_x,k'_x) e^{-il\omega t}.
+\end{equation}
+In addition, using Jacobi-Anger expansion \cite{cuyt08,abramowitz64}
+\begin{equation} \label{eq:c34}
+    e^{iz\cos(\theta)} = \sum_{l=-\infty}^{\infty} i^l J_l(z) e^{-il\theta},
+\end{equation}
+where $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, we can re-write the Eq.~(\ref{eq:c32}) as follows
+\begin{equation} \label{eq:c35}
+  \begin{aligned}
+    a_{\alpha\beta}&(k_x,k'_x,t)  \\
+    & =
+    \sum_{l=-\infty}^{\infty}
+    -2\pi i^{l+1}
+    \eta_{imp} L_x V_{{k'}_x,k_x}
+    J_l\bm{(}b({y'}_0 - y_0)\bm{)} \\
+    & \quad\times
+    \delta(\varepsilon_{N} - \varepsilon)
+    \int_{-\infty}^{\infty}
+    {\chi}_{N}(y)
+    {\chi}_{N}(y_0 - {y'}_0 - y)  dy \;e^{-il\omega t}.
+  \end{aligned}
+\end{equation}
+Thus, we can identify the Fourier series component of the scattering amplitude as
+\begin{equation} \label{eq:c36}
+  \begin{aligned}
+    a^l_{\alpha\beta}(k_x,k'_x) = &
+    -2\pi i^{l+1}
+    \eta_{imp} L_x V_{{k'}_x,k_x}\\
+    & \times
+    \delta(\varepsilon_{N} - \varepsilon)
+    J_l\bm{(}b({y'}_0 - y_0)\bm{)}\\
+    & \times
+    \int_{-\infty}^{\infty}
+    {\chi}_N(y)
+    {\chi}_N(y_0 - {y'}_0 - y) dy.
+  \end{aligned}
+\end{equation}
+Furthermore, we can define \textit{transition probability matrix} as
+\begin{equation} \label{eq:c37}
+    \left(A_{\alpha\beta} \right)^{l,l'} =
+    a^l_{\alpha\beta}\left[a^{l'}_{\alpha\beta} \right]^{*},
+\end{equation}
+and this becomes
+\begin{equation} \label{eq:c38}
+  \begin{aligned}
+      \left(A_{\alpha\beta} \right)^{l,l'}(k_x,k'_x) = &
+      \left({ 2 \pi \eta_{imp} L_x V_{{k'}_x,k_x}}\right)^2
+      \delta^2(\varepsilon_{N} - \varepsilon) \\
+      & \times
+      J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)}\\
+      & \times
+      \left|
+      \int_{-\infty}^{\infty}
+      {\chi}_N(y)
+      {\chi}_N(y_0 - {y'}_0 - y) dy \right|^2.
+  \end{aligned}
+\end{equation}
+Then describing the square of the delta distribution using the following interpretation \cite{dini16,kibis14}
+\begin{equation} \label{eq:c39}
+    \delta^2(\varepsilon) =
+    \delta(\varepsilon)\delta(0) =
+    \frac{\delta(\varepsilon)}{2\pi \hbar}
+    \int_{-t/2}^{t/2} e^{i0\times t'/\hbar} dt'\; =
+    \frac{\delta(\varepsilon)t}{2\pi \hbar},
+\end{equation}
+and executing the time derivation operation on each matrix element of transition probability matrix, we receive the \textit{transition amplitude matrix} elements
+\begin{equation} \label{eq:40}
+  \begin{aligned}
+    \Gamma_{\alpha\beta}^{ll'}(k_x,k'_x) = &
+    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar} |V_{{k'}_x,k_x}|^2
+    \delta(\varepsilon_{\beta} - \varepsilon)\\
+    & \times
+    J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)} \\
+    & \times
+    \left|
+    \int_{-\infty}^{\infty}
+    {\chi}_N(y)
+    {\chi}_N(y_0 - {y'}_0 - y) dy \right|^2.
+  \end{aligned}
+\end{equation}
+
+Additionally, the inverse scattering time matrix can be identified as the sum of all available momentum over the impurity averaged transition probability matrix element \cite{wackerl20,wackerlthesis20}
+\begin{equation} \label{eq:41}
+    \left(\frac{1}{\tau(\varepsilon,k_x)} \right)^{ll'}_{\alpha\beta} =
+    \frac{1}{L_x} \sum_{{k'}_x}
+    \expval**{\Gamma_{\alpha\beta}^{ll'}({k'}_x,k_x)}_{imp}.
+\end{equation}
+Next, applying the 1-dimensional momentum continuum limit $\sum_{{k'}_x} \longrightarrow {L_x}/{2\pi}\int d {k'}_x$, we can obtain
+\begin{widetext}
+\begin{equation} \label{eq:42}
+  \begin{aligned}
+    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_{\alpha\beta} = &
+    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar}
+    \frac{V_{imp}}{2\pi}
+    \delta(\varepsilon_{\beta} - \varepsilon) \\
+    & \times
+    \int_{-\infty}^{\infty} \left\{
+    J_l\bm{\left(}\frac{b\hbar}{eB}({k}_x - {k'}_x)\bm{\right)}
+    J_{l'}\bm{\left(}\frac{b\hbar}{eB}({k}_x - {k'}_x)\bm{\right)}
+    \left|
+    \int_{-\infty}^{\infty}
+    {\chi}_N(y)
+    {\chi}_N \bm{\left(}\frac{\hbar}{eB} ({k'}_x - {k}_x) - y \bm{\right)} dy\right|^2 \right\} d {k'}_x.
+  \end{aligned}
+\end{equation}
+Here an impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2}_{imp} = V_{imp}$.
+Finally, using substitutions $k'_x = k_1$ and $y = \flatfrac{\hbar{k_2}}{(eB)}$, we can derive our expression for the inverse scattering time matrix for $N$-th Landau
+level as follows
+\begin{equation} \label{eq:43}
+  \begin{aligned}
+    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_{N} &=
+    \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{e^2B^2}
+    \delta(\varepsilon - \varepsilon_{N}) \\
+    & \times
+    \int_{-\infty}^{\infty} \left\{
+    J_l\bm{\left(}\frac{b\hbar}{eB}({k}_x - k_1)\bm{\right)}
+    J_{l'}\bm{\left(}\frac{b\hbar}{eB}({k}_x - k_1)\bm{\right)}
+    \left|
+    \int_{-\infty}^{\infty}
+    {\chi}_N\left(\frac{\hbar}{eB}k_2 \right)
+    {\chi}_N \bm{\left(}\frac{\hbar}{eB} (k_1 - k_x - k_2) \bm{\right)} dk_2 \right|^2 \right\} d k_1.
+  \end{aligned}
+\end{equation}
+\end{widetext}
+%===============================================================================
+
+%===============================================================================
 % Appendix D :
+%===============================================================================
 \section{\label{appendix_d} Current operators for a dressed quantum Hall system}
-\input{sections/appendix_d.tex}
 
+In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system.
+We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(\ref{eq:1}) and we identified them as the Floquet states in Eq.~(\ref{eq:14}).
+For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(\ref{eq:10}) as quantum states using their corresponding quantum numbers as follows
+\begin{equation} \label{eq:d1}
+  \ket{\phi_{n,m}} = \ket{n,k_x}.
+\end{equation}
+Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
+\begin{equation} \label{eq:d2}
+  \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
+\end{equation}
+Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
+\begin{equation} \label{eq:d3}
+  \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
+\end{equation}
+where $\widetilde{m}$ is the mass of the considering particle.
+
+First, we consider the $x$-directional particle current operator component, and we can identify that as
+\begin{equation} \label{eq:d4}
+  \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
+\end{equation}
+Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
+\begin{equation} \label{eq:d5}
+  \left({j}_x \right)_{nm,n'm'} =
+  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
+\end{equation}
+and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq:7}) as follows
+\begin{equation} \label{eq:d6}
+  \begin{aligned}
+    \left({j}_x \right)_{nm,n'm'} = &
+    \frac{1}{{\widetilde{m}}}
+    \delta_{k_x,k'_x}
+    \int
+    \left(\hbar k'_x + eBy\right) \\
+    & \times
+     \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
+    \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
+    dy.
+  \end{aligned}
+\end{equation}
+Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
+\begin{equation} \label{eq:d7}
+  \begin{aligned}
+    \left({j}_x \right)_{nm,n'm'} =
+    \frac{1}{{\widetilde{m}}}
+    \delta_{k_x,k'_x}
+    \int &
+    \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right] \\
+    & \times
+    \chi_{n}(\bar{y})
+    \chi_{n'}(\bar{y})
+    d\bar{y}.
+  \end{aligned}
+\end{equation}
+Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
+\begin{subequations} \label{eq:d8}
+  \begin{align}
+    \int
+    \chi_{n}({y})
+    \chi_{n'}({y}) d{y} &=
+    \delta_{n',n}, \\
+    \int
+    y \chi_{n}({y})\chi_{n'}({y}) d{y} &=
+    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1} \right),
+  \end{align}
+\end{subequations}
+we simplify the matrix elements of $x$-directional current operator to obtain
+\begin{equation} \label{eq:d9}
+  \begin{aligned}
+    &\left({j}_x \right)_{nm,n'm'} =
+    \frac{eB}{{\widetilde{m}}}
+    \delta_{k_x,k'_x} \\
+    & \qquad\times
+    \left[
+    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1}\right)
+    + \zeta(t) \delta_{n',n}
+    \right].
+  \end{aligned}
+\end{equation}
+Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
+\begin{equation} \label{eq:d10}
+  \begin{aligned}
+      \left({j}_x \right)_{nm,n'm'} =&
+      \frac{eB}{\widetilde{m}}
+      \delta_{k_x,k'_x} \\
+      & \times
+      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+      \delta_{n',n-1} \right).
+  \end{aligned}
+\end{equation}
+For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
+\begin{equation} \label{eq:d11}
+  \begin{aligned}
+      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
+      \frac{e^2B}{{m_e}}
+      \delta_{k_x,k'_x}\\
+      & \times
+      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+      \delta_{n',n-1} \right).
+  \end{aligned}
+\end{equation}
+
+Moreover, we can identify the $y$-directional current operator component as
+\begin{equation} \label{eq:d12}
+  \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
+\end{equation}
+Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
+\begin{equation} \label{eq:d13}
+  \left({j}_y \right)_{nm,n'm'} =
+  \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
+\end{equation}
+After following the same steps done for the $x$-directional current operator, we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
+\begin{equation} \label{eq:d14}
+  \begin{aligned}
+    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
+    \frac{ie\hbar}{{m_e}}
+    \delta_{k_x,k'_x} \\
+    & \times
+    \left(
+    \sqrt{\frac{n}{2}} \delta_{n',n-1}
+    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
+    \right).
+  \end{aligned}
+\end{equation}
+%===============================================================================
+\end{appendix}
+
+%===============================================================================
 % Bibliography
+%===============================================================================
 \bibliography{aps_article}
+%===============================================================================
 

### 2021-08-22 paper/dressed_quantum_hall/dressed_quantum_hall.tex
Add final folder

--- 2021-08-22 paper/v3-release/aps_article.tex
@@
 %===============================================================================
-\title{A generalized model for the charge transport properties of
-\\dressed quantum Hall systems}
+\title{A generalized model for the charge transport properties of dressed quantum Hall systems}
 %===============================================================================
@@
 \begin{figure}[b]
-\includegraphics[scale=0.9]{figures/fig_1.pdf}
+\includegraphics[scale=0.9]{fig_1}
 \caption{\label{fig:1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.55]{figures/fig_2}
+\includegraphics[scale=0.55]{fig_2}
 \caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_3}
+\includegraphics[scale=0.54]{fig_3}
 \caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_4}
+\includegraphics[scale=0.54]{fig_4}
 \caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_5}
+\includegraphics[scale=0.54]{fig_5}
 \caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[b]
-  \includegraphics[scale=1.0]{figures/fig_6.pdf}
+  \includegraphics[scale=1.0]{fig_6.pdf}
   \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
@@
 %===============================================================================
-\bibliography{aps_article}
+%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
+%Control: key (0)
+%Control: author (72) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}%
+\begin{thebibliography}{73}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{https://doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Liu}\ \emph {et~al.}(2016)\citenamefont {Liu},
+  \citenamefont {Weiss}, \citenamefont {Duan}, \citenamefont {Cheng},
+  \citenamefont {Huang},\ and\ \citenamefont {Duan}}]{liu16}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {N.~O.}\ \bibnamefont {Weiss}},
+  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Duan}}, \bibinfo {author}
+  {\bibfnamefont {H.~C.}\ \bibnamefont {Cheng}}, \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Huang}},\ and\ \bibinfo {author}
+  {\bibfnamefont {X.}~\bibnamefont {Duan}},\ }\href
+  {https://doi.org/10.1038/natrevmats.2016.42} {\bibfield  {journal} {\bibinfo
+  {journal} {Nat. Rev. Mater.}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo
+  {pages} {16042} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wijesekara}\ \emph {et~al.}(2020)\citenamefont
+  {Wijesekara}, \citenamefont {Gunapala}, \citenamefont {Stockman},\ and\
+  \citenamefont {Premaratne}}]{wijesekara20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~T.}\ \bibnamefont
+  {Wijesekara}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+  {Gunapala}}, \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont
+  {Stockman}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Premaratne}},\ }\href {https://doi.org/10.1103/PhysRevB.101.245402}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
+  {volume} {101}},\ \bibinfo {pages} {245402} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tao}\ \emph {et~al.}(2020)\citenamefont {Tao},
+  \citenamefont {Chen}, \citenamefont {Li}, \citenamefont {Wang}, \citenamefont
+  {Xu},\ and\ \citenamefont {Xu}}]{tao21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Tao}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Chen}}, \bibinfo
+  {author} {\bibfnamefont {Z.}~\bibnamefont {Li}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Xu}},\ and\ \bibinfo {author} {\bibfnamefont {J.-B.}\
+  \bibnamefont {Xu}},\ }\href {https://doi.org/10.1002/inf2.12148} {\bibfield
+  {journal} {\bibinfo  {journal} {InfoMat}\ }\textbf {\bibinfo {volume} {3}},\
+  \bibinfo {pages} {36} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wijesekara}\ \emph {et~al.}(2021)\citenamefont
+  {Wijesekara}, \citenamefont {Gunapala},\ and\ \citenamefont
+  {Premaratne}}]{wijesekara21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~T.}\ \bibnamefont
+  {Wijesekara}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+  {Gunapala}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Premaratne}},\ }\href {https://doi.org/10.1103/PhysRevB.104.045405}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
+  {volume} {104}},\ \bibinfo {pages} {045405} (\bibinfo {year}
+  {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rodrigo}\ \emph {et~al.}(2015)\citenamefont
+  {Rodrigo}, \citenamefont {Limaj}, \citenamefont {Janner}, \citenamefont
+  {Etezadi}, \citenamefont {De~Abajo}, \citenamefont {Pruneri},\ and\
+  \citenamefont {Altug}}]{rodrigo15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Rodrigo}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Limaj}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Janner}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Etezadi}}, \bibinfo {author}
+  {\bibfnamefont {F.~J.~G.}\ \bibnamefont {De~Abajo}}, \bibinfo {author}
+  {\bibfnamefont {V.}~\bibnamefont {Pruneri}},\ and\ \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Altug}},\ }\href
+  {https://doi.org/10.1126/science.aab2051} {\bibfield  {journal} {\bibinfo
+  {journal} {Science}\ }\textbf {\bibinfo {volume} {349}},\ \bibinfo {pages}
+  {165} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pirandola}\ \emph {et~al.}(2018)\citenamefont
+  {Pirandola}, \citenamefont {Bardhan}, \citenamefont {Gehring}, \citenamefont
+  {Weedbrook},\ and\ \citenamefont {Lloyd}}]{pirandola18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Pirandola}}, \bibinfo {author} {\bibfnamefont {B.~R.}\ \bibnamefont
+  {Bardhan}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Gehring}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Weedbrook}},\ and\
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Lloyd}},\ }\href
+  {https://doi.org/10.1038/s41566-018-0301-6} {\bibfield  {journal} {\bibinfo
+  {journal} {Nat. Photoics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
+  {pages} {724} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hapuarachchi}\ \emph {et~al.}(2018)\citenamefont
+  {Hapuarachchi}, \citenamefont {Mallawaarachchi}, \citenamefont {Hattori},
+  \citenamefont {Zhu},\ and\ \citenamefont {Premaratne}}]{hapuarachchi2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Hapuarachchi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Mallawaarachchi}}, \bibinfo {author} {\bibfnamefont {H.~T.}\ \bibnamefont
+  {Hattori}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Zhu}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Premaratne}},\ }\href
+  {https://doi.org/10.1088/1361-648X/aaa46d} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Phys. Condens. Matter.}\ }\textbf {\bibinfo {volume} {30}},\
+  \bibinfo {pages} {054006} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Weeraddana}\ \emph {et~al.}(2015)\citenamefont
+  {Weeraddana}, \citenamefont {Premaratne},\ and\ \citenamefont
+  {Andrews}}]{weeraddana15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Weeraddana}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Premaratne}},\ and\ \bibinfo {author} {\bibfnamefont {D.~L.}\ \bibnamefont
+  {Andrews}},\ }\href {https://10.1103/PhysRevB.92.035128} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {92}},\ \bibinfo {pages} {035128} (\bibinfo {year} {2015})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Yuan}\ \emph {et~al.}(2016)\citenamefont {Yuan},
+  \citenamefont {Liu},\ and\ \citenamefont {Sargent}}]{yuan16}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Yuan}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}},\ and\
+  \bibinfo {author} {\bibfnamefont {E.~H.}\ \bibnamefont {Sargent}},\ }\href
+  {https://doi.org/10.1038/nenergy.2016.16} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature Energy}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo
+  {pages} {16016} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2018)\citenamefont {Sun},
+  \citenamefont {Ouellette}, \citenamefont {de~Arquer}, \citenamefont {Voznyy},
+  \citenamefont {Kim}, \citenamefont {Wei}, \citenamefont {Proppe},
+  \citenamefont {Saidaminov}, \citenamefont {Xu}, \citenamefont {Liu} \emph
+  {et~al.}}]{sun18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Sun}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Ouellette}},
+  \bibinfo {author} {\bibfnamefont {F.~P.~G.}\ \bibnamefont {de~Arquer}},
+  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Voznyy}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Kim}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Wei}}, \bibinfo {author} {\bibfnamefont
+  {A.~H.}\ \bibnamefont {Proppe}}, \bibinfo {author} {\bibfnamefont {M.~I.}\
+  \bibnamefont {Saidaminov}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Xu}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Liu}}, \emph {et~al.},\ }\href {https://doi.org/10.1038/s41467-018-06342-7}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nat. Commun.}\ }\textbf {\bibinfo
+  {volume} {9}},\ \bibinfo {pages} {4003} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Huh}\ \emph {et~al.}(2015)\citenamefont {Huh},
+  \citenamefont {Guerreschi}, \citenamefont {Peropadre}, \citenamefont
+  {McClean},\ and\ \citenamefont {Aspuru-Guzik}}]{huh15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Huh}}, \bibinfo {author} {\bibfnamefont {G.~G.}\ \bibnamefont {Guerreschi}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Peropadre}}, \bibinfo
+  {author} {\bibfnamefont {J.~R.}\ \bibnamefont {McClean}},\ and\ \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Aspuru-Guzik}},\ }\href
+  {https://doi.org/10.1038/nphoton.2015.153} {\bibfield  {journal} {\bibinfo
+  {journal} {Nat. Photonics}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo
+  {pages} {615} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Slussarenko}\ and\ \citenamefont
+  {Pryde}(2019)}]{slussarenko19}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Slussarenko}}\ and\ \bibinfo {author} {\bibfnamefont {G.~J.}\ \bibnamefont
+  {Pryde}},\ }\href {https://doi.org/10.1063/1.5115814} {\bibfield  {journal}
+  {\bibinfo  {journal} {Appl. Phys. Rev.}\ }\textbf {\bibinfo {volume} {6}},\
+  \bibinfo {pages} {041303} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Andersen}(2021)}]{andersen21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.~L.}\ \bibnamefont
+  {Andersen}},\ }\href {https://doi.org/10.1038/d41586-021-00488-z} {\bibfield
+  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {591}},\
+  \bibinfo {pages} {40} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Marais}\ \emph {et~al.}(2018)\citenamefont {Marais},
+  \citenamefont {Adams}, \citenamefont {Ringsmuth}, \citenamefont {Ferretti},
+  \citenamefont {Gruber}, \citenamefont {Hendrikx}, \citenamefont {Schuld},
+  \citenamefont {Smith}, \citenamefont {Sinayskiy}, \citenamefont {Kr{\"u}ger}
+  \emph {et~al.}}]{marais18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Marais}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Adams}},
+  \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont {Ringsmuth}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Ferretti}}, \bibinfo {author}
+  {\bibfnamefont {J.~M.}\ \bibnamefont {Gruber}}, \bibinfo {author}
+  {\bibfnamefont {R.}~\bibnamefont {Hendrikx}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Schuld}}, \bibinfo {author} {\bibfnamefont
+  {S.~L.}\ \bibnamefont {Smith}}, \bibinfo {author} {\bibfnamefont
+  {I.}~\bibnamefont {Sinayskiy}}, \bibinfo {author} {\bibfnamefont {T.~P.}\
+  \bibnamefont {Kr{\"u}ger}}, \emph {et~al.},\ }\href
+  {https://doi.org/10.1098/rsif.2018.0640} {\bibfield  {journal} {\bibinfo
+  {journal} {J. R. Soc. Interface}\ }\textbf {\bibinfo {volume} {15}},\
+  \bibinfo {pages} {20180640} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bian}\ \emph {et~al.}(2020)\citenamefont {Bian},
+  \citenamefont {Sun}, \citenamefont {Cai}, \citenamefont {Wang},\ and\
+  \citenamefont {Zhao}}]{bian20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Bian}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Sun}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Cai}}, \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Wang}},\ and\ \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Zhao}},\ }\href
+  {https://doi.org/10.1073/pnas.2011660117} {\bibfield  {journal} {\bibinfo
+  {journal} {Proc. Natl. Acad. Sci.}\ }\textbf {\bibinfo {volume} {117}},\
+  \bibinfo {pages} {22736} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rivera}\ and\ \citenamefont
+  {Kaminer}(2020)}]{rivera20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Rivera}}\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Kaminer}},\ }\href {https://doi.org/10.1038/s42254-020-0224-2} {\bibfield
+  {journal} {\bibinfo  {journal} {Nat. Rev. Phys.}\ }\textbf {\bibinfo {volume}
+  {2}},\ \bibinfo {pages} {538} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Shalaev}(2007)}]{shalaev07}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~M.}\ \bibnamefont
+  {Shalaev}},\ }\href {https://doi.org/10.1038/nphoton.2006.49} {\bibfield
+  {journal} {\bibinfo  {journal} {Nat. Photonics}\ }\textbf {\bibinfo {volume}
+  {1}},\ \bibinfo {pages} {41} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Si}\ \emph {et~al.}(2014)\citenamefont {Si},
+  \citenamefont {Sikdar}, \citenamefont {Chen}, \citenamefont {Eftekhari},
+  \citenamefont {Xu}, \citenamefont {Tang}, \citenamefont {Xiong},
+  \citenamefont {Guo}, \citenamefont {Zhang}, \citenamefont {Lu} \emph
+  {et~al.}}]{si14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~J.}\ \bibnamefont
+  {Si}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Sikdar}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Chen}}, \bibinfo {author}
+  {\bibfnamefont {F.}~\bibnamefont {Eftekhari}}, \bibinfo {author}
+  {\bibfnamefont {Z.}~\bibnamefont {Xu}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Tang}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Xiong}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Guo}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Zhang}}, \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Lu}}, \emph {et~al.},\ }\href
+  {https://doi.org/10.1021/nn504615a} {\bibfield  {journal} {\bibinfo
+  {journal} {ACS Nano}\ }\textbf {\bibinfo {volume} {8}},\ \bibinfo {pages}
+  {11086} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hapuarachchi}\ \emph {et~al.}(2019)\citenamefont
+  {Hapuarachchi}, \citenamefont {Gunapala},\ and\ \citenamefont
+  {Premaratne}}]{hapuarachchi19}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Hapuarachchi}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+  {Gunapala}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Premaratne}},\ }\href {https://doi.org/10.1088/1361-648X/ab1234} {\bibfield
+  {journal} {\bibinfo  {journal} {J. Phys. Condens. Matter.}\ }\textbf
+  {\bibinfo {volume} {31}},\ \bibinfo {pages} {325301} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Perera}\ \emph {et~al.}(2020)\citenamefont {Perera},
+  \citenamefont {Gunapala}, \citenamefont {Stockman},\ and\ \citenamefont
+  {Premaratne}}]{perera20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Perera}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+  {Gunapala}}, \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont
+  {Stockman}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Premaratne}},\ }\href {https://doi.org/10.1021/acs.jpcc.0c10507} {\bibfield
+  {journal} {\bibinfo  {journal} {J. Phys. Chem. C}\ }\textbf {\bibinfo
+  {volume} {124}},\ \bibinfo {pages} {27694} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chow}\ and\ \citenamefont {Jahnke}(2013)}]{chow13}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~W.}\ \bibnamefont
+  {Chow}}\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Jahnke}},\
+  }\href {https://doi.org/10.1016/j.pquantelec.2013.04.001} {\bibfield
+  {journal} {\bibinfo  {journal} {Prog. Quantum. Electron.}\ }\textbf {\bibinfo
+  {volume} {37}},\ \bibinfo {pages} {109} (\bibinfo {year} {2013})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Jayasekara}\ \emph {et~al.}(2016)\citenamefont
+  {Jayasekara}, \citenamefont {Premaratne}, \citenamefont {Gunapala},\ and\
+  \citenamefont {Stockman}}]{jayasekara16}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Jayasekara}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Premaratne}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+  {Gunapala}},\ and\ \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont
+  {Stockman}},\ }\href {https://doi.org/10.1063/1.4945378} {\bibfield
+  {journal} {\bibinfo  {journal} {J. Appl. Phys.}\ }\textbf {\bibinfo {volume}
+  {119}},\ \bibinfo {pages} {133101} (\bibinfo {year} {2016})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Premaratne}\ and\ \citenamefont
+  {Stockman}(2017)}]{premaratne17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Premaratne}}\ and\ \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont
+  {Stockman}},\ }\href {https://doi.org/10.1364/AOP.9.000079} {\bibfield
+  {journal} {\bibinfo  {journal} {Adv. Opt. Photonics}\ }\textbf {\bibinfo
+  {volume} {9}},\ \bibinfo {pages} {79} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Tsang}(2010)}]{tsang10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Tsang}},\ }\href {https://doi.org/10.1103/PhysRevA.81.063837} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+  {81}},\ \bibinfo {pages} {063837} (\bibinfo {year} {2010})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Liu}\ \emph {et~al.}(2017)\citenamefont {Liu},
+  \citenamefont {Zhu}, \citenamefont {Gunapala}, \citenamefont {Stockman},\
+  and\ \citenamefont {Premaratne}}]{liu17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Zhu}}, \bibinfo
+  {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Gunapala}}, \bibinfo {author}
+  {\bibfnamefont {M.~I.}\ \bibnamefont {Stockman}},\ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Premaratne}},\ }\href
+  {https://doi.org/10.1021/acsnano.7b06735} {\bibfield  {journal} {\bibinfo
+  {journal} {ACS Nano}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages}
+  {12573} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Devi}\ \emph {et~al.}(2020)\citenamefont {Devi},
+  \citenamefont {Gunapala}, \citenamefont {Stockman},\ and\ \citenamefont
+  {Premaratne}}]{devi20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Devi}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Gunapala}},
+  \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont {Stockman}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Premaratne}},\ }\href
+  {https://doi.org/10.1103/PhysRevA.102.013701} {\bibfield  {journal} {\bibinfo
+   {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {102}},\ \bibinfo
+  {pages} {013701} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kitagawa}\ \emph {et~al.}(2011)\citenamefont
+  {Kitagawa}, \citenamefont {Oka}, \citenamefont {Brataas}, \citenamefont
+  {Fu},\ and\ \citenamefont {Demler}}]{kitagawa11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Kitagawa}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Oka}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Brataas}}, \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Fu}},\ and\ \bibinfo {author}
+  {\bibfnamefont {E.}~\bibnamefont {Demler}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.84.235108} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {84}},\ \bibinfo
+  {pages} {235108} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhou}\ and\ \citenamefont {Wu}(2011)}]{zhou11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhou}}\ and\ \bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont {Wu}},\
+  }\href {https://doi.org/10.1103/PhysRevB.83.245436} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys.Rev.B}\ }\textbf {\bibinfo {volume} {83}},\
+  \bibinfo {pages} {245436} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kibis}(2014)}]{kibis14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.~V.}\ \bibnamefont
+  {Kibis}},\ }\href {https://doi.org/10.1209/0295-5075/107/57003} {\bibfield
+  {journal} {\bibinfo  {journal} {Europhys. Lett.}\ }\textbf {\bibinfo {volume}
+  {107}},\ \bibinfo {pages} {57003} (\bibinfo {year} {2014})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Pervishko}\ \emph {et~al.}(2015)\citenamefont
+  {Pervishko}, \citenamefont {Kibis}, \citenamefont {Morina},\ and\
+  \citenamefont {Shelykh}}]{pervishko15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
+  {Pervishko}}, \bibinfo {author} {\bibfnamefont {O.~V.}\ \bibnamefont
+  {Kibis}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Morina}},\ and\
+  \bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont {Shelykh}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.92.205403} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo
+  {pages} {205403} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Morina}\ \emph {et~al.}(2015)\citenamefont {Morina},
+  \citenamefont {Kibis}, \citenamefont {Pervishko},\ and\ \citenamefont
+  {Shelykh}}]{morina15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Morina}}, \bibinfo {author} {\bibfnamefont {O.~V.}\ \bibnamefont {Kibis}},
+  \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont {Pervishko}},\ and\
+  \bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont {Shelykh}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.91.155312} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {91}},\ \bibinfo
+  {pages} {155312} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dehghani}\ \emph {et~al.}(2015)\citenamefont
+  {Dehghani}, \citenamefont {Oka},\ and\ \citenamefont {Mitra}}]{dehghani15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Dehghani}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Oka}},\ and\
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mitra}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.91.155422} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {91}},\ \bibinfo
+  {pages} {155422} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dini}\ \emph {et~al.}(2016)\citenamefont {Dini},
+  \citenamefont {Kibis},\ and\ \citenamefont {Shelykh}}]{dini16}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Dini}}, \bibinfo {author} {\bibfnamefont {O.~V.}\ \bibnamefont {Kibis}},\
+  and\ \bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont {Shelykh}},\
+  }\href {https://doi.org/10.1103/PhysRevB.93.235411} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {93}},\
+  \bibinfo {pages} {235411} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wackerl}\ \emph {et~al.}(2020)\citenamefont
+  {Wackerl}, \citenamefont {Wenk},\ and\ \citenamefont
+  {Schliemann}}]{wackerl20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Wackerl}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Wenk}},\ and\
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Schliemann}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.101.184204} {\bibfield  {journal} {\bibinfo
+   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {101}},\ \bibinfo
+  {pages} {184204} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Premaratne}\ and\ \citenamefont
+  {Agrawal}(2021)}]{premaratne21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Premaratne}}\ and\ \bibinfo {author} {\bibfnamefont {G.~P.}\ \bibnamefont
+  {Agrawal}},\ }\href@noop {} {\emph {\bibinfo {title} {Theoretical Foundations
+  of Nanoscale Quantum Devices}}}\ (\bibinfo  {publisher} {Cambridge University
+  Press},\ \bibinfo {year} {2021})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Grifoni}\ and\ \citenamefont
+  {Hänggi}(1998)}]{grifoni98}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Grifoni}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Hänggi}},\ }\href {https://doi.org/10.1016/S0370-1573(98)00022-2}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rep.}\ }\textbf {\bibinfo
+  {volume} {304}},\ \bibinfo {pages} {229} (\bibinfo {year}
+  {1998})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cohen-Tannoudji}\ \emph {et~al.}(1998)\citenamefont
+  {Cohen-Tannoudji}, \citenamefont {Dupont-Roc},\ and\ \citenamefont
+  {Grynberg}}]{cohen98}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Cohen-Tannoudji}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Dupont-Roc}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Grynberg}},\ }\href@noop {} {\emph {\bibinfo {title} {Atom—Photon
+  Interactions}}}\ (\bibinfo  {publisher} {John Wiley \& Sons, Ltd},\ \bibinfo
+  {year} {1998})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Scully}\ and\ \citenamefont
+  {Zubairy}(2001)}]{scully01}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Scully}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Zubairy}},\ }\href@noop {} {\emph {\bibinfo {title} {Introduction to Quantum
+  Optics}}}\ (\bibinfo  {publisher} {Cambridge University Press},\ \bibinfo
+  {year} {2001})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Girvin}\ and\ \citenamefont
+  {Prange}(1990)}]{girvin90}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Girvin}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Prange}},\ }\href@noop {} {\emph {\bibinfo {title} {The quantum Hall
+  effect}}}\ (\bibinfo  {publisher} {Springer-Verlag, New York},\ \bibinfo
+  {year} {1990})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ando}\ \emph {et~al.}(1972)\citenamefont {Ando},
+  \citenamefont {Matsumoto}, \citenamefont {Uemura}, \citenamefont
+  {Kobayashi},\ and\ \citenamefont {Komatsubara}}]{ando72}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ando}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Matsumoto}},
+  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Uemura}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Kobayashi}},\ and\ \bibinfo
+  {author} {\bibfnamefont {K.~F.}\ \bibnamefont {Komatsubara}},\ }\href
+  {https://doi.org/10.1143/JPSJ.32.859} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume} {32}},\ \bibinfo
+  {pages} {859} (\bibinfo {year} {1972})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ando}\ and\ \citenamefont
+  {Uemura}(1974{\natexlab{a}})}]{ando74_1}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ando}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Uemura}},\
+  }\href {https://doi.org/10.1143/JPSJ.36.959} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume} {36}},\ \bibinfo
+  {pages} {959} (\bibinfo {year} {1974}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ando}(1974{\natexlab{a}})}]{ando74_2}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ando}},\ }\href {https://doi.org/10.1143/JPSJ.36.1521} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume}
+  {36}},\ \bibinfo {pages} {1521} (\bibinfo {year}
+  {1974}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ando}(1974{\natexlab{b}})}]{ando74_3}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ando}},\ }\href {https://doi.org/10.1143/JPSJ.37.622} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume}
+  {37}},\ \bibinfo {pages} {622} (\bibinfo {year}
+  {1974}{\natexlab{b}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ando}\ and\ \citenamefont
+  {Uemura}(1974{\natexlab{b}})}]{ando74_4}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ando}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Uemura}},\
+  }\href {https://doi.org/10.1143/JPSJ.37.1233} {\bibfield  {journal} {\bibinfo
+   {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume} {37}},\ \bibinfo
+  {pages} {1233} (\bibinfo {year} {1974}{\natexlab{b}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ando}\ \emph {et~al.}(1982)\citenamefont {Ando},
+  \citenamefont {Fowler},\ and\ \citenamefont {Stern}}]{ando82}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ando}}, \bibinfo {author} {\bibfnamefont {A.~B.}\ \bibnamefont {Fowler}},\
+  and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Stern}},\ }\href
+  {https://doi.org/10.1103/RevModPhys.54.437} {\bibfield  {journal} {\bibinfo
+  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {54}},\ \bibinfo
+  {pages} {437} (\bibinfo {year} {1982})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Endo}\ \emph {et~al.}(2009)\citenamefont {Endo},
+  \citenamefont {Hatano}, \citenamefont {Nakamura},\ and\ \citenamefont
+  {Shirasaki}}]{endo09}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Endo}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Hatano}},
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Nakamura}},\ and\
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Shirasaki}},\ }\href
+  {https://doi.org/10.1088/0953-8984/21/34/345803} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Phys.: Condens. Matter}\ }\textbf {\bibinfo {volume}
+  {21}},\ \bibinfo {pages} {345803} (\bibinfo {year} {2009})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Allerman}\ \emph {et~al.}(1995)\citenamefont
+  {Allerman}, \citenamefont {Xu}, \citenamefont {Hauser},\ and\ \citenamefont
+  {Jagadish}}]{allerman95}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Allerman}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Xu}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Hauser}},\ and\ \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {Jagadish}},\ }\href
+  {https://doi.org/10.1063/1.358844} {\bibfield  {journal} {\bibinfo  {journal}
+  {J. Appl. Phys.}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo {pages} {2052}
+  (\bibinfo {year} {1995})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tieke}\ \emph {et~al.}(1997)\citenamefont {Tieke},
+  \citenamefont {Fletcher}, \citenamefont {Zeitler}, \citenamefont {Geim},
+  \citenamefont {Henini},\ and\ \citenamefont {Maan}}]{tieke97}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Tieke}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Fletcher}},
+  \bibinfo {author} {\bibfnamefont {U.}~\bibnamefont {Zeitler}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Geim}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Henini}},\ and\ \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Maan}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.78.4621} {\bibfield  {journal} {\bibinfo
+   {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {78}},\ \bibinfo
+  {pages} {4621} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pan}\ \emph {et~al.}(2005)\citenamefont {Pan},
+  \citenamefont {Xia}, \citenamefont {Stormer}, \citenamefont {Tsui},
+  \citenamefont {Vicente}, \citenamefont {Adams}, \citenamefont {Sullivan},
+  \citenamefont {Pfeiffer}, \citenamefont {Baldwin},\ and\ \citenamefont
+  {West}}]{pan05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Pan}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Xia}}, \bibinfo
+  {author} {\bibfnamefont {H.}~\bibnamefont {Stormer}}, \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Tsui}}, \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Vicente}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Adams}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Sullivan}}, \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Pfeiffer}}, \bibinfo {author} {\bibfnamefont
+  {K.}~\bibnamefont {Baldwin}},\ and\ \bibinfo {author} {\bibfnamefont
+  {K.}~\bibnamefont {West}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.95.066808} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {95}},\
+  \bibinfo {pages} {066808} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Landau}(1930)}]{landau30}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Landau}},\ }\href {https://doi.org/10.1007/BF01397213} {\bibfield  {journal}
+  {\bibinfo  {journal} {Z. Physik}\ }\textbf {\bibinfo {volume} {64}},\
+  \bibinfo {pages} {629} (\bibinfo {year} {1930})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mahan}(2000)}]{mahan00}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~D.}\ \bibnamefont
+  {Mahan}},\ }\href@noop {} {\emph {\bibinfo {title} {Many-particle physics}}}\
+  (\bibinfo  {publisher} {Springer Science \& Business Media, New York},\
+  \bibinfo {year} {2000})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bruus}\ and\ \citenamefont
+  {Flensberg}(2004)}]{bruus04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Bruus}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Flensberg}},\ }\href@noop {} {\emph {\bibinfo {title} {Many-body quantum
+  theory in condensed matter physics: an introduction}}}\ (\bibinfo
+  {publisher} {Oxford University Press, New York},\ \bibinfo {year}
+  {2004})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Husimi}(1953)}]{husimi53}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Husimi}},\ }\href {https://doi.org/10.1143/ptp/9.4.381} {\bibfield
+  {journal} {\bibinfo  {journal} {Prog. Theor. Phys.}\ }\textbf {\bibinfo
+  {volume} {9}},\ \bibinfo {pages} {381} (\bibinfo {year} {1953})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Dittrich}\ \emph {et~al.}(1998)\citenamefont
+  {Dittrich}, \citenamefont {Hänggi}, \citenamefont {Ingold}, \citenamefont
+  {Kramer}, \citenamefont {Schön},\ and\ \citenamefont {Zwerger}}]{ditt98}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Dittrich}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Hänggi}},
+  \bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont {Ingold}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Kramer}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {Schön}},\ and\ \bibinfo {author}
+  {\bibfnamefont {W.}~\bibnamefont {Zwerger}},\ }\href@noop {} {\emph {\bibinfo
+  {title} {Quantum Transport and Dissipation}}}\ (\bibinfo  {publisher}
+  {Wiley-VCH, Weinheim},\ \bibinfo {year} {1998})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Floquet}(1883)}]{floquet83}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Floquet}},\ }\href {https://doi.org/10.24033/asens.220} {\bibfield
+  {journal} {\bibinfo  {journal} {Scientific annals of the École Normale
+  Supérieure}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {47}
+  (\bibinfo {year} {1883})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Holthaus}(2015)}]{holthaus15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Holthaus}},\ }\href {https://doi.org/10.1088/0953-4075/49/1/013001}
+  {\bibfield  {journal} {\bibinfo  {journal} {J. Phys. B: At., Mol. Opt.
+  Phys.}\ }\textbf {\bibinfo {volume} {49}},\ \bibinfo {pages} {013001}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Popov}\ and\ \citenamefont
+  {Perelomov}(1970)}]{popov70}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Popov}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Perelomov}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Exp. Theor. Phys.}\ }\textbf {\bibinfo {volume} {30}},\ \bibinfo {pages}
+  {910} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sambe}(1975)}]{sambe75}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Sambe}},\ }\href {https://doi.org/10.1103/PhysRevA.7.2203} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+  {7}},\ \bibinfo {pages} {2203} (\bibinfo {year} {1975})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Peskin}\ \emph {et~al.}(1994)\citenamefont {Peskin},
+  \citenamefont {Kosloff},\ and\ \citenamefont {Moiseyev}}]{peskin93}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
+  {Peskin}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Kosloff}},\
+  and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Moiseyev}},\ }\href
+  {https://doi.org/10.1063/1.466739} {\bibfield  {journal} {\bibinfo  {journal}
+  {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {100}},\ \bibinfo {pages}
+  {8849} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Althorpe}\ \emph {et~al.}(1997)\citenamefont
+  {Althorpe}, \citenamefont {Kouri}, \citenamefont {Hoffman},\ and\
+  \citenamefont {Moiseyev}}]{althorpe97}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~C.}\ \bibnamefont
+  {Althorpe}}, \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont {Kouri}},
+  \bibinfo {author} {\bibfnamefont {D.~K.}\ \bibnamefont {Hoffman}},\ and\
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Moiseyev}},\ }\href
+  {https://doi.org/10.1016/S0301-0104(97)00062-1} {\bibfield  {journal}
+  {\bibinfo  {journal} {Chem. Phys.}\ }\textbf {\bibinfo {volume} {217}},\
+  \bibinfo {pages} {289} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Winkler}(2003)}]{winkler03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Winkler}},\ }\href@noop {} {\emph {\bibinfo {title} {Spin-orbit Coupling
+  Effects in Two-Dimensional Electron and Hole Systems}}}\ (\bibinfo
+  {publisher} {Springer, Berlin},\ \bibinfo {year} {2003})\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Wackerl}(2020)}]{wackerlthesis20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Wackerl}},\ }\emph {\bibinfo {title} {Transport in Periodically Driven
+  Systems}},\ \href@noop {} {Ph.D. thesis},\ \bibinfo  {school} {University of
+  Regensburg} (\bibinfo {year} {2020})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Tsuji}\ \emph {et~al.}(2008)\citenamefont {Tsuji},
+  \citenamefont {Oka},\ and\ \citenamefont {Aoki}}]{tsuji08}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Tsuji}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Oka}},\ and\
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Aoki}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.78.235124} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {78}},\ \bibinfo
+  {pages} {235124} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Griffiths}\ and\ \citenamefont
+  {Schroeter}(2018)}]{griffiths18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+  {Griffiths}}\ and\ \bibinfo {author} {\bibfnamefont {D.~F.}\ \bibnamefont
+  {Schroeter}},\ }\href@noop {} {\emph {\bibinfo {title} {Introduction to
+  Quantum Mechanics}}}\ (\bibinfo  {publisher} {Cambridge University Press},\
+  \bibinfo {year} {2018})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Shankar}(1994)}]{shankar94}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Shankar}},\ }\href@noop {} {\emph {\bibinfo {title} {Principles of Quantum
+  Mechanics}}}\ (\bibinfo  {publisher} {Springer, New York},\ \bibinfo {year}
+  {1994})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Celeghini}\ \emph {et~al.}(2021)\citenamefont
+  {Celeghini}, \citenamefont {Gadella},\ and\ \citenamefont {del
+  Olmo}}]{celeghini21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Celeghini}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Gadella}},\
+  and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {del Olmo}},\
+  }\href {https://doi.org/10.3390/sym13050853} {\bibfield  {journal} {\bibinfo
+  {journal} {Symmetry}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages}
+  {853} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Akkermans}\ and\ \citenamefont
+  {Montambaux}(2010)}]{akkermans10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Akkermans}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Montambaux}},\ }\href@noop {} {\emph {\bibinfo {title} {Mesoscopic Physics
+  of Electrons and Photons}}}\ (\bibinfo  {publisher} {Cambridge University
+  Press},\ \bibinfo {year} {2010})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Arfken}(1985)}]{arfken85}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Arfken}},\ }\href@noop {} {\emph {\bibinfo {title} {Mathematical Methods for
+  Physicists}}}\ (\bibinfo  {publisher} {Academic Press, Inc. , San Diego},\
+  \bibinfo {year} {1985})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bracewell}(1978)}]{bracewell78}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Bracewell}},\ }\href@noop {} {\emph {\bibinfo {title} {The Fourier Transform
+  and Its Applications}}}\ (\bibinfo  {publisher} {McGraw-Hill, New York},\
+  \bibinfo {year} {1978})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cuyt}\ \emph {et~al.}(2008)\citenamefont {Cuyt},
+  \citenamefont {Petersen}, \citenamefont {Verdonk}, \citenamefont
+  {Waadeland},\ and\ \citenamefont {Jones}}]{cuyt08}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Cuyt}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Petersen}},
+  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Verdonk}}, \bibinfo
+  {author} {\bibfnamefont {H.}~\bibnamefont {Waadeland}},\ and\ \bibinfo
+  {author} {\bibfnamefont {W.}~\bibnamefont {Jones}},\ }\href@noop {} {\emph
+  {\bibinfo {title} {Handbook of Continued Fractions for Special Functions}}}\
+  (\bibinfo  {publisher} {Springer, Dordrecht},\ \bibinfo {year}
+  {2008})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Abramowitz}\ and\ \citenamefont
+  {Stegun}(1964)}]{abramowitz64}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Abramowitz}}\ and\ \bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont
+  {Stegun}},\ }\href@noop {} {\emph {\bibinfo {title} {Handbook of Mathematical
+  Functions with Formulas, Graphs, and Mathematical Tables}}}\ (\bibinfo
+  {publisher} {Dover, New York},\ \bibinfo {year} {1964})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {V.Vedenyapin}\ \emph {et~al.}(2011)\citenamefont
+  {V.Vedenyapin}, \citenamefont {Sinitsyn},\ and\ \citenamefont
+  {Dulov}}]{vedenyapin11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibnamefont {V.Vedenyapin}},
+  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Sinitsyn}},\ and\
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Dulov}},\ }\href@noop {}
+  {\emph {\bibinfo {title} {Kinetic Boltzmann, Vlasov and Related Equations}}}\
+  (\bibinfo  {publisher} {Elsevier, Amsterdam},\ \bibinfo {year}
+  {2011})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Szegö}(1959)}]{szego59}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Szegö}},\ }\href@noop {} {\emph {\bibinfo {title} {Orthogonal
+  Polynomials}}}\ (\bibinfo  {publisher} {American Mathematical Society, New
+  York},\ \bibinfo {year} {1959})\BibitemShut {NoStop}%
+\end{thebibliography}%
 %===============================================================================

### 2021-08-22 paper/Submission/dressed_quantum_hall/dressed_quantum_hall.tex
Re-structure

--- 2021-08-22 paper/dressed_quantum_hall/dressed_quantum_hall.tex
@@
 \author{Kosala Herath,}
-\email[]{kosala.herath@monash.edu}
+\email{kosala.herath@monash.edu}
 \author{Malin Premaratne}
-\email[]{malin.premaratne@monash.edu}
+\email{malin.premaratne@monash.edu}
 \affiliation{Advanced Computing and Simulation Laboratory (A$\chi$L), Department of Electrical and Computer Systems Engineering, Monash University, Clayton, Victoria 3800, Australia.}
@@
 %===============================================================================
-\section{\label{sec_introduction} Introduction}
+\section{\label{sec:introduction} Introduction}
 
@@
 Sec.
-\ref{sec_schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration.
+\ref{sec:schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration.
 Sec.
-\ref{sec_floquet_theory} provides the Floquet theory interpretation of these wave functions.
+\ref{sec:floquet_theory} provides the Floquet theory interpretation of these wave functions.
 We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec.
-\ref{sec_inverse_scattering_time}, and use it in Sec.
-\ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
-The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}.
-In Sec. \ref{sec_conclusions}, we summarize our analysis and present our conclusions.
+\ref{sec:inverse_scattering_time}, and use it in Sec.
+\ref{sec:floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
+The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec:manipulate_conductivity}.
+In Sec. \ref{sec:conclusions}, we summarize our analysis and present our conclusions.
 %===============================================================================
@@
 %===============================================================================
-\section{\label{sec_schrodinger_problem} Schrodinger Problem for a Dressed Quantum Hall System}
+\section{\label{sec:schrodinger_problem} Schrodinger Problem for a Dressed Quantum Hall System}
 
@@
 \begin{figure}[b]
-\includegraphics[scale=0.9]{fig_1}
+\includegraphics[scale=0.9]{fig_1_system_diagram}
 \caption{\label{fig:1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
@@
 %===============================================================================
-\section{\label{sec_floquet_theory} Floquet Theory Perspective}
+\section{\label{sec:floquet_theory} Floquet Theory Perspective}
 
@@
 %===============================================================================
-\section{\label{sec_inverse_scattering_time}  Inverse Scattering Time Analysis}
+\section{\label{sec:inverse_scattering_time}  Inverse Scattering Time Analysis}
 
@@
 \begin{figure}[t]
-\includegraphics[scale=0.55]{fig_2}
+\includegraphics[scale=0.55]{fig_2_normalized_broadening_with_momentum}
 \caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.54]{fig_3}
+\includegraphics[scale=0.54]{fig_3_normalized_broadening_with_intensity}
 \caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
@@
 %===============================================================================
-\section{\label{sec_floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}
+\section{\label{sec:floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}
 
@@
 %===============================================================================
-\section{\label{sec_manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}
+\section{\label{sec:manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}
 
@@
 \begin{figure}[t]
-\includegraphics[scale=0.54]{fig_4}
+\includegraphics[scale=0.54]{fig_4_conductivity_with_fermi_level}
 \caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.54]{fig_5}
+\includegraphics[scale=0.54]{fig_5_conductivity_with_fermi_level_zoomed}
 \caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
@@
 %===============================================================================
-\section{\label{sec_conclusions} Conclusions}
+\section{\label{sec:conclusions} Conclusions}
 
@@
 %===============================================================================
-\begin{appendix}
+\appendix
 
@@
 \begin{figure}[b]
-  \includegraphics[scale=1.0]{fig_6.pdf}
+  \includegraphics[scale=1.0]{fig_6_scattering_scenario.pdf}
   \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
@@
 %===============================================================================
-\end{appendix}
 

### 2021-08-22 paper/v3.0/sections/2_schrodinger_problem.tex
Re-structure

--- 2021-08-22 paper/v3-release/aps_article.tex
@@
-% ****** Start of file dressed_quantum_hall.tex ****** %
+% Section 02 - Schrodinger problem for dressed quantum Hall system
 
-\documentclass[
- reprint,
- amsmath,amssymb,
- aps,
- prb,
-]{revtex4-2}
+Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space.
+In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{T}$, which is pointed towards the $z$-axis.
+In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface.
+We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field.
+Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field as given in Fig.~\ref{fig:1}.
+\begin{figure}[b]
+\includegraphics[scale=0.9]{figures/fig_1.pdf}
+\caption{\label{fig:1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
+The dressing field is linearly polarized with a $y$-polarized electric field $\vb{E}$.}
+\end{figure}
+Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field, respectively.
 
-%===============================================================================
-% Import packages
-%===============================================================================
-% Bold math
-\usepackage{bm}
-% AMS packages
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathtools}
-% Physics package
-\usepackage{physics}
-% SI units package
-\usepackage{siunitx}
-% Hypertext package
-\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
-% Language and font encodings
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage[T1]{fontenc}
-%===============================================================================
-% Bibliography style
-\bibliographystyle{apsrev4-2}
-
-\begin{document}
-
-\preprint{APS/123-QED}
-
-% Title of the manuscript
-\title{A generalized model for the charge transport properties of
-\\dressed quantum Hall systems}
-
-% Authors of the manuscript
-\author{Kosala Herath,}
-\email[]{kosala.herath@monash.edu}
-\author{Malin Premaratne}
-\email[]{malin.premaratne@monash.edu}
-\affiliation{Advanced Computing and Simulation Laboratory (A$\chi$L), Department of Electrical and Computer Systems Engineering, Monash University, Clayton, Victoria 3800, Australia.}
-
-% Add date
-\date{\today}
-
-% Abstract
-\begin{abstract}
-\input{sections/abstract.tex}
-\end{abstract}
-
-% Make title of the manuscript
-\maketitle
-
-% Section 01 : Introduction
-\section{\label{sec_introduction} Introduction}
-\input{sections/1_introduction.tex}
-
-% Section 02 : Schrodinger problem for a dressed quantum Hall system
-\section{\label{sec_schrodinger_problem} Schrodinger problem for a dressed quantum Hall system}
-\input{sections/2_schrodinger_problem.tex}
-
-% Section 03 : Floquet theory perspectiv
-\section{\label{sec_floquet_theory} Floquet theory perspective}
-\input{sections/3_floquet_theory.tex}
-
-% Section 04 :
-\section{\label{sec_inverse_scattering_time}  Inverse Scattering Time Analysis}
-\input{sections/4_inverse_scattering_time.tex}
-
-% Section 05 :
-\section{\label{sec_floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}
-\input{sections/5_floquet_drude_conductivity.tex}
-
-% Section 06 :
-\section{\label{sec_manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}
-\input{sections/6_manipulate_conductivity.tex}
-
-% Section 07 :
-\section{\label{sec_conclusions} Conclusions}
-\input{sections/7_conclusions.tex}
-
-% Acknowledgments
-\begin{acknowledgments}
-\input{sections/acknowledgments.tex}
-\end{acknowledgments}
-
-% Add appendixes
-\appendix
-
-% Appendix A : Wave function solutions for a dressed quantum Hall system
-\section{\label{appendix_a} Wave function solutions for a dressed quantum Hall system}
-\input{sections/appendix_a.tex}
-
-% Appendix B :
-\section{\label{appendix_b} Floquet modes and quasienergies}
-\input{sections/appendix_b.tex}
-
-% Appendix C :
-\section{\label{appendix_c} Floquet-Fermi golden rule for a dressed quantum  Hall system}
-\input{sections/appendix_c.tex}
-
-% Appendix D :
-\section{\label{appendix_d} Current operators for a dressed quantum Hall system}
-\input{sections/appendix_d.tex}
-
-% Bibliography
-\bibliography{aps_article}
-
-\end{document}
-
-% ****** End of file dressed_quantum_hall.tex ****** %
+Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{T}$.
+Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E\cos(\omega t)]/\omega,0)^{T}$.
+These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}.
+Thus, we can represent our system with a time-dependent Hamiltonian
+\begin{equation} \label{eq:1}
+  \hat{H}_e(t) =
+  \frac{1}{2m_e}
+  \left\{ \hat{\vb{p}} - e\right[ \vb{A}_{s}+\vb{A}_{d}(t) \left] \right\}^2,
+\end{equation}
+where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{T}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{T}$.
+The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv*{\psi}{t} = \hat{H}_e(t)\psi$ were already derived in Refs.
+\cite{husimi53,ditt98,dini16}.
+Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
+\begin{equation} \label{eq:2}
+  \begin{aligned}
+    &\psi_{n,m}(x,y,t)  \\
+      & \quad = \frac{1}{\sqrt{L_x}}
+        \chi_n \bm{\left(} y - y_0 - \zeta(t) \bm{\right)}\\
+      & \qquad \times
+        \exp \bm{\left(}
+        \frac{i}{\hbar}\left\{- \epsilon_n t
+        + p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right.\\
+      & \left.\left. \qquad\qquad +
+        m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
+        \int_0^{t}L(\zeta,\dot{\zeta},t')\,dt' \right\}\bm{\right)},
+  \end{aligned}
+\end{equation}
+where $n \in \mathbb{Z}^+_0$ and $m \in \mathbb{Z}$.
+Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant.
+The center of the cyclotron orbit on the $y$-axis is given by $y_0 = \flatfrac{-p_x}{(eB)}$ with $p_x = \flatfrac{2\pi\hbar m}{L_x}$.
+Moreover, $\chi_n$ are well-known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
+\begin{equation} \label{eq:3}
+  \chi_n(y) =
+  \left( \frac{\kappa}{2^{n}n! \sqrt{\pi}}\right)^{1/2}
+  e^{-\kappa^2 y^2/2}
+  \mathcal{H}_n \qty(\kappa y),
+\end{equation}
+with eigenvalues $\epsilon_n = \hbar \omega_0 [n + (1/2)]$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
+We represent the path shift of the driven classical oscillator $\zeta(t)$ by
+\begin{equation} \label{eq:4}
+  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
+\end{equation}
+and we introduce $\dot{\zeta}(t) = \pdv*{\zeta(t)}{t}$ for the sake of notational ease. We can identify the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ as
+\begin{equation} \label{eq:5}
+  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
+\end{equation}
+For details of the full derivation, refer to Appendix \ref{appendix_a}.
+The exponential phase shifts in Eq.~(\ref{eq:2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system.
+Therefore, we can renormalize the magneto-transport characteristics of 2DEG by a nonoscillating magnetic field along with a dressing field.

### 2021-08-22 paper/v3.0/sections/4_inverse_scattering_time.tex
Re-structure

--- 2021-08-22 paper/v3-release/aps_article.tex
@@
-% ****** Start of file dressed_quantum_hall.tex ****** %
+% Section 04 - Inverse Scattering Time Analysis
 
-\documentclass[
- reprint,
- amsmath,amssymb,
- aps,
- prb,
-]{revtex4-2}
+The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
+However, this theory has not been applied for a dressed quantum Hall system in the previous studies.
+In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
+With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
+\begin{widetext}
+\begin{equation} \label{eq:15}
+  \begin{aligned}
+    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
+    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
+    & \times
+    \int_{-\infty}^{\infty}
+    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+    \left|
+    \int_{-\infty}^{\infty}
+    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
+    \chi_N \bm{\left(} \frac{\hbar}{eB}
+    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
+    dk_2 \right|^2 d k_1,
+  \end{aligned}
+\end{equation}
+\end{widetext}
+where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
+A more detailed derivation is given in Appendix \ref{appendix_c}.
+We modeled the effect caused by impurities in the considered system as a single perturbation potential.
+Since random impurities in a disordered metal offer a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
+Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
+Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
 
-%===============================================================================
-% Import packages
-%===============================================================================
-% Bold math
-\usepackage{bm}
-% AMS packages
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathtools}
-% Physics package
-\usepackage{physics}
-% SI units package
-\usepackage{siunitx}
-% Hypertext package
-\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
-% Language and font encodings
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage[T1]{fontenc}
-%===============================================================================
-% Bibliography style
-\bibliographystyle{apsrev4-2}
+Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
+Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
+Subsequently, we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
+Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
+\begin{equation} \label{eq:16}
+ \Gamma^{00}_{N}(\varepsilon,k_x) =
+ \hbar \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{00}_N.
+\end{equation}
+We can evaluate this as
+\begin{widetext}
+  \begin{equation} \label{eq:17}
+   \begin{aligned}
+     &\Gamma^{00}_{N} (\varepsilon,k_x) =
+     \frac{ \pi \hbar^2 \varrho^2}{e^2B^2}
+     \delta(\varepsilon - \varepsilon_{N})
+     \int_{-\infty}^{\infty}
+     J_0^2 \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+     \left|
+     \int_{-\infty}^{\infty}
+     \chi_N \left( \frac{\hbar}{eB}k_2 \right)
+     \chi_N \bm{\left(} \frac{\hbar}{eB}
+     \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
+     dk_2 \right|^2 d k_1.
+   \end{aligned}
+  \end{equation}
+In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
+\begin{equation} \label{eq:18}
+ \delta(\varepsilon - \varepsilon_{N}) \approx
+ \frac{1}{\pi \Gamma^{00}_N (\varepsilon,k_x)}.
+\end{equation}
+Subsequently, we write the central element of inverse scattering time matrix in the more compact form
+\begin{equation} \label{eq:19}
+  \begin{aligned}
+    &\Gamma^{00}_{N}(\varepsilon,k_x) =
+     \varrho
+      \left[
+      \int_{-\infty}^{\infty}
+      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
+      \left|
+      \int_{-\infty}^{\infty}
+      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
+      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
+      dk_2 \right|^2
+      dk_1
+      \right]^{-\frac{1}{2}},
+  \end{aligned}
+\end{equation}
+where $ \lambda_1 = \flatfrac{\hbar b}{(eB)}$ and  $\lambda_2 = \flatfrac{\hbar \kappa}{(eB)}$.
+To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
+\begin{equation} \label{eq:20}
+    \Lambda_N(k_x) =
+    \frac{\Gamma^{00}_N (\varepsilon,k_x)}
+    {\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
+\end{equation}
+which we can evaluate with
+\begin{equation} \label{eq:21}
+    \Lambda_N (k_x) =
+    \left[
+    \frac
+    {
+      \int_{-\infty}^{\infty}
+      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
+      \left|
+      \int_{-\infty}^{\infty}
+      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
+      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
+      dk_2 \right|^2
+      dk_1
+    }
+    {
+      \int_{-\infty}^{\infty}
+      \left|
+      \int_{-\infty}^{\infty}
+      \widetilde{\chi}_0 \left(\lambda_2 k_2 \right)
+      \widetilde{\chi}_0 \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
+      dk_2 \right|^2
+      dk_1
+    }
+    \right]^{1/2}.
+\end{equation}
+\end{widetext}
 
-\begin{document}
+\begin{figure}[t]
+\includegraphics[scale=0.55]{figures/fig_2}
+\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\end{figure}
 
-\preprint{APS/123-QED}
+\begin{figure}[t]
+\includegraphics[scale=0.54]{figures/fig_3}
+\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
+In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\end{figure}
 
-% Title of the manuscript
-\title{A generalized model for the charge transport properties of
-\\dressed quantum Hall systems}
-
-% Authors of the manuscript
-\author{Kosala Herath,}
-\email[]{kosala.herath@monash.edu}
-\author{Malin Premaratne}
-\email[]{malin.premaratne@monash.edu}
-\affiliation{Advanced Computing and Simulation Laboratory (A$\chi$L), Department of Electrical and Computer Systems Engineering, Monash University, Clayton, Victoria 3800, Australia.}
-
-% Add date
-\date{\today}
-
-% Abstract
-\begin{abstract}
-\input{sections/abstract.tex}
-\end{abstract}
-
-% Make title of the manuscript
-\maketitle
-
-% Section 01 : Introduction
-\section{\label{sec_introduction} Introduction}
-\input{sections/1_introduction.tex}
-
-% Section 02 : Schrodinger problem for a dressed quantum Hall system
-\section{\label{sec_schrodinger_problem} Schrodinger problem for a dressed quantum Hall system}
-\input{sections/2_schrodinger_problem.tex}
-
-% Section 03 : Floquet theory perspectiv
-\section{\label{sec_floquet_theory} Floquet theory perspective}
-\input{sections/3_floquet_theory.tex}
-
-% Section 04 :
-\section{\label{sec_inverse_scattering_time}  Inverse Scattering Time Analysis}
-\input{sections/4_inverse_scattering_time.tex}
-
-% Section 05 :
-\section{\label{sec_floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}
-\input{sections/5_floquet_drude_conductivity.tex}
-
-% Section 06 :
-\section{\label{sec_manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}
-\input{sections/6_manipulate_conductivity.tex}
-
-% Section 07 :
-\section{\label{sec_conclusions} Conclusions}
-\input{sections/7_conclusions.tex}
-
-% Acknowledgments
-\begin{acknowledgments}
-\input{sections/acknowledgments.tex}
-\end{acknowledgments}
-
-% Add appendixes
-\appendix
-
-% Appendix A : Wave function solutions for a dressed quantum Hall system
-\section{\label{appendix_a} Wave function solutions for a dressed quantum Hall system}
-\input{sections/appendix_a.tex}
-
-% Appendix B :
-\section{\label{appendix_b} Floquet modes and quasienergies}
-\input{sections/appendix_b.tex}
-
-% Appendix C :
-\section{\label{appendix_c} Floquet-Fermi golden rule for a dressed quantum  Hall system}
-\input{sections/appendix_c.tex}
-
-% Appendix D :
-\section{\label{appendix_d} Current operators for a dressed quantum Hall system}
-\input{sections/appendix_d.tex}
-
-% Bibliography
-\bibliography{aps_article}
-
-\end{document}
-
-% ****** End of file dressed_quantum_hall.tex ****** %
+Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig_3} and Fig.~\ref{fig_4}.
+To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
+In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
+In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
+Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
+Here, we observe that the normalized energy broadening value for each Landau level is independent of the $x$-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
+When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
+To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.

### 2021-08-22 paper/v3.0/sections/5_floquet_drude_conductivity.tex
Re-structure

--- 2021-08-22 paper/v3-release/aps_article.tex
@@
-% ****** Start of file dressed_quantum_hall.tex ****** %
-
-\documentclass[
- reprint,
- amsmath,amssymb,
- aps,
- prb,
-]{revtex4-2}
-
-%===============================================================================
-% Import packages
-%===============================================================================
-% Bold math
-\usepackage{bm}
-% AMS packages
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathtools}
-% Physics package
-\usepackage{physics}
-% SI units package
-\usepackage{siunitx}
-% Hypertext package
-\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
-% Language and font encodings
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage[T1]{fontenc}
-%===============================================================================
-% Bibliography style
-\bibliographystyle{apsrev4-2}
-
-\begin{document}
-
-\preprint{APS/123-QED}
-
-%===============================================================================
-% Title of the manuscript
-%===============================================================================
-\title{A generalized model for the charge transport properties of
-\\dressed quantum Hall systems}
-%===============================================================================
-
-%===============================================================================
-% Authors of the manuscript
-%===============================================================================
-\author{Kosala Herath,}
-\email[]{kosala.herath@monash.edu}
-\author{Malin Premaratne}
-\email[]{malin.premaratne@monash.edu}
-\affiliation{Advanced Computing and Simulation Laboratory (A$\chi$L), Department of Electrical and Computer Systems Engineering, Monash University, Clayton, Victoria 3800, Australia.}
-%===============================================================================
-
-%===============================================================================
-% Add date
-%===============================================================================
-\date{\today}
-%===============================================================================
-
-%===============================================================================
-% Abstract
-%===============================================================================
-\begin{abstract}
-We present a generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high-intensity electromagnetic field.
-The new formulation, which applies to two-dimensional(2D) dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
-We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields.
-To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure.
-Moreover, the Floquet-Fermi golden rule is adopted to explore the impurity scattering effects on charge transport in disordered quantum Hall systems.
-We derive fully analytical expressions to describe longitudinal components in the conductivity tensor in dressed quantum Hall systems.
-Subsequently, we demonstrate that the conductivity characteristics of quantum Hall systems can be manipulated using strong external light.
-Our results align with well-established and experimentally
-verified theoretical descriptions for undressed systems while providing a more generalized analysis of the conductivity characteristics in quantum Hall systems.
-Thus, our model can be applied to accurately interpret the usage of strong external radiation as a tool in nanoscale quantum devices.
-\end{abstract}
-%===============================================================================
-
-%===============================================================================
-% Make title of the manuscript
-%===============================================================================
-\maketitle
-%===============================================================================
-
-%===============================================================================
-% Section 01 : Introduction
-%===============================================================================
-\section{\label{sec_introduction} Introduction}
-
-Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century.
-Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo15,pirandola18,hapuarachchi2018}, energy harvesting \cite{weeraddana15,yuan16,sun18},
-quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
-The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{chow13,jayasekara16,premaratne17}, and quantum cavity physics \cite{tsang10,liu17,devi20}.
-However, in recent years, one of the foremost aims of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
-
-Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
-Most recent studies on the subject have considered the driving field as a perturbation field \cite{pervishko15,morina15}.
-However, this assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
-Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity.
-At high intensities, the higher-order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
-In these instances, a more accurate treatment needs to be adopted.
-Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}.
-Here the applied high-intensity  electromagnetic field identify as the \textit{dressing field}.
-
-Theoretical analyses on the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
-Furthermore, in Ref.
-\cite{wackerl20} a general expression for conductivity in a dressed system has been derived in a fully closed analytical form.
-In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula.
-This opened the path for exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.
-
-Quantum Hall effect \cite{girvin90} observed in two-dimensional (2D) fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors.
-Transport properties of these systems have recently attracted both theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{allerman95,tieke97,pan05} interest.
-Endo \textit{et al.} \cite{endo09} presented the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system.
-These theoretical calculations  align better with experimental observations compared to previous studies.
-
-In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
-Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
-Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems.
-However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
-In their study, they used the conductivity models from Refs.
-\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
-
-In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
-A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system.
-This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
-In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
-Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref.
-\cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
-Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices.
-We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport.
-Moreover, this will inspire advanced  developments in nanoscale quantum devices.
-
-The paper is organized as follows.
-Sec.
-\ref{sec_schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration.
-Sec.
-\ref{sec_floquet_theory} provides the Floquet theory interpretation of these wave functions.
-We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec.
-\ref{sec_inverse_scattering_time}, and use it in Sec.
-\ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
-The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}.
-In Sec. \ref{sec_conclusions}, we summarize our analysis and present our conclusions.
-%===============================================================================
-
-%===============================================================================
-% Section 02 : Schrodinger problem for a dressed quantum Hall system
-%===============================================================================
-\section{\label{sec_schrodinger_problem} Schrodinger Problem for a Dressed Quantum Hall System}
-
-Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space.
-In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{T}$, which is pointed towards the $z$-axis.
-In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface.
-We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field.
-Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field as given in Fig.~\ref{fig:1}.
-\begin{figure}[b]
-\includegraphics[scale=0.9]{figures/fig_1.pdf}
-\caption{\label{fig:1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
-The dressing field is linearly polarized with a $y$-polarized electric field $\vb{E}$.}
-\end{figure}
-Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field, respectively.
-
-Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{T}$.
-Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E\cos(\omega t)]/\omega,0)^{T}$.
-These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}.
-Thus, we can represent our system with a time-dependent Hamiltonian
-\begin{equation} \label{eq:1}
-  \hat{H}_e(t) =
-  \frac{1}{2m_e}
-  \left\{ \hat{\vb{p}} - e\right[ \vb{A}_{s}+\vb{A}_{d}(t) \left] \right\}^2,
-\end{equation}
-where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{T}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{T}$.
-The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv*{\psi}{t} = \hat{H}_e(t)\psi$ were already derived in Refs.
-\cite{husimi53,ditt98,dini16}.
-Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
-\begin{equation} \label{eq:2}
-  \begin{aligned}
-    &\psi_{n,m}(x,y,t)  \\
-      & \quad = \frac{1}{\sqrt{L_x}}
-        \chi_n \bm{\left(} y - y_0 - \zeta(t) \bm{\right)}\\
-      & \qquad \times
-        \exp \bm{\left(}
-        \frac{i}{\hbar}\left\{- \epsilon_n t
-        + p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right.\\
-      & \left.\left. \qquad\qquad +
-        m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
-        \int_0^{t}L(\zeta,\dot{\zeta},t')\,dt' \right\}\bm{\right)},
-  \end{aligned}
-\end{equation}
-where $n \in \mathbb{Z}^+_0$ and $m \in \mathbb{Z}$.
-Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant.
-The center of the cyclotron orbit on the $y$-axis is given by $y_0 = \flatfrac{-p_x}{(eB)}$ with $p_x = \flatfrac{2\pi\hbar m}{L_x}$.
-Moreover, $\chi_n$ are well-known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
-\begin{equation} \label{eq:3}
-  \chi_n(y) =
-  \left( \frac{\kappa}{2^{n}n! \sqrt{\pi}}\right)^{1/2}
-  e^{-\kappa^2 y^2/2}
-  \mathcal{H}_n \qty(\kappa y),
-\end{equation}
-with eigenvalues $\epsilon_n = \hbar \omega_0 [n + (1/2)]$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
-We represent the path shift of the driven classical oscillator $\zeta(t)$ by
-\begin{equation} \label{eq:4}
-  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
-\end{equation}
-and we introduce $\dot{\zeta}(t) = \pdv*{\zeta(t)}{t}$ for the sake of notational ease. We can identify the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ as
-\begin{equation} \label{eq:5}
-  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
-\end{equation}
-For details of the full derivation, refer to Appendix \ref{appendix_a}.
-The exponential phase shifts in Eq.~(\ref{eq:2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system.
-Therefore, we can renormalize the magneto-transport characteristics of 2DEG by a nonoscillating magnetic field along with a dressing field.
-%===============================================================================
-
-%===============================================================================
-% Section 03 : Floquet theory perspective
-%===============================================================================
-\section{\label{sec_floquet_theory} Floquet Theory Perspective}
-
-Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
-For instance, the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space.
-Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
-The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
-In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field.
-Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
-
-First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq:2}).
-By factorizing the wave function into a linearly time-dependent part and a periodic time-dependent part, we present the quasienergies with
-\begin{equation} \label{eq:6}
-  \varepsilon_{n} =
-  \hbar \omega_0 \left(n + \flatfrac{1}{2}\right) - \Delta_{\varepsilon},
-\end{equation}
-which only depends on a single quantum number $n$. Furthermore, we can recognize the Floquet modes as
-\begin{equation} \label{eq:7}
-  \begin{aligned}
-    \phi_{n,m}(x,y,t) =&
-    \frac{1}{\sqrt{L_x}} \chi_{n}\bm{\left(}y - y_0 -\zeta(t)\bm{\right)} \\
-    & \times
-      \exp \bm{\left(}
-      \frac{i}{\hbar}\left\{
-      p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right. \\
-    & \left.\left. \qquad\qquad +
-      m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
-      \xi \right\}\bm{\right)},
-  \end{aligned}
-\end{equation}
-with
-\begin{equation} \label{eq:8}
-  \Delta_{\varepsilon} = \frac{e^2E^2}{4m_e(\omega_0^2 - \omega^2)},
-\end{equation}
-and
-\begin{equation} \label{eq:9}
-  \xi = \frac{e^2E^2 \left(3\omega^2 - \omega_0^2 \right)}
-  {8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
-\end{equation}
-For a detailed derivation, refer to Appendix \ref{appendix_b}.
-It is important to note that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
-At resonance $\omega = \omega_0$, the energy levels occupy a continuous spectrum and the quasienergy formalism is no longer valid \cite{popov70}.
-Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.
-
-Performing the Fourier transform over the confined 2D space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
-\begin{equation} \label{eq:10}
-  \begin{aligned}
-    \phi_{n,m}\big(k_x,k_y,t\big)  =&
-    \sqrt{L_x}
-    \widetilde{\chi}_{n} \bm{\left(}k_y - b\cos(\omega t)\bm{\right) }\\
-    & \times
-    \exp \bm{\left(} i\xi -ik_y  \left[d\sin(\omega t) + y_0 \right] \bm{\right)},
-  \end{aligned}
-\end{equation}
-where
-\begin{equation} \label{eq:11}
-  \widetilde{\chi}_{n}(k) =
-  i^n \left(\frac{1}{ 2^{n} n! \sqrt{\pi} \kappa}\right)^{1/2}
-  e^{-\flatfrac{k^2}{(2 \kappa^2)}}
-  \mathcal{H}_{n} \left(\flatfrac{k}{\kappa}\right).
-\end{equation}
-Here we have introduced new parameters
-\begin{equation} \label{eq:12}
-  b =
-  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
-\end{equation}
-and
-\begin{equation} \label{eq:13}
-  d =
- \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
-\end{equation}
-Using Floquet theory, we can re-write the wave functions derived in Eq.~(\ref{eq:2}) as the \textit{Floquet states} in momentum space
-\begin{equation} \label{eq:14}
-  \psi_{n,m}(k_x,k_y,t) =
-  \exp(-\flatfrac{i\varepsilon_{n}t}{\hbar}) \phi_{n,m} (k_x,k_y,t).
-\end{equation}
-%===============================================================================
-
-%===============================================================================
-% Section 04 : Inverse scattering time analysis
-%===============================================================================
-\section{\label{sec_inverse_scattering_time}  Inverse Scattering Time Analysis}
-
-The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
-However, this theory has not been applied for a dressed quantum Hall system in the previous studies.
-In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
-With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
-\begin{widetext}
-\begin{equation} \label{eq:15}
-  \begin{aligned}
-    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
-    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
-    & \times
-    \int_{-\infty}^{\infty}
-    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
-    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
-    \left|
-    \int_{-\infty}^{\infty}
-    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
-    \chi_N \bm{\left(} \frac{\hbar}{eB}
-    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
-    dk_2 \right|^2 d k_1,
-  \end{aligned}
-\end{equation}
-\end{widetext}
-where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
-A more detailed derivation is given in Appendix \ref{appendix_c}.
-We modeled the effect caused by impurities in the considered system as a single perturbation potential.
-Since random impurities in a disordered metal offer a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
-Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
-Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
-
-Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
-Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
-Subsequently, we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
-Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
-\begin{equation} \label{eq:16}
- \Gamma^{00}_{N}(\varepsilon,k_x) =
- \hbar \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{00}_N.
-\end{equation}
-We can evaluate this as
-\begin{widetext}
-  \begin{equation} \label{eq:17}
-   \begin{aligned}
-     &\Gamma^{00}_{N} (\varepsilon,k_x) =
-     \frac{ \pi \hbar^2 \varrho^2}{e^2B^2}
-     \delta(\varepsilon - \varepsilon_{N})
-     \int_{-\infty}^{\infty}
-     J_0^2 \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
-     \left|
-     \int_{-\infty}^{\infty}
-     \chi_N \left( \frac{\hbar}{eB}k_2 \right)
-     \chi_N \bm{\left(} \frac{\hbar}{eB}
-     \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
-     dk_2 \right|^2 d k_1.
-   \end{aligned}
-  \end{equation}
-In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
-\begin{equation} \label{eq:18}
- \delta(\varepsilon - \varepsilon_{N}) \approx
- \frac{1}{\pi \Gamma^{00}_N (\varepsilon,k_x)}.
-\end{equation}
-Subsequently, we write the central element of inverse scattering time matrix in the more compact form
-\begin{equation} \label{eq:19}
-  \begin{aligned}
-    &\Gamma^{00}_{N}(\varepsilon,k_x) =
-     \varrho
-      \left[
-      \int_{-\infty}^{\infty}
-      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
-      \left|
-      \int_{-\infty}^{\infty}
-      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
-      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
-      dk_2 \right|^2
-      dk_1
-      \right]^{-\frac{1}{2}},
-  \end{aligned}
-\end{equation}
-where $ \lambda_1 = \flatfrac{\hbar b}{(eB)}$ and  $\lambda_2 = \flatfrac{\hbar \kappa}{(eB)}$.
-To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
-\begin{equation} \label{eq:20}
-    \Lambda_N(k_x) =
-    \frac{\Gamma^{00}_N (\varepsilon,k_x)}
-    {\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
-\end{equation}
-which we can evaluate with
-\begin{equation} \label{eq:21}
-    \Lambda_N (k_x) =
-    \left[
-    \frac
-    {
-      \int_{-\infty}^{\infty}
-      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
-      \left|
-      \int_{-\infty}^{\infty}
-      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
-      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
-      dk_2 \right|^2
-      dk_1
-    }
-    {
-      \int_{-\infty}^{\infty}
-      \left|
-      \int_{-\infty}^{\infty}
-      \widetilde{\chi}_0 \left(\lambda_2 k_2 \right)
-      \widetilde{\chi}_0 \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
-      dk_2 \right|^2
-      dk_1
-    }
-    \right]^{1/2}.
-\end{equation}
-\end{widetext}
-
-\begin{figure}[t]
-\includegraphics[scale=0.55]{figures/fig_2}
-\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_3}
-\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
-In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\end{figure}
-
-Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig_3} and Fig.~\ref{fig_4}.
-To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
-In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
-In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
-Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
-Here, we observe that the normalized energy broadening value for each Landau level is independent of the $x$-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
-When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
-To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.
-%===============================================================================
-
-%===============================================================================
-% Section 05 : Floquet-Drude Conductivity in a Dressed Quantum Hall System
-%===============================================================================
-\section{\label{sec_floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}
+% Section 05 - Floquet-Drude Conductivity in Quantum Hall Systems
 
@@
 \end{equation}
-%===============================================================================
-
-%===============================================================================
-% Section 06 : Manipulate Conductivity in Quantum Hall Systems
-%===============================================================================
-\section{\label{sec_manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}
-
-To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
-We can identify the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
-\begin{equation}\label{eq:37}
-  \widetilde{\sigma}^{xx}(X_F,I) =
-  \flatfrac{\sigma^{xx}}{\sigma_{0}},
-\end{equation}
-with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and we can express this as
-\begin{equation} \label{eq:38}
-  \begin{aligned}
-    \widetilde{\sigma}^{xx}(X_F,I) &=
-    \sum_{n}
-    \frac{(n+1)}{\varsigma^2 \Lambda_n \Lambda_{n+1}} \\
-    &\quad\times
-    \left[
-      \frac{1}
-      {
-        1 + \left(\frac{X_F - n -1}{\varsigma \Lambda_n}\right)^2
-      }
-    \right]
-    \left[
-      \frac{1}
-      {
-        1 + \left(\frac{X_F - n}{\varsigma \Lambda_{n+1}}\right)^2
-      }
-    \right],
-  \end{aligned}
-\end{equation}
-where $\varsigma = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.
-
-As illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6}, we can manipulate the normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
-For a given dressing field intensity, the longitudinal conductivity varies with  the Fermi level of the system showing sharp peaks at each Landau energy level.
-In quantum Hall systems, electrons are restricted to bear only the Landau energies.
-Thus, the conductivity reduces significantly when the Fermi level is not aligned with any of the Landau levels.
-In contrast, near each Landau level, the conductivity achieves excessive values compared to other areas.
-Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.
-
-On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.
-When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:6}.
-However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
-This demonstrates our ability to tune the width of the conductivity regions in these quantum Hall systems with the help of a dressing field.
-
-These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
-As the authors remarked in that publication, since the Fermi level of the system can be changed with the applied gate voltage of the material, this can be utilized as a 2D switch for nanoscale optoelectronics applications.
-Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
-However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
-This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
-The semi-elliptical conductivity regions are  illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed data for Landau levels \cite{endo09}.
-In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the results depicted in Ref.
-\cite{endo09}.
-The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimentally observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
-However, they have not considered the tunability that can be achieved with a dressing field.
-In this analysis, we account for both the magnetic and dressing field effects that can affect the transport properties of 2DEG, leading to a more generalized theory.
-Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_4}
-\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:5}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_5}
-\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:6}
-\end{figure}
-%===============================================================================
-
-%===============================================================================
-% Section 07 : Conclusions
-%===============================================================================
-\section{\label{sec_conclusions} Conclusions}
-
-In this paper, we introduced a generalized mathematical model for predicting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high-intensity light.
-Under the uniform magnetic field, the charged particles can only settle in discrete energy values, which leads to the Landau quantization.
-We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method.
-We assumed the impurities in the material as a Gaussian random scattering potential.
-Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
-
-Our derived analytical expressions disclosed that we are able to control the transport characteristics of the dressed quantum Hall system by the applied dressing field’s intensity.
-Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
-We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
-Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels.
-Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.
-However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.
-
-In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems.
-Moreover, our detailed theoretical analysis showed that we can adapt the recently introduced Floquet-Drude conductivity model to extend the models that were used to describe the transport characteristics in quantum Hall systems.
-Owing to the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices, which are employed as the building blocks of next-generation nanoelectronic devices.
-As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D optoelectronic nanotransistors, enhancing their performance and inventing novel appliances.
-%===============================================================================
-
-%===============================================================================
-% Acknowledgments
-%===============================================================================
-\begin{acknowledgments}
-K.H wish to acknowledge the members of A$\chi$L at Monash University for their encouragement and support and specially T.N.
-Perera and R.T.Wijesekara for insightful discussions.
-The work of K.H is supported by the Australian Government Research Training Program (RTP) Scholarship and the Monash University Institute of Graduate Research.
-\end{acknowledgments}
-%===============================================================================
-
-%===============================================================================
-% Add appendixes
-%===============================================================================
-\begin{appendix}
-
-%===============================================================================
-% Appendix A : Wave function solutions for a dressed quantum Hall system
-%===============================================================================
-\section{\label{appendix_a} Wave function solutions for a dressed quantum Hall system}
-
-The derivation of the solutions for the time-dependent Schrödinger equation with our system's Hamiltonian (Eq.
-\ref{eq:1}) is quite similar to that followed in Refs.
-\cite{husimi53,dini16}.
-We start with expanding the Hamiltonian for two-dimensional scenario
-\begin{equation} \label{eq:a1}
-  \hat{H}_e(t) = \frac{1}{2m_e}
-  \left\{
-    \left(\hat{p}_x + eBy \right)^2 +
-    \left[
-      \hat{p}_y - \frac{eE}{\omega}\cos(\omega t)
-    \right]^2
-  \right\}.
-\end{equation}
-Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
-${L_x}^{-1/2}\exp(\flatfrac{ip_x x}{\hbar})$ where $p_x = \flatfrac{2\pi \hbar m}{L_x}$ with $ m \in \mathbb{Z}$.
-Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
-\begin{equation} \label{eq:a2}
-    \hat{H}_e(t) = \frac{1}{2m_e}
-    \left\{
-      \left({p}_x + eBy \right)^2 +
-      \left[
-        i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)
-      \right]^2
-    \right\}.
-\end{equation}
-Subsequently, we define the \textit{center of the cyclotron orbit} on the $y$-axis as $y_0 = \flatfrac{-p_x}{(eB)}$, and the \textit{cyclotron frequency} as  $\omega_0 = {eB}/{m_e}$.
-This leads to a new arrangement of the Hamiltonian
-\begin{equation} \label{eq:a3}
-  \begin{aligned}
-    \hat{H}_e(t) =
-      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
-      \frac{1}{2m_e} &
-      \left[
-        -\hbar^2 \pdv[2]{\tilde{y}}  +
-        \frac{2i\hbar eE}{\omega} \cos(\omega t) \pdv{\tilde{y}}
-        \right.\\
-        & \left. \qquad\qquad\quad +
-        \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
-        \right],
-  \end{aligned}
-\end{equation}
-where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
-\begin{equation} \label{eq:a4}
-    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
-\end{equation}
-can be presented by the following form
-\begin{equation} \label{eq:a5}
-    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}}
-    \exp\left(
-      \frac{ip_x x}{\hbar} +
-      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
-    \right) \vartheta(\tilde{y},t),
-\end{equation}
-where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
-\begin{equation} \label{eq:a6}
-    \left[
-    \frac{m_e \omega_0^2}{2} \tilde{y}^2
-    - {eE\tilde{y}}\sin(\omega t)
-    - \frac{\hbar^2}{2m_e} \pdv[2]{\tilde{y}}
-    - i \hbar \dv{t}
-    \right]
-    \vartheta(\tilde{y},t) = 0.
-\end{equation}
-If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
-\begin{equation} \label{eq:a7}
-     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
-    \left(
-    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
-    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
-    \right)
-    \vartheta(\tilde{y},t).
-\end{equation}
-Thus, we can identify $S(t) = eE\sin(\omega t)$ term as an external force that act on the harmonic oscillator, and we can solve Eq.~(\ref{eq:a6}) as a forced harmonic oscillator on $\tilde{y}$ axis
-\begin{equation} \label{eq:a8}
-  \begin{aligned}
-    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
-    \bigg[
-    -
-    \frac{\hbar^2}{2m_e}
-    \pdv[2]{\tilde{y}} +
-    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
-    - \tilde{y}S(t)]
-    \bigg]
-    \vartheta(\tilde{y},t).
-  \end{aligned}
-\end{equation}
-This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}.
-We introduce a time-dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
-\begin{equation} \label{eq:a9}
-    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
-\end{equation}
-and this leads to
-\begin{equation} \label{eq:a10}
-  \begin{aligned}
-    i \hbar \pdv{\varphi(y',t)}{t}   &=
-    \left\{
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 y'^2
-        \right. \\
-        & \left. \qquad
-        - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
-        \right. \\
-        & \left. \qquad +
-        \left[
-            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
-        \right]y'
-    \right\} \varphi(y',t).
-  \end{aligned}
-\end{equation}
-Here, we introduced $\dot{\zeta} = \pdv*{\zeta}{t}$ and $\ddot{\zeta} = \pdv*[2]{\zeta}{t}$ for the sake of notational convenience. Subsequently, we can restrict $\zeta(t)$ function such that
-\begin{equation} \label{eq:a11}
-  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
-\end{equation}
-and that simply our previous expression as
-\begin{equation} \label{eq:a12}
-  \begin{aligned}
-    i \hbar \pdv{\varphi(y',t)}{t} =&
-    \left[
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \right. \\
-        & \left. \qquad\qquad\qquad
-        - L(\zeta,\dot{\zeta},t)
-    \right]\varphi(y',t).
-  \end{aligned}
-\end{equation}
-Here
-\begin{equation} \label{eq:a13}
-  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
-\end{equation}
-is the Lagrangian of a classical driven oscillator. To proceed further, we introduce another unitary transform as follows
-\begin{equation} \label{eq:a14}
-    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t} L(\zeta,\dot{\zeta},t')dt') \chi(y',t),
-\end{equation}
-and subtitling Eq.~(\ref{eq:a14}) back in Eq.~(\ref{eq:a12}), we can obtain
-\begin{equation} \label{eq:a15}
-    i \hbar \pdv{t} \chi(y',t)  =
-    \left(
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 {y'}^2
-    \right) \chi(y',t).
-\end{equation}
-This is the well-known Schrödinger equation of the quantum harmonic oscillator.
-This allows us to identify the well known eigenfunction solutions \cite{griffiths18,shankar94}
-\begin{equation} \label{eq:a16}
-  \chi_n(y) =
-  \sqrt{\frac{\kappa}{2^{n}n!\sqrt{\pi}}}
-  e^{-\kappa^2 y^2/2}
-  \mathcal{H}_n \qty(\kappa y),
-\end{equation}
-with eigenvalues
-\begin{equation} \label{eq:a17}
-  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
-  ~\text{for}~
-  n \in \mathbb{Z}^{+}_0.
-\end{equation}
-Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
-Thus, we can identify the solutions for Eq.~(\ref{eq:a8}) as
-\begin{equation} \label{eq:a18}
-  \begin{aligned}
-    \vartheta_n(\tilde{y},t) = \chi_n\bm{(}\tilde{y} - \zeta(t)\bm{)}
-     \text{exp}&
-     \left(
-     \frac{i}{\hbar}
-     \left\{
-     - \epsilon_nt +
-     m_e \left[\tilde{y}-\zeta(t)\right] \dot{\zeta(t)} \right. \right. \\
-     & \left. \left. \qquad
-     + \int_0^{t}L(\zeta,\dot{\zeta},t') dt'
-     \right\}
-     \right).
-  \end{aligned}
-\end{equation}
-Since $\chi_n(x)$ functions forms a complete set, we can present any general solution for  $\vartheta_(\tilde{y},t)$ using the solutions derived in Eq.~(\ref{eq:a18}).
-
-Finally, we consider our scenario where we can assume that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq:a11}) as
-\begin{equation} \label{eq:a19}
-  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
-\end{equation}
-Substituting solutions given in Eq.~(\ref{eq:a18}) back in Eq.~(\ref{eq:a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq:a4}) as follows
-\begin{equation} \label{eq:a20}
-  \begin{aligned}
-    &\psi_{n,m}(x,y,t) \\
-    & \quad=  \frac{1}{\sqrt{L_x}}
-    \chi_n\left(y - y_0 - \zeta(t)\right)\\
-    &\qquad\times
-    \text{exp}\left(
-    \frac{i}{\hbar}
-    \left\{- \epsilon_nt
-    + p_x x
-    + \frac{eE(y - y_0)}{\omega}\cos(\omega t) \right. \right. \\
-    & \left. \left. \qquad\qquad +
-    m_e\left[y - y_0 -\zeta(t)\right] \dot{\zeta}(t)+
-    \int_0^{t}L(\zeta,\dot{\zeta},t') dt'
-    \right\}
-    \right).
-  \end{aligned}
-\end{equation}
-%===============================================================================
-
-%===============================================================================
-% Appendix B :
-%===============================================================================
-\section{\label{appendix_b} Floquet modes and quasienergies}
-
-\subsection{Position space representation}
-
-First we define the time integral of the Lagrangian of the classical oscillator given in Eq.~(\ref{eq:5}), over a period $T=2\pi/\omega$ as
-\begin{equation} \label{eq:b1}
-  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T L(\zeta,\dot{\zeta},t') dt'.
-\end{equation}
-Additionally, performing this integral, we can obtain a more simplified result
-\begin{equation} \label{eq:b2}
-  \Delta_{\varepsilon} = \frac{e^2E^2}{4m_e(\omega_0^2 - \omega^2)}.
-\end{equation}
-Next, we define another parameter
-\begin{equation} \label{eq:b3}
-  \xi =
-  \int_0^t \; L(\zeta,\dot{\zeta},t') dt' -
-  \Delta_{\varepsilon} t,
-\end{equation}
-and after simplifying, we can identify
-\begin{equation} \label{eq:b4}
-  \xi =
-  \frac{e^2E^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t),
-\end{equation}
-which is a periodic function in time. Using these parameters, we can factorize the wave function given in Eq.~(\ref{eq:2}) as linearly time-dependent part and periodic time-dependent part as follows
-\begin{equation} \label{eq:b5}
-  \begin{aligned}
-    \psi_{\alpha}&(x,y,t) \\
-    & =
-    \exp(\frac{i}{\hbar} \left(-\epsilon_nt + \Delta_{\varepsilon} t \right) )
-    \frac{1}{\sqrt{L_x}} \chi_n\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
-    \\
-    & \quad\times
-    \exp \left(
-       \frac{i}{\hbar}
-       \left\{
-       p_x x +
-       \frac{eE(y-y_0)}{\omega}\cos(\omega t)  \right. \right. \\
-    & \left. \left. \qquad\qquad\qquad\qquad
-    + m_e\dot{\zeta}(t) \left[ y-y_0 -\zeta(t) \right]
-    + \xi \right\}
-     \right).
-  \end{aligned}
-\end{equation}
-This leads to separate the linear time-dependent phase component as the quasienergies
-\begin{equation} \label{eq:b6}
-  \varepsilon_{n} =
-  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
-\end{equation}
-while rest of the components as time-periodic Floquet modes
-\begin{equation} \label{eq:b7}
-  \begin{aligned}
-    \phi_{n,m}(x,y,t) =  &
-    \frac{1}{\sqrt{L_x}} \chi_n\bm{\left(}y - y_0 - \zeta(t)\bm{\right)} \\
-    & \times
-    \exp \left(
-       \frac{i}{\hbar}
-       \left\{
-       p_x x +
-       \frac{eE(y-y_0)}{\omega}\cos(\omega t)  \right. \right. \\
-    & \left. \left. \qquad\qquad\quad
-    + m_e\dot{\zeta}(t) \left[ y-y_0 -\zeta(t) \right]
-    + \xi \right\}
-     \right).
-  \end{aligned}
-\end{equation}
-
-\subsection{Momentum space representation}
-
-We perform continuous Fourier transform over the considering confined space $A=L_xL_y$ on the Floquet modes given in Eq.~(\ref{eq:7}) to realize the Floquet modes in momentum space
-\begin{equation} \label{eq:b8}
-  \begin{aligned}
-    \phi_{n,m}&(k_x,k_y,t) \\
-    & =
-    \exp(\frac{-i\gamma(t)}{\hbar}y_0)
-    \exp(\frac{-i}{\hbar}\left[m_e \dot{\zeta}(t) \zeta(t) - \xi \right]) \\
-    & \quad\times
-    \int_{-L_y/2}^{L_y/2} \exp(-i \left[k_y - \gamma(t) \right]y)
-      \chi_n \bm{\left(}y - \mu(t)\bm{\right)} dy \\
-    & \quad\times
-    \frac{1}{\sqrt{L_x}} \int_{-L_x/2}^{L_x/2}
-     \exp(-ik_x x)\exp( \flatfrac{i p_x }{\hbar}x ) dx.
-  \end{aligned}
-\end{equation}
-Here we used new two parameters
-\begin{equation} \label{eq:b9}
-  \mu(t) = \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0,
-\end{equation}
-and
-\begin{equation} \label{eq:b10}
-  \gamma(t) =
-  \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
-\end{equation}
-Subsequently, using the Fourier transform identity \cite{bruus04}
-\begin{equation} \label{eq:b11}
-  \int_{-L_x/2}^{L_x/2}
-  \exp( -ik_x x + \flatfrac{i p_x x}{\hbar}) dx =
-  L_x \delta_{k_x,\flatfrac{p_x}{\hbar}},
-\end{equation}
-we can derive
-\begin{equation} \label{eq:b12}
-  \begin{aligned}
-    \phi_{n,m}(k_x,k_y,t)  =
-    \Phi_{n,m}&(k_y,t)
-    \delta_{k_x,\flatfrac{p_x}{\hbar}}
-    \exp(\frac{-i}{\hbar} \gamma(t)y_0) \\
-    & \times
-    \exp(\frac{-i}{\hbar}
-    \left[ m_e \dot{\zeta}(t) \zeta(t) - \xi \right]),
-  \end{aligned}
-\end{equation}
-where we can define $\Phi_{n,m}(k_y,t)$ as
-\begin{equation} \label{eq:b13}
-  \begin{aligned}
-    &\Phi_{n,m}(k_y,t) \\
-    & \quad=
-    \sqrt{L_x}
-    \int_{-L_y/2}^{L_y/2}
-    \chi_n \bm{\left(}y - \mu(t)\bm{\right)}
-    \exp \bm{\left(}-i\left[k_y - \gamma(t) \right]y\bm{\right)} dy.
-  \end{aligned}
-\end{equation}
-Substituting ${k'_y} = k_y -\gamma(t)$ with $y' = y -\mu(t)$, and assuming that the size of the considered 2DEG sample in $y$-direction is considerably large ($L_y \rightarrow \infty$), we can obtain
-\begin{equation} \label{eq:b14}
-  \Phi_{n,m}({k'_y} ,t) =
-  {\sqrt{L_x}} e^{-i {k'_y}\mu}
-  \int_{-\infty}^{\infty} \chi_{n}(y') \exp(-i{k'_y} y') dy'.
-\end{equation}
-Moreover, we can identify that the above integral represents the Fourier transform of $\chi_n$ functions.
-In addition, using the symmetric conditions of the Fourier transform for Gauss-Hermite functions $\theta_n(x)$ \cite{celeghini21}
-\begin{equation} \label{eq:b15}
-  \mathcal{FT}[\theta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\theta_n(k/\kappa),
-\end{equation}
-we can simply the Eq.~(\ref{eq:b14}) as
-\begin{equation} \label{eq:b16}
-  \Phi_{n,m}({k'_y} ,t) =
-  \sqrt{L_x} e^{-i {k'_y}\mu} \widetilde{\chi}_n(k'_y),
-\end{equation}
-with
-\begin{equation} \label{eq:b17}
-  \widetilde{\chi}_{n}(k) =
-  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
-  \left(\frac{1}{\kappa} \right)^{1/2}
-  e^{-\flatfrac{k^2}{(2 \kappa^2)}}
-  \mathcal{H}_n (\flatfrac{k}{\kappa}).
-\end{equation}
-Finally, substitute Eq.~(\ref{eq:b16}) back into Eq.~(\ref{eq:b12}) and this leads to
-\begin{equation} \label{eq:b18}
-  \begin{aligned}
-    \phi_{n,m}(k_x,k_y,t)  = &
-    {\sqrt{L_x}} \widetilde{\chi}_n \bm{\left(} k_y - b\cos(\omega t)\bm{\right)} \\
-    & \times
-    \exp \left(
-      i\xi -ik_y  \left[d\sin(\omega t) + \frac{\hbar k_x}{eB} \right]
-    \right),
-  \end{aligned}
-\end{equation}
-where
-\begin{equation} \label{eq:b19}
-  b =
-  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
-\end{equation}
-and
-\begin{equation} \label{eq:b20}
-  d =
- \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
-\end{equation}
-It is necessary to notice that $k_x$ is quantized with $k_x = \flatfrac{2\pi m}{L_x} ~,~ m \in \mathbb{Z}$.
-%===============================================================================
-
-%===============================================================================
-% Appendix C :
-%===============================================================================
-\section{\label{appendix_c} Floquet-Fermi golden rule for a dressed quantum  Hall system}
-
-We derive the Floquet-Fermi golden rule for our dressed quantum Hall system with the help of the $t$-$t'$ formalism. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
-\begin{equation} \label{eq:c1}
-  \ket{\psi_{n,m}(t,t')} =
-  \exp(-\frac{i}{\hbar}\varepsilon_{n} t)\ket{\phi_{n,m}(t')},
-\end{equation}
-are derived by separating the aperiodic and periodic components of the Floquet states given in Eq.~(\ref{eq:14}).
-Additionally, these states fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
-\begin{equation} \label{eq:c2}
-  i \hbar \pdv{t}\ket{\psi_{n,m}(t,t')} =
-  H_F(t') \ket{\psi_{n,m}(t,t')},
-\end{equation}
-where the \textit{Floquet Hamiltonian} defined as
-\begin{equation} \label{eq:c3}
-  H_F(t') =
-  H_e(t') - i\hbar \pdv{t'}.
-\end{equation}
-Next, we can identify the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation as
-\begin{equation} \label{eq:c4}
-  U_F(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\left[t-t_0 \right]).
-\end{equation}
-The advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time ordering operators \cite{wackerl20}.
-
-We model the effect caused by impurities in the considered system as a single perturbation potential formed by a group of randomly distributed impurities.
-Thus, we introduce a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, and the $t$-$t'$-Schrödinger equation becomes
-\begin{equation} \label{eq:c5}
-  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')} =
-  \left[H_F(t') + V(\vb{r}) \right]\ket{\Psi_{n,m}(t,t')}.
-\end{equation}
-This introduces a new wave function solution $\ket{\Psi_{n,m}}$ for a system with a given perturbation. If $t\leq t_0$, both of the solutions for Eq.~(\ref{eq:c2}) and Eq.~(\ref{eq:c5}) coincide
-\begin{equation} \label{eq:c6}
-  \ket{\psi_{n,m}(t,t')} =\ket{\Psi_{n,m}(t,t')} \quad
-  \text{when} \quad
-  t \leq t_0.
-\end{equation}
-Next, we move our analysis into the interaction picture representation \cite{bruus04,mahan00} and in the interaction picture, we can identify the $t$-$t'$-Floquet state as
-\begin{equation} \label{eq:c7}
-  \ket{\Psi_{n,m}(t,t')}_I = U_0^{\dagger}(t,t_0;t')
-  \ket{\Psi_{n,m}(t,t')}.
-\end{equation}
-Due to time-independence, the perturbation in the interaction picture has the same form as the Schrödinger picture representation
-\begin{equation} \label{eq:c8}
-  V_I(\vb{r}) = U_0^{\dagger}(t,t_0;t')V(\vb{r})U_0(t,t_0;t') =
-  V(\vb{r}).
-\end{equation}
-This leads us to the $t$-$t'$-Schrödinger equation in the interaction picture representation
-\begin{equation} \label{eq:c9}
-  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')}_I =
-  V_I(\vb{r})\ket{\Psi_{n,m}(t,t')}_I,
-\end{equation}
-with the recursive solutions \cite{bruus04,mahan00}
-\begin{equation} \label{eq:c10}
-  \begin{aligned}
-  \ket{\Psi_{n,m}(t,t')}_I = &\ket{\Psi_{n,m}(t_0,t')}_I \\
-  &+
-  \frac{1}{i\hbar}
-  \int_{t_0}^t
-  V_I(\vb{r}) \ket{\Psi_{n,m}(t_1,t')}_I dt_1.
-  \end{aligned}
-\end{equation}
-Iterating the solution only up to the first order (Born approximation) we obtain
-\begin{equation} \label{eq:c11}
-  \begin{aligned}
-    \ket{\Psi_{n,m}(t,t')}_I \approx &\ket{\psi_{n,m}(t_0,t')} \\
-    &+
-    \frac{1}{i\hbar}
-    \int_{t_0}^t
-    V_I(\vb{r}) \ket{\psi_{n,m}(t_0,t')} dt_1.
-  \end{aligned}
-\end{equation}
-
-Since our $t$-$t'$-Floquet states create a basis, we can represent the solutions for the $t$-$t'$-Schrödinger equation given in Eq.~(\ref{eq:c5}) using our known $t$-$t'$-Floquet states as follows
-\begin{equation} \label{eq:c12}
-  \ket{\Psi_{\alpha}(t,t')} = \sum_{\beta} a_{\alpha,\beta}(t,t')
-  \ket{\psi_{\beta}(t,t')}.
-\end{equation}
-Here, we used a single term notation to represent two quantum numbers; $\alpha \equiv (n_{\alpha},m_{\alpha})$ and $\beta \equiv (n_{\beta},m_{\beta})$.
-Subsequently, we can identify the \textit{scattering amplitude} as $a_{\alpha,\beta}(t,t') =
-\braket{\psi_{\beta}(t,t')}{\Psi_{\alpha}(t,t')}$ and we can evaluate this with
-\begin{equation} \label{eq:c13}
-  \begin{aligned}
-  a_{\alpha,\beta}(t,t') = &
-  \braket{\psi_{\beta}(t,t')}{\psi_{\alpha}(t,t')} \\
-  &+
-  \frac{1}{i\hbar}
-  \int_{t_0}^t
-  \bra{\psi_{\beta}(t_1,t')}
-  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
-  \end{aligned}
-\end{equation}
-Since the $t$-$t'$-Floquet states are orthonormal and assuming $t_0 = 0$ and $\alpha \neq \beta$ this leads to
-\begin{equation} \label{eq:c14}
-  a_{\alpha,\beta}(t,t') =
-  -
-  \frac{i}{\hbar}
-  \int_{0}^t
-  \bra{\psi_{\beta}(t_1,t')}
-  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
-\end{equation}
-
-Next, we consider a scattering phenomenon when a electron scatters from a known $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with a constant quansienergy $\varepsilon$ as follows
-\begin{equation} \label{eq:c15}
-  \begin{aligned}
-  \ket{\psi_{\beta}(t,t')} &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
-  \ket{\phi_{\beta}(t')} \\
-  &
-  \xRightarrow{\text{scattering}}
-  \ket{\Psi_{\alpha}(t,t')} = \exp(-\frac{i}{\hbar}\varepsilon t)
-  \ket{\Phi_{\alpha}(t')}.
-  \end{aligned}
-\end{equation}
-\begin{figure}[b]
-  \includegraphics[scale=1.0]{figures/fig_6.pdf}
-  \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
-  \label{fig:2}
-\end{figure}
-This phenomenon is illustrated in Fig.~\ref{fig:2}.
-We can calculate the scattering amplitude for this scattering scenario using the expression derived in Eq.~(\ref{eq:c14}) as follows
-\begin{equation} \label{eq:c16}
-  \begin{aligned}
-    a_{\alpha\beta}(t,t') =
-    -\frac{i}{\hbar}
-    \int_{0}^t
-    e^{\frac{i}{\hbar}\left(\varepsilon_{\beta} - \varepsilon \right)t_1}
-    \bra{\phi_{\beta}(t')}
-    V(\vb{r}) \ket{\phi_{\alpha}(t')}  dt_1.
-  \end{aligned}
-\end{equation}
-By assuming for a long duration ($t \rightarrow \infty$), we can turn this integral into a delta distribution
-\begin{equation} \label{eq:c17}
-  \begin{aligned}
-    a_{\alpha\beta}(t') =
-    -2\pi i \delta(\varepsilon_{\beta} - \varepsilon)Q,
-  \end{aligned}
-\end{equation}
-where $Q = \bra{\phi_{\beta}(t')} V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using the completeness properties we can re-write this as
-\begin{equation} \label{eq:c18}
-    Q =
-    \sum_{\vb{k}}\sum_{\vb{k'}}
-    \braket{\phi_{\beta}(t')}{\vb{k'}}
-    \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}
-    \braket{\vb{k}}{\phi_{\alpha}(t')}.
-\end{equation}
-Moreover, separating $x$-directional and $y$-directional momentum components, we can simply this to obtain
-\begin{equation} \label{eq:c19}
-    Q =
-    \sum_{k_x}\sum_{{k'}_x}
-    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
-    V_{\vb{k'},\vb{k}}
-    \phi_{\beta}^{\dagger}(\vb{k'},t')
-    \phi_{\alpha}(\vb{k},t')  dk_y d{k'}_y,
-\end{equation}
-with $V_{\vb{k'},\vb{k}} = \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.
-
-Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
-Thus, we can describe the scattering potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
-\begin{equation} \label{eq:c20}
-  V(\vb{r}) =
-  \sum_{i=1}^{N_{imp}}
-  \upsilon (\vb{r}-\vb{r}_i).
-\end{equation}
-Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
-This model is characterized by the following two equations \cite{akkermans10}
-\begin{subequations}
-\begin{equation} \label{eq:c21a}
-  \expval{\upsilon(\vb{r})}_{imp} =0,
-\end{equation}
-\begin{equation} \label{eq:c21b}
-  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
-\end{equation}
-\end{subequations}
-where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
-In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
-Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
-\begin{equation} \label{eq:c22}
-  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
-\end{equation}
-where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
-\begin{equation} \label{eq:c23}
-  V(\vb{r}) =
-  \sum_{i=1}^{N_{imp}}
-  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
-\end{equation}
-Here we can identify the $\Upsilon_{imp}$ as the strength of the delta potential.
-Furthermore, we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
-\begin{subequations} \label{eq:c24}
-\begin{align}
- V_{\vb{k'},\vb{k}} & =
- \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
- \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq:c24a} \\
- & =
- \sum_{i=1}^{N_{imp}}
- \int_{-\infty}^{\infty} \left[
- \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \right. \\
- & \left. \qquad\quad\times
- \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
- \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \right] dy \label{eq:c24b} \\
-  & =
- \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
- e^{i(k'_y - k_y )y}
- \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq:c24c}.
-\end{align}
-\end{subequations}
-Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs.
-Additionally, assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
-\begin{subequations} \label{eq:c25}
-  \begin{align}
-    V_{\vb{k'},\vb{k}}
-    & =
-    V_{k'_x,k_x}
-    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty}
-    e^{i\left({k'}_y - k_y \right)y_i} dy_i \label{eq:c25a} \\
-    & =
-    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y). \label{eq:c25b}
-  \end{align}
-\end{subequations}
-In the above equation we introduced
-\begin{equation} \label{eq:c26}
-  V_{{k'}_x,k_x} =
-  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x},
-\end{equation}
-which is a constant value for every $i$-th impurity.
-Moreover, $\eta_{imp}$ is the number of impurities in a unit area.
-It is important to note that in the above expression $\braket{x}{k_x} = e^{-ik_xx}$.
-
-Now using Eq.~(\ref{eq:10}) and Eq.~(\ref{eq:c25b}) on Eq.~(\ref{eq:c19}), we obtain
-\begin{equation} \label{eq:c27}
-  \begin{aligned}
-    Q  =
-    \sum_{k_x}\sum_{{k'}_x} &
-    {\eta_{imp} V_{{k'}_x,k_x}} L_x
-    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
-    \delta({k'}_y - k_y)
-    \\
-    & \times
-    \widetilde{\chi}_{n_{\beta}} \bm{\left(} {k'}_y -b\cos(\omega t) \bm{\right)}
-    \widetilde{\chi}_{n_{\alpha}}  \bm{\left(}k_y -b\cos(\omega t) \bm{\right)}
-    \\
-    & \times
-    e^{i[{k'}_y - k_y]d\sin(\omega t)}
-    e^{i[{k'}_y {y'}_0 - k_y y_0]}
-     dk'_y dk_y.
-  \end{aligned}
-\end{equation}
-Here we have changed the time variable $t' \rightarrow t$ only for the simplicity of notation. We can more simply this as
-\begin{equation} \label{eq:c28}
-  \begin{aligned}
-    Q =
-    \sum_{k_x}\sum_{{k'}_x} \eta_{imp} L_x V_{{k'}_x,k_x} I,
-  \end{aligned}
-\end{equation}
-with
-\begin{equation} \label{eq:c29}
-  \begin{aligned}
-    I =
-    \int_{-\infty}^{\infty}
-    \widetilde{\chi}_{n_{\beta}} &\bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
-    \widetilde{\chi}_{n_{\alpha}} \bm{\left(} k_y -b\cos(\omega t) \bm{\right)} \\
-    & \times
-    \exp \bm{(}
-      -ik_y  \left(y_0 - {y'}_0 \right)
-    \bm{)} dk_y.
-  \end{aligned}
-\end{equation}
-To avoid the energy exchange from the dressing field and electrons in Landau levels, the applied radiation must be a purely dressing field.
-Therefore, in this study we assume that the dressing field can only renormalize the the probability of electron scattering inside a same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
-This transform the Eq.~(\ref{eq:c29}) to
-\begin{equation} \label{eq:c30}
-    I =
-    \int_{-\infty}^{\infty}
-    \widetilde{\chi}_N^2 \bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
-    \exp \bm{(}
-      -ik_y  \left(y_0 - {y'}_0 \right)
-    \bm{)} dk_y.
-\end{equation}
-Using the Fourier transform of Gauss-Hermite functions \cite{celeghini21} and the convolution theorem \cite{arfken85,bracewell78} we obtain
-\begin{equation} \label{eq:c31}
-  \begin{aligned}
-    I =
-    {2\pi} &
-    \exp \bm{(} b({y'}_0 - y_0)\cos(\omega t) \bm{)} \\
-    & \times
-    \int_{-\infty}^{\infty}
-    {\chi}_{N}(y)
-    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
-  \end{aligned}
-\end{equation}
-Finally, we can evaluate the scattering amplitude derived in Eq.~(\ref{eq:c17}) for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as follows
-\begin{equation} \label{eq:c32}
-  \begin{aligned}
-    a_{\alpha\beta}&(k_x,k'_x,t)
-    \\
-    & =
-    -2\pi i
-    \eta_{imp} L_x V_{{k'}_x,k_x}
-    e^{ b({y'}_0 - y_0)\cos(\omega t)}\\
-    & \quad\times
-    \delta(\varepsilon_{N} - \varepsilon)
-    \int_{-\infty}^{\infty}
-    {\chi}_{N}(y)
-    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
-  \end{aligned}
-\end{equation}
-Since this scattering amplitude is time-periodic, we can write this as a Fourier series expansion
-\begin{equation} \label{eq:c33}
-    a_{\alpha\beta}(k_x,k'_x,t) =
-    \sum_{l=-\infty}^{\infty} a^l_{\alpha\beta}(k_x,k'_x) e^{-il\omega t}.
-\end{equation}
-In addition, using Jacobi-Anger expansion \cite{cuyt08,abramowitz64}
-\begin{equation} \label{eq:c34}
-    e^{iz\cos(\theta)} = \sum_{l=-\infty}^{\infty} i^l J_l(z) e^{-il\theta},
-\end{equation}
-where $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, we can re-write the Eq.~(\ref{eq:c32}) as follows
-\begin{equation} \label{eq:c35}
-  \begin{aligned}
-    a_{\alpha\beta}&(k_x,k'_x,t)  \\
-    & =
-    \sum_{l=-\infty}^{\infty}
-    -2\pi i^{l+1}
-    \eta_{imp} L_x V_{{k'}_x,k_x}
-    J_l\bm{(}b({y'}_0 - y_0)\bm{)} \\
-    & \quad\times
-    \delta(\varepsilon_{N} - \varepsilon)
-    \int_{-\infty}^{\infty}
-    {\chi}_{N}(y)
-    {\chi}_{N}(y_0 - {y'}_0 - y)  dy \;e^{-il\omega t}.
-  \end{aligned}
-\end{equation}
-Thus, we can identify the Fourier series component of the scattering amplitude as
-\begin{equation} \label{eq:c36}
-  \begin{aligned}
-    a^l_{\alpha\beta}(k_x,k'_x) = &
-    -2\pi i^{l+1}
-    \eta_{imp} L_x V_{{k'}_x,k_x}\\
-    & \times
-    \delta(\varepsilon_{N} - \varepsilon)
-    J_l\bm{(}b({y'}_0 - y_0)\bm{)}\\
-    & \times
-    \int_{-\infty}^{\infty}
-    {\chi}_N(y)
-    {\chi}_N(y_0 - {y'}_0 - y) dy.
-  \end{aligned}
-\end{equation}
-Furthermore, we can define \textit{transition probability matrix} as
-\begin{equation} \label{eq:c37}
-    \left(A_{\alpha\beta} \right)^{l,l'} =
-    a^l_{\alpha\beta}\left[a^{l'}_{\alpha\beta} \right]^{*},
-\end{equation}
-and this becomes
-\begin{equation} \label{eq:c38}
-  \begin{aligned}
-      \left(A_{\alpha\beta} \right)^{l,l'}(k_x,k'_x) = &
-      \left({ 2 \pi \eta_{imp} L_x V_{{k'}_x,k_x}}\right)^2
-      \delta^2(\varepsilon_{N} - \varepsilon) \\
-      & \times
-      J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)}\\
-      & \times
-      \left|
-      \int_{-\infty}^{\infty}
-      {\chi}_N(y)
-      {\chi}_N(y_0 - {y'}_0 - y) dy \right|^2.
-  \end{aligned}
-\end{equation}
-Then describing the square of the delta distribution using the following interpretation \cite{dini16,kibis14}
-\begin{equation} \label{eq:c39}
-    \delta^2(\varepsilon) =
-    \delta(\varepsilon)\delta(0) =
-    \frac{\delta(\varepsilon)}{2\pi \hbar}
-    \int_{-t/2}^{t/2} e^{i0\times t'/\hbar} dt'\; =
-    \frac{\delta(\varepsilon)t}{2\pi \hbar},
-\end{equation}
-and executing the time derivation operation on each matrix element of transition probability matrix, we receive the \textit{transition amplitude matrix} elements
-\begin{equation} \label{eq:40}
-  \begin{aligned}
-    \Gamma_{\alpha\beta}^{ll'}(k_x,k'_x) = &
-    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar} |V_{{k'}_x,k_x}|^2
-    \delta(\varepsilon_{\beta} - \varepsilon)\\
-    & \times
-    J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)} \\
-    & \times
-    \left|
-    \int_{-\infty}^{\infty}
-    {\chi}_N(y)
-    {\chi}_N(y_0 - {y'}_0 - y) dy \right|^2.
-  \end{aligned}
-\end{equation}
-
-Additionally, the inverse scattering time matrix can be identified as the sum of all available momentum over the impurity averaged transition probability matrix element \cite{wackerl20,wackerlthesis20}
-\begin{equation} \label{eq:41}
-    \left(\frac{1}{\tau(\varepsilon,k_x)} \right)^{ll'}_{\alpha\beta} =
-    \frac{1}{L_x} \sum_{{k'}_x}
-    \expval**{\Gamma_{\alpha\beta}^{ll'}({k'}_x,k_x)}_{imp}.
-\end{equation}
-Next, applying the 1-dimensional momentum continuum limit $\sum_{{k'}_x} \longrightarrow {L_x}/{2\pi}\int d {k'}_x$, we can obtain
-\begin{widetext}
-\begin{equation} \label{eq:42}
-  \begin{aligned}
-    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_{\alpha\beta} = &
-    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar}
-    \frac{V_{imp}}{2\pi}
-    \delta(\varepsilon_{\beta} - \varepsilon) \\
-    & \times
-    \int_{-\infty}^{\infty} \left\{
-    J_l\bm{\left(}\frac{b\hbar}{eB}({k}_x - {k'}_x)\bm{\right)}
-    J_{l'}\bm{\left(}\frac{b\hbar}{eB}({k}_x - {k'}_x)\bm{\right)}
-    \left|
-    \int_{-\infty}^{\infty}
-    {\chi}_N(y)
-    {\chi}_N \bm{\left(}\frac{\hbar}{eB} ({k'}_x - {k}_x) - y \bm{\right)} dy\right|^2 \right\} d {k'}_x.
-  \end{aligned}
-\end{equation}
-Here an impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2}_{imp} = V_{imp}$.
-Finally, using substitutions $k'_x = k_1$ and $y = \flatfrac{\hbar{k_2}}{(eB)}$, we can derive our expression for the inverse scattering time matrix for $N$-th Landau
-level as follows
-\begin{equation} \label{eq:43}
-  \begin{aligned}
-    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_{N} &=
-    \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{e^2B^2}
-    \delta(\varepsilon - \varepsilon_{N}) \\
-    & \times
-    \int_{-\infty}^{\infty} \left\{
-    J_l\bm{\left(}\frac{b\hbar}{eB}({k}_x - k_1)\bm{\right)}
-    J_{l'}\bm{\left(}\frac{b\hbar}{eB}({k}_x - k_1)\bm{\right)}
-    \left|
-    \int_{-\infty}^{\infty}
-    {\chi}_N\left(\frac{\hbar}{eB}k_2 \right)
-    {\chi}_N \bm{\left(}\frac{\hbar}{eB} (k_1 - k_x - k_2) \bm{\right)} dk_2 \right|^2 \right\} d k_1.
-  \end{aligned}
-\end{equation}
-\end{widetext}
-%===============================================================================
-
-%===============================================================================
-% Appendix D :
-%===============================================================================
-\section{\label{appendix_d} Current operators for a dressed quantum Hall system}
-
-In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system.
-We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(\ref{eq:1}) and we identified them as the Floquet states in Eq.~(\ref{eq:14}).
-For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(\ref{eq:10}) as quantum states using their corresponding quantum numbers as follows
-\begin{equation} \label{eq:d1}
-  \ket{\phi_{n,m}} = \ket{n,k_x}.
-\end{equation}
-Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
-\begin{equation} \label{eq:d2}
-  \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
-\end{equation}
-Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
-\begin{equation} \label{eq:d3}
-  \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
-\end{equation}
-where $\widetilde{m}$ is the mass of the considering particle.
-
-First, we consider the $x$-directional particle current operator component, and we can identify that as
-\begin{equation} \label{eq:d4}
-  \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
-\end{equation}
-Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
-\begin{equation} \label{eq:d5}
-  \left({j}_x \right)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
-\end{equation}
-and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq:7}) as follows
-\begin{equation} \label{eq:d6}
-  \begin{aligned}
-    \left({j}_x \right)_{nm,n'm'} = &
-    \frac{1}{{\widetilde{m}}}
-    \delta_{k_x,k'_x}
-    \int
-    \left(\hbar k'_x + eBy\right) \\
-    & \times
-     \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
-    \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
-    dy.
-  \end{aligned}
-\end{equation}
-Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
-\begin{equation} \label{eq:d7}
-  \begin{aligned}
-    \left({j}_x \right)_{nm,n'm'} =
-    \frac{1}{{\widetilde{m}}}
-    \delta_{k_x,k'_x}
-    \int &
-    \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right] \\
-    & \times
-    \chi_{n}(\bar{y})
-    \chi_{n'}(\bar{y})
-    d\bar{y}.
-  \end{aligned}
-\end{equation}
-Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
-\begin{subequations} \label{eq:d8}
-  \begin{align}
-    \int
-    \chi_{n}({y})
-    \chi_{n'}({y}) d{y} &=
-    \delta_{n',n}, \\
-    \int
-    y \chi_{n}({y})\chi_{n'}({y}) d{y} &=
-    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-    \delta_{n',n-1} \right),
-  \end{align}
-\end{subequations}
-we simplify the matrix elements of $x$-directional current operator to obtain
-\begin{equation} \label{eq:d9}
-  \begin{aligned}
-    &\left({j}_x \right)_{nm,n'm'} =
-    \frac{eB}{{\widetilde{m}}}
-    \delta_{k_x,k'_x} \\
-    & \qquad\times
-    \left[
-    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-    \delta_{n',n-1}\right)
-    + \zeta(t) \delta_{n',n}
-    \right].
-  \end{aligned}
-\end{equation}
-Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
-\begin{equation} \label{eq:d10}
-  \begin{aligned}
-      \left({j}_x \right)_{nm,n'm'} =&
-      \frac{eB}{\widetilde{m}}
-      \delta_{k_x,k'_x} \\
-      & \times
-      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-      \delta_{n',n-1} \right).
-  \end{aligned}
-\end{equation}
-For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
-\begin{equation} \label{eq:d11}
-  \begin{aligned}
-      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
-      \frac{e^2B}{{m_e}}
-      \delta_{k_x,k'_x}\\
-      & \times
-      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-      \delta_{n',n-1} \right).
-  \end{aligned}
-\end{equation}
-
-Moreover, we can identify the $y$-directional current operator component as
-\begin{equation} \label{eq:d12}
-  \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
-\end{equation}
-Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
-\begin{equation} \label{eq:d13}
-  \left({j}_y \right)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
-\end{equation}
-After following the same steps done for the $x$-directional current operator, we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
-\begin{equation} \label{eq:d14}
-  \begin{aligned}
-    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
-    \frac{ie\hbar}{{m_e}}
-    \delta_{k_x,k'_x} \\
-    & \times
-    \left(
-    \sqrt{\frac{n}{2}} \delta_{n',n-1}
-    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
-    \right).
-  \end{aligned}
-\end{equation}
-%===============================================================================
-\end{appendix}
-
-%===============================================================================
-% Bibliography
-%===============================================================================
-\bibliography{aps_article}
-%===============================================================================
-
-\end{document}
-
-% ****** End of file dressed_quantum_hall.tex ****** %

### 2021-08-22 paper/v3.0/sections/7_conclusions.tex
Re-structure

--- 2021-08-22 paper/v3-release/aps_article.tex
@@
-% ****** Start of file dressed_quantum_hall.tex ****** %
-
-\documentclass[
- reprint,
- amsmath,amssymb,
- aps,
- prb,
-]{revtex4-2}
-
-%===============================================================================
-% Import packages
-%===============================================================================
-% Bold math
-\usepackage{bm}
-% AMS packages
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathtools}
-% Physics package
-\usepackage{physics}
-% SI units package
-\usepackage{siunitx}
-% Hypertext package
-\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
-% Language and font encodings
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage[T1]{fontenc}
-%===============================================================================
-% Bibliography style
-\bibliographystyle{apsrev4-2}
-
-\begin{document}
-
-\preprint{APS/123-QED}
-
-%===============================================================================
-% Title of the manuscript
-%===============================================================================
-\title{A generalized model for the charge transport properties of
-\\dressed quantum Hall systems}
-%===============================================================================
-
-%===============================================================================
-% Authors of the manuscript
-%===============================================================================
-\author{Kosala Herath,}
-\email[]{kosala.herath@monash.edu}
-\author{Malin Premaratne}
-\email[]{malin.premaratne@monash.edu}
-\affiliation{Advanced Computing and Simulation Laboratory (A$\chi$L), Department of Electrical and Computer Systems Engineering, Monash University, Clayton, Victoria 3800, Australia.}
-%===============================================================================
-
-%===============================================================================
-% Add date
-%===============================================================================
-\date{\today}
-%===============================================================================
-
-%===============================================================================
-% Abstract
-%===============================================================================
-\begin{abstract}
-We present a generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high-intensity electromagnetic field.
-The new formulation, which applies to two-dimensional(2D) dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
-We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields.
-To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure.
-Moreover, the Floquet-Fermi golden rule is adopted to explore the impurity scattering effects on charge transport in disordered quantum Hall systems.
-We derive fully analytical expressions to describe longitudinal components in the conductivity tensor in dressed quantum Hall systems.
-Subsequently, we demonstrate that the conductivity characteristics of quantum Hall systems can be manipulated using strong external light.
-Our results align with well-established and experimentally
-verified theoretical descriptions for undressed systems while providing a more generalized analysis of the conductivity characteristics in quantum Hall systems.
-Thus, our model can be applied to accurately interpret the usage of strong external radiation as a tool in nanoscale quantum devices.
-\end{abstract}
-%===============================================================================
-
-%===============================================================================
-% Make title of the manuscript
-%===============================================================================
-\maketitle
-%===============================================================================
-
-%===============================================================================
-% Section 01 : Introduction
-%===============================================================================
-\section{\label{sec_introduction} Introduction}
-
-Manipulating light-matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the last century.
-Quantum optics, which study these interactions, have drawn research attention to the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21,wijesekara21}, sensing \cite{rodrigo15,pirandola18,hapuarachchi2018}, energy harvesting \cite{weeraddana15,yuan16,sun18},
-quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
-The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{chow13,jayasekara16,premaratne17}, and quantum cavity physics \cite{tsang10,liu17,devi20}.
-However, in recent years, one of the foremost aims of examining nanostructures under external radiation was understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.
-
-Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
-Most recent studies on the subject have considered the driving field as a perturbation field \cite{pervishko15,morina15}.
-However, this assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
-Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity.
-At high intensities, the higher-order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
-In these instances, a more accurate treatment needs to be adopted.
-Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}.
-Here the applied high-intensity  electromagnetic field identify as the \textit{dressing field}.
-
-Theoretical analyses on the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
-Furthermore, in Ref.
-\cite{wackerl20} a general expression for conductivity in a dressed system has been derived in a fully closed analytical form.
-In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula.
-This opened the path for exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.
-
-Quantum Hall effect \cite{girvin90} observed in two-dimensional (2D) fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors.
-Transport properties of these systems have recently attracted both theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{allerman95,tieke97,pan05} interest.
-Endo \textit{et al.} \cite{endo09} presented the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system.
-These theoretical calculations  align better with experimental observations compared to previous studies.
-
-In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
-Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
-Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems.
-However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
-In their study, they used the conductivity models from Refs.
-\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
-
-In the present analysis, we introduce a robust mathematical model for a dressed two-dimensional electron gas (2DEG) subject to another nonoscillating magnetic field.
-A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system.
-This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
-In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
-Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref.
-\cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
-Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous 2D nanostructures which can serve as a basis for many useful nanoelectronic devices.
-We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport.
-Moreover, this will inspire advanced  developments in nanoscale quantum devices.
-
-The paper is organized as follows.
-Sec.
-\ref{sec_schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration.
-Sec.
-\ref{sec_floquet_theory} provides the Floquet theory interpretation of these wave functions.
-We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec.
-\ref{sec_inverse_scattering_time}, and use it in Sec.
-\ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
-The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}.
-In Sec. \ref{sec_conclusions}, we summarize our analysis and present our conclusions.
-%===============================================================================
-
-%===============================================================================
-% Section 02 : Schrodinger problem for a dressed quantum Hall system
-%===============================================================================
-\section{\label{sec_schrodinger_problem} Schrodinger Problem for a Dressed Quantum Hall System}
-
-Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space.
-In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{T}$, which is pointed towards the $z$-axis.
-In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface.
-We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field.
-Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field as given in Fig.~\ref{fig:1}.
-\begin{figure}[b]
-\includegraphics[scale=0.9]{figures/fig_1.pdf}
-\caption{\label{fig:1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
-The dressing field is linearly polarized with a $y$-polarized electric field $\vb{E}$.}
-\end{figure}
-Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field, respectively.
-
-Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{T}$.
-Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E\cos(\omega t)]/\omega,0)^{T}$.
-These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}.
-Thus, we can represent our system with a time-dependent Hamiltonian
-\begin{equation} \label{eq:1}
-  \hat{H}_e(t) =
-  \frac{1}{2m_e}
-  \left\{ \hat{\vb{p}} - e\right[ \vb{A}_{s}+\vb{A}_{d}(t) \left] \right\}^2,
-\end{equation}
-where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{T}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{T}$.
-The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv*{\psi}{t} = \hat{H}_e(t)\psi$ were already derived in Refs.
-\cite{husimi53,ditt98,dini16}.
-Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
-\begin{equation} \label{eq:2}
-  \begin{aligned}
-    &\psi_{n,m}(x,y,t)  \\
-      & \quad = \frac{1}{\sqrt{L_x}}
-        \chi_n \bm{\left(} y - y_0 - \zeta(t) \bm{\right)}\\
-      & \qquad \times
-        \exp \bm{\left(}
-        \frac{i}{\hbar}\left\{- \epsilon_n t
-        + p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right.\\
-      & \left.\left. \qquad\qquad +
-        m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
-        \int_0^{t}L(\zeta,\dot{\zeta},t')\,dt' \right\}\bm{\right)},
-  \end{aligned}
-\end{equation}
-where $n \in \mathbb{Z}^+_0$ and $m \in \mathbb{Z}$.
-Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant.
-The center of the cyclotron orbit on the $y$-axis is given by $y_0 = \flatfrac{-p_x}{(eB)}$ with $p_x = \flatfrac{2\pi\hbar m}{L_x}$.
-Moreover, $\chi_n$ are well-known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
-\begin{equation} \label{eq:3}
-  \chi_n(y) =
-  \left( \frac{\kappa}{2^{n}n! \sqrt{\pi}}\right)^{1/2}
-  e^{-\kappa^2 y^2/2}
-  \mathcal{H}_n \qty(\kappa y),
-\end{equation}
-with eigenvalues $\epsilon_n = \hbar \omega_0 [n + (1/2)]$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
-We represent the path shift of the driven classical oscillator $\zeta(t)$ by
-\begin{equation} \label{eq:4}
-  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
-\end{equation}
-and we introduce $\dot{\zeta}(t) = \pdv*{\zeta(t)}{t}$ for the sake of notational ease. We can identify the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ as
-\begin{equation} \label{eq:5}
-  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
-\end{equation}
-For details of the full derivation, refer to Appendix \ref{appendix_a}.
-The exponential phase shifts in Eq.~(\ref{eq:2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system.
-Therefore, we can renormalize the magneto-transport characteristics of 2DEG by a nonoscillating magnetic field along with a dressing field.
-%===============================================================================
-
-%===============================================================================
-% Section 03 : Floquet theory perspective
-%===============================================================================
-\section{\label{sec_floquet_theory} Floquet Theory Perspective}
-
-Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
-For instance, the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space.
-Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
-The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
-In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field.
-Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
-
-First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq:2}).
-By factorizing the wave function into a linearly time-dependent part and a periodic time-dependent part, we present the quasienergies with
-\begin{equation} \label{eq:6}
-  \varepsilon_{n} =
-  \hbar \omega_0 \left(n + \flatfrac{1}{2}\right) - \Delta_{\varepsilon},
-\end{equation}
-which only depends on a single quantum number $n$. Furthermore, we can recognize the Floquet modes as
-\begin{equation} \label{eq:7}
-  \begin{aligned}
-    \phi_{n,m}(x,y,t) =&
-    \frac{1}{\sqrt{L_x}} \chi_{n}\bm{\left(}y - y_0 -\zeta(t)\bm{\right)} \\
-    & \times
-      \exp \bm{\left(}
-      \frac{i}{\hbar}\left\{
-      p_x x + \frac{eE}{\omega}(y - y_0)\cos(\omega t) \right.\right. \\
-    & \left.\left. \qquad\qquad +
-      m_e\dot{\zeta}(t)\left[y - y_0 -\zeta(t)\right] +
-      \xi \right\}\bm{\right)},
-  \end{aligned}
-\end{equation}
-with
-\begin{equation} \label{eq:8}
-  \Delta_{\varepsilon} = \frac{e^2E^2}{4m_e(\omega_0^2 - \omega^2)},
-\end{equation}
-and
-\begin{equation} \label{eq:9}
-  \xi = \frac{e^2E^2 \left(3\omega^2 - \omega_0^2 \right)}
-  {8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
-\end{equation}
-For a detailed derivation, refer to Appendix \ref{appendix_b}.
-It is important to note that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions.
-At resonance $\omega = \omega_0$, the energy levels occupy a continuous spectrum and the quasienergy formalism is no longer valid \cite{popov70}.
-Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.
-
-Performing the Fourier transform over the confined 2D space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
-\begin{equation} \label{eq:10}
-  \begin{aligned}
-    \phi_{n,m}\big(k_x,k_y,t\big)  =&
-    \sqrt{L_x}
-    \widetilde{\chi}_{n} \bm{\left(}k_y - b\cos(\omega t)\bm{\right) }\\
-    & \times
-    \exp \bm{\left(} i\xi -ik_y  \left[d\sin(\omega t) + y_0 \right] \bm{\right)},
-  \end{aligned}
-\end{equation}
-where
-\begin{equation} \label{eq:11}
-  \widetilde{\chi}_{n}(k) =
-  i^n \left(\frac{1}{ 2^{n} n! \sqrt{\pi} \kappa}\right)^{1/2}
-  e^{-\flatfrac{k^2}{(2 \kappa^2)}}
-  \mathcal{H}_{n} \left(\flatfrac{k}{\kappa}\right).
-\end{equation}
-Here we have introduced new parameters
-\begin{equation} \label{eq:12}
-  b =
-  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
-\end{equation}
-and
-\begin{equation} \label{eq:13}
-  d =
- \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
-\end{equation}
-Using Floquet theory, we can re-write the wave functions derived in Eq.~(\ref{eq:2}) as the \textit{Floquet states} in momentum space
-\begin{equation} \label{eq:14}
-  \psi_{n,m}(k_x,k_y,t) =
-  \exp(-\flatfrac{i\varepsilon_{n}t}{\hbar}) \phi_{n,m} (k_x,k_y,t).
-\end{equation}
-%===============================================================================
-
-%===============================================================================
-% Section 04 : Inverse scattering time analysis
-%===============================================================================
-\section{\label{sec_inverse_scattering_time}  Inverse Scattering Time Analysis}
-
-The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
-However, this theory has not been applied for a dressed quantum Hall system in the previous studies.
-In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
-With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
-\begin{widetext}
-\begin{equation} \label{eq:15}
-  \begin{aligned}
-    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
-    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
-    & \times
-    \int_{-\infty}^{\infty}
-    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
-    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
-    \left|
-    \int_{-\infty}^{\infty}
-    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
-    \chi_N \bm{\left(} \frac{\hbar}{eB}
-    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
-    dk_2 \right|^2 d k_1,
-  \end{aligned}
-\end{equation}
-\end{widetext}
-where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
-A more detailed derivation is given in Appendix \ref{appendix_c}.
-We modeled the effect caused by impurities in the considered system as a single perturbation potential.
-Since random impurities in a disordered metal offer a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
-Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
-Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
-
-Next, we analyze the contribution of the inverse scattering time matrix elements on the transport properties of our system.
-Since the disorder in the system can not significantly alter the eigenenergy values of the undressed system \cite{wackerl20}, we can neglect the contribution of all off-diagonal elements in the inverse scattering time matrix.
-Subsequently, we consider only the central diagonal element (${l=l'=0}$) of the inverse scattering time matrix which has the largest contribution to the transport characteristics.
-Along with this assumption, we introduce a new parameter as the scattering-induced broadening of the $N$-th Landau level \cite{dini16,endo09}
-\begin{equation} \label{eq:16}
- \Gamma^{00}_{N}(\varepsilon,k_x) =
- \hbar \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{00}_N.
-\end{equation}
-We can evaluate this as
-\begin{widetext}
-  \begin{equation} \label{eq:17}
-   \begin{aligned}
-     &\Gamma^{00}_{N} (\varepsilon,k_x) =
-     \frac{ \pi \hbar^2 \varrho^2}{e^2B^2}
-     \delta(\varepsilon - \varepsilon_{N})
-     \int_{-\infty}^{\infty}
-     J_0^2 \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
-     \left|
-     \int_{-\infty}^{\infty}
-     \chi_N \left( \frac{\hbar}{eB}k_2 \right)
-     \chi_N \bm{\left(} \frac{\hbar}{eB}
-     \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
-     dk_2 \right|^2 d k_1.
-   \end{aligned}
-  \end{equation}
-In addition, for a scattering scenario taking place within the same Landau level, we are able to present the delta distribution of the energy by the  interpretation \cite{dini16}
-\begin{equation} \label{eq:18}
- \delta(\varepsilon - \varepsilon_{N}) \approx
- \frac{1}{\pi \Gamma^{00}_N (\varepsilon,k_x)}.
-\end{equation}
-Subsequently, we write the central element of inverse scattering time matrix in the more compact form
-\begin{equation} \label{eq:19}
-  \begin{aligned}
-    &\Gamma^{00}_{N}(\varepsilon,k_x) =
-     \varrho
-      \left[
-      \int_{-\infty}^{\infty}
-      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
-      \left|
-      \int_{-\infty}^{\infty}
-      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
-      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
-      dk_2 \right|^2
-      dk_1
-      \right]^{-\frac{1}{2}},
-  \end{aligned}
-\end{equation}
-where $ \lambda_1 = \flatfrac{\hbar b}{(eB)}$ and  $\lambda_2 = \flatfrac{\hbar \kappa}{(eB)}$.
-To analyze the effects of the dressing field on the scattering-induced broadening, we introduce the normalized $N$-th Landau level scattering-induced broadening as
-\begin{equation} \label{eq:20}
-    \Lambda_N(k_x) =
-    \frac{\Gamma^{00}_N (\varepsilon,k_x)}
-    {\Gamma^{00}_{N=0}(\varepsilon,k_x)\big|_{E=0}},
-\end{equation}
-which we can evaluate with
-\begin{equation} \label{eq:21}
-    \Lambda_N (k_x) =
-    \left[
-    \frac
-    {
-      \int_{-\infty}^{\infty}
-      J_0^2 \bm{\left(} \lambda_1 (k_x - k_1) \bm{\right)}
-      \left|
-      \int_{-\infty}^{\infty}
-      \widetilde{\chi}_{N}\left(\lambda_2 k_2 \right)
-      \widetilde{\chi}_{N} \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
-      dk_2 \right|^2
-      dk_1
-    }
-    {
-      \int_{-\infty}^{\infty}
-      \left|
-      \int_{-\infty}^{\infty}
-      \widetilde{\chi}_0 \left(\lambda_2 k_2 \right)
-      \widetilde{\chi}_0 \bm{\left(} \lambda_2 (k_1 - k_2 - k_x) \bm{\right)}
-      dk_2 \right|^2
-      dk_1
-    }
-    \right]^{1/2}.
-\end{equation}
-\end{widetext}
-
-\begin{figure}[t]
-\includegraphics[scale=0.55]{figures/fig_2}
-\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_3}
-\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
-In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\end{figure}
-
-Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig_3} and Fig.~\ref{fig_4}.
-To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
-In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
-In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
-Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
-Here, we observe that the normalized energy broadening value for each Landau level is independent of the $x$-directional momentum $k_x$ value and we are able to manipulate it by the dressing field.
-When the dressing field's intensity increases, the energy broadening is reduced, which leads to changes in the transport properties of the dressed quantum Hall system.
-To analyze these adjustments in detail, we derive an analytical expression for the conductivity of a dressed quantum Hall system in the next section.
-%===============================================================================
-
-%===============================================================================
-% Section 05 : Floquet-Drude Conductivity in a Dressed Quantum Hall System
-%===============================================================================
-\section{\label{sec_floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}
-
-A general theory for the conductivity of a dressed system with disorder was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}.
-This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
-\begin{equation} \label{eq:22}
-  \begin{aligned}
-    \sigma^{xx} = &
-    \frac{-1}{4\pi\hbar A}
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
-    \left(
-    -\pdv*{f}{\varepsilon }\right) \\
-    &  \quad\times
-    \tr
-    \left\{
-    {j}^x_0
-    \left[
-    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    \right]
-    {j}^x_0
-    \left[
-    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    \right]
-    \right\} d\varepsilon,
-  \end{aligned}
-\end{equation}
-where $j^x_0$ is the $x$-directional electric current operator matrix elements' $0$-th Fourier component.
-Here, $\vb{G}^{r}(\varepsilon)$ and $\vb{G}^{a} (\varepsilon)$ are the retarded and advanced white noise disorder averaged Floquet Green function matrices \cite{wackerl20,wackerlthesis20}, respectively.
-These matrices are defined against the Floquet modes of the considering system.
-Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity.
-In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
-\begin{equation} \label{eq:23}
-    \Pi- \flatfrac{\hbar \omega}{2}
-    \leq \varepsilon_N
-    <
-    \Pi + \flatfrac{\hbar \omega}{2}.
-\end{equation}
-Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr\{\cdot\}$ is the trace of the considering operator.
-
-Next, we restrict our analysis into the off-resonant regime $\omega\tau_0 \gg 1$), where $\tau_0$ is the scattering time of the undriven system.
-Thus, we can expand the $x$-directional longitudinal conductivity given in
-Eq.~(\ref{eq:22}) using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} = \ket{n,k_x}$ as
-\begin{widetext}
-\begin{equation} \label{eq:24}
-  \begin{aligned}
-    \sigma^{xx} =
-    \frac{-1}{4\pi\hbar A}
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
-    \left(
-      -\frac{\partial f}{\partial \varepsilon}
-    \right)
-    \frac{1}{V_{k_x}} \sum_{k_x}
-    \sum_{n}
-    \mel{n,k_x}
-    {
-      {j}^x_0
-      \left[
-        \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-      \right]
-      {j}^x_0
-      \left[
-        \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-      \right]
-    }
-    {n,k_x}
-    d\varepsilon,
-  \end{aligned}
-\end{equation}
-where $V_{k_x}$ is the volume of considering $x$-directional momentum space. Next, we evaluate the above expression as follows
-\begin{equation} \label{eq:25}
-  \begin{aligned}
-    \sigma^{xx}  = &
-    \frac{-1}{4\pi\hbar A}
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
-    \left(
-      -\frac{\partial f}{\partial \varepsilon}
-    \right)
-    \frac{1}{V_{k_x}^4}
-    \sum_{k_x} \sum_{n}
-    \sum_{{k_x}_1,{k_x}_2,{k_x}_3}
-    \sum_{n_1,n_2,n_3} \\
-    & \quad\times \mel{n,k_x}{
-    {j}^x_0}
-    {n_1,{k_x}_1}
-    \mel{{n_1,{k_x}_1}}{
-    \left[
-      \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    \right]
-    }
-    {n_2,{k_x}_2}
-    \mel{n_2,{k_x}_2}{
-    {j}^x_0}
-    {n_3,{k_x}_3}
-    \mel{n_3,{k_x}_3}{
-    \left[
-      \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    \right]
-    }
-    {n,k_x} d\varepsilon.
-  \end{aligned}
-\end{equation}
-We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  = \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}.
-Thus, we evaluate the matrix elements of the difference between retarded and advanced Green's functions as
-\begin{equation} \label{eq:26}
-  \mel{{n_1,{k_x}_1}}
-  {
-    \vb{T}^{\dagger}
-    \left[
-    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-    \right]\vb{T}
-  }
-  {n_2,{k_x}_2} =
-  \frac
-  {
-    2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
-    \delta_{n_1,n_2}\delta_{{k_x}_1,{k_x}_2}
-  }
-  {
-    \left(
-    \flatfrac{\varepsilon}{\hbar} -
-    \flatfrac{\varepsilon_{n_1}}{\hbar}
-    \right)^2
-    + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
-  },
-\end{equation}
-and
-\begin{equation} \label{eq:27}
-  \mel{{n_3,{k_x}_3}}{
-  \vb{T}^{\dagger}
-  \left[
-  \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
-  \right]\vb{T}}
-  {n,{k_x}} =
-  \frac{
-    2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
-    \delta_{n_3,n}\delta_{{k_x}_3,{k_x}}
-  }
-  {
-    \left(
-    \flatfrac{\varepsilon }{\hbar}-
-    \flatfrac{\varepsilon_{n}}{\hbar}
-    \right)^2
-    + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
-  }.
-\end{equation}
-Here we introduced the retarded self-energy matrix $\vb{\Sigma}^r$ which is the sum of all irreducible diagrams \cite{wackerl20,wackerlthesis20}.
-Applying the matrix elements of the electric current operator in Landau levels and
-expressions from Eq.~(\ref{eq:26}) and Eq.~(\ref{eq:27}) back into Eq.~(\ref{eq:25}) we obtain
-\begin{equation} \label{eq:28}
-  \begin{aligned}
-    \sigma^{xx}  =
-    \frac{-1}{4\pi\hbar A}
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}&
-    \left(
-    -\frac{\partial f}{\partial \varepsilon}
-    \right)
-    \frac{1}{V_{k_x}}
-    \sum_{k_x} \sum_{n} \sum_{n_1,n_2}
-    \\
-    & \times
-    \frac{e^2B}{{m_e}}
-    \left(
-    \sqrt{\frac{n+1}{2}} \delta_{n_1,n+1} + \sqrt{\frac{n}{2}}\delta_{n_1,n-1}
-    \right)
-    \left\{
-    \frac
-    {
-      2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
-      \delta_{n_1,n_2}
-    }
-    {
-      \left(
-      \flatfrac{\varepsilon}{\hbar} -
-      \flatfrac{\varepsilon_{n_1}}{\hbar}
-      \right)^2
-      + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
-    }
-    \right\} \\
-    & \times
-    \frac{e^2B}{{m_e}}
-    \left(
-    \sqrt{\frac{n_2+1}{2}} \delta_{n,n_2+1} + \sqrt{\frac{n_2}{2}}
-    \delta_{n,n_2-1}
-    \right)
-    \left\{
-    \frac{
-      2i \Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})
-    }
-    {
-      \left(
-      \flatfrac{\varepsilon }{\hbar}-
-      \flatfrac{\varepsilon_{n}}{\hbar}
-      \right)^2
-      + \left[\Im(\vb{T}^{\dagger} \vb{\Sigma}^r \vb{T})\right]^2
-    }
-    \right\}  d\varepsilon,
-  \end{aligned}
-\end{equation}
-For the full derivation of electric current operators in a quantum Hall system, refer to Appendix \ref{appendix_d}.
-After the expansion, we can identify the the only non-zero term as follows
-\begin{equation} \label{eq:29}
-  \begin{aligned}
-    \sigma^{xx} =
-    \frac{-1}{4\pi\hbar A}
-    \frac{e^4B^2}{{{m_e}^2}} &
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
-    \left(
-    -\frac{\partial f}{\partial \varepsilon}\right)
-    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n}
-    (n+1)
-    \\
-    & \times
-    \left\{
-    \frac
-    {
-      2i \Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_{n+1},k_x) \vb{T}\bm{)}
-    }
-    {
-      \left(
-      \flatfrac{\varepsilon}{\hbar} -
-      \flatfrac{\varepsilon_{n+1}}{\hbar}
-      \right)^2
-      + \left[\Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_{n+1},k_x) \vb{T}\bm{)}\right]^2
-    }
-    \right\}
-    \left\{
-    \frac{
-      2i \Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_n,k_x) \vb{T}\bm{)}
-    }
-    {
-      \left(
-      \flatfrac{\varepsilon }{\hbar}-
-      \flatfrac{\varepsilon_{n}}{\hbar}
-      \right)^2
-      + \left[\Im\bm{(}\vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon_n,k_x) \vb{T}\bm{)}\right]^2
-    }
-    \right\}
-    d\varepsilon.
-  \end{aligned}
-\end{equation}
-The inverse scattering time matrix is equal to the diagonalized contrast of the retarded and advanced self-energy \cite{wackerl20,wackerlthesis20}.
-In addition, on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20}.
-Subsequently, we can identify the following property
-\begin{equation} \label{eq:30}
-  \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll} =
-  -2\text{Im} \left[ \vb{T}^{\dagger} \vb{\Sigma}^r(\varepsilon,k_x) \vb{T}\right]^{ll}.
-\end{equation}
-Afterwards, considering only the central element ($l=0$) of the inverse scattering time matrix, we can restructure the derived conductivity expression in Eq.~(\ref{eq:29}) as follows
-\begin{equation} \label{eq:31}
-    \sigma^{xx}   =
-    \frac{1}{\pi\hbar A}
-    \frac{e^4B^2}{{{m_e}^2}}
-    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2}
-    \left(
-      -\frac{\partial f}{\partial \varepsilon}
-    \right)
-    \frac{1}{V_{k_x}} \sum_{k_x} \sum_{n} (n+1)
-    \left[
-    \frac{\widetilde{{\Gamma}}(\varepsilon_{n+1})
-    }
-    {
-    \left(
-    \varepsilon_F - \varepsilon_{n+1}
-    \right)^2
-    + \widetilde{{\Gamma}}^2(\varepsilon_{n+1})
-    }
-    \right]
-    \left[
-    \frac{\widetilde{{\Gamma}}(\varepsilon_{n})
-    }
-    {
-    \left(
-    \varepsilon_F - \varepsilon_{n}
-    \right)^2
-    + \widetilde{{\Gamma}}^2(\varepsilon_{n})
-    }
-    \right]
-    d\varepsilon,
-\end{equation}
-\end{widetext}
-with $\widetilde{{\Gamma}}(\varepsilon_n,k_x) = \left[\flatfrac{\hbar}{2\tau(\varepsilon_n,k_x)}\right]^{00}$.
-Since we already identified that the inverse scattering time matrix's central element is independent of $k_x$ value, we can drop the $k_x$-dependent in the $\widetilde{{\Gamma}}(\varepsilon_n,k_x)$ terms.
-Subsequently, we can get the sum over available momentum in $x$-direction.
-However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considered system, we can identify that
-\begin{equation} \label{eq:32}
- -\flatfrac{m_e\omega_0 Ly}{(2\hbar)} \leq k_x \leq \flatfrac{m_e\omega_0 Ly}{(2\hbar)}.
-\end{equation}
-We use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
-\begin{equation} \label{eq:33}
-  f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
-\end{equation}
-where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Considering the above distribution for extremely low-temperature conditions, we can use the following approximation
-\begin{equation} \label{eq:34}
-  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
-\end{equation}
-Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
-\begin{equation} \label{eq:35}
-  \begin{aligned}
-    \sigma^{xx}  =
-    \frac{e^2}{\pi\hbar A}
-    \sum_{n} &
-    \frac{(n+1)}{\gamma_{n}\gamma_{n+1}} \\
-    &\times
-    \left[
-      \frac{1}
-      {
-        1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
-      }
-    \right]
-    \left[
-      \frac{1}
-      {
-        1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
-      }
-    \right],
-  \end{aligned}
-\end{equation}
-where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$
-and
-$\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$.
-Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
-\begin{equation} \label{eq:36}
-  \begin{aligned}
-    {\sigma}^{yy} =
-    \frac{e^2}{\pi\hbar A} &
-    \frac{1}{e^2B^2}
-    \sum_{n}
-    \frac{(n+1)}{\gamma_{n}\gamma_{n+1}} \\
-    & \times
-    \left[
-      \frac{1}
-      {
-        1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
-      }
-    \right]
-    \left[
-      \frac{1}
-      {
-        1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
-      }
-    \right].
-  \end{aligned}
-\end{equation}
-%===============================================================================
-
-%===============================================================================
-% Section 06 : Manipulate Conductivity in Quantum Hall Systems
-%===============================================================================
-\section{\label{sec_manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}
-
-To identify the longitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
-We can identify the normalized $x$-directional longitudinal conductivity of dressed quantum Hall system by
-\begin{equation}\label{eq:37}
-  \widetilde{\sigma}^{xx}(X_F,I) =
-  \flatfrac{\sigma^{xx}}{\sigma_{0}},
-\end{equation}
-with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and we can express this as
-\begin{equation} \label{eq:38}
-  \begin{aligned}
-    \widetilde{\sigma}^{xx}(X_F,I) &=
-    \sum_{n}
-    \frac{(n+1)}{\varsigma^2 \Lambda_n \Lambda_{n+1}} \\
-    &\quad\times
-    \left[
-      \frac{1}
-      {
-        1 + \left(\frac{X_F - n -1}{\varsigma \Lambda_n}\right)^2
-      }
-    \right]
-    \left[
-      \frac{1}
-      {
-        1 + \left(\frac{X_F - n}{\varsigma \Lambda_{n+1}}\right)^2
-      }
-    \right],
-  \end{aligned}
-\end{equation}
-where $\varsigma = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.
-
-As illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6}, we can manipulate the normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
-For a given dressing field intensity, the longitudinal conductivity varies with  the Fermi level of the system showing sharp peaks at each Landau energy level.
-In quantum Hall systems, electrons are restricted to bear only the Landau energies.
-Thus, the conductivity reduces significantly when the Fermi level is not aligned with any of the Landau levels.
-In contrast, near each Landau level, the conductivity achieves excessive values compared to other areas.
-Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.
-
-On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.
-When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:6}.
-However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
-This demonstrates our ability to tune the width of the conductivity regions in these quantum Hall systems with the help of a dressing field.
-
-These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
-As the authors remarked in that publication, since the Fermi level of the system can be changed with the applied gate voltage of the material, this can be utilized as a 2D switch for nanoscale optoelectronics applications.
-Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
-However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
-This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
-The semi-elliptical conductivity regions are  illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed data for Landau levels \cite{endo09}.
-In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the results depicted in Ref.
-\cite{endo09}.
-The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimentally observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
-However, they have not considered the tunability that can be achieved with a dressing field.
-In this analysis, we account for both the magnetic and dressing field effects that can affect the transport properties of 2DEG, leading to a more generalized theory.
-Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_4}
-\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:5}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_5}
-\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:6}
-\end{figure}
-%===============================================================================
-
-%===============================================================================
-% Section 07 : Conclusions
-%===============================================================================
-\section{\label{sec_conclusions} Conclusions}
-
 In this paper, we introduced a generalized mathematical model for predicting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high-intensity light.
@@
 As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D optoelectronic nanotransistors, enhancing their performance and inventing novel appliances.
-%===============================================================================
-
-%===============================================================================
-% Acknowledgments
-%===============================================================================
-\begin{acknowledgments}
-K.H wish to acknowledge the members of A$\chi$L at Monash University for their encouragement and support and specially T.N.
-Perera and R.T.Wijesekara for insightful discussions.
-The work of K.H is supported by the Australian Government Research Training Program (RTP) Scholarship and the Monash University Institute of Graduate Research.
-\end{acknowledgments}
-%===============================================================================
-
-%===============================================================================
-% Add appendixes
-%===============================================================================
-\begin{appendix}
-
-%===============================================================================
-% Appendix A : Wave function solutions for a dressed quantum Hall system
-%===============================================================================
-\section{\label{appendix_a} Wave function solutions for a dressed quantum Hall system}
-
-The derivation of the solutions for the time-dependent Schrödinger equation with our system's Hamiltonian (Eq.
-\ref{eq:1}) is quite similar to that followed in Refs.
-\cite{husimi53,dini16}.
-We start with expanding the Hamiltonian for two-dimensional scenario
-\begin{equation} \label{eq:a1}
-  \hat{H}_e(t) = \frac{1}{2m_e}
-  \left\{
-    \left(\hat{p}_x + eBy \right)^2 +
-    \left[
-      \hat{p}_y - \frac{eE}{\omega}\cos(\omega t)
-    \right]^2
-  \right\}.
-\end{equation}
-Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
-${L_x}^{-1/2}\exp(\flatfrac{ip_x x}{\hbar})$ where $p_x = \flatfrac{2\pi \hbar m}{L_x}$ with $ m \in \mathbb{Z}$.
-Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
-\begin{equation} \label{eq:a2}
-    \hat{H}_e(t) = \frac{1}{2m_e}
-    \left\{
-      \left({p}_x + eBy \right)^2 +
-      \left[
-        i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)
-      \right]^2
-    \right\}.
-\end{equation}
-Subsequently, we define the \textit{center of the cyclotron orbit} on the $y$-axis as $y_0 = \flatfrac{-p_x}{(eB)}$, and the \textit{cyclotron frequency} as  $\omega_0 = {eB}/{m_e}$.
-This leads to a new arrangement of the Hamiltonian
-\begin{equation} \label{eq:a3}
-  \begin{aligned}
-    \hat{H}_e(t) =
-      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
-      \frac{1}{2m_e} &
-      \left[
-        -\hbar^2 \pdv[2]{\tilde{y}}  +
-        \frac{2i\hbar eE}{\omega} \cos(\omega t) \pdv{\tilde{y}}
-        \right.\\
-        & \left. \qquad\qquad\quad +
-        \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
-        \right],
-  \end{aligned}
-\end{equation}
-where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
-\begin{equation} \label{eq:a4}
-    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
-\end{equation}
-can be presented by the following form
-\begin{equation} \label{eq:a5}
-    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}}
-    \exp\left(
-      \frac{ip_x x}{\hbar} +
-      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
-    \right) \vartheta(\tilde{y},t),
-\end{equation}
-where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
-\begin{equation} \label{eq:a6}
-    \left[
-    \frac{m_e \omega_0^2}{2} \tilde{y}^2
-    - {eE\tilde{y}}\sin(\omega t)
-    - \frac{\hbar^2}{2m_e} \pdv[2]{\tilde{y}}
-    - i \hbar \dv{t}
-    \right]
-    \vartheta(\tilde{y},t) = 0.
-\end{equation}
-If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
-\begin{equation} \label{eq:a7}
-     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
-    \left(
-    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
-    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
-    \right)
-    \vartheta(\tilde{y},t).
-\end{equation}
-Thus, we can identify $S(t) = eE\sin(\omega t)$ term as an external force that act on the harmonic oscillator, and we can solve Eq.~(\ref{eq:a6}) as a forced harmonic oscillator on $\tilde{y}$ axis
-\begin{equation} \label{eq:a8}
-  \begin{aligned}
-    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
-    \bigg[
-    -
-    \frac{\hbar^2}{2m_e}
-    \pdv[2]{\tilde{y}} +
-    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
-    - \tilde{y}S(t)]
-    \bigg]
-    \vartheta(\tilde{y},t).
-  \end{aligned}
-\end{equation}
-This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}.
-We introduce a time-dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
-\begin{equation} \label{eq:a9}
-    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
-\end{equation}
-and this leads to
-\begin{equation} \label{eq:a10}
-  \begin{aligned}
-    i \hbar \pdv{\varphi(y',t)}{t}   &=
-    \left\{
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 y'^2
-        \right. \\
-        & \left. \qquad
-        - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
-        \right. \\
-        & \left. \qquad +
-        \left[
-            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
-        \right]y'
-    \right\} \varphi(y',t).
-  \end{aligned}
-\end{equation}
-Here, we introduced $\dot{\zeta} = \pdv*{\zeta}{t}$ and $\ddot{\zeta} = \pdv*[2]{\zeta}{t}$ for the sake of notational convenience. Subsequently, we can restrict $\zeta(t)$ function such that
-\begin{equation} \label{eq:a11}
-  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
-\end{equation}
-and that simply our previous expression as
-\begin{equation} \label{eq:a12}
-  \begin{aligned}
-    i \hbar \pdv{\varphi(y',t)}{t} =&
-    \left[
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \right. \\
-        & \left. \qquad\qquad\qquad
-        - L(\zeta,\dot{\zeta},t)
-    \right]\varphi(y',t).
-  \end{aligned}
-\end{equation}
-Here
-\begin{equation} \label{eq:a13}
-  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
-\end{equation}
-is the Lagrangian of a classical driven oscillator. To proceed further, we introduce another unitary transform as follows
-\begin{equation} \label{eq:a14}
-    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t} L(\zeta,\dot{\zeta},t')dt') \chi(y',t),
-\end{equation}
-and subtitling Eq.~(\ref{eq:a14}) back in Eq.~(\ref{eq:a12}), we can obtain
-\begin{equation} \label{eq:a15}
-    i \hbar \pdv{t} \chi(y',t)  =
-    \left(
-        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
-        + \frac{1}{2} m_e \omega_0^2 {y'}^2
-    \right) \chi(y',t).
-\end{equation}
-This is the well-known Schrödinger equation of the quantum harmonic oscillator.
-This allows us to identify the well known eigenfunction solutions \cite{griffiths18,shankar94}
-\begin{equation} \label{eq:a16}
-  \chi_n(y) =
-  \sqrt{\frac{\kappa}{2^{n}n!\sqrt{\pi}}}
-  e^{-\kappa^2 y^2/2}
-  \mathcal{H}_n \qty(\kappa y),
-\end{equation}
-with eigenvalues
-\begin{equation} \label{eq:a17}
-  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
-  ~\text{for}~
-  n \in \mathbb{Z}^{+}_0.
-\end{equation}
-Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
-Thus, we can identify the solutions for Eq.~(\ref{eq:a8}) as
-\begin{equation} \label{eq:a18}
-  \begin{aligned}
-    \vartheta_n(\tilde{y},t) = \chi_n\bm{(}\tilde{y} - \zeta(t)\bm{)}
-     \text{exp}&
-     \left(
-     \frac{i}{\hbar}
-     \left\{
-     - \epsilon_nt +
-     m_e \left[\tilde{y}-\zeta(t)\right] \dot{\zeta(t)} \right. \right. \\
-     & \left. \left. \qquad
-     + \int_0^{t}L(\zeta,\dot{\zeta},t') dt'
-     \right\}
-     \right).
-  \end{aligned}
-\end{equation}
-Since $\chi_n(x)$ functions forms a complete set, we can present any general solution for  $\vartheta_(\tilde{y},t)$ using the solutions derived in Eq.~(\ref{eq:a18}).
-
-Finally, we consider our scenario where we can assume that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq:a11}) as
-\begin{equation} \label{eq:a19}
-  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
-\end{equation}
-Substituting solutions given in Eq.~(\ref{eq:a18}) back in Eq.~(\ref{eq:a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq:a4}) as follows
-\begin{equation} \label{eq:a20}
-  \begin{aligned}
-    &\psi_{n,m}(x,y,t) \\
-    & \quad=  \frac{1}{\sqrt{L_x}}
-    \chi_n\left(y - y_0 - \zeta(t)\right)\\
-    &\qquad\times
-    \text{exp}\left(
-    \frac{i}{\hbar}
-    \left\{- \epsilon_nt
-    + p_x x
-    + \frac{eE(y - y_0)}{\omega}\cos(\omega t) \right. \right. \\
-    & \left. \left. \qquad\qquad +
-    m_e\left[y - y_0 -\zeta(t)\right] \dot{\zeta}(t)+
-    \int_0^{t}L(\zeta,\dot{\zeta},t') dt'
-    \right\}
-    \right).
-  \end{aligned}
-\end{equation}
-%===============================================================================
-
-%===============================================================================
-% Appendix B :
-%===============================================================================
-\section{\label{appendix_b} Floquet modes and quasienergies}
-
-\subsection{Position space representation}
-
-First we define the time integral of the Lagrangian of the classical oscillator given in Eq.~(\ref{eq:5}), over a period $T=2\pi/\omega$ as
-\begin{equation} \label{eq:b1}
-  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T L(\zeta,\dot{\zeta},t') dt'.
-\end{equation}
-Additionally, performing this integral, we can obtain a more simplified result
-\begin{equation} \label{eq:b2}
-  \Delta_{\varepsilon} = \frac{e^2E^2}{4m_e(\omega_0^2 - \omega^2)}.
-\end{equation}
-Next, we define another parameter
-\begin{equation} \label{eq:b3}
-  \xi =
-  \int_0^t \; L(\zeta,\dot{\zeta},t') dt' -
-  \Delta_{\varepsilon} t,
-\end{equation}
-and after simplifying, we can identify
-\begin{equation} \label{eq:b4}
-  \xi =
-  \frac{e^2E^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t),
-\end{equation}
-which is a periodic function in time. Using these parameters, we can factorize the wave function given in Eq.~(\ref{eq:2}) as linearly time-dependent part and periodic time-dependent part as follows
-\begin{equation} \label{eq:b5}
-  \begin{aligned}
-    \psi_{\alpha}&(x,y,t) \\
-    & =
-    \exp(\frac{i}{\hbar} \left(-\epsilon_nt + \Delta_{\varepsilon} t \right) )
-    \frac{1}{\sqrt{L_x}} \chi_n\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
-    \\
-    & \quad\times
-    \exp \left(
-       \frac{i}{\hbar}
-       \left\{
-       p_x x +
-       \frac{eE(y-y_0)}{\omega}\cos(\omega t)  \right. \right. \\
-    & \left. \left. \qquad\qquad\qquad\qquad
-    + m_e\dot{\zeta}(t) \left[ y-y_0 -\zeta(t) \right]
-    + \xi \right\}
-     \right).
-  \end{aligned}
-\end{equation}
-This leads to separate the linear time-dependent phase component as the quasienergies
-\begin{equation} \label{eq:b6}
-  \varepsilon_{n} =
-  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
-\end{equation}
-while rest of the components as time-periodic Floquet modes
-\begin{equation} \label{eq:b7}
-  \begin{aligned}
-    \phi_{n,m}(x,y,t) =  &
-    \frac{1}{\sqrt{L_x}} \chi_n\bm{\left(}y - y_0 - \zeta(t)\bm{\right)} \\
-    & \times
-    \exp \left(
-       \frac{i}{\hbar}
-       \left\{
-       p_x x +
-       \frac{eE(y-y_0)}{\omega}\cos(\omega t)  \right. \right. \\
-    & \left. \left. \qquad\qquad\quad
-    + m_e\dot{\zeta}(t) \left[ y-y_0 -\zeta(t) \right]
-    + \xi \right\}
-     \right).
-  \end{aligned}
-\end{equation}
-
-\subsection{Momentum space representation}
-
-We perform continuous Fourier transform over the considering confined space $A=L_xL_y$ on the Floquet modes given in Eq.~(\ref{eq:7}) to realize the Floquet modes in momentum space
-\begin{equation} \label{eq:b8}
-  \begin{aligned}
-    \phi_{n,m}&(k_x,k_y,t) \\
-    & =
-    \exp(\frac{-i\gamma(t)}{\hbar}y_0)
-    \exp(\frac{-i}{\hbar}\left[m_e \dot{\zeta}(t) \zeta(t) - \xi \right]) \\
-    & \quad\times
-    \int_{-L_y/2}^{L_y/2} \exp(-i \left[k_y - \gamma(t) \right]y)
-      \chi_n \bm{\left(}y - \mu(t)\bm{\right)} dy \\
-    & \quad\times
-    \frac{1}{\sqrt{L_x}} \int_{-L_x/2}^{L_x/2}
-     \exp(-ik_x x)\exp( \flatfrac{i p_x }{\hbar}x ) dx.
-  \end{aligned}
-\end{equation}
-Here we used new two parameters
-\begin{equation} \label{eq:b9}
-  \mu(t) = \frac{eE\sin(\omega t)}{m_e(\omega_0^2 - \omega^2)} + y_0,
-\end{equation}
-and
-\begin{equation} \label{eq:b10}
-  \gamma(t) =
-  \frac{eE\omega_0^2\cos(\omega t)}{\hbar\omega(\omega_0^2 - \omega^2)}.
-\end{equation}
-Subsequently, using the Fourier transform identity \cite{bruus04}
-\begin{equation} \label{eq:b11}
-  \int_{-L_x/2}^{L_x/2}
-  \exp( -ik_x x + \flatfrac{i p_x x}{\hbar}) dx =
-  L_x \delta_{k_x,\flatfrac{p_x}{\hbar}},
-\end{equation}
-we can derive
-\begin{equation} \label{eq:b12}
-  \begin{aligned}
-    \phi_{n,m}(k_x,k_y,t)  =
-    \Phi_{n,m}&(k_y,t)
-    \delta_{k_x,\flatfrac{p_x}{\hbar}}
-    \exp(\frac{-i}{\hbar} \gamma(t)y_0) \\
-    & \times
-    \exp(\frac{-i}{\hbar}
-    \left[ m_e \dot{\zeta}(t) \zeta(t) - \xi \right]),
-  \end{aligned}
-\end{equation}
-where we can define $\Phi_{n,m}(k_y,t)$ as
-\begin{equation} \label{eq:b13}
-  \begin{aligned}
-    &\Phi_{n,m}(k_y,t) \\
-    & \quad=
-    \sqrt{L_x}
-    \int_{-L_y/2}^{L_y/2}
-    \chi_n \bm{\left(}y - \mu(t)\bm{\right)}
-    \exp \bm{\left(}-i\left[k_y - \gamma(t) \right]y\bm{\right)} dy.
-  \end{aligned}
-\end{equation}
-Substituting ${k'_y} = k_y -\gamma(t)$ with $y' = y -\mu(t)$, and assuming that the size of the considered 2DEG sample in $y$-direction is considerably large ($L_y \rightarrow \infty$), we can obtain
-\begin{equation} \label{eq:b14}
-  \Phi_{n,m}({k'_y} ,t) =
-  {\sqrt{L_x}} e^{-i {k'_y}\mu}
-  \int_{-\infty}^{\infty} \chi_{n}(y') \exp(-i{k'_y} y') dy'.
-\end{equation}
-Moreover, we can identify that the above integral represents the Fourier transform of $\chi_n$ functions.
-In addition, using the symmetric conditions of the Fourier transform for Gauss-Hermite functions $\theta_n(x)$ \cite{celeghini21}
-\begin{equation} \label{eq:b15}
-  \mathcal{FT}[\theta_n(\kappa x),x,k] = \frac{i^n}{|\kappa|}\theta_n(k/\kappa),
-\end{equation}
-we can simply the Eq.~(\ref{eq:b14}) as
-\begin{equation} \label{eq:b16}
-  \Phi_{n,m}({k'_y} ,t) =
-  \sqrt{L_x} e^{-i {k'_y}\mu} \widetilde{\chi}_n(k'_y),
-\end{equation}
-with
-\begin{equation} \label{eq:b17}
-  \widetilde{\chi}_{n}(k) =
-  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
-  \left(\frac{1}{\kappa} \right)^{1/2}
-  e^{-\flatfrac{k^2}{(2 \kappa^2)}}
-  \mathcal{H}_n (\flatfrac{k}{\kappa}).
-\end{equation}
-Finally, substitute Eq.~(\ref{eq:b16}) back into Eq.~(\ref{eq:b12}) and this leads to
-\begin{equation} \label{eq:b18}
-  \begin{aligned}
-    \phi_{n,m}(k_x,k_y,t)  = &
-    {\sqrt{L_x}} \widetilde{\chi}_n \bm{\left(} k_y - b\cos(\omega t)\bm{\right)} \\
-    & \times
-    \exp \left(
-      i\xi -ik_y  \left[d\sin(\omega t) + \frac{\hbar k_x}{eB} \right]
-    \right),
-  \end{aligned}
-\end{equation}
-where
-\begin{equation} \label{eq:b19}
-  b =
-  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
-\end{equation}
-and
-\begin{equation} \label{eq:b20}
-  d =
- \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
-\end{equation}
-It is necessary to notice that $k_x$ is quantized with $k_x = \flatfrac{2\pi m}{L_x} ~,~ m \in \mathbb{Z}$.
-%===============================================================================
-
-%===============================================================================
-% Appendix C :
-%===============================================================================
-\section{\label{appendix_c} Floquet-Fermi golden rule for a dressed quantum  Hall system}
-
-We derive the Floquet-Fermi golden rule for our dressed quantum Hall system with the help of the $t$-$t'$ formalism. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
-\begin{equation} \label{eq:c1}
-  \ket{\psi_{n,m}(t,t')} =
-  \exp(-\frac{i}{\hbar}\varepsilon_{n} t)\ket{\phi_{n,m}(t')},
-\end{equation}
-are derived by separating the aperiodic and periodic components of the Floquet states given in Eq.~(\ref{eq:14}).
-Additionally, these states fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
-\begin{equation} \label{eq:c2}
-  i \hbar \pdv{t}\ket{\psi_{n,m}(t,t')} =
-  H_F(t') \ket{\psi_{n,m}(t,t')},
-\end{equation}
-where the \textit{Floquet Hamiltonian} defined as
-\begin{equation} \label{eq:c3}
-  H_F(t') =
-  H_e(t') - i\hbar \pdv{t'}.
-\end{equation}
-Next, we can identify the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation as
-\begin{equation} \label{eq:c4}
-  U_F(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\left[t-t_0 \right]).
-\end{equation}
-The advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time ordering operators \cite{wackerl20}.
-
-We model the effect caused by impurities in the considered system as a single perturbation potential formed by a group of randomly distributed impurities.
-Thus, we introduce a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, and the $t$-$t'$-Schrödinger equation becomes
-\begin{equation} \label{eq:c5}
-  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')} =
-  \left[H_F(t') + V(\vb{r}) \right]\ket{\Psi_{n,m}(t,t')}.
-\end{equation}
-This introduces a new wave function solution $\ket{\Psi_{n,m}}$ for a system with a given perturbation. If $t\leq t_0$, both of the solutions for Eq.~(\ref{eq:c2}) and Eq.~(\ref{eq:c5}) coincide
-\begin{equation} \label{eq:c6}
-  \ket{\psi_{n,m}(t,t')} =\ket{\Psi_{n,m}(t,t')} \quad
-  \text{when} \quad
-  t \leq t_0.
-\end{equation}
-Next, we move our analysis into the interaction picture representation \cite{bruus04,mahan00} and in the interaction picture, we can identify the $t$-$t'$-Floquet state as
-\begin{equation} \label{eq:c7}
-  \ket{\Psi_{n,m}(t,t')}_I = U_0^{\dagger}(t,t_0;t')
-  \ket{\Psi_{n,m}(t,t')}.
-\end{equation}
-Due to time-independence, the perturbation in the interaction picture has the same form as the Schrödinger picture representation
-\begin{equation} \label{eq:c8}
-  V_I(\vb{r}) = U_0^{\dagger}(t,t_0;t')V(\vb{r})U_0(t,t_0;t') =
-  V(\vb{r}).
-\end{equation}
-This leads us to the $t$-$t'$-Schrödinger equation in the interaction picture representation
-\begin{equation} \label{eq:c9}
-  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')}_I =
-  V_I(\vb{r})\ket{\Psi_{n,m}(t,t')}_I,
-\end{equation}
-with the recursive solutions \cite{bruus04,mahan00}
-\begin{equation} \label{eq:c10}
-  \begin{aligned}
-  \ket{\Psi_{n,m}(t,t')}_I = &\ket{\Psi_{n,m}(t_0,t')}_I \\
-  &+
-  \frac{1}{i\hbar}
-  \int_{t_0}^t
-  V_I(\vb{r}) \ket{\Psi_{n,m}(t_1,t')}_I dt_1.
-  \end{aligned}
-\end{equation}
-Iterating the solution only up to the first order (Born approximation) we obtain
-\begin{equation} \label{eq:c11}
-  \begin{aligned}
-    \ket{\Psi_{n,m}(t,t')}_I \approx &\ket{\psi_{n,m}(t_0,t')} \\
-    &+
-    \frac{1}{i\hbar}
-    \int_{t_0}^t
-    V_I(\vb{r}) \ket{\psi_{n,m}(t_0,t')} dt_1.
-  \end{aligned}
-\end{equation}
-
-Since our $t$-$t'$-Floquet states create a basis, we can represent the solutions for the $t$-$t'$-Schrödinger equation given in Eq.~(\ref{eq:c5}) using our known $t$-$t'$-Floquet states as follows
-\begin{equation} \label{eq:c12}
-  \ket{\Psi_{\alpha}(t,t')} = \sum_{\beta} a_{\alpha,\beta}(t,t')
-  \ket{\psi_{\beta}(t,t')}.
-\end{equation}
-Here, we used a single term notation to represent two quantum numbers; $\alpha \equiv (n_{\alpha},m_{\alpha})$ and $\beta \equiv (n_{\beta},m_{\beta})$.
-Subsequently, we can identify the \textit{scattering amplitude} as $a_{\alpha,\beta}(t,t') =
-\braket{\psi_{\beta}(t,t')}{\Psi_{\alpha}(t,t')}$ and we can evaluate this with
-\begin{equation} \label{eq:c13}
-  \begin{aligned}
-  a_{\alpha,\beta}(t,t') = &
-  \braket{\psi_{\beta}(t,t')}{\psi_{\alpha}(t,t')} \\
-  &+
-  \frac{1}{i\hbar}
-  \int_{t_0}^t
-  \bra{\psi_{\beta}(t_1,t')}
-  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
-  \end{aligned}
-\end{equation}
-Since the $t$-$t'$-Floquet states are orthonormal and assuming $t_0 = 0$ and $\alpha \neq \beta$ this leads to
-\begin{equation} \label{eq:c14}
-  a_{\alpha,\beta}(t,t') =
-  -
-  \frac{i}{\hbar}
-  \int_{0}^t
-  \bra{\psi_{\beta}(t_1,t')}
-  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
-\end{equation}
-
-Next, we consider a scattering phenomenon when a electron scatters from a known $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with a constant quansienergy $\varepsilon$ as follows
-\begin{equation} \label{eq:c15}
-  \begin{aligned}
-  \ket{\psi_{\beta}(t,t')} &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
-  \ket{\phi_{\beta}(t')} \\
-  &
-  \xRightarrow{\text{scattering}}
-  \ket{\Psi_{\alpha}(t,t')} = \exp(-\frac{i}{\hbar}\varepsilon t)
-  \ket{\Phi_{\alpha}(t')}.
-  \end{aligned}
-\end{equation}
-\begin{figure}[b]
-  \includegraphics[scale=1.0]{figures/fig_6.pdf}
-  \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
-  \label{fig:2}
-\end{figure}
-This phenomenon is illustrated in Fig.~\ref{fig:2}.
-We can calculate the scattering amplitude for this scattering scenario using the expression derived in Eq.~(\ref{eq:c14}) as follows
-\begin{equation} \label{eq:c16}
-  \begin{aligned}
-    a_{\alpha\beta}(t,t') =
-    -\frac{i}{\hbar}
-    \int_{0}^t
-    e^{\frac{i}{\hbar}\left(\varepsilon_{\beta} - \varepsilon \right)t_1}
-    \bra{\phi_{\beta}(t')}
-    V(\vb{r}) \ket{\phi_{\alpha}(t')}  dt_1.
-  \end{aligned}
-\end{equation}
-By assuming for a long duration ($t \rightarrow \infty$), we can turn this integral into a delta distribution
-\begin{equation} \label{eq:c17}
-  \begin{aligned}
-    a_{\alpha\beta}(t') =
-    -2\pi i \delta(\varepsilon_{\beta} - \varepsilon)Q,
-  \end{aligned}
-\end{equation}
-where $Q = \bra{\phi_{\beta}(t')} V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using the completeness properties we can re-write this as
-\begin{equation} \label{eq:c18}
-    Q =
-    \sum_{\vb{k}}\sum_{\vb{k'}}
-    \braket{\phi_{\beta}(t')}{\vb{k'}}
-    \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}
-    \braket{\vb{k}}{\phi_{\alpha}(t')}.
-\end{equation}
-Moreover, separating $x$-directional and $y$-directional momentum components, we can simply this to obtain
-\begin{equation} \label{eq:c19}
-    Q =
-    \sum_{k_x}\sum_{{k'}_x}
-    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
-    V_{\vb{k'},\vb{k}}
-    \phi_{\beta}^{\dagger}(\vb{k'},t')
-    \phi_{\alpha}(\vb{k},t')  dk_y d{k'}_y,
-\end{equation}
-with $V_{\vb{k'},\vb{k}} = \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.
-
-Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
-Thus, we can describe the scattering potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
-\begin{equation} \label{eq:c20}
-  V(\vb{r}) =
-  \sum_{i=1}^{N_{imp}}
-  \upsilon (\vb{r}-\vb{r}_i).
-\end{equation}
-Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
-This model is characterized by the following two equations \cite{akkermans10}
-\begin{subequations}
-\begin{equation} \label{eq:c21a}
-  \expval{\upsilon(\vb{r})}_{imp} =0,
-\end{equation}
-\begin{equation} \label{eq:c21b}
-  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
-\end{equation}
-\end{subequations}
-where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
-In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
-Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
-\begin{equation} \label{eq:c22}
-  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
-\end{equation}
-where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
-\begin{equation} \label{eq:c23}
-  V(\vb{r}) =
-  \sum_{i=1}^{N_{imp}}
-  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
-\end{equation}
-Here we can identify the $\Upsilon_{imp}$ as the strength of the delta potential.
-Furthermore, we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
-\begin{subequations} \label{eq:c24}
-\begin{align}
- V_{\vb{k'},\vb{k}} & =
- \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
- \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq:c24a} \\
- & =
- \sum_{i=1}^{N_{imp}}
- \int_{-\infty}^{\infty} \left[
- \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \right. \\
- & \left. \qquad\quad\times
- \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
- \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \right] dy \label{eq:c24b} \\
-  & =
- \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
- e^{i(k'_y - k_y )y}
- \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq:c24c}.
-\end{align}
-\end{subequations}
-Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs.
-Additionally, assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
-\begin{subequations} \label{eq:c25}
-  \begin{align}
-    V_{\vb{k'},\vb{k}}
-    & =
-    V_{k'_x,k_x}
-    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty}
-    e^{i\left({k'}_y - k_y \right)y_i} dy_i \label{eq:c25a} \\
-    & =
-    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y). \label{eq:c25b}
-  \end{align}
-\end{subequations}
-In the above equation we introduced
-\begin{equation} \label{eq:c26}
-  V_{{k'}_x,k_x} =
-  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x},
-\end{equation}
-which is a constant value for every $i$-th impurity.
-Moreover, $\eta_{imp}$ is the number of impurities in a unit area.
-It is important to note that in the above expression $\braket{x}{k_x} = e^{-ik_xx}$.
-
-Now using Eq.~(\ref{eq:10}) and Eq.~(\ref{eq:c25b}) on Eq.~(\ref{eq:c19}), we obtain
-\begin{equation} \label{eq:c27}
-  \begin{aligned}
-    Q  =
-    \sum_{k_x}\sum_{{k'}_x} &
-    {\eta_{imp} V_{{k'}_x,k_x}} L_x
-    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
-    \delta({k'}_y - k_y)
-    \\
-    & \times
-    \widetilde{\chi}_{n_{\beta}} \bm{\left(} {k'}_y -b\cos(\omega t) \bm{\right)}
-    \widetilde{\chi}_{n_{\alpha}}  \bm{\left(}k_y -b\cos(\omega t) \bm{\right)}
-    \\
-    & \times
-    e^{i[{k'}_y - k_y]d\sin(\omega t)}
-    e^{i[{k'}_y {y'}_0 - k_y y_0]}
-     dk'_y dk_y.
-  \end{aligned}
-\end{equation}
-Here we have changed the time variable $t' \rightarrow t$ only for the simplicity of notation. We can more simply this as
-\begin{equation} \label{eq:c28}
-  \begin{aligned}
-    Q =
-    \sum_{k_x}\sum_{{k'}_x} \eta_{imp} L_x V_{{k'}_x,k_x} I,
-  \end{aligned}
-\end{equation}
-with
-\begin{equation} \label{eq:c29}
-  \begin{aligned}
-    I =
-    \int_{-\infty}^{\infty}
-    \widetilde{\chi}_{n_{\beta}} &\bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
-    \widetilde{\chi}_{n_{\alpha}} \bm{\left(} k_y -b\cos(\omega t) \bm{\right)} \\
-    & \times
-    \exp \bm{(}
-      -ik_y  \left(y_0 - {y'}_0 \right)
-    \bm{)} dk_y.
-  \end{aligned}
-\end{equation}
-To avoid the energy exchange from the dressing field and electrons in Landau levels, the applied radiation must be a purely dressing field.
-Therefore, in this study we assume that the dressing field can only renormalize the the probability of electron scattering inside a same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
-This transform the Eq.~(\ref{eq:c29}) to
-\begin{equation} \label{eq:c30}
-    I =
-    \int_{-\infty}^{\infty}
-    \widetilde{\chi}_N^2 \bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
-    \exp \bm{(}
-      -ik_y  \left(y_0 - {y'}_0 \right)
-    \bm{)} dk_y.
-\end{equation}
-Using the Fourier transform of Gauss-Hermite functions \cite{celeghini21} and the convolution theorem \cite{arfken85,bracewell78} we obtain
-\begin{equation} \label{eq:c31}
-  \begin{aligned}
-    I =
-    {2\pi} &
-    \exp \bm{(} b({y'}_0 - y_0)\cos(\omega t) \bm{)} \\
-    & \times
-    \int_{-\infty}^{\infty}
-    {\chi}_{N}(y)
-    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
-  \end{aligned}
-\end{equation}
-Finally, we can evaluate the scattering amplitude derived in Eq.~(\ref{eq:c17}) for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as follows
-\begin{equation} \label{eq:c32}
-  \begin{aligned}
-    a_{\alpha\beta}&(k_x,k'_x,t)
-    \\
-    & =
-    -2\pi i
-    \eta_{imp} L_x V_{{k'}_x,k_x}
-    e^{ b({y'}_0 - y_0)\cos(\omega t)}\\
-    & \quad\times
-    \delta(\varepsilon_{N} - \varepsilon)
-    \int_{-\infty}^{\infty}
-    {\chi}_{N}(y)
-    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
-  \end{aligned}
-\end{equation}
-Since this scattering amplitude is time-periodic, we can write this as a Fourier series expansion
-\begin{equation} \label{eq:c33}
-    a_{\alpha\beta}(k_x,k'_x,t) =
-    \sum_{l=-\infty}^{\infty} a^l_{\alpha\beta}(k_x,k'_x) e^{-il\omega t}.
-\end{equation}
-In addition, using Jacobi-Anger expansion \cite{cuyt08,abramowitz64}
-\begin{equation} \label{eq:c34}
-    e^{iz\cos(\theta)} = \sum_{l=-\infty}^{\infty} i^l J_l(z) e^{-il\theta},
-\end{equation}
-where $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, we can re-write the Eq.~(\ref{eq:c32}) as follows
-\begin{equation} \label{eq:c35}
-  \begin{aligned}
-    a_{\alpha\beta}&(k_x,k'_x,t)  \\
-    & =
-    \sum_{l=-\infty}^{\infty}
-    -2\pi i^{l+1}
-    \eta_{imp} L_x V_{{k'}_x,k_x}
-    J_l\bm{(}b({y'}_0 - y_0)\bm{)} \\
-    & \quad\times
-    \delta(\varepsilon_{N} - \varepsilon)
-    \int_{-\infty}^{\infty}
-    {\chi}_{N}(y)
-    {\chi}_{N}(y_0 - {y'}_0 - y)  dy \;e^{-il\omega t}.
-  \end{aligned}
-\end{equation}
-Thus, we can identify the Fourier series component of the scattering amplitude as
-\begin{equation} \label{eq:c36}
-  \begin{aligned}
-    a^l_{\alpha\beta}(k_x,k'_x) = &
-    -2\pi i^{l+1}
-    \eta_{imp} L_x V_{{k'}_x,k_x}\\
-    & \times
-    \delta(\varepsilon_{N} - \varepsilon)
-    J_l\bm{(}b({y'}_0 - y_0)\bm{)}\\
-    & \times
-    \int_{-\infty}^{\infty}
-    {\chi}_N(y)
-    {\chi}_N(y_0 - {y'}_0 - y) dy.
-  \end{aligned}
-\end{equation}
-Furthermore, we can define \textit{transition probability matrix} as
-\begin{equation} \label{eq:c37}
-    \left(A_{\alpha\beta} \right)^{l,l'} =
-    a^l_{\alpha\beta}\left[a^{l'}_{\alpha\beta} \right]^{*},
-\end{equation}
-and this becomes
-\begin{equation} \label{eq:c38}
-  \begin{aligned}
-      \left(A_{\alpha\beta} \right)^{l,l'}(k_x,k'_x) = &
-      \left({ 2 \pi \eta_{imp} L_x V_{{k'}_x,k_x}}\right)^2
-      \delta^2(\varepsilon_{N} - \varepsilon) \\
-      & \times
-      J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)}\\
-      & \times
-      \left|
-      \int_{-\infty}^{\infty}
-      {\chi}_N(y)
-      {\chi}_N(y_0 - {y'}_0 - y) dy \right|^2.
-  \end{aligned}
-\end{equation}
-Then describing the square of the delta distribution using the following interpretation \cite{dini16,kibis14}
-\begin{equation} \label{eq:c39}
-    \delta^2(\varepsilon) =
-    \delta(\varepsilon)\delta(0) =
-    \frac{\delta(\varepsilon)}{2\pi \hbar}
-    \int_{-t/2}^{t/2} e^{i0\times t'/\hbar} dt'\; =
-    \frac{\delta(\varepsilon)t}{2\pi \hbar},
-\end{equation}
-and executing the time derivation operation on each matrix element of transition probability matrix, we receive the \textit{transition amplitude matrix} elements
-\begin{equation} \label{eq:40}
-  \begin{aligned}
-    \Gamma_{\alpha\beta}^{ll'}(k_x,k'_x) = &
-    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar} |V_{{k'}_x,k_x}|^2
-    \delta(\varepsilon_{\beta} - \varepsilon)\\
-    & \times
-    J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)} \\
-    & \times
-    \left|
-    \int_{-\infty}^{\infty}
-    {\chi}_N(y)
-    {\chi}_N(y_0 - {y'}_0 - y) dy \right|^2.
-  \end{aligned}
-\end{equation}
-
-Additionally, the inverse scattering time matrix can be identified as the sum of all available momentum over the impurity averaged transition probability matrix element \cite{wackerl20,wackerlthesis20}
-\begin{equation} \label{eq:41}
-    \left(\frac{1}{\tau(\varepsilon,k_x)} \right)^{ll'}_{\alpha\beta} =
-    \frac{1}{L_x} \sum_{{k'}_x}
-    \expval**{\Gamma_{\alpha\beta}^{ll'}({k'}_x,k_x)}_{imp}.
-\end{equation}
-Next, applying the 1-dimensional momentum continuum limit $\sum_{{k'}_x} \longrightarrow {L_x}/{2\pi}\int d {k'}_x$, we can obtain
-\begin{widetext}
-\begin{equation} \label{eq:42}
-  \begin{aligned}
-    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_{\alpha\beta} = &
-    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar}
-    \frac{V_{imp}}{2\pi}
-    \delta(\varepsilon_{\beta} - \varepsilon) \\
-    & \times
-    \int_{-\infty}^{\infty} \left\{
-    J_l\bm{\left(}\frac{b\hbar}{eB}({k}_x - {k'}_x)\bm{\right)}
-    J_{l'}\bm{\left(}\frac{b\hbar}{eB}({k}_x - {k'}_x)\bm{\right)}
-    \left|
-    \int_{-\infty}^{\infty}
-    {\chi}_N(y)
-    {\chi}_N \bm{\left(}\frac{\hbar}{eB} ({k'}_x - {k}_x) - y \bm{\right)} dy\right|^2 \right\} d {k'}_x.
-  \end{aligned}
-\end{equation}
-Here an impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2}_{imp} = V_{imp}$.
-Finally, using substitutions $k'_x = k_1$ and $y = \flatfrac{\hbar{k_2}}{(eB)}$, we can derive our expression for the inverse scattering time matrix for $N$-th Landau
-level as follows
-\begin{equation} \label{eq:43}
-  \begin{aligned}
-    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_{N} &=
-    \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{e^2B^2}
-    \delta(\varepsilon - \varepsilon_{N}) \\
-    & \times
-    \int_{-\infty}^{\infty} \left\{
-    J_l\bm{\left(}\frac{b\hbar}{eB}({k}_x - k_1)\bm{\right)}
-    J_{l'}\bm{\left(}\frac{b\hbar}{eB}({k}_x - k_1)\bm{\right)}
-    \left|
-    \int_{-\infty}^{\infty}
-    {\chi}_N\left(\frac{\hbar}{eB}k_2 \right)
-    {\chi}_N \bm{\left(}\frac{\hbar}{eB} (k_1 - k_x - k_2) \bm{\right)} dk_2 \right|^2 \right\} d k_1.
-  \end{aligned}
-\end{equation}
-\end{widetext}
-%===============================================================================
-
-%===============================================================================
-% Appendix D :
-%===============================================================================
-\section{\label{appendix_d} Current operators for a dressed quantum Hall system}
-
-In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system.
-We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(\ref{eq:1}) and we identified them as the Floquet states in Eq.~(\ref{eq:14}).
-For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(\ref{eq:10}) as quantum states using their corresponding quantum numbers as follows
-\begin{equation} \label{eq:d1}
-  \ket{\phi_{n,m}} = \ket{n,k_x}.
-\end{equation}
-Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
-\begin{equation} \label{eq:d2}
-  \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
-\end{equation}
-Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
-\begin{equation} \label{eq:d3}
-  \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
-\end{equation}
-where $\widetilde{m}$ is the mass of the considering particle.
-
-First, we consider the $x$-directional particle current operator component, and we can identify that as
-\begin{equation} \label{eq:d4}
-  \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
-\end{equation}
-Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
-\begin{equation} \label{eq:d5}
-  \left({j}_x \right)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
-\end{equation}
-and we evaluate these using the Floquet modes derived in Eq.~(\ref{eq:7}) as follows
-\begin{equation} \label{eq:d6}
-  \begin{aligned}
-    \left({j}_x \right)_{nm,n'm'} = &
-    \frac{1}{{\widetilde{m}}}
-    \delta_{k_x,k'_x}
-    \int
-    \left(\hbar k'_x + eBy\right) \\
-    & \times
-     \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
-    \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
-    dy.
-  \end{aligned}
-\end{equation}
-Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
-\begin{equation} \label{eq:d7}
-  \begin{aligned}
-    \left({j}_x \right)_{nm,n'm'} =
-    \frac{1}{{\widetilde{m}}}
-    \delta_{k_x,k'_x}
-    \int &
-    \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right] \\
-    & \times
-    \chi_{n}(\bar{y})
-    \chi_{n'}(\bar{y})
-    d\bar{y}.
-  \end{aligned}
-\end{equation}
-Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
-\begin{subequations} \label{eq:d8}
-  \begin{align}
-    \int
-    \chi_{n}({y})
-    \chi_{n'}({y}) d{y} &=
-    \delta_{n',n}, \\
-    \int
-    y \chi_{n}({y})\chi_{n'}({y}) d{y} &=
-    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-    \delta_{n',n-1} \right),
-  \end{align}
-\end{subequations}
-we simplify the matrix elements of $x$-directional current operator to obtain
-\begin{equation} \label{eq:d9}
-  \begin{aligned}
-    &\left({j}_x \right)_{nm,n'm'} =
-    \frac{eB}{{\widetilde{m}}}
-    \delta_{k_x,k'_x} \\
-    & \qquad\times
-    \left[
-    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-    \delta_{n',n-1}\right)
-    + \zeta(t) \delta_{n',n}
-    \right].
-  \end{aligned}
-\end{equation}
-Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
-\begin{equation} \label{eq:d10}
-  \begin{aligned}
-      \left({j}_x \right)_{nm,n'm'} =&
-      \frac{eB}{\widetilde{m}}
-      \delta_{k_x,k'_x} \\
-      & \times
-      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-      \delta_{n',n-1} \right).
-  \end{aligned}
-\end{equation}
-For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
-\begin{equation} \label{eq:d11}
-  \begin{aligned}
-      \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
-      \frac{e^2B}{{m_e}}
-      \delta_{k_x,k'_x}\\
-      & \times
-      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-      \delta_{n',n-1} \right).
-  \end{aligned}
-\end{equation}
-
-Moreover, we can identify the $y$-directional current operator component as
-\begin{equation} \label{eq:d12}
-  \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
-\end{equation}
-Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
-\begin{equation} \label{eq:d13}
-  \left({j}_y \right)_{nm,n'm'} =
-  \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
-\end{equation}
-After following the same steps done for the $x$-directional current operator, we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
-\begin{equation} \label{eq:d14}
-  \begin{aligned}
-    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
-    \frac{ie\hbar}{{m_e}}
-    \delta_{k_x,k'_x} \\
-    & \times
-    \left(
-    \sqrt{\frac{n}{2}} \delta_{n',n-1}
-    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
-    \right).
-  \end{aligned}
-\end{equation}
-%===============================================================================
-\end{appendix}
-
-%===============================================================================
-% Bibliography
-%===============================================================================
-\bibliography{aps_article}
-%===============================================================================
-
-\end{document}
-
-% ****** End of file dressed_quantum_hall.tex ****** %

### 2021-11-02 response/response.tex
Add response and v40

% ****** Start of file response.tex ****** %
\documentclass{article}

%===============================================================================
% Import packages
%===============================================================================

\usepackage[top=0.8in,bottom=1in,left=1in,right=1in]{geometry}
% Physics package
\usepackage{physics}
% Paragraph skip package
\usepackage[parfill]{parskip}
% AMS packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
% Color package
\usepackage[dvipsnames]{xcolor}
% Acronym package
\usepackage[acronym]{glossaries}
% SI units package
\usepackage{siunitx}
% Hypertext package
\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=black,citecolor=blue]{hyperref}
% Bold math
\usepackage{bm}
% Other packages
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float}

% Bibliography style
\bibliographystyle{abbrv}

\begin{document}

% Define acronyms
\newacronym{tls}{TLS}{two-level system}

%===============================================================================
% Add date
%===============================================================================
\today\\

Ashot Melikyan,\\
Associate Editor,\\
Physical Review B.\\

Dear Professor Melikyan,

Thank you very much for your effort in managing the review process of our manuscript. We are also thankful for the reviewer comments, and believe the second version of the manuscript we submit herewith has been significantly improved by the constructive criticism we received. Additionally, the subsequent sections of this document discusses the reviewer comments and our responses to them.

Please note that in the following sections, the statements in {\color{RoyalBlue} \textbf{blue}} are the comments of the reviewers. Our responses are shown in black letters and the modifications we have done to the manuscript are given in {\color{Maroon} red}.

\subsection*{General changes to the manuscript}

\begin{itemize}
    \item We have made minor changes in language and presentation to improve clarity, and to match the rest of the manuscript better to the changes done to address the reviewer's comments.
    \begin{itemize}
        \item Section IV-A first paragraph - \\
            {\color{Maroon} We prepare the thermal reservoirs $B_L$ and $B_R$ so that the temperature $T_L$ of $B_L$ is significantly higher than the temperature $T_R$ of $B_R$ \acrshort{tls}.}
    \end{itemize}
\end{itemize}

\subsection*{Response to the comments of Reviewer 1}

We would like to thank the reviewer for bringing the deficiencies of our manuscript to our attention and providing constructive feedback to improve the quality of our work. We have considered all of your suggestions seriously and revised our paper manuscript as described below.

\subsubsection*{Comment 1 -
\color{RoyalBlue} My concern is that the manuscript is heavily skewed towards a purely mathematical formulation of the problem. It has a minimal connection to realistic two-dimensional electron systems. The manuscript does not discuss how the results can be applied to understanding mechanisms of charge transport in nanoelectronic devices and can be used to optimize device performance. Without such discussion, the manuscript will have a minimal impact on the community working on developing nanoelectronics.}

In the initial version of the manuscript, we used natural units with $\hbar=k_B=1$ mainly because a similar system of units was used in Joulain \textit{et al.} \cite{mahan00} whose work we extend. Also, some of the widely used standard textbooks (e.g. Breuer \textit{et al.} \cite{breuer2002theory}) use a similar scheme. It was our belief at the time that it would have improved the readability of the manuscript for a reader well-versed in the relevant literature.

However we admit that the use of natural units would make it harder for some experimentally inclined readers as measurement instruments usually provide SI readings. To such a reader, mapping our simulated results with their corresponding experimental values by transforming the units would have been an additional task.

Thus, as per your suggestion, we have mapped all natural units to their equivalent SI units in the revised manuscript. For comparison with earlier work (as per your Comment 2), we have taken the liberty of recreating the thermal transistor system analyzed by Joulain \textit{et al.} \cite{joulain2016quantum} and converting it also into SI units.

We detail these changes below.

\begin{itemize}
    \item Section IV first paragraph -
        Changed to reflect the new SI system of units. - \\
            {\color{Maroon} Note that in the following, we work in SI units where $\hbar=1.055\cross10^{-34} \text{Js}$ and $k_B=1.381\cross10^{-23} \text{J/K}$.}
    \item Section IV-A fourth paragraph -
        When moving to SI units, we had to insert conversion factors to deal with differently scaled energy levels, frequencies and temperatures. We have introduced Eq.~\ref{eq:unitequivalence} and the text below to establish these exact relationships. The factor of $5$ used there originates from the work of Joulain \textit{et al.} \cite{joulain2016quantum} and is verified further by our simulations. (The system energy levels need to be at least $5$ times higher for it to demonstrate the thermal transistor and optical-gating behaviors well. If the system energy levels were lower, the baths would have had enough energy to drive the conduction mechanism by its own, without the need for raised temperature $T_M$ or the optical field. Thus the optical gating action or thermal transistor action would diminish.) - \\
            {\color{Maroon} Our next task is to select the appropriate system parameters. For proper operation, the overall scale of the system energy levels should be chosen to be around five times greater than the energy levels associated with the thermal baths \cite{joulain2016quantum}. Mathematically, this condition can be written as
            \setcounter{equation}{24}
            \begin{equation}
                \hbar \omega \approx 5 k_B T
                \label{eq:unitequivalence}
            \end{equation}
            where $\omega$ and $T$ represent the typical frequency and the temperature scales associated with the system and its environment. We then specify the relationships between different energy levels as $\omega_L=\omega_R=0$, $\omega_{RL}=0$, and $\omega_{LM}=\omega_{MR}\gg\omega_M>0$ to obtain a system whose energy level diagram is similar to Fig. 2. This provides us with a relatively simple system while showcasing thermal gating behavior well.}
\end{itemize}

\subsubsection*{Comment 2 -
\color{RoyalBlue} As the proposed system is an extension of the one reported in
reference \cite{joulain2016quantum}, authors should compare their results with the
corresponding ones reported in that reference. In particular, the
comparison of the amplification factors would be interesting.}

We agree with the reviewer that a comparison between the our optical-gating system and the device reported in \cite{joulain2016quantum} would be valuable to the reader. However it is important to note that the previous device controlled the $J_L$ and $J_R$ heat flows via changing the temperature $T_M$ of the terminal $M$. In contrast, we employ the driving strength of the field $F$, or in other words its Rabi frequency $\Omega$, to control the same heat flows. Even though the two devices are basically identical in the output side, they are quite different on the input side. This makes a simple, direct comparison of the two devices impossible. Therefore, we had to resort to the following methodology for our comparison.
\begin{enumerate}
    \item First we simulate both systems with the same bath temperatures $T_L$ and $T_R$, and same system parameters $\omega_P$s and $\omega_{PQ}$s. -
    \begin{itemize}
        \item We first reproduced the results of Joulain \textit{et al.} \cite{joulain2016quantum}. Since we use SI units for our work, we mapped all their parameters to SI units and generated corresponding results.
        \item We then used the same parameter set as Joulain \textit{et al.} \cite{joulain2016quantum} to simulate our device.
    \end{itemize}

    \item Then, we find the control-parameter (i.e. $T_M$ for original system, $\Omega$ for our system) ranges within which each system shows the required thermal behaviors. -
    \begin{itemize}
        \item For the previous system, the original authors had found that the control range is between the lower bound $T_R$ and the upper bound $T_L$.
        \item In our system the magnitude of $\Omega$ has the lower bound of zero, but does not have a hard upper bound. However we see from Fig. \ref{fig:energyflows2}, that our system eventually saturates for large $\Omega$ values, after which increasing $\Omega$ further has minimal effect on the heat flows. We use this $\Omega$ value at saturation to define an approximate upper bound, which turns out to be around $3\Delta$ in our simulations.
    \end{itemize}

    \item Next, we simulate all output heat flows of each device for the full control-parameter range of that particular device. -
    \begin{itemize}
        \item For each system, we use a very small step-size and vary the control-parameter from its minimum value to its maximum value, and measure the output heat flows.
        \item The resulting plots are shown in Fig. \ref{fig:energyflows2} and Fig. \ref{fig:energyefficiency}. Each plot have a single vertical axis, and two horizontal axes. The top horizontal axis measures $T_M$ and corresponds to the device of Joulain \textit{et al.} \cite{joulain2016quantum}, while the bottom axis measures $\Omega$ and corresponds to our system. We plot the values measured from the previous device with dashed lines, and values measured from our device with solid lines.
    \end{itemize}
\end{enumerate}

\bibliography{response}

\bigskip
\bigskip

Sincerely yours,

\def\s#1#2#3{\vbox{\hsize=4.5cm
		\kern2cm
		\hrule\kern1ex
		\hbox to \hsize{\strut\hfil #1 \hfil}
		\hbox to \hsize{\strut\hfil #2 \hfil}
		\hbox to \hsize{\strut\hfil #3 \hfil}}}

\hbox to \hsize{\s{Malin Premaratne}{(Corresponding Author)}{\href{malin.premaratne@monash.edu}{malin.premaratne@monash.edu}}}

\end{document}

% ****** End of file dressed_quantum_hall.tex ****** %

### 2021-11-02 paper/v4.0/sections/appendix_c.tex
Add response and v40

--- 2021-08-22 paper/v3-release/aps_article.tex
@@
-% ****** Start of file dressed_quantum_hall.tex ****** %
+We derive the Floquet-Fermi golden rule for our dressed quantum Hall system with the help of the $t$-$t'$ formalism. The $t$-$t'$-Floquet states \cite{grifoni98,wackerl20}
+\begin{equation} \label{eq:c1}
+  \ket{\psi_{n,m}(t,t')} =
+  \exp(-\frac{i}{\hbar}\varepsilon_{n} t)\ket{\phi_{n,m}(t')},
+\end{equation}
+are derived by separating the aperiodic and periodic components of the Floquet states given in Eq.~(\ref{eq:14}).
+Additionally, these states fulfill the $t$-$t'$-Schrödinger equation \cite{grifoni98,wackerl20}
+\begin{equation} \label{eq:c2}
+  i \hbar \pdv{t}\ket{\psi_{n,m}(t,t')} =
+  H_F(t') \ket{\psi_{n,m}(t,t')},
+\end{equation}
+where the \textit{Floquet Hamiltonian} defined as
+\begin{equation} \label{eq:c3}
+  H_F(t') =
+  H_e(t') - i\hbar \pdv{t'}.
+\end{equation}
+Next, we can identify the time evolution operator corresponding to the $t$-$t'$-Schrödinger equation as
+\begin{equation} \label{eq:c4}
+  U_F(t,t_0;t') = \exp(-\frac{i}{\hbar}H_F(t')\left[t-t_0 \right]).
+\end{equation}
+The advantage of $t$-$t'$ formalism lies on this time evolution operator which avoids any time ordering operators \cite{wackerl20}.
 
-\documentclass[
- reprint,
- amsmath,amssymb,
- aps,
- prb,
-]{revtex4-2}
+We model the effect caused by impurities in the considered system as a single perturbation potential formed by a group of randomly distributed impurities.
+Thus, we introduce a time-independent total perturbation $V(\vb{r})$ which has been turned on at the reference time $t=t_0$, and the $t$-$t'$-Schrödinger equation becomes
+\begin{equation} \label{eq:c5}
+  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')} =
+  \left[H_F(t') + V(\vb{r}) \right]\ket{\Psi_{n,m}(t,t')}.
+\end{equation}
+This introduces a new wave function solution $\ket{\Psi_{n,m}}$ for a system with a given perturbation. If $t\leq t_0$, both of the solutions for Eq.~(\ref{eq:c2}) and Eq.~(\ref{eq:c5}) coincide
+\begin{equation} \label{eq:c6}
+  \ket{\psi_{n,m}(t,t')} =\ket{\Psi_{n,m}(t,t')} \quad
+  \text{when} \quad
+  t \leq t_0.
+\end{equation}
+Next, we move our analysis into the interaction picture representation \cite{bruus04,mahan00} and in the interaction picture, we can identify the $t$-$t'$-Floquet state as
+\begin{equation} \label{eq:c7}
+  \ket{\Psi_{n,m}(t,t')}_I = U_0^{\dagger}(t,t_0;t')
+  \ket{\Psi_{n,m}(t,t')}.
+\end{equation}
+Due to time-independence, the perturbation in the interaction picture has the same form as the Schrödinger picture representation
+\begin{equation} \label{eq:c8}
+  V_I(\vb{r}) = U_0^{\dagger}(t,t_0;t')V(\vb{r})U_0(t,t_0;t') =
+  V(\vb{r}).
+\end{equation}
+This leads us to the $t$-$t'$-Schrödinger equation in the interaction picture representation
+\begin{equation} \label{eq:c9}
+  i \hbar \pdv{t}\ket{\Psi_{n,m}(t,t')}_I =
+  V_I(\vb{r})\ket{\Psi_{n,m}(t,t')}_I,
+\end{equation}
+with the recursive solutions \cite{bruus04,mahan00}
+\begin{equation} \label{eq:c10}
+  \begin{aligned}
+  \ket{\Psi_{n,m}(t,t')}_I = &\ket{\Psi_{n,m}(t_0,t')}_I \\
+  &+
+  \frac{1}{i\hbar}
+  \int_{t_0}^t
+  V_I(\vb{r}) \ket{\Psi_{n,m}(t_1,t')}_I dt_1.
+  \end{aligned}
+\end{equation}
+Iterating the solution only up to the first order (Born approximation) we obtain
+\begin{equation} \label{eq:c11}
+  \begin{aligned}
+    \ket{\Psi_{n,m}(t,t')}_I \approx &\ket{\psi_{n,m}(t_0,t')} \\
+    &+
+    \frac{1}{i\hbar}
+    \int_{t_0}^t
+    V_I(\vb{r}) \ket{\psi_{n,m}(t_0,t')} dt_1.
+  \end{aligned}
+\end{equation}
 
-%===============================================================================
-% Import packages
-%===============================================================================
-% Bold math
-\usepackage{bm}
-% AMS packages
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathtools}
-% Physics package
-\usepackage{physics}
-% SI units package
-\usepackage{siunitx}
-% Hypertext package
-\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
-% Language and font encodings
-\usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage[T1]{fontenc}
-%===============================================================================
-% Bibliography style
-\bibliographystyle{apsrev4-2}
+Since our $t$-$t'$-Floquet states create a basis, we can represent the solutions for the $t$-$t'$-Schrödinger equation given in Eq.~(\ref{eq:c5}) using our known $t$-$t'$-Floquet states as follows
+\begin{equation} \label{eq:c12}
+  \ket{\Psi_{\alpha}(t,t')} = \sum_{\beta} a_{\alpha,\beta}(t,t')
+  \ket{\psi_{\beta}(t,t')}.
+\end{equation}
+Here, we used a single term notation to represent two quantum numbers; $\alpha \equiv (n_{\alpha},m_{\alpha})$ and $\beta \equiv (n_{\beta},m_{\beta})$.
+Subsequently, we can identify the \textit{scattering amplitude} as $a_{\alpha,\beta}(t,t') =
+\braket{\psi_{\beta}(t,t')}{\Psi_{\alpha}(t,t')}$ and we can evaluate this with
+\begin{equation} \label{eq:c13}
+  \begin{aligned}
+  a_{\alpha,\beta}(t,t') = &
+  \braket{\psi_{\beta}(t,t')}{\psi_{\alpha}(t,t')} \\
+  &+
+  \frac{1}{i\hbar}
+  \int_{t_0}^t
+  \bra{\psi_{\beta}(t_1,t')}
+  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
+  \end{aligned}
+\end{equation}
+Since the $t$-$t'$-Floquet states are orthonormal and assuming $t_0 = 0$ and $\alpha \neq \beta$ this leads to
+\begin{equation} \label{eq:c14}
+  a_{\alpha,\beta}(t,t') =
+  -
+  \frac{i}{\hbar}
+  \int_{0}^t
+  \bra{\psi_{\beta}(t_1,t')}
+  V(\vb{r}) \ket{\psi_{\alpha}(t_1,t')} dt_1.
+\end{equation}
 
-\begin{document}
+Next, we consider a scattering phenomenon when a electron scatters from a known $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into a distinct $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with a constant quansienergy $\varepsilon$ as follows
+\begin{equation} \label{eq:c15}
+  \begin{aligned}
+  \ket{\psi_{\beta}(t,t')} &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
+  \ket{\phi_{\beta}(t')} \\
+  &
+  \xRightarrow{\text{scattering}}
+  \ket{\Psi_{\alpha}(t,t')} = \exp(-\frac{i}{\hbar}\varepsilon t)
+  \ket{\Phi_{\alpha}(t')}.
+  \end{aligned}
+\end{equation}
+\begin{figure}[b]
+  \includegraphics[scale=1.0]{figures/fig_6.pdf}
+  \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
+  \label{fig:2}
+\end{figure}
+This phenomenon is illustrated in Fig.~\ref{fig:2}.
+We can calculate the scattering amplitude for this scattering scenario using the expression derived in Eq.~(\ref{eq:c14}) as follows
+\begin{equation} \label{eq:c16}
+  \begin{aligned}
+    a_{\alpha\beta}(t,t') =
+    -\frac{i}{\hbar}
+    \int_{0}^t
+    e^{\frac{i}{\hbar}\left(\varepsilon_{\beta} - \varepsilon \right)t_1}
+    \bra{\phi_{\beta}(t')}
+    V(\vb{r}) \ket{\phi_{\alpha}(t')}  dt_1.
+  \end{aligned}
+\end{equation}
+By assuming for a long duration ($t \rightarrow \infty$), we can turn this integral into a delta distribution
+\begin{equation} \label{eq:c17}
+  \begin{aligned}
+    a_{\alpha\beta}(t') =
+    -2\pi i \delta(\varepsilon_{\beta} - \varepsilon)Q,
+  \end{aligned}
+\end{equation}
+where $Q = \bra{\phi_{\beta}(t')} V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using the completeness properties we can re-write this as
+\begin{equation} \label{eq:c18}
+    Q =
+    \sum_{\vb{k}}\sum_{\vb{k'}}
+    \braket{\phi_{\beta}(t')}{\vb{k'}}
+    \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}
+    \braket{\vb{k}}{\phi_{\alpha}(t')}.
+\end{equation}
+Moreover, separating $x$-directional and $y$-directional momentum components, we can simply this to obtain
+\begin{equation} \label{eq:c19}
+    Q =
+    \sum_{k_x}\sum_{{k'}_x}
+    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
+    V_{\vb{k'},\vb{k}}
+    \phi_{\beta}^{\dagger}(\vb{k'},t')
+    \phi_{\alpha}(\vb{k},t')  dk_y d{k'}_y,
+\end{equation}
+with $V_{\vb{k'},\vb{k}} = \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.
 
-\preprint{APS/123-QED}
+Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
+Thus, we can describe the scattering potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
+\begin{equation} \label{eq:c20}
+  V(\vb{r}) =
+  \sum_{i=1}^{N_{imp}}
+  \upsilon (\vb{r}-\vb{r}_i).
+\end{equation}
+Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
+This model is characterized by the following two equations \cite{akkermans10}
+\begin{subequations}
+\begin{equation} \label{eq:c21a}
+  \expval{\upsilon(\vb{r})}_{imp} =0,
+\end{equation}
+\begin{equation} \label{eq:c21b}
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
+\end{equation}
+\end{subequations}
+where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
+In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
+Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
+\begin{equation} \label{eq:c22}
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
+\end{equation}
+where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
+\begin{equation} \label{eq:c23}
+  V(\vb{r}) =
+  \sum_{i=1}^{N_{imp}}
+  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
+\end{equation}
+Here we can identify the $\Upsilon_{imp}$ as the strength of the delta potential.
+Furthermore, we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
+\begin{subequations} \label{eq:c24}
+\begin{align}
+ V_{\vb{k'},\vb{k}} & =
+ \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
+ \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq:c24a} \\
+ & =
+ \sum_{i=1}^{N_{imp}}
+ \int_{-\infty}^{\infty} \left[
+ \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \right. \\
+ & \left. \qquad\quad\times
+ \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
+ \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \right] dy \label{eq:c24b} \\
+  & =
+ \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
+ e^{i(k'_y - k_y )y}
+ \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq:c24c}.
+\end{align}
+\end{subequations}
+Since $\upsilon (\vb{r})$ in momentum space is a constant value, each impurity  produce same impurity potential for every $x$-directional momentum pairs.
+Additionally, assuming the total number of scatters $N_{imp}$ is microscopically large, we can derive
+\begin{subequations} \label{eq:c25}
+  \begin{align}
+    V_{\vb{k'},\vb{k}}
+    & =
+    V_{k'_x,k_x}
+    \frac{N_{imp}}{L_y L_x} \int_{-\infty}^{\infty}
+    e^{i\left({k'}_y - k_y \right)y_i} dy_i \label{eq:c25a} \\
+    & =
+    \eta_{imp} V_{k'_x,k_x} \delta(k'_y - k_y). \label{eq:c25b}
+  \end{align}
+\end{subequations}
+In the above equation we introduced
+\begin{equation} \label{eq:c26}
+  V_{{k'}_x,k_x} =
+  \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x},
+\end{equation}
+which is a constant value for every $i$-th impurity.
+Moreover, $\eta_{imp}$ is the number of impurities in a unit area.
+It is important to note that in the above expression $\braket{x}{k_x} = e^{-ik_xx}$.
 
-% Title of the manuscript
-\title{A generalized model for the charge transport properties of
-\\dressed quantum Hall systems}
+Now using Eq.~(\ref{eq:10}) and Eq.~(\ref{eq:c25b}) on Eq.~(\ref{eq:c19}), we obtain
+\begin{equation} \label{eq:c27}
+  \begin{aligned}
+    Q  =
+    \sum_{k_x}\sum_{{k'}_x} &
+    {\eta_{imp} V_{{k'}_x,k_x}} L_x
+    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
+    \delta({k'}_y - k_y)
+    \\
+    & \times
+    \widetilde{\chi}_{n_{\beta}} \bm{\left(} {k'}_y -b\cos(\omega t) \bm{\right)}
+    \widetilde{\chi}_{n_{\alpha}}  \bm{\left(}k_y -b\cos(\omega t) \bm{\right)}
+    \\
+    & \times
+    e^{i[{k'}_y - k_y]d\sin(\omega t)}
+    e^{i[{k'}_y {y'}_0 - k_y y_0]}
+     dk'_y dk_y.
+  \end{aligned}
+\end{equation}
+Here we have changed the time variable $t' \rightarrow t$ only for the simplicity of notation. We can more simply this as
+\begin{equation} \label{eq:c28}
+  \begin{aligned}
+    Q =
+    \sum_{k_x}\sum_{{k'}_x} \eta_{imp} L_x V_{{k'}_x,k_x} I,
+  \end{aligned}
+\end{equation}
+with
+\begin{equation} \label{eq:c29}
+  \begin{aligned}
+    I =
+    \int_{-\infty}^{\infty}
+    \widetilde{\chi}_{n_{\beta}} &\bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
+    \widetilde{\chi}_{n_{\alpha}} \bm{\left(} k_y -b\cos(\omega t) \bm{\right)} \\
+    & \times
+    \exp \bm{(}
+      -ik_y  \left(y_0 - {y'}_0 \right)
+    \bm{)} dk_y.
+  \end{aligned}
+\end{equation}
+To avoid the energy exchange from the dressing field and electrons in Landau levels, the applied radiation must be a purely dressing field.
+Therefore, in this study we assume that the dressing field can only renormalize the the probability of electron scattering inside a same Landau energy level $(n_{\alpha} = n_{\beta} =N)$.
+This transform the Eq.~(\ref{eq:c29}) to
+\begin{equation} \label{eq:c30}
+    I =
+    \int_{-\infty}^{\infty}
+    \widetilde{\chi}_N^2 \bm{\left(}  k_y -b\cos(\omega t) \bm{\right)}
+    \exp \bm{(}
+      -ik_y  \left(y_0 - {y'}_0 \right)
+    \bm{)} dk_y.
+\end{equation}
+Using the Fourier transform of Gauss-Hermite functions \cite{celeghini21} and the convolution theorem \cite{arfken85,bracewell78} we obtain
+\begin{equation} \label{eq:c31}
+  \begin{aligned}
+    I =
+    {2\pi} &
+    \exp \bm{(} b({y'}_0 - y_0)\cos(\omega t) \bm{)} \\
+    & \times
+    \int_{-\infty}^{\infty}
+    {\chi}_{N}(y)
+    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
+  \end{aligned}
+\end{equation}
+Finally, we can evaluate the scattering amplitude derived in Eq.~(\ref{eq:c17}) for given $k_x = 2\pi m_{\alpha}/L_x$ and $k'_x =  2\pi m_{\beta}/L_x$ as follows
+\begin{equation} \label{eq:c32}
+  \begin{aligned}
+    a_{\alpha\beta}&(k_x,k'_x,t)
+    \\
+    & =
+    -2\pi i
+    \eta_{imp} L_x V_{{k'}_x,k_x}
+    e^{ b({y'}_0 - y_0)\cos(\omega t)}\\
+    & \quad\times
+    \delta(\varepsilon_{N} - \varepsilon)
+    \int_{-\infty}^{\infty}
+    {\chi}_{N}(y)
+    {\chi}_{N}(y_0 - {y'}_0 - y) dy.
+  \end{aligned}
+\end{equation}
+Since this scattering amplitude is time-periodic, we can write this as a Fourier series expansion
+\begin{equation} \label{eq:c33}
+    a_{\alpha\beta}(k_x,k'_x,t) =
+    \sum_{l=-\infty}^{\infty} a^l_{\alpha\beta}(k_x,k'_x) e^{-il\omega t}.
+\end{equation}
+In addition, using Jacobi-Anger expansion \cite{cuyt08,abramowitz64}
+\begin{equation} \label{eq:c34}
+    e^{iz\cos(\theta)} = \sum_{l=-\infty}^{\infty} i^l J_l(z) e^{-il\theta},
+\end{equation}
+where $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, we can re-write the Eq.~(\ref{eq:c32}) as follows
+\begin{equation} \label{eq:c35}
+  \begin{aligned}
+    a_{\alpha\beta}&(k_x,k'_x,t)  \\
+    & =
+    \sum_{l=-\infty}^{\infty}
+    -2\pi i^{l+1}
+    \eta_{imp} L_x V_{{k'}_x,k_x}
+    J_l\bm{(}b({y'}_0 - y_0)\bm{)} \\
+    & \quad\times
+    \delta(\varepsilon_{N} - \varepsilon)
+    \int_{-\infty}^{\infty}
+    {\chi}_{N}(y)
+    {\chi}_{N}(y_0 - {y'}_0 - y)  dy \;e^{-il\omega t}.
+  \end{aligned}
+\end{equation}
+Thus, we can identify the Fourier series component of the scattering amplitude as
+\begin{equation} \label{eq:c36}
+  \begin{aligned}
+    a^l_{\alpha\beta}(k_x,k'_x) = &
+    -2\pi i^{l+1}
+    \eta_{imp} L_x V_{{k'}_x,k_x}\\
+    & \times
+    \delta(\varepsilon_{N} - \varepsilon)
+    J_l\bm{(}b({y'}_0 - y_0)\bm{)}\\
+    & \times
+    \int_{-\infty}^{\infty}
+    {\chi}_N(y)
+    {\chi}_N(y_0 - {y'}_0 - y) dy.
+  \end{aligned}
+\end{equation}
+Furthermore, we can define \textit{transition probability matrix} as
+\begin{equation} \label{eq:c37}
+    \left(A_{\alpha\beta} \right)^{l,l'} =
+    a^l_{\alpha\beta}\left[a^{l'}_{\alpha\beta} \right]^{*},
+\end{equation}
+and this becomes
+\begin{equation} \label{eq:c38}
+  \begin{aligned}
+      \left(A_{\alpha\beta} \right)^{l,l'}(k_x,k'_x) = &
+      \left({ 2 \pi \eta_{imp} L_x V_{{k'}_x,k_x}}\right)^2
+      \delta^2(\varepsilon_{N} - \varepsilon) \\
+      & \times
+      J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)}\\
+      & \times
+      \left|
+      \int_{-\infty}^{\infty}
+      {\chi}_N(y)
+      {\chi}_N(y_0 - {y'}_0 - y) dy \right|^2.
+  \end{aligned}
+\end{equation}
+Then describing the square of the delta distribution using the following interpretation \cite{dini16,kibis14}
+\begin{equation} \label{eq:c39}
+    \delta^2(\varepsilon) =
+    \delta(\varepsilon)\delta(0) =
+    \frac{\delta(\varepsilon)}{2\pi \hbar}
+    \int_{-t/2}^{t/2} e^{i0\times t'/\hbar} dt'\; =
+    \frac{\delta(\varepsilon)t}{2\pi \hbar},
+\end{equation}
+and executing the time derivation operation on each matrix element of transition probability matrix, we receive the \textit{transition amplitude matrix} elements
+\begin{equation} \label{eq:40}
+  \begin{aligned}
+    \Gamma_{\alpha\beta}^{ll'}(k_x,k'_x) = &
+    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar} |V_{{k'}_x,k_x}|^2
+    \delta(\varepsilon_{\beta} - \varepsilon)\\
+    & \times
+    J_l\bm{(}b({y'}_0 - y_0)\bm{)} J_{l'}\bm{(}b({y'}_0 - y_0)\bm{)} \\
+    & \times
+    \left|
+    \int_{-\infty}^{\infty}
+    {\chi}_N(y)
+    {\chi}_N(y_0 - {y'}_0 - y) dy \right|^2.
+  \end{aligned}
+\end{equation}
 
-% Authors of the manuscript
-\author{Kosala Herath,}
-\email[]{kosala.herath@monash.edu}
-\author{Malin Premaratne}
-\email[]{malin.premaratne@monash.edu}
-\affiliation{Advanced Computing and Simulation Laboratory (A$\chi$L), Department of Electrical and Computer Systems Engineering, Monash University, Clayton, Victoria 3800, Australia.}
-
-% Add date
-\date{\today}
-
-% Abstract
-\begin{abstract}
-\input{sections/abstract.tex}
-\end{abstract}
-
-% Make title of the manuscript
-\maketitle
-
-% Section 01 : Introduction
-\section{\label{sec_introduction} Introduction}
-\input{sections/1_introduction.tex}
-
-% Section 02 : Schrodinger problem for a dressed quantum Hall system
-\section{\label{sec_schrodinger_problem} Schrodinger problem for a dressed quantum Hall system}
-\input{sections/2_schrodinger_problem.tex}
-
-% Section 03 : Floquet theory perspectiv
-\section{\label{sec_floquet_theory} Floquet theory perspective}
-\input{sections/3_floquet_theory.tex}
-
-% Section 04 :
-\section{\label{sec_inverse_scattering_time}  Inverse Scattering Time Analysis}
-\input{sections/4_inverse_scattering_time.tex}
-
-% Section 05 :
-\section{\label{sec_floquet_drude_conductivity} Floquet-Drude Conductivity in a Dressed Quantum Hall System}
-\input{sections/5_floquet_drude_conductivity.tex}
-
-% Section 06 :
-\section{\label{sec_manipulate_conductivity} Manipulate Conductivity in Quantum Hall Systems}
-\input{sections/6_manipulate_conductivity.tex}
-
-% Section 07 :
-\section{\label{sec_conclusions} Conclusions}
-\input{sections/7_conclusions.tex}
-
-% Acknowledgments
-\begin{acknowledgments}
-\input{sections/acknowledgments.tex}
-\end{acknowledgments}
-
-% Add appendixes
-\appendix
-
-% Appendix A : Wave function solutions for a dressed quantum Hall system
-\section{\label{appendix_a} Wave function solutions for a dressed quantum Hall system}
-\input{sections/appendix_a.tex}
-
-% Appendix B :
-\section{\label{appendix_b} Floquet modes and quasienergies}
-\input{sections/appendix_b.tex}
-
-% Appendix C :
-\section{\label{appendix_c} Floquet-Fermi golden rule for a dressed quantum  Hall system}
-\input{sections/appendix_c.tex}
-
-% Appendix D :
-\section{\label{appendix_d} Current operators for a dressed quantum Hall system}
-\input{sections/appendix_d.tex}
-
-% Bibliography
-\bibliography{aps_article}
-
-\end{document}
-
-% ****** End of file dressed_quantum_hall.tex ****** %
+Additionally, the inverse scattering time matrix can be identified as the sum of all available momentum over the impurity averaged transition probability matrix element \cite{wackerl20,wackerlthesis20}
+\begin{equation} \label{eq:41}
+    \left(\frac{1}{\tau(\varepsilon,k_x)} \right)^{ll'}_{\alpha\beta} =
+    \frac{1}{L_x} \sum_{{k'}_x}
+    \expval**{\Gamma_{\alpha\beta}^{ll'}({k'}_x,k_x)}_{imp}.
+\end{equation}
+Next, applying the 1-dimensional momentum continuum limit $\sum_{{k'}_x} \longrightarrow {L_x}/{2\pi}\int d {k'}_x$, we can obtain
+\begin{widetext}
+\begin{equation} \label{eq:42}
+  \begin{aligned}
+    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_{\alpha\beta} = &
+    \frac { 2\pi \eta_{imp}^2 L_x^2}{ \hbar}
+    \frac{V_{imp}}{2\pi}
+    \delta(\varepsilon_{\beta} - \varepsilon) \\
+    & \times
+    \int_{-\infty}^{\infty} \left\{
+    J_l\bm{\left(}\frac{b\hbar}{eB}({k}_x - {k'}_x)\bm{\right)}
+    J_{l'}\bm{\left(}\frac{b\hbar}{eB}({k}_x - {k'}_x)\bm{\right)}
+    \left|
+    \int_{-\infty}^{\infty}
+    {\chi}_N(y)
+    {\chi}_N \bm{\left(}\frac{\hbar}{eB} ({k'}_x - {k}_x) - y \bm{\right)} dy\right|^2 \right\} d {k'}_x.
+  \end{aligned}
+\end{equation}
+Here an impurity average of white noise potential allows to identify $\expval{|V_{{k'}_x,k_x}|^2}_{imp} = V_{imp}$.
+Finally, using substitutions $k'_x = k_1$ and $y = \flatfrac{\hbar{k_2}}{(eB)}$, we can derive our expression for the inverse scattering time matrix for $N$-th Landau
+level as follows
+\begin{equation} \label{eq:43}
+  \begin{aligned}
+    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_{N} &=
+    \frac { \eta_{imp}^2 L_x^2 \hbar V_{imp}}{e^2B^2}
+    \delta(\varepsilon - \varepsilon_{N}) \\
+    & \times
+    \int_{-\infty}^{\infty} \left\{
+    J_l\bm{\left(}\frac{b\hbar}{eB}({k}_x - k_1)\bm{\right)}
+    J_{l'}\bm{\left(}\frac{b\hbar}{eB}({k}_x - k_1)\bm{\right)}
+    \left|
+    \int_{-\infty}^{\infty}
+    {\chi}_N\left(\frac{\hbar}{eB}k_2 \right)
+    {\chi}_N \bm{\left(}\frac{\hbar}{eB} (k_1 - k_x - k_2) \bm{\right)} dk_2 \right|^2 \right\} d k_1.
+  \end{aligned}
+\end{equation}
+\end{widetext}

### 2021-11-04 response/response.tex
Add physical significance to res

@@
 % Hypertext package
-\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=black,citecolor=blue]{hyperref}
+\usepackage{hyperref}
 % Bold math
@@
 % Bibliography style
-\bibliographystyle{abbrv}
+\bibliographystyle{unsrt}
 
@@
 
-In the initial version of the manuscript, we used natural units with $\hbar=k_B=1$ mainly because a similar system of units was used in Joulain \textit{et al.} \cite{mahan00} whose work we extend.
-Also, some of the widely used standard textbooks (e.g.
-Breuer \textit{et al.} \cite{breuer2002theory}) use a similar scheme.
-It was our belief at the time that it would have improved the readability of the manuscript for a reader well-versed in the relevant literature.
+We strongly agree with the reviewer that a reasoning on our theoritical results and their application in current nanoelectronic devices would be essential to the reader.
+Therefore, we have made a discussion on physical significance of our theoritical results and their possible employments in the optimization of nanoelectronic device performance.
+We have inserted a new Section VII to incorporate the above discussion into the manuscript.
+The total content of the section is given below,
 
-However we admit that the use of natural units would make it harder for some experimentally inclined readers as measurement instruments usually provide SI readings.
-To such a reader, mapping our simulated results with their corresponding experimental values by transforming the units would have been an additional task.
+{\color{Maroon}
+\subsection*{Physical significance of outcomes}
 
-Thus, as per your suggestion, we have mapped all natural units to their equivalent SI units in the revised manuscript.
-For comparison with earlier work (as per your Comment 2), we have taken the liberty of recreating the thermal transistor system analyzed by Joulain \textit{et al.} \cite{joulain2016quantum} and converting it also into SI units.
+With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \cite{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
+The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic system.
+The quantum Hall effects in a 2DEG under a static magnetic field are discribed by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
+This is due to the applied magnetic field and it changes the energy spectrum of 2DEG in a dramatic way.
+The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which is depend on the appplied magnetic field.
+However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening  in low temperatures is the disorders in materials \cite{ando85,dial07}.
+This behavour imply the  oscillating behavior of the experimental measurement of longitudinal conductivity (the Shubnikov–de Haas oscillations) \cite{endo09,wakabayashi78}.
 
-We detail these changes below.
+Our theoritical analysis on longitudinal conductivity behaviour of dressed quantum Hall system developed by consideirng low temperature limit with gaussian impurity broadening assumptions.
+As illustrated in Fig.
+4, we also able to demostrate same Shubnikov–de Haas conductivity oscillations as experimental results \cite{endo09,wakabayashi78} through our model.
+Under the undressed ($I=0$) condition, our results are overlap with the conductivity measurement for quantum Hall systems.
+However, from our results given in Fig.
+5, we demostrate that we are able to manipulate the broadening of these conductivity peaks using an external dressing field.
+In low temperature the principal cause of broadening of these conductivity peaks are impurity scattering and using an external dressing field we are able suppress the scattering which results in shrinkage both the scattering-induced broadening and the longitudinal conductivity.
 
-\begin{itemize}
-    \item Section IV first paragraph -
-        Changed to reflect the new SI system of units. - \\
-            {\color{Maroon} Note that in the following, we work in SI units where $\hbar=1.055\cross10^{-34} \text{Js}$ and $k_B=1.381\cross10^{-23} \text{J/K}$.}
-    \item Section IV-A fourth paragraph -
-        When moving to SI units, we had to insert conversion factors to deal with differently scaled energy levels, frequencies and temperatures.
-We have introduced Eq.~\ref{eq:unitequivalence} and the text below to establish these exact relationships.
-The factor of $5$ used there originates from the work of Joulain \textit{et al.} \cite{joulain2016quantum} and is verified further by our simulations.
-(The system energy levels need to be at least $5$ times higher for it to demonstrate the thermal transistor and optical-gating behaviors well.
-If the system energy levels were lower, the baths would have had enough energy to drive the conduction mechanism by its own, without the need for raised temperature $T_M$ or the optical field.
-Thus the optical gating action or thermal transistor action would diminish.) - \\
-            {\color{Maroon} Our next task is to select the appropriate system parameters.
-For proper operation, the overall scale of the system energy levels should be chosen to be around five times greater than the energy levels associated with the thermal baths \cite{joulain2016quantum}.
-Mathematically, this condition can be written as
-            \setcounter{equation}{24}
-            \begin{equation}
-                \hbar \omega \approx 5 k_B T
-                \label{eq:unitequivalence}
-            \end{equation}
-            where $\omega$ and $T$ represent the typical frequency and the temperature scales associated with the system and its environment.
-We then specify the relationships between different energy levels as $\omega_L=\omega_R=0$, $\omega_{RL}=0$, and $\omega_{LM}=\omega_{MR}\gg\omega_M>0$ to obtain a system whose energy level diagram is similar to Fig.
-2.
-This provides us with a relatively simple system while showcasing thermal gating behavior well.}
-\end{itemize}
+Research on novel states of matter has driven the evolution of present-day nanoelectronic devices.
+In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development  material science and technology \cite{ahn03,deng18}.
+Charge carrier concentration of a considering system is an imperative parameter that define the conductivity properties of system.
+We can manipulate that using the electrostatic field-effect machanism and it is an ideal tool to controll the conductivity in some specific systems.
+A 2DEG under static magnetic field with quantum Hall effects, is a excellent example that the gate electric field can be used to manipulate the conductivity.
+Considerable number researches has been performed using different type of 2D field-effect transistors(FETs) in magnetic fields to study the electronic transport in quantum limit \cite{wakabayashi78,yang18,long20,li14}.
+In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate volatage in black phosphorus FET under high magnetic fields in low temperatures.
+Since the Fermi level of the system can be altered with applied gate volatge, this behaviour can be easily map into our results given in Fig.
+4.
+However, specility of our outcomes is we owned the capability of manipulate the broadening of the conductivity regions using an external dressing field.
+Although Yang \textit{et al.} \cite{yang18}, achieved this broadening manipulation by changing the temperature in low range, in this study we present a general methematical describtion to perform that using only a high intensity electromagnetic field.
 
-\subsubsection*{Comment 2 -
-\color{RoyalBlue} As the proposed system is an extension of the one reported in
-reference \cite{joulain2016quantum}, authors should compare their results with the
-corresponding ones reported in that reference. In particular, the
-comparison of the amplification factors would be interesting.}
+As a result of manipulating the broadening of conductivity regions, we can enhance the sensitivity of FETs which gives the ability of observe narrow changes in gate volage.
 
-We agree with the reviewer that a comparison between the our optical-gating system and the device reported in \cite{joulain2016quantum} would be valuable to the reader.
+}
+
+%
+% \subsubsection*{Comment 2 -
+% \color{RoyalBlue} As the proposed system is an extension of the one reported in
+% reference \cite{joulain2016quantum}, authors should compare their results with the
+% corresponding ones reported in that reference. In particular, the
+% comparison of the amplification factors would be interesting.}
+%
+% We agree with the reviewer that a comparison between the our optical-gating system and the device reported in \cite{joulain2016quantum} would be valuable to the reader.
 However it is important to note that the previous device controlled the $J_L$ and $J_R$ heat flows via changing the temperature $T_M$ of the terminal $M$.
@@
 Therefore, we had to resort to the following methodology for our comparison.
-\begin{enumerate}
-    \item First we simulate both systems with the same bath temperatures $T_L$ and $T_R$, and same system parameters $\omega_P$s and $\omega_{PQ}$s. -
-    \begin{itemize}
-        \item We first reproduced the results of Joulain \textit{et al.} \cite{joulain2016quantum}.
+% \begin{enumerate}
+%     \item First we simulate both systems with the same bath temperatures $T_L$ and $T_R$, and same system parameters $\omega_P$s and $\omega_{PQ}$s. -
+%     \begin{itemize}
+%         \item We first reproduced the results of Joulain \textit{et al.} \cite{joulain2016quantum}.
 Since we use SI units for our work, we mapped all their parameters to SI units and generated corresponding results.
-        \item We then used the same parameter set as Joulain \textit{et al.} \cite{joulain2016quantum} to simulate our device.
-    \end{itemize}
-
-    \item Then, we find the control-parameter (i.e. $T_M$ for original system, $\Omega$ for our system) ranges within which each system shows the required thermal behaviors. -
-    \begin{itemize}
-        \item For the previous system, the original authors had found that the control range is between the lower bound $T_R$ and the upper bound $T_L$.
-        \item In our system the magnitude of $\Omega$ has the lower bound of zero, but does not have a hard upper bound.
+%         \item We then used the same parameter set as Joulain \textit{et al.} \cite{joulain2016quantum} to simulate our device.
+%     \end{itemize}
+%
+%     \item Then, we find the control-parameter (i.e. $T_M$ for original system, $\Omega$ for our system) ranges within which each system shows the required thermal behaviors. -
+%     \begin{itemize}
+%         \item For the previous system, the original authors had found that the control range is between the lower bound $T_R$ and the upper bound $T_L$.
+%         \item In our system the magnitude of $\Omega$ has the lower bound of zero, but does not have a hard upper bound.
 However we see from Fig.
@@
 We use this $\Omega$ value at saturation to define an approximate upper bound, which turns out to be around $3\Delta$ in our simulations.
-    \end{itemize}
-
-    \item Next, we simulate all output heat flows of each device for the full control-parameter range of that particular device. -
-    \begin{itemize}
-        \item For each system, we use a very small step-size and vary the control-parameter from its minimum value to its maximum value, and measure the output heat flows.
-        \item The resulting plots are shown in Fig.
+%     \end{itemize}
+%
+%     \item Next, we simulate all output heat flows of each device for the full control-parameter range of that particular device. -
+%     \begin{itemize}
+%         \item For each system, we use a very small step-size and vary the control-parameter from its minimum value to its maximum value, and measure the output heat flows.
+%         \item The resulting plots are shown in Fig.
 \ref{fig:energyflows2} and Fig.
@@
 We plot the values measured from the previous device with dashed lines, and values measured from our device with solid lines.
-    \end{itemize}
-\end{enumerate}
+%     \end{itemize}
+% \end{enumerate}
 

### 2021-11-04 response/response.tex
Add applications in res

@@
 With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \cite{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
-The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic system.
-The quantum Hall effects in a 2DEG under a static magnetic field are discribed by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
+The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
+The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
 This is due to the applied magnetic field and it changes the energy spectrum of 2DEG in a dramatic way.
-The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which is depend on the appplied magnetic field.
+The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
 However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low temperatures is the disorders in materials \cite{ando85,dial07}.
-This behavour imply the  oscillating behavior of the experimental measurement of longitudinal conductivity (the Shubnikov–de Haas oscillations) \cite{endo09,wakabayashi78}.
+This behavior implies the oscillating behavior of the experimental measurement of longitudinal conductivity (Shubnikov–de Haas oscillations) \cite{endo09,wakabayashi78}.
 
-Our theoritical analysis on longitudinal conductivity behaviour of dressed quantum Hall system developed by consideirng low temperature limit with gaussian impurity broadening assumptions.
+Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
 As illustrated in Fig.
-4, we also able to demostrate same Shubnikov–de Haas conductivity oscillations as experimental results \cite{endo09,wakabayashi78} through our model.
-Under the undressed ($I=0$) condition, our results are overlap with the conductivity measurement for quantum Hall systems.
+4, we were also able to demonstrate the same Shubnikov–de Haas conductivity oscillations as experimental results \cite{endo09,wakabayashi78} through our model.
+Under the undressed ($I=0$) condition, our results overlap with the conductivity measurement for quantum Hall systems.
 However, from our results given in Fig.
-5, we demostrate that we are able to manipulate the broadening of these conductivity peaks using an external dressing field.
-In low temperature the principal cause of broadening of these conductivity peaks are impurity scattering and using an external dressing field we are able suppress the scattering which results in shrinkage both the scattering-induced broadening and the longitudinal conductivity.
+5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+In low temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity.
 
 Research on novel states of matter has driven the evolution of present-day nanoelectronic devices.
-In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development  material science and technology \cite{ahn03,deng18}.
-Charge carrier concentration of a considering system is an imperative parameter that define the conductivity properties of system.
-We can manipulate that using the electrostatic field-effect machanism and it is an ideal tool to controll the conductivity in some specific systems.
-A 2DEG under static magnetic field with quantum Hall effects, is a excellent example that the gate electric field can be used to manipulate the conductivity.
-Considerable number researches has been performed using different type of 2D field-effect transistors(FETs) in magnetic fields to study the electronic transport in quantum limit \cite{wakabayashi78,yang18,long20,li14}.
-In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate volatage in black phosphorus FET under high magnetic fields in low temperatures.
-Since the Fermi level of the system can be altered with applied gate volatge, this behaviour can be easily map into our results given in Fig.
+In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
+The charge carrier concentration of a considering system is an imperative parameter that defines the conductivity properties of the system.
+We can manipulate that using the electrostatic field-effect mechanism and it is an ideal tool to control the conductivity in some specific systems.
+A 2DEG under static magnetic field with quantum Hall effects is an excellent example that the gate electric field can be used to manipulate the conductivity.
+A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the electronic transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
+In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under high magnetic fields in low temperatures.
+Since the Fermi level of the system can be altered with applied gate voltage, this behavior can be easily mapped into our results given in Fig.
 4.
-However, specility of our outcomes is we owned the capability of manipulate the broadening of the conductivity regions using an external dressing field.
-Although Yang \textit{et al.} \cite{yang18}, achieved this broadening manipulation by changing the temperature in low range, in this study we present a general methematical describtion to perform that using only a high intensity electromagnetic field.
+However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field.
+Although Yang \textit{et al.} \cite{yang18}, achieved this broadening manipulation by changing the temperature in a low range, in this study we present a general mathematical description to perform that using only a high-intensity electromagnetic field.
 
-As a result of manipulating the broadening of conductivity regions, we can enhance the sensitivity of FETs which gives the ability of observe narrow changes in gate volage.
+The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
+In a particular application that uses the switching operation of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
+As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field.
+This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
+Based on these available nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers great potential to realize advanced nanoelectronic devices.
+Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
 

### 2021-11-06 response/response.tex
Add differences to res

@@
 \usepackage{float}
+\usepackage{cite}
 
@@
 Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
+}
 
-}
+\subsubsection*{Comment 2 -
+\color{RoyalBlue} Moreover, this current research direction has a significant overlap with previous experimental and theoretical studies of quantum Hall systems that started with the observation of zero-resistance states in high mobility systems [Zudov et al, Phys.
+Rev.
+B 64, 201311 (2001), Mani et al, Phys.
+Rev.
+Lett.
+92, 146801 (2004)] and gave rise to theoretical models for the phenomenon [Durst et al, Phys.
+Rev.
+Lett.
+91, 086803 (2003), Dmitriev et al., Phys.
+Rev.
+B 71, 115316 (2005), Dmitriev et al, Phys.
+Rev.
+B 80, 165327 (2009)].
+The present manuscript needs to connect to various known phenomena discussed earlier in the literature on quantum Hall systems.}
+
+We thank the reviewer for pointing out that the nessisity of a comparison between the our theoritical model and previous discussions on transport properties of quantum Hall systems.
+Among the mentioned studies we can identify that experimental researches \cite{zudov01,mani02,zudov03,mani04} are specificly aim on the unusual oscillations of the magnetoresistance induced by the microwave (millimeterwave) radiation in 2DEG quantum Hall systems.
+These oscillations are know as \textit{microwave-induced resistance oscillations} (MIROs).
+To describe these behaviors Durst \textit{et al.} \cite{durst03} introduced a simple theoretical model assuming that the experimentally observed oscillations are a consequence of photoexcited disorder-scattered electrons.
+However, later a novel model was proposed in Ref.
+\cite{dmitriev03,dmitriev05,dmitriev09} considering the changes of the electron distribution function done by the microwave field.
+These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have succesfully describe the behavior of MIROs in experimentally relevent emperatures which was missed in previous model \cite{durst03}.
+Furthermore we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorbtion by electron in the considering system.
+However, in our theoritical model we consider higher frequencies than microwaves for the dressing field.
+Therefore we can clearly identify major dissimilarities between our system under the analysis and MIROs systems \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+We listed these dissimilarities as follows for our comparison.
+\begin{itemize}
+  \item
+  Dressing field frequency ($\omega \approx \SI{1}{\tera\hertz} \gg \SI{150}{\giga\hertz}$)
+  \item
+  Dressing field intensity  ($I \approx \SI{100}{\watt\per\square\centi\metre}$)
+  \item
+  Magnetic field intensity ($B \gg \SI{1}{\tesla}$). Their a weak magnetic field.
+  \item
+  Purely dressing field vs absorbtion.
+  \item
+  Quantum mechanical electron state absolute solutions because new electron ststes are created in our system.
+  \item
+  Polarization dependent of our system.
+  \item
+  We consdier only on SdH oscillations which are only important in low temperature limits.
+\end{itemize}
 

### 2021-11-07 response/response.tex
Add second comment res to res

@@
 \usepackage{cite}
+\usepackage{multicol}
+\usepackage{multirow}
 
@@
 However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low temperatures is the disorders in materials \cite{ando85,dial07}.
-This behavior implies the oscillating behavior of the experimental measurement of longitudinal conductivity (Shubnikov–de Haas oscillations) \cite{endo09,wakabayashi78}.
+This behavior implies the oscillating behavior of the experimental measurement of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
+\cite{endo09,wakabayashi78}.
 
@@
 As illustrated in Fig.
-4, we were also able to demonstrate the same Shubnikov–de Haas conductivity oscillations as experimental results \cite{endo09,wakabayashi78} through our model.
+4, we were also able to demonstrate the same SdH oscillations as experimental results \cite{endo09,wakabayashi78} through our model.
 Under the undressed ($I=0$) condition, our results overlap with the conductivity measurement for quantum Hall systems.
@@
   \item
-  Dressing field frequency ($\omega \approx \SI{1}{\tera\hertz} \gg \SI{150}{\giga\hertz}$)
+  The mentioned experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in microwave frequency range ($30 -\SI{150}{\giga\hertz}$).
+This leads to build the theoritical models presented in Ref.
+\cite{durst03,dmitriev03} by assuming that these oscillations are caused by photoexcited electrons.
+Since these models consider on relevant frequency range (microwave radiation), it will allow to acknowledge the photon absorbtion by electrons.
+In cotrast to that, our consideration is only focus on the systems with high frequency range dressing fields which will not be associated to any photon absorbtion.
   \item
-  Dressing field intensity  ($I \approx \SI{100}{\watt\per\square\centi\metre}$)
+  The applied microwave radiation power on the MIROs experiments \cite{mani02,zudov03} are varies around $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
+However, in our analysis we take the dressing field as a high intensity field, where we can not address the dressing field as a perturbation to our considering system.
+This leads us to use regonize new Floquet states together with conventinal Landau levels.
+As we mentioned in our results, we used high intensity dressing fields of magnitude around $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.
   \item
-  Magnetic field intensity ($B \gg \SI{1}{\tesla}$). Their a weak magnetic field.
+  These fascinating MIROs are only observed under the weak magnetic fields ($B < \SI{0.2}{\tesla}$) in the experiments performed in Ref.
+\cite{zudov01,mani02,zudov03,mani04}.
+In this range of weak magnetic fields we can only observe MIROs and Shubnikov–de Haas (SdH) oscillations reveal only on high intensity magnetic fields.
+In comaparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics.
+Thesefore in our analysis we aim on the effects induced by high intensity magnetic fields ($B \sim \SI{1}{\tesla}$).
   \item
-  Purely dressing field vs absorbtion.
-  \item
-  Quantum mechanical electron state absolute solutions because new electron ststes are created in our system.
-  \item
-  Polarization dependent of our system.
-  \item
-  We consdier only on SdH oscillations which are only important in low temperature limits.
+  In our work, we analysed the 2DEG quantum Hall system with high-intensity dressing field which does not contribute to the energy exchange between a high-frequency dressing field and electrons.
+Therefore we have assumed the applied electromagnetic radiation as a purely dressing field.
+There are two possible absorbtion mechanism in 2DEG quantum Hall system namely electron transitions bewtween distinct Landau levels and electron transitions between distinct states of a same broadened Landau level.
+To avoid these absorbtions we have tuned the dressing field to a high frequency in our system under the analysis.
+Furthermore due to high intensity dressing field, it will restructure the entire electronic states of the conventinal 2DEG quantum Hall systems.
+We have address these modifications throuth the Floquet theory.
+However, the MIROs models \cite{durst03,dmitriev03} are based on low frequecy case where the system is able to absorb low frequency photons from the field.
 \end{itemize}

### 2021-11-09 response/response.tex
Add res for comment 2 to res

@@
 
+Examine above mentioned points, we can clearly identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two particular natures of the magnetotransport properties.
+However, we identify that it is crusial to acknowledge these well-defined findings in MIROs and the their relatioship to the our considered system.
+We have added this clarification in the manuscript.
+
+\begin{itemize}
+        \item Section I - fifth paragraph (page 1):\\
+        {\color{Maroon}
+        In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
+        Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
+Recently, an experimental research on the effect of microwave illumination of 2DEG systems revealed microwave induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
+        This inspired investigations on theoretical description of MIROs and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+These analytical formalisms provide a good explanation of the experimental characteristics of MIROs.
+However, these experimental and theoretical works have been linked to the photon absorbtion from low-frequecy (microwave) fields.
+In contrast to that, high-frequency external illumination on 2DEG quantum Hall system need to be study as a purely dressing (nonabsorbable) field.
+        The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be descriped by a nonabsorbtion mechanism and it has escaped the researchers’ attention before.
+        Then, lately Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems for high-frequency case.
+However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
+In their study, they used the conductivity models from Refs.
+\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
+        }
+        \item Section VI - fifth paragraph (page 8):\\
+        {\color{Maroon}
+        By comparing the theoritical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78} studies on magnetoresistance of 2DEG qunatum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
+        These SdH oscillations shows $\hbar\omega_0$ periodicity with gate voltage and the periodicity of these oscillations are not effected by appplied dressing field frequency.
+It is important to state that the difference between SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering this frequency dependence on periodicity.
+In our case, the applied dressing field only change the the broadening of Landau levels and avoid any contribution towards the photon absorbtions.
+This will clearly describe the crusial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
+        }
+    \end{itemize}
+
 %

### 2021-11-09 paper/Submission/Manuscript/dressed_quantum_hall.tex
Rename folders
Add res for comment 2 to res

--- 2021-08-22 paper/Submission/dressed_quantum_hall/dressed_quantum_hall.tex
@@
 \includegraphics[scale=0.55]{fig_2_normalized_broadening_with_momentum}
-\caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
+\caption{\label{fig:2} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
 In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
@@
 \includegraphics[scale=0.54]{fig_3_normalized_broadening_with_intensity}
-\caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
+\caption{\label{fig:3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
 In this calculation, we have assumed that the natural broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
@@
 
-Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig_3} and Fig.~\ref{fig_4}.
+Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig:2} and Fig.~\ref{fig:3}.
 To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
@@
 
-As illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6}, we can manipulate the normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
+As illustrated in Fig.~\ref{fig:4} and Fig.~\ref{fig:5}, we can manipulate the normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
 For a given dressing field intensity, the longitudinal conductivity varies with  the Fermi level of the system showing sharp peaks at each Landau energy level.
@@
 In contrast, near each Landau level, the conductivity achieves excessive values compared to other areas.
-Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.
+Moreover, as illustrates in Fig.~\ref{fig:4}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.
 
 On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.
-When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:6}.
+When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:5}.
 However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
@@
 Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
-However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:4} and Fig.~\ref{fig:5} are generally incompatible with the results reported in Ref.~\cite{dini16}.
 This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
@@
 In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:5}
+\label{fig:4}
 \end{figure}
@@
 In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:6}
+\label{fig:5}
 \end{figure}
@@
   \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
-  \label{fig:2}
+  \label{fig:6}
 \end{figure}
-This phenomenon is illustrated in Fig.~\ref{fig:2}.
+This phenomenon is illustrated in Fig.~\ref{fig:6}.
 We can calculate the scattering amplitude for this scattering scenario using the expression derived in Eq.~(\ref{eq:c14}) as follows
@@
   \bibinfo {author} {\bibfnamefont {U.}~\bibnamefont {Zeitler}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Geim}}, \bibinfo {author}
+  {author} {\bibfnamefont {A.~K.}~\bibnamefont {Geim}}, \bibinfo {author}
   {\bibfnamefont {M.}~\bibnamefont {Henini}},\ and\ \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Maan}},\ }\href
+  {\bibfnamefont {J.~C.}~\bibnamefont {Maan}},\ }\href
   {https://doi.org/10.1103/PhysRevLett.78.4621} {\bibfield  {journal} {\bibinfo
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-  {Pan}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Xia}}, \bibinfo
-  {author} {\bibfnamefont {H.}~\bibnamefont {Stormer}}, \bibinfo {author}
-  {\bibfnamefont {D.}~\bibnamefont {Tsui}}, \bibinfo {author} {\bibfnamefont
-  {C.}~\bibnamefont {Vicente}}, \bibinfo {author} {\bibfnamefont
-  {E.}~\bibnamefont {Adams}}, \bibinfo {author} {\bibfnamefont
-  {N.}~\bibnamefont {Sullivan}}, \bibinfo {author} {\bibfnamefont
-  {L.}~\bibnamefont {Pfeiffer}}, \bibinfo {author} {\bibfnamefont
-  {K.}~\bibnamefont {Baldwin}},\ and\ \bibinfo {author} {\bibfnamefont
-  {K.}~\bibnamefont {West}},\ }\href
+  {Pan}}, \bibinfo {author} {\bibfnamefont {J.~S.}~\bibnamefont {Xia}}, \bibinfo
+  {author} {\bibfnamefont {H.~L.}~\bibnamefont {Stormer}}, \bibinfo {author}
+  {\bibfnamefont {D.~C.}~\bibnamefont {Tsui}}, \bibinfo {author} {\bibfnamefont
+  {C.~L.}~\bibnamefont {Vicente}}, \bibinfo {author} {\bibfnamefont
+  {E.~D.}~\bibnamefont {Adams}}, \bibinfo {author} {\bibfnamefont
+  {N.~S.}~\bibnamefont {Sullivan}}, \bibinfo {author} {\bibfnamefont
+  {L.~N.}~\bibnamefont {Pfeiffer}}, \bibinfo {author} {\bibfnamefont
+  {K.~W.}~\bibnamefont {Baldwin}},\ and\ \bibinfo {author} {\bibfnamefont
+  {K.~W.}~\bibnamefont {West}},\ }\href
   {https://doi.org/10.1103/PhysRevLett.95.066808} {\bibfield  {journal}

### 2021-11-09 response/response.tex
Add res for Q1 to res

@@
 
+\begin{itemize}
+  \item Section VII (page 8):\\
   {\color{Maroon}
@@
   }
+\end{itemize}
 
@@
 
+\subsubsection*{Comment 3 -
+\color{RoyalBlue} The manuscript will also provide more impact if it demonstrates how the new results can help to improve the future development of nanoelectronic devices.
+After these questions are addressed, the manuscript will be suitable for publication in Physical Review B.
+Otherwise, it will fit better to a more mathematically oriented journal.
+}
+
+We thank the reviewer for pointing out the importance of these facts that will help to elevate the value of our work.
+As we mentioned in the commnet 1, consideirng the important of discussing physical significance of our results, we added a new section(Section VII) to address these facts.
+
+\begin{itemize}
+  \item Section VII (page 8):\\
+  {\color{Maroon}
+  \subsection*{Physical significance of outcomes}
+
+  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \cite{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
+The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
+The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
+This is due to the applied magnetic field and it changes the energy spectrum of 2DEG in a dramatic way.
+The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
+  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low temperatures is the disorders in materials \cite{ando85,dial07}.
+This behavior implies the oscillating behavior of the experimental measurement of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
+\cite{endo09,wakabayashi78}.
+
+  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
+As illustrated in Fig.
+4, we were also able to demonstrate the same SdH oscillations as experimental results \cite{endo09,wakabayashi78} through our model.
+Under the undressed ($I=0$) condition, our results overlap with the conductivity measurement for quantum Hall systems.
+However, from our results given in Fig.
+5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+In low temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity.
+
+  Research on novel states of matter has driven the evolution of present-day nanoelectronic devices.
+In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
+  The charge carrier concentration of a considering system is an imperative parameter that defines the conductivity properties of the system.
+We can manipulate that using the electrostatic field-effect mechanism and it is an ideal tool to control the conductivity in some specific systems.
+  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that the gate electric field can be used to manipulate the conductivity.
+A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the electronic transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
+In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under high magnetic fields in low temperatures.
+Since the Fermi level of the system can be altered with applied gate voltage, this behavior can be easily mapped into our results given in Fig.
+4.
+However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field.
+Although Yang \textit{et al.} \cite{yang18}, achieved this broadening manipulation by changing the temperature in a low range, in this study we present a general mathematical description to perform that using only a high-intensity electromagnetic field.
+
+  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
+In a particular application that uses the switching operation of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
+As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field.
+This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
+Based on these available nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers great potential to realize advanced nanoelectronic devices.
+Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
+  }
+\end{itemize}
+
+\subsubsection*{Comment 4 -
+\color{RoyalBlue} The quantum Quantum Hall effect requires high mobility samples.
+In these samples, the structure of the disorder is usually complicated and combines both short-length potentials of impurities and long-length electrostatic inhomogeneities.
+The interplay of these components of disorder opens exciting questions about the transport properties of 2DEGs.
+What is the structure of disorder considered in the present manuscript and hidden in the notations for Vimp?
+What are the conditions for validity of eq.
+(15)?
+}
+
+We thank the reviewer for raising this important question.
+In our previous manuscript, we have presented the detailed derivation of Eq.~[15] with a discusssion on models of disorder under the Appendix C.
+However we will discuss our selection of disorder model and approximations made to derive the Eq.~[15] here as well.
+
+We modeled the effect caused by impurities in the considered system as a single perturbation potential.
+Analyzing the electric propeties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
+Therefore, in this study we consider on the statistically averaged propeties of 2DEG over impurity configurations.
+In addition, we consider only the our considering static disorder corresponds to the situation in which the electrons scatter elastically.
+First, we adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the considering system and we approximate this into a Gaussian white noise.
+
+Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
+Thus, we can describe the scattering potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
+\begin{equation} \label{eq:1}
+  V(\vb{r}) =
+  \sum_{i=1}^{N_{imp}}
+  \upsilon (\vb{r}-\vb{r}_i).
+\end{equation}
+Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
+This model is characterized by the following two equations \cite{akkermans10}
+\begin{subequations}
+\begin{equation} \label{eq:2}
+  \expval{\upsilon(\vb{r})}_{imp} =0,
+\end{equation}
+\begin{equation} \label{eq:3}
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
+\end{equation}
+\end{subequations}
+where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
+In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
+Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
+\begin{equation} \label{eq:4}
+  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
+\end{equation}
+where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
+\begin{equation} \label{eq:5}
+  V(\vb{r}) =
+  \sum_{i=1}^{N_{imp}}
+  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
+\end{equation}
+
+Then we calculate the Floquet-Fermi golden rule for a dressed quantum Hall system using this perturbative impurity potential.
+In the derivation we have defined the $V_{imp}$ value which is constant in moemntum space.
+It is a propety of Gaussian white noise impurity distribution \cite{akkermans10,wackerl20}.
+However, throughout the derivation we use only the first order contribution (Born approximation) of the impurity potential.
+All the detailed step for the derivation of the Floquet-Fermi golden rule for a dressed quantum Hall system are included in Appendix C.
+
+Since previous studies on Floquet-Drude consuctivity \cite{wackerl20}, and magnetotransport propeties in dressed qunatum Hall systems \cite{dini16} have  used this perticular Gaussian white noise potential, we also selected this pertucular impurity model to describe our system.
+This open a path to compare our analytical outcomes with these previous models.
+
+Since we have not mentioned the validity conditions we used to derive the Eq.~[15] in the main text of the previous manuscript, we have added validity conditions to the new manuscript.
+
+\begin{itemize}
+  \item Section IV - first paragraph (page 4):\\
+  {\color{Maroon}
+  The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
+  However, this theory has not been applied for a dressed quantum Hall system in the previous studies.
+In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
+  With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(14), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
+  \begin{equation} \label{eq:15}
+    \begin{aligned}
+      \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N =
+      \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N)
+      \int_{-\infty}^{\infty} &
+      J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+      J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
+      \\
+      & \times
+      \left|
+      \int_{-\infty}^{\infty}
+      \chi_N \left( \frac{\hbar}{eB}k_2 \right)
+      \chi_N \bm{\left(} \frac{\hbar}{eB}
+      \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
+      dk_2 \right|^2 d k_1,
+    \end{aligned}
+  \end{equation}
+  where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
+  A more detailed derivation is given in Appendix C.
+  We modeled the effect caused by impurities in the considered system as a single perturbation potential.
+Analyzing the electric propeties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
+  Furthermore, we assumed that our perturbation potential is formed by a group of randomly distributed impurities under the Edwards impurity model \cite{akkermans10,wackerl20}.
+  Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+Then we  approximate the impurity potential into a Gaussian white noise \cite{akkermans10,wackerl20}.
+  Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
+  Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
+In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential and
+  }
+\end{itemize}
+
 %
@@
 
+\newpage
 \bibliography{response}

### 2021-11-09 response/response.tex
Corrections

@@
 In our previous manuscript, we have presented the detailed derivation of Eq.~[15] with a discusssion on models of disorder under the Appendix C.
-However we will discuss our selection of disorder model and approximations made to derive the Eq.~[15] here as well.
+However we will discuss on our selection of disorder model and approximations made to derive the Eq.~[15] here as well.
 
@@
 
-Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly distributed impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
+Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly localized impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
 Thus, we can describe the scattering potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
@@
 This open a path to compare our analytical outcomes with these previous models.
+As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the magnetotransport properties of dressed qunatum Hall system would be an interesting future research possibility.
 

### 2021-11-09 response/response.tex
Corrections

@@
 
+\subsubsection*{Comment 5 -
+\color{RoyalBlue} If continuous illumination is applied to an electron system, the system will heat indefinitely.
+The distribution function is stabilized when the electron-electron and electron-phonon scattering mechanisms are included.
+What are the conditions of validity for eqs.
+(33-34)?
+The deviations of the distribution function from its equilibrium result in effects that can significantly overcome the equilibrium contributions, see Dmitriev et al, Phys.
+Rev.
+B 80, 165327 (2009).
+However, to capture these effects, a treatment within Floquet-Drude formalism is insufficient and a complete quantum kinetic equation has to be analyzed.
+Can the authors argue why their results still present some interest to the community even if they potentially disregard more significant contributions?
+}
+
+This is a good, valid question.
+First, we discuss the validity of the Eq.~[33] and Eqq.~[34].
+In our analysis we have derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
+Then we selected an special scenario where we assumed that the system is under low temperature limit.
+Since previous theoritical studies on magnetotransport propeties of 2DEG quantum Hall systems were derived under this assumption, we selected this conditions to provide a better comparison with their outcomes.
+In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing tempurature, we can identify the decaying behaviour of SdH oscillations.
+Therefore, if we need to maintain a good oscillator behavior we need to work in low temperatures.
+Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, we have extend our general derivation in given Eq.~[31] into a simple expression for low temperature case.
+On the other hand, under the off-resonant condition, absorption of photons is avoided, and we can choose the the Fermi-Dirac distribution as our partical distribution function in Eq.~[31] as given in Eq.~[33].
+Under low temperature assumption, we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy as given mentioned in the Eq.~[34].
+Applying these two conditions, we can simplify our derivation into new expression that can be compared with previous studies on magnetotransport in dressed quantum Hall systems.
+
+Yes, it is true that when we consider the experimental observations of a qunatum Hall system a strong dressing field can increase the temperature of the sample.
+However, as mentioned in previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low temperature by applying narroaw pulses of a strong dressing field to observe the discussed phenomena.
+
+Although we have extend our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoritical model into different type of partical distribution functions.
+As discussed by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion need to address the changes in distribution functions in our derived general longitudinal conductivity formula and this would be an interesting extension to our study.
+
+\subsubsection*{Comment 6 -
+\color{RoyalBlue} The authors presented the results for the conductivity tensor's xx- and yy-components.
+They seem to be identical, apart of a dimensional factor $(eB)^2$ in the denominator.
+The equality of these two components is expected for isotropic systems.
+Does the polarization of the electromagnetic field break the isotropy?
+Do the two components of the conductivity remain equal even for an arbitrary direction of a linearly polarized field?
+Is there a non-Hall contribution to the xy-component?
+}
+
 %

### 2021-11-10 response/response.tex
Finish reviewer 1 to res

@@
 
+For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
+The Floquet-Drude conductivity formula was only developed for the diogonal components of the conductivity tensor of the considering system.
+In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diogonal components of the conductivity tensor.
+
+As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the qunatum state of the consideirng system and creates novel states called Floquet states.
+The propeties of these states are depends on the characteristics of applied dressing field.
+Therefore, the polarization method also change the behavior of the Floquet states.
+These polarization dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields.
+In addition, they have mentioned the impact on the direction of the linearly polarization dressing field and this will break the isotropy behaviour of the longitudinal conductivities in the consideirng system.
+
+We also followed the same formalism of Floquet states for 2DEG quantum Hall systems.
+In our work also we were able to identify that the applied dressing field's polarization direction can be effect the magnitude of the longitudinal conductivity component.
+A detailed derivation of these two longitudinal conductivity component's current operators are given in Appendix D.
+If we applied a arbitary directional polarized dressing field, we can derive a expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with same steps in this analysis.
+This would change the amplitude of the considering dressing field ($E$) in each direction.
+However, now there will be a new conponent in parallel to the considering conductivity component and we need to solve the Schrödinger equation with the modified Hamiltonian in Eq.~[2] for the new system with these changes.
+However in our analysis, our main objective was to identify the manipulation capabilities of SdH oscillations using dressing field intensity.
+In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diogonal components in conductivity tensor.
+Therefore we are unable to predict the off-diogonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.
+
 %

### 2021-11-10 response/response.tex
Add comment 1 to rev2 to res

@@
   {\color{Maroon}
-  By comparing the theoritical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78} studies on magnetoresistance of 2DEG qunatum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
-  These SdH oscillations shows $\hbar\omega_0$ periodicity with gate voltage and the periodicity of these oscillations are not effected by appplied dressing field frequency.
-It is important to state that the difference between SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering this frequency dependence on periodicity.
-In our case, the applied dressing field only change the the broadening of Landau levels and avoid any contribution towards the photon absorbtions.
+  By comparing the theoritical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on magnetoresistance of 2DEG qunatum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
+  As observed in the experimental work by Caviglia \textit{et al.} \cite{caviglia10}, SdH oscillations period is only depend on the perpendicular component of the applied magnetic field.
+  Therefore, we can identify that many experiments done in low temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with different type of 2DEG has been oberved these SdH oscillations against applied magnetic field.
+  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the consdiering system.
+  Therefore we can achieve the same oscillation behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
+Due to the change of the gate volatge applied to the system will modify the Fermi level of the system.
+  Since the Landau level energy is only depend on the cyclotron frequency, this will generate the same SdH oscillations against gate volatage.
+  This osillating behavior with applied gate volatge has been observed in experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+With comparing these empirical observations with our results given in Fig[4], we can easly identify that our oscillations are also shows the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
+Furthermore, when we increase the gate volatge, the Fermi level of the system get increased.
+This will locate to the the Fermi level on higher order Landau levels.
+As illustrated in Fig.~[4], this will result a higher conductivity peak value at higher order Landau level.
+This same behaviour also observed in the experimental observations presented in Ref.
+\cite{wakabayashi78} as well.
+However, in our analysis we have analytically explained the controllability of these conductivity regions using a dressing field.
+  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered a number of remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
+However these experiments and theoritical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorbtion from the applied low-frequency field.
+  It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
+In our case, the applied dressing field is in off-resonant range and that will only change the the broadening of Landau levels and avoid any contribution towards the photon absorbtions.
 This will clearly describe the crusial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
+Therefore our approach can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
   }
@@
 
+\subsection*{Response to the comments of Reviewer 2}
+
+We would like to thank the reviewer for his/her insightful comments our work.
+To address your comments, we had to add new materials and reorganize our text.
+As a result we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis.
+We hence believe that both the presentation and scientific content of this manuscript is of a much higher quality than our previous submission.
+We hope our response, and the corresponding changes we incorporated to the manuscript would be sufficient to clarify the issues raised.
+
+\subsubsection*{Comment 1 -
+\color{RoyalBlue} The paper is very low on comparison with experiments, for which there is a large amount of data available for the zero radiation case.
+I would like to see detailed analysis of how Figs 4 and 5 compare with available
+experimental data. Without this addition, physical relevance of such
+detailed calculations is questionable.
+}
+
+We thank the reviewer for pointing out the importance of this fact.
+To overcome this shortage of discussion we made a detailed analysis on our results against the undressed 2DEG quantum Hall system behavior.
+We have inserted this discussion into the our manuscript under Section VI.
+
+\begin{itemize}
+  \item Section VI - fifth paragraph (page 8):\\
+  {\color{Maroon}
+  By comparing the theoritical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on magnetoresistance of 2DEG qunatum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
+  As observed in the experimental work by Caviglia \textit{et al.} \cite{caviglia10}, SdH oscillations period is only depend on the perpendicular component of the applied magnetic field.
+  Therefore, we can identify that many experiments done in low temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with different type of 2DEG has been oberved these SdH oscillations against applied magnetic field.
+  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the consdiering system.
+  Therefore we can achieve the same oscillation behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
+Due to the change of the gate volatge applied to the system will modify the Fermi level of the system.
+  Since the Landau level energy is only depend on the cyclotron frequency, this will generate the same SdH oscillations against gate volatage.
+  This osillating behavior with applied gate volatge has been observed in experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+With comparing these empirical observations with our results given in Fig[4], we can easly identify that our oscillations are also shows the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
+Furthermore, when we increase the gate volatge, the Fermi level of the system get increased.
+This will locate to the the Fermi level on higher order Landau levels.
+As illustrated in Fig.~[4], this will result a higher conductivity peak value at higher order Landau level.
+This same behaviour also observed in the experimental observations presented in Ref.
+\cite{wakabayashi78} as well.
+However, in our analysis we have analytically explained the controllability of these conductivity regions using a dressing field.
+  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered a number of remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
+However these experiments and theoritical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorbtion from the applied low-frequency field.
+  It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
+In our case, the applied dressing field is in off-resonant range and that will only change the the broadening of Landau levels and avoid any contribution towards the photon absorbtions.
+This will clearly describe the crusial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
+Therefore our approach can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
+  }
+\end{itemize}
+
 %

### 2021-11-10 response/response.tex
Add comment 5 to rev2 to res

@@
   {\color{Maroon}
-  \subsection*{Physical significance of outcomes}
+  \subsection*{Physical significance of the outcomes}
 
@@
 
+\newpage
 \subsection*{Response to the comments of Reviewer 2}
@@
 
-%
-% \subsubsection*{Comment 2 -
-% \color{RoyalBlue} As the proposed system is an extension of the one reported in
-% reference \cite{joulain2016quantum}, authors should compare their results with the
-% corresponding ones reported in that reference. In particular, the
-% comparison of the amplification factors would be interesting.}
-%
-% We agree with the reviewer that a comparison between the our optical-gating system and the device reported in \cite{joulain2016quantum} would be valuable to the reader.
-However it is important to note that the previous device controlled the $J_L$ and $J_R$ heat flows via changing the temperature $T_M$ of the terminal $M$.
-In contrast, we employ the driving strength of the field $F$, or in other words its Rabi frequency $\Omega$, to control the same heat flows.
-Even though the two devices are basically identical in the output side, they are quite different on the input side.
-This makes a simple, direct comparison of the two devices impossible.
-Therefore, we had to resort to the following methodology for our comparison.
-% \begin{enumerate}
-%     \item First we simulate both systems with the same bath temperatures $T_L$ and $T_R$, and same system parameters $\omega_P$s and $\omega_{PQ}$s. -
-%     \begin{itemize}
-%         \item We first reproduced the results of Joulain \textit{et al.} \cite{joulain2016quantum}.
-Since we use SI units for our work, we mapped all their parameters to SI units and generated corresponding results.
-%         \item We then used the same parameter set as Joulain \textit{et al.} \cite{joulain2016quantum} to simulate our device.
-%     \end{itemize}
-%
-%     \item Then, we find the control-parameter (i.e. $T_M$ for original system, $\Omega$ for our system) ranges within which each system shows the required thermal behaviors. -
-%     \begin{itemize}
-%         \item For the previous system, the original authors had found that the control range is between the lower bound $T_R$ and the upper bound $T_L$.
-%         \item In our system the magnitude of $\Omega$ has the lower bound of zero, but does not have a hard upper bound.
-However we see from Fig.
-\ref{fig:energyflows2}, that our system eventually saturates for large $\Omega$ values, after which increasing $\Omega$ further has minimal effect on the heat flows.
-We use this $\Omega$ value at saturation to define an approximate upper bound, which turns out to be around $3\Delta$ in our simulations.
-%     \end{itemize}
-%
-%     \item Next, we simulate all output heat flows of each device for the full control-parameter range of that particular device. -
-%     \begin{itemize}
-%         \item For each system, we use a very small step-size and vary the control-parameter from its minimum value to its maximum value, and measure the output heat flows.
-%         \item The resulting plots are shown in Fig.
-\ref{fig:energyflows2} and Fig.
-\ref{fig:energyefficiency}.
-Each plot have a single vertical axis, and two horizontal axes.
-The top horizontal axis measures $T_M$ and corresponds to the device of Joulain \textit{et al.} \cite{joulain2016quantum}, while the bottom axis measures $\Omega$ and corresponds to our system.
-We plot the values measured from the previous device with dashed lines, and values measured from our device with solid lines.
-%     \end{itemize}
-% \end{enumerate}
+\subsubsection*{Comment 2 -
+\color{RoyalBlue} In the presence of disorder, Anderson localization and topologically protected edge modes are dominant considerations when calculating DC transport coefficients.
+How are these factors taken into account?
+}
+
+\subsubsection*{Comment 3 -
+\color{RoyalBlue} Can the authors reproduce the quantized Hall conductance of filled Landau levels in the presence of disorder? Please discuss.
+}
+
+\subsubsection*{Comment 4 -
+\color{RoyalBlue} The way some previous works are cited is disappointing.
+Example from page 8: “Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.” This is not informative.
+Where, specifically, did results from earlier works fall short of reality, which have been better addressed in this work?
+}
+
+\subsubsection*{Comment 5 -
+\color{RoyalBlue} Adding some physical insight into the remarkable observation of radiation-induced narrowing of lineshapes (Figs 4, 5) will help elevate
+this work.
+}
+
+We agree with the reviewer that a discussion on our theoritical results and their physical significance into modern nanoelectronic devices is a vital requirement.
+We have added a new Section VII to overcome the above mentioned deficiency of our manuscript.
+The total content of the section is given below,
+
+\begin{itemize}
+  \item Section VII (page 8):\\
+  {\color{Maroon}
+  \subsection*{Physical significance of the outcomes}
+
+  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \cite{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
+The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
+The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
+This is due to the applied magnetic field and it changes the energy spectrum of 2DEG in a dramatic way.
+The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
+  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low temperatures is the disorders in materials \cite{ando85,dial07}.
+This behavior implies the oscillating behavior of the experimental measurement of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
+\cite{endo09,wakabayashi78}.
+
+  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
+As illustrated in Fig.
+4, we were also able to demonstrate the same SdH oscillations as experimental results \cite{endo09,wakabayashi78} through our model.
+Under the undressed ($I=0$) condition, our results overlap with the conductivity measurement for quantum Hall systems.
+However, from our results given in Fig.
+5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+In low temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity.
+
+  Research on novel states of matter has driven the evolution of present-day nanoelectronic devices.
+In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
+  The charge carrier concentration of a considering system is an imperative parameter that defines the conductivity properties of the system.
+We can manipulate that using the electrostatic field-effect mechanism and it is an ideal tool to control the conductivity in some specific systems.
+  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that the gate electric field can be used to manipulate the conductivity.
+A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the electronic transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
+In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under high magnetic fields in low temperatures.
+Since the Fermi level of the system can be altered with applied gate voltage, this behavior can be easily mapped into our results given in Fig.
+4.
+However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field.
+Although Yang \textit{et al.} \cite{yang18}, achieved this broadening manipulation by changing the temperature in a low range, in this study we present a general mathematical description to perform that using only a high-intensity electromagnetic field.
+
+  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
+In a particular application that uses the switching operation of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
+As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field.
+This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
+Based on these available nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers great potential to realize advanced nanoelectronic devices.
+Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
+  }
+\end{itemize}
 

### 2021-11-11 response/response.tex
Add corrections to xx-yy components to res

@@
 
-For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
+We thank the reviewer for pointing out the importance mistake we have made in the $yy$-component calculation.
+We have made an mistake in the current operator calculations and this has leaded to a unexpected normalization factor in the conductivity expresiion.
+Since we have only analyzed the $xx$-component this is not used to any further calculations and remaining analysis is not effected by this change.
+After this changes we can predict that the both $xx$-component and $yy$-component shows the same conductivity behaviours.
+We added these changes to the calculations done in Appendix D and the conductivity calculation under Section V.
+
+\begin{itemize}
+  \item Appendix D - (page 14):\\
+  {\color{Maroon}
+  \subsection*{\label{appendix_d}Current operators for a dressed quantum Hall system}
+
+  In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system.
+We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(1) and we identified them as the Floquet states in Eq.~(14).
+For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(10) as quantum states using their corresponding quantum numbers as follows
+  \begin{equation} \tag{D1}
+    \ket{\phi_{n,m}} = \ket{n,k_x}.
+  \end{equation}
+  Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
+  \begin{equation} \tag{D2}
+    \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
+  \end{equation}
+  Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
+  \begin{equation} \tag{D3}
+    \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
+  \end{equation}
+  where $\widetilde{m}$ is the mass of the considering particle.
+
+  First, we consider the $x$-directional particle current operator component, and we can identify that as
+  \begin{equation} \tag{D4}
+    \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
+  \end{equation}
+  Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
+  \begin{equation} \tag{D5}
+    \left({j}_x \right)_{nm,n'm'} =
+    \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
+  \end{equation}
+  and we evaluate these using the Floquet modes derived in Eq.~(7) as follows
+  \begin{equation} \tag{D6}
+    \begin{aligned}
+      \left({j}_x \right)_{nm,n'm'} = &
+      \frac{1}{{\widetilde{m}}}
+      \delta_{k_x,k'_x}
+      \int
+      \left(\hbar k'_x + eBy\right) \\
+      & \times
+       \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
+      \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
+      dy.
+    \end{aligned}
+  \end{equation}
+  Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
+  \begin{equation} \tag{D7}
+    \begin{aligned}
+      \left({j}_x \right)_{nm,n'm'} =
+      \frac{1}{{\widetilde{m}}}
+      \delta_{k_x,k'_x}
+      \int &
+      \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right]
+      \chi_{n}(\bar{y})
+      \chi_{n'}(\bar{y})
+      d\bar{y}.
+    \end{aligned}
+  \end{equation}
+  Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
+  \begin{equation} \tag{D8}
+    \int
+    \chi_{n}({y})
+    \chi_{n'}({y}) d{y} =
+    \kappa\delta_{n',n},
+  \end{equation}
+  \begin{equation} \tag{D9}
+    \int
+    y \chi_{n}({y})\chi_{n'}({y}) d{y} =
+    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+    \delta_{n',n-1} \right),
+  \end{equation}
+  we simplify the matrix elements of $x$-directional current operator to obtain
+  \begin{equation} \tag{D10}
+    \begin{aligned}
+      &\left({j}_x \right)_{nm,n'm'} =
+      \frac{eB}{{\widetilde{m}}}
+      \delta_{k_x,k'_x}
+      \left[
+      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+      \delta_{n',n-1}\right)
+      + \zeta(t) \delta_{n',n}
+      \right].
+    \end{aligned}
+  \end{equation}
+  Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
+  \begin{equation} \tag{D11}
+    \begin{aligned}
+        \left({j}_x \right)_{nm,n'm'} =&
+        \frac{eB}{\widetilde{m}}
+        \delta_{k_x,k'_x}
+        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+        \delta_{n',n-1} \right).
+    \end{aligned}
+  \end{equation}
+  For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
+  \begin{equation} \tag{D12}
+    \begin{aligned}
+        \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
+        \frac{e^2B}{{m_e}}
+        \delta_{k_x,k'_x}
+        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
+        \delta_{n',n-1} \right).
+    \end{aligned}
+  \end{equation}
+
+  Moreover, we can identify the $y$-directional current operator component as
+  \begin{equation} \tag{D13}
+    \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
+  \end{equation}
+  Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
+  \begin{equation} \tag{D14}
+    \left({j}_y \right)_{nm,n'm'} =
+    \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
+  \end{equation}
+  After following the same steps done for the $x$-directional current operator, and recursion relation of the first derivative of Gauss-Hermite functions
+  \begin{equation} \tag{D15}
+    \begin{aligned}
+      \pdv{\chi_{n}({y})}{y} =
+      \kappa\left[
+      -  \sqrt{\frac{n+1}{2}} \chi_{n+1}({y})
+      +  \sqrt{\frac{n}{2}} \chi_{n - 1}({y})
+      \right],
+    \end{aligned}
+  \end{equation}
+  we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
+  \begin{equation} \tag{D16}
+    \begin{aligned}
+      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
+      \frac{ie\hbar\kappa^2}{m_e}
+      \delta_{k_x,k'_x}
+      \left(
+      \sqrt{\frac{n}{2}} \delta_{n',n-1}
+      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
+      \right).
+    \end{aligned}
+  \end{equation}
+  \begin{equation} \tag{D17}
+    \begin{aligned}
+      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
+      \frac{ie^2 B}{m_e}
+      \delta_{k_x,k'_x}
+      \left(
+      \sqrt{\frac{n}{2}} \delta_{n',n-1}
+      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
+      \right).
+    \end{aligned}
+  \end{equation}
+  }
+  \item Section V - (page 7):\\
+  {\color{Maroon}
+  Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
+  \begin{equation} \tag{36}
+    \begin{aligned}
+      {\sigma}^{yy} =
+      \frac{e^2}{\pi\hbar A} &
+      \sum_{n}
+      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
+      \left[
+        \frac{1}
+        {
+          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
+        }
+      \right]
+      \left[
+        \frac{1}
+        {
+          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
+        }
+      \right].
+    \end{aligned}
+  \end{equation}
+  }
+\end{itemize}
+
+% For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
 The Floquet-Drude conductivity formula was only developed for the diogonal components of the conductivity tensor of the considering system.
 In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diogonal components of the conductivity tensor.
-
-As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the qunatum state of the consideirng system and creates novel states called Floquet states.
+%
+% As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the qunatum state of the consideirng system and creates novel states called Floquet states.
 The propeties of these states are depends on the characteristics of applied dressing field.
 Therefore, the polarization method also change the behavior of the Floquet states.
-These polarization dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields.
+% These polarization dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields.
 In addition, they have mentioned the impact on the direction of the linearly polarization dressing field and this will break the isotropy behaviour of the longitudinal conductivities in the consideirng system.
-
-We also followed the same formalism of Floquet states for 2DEG quantum Hall systems.
+%
+% We also followed the same formalism of Floquet states for 2DEG quantum Hall systems.
 In our work also we were able to identify that the applied dressing field's polarization direction can be effect the magnitude of the longitudinal conductivity component.
@@
 However, now there will be a new conponent in parallel to the considering conductivity component and we need to solve the Schrödinger equation with the modified Hamiltonian in Eq.~[2] for the new system with these changes.
-However in our analysis, our main objective was to identify the manipulation capabilities of SdH oscillations using dressing field intensity.
+% However in our analysis, our main objective was to identify the manipulation capabilities of SdH oscillations using dressing field intensity.
 In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diogonal components in conductivity tensor.
@@
 }
+
+We agree with the reviewer that the discussion on the Anderson localization and topologically protected edge modes are was missing from the manuscript.
+We would like to mentioned the reviewer that while deriving Eq.~[31], we have assumed that the applyed static magnetic field is placed in a lower intensity range where we can neglect a number of effects known to appear in a 2DEG quantum Hall system.
+Under this condition we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions and the spin splitting as well.
+As mentioned in the work done by Endo \textit{et al.} \cite{endo09}, under the given magnetic field range, the undressed magnetotransport properties of GaAs/AlGaAs 2DEG quantum Hall system provides excellent agrrement between the experimental observations and theory.
+The authors of the Ref.\cite{endo09} has neglect the effects mentioned above during the development the theory.
+We also follwed the same theoritical derivation with given assumtions but with a additionl dressing field.
+Our results for undressed system gives a better aggrement with the results from Ref.\cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks.
+We have added this clarification in the manuscript.
+
+\begin{itemize}
+  \item Section I - sixth paragraph (page 2):\\
+  {\color{Maroon}
+  It is important to note that, in this analysis we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting and the electron–electron interactions can be neglected.
+The use of this assumption can also be found in study done by  Endo \textit{et al.} \cite{endo09}.
+  }
+  \item Section VIII - sixth paragraph (page 2):\\
+  {\color{Maroon}
+  We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within a order where we can neglect effects of the the Anderson localization, the formation of the edge states, the spin splitting and the electron–electron interactions.
+  }
+\end{itemize}
 

### 2021-11-12 response/response.tex
Add corretions to xx yy to res

@@
 We have made an mistake in the current operator calculations and this has leaded to a unexpected normalization factor in the conductivity expresiion.
-Since we have only analyzed the $xx$-component this is not used to any further calculations and remaining analysis is not effected by this change.
-After this changes we can predict that the both $xx$-component and $yy$-component shows the same conductivity behaviours.
+Since we have only analyzed the normalized $xx$-component of the conductivity tensor, the remaining analysis is not effected by this change.
+After this change we can predict that the both $xx$-component and $yy$-component shows the same conductivity behaviours.
 We added these changes to the calculations done in Appendix D and the conductivity calculation under Section V.
@@
     \chi_{n'}({y}) d{y} =
-    \kappa\delta_{n',n},
+    \delta_{n',n},
   \end{equation}
@@
     y \chi_{n}({y})\chi_{n'}({y}) d{y} =
+    \frac{1}{\kappa}
     \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
@@
       &\left({j}_x \right)_{nm,n'm'} =
-      \frac{eB}{{\widetilde{m}}}
+      \frac{eB}{{\widetilde{m}\kappa}}
       \delta_{k_x,k'_x}
@@
         \left({j}_x \right)_{nm,n'm'} =&
-        \frac{eB}{\widetilde{m}}
+        \frac{eB}{\widetilde{m}\kappa}
         \delta_{k_x,k'_x}
@@
         \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
-        \frac{e^2B}{{m_e}}
+        \frac{e\hbar}{{m_e}l_0}
         \delta_{k_x,k'_x}
@@
   \end{equation}
+  where $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$ is the magnetic length.
 
@@
       \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
-      \frac{ie\hbar\kappa^2}{m_e}
+      \frac{ie\hbar\kappa}{m_e}
       \delta_{k_x,k'_x}
@@
       \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
-      \frac{ie^2 B}{m_e}
+      \frac{ie \hbar}{m_e l_0}
       \delta_{k_x,k'_x}
@@
   {\color{Maroon}
+  Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(31) leads to
+  \begin{equation} \label{eq:35}
+    \begin{aligned}
+      \sigma^{xx}  =
+      \frac{e^2l_0^2}{\pi\hbar A}
+      \sum_{n}
+      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
+      \left[
+        \frac{1}
+        {
+          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
+        }
+      \right]
+      \left[
+        \frac{1}
+        {
+          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
+        }
+      \right],
+    \end{aligned}
+  \end{equation}
+  where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$,
+  $\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$, and $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$.
   Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
-  \begin{equation} \tag{36}
+  \begin{equation} \label{eq:36}
     \begin{aligned}
       {\sigma}^{yy} =
-      \frac{e^2}{\pi\hbar A} &
+      \frac{e^2l_0^2}{\pi\hbar A}
       \sum_{n}
@@
 
+For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
+The Floquet-Drude conductivity formula was only developed for the diogonal components of the conductivity tensor of the considering system.
+In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diogonal components of the conductivity tensor through Floquet-Drude conductivity formula.
+Therefore we are unable to predict the off-diogonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.
+However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behaviour of off-diogonal components of the conductivity tensor.
+As mentioned in the Ref.~\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations
+\begin{equation} \nonumber
+  \dv{\widetilde{\sigma}^{xy}(X_F,I)}{B} \approx
+    \pi\mu \frac{\hbar \omega_0}{\varepsilon_F} [\widetilde{\sigma}^{xx}(X_F,I)]^2.
+\end{equation}
+By comparing the resultion between longitudinal and transverse conductivities in 2DEG quantum Hall system, we can expect the same Hall conductivity behaviour in a dressed quantum Hall system.
+However, using the dressing field we are able to squeeze the conductivity peaks on Landau levels.
+This will reduce the region of high conductivity peaks placed near the Landau levels.
+This will imply sudden Hall conductivity transitions between one plateau to another one near a Landau level.
+As empherical observation showed in Ref.
+\cite{klitzing80,gusynin06}, we can predict a staircase behavior for quantum Hall conductivity but with higher intensity dressing field we will get rapid transitions then the undressed system.
+However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulate from the begin and it will be the subject of our future study.
+
 \subsubsection*{Comment 4 -
@@
 }
+
+We would like to thank the reviewer for pointing out the deficiencies on our manuscript and we have considered your recommendations seriously.
+We made the following changes in language and presentation to improve the clarity of our manuscript.
+
+\begin{itemize}
+  \item Section VIII (page 8):\\
+  {\color{Maroon}
+  Our derived analytical expressions disclosed that we are able to control the transport characteristics of the dressed quantum Hall system by the applied dressing field’s intensity.
+Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
+  We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
+  Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels.
+Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results did not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}.
+This is due to the fact that the authors of Ref.\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Ref.\cite{ando74_1,ando82}.
+However this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
+  However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empherically observed behaviours of undressed quantum Hall systems as well.
+  }
+  \item Section III (page 3):\\
+  {\color{Maroon}
+  The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
+  In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.
+Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
+  }
+\end{itemize}
 

### 2021-11-12 response/response.tex
Finish commnets in res

@@
   }
+  \item Section I (page 2):\\
+  {\color{Maroon}
+  In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
+  Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
+  Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems.
+However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
+The authors of Ref.\cite{dini16} used the conductivity models from Refs.
+\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
+  }
+  \item Section IV (page 5):\\
+  {\color{Maroon}
+  Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~3 and Fig.~4.
+To make a comparison, we have selected the experiment parameters to match with the analysis done in Ref.~\cite{endo09}.
+  In the study presented in Ref.~\cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
+  }
 \end{itemize}

### 2021-11-14 response/response.tex
Correction to res

@@
 % Hypertext package
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 % Bold math
@@
 \usepackage{multirow}
+% \usepackage{kpfonts}
 
@@
 We are also thankful for the reviewer comments, and believe the second version of the manuscript we submit herewith has been significantly improved by the constructive criticism we received.
-Additionally, the subsequent sections of this document discusses the reviewer comments and our responses to them.
+Additionally, the subsequent sections of this document discuss the reviewer comments and our responses to them.
 
 Please note that in the following sections, the statements in {\color{RoyalBlue} \textbf{blue}} are the comments of the reviewers.
-Our responses are shown in black letters and the modifications we have done to the manuscript are given in {\color{Maroon} red}.
+Our responses are shown in black letters, and the modifications we have done to the manuscript are given in {\color{Maroon} red}.
 
@@
 We would like to thank the reviewer for bringing the deficiencies of our manuscript to our attention and providing constructive feedback to improve the quality of our work.
-We have considered all of your suggestions seriously and revised our paper manuscript as described below.
+We have considered all of your suggestions seriously and revised our manuscript as described below.
 
@@
 
-We strongly agree with the reviewer that a reasoning on our theoritical results and their application in current nanoelectronic devices would be essential to the reader.
-Therefore, we have made a discussion on physical significance of our theoritical results and their possible employments in the optimization of nanoelectronic device performance.
-We have inserted a new Section VII to incorporate the above discussion into the manuscript.
+We strongly agree with the reviewer that reasoning on our theoretical results and their application in current nanoelectronic devices would be essential to the reader.
+Therefore, we have made a discussion on the physical significance of our theoretical results and their possible employments in the optimization of nanoelectronic device performance.
+We have inserted a new section (Section VII) to incorporate the above discussion into the manuscript.
 The total content of the section is given below,
@@
   {\color{Maroon}
-  \subsection*{Physical significance of the outcomes}
+  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}
 
@@
 The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
-This is due to the applied magnetic field and it changes the energy spectrum of 2DEG in a dramatic way.
+This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically.
 The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
-  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low temperatures is the disorders in materials \cite{ando85,dial07}.
-This behavior implies the oscillating behavior of the experimental measurement of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
+  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low-temperatures is the disorders in materials \cite{ando85,dial07}.
+The broaden sequence of delta functions of density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
 \cite{endo09,wakabayashi78}.
@@
 As illustrated in Fig.
-4, we were also able to demonstrate the same SdH oscillations as experimental results \cite{endo09,wakabayashi78} through our model.
-Under the undressed ($I=0$) condition, our results overlap with the conductivity measurement for quantum Hall systems.
+4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Ref.\cite{endo09,wakabayashi78} through our model.
+Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
 However, from our results given in Fig.
 5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-In low temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity.
+In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.
 
@@
   A 2DEG under static magnetic field with quantum Hall effects is an excellent example that the gate electric field can be used to manipulate the conductivity.
-A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the electronic transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
-In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under high magnetic fields in low temperatures.
-Since the Fermi level of the system can be altered with applied gate voltage, this behavior can be easily mapped into our results given in Fig.
+A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the charge transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
+In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures.
+Since the Fermi level of the system can be altered with the applied gate voltage, this behavior can be easily mapped into our results given in Fig.
 4.
 However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field.
-Although Yang \textit{et al.} \cite{yang18}, achieved this broadening manipulation by changing the temperature in a low range, in this study we present a general mathematical description to perform that using only a high-intensity electromagnetic field.
+Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general mathematical description to manipulate longitudinal conductivity broadening using only a high-intensity electromagnetic field.
 
   The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
-In a particular application that uses the switching operation of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
+In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
 As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field.
 This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
-Based on these available nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers great potential to realize advanced nanoelectronic devices.
+  Furthermore, adopting the mechanism presented in Ref.\cite{hirakawa01}, we can utilize our manipulation of conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
+  Based on these ready-to-use nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers the potential to realize advanced nanoelectronic devices.
 Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
@@
 
-We thank the reviewer for pointing out that the nessisity of a comparison between the our theoritical model and previous discussions on transport properties of quantum Hall systems.
-Among the mentioned studies we can identify that experimental researches \cite{zudov01,mani02,zudov03,mani04} are specificly aim on the unusual oscillations of the magnetoresistance induced by the microwave (millimeterwave) radiation in 2DEG quantum Hall systems.
-These oscillations are know as \textit{microwave-induced resistance oscillations} (MIROs).
+We thank the reviewer for pointing out that the necessity of comparison between our theoretical model and previous discussions on transport properties of quantum Hall systems.
+Among the mentioned studies we can identify that experimental researches \cite{zudov01,mani02,zudov03,mani04} are specifically aimed at the unusual oscillations of the magnetoresistance induced by the microwave (millimeter-wave) radiation in 2DEG quantum Hall systems.
+These oscillations are known as \textit{microwave-induced resistance oscillations} (MIROs).
 To describe these behaviors Durst \textit{et al.} \cite{durst03} introduced a simple theoretical model assuming that the experimentally observed oscillations are a consequence of photoexcited disorder-scattered electrons.
-However, later a novel model was proposed in Ref.
-\cite{dmitriev03,dmitriev05,dmitriev09} considering the changes of the electron distribution function done by the microwave field.
-These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have succesfully describe the behavior of MIROs in experimentally relevent emperatures which was missed in previous model \cite{durst03}.
-Furthermore we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorbtion by electron in the considering system.
-However, in our theoritical model we consider higher frequencies than microwaves for the dressing field.
-Therefore we can clearly identify major dissimilarities between our system under the analysis and MIROs systems \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+However, later a novel model was proposed in Ref. \cite{dmitriev03,dmitriev05,dmitriev09} considering the changes of the electron distribution function done by the microwave field.
+These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have successfully described the behavior of MIROs in experimentally relevant temperatures which were missed in the previous model \cite{durst03}.
+Furthermore, we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorption by an electron in the considering system.
+However, in our theoretical model, we take into account higher frequencies than microwaves as the dressing field.
+Therefore we can identify major dissimilarities between our system under the analysis and MIROs systems \cite{zudov01,mani02,zudov03,mani04,durst03,dmitriev03,dmitriev05,dmitriev09}.
 We listed these dissimilarities as follows for our comparison.
@@
   \item
-  The mentioned experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in microwave frequency range ($30 -\SI{150}{\giga\hertz}$).
-This leads to build the theoritical models presented in Ref.
+  The mentioned experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$).
+This leads to building the theoretical models presented in Ref.
 \cite{durst03,dmitriev03} by assuming that these oscillations are caused by photoexcited electrons.
-Since these models consider on relevant frequency range (microwave radiation), it will allow to acknowledge the photon absorbtion by electrons.
-In cotrast to that, our consideration is only focus on the systems with high frequency range dressing fields which will not be associated to any photon absorbtion.
+Since these models consider on relevant frequency range (microwave radiation), it will allow us to acknowledge the photon absorption by electrons.
+In contrast to that, our consideration is only focused on the systems with high-frequency range dressing fields which will not be associated with any photon absorption.
   \item
-  The applied microwave radiation power on the MIROs experiments \cite{mani02,zudov03} are varies around $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
-However, in our analysis we take the dressing field as a high intensity field, where we can not address the dressing field as a perturbation to our considering system.
-This leads us to use regonize new Floquet states together with conventinal Landau levels.
-As we mentioned in our results, we used high intensity dressing fields of magnitude around $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.
+  The applied microwave radiation power on the MIROs experiments \cite{mani02,zudov03} are varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
+However, in our analysis, we take the dressing field as a high-intensity field, where we can not address the dressing field as a perturbation to our considering system.
+This leads us to use recognize new Floquet states together with conventional Landau levels.
+As we mentioned in our results, we used high-intensity dressing fields of magnitude around the $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.
   \item
@@
 \cite{zudov01,mani02,zudov03,mani04}.
-In this range of weak magnetic fields we can only observe MIROs and Shubnikov–de Haas (SdH) oscillations reveal only on high intensity magnetic fields.
-In comaparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics.
-Thesefore in our analysis we aim on the effects induced by high intensity magnetic fields ($B \sim \SI{1}{\tesla}$).
+In this range of weak magnetic fields,  we can only observe MIROs and Shubnikov–de Haas (SdH) oscillations reveal only on high-intensity magnetic fields.
+In comparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics.
+Therefore in our analysis, we aim at the effects induced by high-intensity magnetic fields ($B \sim \SI{1}{\tesla}$).
   \item
-  In our work, we analysed the 2DEG quantum Hall system with high-intensity dressing field which does not contribute to the energy exchange between a high-frequency dressing field and electrons.
+  In our work, we analyzed the 2DEG quantum Hall system with a high-intensity dressing field which does not contribute to a energy exchange between the high-frequency dressing field and electrons.
 Therefore we have assumed the applied electromagnetic radiation as a purely dressing field.
-There are two possible absorbtion mechanism in 2DEG quantum Hall system namely electron transitions bewtween distinct Landau levels and electron transitions between distinct states of a same broadened Landau level.
-To avoid these absorbtions we have tuned the dressing field to a high frequency in our system under the analysis.
-Furthermore due to high intensity dressing field, it will restructure the entire electronic states of the conventinal 2DEG quantum Hall systems.
-We have address these modifications throuth the Floquet theory.
-However, the MIROs models \cite{durst03,dmitriev03} are based on low frequecy case where the system is able to absorb low frequency photons from the field.
+There are two possible absorption mechanisms in a 2DEG quantum Hall system namely electron transitions between distinct Landau levels and electron transitions between distinct states of the same broadened Landau level.
+To avoid these absorptions we have tuned the dressing field into a high-frequency range in our system under the analysis.
+Furthermore, due to the high-intensity dressing field, the entire electronic states of the conventional 2DEG quantum Hall system will be restructured.
+We have addressed these modifications through the Floquet theory.
+However, the MIROs models \cite{durst03,dmitriev03} are based on low-frequency cases where the system is able to absorb low-frequency photons from the field.
 \end{itemize}
 
-Examine above mentioned points, we can clearly identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two particular natures of the magnetotransport properties.
-However, we identify that it is crusial to acknowledge these well-defined findings in MIROs and the their relatioship to the our considered system.
-We have added this clarification in the manuscript.
+Examining the above-mentioned points, we can identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two particular natures of magnetotransport properties.
+However, we identify that it is crucial to acknowledge these well-defined findings in MIROs and their relationship to our considered system. We have added this clarification in the manuscript.
 
@@
   Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
-Recently, an experimental research on the effect of microwave illumination of 2DEG systems revealed microwave induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
+Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
   This inspired investigations on theoretical description of MIROs and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
-These analytical formalisms provide a good explanation of the experimental characteristics of MIROs.
-However, these experimental and theoretical works have been linked to the photon absorbtion from low-frequecy (microwave) fields.
-In contrast to that, high-frequency external illumination on 2DEG quantum Hall system need to be study as a purely dressing (nonabsorbable) field.
-  The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be descriped by a nonabsorbtion mechanism and it has escaped the researchers’ attention before.
-  Then, lately Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems for high-frequency case.
+These analytical formalisms provide a proper explanation for the experimental observations of MIROs.
+However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) fields.
+  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a purely dressing (nonabsorbable) field.
+  The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism and it has escaped the researchers’ attention before.
+  Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems for a high-frequency case.
 However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
@@
   {\color{Maroon}
-  By comparing the theoritical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on magnetoresistance of 2DEG qunatum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
-  As observed in the experimental work by Caviglia \textit{et al.} \cite{caviglia10}, SdH oscillations period is only depend on the perpendicular component of the applied magnetic field.
-  Therefore, we can identify that many experiments done in low temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with different type of 2DEG has been oberved these SdH oscillations against applied magnetic field.
-  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the consdiering system.
-  Therefore we can achieve the same oscillation behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
-Due to the change of the gate volatge applied to the system will modify the Fermi level of the system.
-  Since the Landau level energy is only depend on the cyclotron frequency, this will generate the same SdH oscillations against gate volatage.
-  This osillating behavior with applied gate volatge has been observed in experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
-With comparing these empirical observations with our results given in Fig[4], we can easly identify that our oscillations are also shows the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
-Furthermore, when we increase the gate volatge, the Fermi level of the system get increased.
-This will locate to the the Fermi level on higher order Landau levels.
-As illustrated in Fig.~[4], this will result a higher conductivity peak value at higher order Landau level.
-This same behaviour also observed in the experimental observations presented in Ref.
+  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are a repetition of the Shubnikov–de Haas(SdH) oscillations.
+  As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
+  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
+  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
+  Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
+The  change of the gate voltage applied to the system will modify the Fermi level of the system.
+  Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
+  This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+By comparing these empirical observations with our results given in Fig.
+[4], we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
+Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
+This will locate to the Fermi level on higher-order Landau levels.
+As illustrated in Fig.~[4], this will result in a higher conductivity peak value at the higher-order Landau levels.
+This same behavior was also observed in the experimental observations presented in Ref.
 \cite{wakabayashi78} as well.
-However, in our analysis we have analytically explained the controllability of these conductivity regions using a dressing field.
-  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered a number of remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
-However these experiments and theoritical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorbtion from the applied low-frequency field.
+However, in our analysis, we have analytically explained the controllability of these conductivity regions using a dressing field.
+  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
+However, these experiments and theoretical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
   It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
-In our case, the applied dressing field is in off-resonant range and that will only change the the broadening of Landau levels and avoid any contribution towards the photon absorbtions.
-This will clearly describe the crusial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
-Therefore our approach can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
+In our case, the applied dressing field is in the off-resonant range and that will only change the broadening of Landau levels and avoid any contribution towards the photon absorptions.
+This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
+Therefore our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
   }
@@
 We thank the reviewer for pointing out the importance of these facts that will help to elevate the value of our work.
-As we mentioned in the commnet 1, consideirng the important of discussing physical significance of our results, we added a new section(Section VII) to address these facts.
+As we mentioned in comment 1, considering the importance of discussing the physical significance of our results, we added a new section (Section VII) to address these facts.
 
@@
   {\color{Maroon}
-  \subsection*{Physical significance of outcomes}
+  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}
 
@@
 We thank the reviewer for raising this important question.
-In our previous manuscript, we have presented the detailed derivation of Eq.~[15] with a discusssion on models of disorder under the Appendix C.
-However we will discuss on our selection of disorder model and approximations made to derive the Eq.~[15] here as well.
+In our previous manuscript, we have presented the detailed derivation of Eq.~[15] with a discussion on models of disorder under Appendix C.
+However we will discuss our selection of disorder model and approximations made to derive the Eq.~[15] here as well.
 
 We modeled the effect caused by impurities in the considered system as a single perturbation potential.
-Analyzing the electric propeties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
-Therefore, in this study we consider on the statistically averaged propeties of 2DEG over impurity configurations.
-In addition, we consider only the our considering static disorder corresponds to the situation in which the electrons scatter elastically.
+Analyzing the electric properties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
+Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
+In addition, we consider only our considering static disorder corresponds to the situation in which the electrons scatter elastically.
 First, we adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the considering system and we approximate this into a Gaussian white noise.
 
-Since we are presenting the the perturbation potential $V(\vb{r})$ by a group of randomly localized impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed at randomly but in fixed positions $\vb{r}_i$.
+Since we are presenting the perturbation potential $V(\vb{r})$ by a group of randomly localized impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed randomly but in fixed positions $\vb{r}_i$.
 Thus, we can describe the scattering potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
@@
 In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
-Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make two-point correlation function to be
+Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make a two-point correlation function be
 \begin{equation} \label{eq:4}
@@
 Then we calculate the Floquet-Fermi golden rule for a dressed quantum Hall system using this perturbative impurity potential.
-In the derivation we have defined the $V_{imp}$ value which is constant in moemntum space.
-It is a propety of Gaussian white noise impurity distribution \cite{akkermans10,wackerl20}.
-However, throughout the derivation we use only the first order contribution (Born approximation) of the impurity potential.
-All the detailed step for the derivation of the Floquet-Fermi golden rule for a dressed quantum Hall system are included in Appendix C.
+In the derivation, we have defined the $V_{imp}$ value which is constant in momentum space.
+It is a property of Gaussian white noise impurity distribution \cite{akkermans10,wackerl20}.
+However, throughout the derivation, we use only the first-order contribution (Born approximation) of the impurity potential.
+All the detailed steps for the derivation of the Floquet-Fermi golden rule for a dressed quantum Hall system are included in Appendix C.
 
-Since previous studies on Floquet-Drude consuctivity \cite{wackerl20}, and magnetotransport propeties in dressed qunatum Hall systems \cite{dini16} have  used this perticular Gaussian white noise potential, we also selected this pertucular impurity model to describe our system.
-This open a path to compare our analytical outcomes with these previous models.
-As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the magnetotransport properties of dressed qunatum Hall system would be an interesting future research possibility.
+Since previous studies on Floquet-Drude conductivity \cite{wackerl20}, and magnetotransport properties in undressed \cite{endo09} and dressed \cite{dini16} quantum Hall systems have used this particular Gaussian white noise potential, we also selected this pertucular impurity model to describe our system.
+This opens a path to compare our analytical outcomes with these previous models.
+As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the magnetotransport properties of dressed quantum Hall system would be an interesting future research possibility.
 
-Since we have not mentioned the validity conditions we used to derive the Eq.~[15] in the main text of the previous manuscript, we have added validity conditions to the new manuscript.
+Since we have only mentioned the validity conditions we used to derive the Eq.~[15] in Appendix C and not in the main text of the previous manuscript, we have added these validity conditions to the main text of the new manuscript.
 
@@
   A more detailed derivation is given in Appendix C.
-  We modeled the effect caused by impurities in the considered system as a single perturbation potential.
-Analyzing the electric propeties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
+  We modeled the effect caused by impurities in the considered system as a single short-range perturbation potential.
+Analyzing the electric properties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
+  Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
   Furthermore, we assumed that our perturbation potential is formed by a group of randomly distributed impurities under the Edwards impurity model \cite{akkermans10,wackerl20}.
@@
   Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
-In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential and
+In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
   }
@@
 In our analysis we have derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
-Then we selected an special scenario where we assumed that the system is under low temperature limit.
-Since previous theoritical studies on magnetotransport propeties of 2DEG quantum Hall systems were derived under this assumption, we selected this conditions to provide a better comparison with their outcomes.
-In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing tempurature, we can identify the decaying behaviour of SdH oscillations.
-Therefore, if we need to maintain a good oscillator behavior we need to work in low temperatures.
-Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, we have extend our general derivation in given Eq.~[31] into a simple expression for low temperature case.
+Then we selected an special scenario where we assumed that the system is under low-temperature limit.
+Since previous theoretical studies on magnetotransport properties of 2DEG quantum Hall systems were derived under this assumption, we selected this conditions to provide a better comparison with their outcomes.
+In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing tempurature, we can identify the decaying behavior of SdH oscillations.
+Therefore, if we need to maintain a good oscillator behavior we need to work in low-temperatures.
+Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, we have extend our general derivation in given Eq.~[31] into a simple expression for low-temperature case.
 On the other hand, under the off-resonant condition, absorption of photons is avoided, and we can choose the the Fermi-Dirac distribution as our partical distribution function in Eq.~[31] as given in Eq.~[33].
-Under low temperature assumption, we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy as given mentioned in the Eq.~[34].
+Under low-temperature assumption, we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy as given mentioned in the Eq.~[34].
 Applying these two conditions, we can simplify our derivation into new expression that can be compared with previous studies on magnetotransport in dressed quantum Hall systems.
 
-Yes, it is true that when we consider the experimental observations of a qunatum Hall system a strong dressing field can increase the temperature of the sample.
-However, as mentioned in previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low temperature by applying narroaw pulses of a strong dressing field to observe the discussed phenomena.
+Yes, it is true that when we consider the experimental observations of a quantum Hall system a strong dressing field can increase the temperature of the sample.
+However, as mentioned in previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low-temperature by applying narroaw pulses of a strong dressing field to observe the discussed phenomena.
 
-Although we have extend our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoritical model into different type of partical distribution functions.
+Although we have extend our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoretical model into different type of partical distribution functions.
 As discussed by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion need to address the changes in distribution functions in our derived general longitudinal conductivity formula and this would be an interesting extension to our study.
@@
 Since we have only analyzed the normalized $xx$-component of the conductivity tensor, the remaining analysis is not effected by this change.
-After this change we can predict that the both $xx$-component and $yy$-component shows the same conductivity behaviours.
+After this change we can predict that the both $xx$-component and $yy$-component shows the same conductivity behaviors.
 We added these changes to the calculations done in Appendix D and the conductivity calculation under Section V.
@@
 %
-% As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the qunatum state of the consideirng system and creates novel states called Floquet states.
-The propeties of these states are depends on the characteristics of applied dressing field.
+% As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the consideirng system and creates novel states called Floquet states.
+The properties of these states are depends on the characteristics of applied dressing field.
 Therefore, the polarization method also change the behavior of the Floquet states.
 % These polarization dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields.
-In addition, they have mentioned the impact on the direction of the linearly polarization dressing field and this will break the isotropy behaviour of the longitudinal conductivities in the consideirng system.
+In addition, they have mentioned the impact on the direction of the linearly polarization dressing field and this will break the isotropy behavior of the longitudinal conductivities in the consideirng system.
 %
@@
   {\color{Maroon}
-  By comparing the theoritical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on magnetoresistance of 2DEG qunatum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
+  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
   As observed in the experimental work by Caviglia \textit{et al.} \cite{caviglia10}, SdH oscillations period is only depend on the perpendicular component of the applied magnetic field.
-  Therefore, we can identify that many experiments done in low temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with different type of 2DEG has been oberved these SdH oscillations against applied magnetic field.
+  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with different type of 2DEG has been oberved these SdH oscillations against applied magnetic field.
   The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the consdiering system.
-  Therefore we can achieve the same oscillation behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
-Due to the change of the gate volatge applied to the system will modify the Fermi level of the system.
-  Since the Landau level energy is only depend on the cyclotron frequency, this will generate the same SdH oscillations against gate volatage.
-  This osillating behavior with applied gate volatge has been observed in experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+  Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
+Due to the change of the gate voltage applied to the system will modify the Fermi level of the system.
+  Since the Landau level energy is only depend on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
+  This oscillating behavior with applied gate voltage has been observed in experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low-temperature.
 With comparing these empirical observations with our results given in Fig[4], we can easly identify that our oscillations are also shows the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
-Furthermore, when we increase the gate volatge, the Fermi level of the system get increased.
+Furthermore, when we increase the gate voltage, the Fermi level of the system get increased.
 This will locate to the the Fermi level on higher order Landau levels.
 As illustrated in Fig.~[4], this will result a higher conductivity peak value at higher order Landau level.
-This same behaviour also observed in the experimental observations presented in Ref.
+This same behavior also observed in the experimental observations presented in Ref.
 \cite{wakabayashi78} as well.
@@
   Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered a number of remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
-However these experiments and theoritical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorbtion from the applied low-frequency field.
+However these experiments and theoretical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
   It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
-In our case, the applied dressing field is in off-resonant range and that will only change the the broadening of Landau levels and avoid any contribution towards the photon absorbtions.
-This will clearly describe the crusial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
+In our case, the applied dressing field is in off-resonant range and that will only change the the broadening of Landau levels and avoid any contribution towards the photon absorptions.
+This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
 Therefore our approach can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
@@
 The authors of the Ref.\cite{endo09} has neglect the effects mentioned above during the development the theory.
-We also follwed the same theoritical derivation with given assumtions but with a additionl dressing field.
+We also follwed the same theoretical derivation with given assumtions but with a additionl dressing field.
 Our results for undressed system gives a better aggrement with the results from Ref.\cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks.
@@
 Therefore we are unable to predict the off-diogonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.
-However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behaviour of off-diogonal components of the conductivity tensor.
+However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diogonal components of the conductivity tensor.
 As mentioned in the Ref.~\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations
@@
 \end{equation}
-By comparing the resultion between longitudinal and transverse conductivities in 2DEG quantum Hall system, we can expect the same Hall conductivity behaviour in a dressed quantum Hall system.
+By comparing the resultion between longitudinal and transverse conductivities in 2DEG quantum Hall system, we can expect the same Hall conductivity behavior in a dressed quantum Hall system.
 However, using the dressing field we are able to squeeze the conductivity peaks on Landau levels.
@@
 However this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
-  However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empherically observed behaviours of undressed quantum Hall systems as well.
+  However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empherically observed behaviors of undressed quantum Hall systems as well.
   }
@@
 
-We agree with the reviewer that a discussion on our theoritical results and their physical significance into modern nanoelectronic devices is a vital requirement.
+We agree with the reviewer that a discussion on our theoretical results and their physical significance into modern nanoelectronic devices is a vital requirement.
 We have added a new Section VII to overcome the above mentioned deficiency of our manuscript.
@@
 The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
-  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low temperatures is the disorders in materials \cite{ando85,dial07}.
+  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low-temperatures is the disorders in materials \cite{ando85,dial07}.
 This behavior implies the oscillating behavior of the experimental measurement of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
@@
 5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-In low temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity.
+In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity.
 
@@
 A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the electronic transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
-In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under high magnetic fields in low temperatures.
+In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under high magnetic fields in low-temperatures.
 Since the Fermi level of the system can be altered with applied gate voltage, this behavior can be easily mapped into our results given in Fig.

### 2021-11-14 response/response.tex
Corrections to res

@@
 This is a good, valid question.
-First, we discuss the validity of the Eq.~[33] and Eqq.~[34].
-In our analysis we have derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
-Then we selected an special scenario where we assumed that the system is under low-temperature limit.
-Since previous theoretical studies on magnetotransport properties of 2DEG quantum Hall systems were derived under this assumption, we selected this conditions to provide a better comparison with their outcomes.
-In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing tempurature, we can identify the decaying behavior of SdH oscillations.
-Therefore, if we need to maintain a good oscillator behavior we need to work in low-temperatures.
-Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, we have extend our general derivation in given Eq.~[31] into a simple expression for low-temperature case.
-On the other hand, under the off-resonant condition, absorption of photons is avoided, and we can choose the the Fermi-Dirac distribution as our partical distribution function in Eq.~[31] as given in Eq.~[33].
-Under low-temperature assumption, we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy as given mentioned in the Eq.~[34].
-Applying these two conditions, we can simplify our derivation into new expression that can be compared with previous studies on magnetotransport in dressed quantum Hall systems.
+First, we discuss the validity of the Eq.~[33] and Eq.~[34].
+In our analysis, we have derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
+In contrast to the MIROs analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, where the absorption of photons are avoided.
+Therefore, we can select the Fermi-Dirac distribution as our particle distribution function on the general expression given in Eq.~[31]
+\begin{equation} \tag{5}
+  f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1}.
+\end{equation}
+Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
+Then we selected a special scenario where we assumed that the system is under a low-temperature limit or the condition $k_BT \ll \varepsilon_F$.
+Since previous theoretical studies \cite{wackerl20,dini16,endo09} on magnetotransport properties of 2DEG quantum Hall systems were derived under this assumption, we selected this condition to provide a better comparison with their outcomes.
+In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing temperature, we can identify the decaying behavior of SdH oscillations.
+Therefore, if we need to maintain a good oscillatory behavior we need to work in low temperatures.
+Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, it is reasonable to extend our general derivation in given Eq.~[31] into a simple expression through a low-temperature limit.
+Furthermore, with the ability of adjusting Fermi level of the system through the applied gate voltage, we can achieve higher Fermi energies.
+This implies the condition $k_BT \ll \varepsilon_F$ and we can approximate that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
+This can be represented by the delta function \cite{endo09}
+\begin{equation} \tag{6}
+  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
+\end{equation}
+Applying these adequate conditions, we can simplify our derivation into single expression that can be compared with previous studies \cite{wackerl20,dini16,endo09} on magnetotransport in dressed quantum Hall systems.
+We have added clarification on the above assumptions in the manuscript.
+\begin{itemize}
+  \item Section V - second paragraph (page 7):\\
+  {\color{Maroon}
+  Since we consider the dressed quantum Hall system under the off-resonant condition, the absorption of photons are avoided.
+Therefore, we select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
+  \begin{equation} \label{eq:33}
+    f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
+  \end{equation}
+  where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
+Under the above distribution in low-temperature conditions or $k_BT \ll \varepsilon_F$ condition, we can approximate that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
+This can be represented by the delta function \cite{endo09}
+  \begin{equation} \label{eq:34}
+    - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
+  \end{equation}
+  }
+\end{itemize}
 
 Yes, it is true that when we consider the experimental observations of a quantum Hall system a strong dressing field can increase the temperature of the sample.
-However, as mentioned in previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low-temperature by applying narroaw pulses of a strong dressing field to observe the discussed phenomena.
+However, as mentioned in a previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low-temperature by applying narrow pulses of a strong dressing field to observe the discussed phenomena.
 
-Although we have extend our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoretical model into different type of partical distribution functions.
-As discussed by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion need to address the changes in distribution functions in our derived general longitudinal conductivity formula and this would be an interesting extension to our study.
+Although we have extended our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoretical model into different types of particle distribution functions.
+As presented in the previous work done by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion needs to address the changes in distribution functions in our derived general longitudinal conductivity formula and this would be an noteworthy extension to our study.
 

### 2021-11-14 response/response.tex
Corrections to res

@@
 
-We thank the reviewer for pointing out the importance mistake we have made in the $yy$-component calculation.
-We have made an mistake in the current operator calculations and this has leaded to a unexpected normalization factor in the conductivity expresiion.
-Since we have only analyzed the normalized $xx$-component of the conductivity tensor, the remaining analysis is not effected by this change.
-After this change we can predict that the both $xx$-component and $yy$-component shows the same conductivity behaviors.
-We added these changes to the calculations done in Appendix D and the conductivity calculation under Section V.
+We express our gratitude towards the reviewer for pointing out this inadvertent oversight done in the $yy$-component of the current operator calculation and this has led to an unexpected normalization factor in the yy-component of conductivity expression.
+Since we have only analyzed the normalized $xx$-component of the conductivity tensor, the remaining analysis is not affected by this change.
+After this change, we can predict that both xx-component and $yy$-component show the same conductivity behaviors.
+We added these amendments to the current operator calculations done in Appendix D and the longitudinal conductivity calculation under Section V.
 
 \begin{itemize}
-  \item Appendix D - (page 14):\\
+  \item Appendix D (page 14):\\
   {\color{Maroon}
-  \subsection*{\label{appendix_d}Current operators for a dressed quantum Hall system}
+  \subsection*{\label{appendix_d}Appendix D: Current operators for a dressed quantum Hall system}
 
@@
   }
-  \item Section V - (page 7):\\
+  \item Section V (page 7):\\
   {\color{Maroon}
@@
 
-% For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
-The Floquet-Drude conductivity formula was only developed for the diogonal components of the conductivity tensor of the considering system.
-In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diogonal components of the conductivity tensor.
+If we applied an arbitrary directional polarized dressing field, we can derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis.
+This would change the amplitude of the considering dressing field ($E$) in each direction.
+Now there will be a new component in parallel to the considering conductivity component and this will modify the time-dependent Hamiltonian given in Eq.~[2].
+Then, we need to solve the Schrödinger equation with the modified Hamiltonian to find the new Floquet modes for the new system.
+These will define the effect on the inverse scattering time matrix components.
+As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the considered system and creates novel states called Floquet states.
+The properties of these states depend on the characteristics of the applied dressing field.
+Therefore, the polarization method also changes the behavior of the Floquet states.
+These polarization-dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields.
+However, in a dressed quantum Hall system with a $y$-directional linear polarized field, we predict the same longitudinal conductivity behaviors in diagonal components of the conductivity tensor.
+
+For analyzing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
+The Floquet-Drude conductivity formula was only developed for the diagonal components of the conductivity tensor of the considering system.
+In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analyzed the dressing field effect on two diagonal components of the conductivity tensor.
+Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these types of behaviors of dressed 2DEG quantum Hall systems.
 %
@@
 % However in our analysis, our main objective was to identify the manipulation capabilities of SdH oscillations using dressing field intensity.
-In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diogonal components in conductivity tensor.
-Therefore we are unable to predict the off-diogonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.
+In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diagonal components in conductivity tensor.
+Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.
 
@@
 For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
-The Floquet-Drude conductivity formula was only developed for the diogonal components of the conductivity tensor of the considering system.
-In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diogonal components of the conductivity tensor through Floquet-Drude conductivity formula.
-Therefore we are unable to predict the off-diogonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.
-However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diogonal components of the conductivity tensor.
+The Floquet-Drude conductivity formula was only developed for the diagonal components of the conductivity tensor of the considering system.
+In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diagonal components of the conductivity tensor through Floquet-Drude conductivity formula.
+Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.
+However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diagonal components of the conductivity tensor.
 As mentioned in the Ref.~\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations

### 2021-11-14 response/response.tex
Corrections to res

@@
 In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diagonal components in conductivity tensor.
-Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.
+Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quantum Hall systems.
 
@@
 
-We would like to thank the reviewer for his/her insightful comments our work.
+We would like to thank the reviewer for his/her insightful comments on our work.
 To address your comments, we had to add new materials and reorganize our text.
-As a result we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis.
-We hence believe that both the presentation and scientific content of this manuscript is of a much higher quality than our previous submission.
-We hope our response, and the corresponding changes we incorporated to the manuscript would be sufficient to clarify the issues raised.
+As a result, we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis.
+We hence believe that both the presentation and scientific content of this manuscript are of a much higher quality than our previous submission.
+We hope our response and the corresponding changes we incorporated into the manuscript would be sufficient to clarify the issues raised.
 
@@
 We thank the reviewer for pointing out the importance of this fact.
-To overcome this shortage of discussion we made a detailed analysis on our results against the undressed 2DEG quantum Hall system behavior.
-We have inserted this discussion into the our manuscript under Section VI.
+To overcome this shortage of discussion we made a detailed analysis of our results against the undressed 2DEG quantum Hall system behavior.
+We have inserted this discussion into our manuscript under Section VI.
 
@@
   {\color{Maroon}
-  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are repetition of the Shubnikov–de Haas(SdH) oscillations.
-  As observed in the experimental work by Caviglia \textit{et al.} \cite{caviglia10}, SdH oscillations period is only depend on the perpendicular component of the applied magnetic field.
-  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with different type of 2DEG has been oberved these SdH oscillations against applied magnetic field.
-  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the consdiering system.
+  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are a repetition of the Shubnikov–de Haas(SdH) oscillations.
+  As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
+  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
+  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
   Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
-Due to the change of the gate voltage applied to the system will modify the Fermi level of the system.
-  Since the Landau level energy is only depend on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
-  This oscillating behavior with applied gate voltage has been observed in experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low-temperature.
-With comparing these empirical observations with our results given in Fig[4], we can easly identify that our oscillations are also shows the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
-Furthermore, when we increase the gate voltage, the Fermi level of the system get increased.
-This will locate to the the Fermi level on higher order Landau levels.
-As illustrated in Fig.~[4], this will result a higher conductivity peak value at higher order Landau level.
-This same behavior also observed in the experimental observations presented in Ref.
+The  change of the gate voltage applied to the system will modify the Fermi level of the system.
+  Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
+  This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+By comparing these empirical observations with our results given in Fig.
+[4], we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
+Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
+This will locate to the Fermi level on higher-order Landau levels.
+As illustrated in Fig.~[4], this will result in a higher conductivity peak value at the higher-order Landau levels.
+This same behavior was also observed in the experimental observations presented in Ref.
 \cite{wakabayashi78} as well.
-However, in our analysis we have analytically explained the controllability of these conductivity regions using a dressing field.
-  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered a number of remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
-However these experiments and theoretical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
+However, in our analysis, we have analytically explained the controllability of these conductivity regions using a dressing field.
+  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
+However, these experiments and theoretical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
   It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
-In our case, the applied dressing field is in off-resonant range and that will only change the the broadening of Landau levels and avoid any contribution towards the photon absorptions.
+In our case, the applied dressing field is in the off-resonant range and that will only change the broadening of Landau levels and avoid any contribution towards the photon absorptions.
 This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
-Therefore our approach can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
+Therefore our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
   }
@@
 
-We agree with the reviewer that the discussion on the Anderson localization and topologically protected edge modes are was missing from the manuscript.
-We would like to mentioned the reviewer that while deriving Eq.~[31], we have assumed that the applyed static magnetic field is placed in a lower intensity range where we can neglect a number of effects known to appear in a 2DEG quantum Hall system.
-Under this condition we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions and the spin splitting as well.
-As mentioned in the work done by Endo \textit{et al.} \cite{endo09}, under the given magnetic field range, the undressed magnetotransport properties of GaAs/AlGaAs 2DEG quantum Hall system provides excellent agrrement between the experimental observations and theory.
-The authors of the Ref.\cite{endo09} has neglect the effects mentioned above during the development the theory.
-We also follwed the same theoretical derivation with given assumtions but with a additionl dressing field.
-Our results for undressed system gives a better aggrement with the results from Ref.\cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks.
+We agree with the reviewer that the discussion on the Anderson localization and topologically protected edge modes were missing from the previous manuscript.
+We would like to mention to the reviewer that while deriving Eq.~[31], we have assumed that the applied static magnetic field is placed in a lower intensity range where we can neglect several effects known to appear in a 2DEG quantum Hall system.
+Under this condition, we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions, and the spin splitting as well.
+As mentioned in the work done by Endo \textit{et al.} \cite{endo09}, under the given magnetic field range, the undressed magnetotransport properties of GaAs/AlGaAs 2DEG quantum Hall system provide an excellent agreement between the experimental observations and theory that was developed by neglecting the above-mentioned effects.
+We also followed the same theoretical derivation with given assumptions but with an additional dressing field.
+Our results for the undressed system give a adequate agreement with the results from Ref.\cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks.
 We have added this clarification in the manuscript.
@@
   {\color{Maroon}
-  It is important to note that, in this analysis we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting and the electron–electron interactions can be neglected.
-The use of this assumption can also be found in study done by  Endo \textit{et al.} \cite{endo09}.
+  It is important to note that, in this analysis, we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions can be neglected.
+The use of this assumption can also be found in the study done by Endo \textit{et al.} \cite{endo09}.
   }
-  \item Section VIII - sixth paragraph (page 2):\\
+  \item Section VIII - sixth paragraph (page 8):\\
   {\color{Maroon}
-  We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within a order where we can neglect effects of the the Anderson localization, the formation of the edge states, the spin splitting and the electron–electron interactions.
+  We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within an order where we can neglect effects of the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions.
   }
@@
 
-For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
+For analyzing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
 The Floquet-Drude conductivity formula was only developed for the diagonal components of the conductivity tensor of the considering system.
-In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diagonal components of the conductivity tensor through Floquet-Drude conductivity formula.
-Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.
+In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analyzed the dressing field effect on two diagonal components of the conductivity tensor through the Floquet-Drude conductivity formula.
+Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these types of behaviors of dressed 2DEG quantum Hall systems.
 However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diagonal components of the conductivity tensor.
-As mentioned in the Ref.~\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations
+As mentioned in Ref.~\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations
 \begin{equation} \nonumber
@@
 \end{equation}
-By comparing the resultion between longitudinal and transverse conductivities in 2DEG quantum Hall system, we can expect the same Hall conductivity behavior in a dressed quantum Hall system.
-However, using the dressing field we are able to squeeze the conductivity peaks on Landau levels.
-This will reduce the region of high conductivity peaks placed near the Landau levels.
-This will imply sudden Hall conductivity transitions between one plateau to another one near a Landau level.
-As empherical observation showed in Ref.
-\cite{klitzing80,gusynin06}, we can predict a staircase behavior for quantum Hall conductivity but with higher intensity dressing field we will get rapid transitions then the undressed system.
-However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulate from the begin and it will be the subject of our future study.
+By examining the connection between longitudinal and transverse conductivities in the 2DEG quantum Hall system, we can expect the same Hall conductivity behavior in a dressed quantum Hall system.
+However, using the dressing field we can squeeze the conductivity peaks on Landau levels.
+This will squeeze the region of longitudinal conductivity peaks placed near the Landau levels.
+This will imply sudden Hall conductivity transitions between one plateau to another near a Landau level.
+As empirical observation shown in Ref.
+\cite{klitzing80,gusynin06}, we can predict a staircase behavior for quantum Hall conductivity agaist the gate voltage.
+With a external dressing field we will be able to get rapid transitions than the undressed system.
+However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulated from the begin and it will be the subject of our future study.
 
@@
 
-We would like to thank the reviewer for pointing out the deficiencies on our manuscript and we have considered your recommendations seriously.
+We would like to thank the reviewer for pointing out the deficiencies in our manuscript and we have considered your recommendations seriously.
 We made the following changes in language and presentation to improve the clarity of our manuscript.
@@
   Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels.
-Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results did not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}.
-This is due to the fact that the authors of Ref.\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Ref.\cite{ando74_1,ando82}.
-However this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
-  However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empherically observed behaviors of undressed quantum Hall systems as well.
+Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results do not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}.
+This is due to the fact that the authors of Ref.\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Ref.\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
+  However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
   }
@@
 
-We agree with the reviewer that a discussion on our theoretical results and their physical significance into modern nanoelectronic devices is a vital requirement.
-We have added a new Section VII to overcome the above mentioned deficiency of our manuscript.
+We agree with the reviewer that a discussion on our theoretical results and their physical significance in modern nanoelectronic devices is a vital requirement.
+We have added a new Section VII to overcome the above-mentioned deficiency of our manuscript.
 The total content of the section is given below,
@@
 The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
-This is due to the applied magnetic field and it changes the energy spectrum of 2DEG in a dramatic way.
+This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically.
 The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
   However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low-temperatures is the disorders in materials \cite{ando85,dial07}.
-This behavior implies the oscillating behavior of the experimental measurement of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
+The broaden sequence of delta functions of density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
 \cite{endo09,wakabayashi78}.
@@
 As illustrated in Fig.
-4, we were also able to demonstrate the same SdH oscillations as experimental results \cite{endo09,wakabayashi78} through our model.
-Under the undressed ($I=0$) condition, our results overlap with the conductivity measurement for quantum Hall systems.
+4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Ref.\cite{endo09,wakabayashi78} through our model.
+Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
 However, from our results given in Fig.
 5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity.
+In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.
 
@@
   A 2DEG under static magnetic field with quantum Hall effects is an excellent example that the gate electric field can be used to manipulate the conductivity.
-A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the electronic transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
-In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under high magnetic fields in low-temperatures.
-Since the Fermi level of the system can be altered with applied gate voltage, this behavior can be easily mapped into our results given in Fig.
+A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the charge transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
+In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures.
+Since the Fermi level of the system can be altered with the applied gate voltage, this behavior can be easily mapped into our results given in Fig.
 4.
 However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field.
-Although Yang \textit{et al.} \cite{yang18}, achieved this broadening manipulation by changing the temperature in a low range, in this study we present a general mathematical description to perform that using only a high-intensity electromagnetic field.
+Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general mathematical description to manipulate longitudinal conductivity broadening using only a high-intensity electromagnetic field.
 
   The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
-In a particular application that uses the switching operation of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
+In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
 As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field.
 This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
-Based on these available nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers great potential to realize advanced nanoelectronic devices.
+  Furthermore, adopting the mechanism presented in Ref.\cite{hirakawa01}, we can utilize our manipulation of conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
+  Based on these ready-to-use nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers the potential to realize advanced nanoelectronic devices.
 Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.

### 2021-11-14 response/response.tex
Refernce correct in res
Add paper_res

@@
 % Bibliography style
-\bibliographystyle{unsrt}
+\usepackage[numbers]{natbib}
+\bibliographystyle{apsrev4-1}
 
@@
 \begin{itemize}
-    \item We have made minor changes in language and presentation to improve clarity, and to match the rest of the manuscript better to the changes done to address the reviewer's comments.
+    \item Introduction section details need to be changed.
     \begin{itemize}
@@
     \end{itemize}
+    \item Near Eq.37 $\sigma_0$ correction.
 \end{itemize}
@@
 
-  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \cite{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
+  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
 The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
@@
 Therefore, we select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
-  \begin{equation} \label{eq:33}
+  \begin{equation} \tag{33}
     f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
@@
 This can be represented by the delta function \cite{endo09}
-  \begin{equation} \label{eq:34}
+  \begin{equation} \tag{34}
     - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
@@
   }
-  \item Section VIII - sixth paragraph (page 8):\\
+  \item Section VIII - second paragraph (page 8):\\
   {\color{Maroon}
@@
   {\color{Maroon}
-  Our derived analytical expressions disclosed that we are able to control the transport characteristics of the dressed quantum Hall system by the applied dressing field’s intensity.
-Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
-  We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
-  Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels.
   Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results do not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}.
@@
   {\color{Maroon}
-  In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
-  Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
-  Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems.
-However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
   The authors of Ref.\cite{dini16} used the conductivity models from Refs.
@@
   {\color{Maroon}
-  Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~3 and Fig.~4.
-To make a comparison, we have selected the experiment parameters to match with the analysis done in Ref.~\cite{endo09}.
   In the study presented in Ref.~\cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
@@
 
-\newpage
 \bibliography{response}

### 2021-11-14 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
Add paper_res

--- 2021-08-22 paper/v3-release/aps_article.tex
@@
 \usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
+% Color package
+\usepackage[dvipsnames]{xcolor}
 % Language and font encodings
@@
 Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
-Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems.
-However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
-In their study, they used the conductivity models from Refs.
-\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
+{\color{Red}Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
+This inspired investigations on theoretical description of MIROs and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+These analytical formalisms provide a proper explanation for the experimental observations of MIROs.
+However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) fields.
+In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a purely dressing (nonabsorbable) field.
+The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism and it has escaped the researchers’ attention before.
+Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems for a high-frequency case.} However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
+{\color{Red}The authors of Ref.\cite{dini16} used the conductivity models from Refs.
+\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.}
 
@@
 This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
-In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
+{\color{Red}
+It is important to note that, in this analysis, we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions can be neglected.
+The use of this assumption can also be found in the study done by Endo \textit{et al.} \cite{endo09}.
+} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
 Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref.
@@
 \begin{figure}[b]
-\includegraphics[scale=0.9]{figures/fig_1.pdf}
+\includegraphics[scale=0.9]{fig_1_system_diagram}
 \caption{\label{fig:1} Our 2DEG system only confined in the $xy$-plane while both of the stationary magnetic field $\vb{B}$ and the dressing field are applied perpendicular to the plane of 2DEG.
@@
 The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
-In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field.
-Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
+{\color{Red}In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.} Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
 
@@
 A more detailed derivation is given in Appendix \ref{appendix_c}.
-We modeled the effect caused by impurities in the considered system as a single perturbation potential.
-Since random impurities in a disordered metal offer a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
+{\color{Red}
+We modeled the effect caused by impurities in the considered system as a single short-range perturbation potential.
+Analyzing the electric properties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
+Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
+Furthermore, we assumed that our perturbation potential is formed by a group of randomly distributed impurities under the Edwards impurity model \cite{akkermans10,wackerl20}.
 Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+Then we  approximate the impurity potential into a Gaussian white noise \cite{akkermans10,wackerl20}.
 Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
 Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
+In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
+}
 
@@
 \begin{figure}[t]
-\includegraphics[scale=0.55]{figures/fig_2}
+\includegraphics[scale=0.55]{fig_2_normalized_broadening_with_momentum}
 \caption{\label{fig_3} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against $x$-directional momentum value $k_x$ in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and intensity $I =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_3}
+\includegraphics[scale=0.54]{fig_3_normalized_broadening_with_intensity}
 \caption{\label{fig_4} The dependence of normalized scattering-induced broadening $\Lambda_N$ for each Landau level ($N =0,1,2,3,4$) against dressing field intensity $I$, in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$.
@@
 To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
-In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
-In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
+{\color{Red}In the study presented in Ref.~\cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.} In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
 Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
@@
 \end{equation}
-We use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
+{\color{Red}
+Since we consider the dressed quantum Hall system under the off-resonant condition, the absorption of photons are avoided.
+Therefore, we select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
 \begin{equation} \label{eq:33}
@@
 where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Considering the above distribution for extremely low-temperature conditions, we can use the following approximation
+Under the above distribution in low-temperature conditions or $k_BT \ll \varepsilon_F$ condition, we can approximate that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
+This can be represented by the delta function \cite{endo09}
 \begin{equation} \label{eq:34}
@@
 \end{equation}
-Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
+Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(31) leads to
 \begin{equation} \label{eq:35}
@@
     \sigma^{xx}  =
-    \frac{e^2}{\pi\hbar A}
+    \frac{e^2l_0^2}{\pi\hbar A}
     \sum_{n} &
@@
 \end{equation}
-where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$
-and
-$\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$.
-Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
+where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$,
+$\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$, and $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$.
+Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
 \begin{equation} \label{eq:36}
@@
     {\sigma}^{yy} =
-    \frac{e^2}{\pi\hbar A} &
-    \frac{1}{e^2B^2}
-    \sum_{n}
+    \frac{e^2l_0^2}{\pi\hbar A}
+    \sum_{n} &
     \frac{(n+1)}{\gamma_{n}\gamma_{n+1}} \\
-    & \times
+    &\times
     \left[
@@
 \end{equation}
+}
 %===============================================================================
@@
 \end{equation}
-with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and we can express this as
+with {\color{Red}$\sigma^0 = \flatfrac{e^2l_0^2}{(\pi \hbar A)}$}, and we can express this as
 \begin{equation} \label{eq:38}
@@
 These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
-As the authors remarked in that publication, since the Fermi level of the system can be changed with the applied gate voltage of the material, this can be utilized as a 2D switch for nanoscale optoelectronics applications.
-Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
 However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_4}
+\includegraphics[scale=0.54]{fig_4_conductivity_with_fermi_level}
 \caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \begin{figure}[t]
-\includegraphics[scale=0.54]{figures/fig_5}
+\includegraphics[scale=0.54]{fig_5_conductivity_with_fermi_level_zoomed}
 \caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
@@
 \end{figure}
-%===============================================================================
-
-%===============================================================================
-% Section 07 : Conclusions
-%===============================================================================
-\section{\label{sec_conclusions} Conclusions}
+
+{\color{Red}
+By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are a repetition of the Shubnikov–de Haas(SdH) oscillations.
+As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
+Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
+The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
+Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
+The  change of the gate voltage applied to the system will modify the Fermi level of the system.
+Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
+This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+By comparing these empirical observations with our results given in Fig.
+[4], we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
+Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
+This will locate to the Fermi level on higher-order Landau levels.
+As illustrated in Fig.~[4], this will result in a higher conductivity peak value at the higher-order Landau levels.
+This same behavior was also observed in the experimental observations presented in Ref.
+\cite{wakabayashi78} as well.
+However, in our analysis, we have analytically explained the controllability of these conductivity regions using a dressing field.
+Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
+However, these experiments and theoretical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
+It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
+In our case, the applied dressing field is in the off-resonant range and that will only change the broadening of Landau levels and avoid any contribution towards the photon absorptions.
+This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
+Therefore our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
+}
+%===============================================================================
+
+%===============================================================================
+% Section 07 : Physical significance of the outcome
+%===============================================================================
+{\color{Red}
+\section{\label{sec:physical_significance} Physical Significance of the Outcomes}
+With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
+The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
+The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
+This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically.
+The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
+However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low-temperatures is the disorders in materials \cite{ando85,dial07}.
+The broaden sequence of delta functions of density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
+\cite{endo09,wakabayashi78}.
+
+Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
+As illustrated in Fig.
+4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Ref.\cite{endo09,wakabayashi78} through our model.
+Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
+However, from our results given in Fig.
+5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.
+
+Research on novel states of matter has driven the evolution of present-day nanoelectronic devices.
+In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
+The charge carrier concentration of a considering system is an imperative parameter that defines the conductivity properties of the system.
+We can manipulate that using the electrostatic field-effect mechanism and it is an ideal tool to control the conductivity in some specific systems.
+A 2DEG under static magnetic field with quantum Hall effects is an excellent example that the gate electric field can be used to manipulate the conductivity.
+A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the charge transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
+In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures.
+Since the Fermi level of the system can be altered with the applied gate voltage, this behavior can be easily mapped into our results given in Fig.
+4.
+However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field.
+Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general mathematical description to manipulate longitudinal conductivity broadening using only a high-intensity electromagnetic field.
+
+The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
+In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
+As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field.
+This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
+Furthermore, adopting the mechanism presented in Ref.\cite{hirakawa01}, we can utilize our manipulation of conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
+Based on these ready-to-use nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers the potential to realize advanced nanoelectronic devices.
+Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
+}
+%===============================================================================
+
+%===============================================================================
+% Section 08 : Conclusions
+%===============================================================================
+\section{\label{sec:conclusions} Conclusions}
 
@@
 We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method.
-We assumed the impurities in the material as a Gaussian random scattering potential.
-Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
+{\color{Red}
+We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within an order where we can neglect effects of the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions.} Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
 
@@
 Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels.
-Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.
-However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.
+{\color{Red}Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results do not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}.
+This is due to the fact that the authors of Ref.\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Ref.\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
+However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.}
 
@@
 \begin{figure}[b]
-  \includegraphics[scale=1.0]{figures/fig_6.pdf}
+  \includegraphics[scale=1.0]{fig_6_scattering_scenario.pdf}
   \caption{Scattering from known $\ket{\psi_{\beta}(t,t')}$ state to a constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to the scattering potential created by impurities in the material.}
@@
 %===============================================================================
+{\color{Red}
 \section{\label{appendix_d} Current operators for a dressed quantum Hall system}
@@
 \end{equation}
-Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
+Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59,boyd18}
 \begin{subequations} \label{eq:d8}
@@
     y \chi_{n}({y})\chi_{n'}({y}) d{y} &=
+    \frac{1}{\kappa}
     \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
@@
     &\left({j}_x \right)_{nm,n'm'} =
-    \frac{eB}{{\widetilde{m}}}
+    \frac{eB}{{\widetilde{m}}\kappa}
     \delta_{k_x,k'_x} \\
@@
       \left({j}_x \right)_{nm,n'm'} =&
-      \frac{eB}{\widetilde{m}}
+      \frac{eB}{\widetilde{m}\kappa}
       \delta_{k_x,k'_x} \\
@@
       \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
-      \frac{e^2B}{{m_e}}
+      \frac{e\hbar}{{m_e}l_0}
       \delta_{k_x,k'_x}\\
@@
       \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-      \delta_{n',n-1} \right).
-  \end{aligned}
-\end{equation}
+      \delta_{n',n-1} \right),
+  \end{aligned}
+\end{equation}
+where $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$ is the magnetic length.
 
@@
 \end{equation}
-After following the same steps done for the $x$-directional current operator, we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
+After following the same steps done for the $x$-directional current operator, and recursion relation of the first derivative of Gauss-Hermite functions \cite{boyd18}
 \begin{equation} \label{eq:d14}
   \begin{aligned}
+    \pdv{\chi_{n}({y})}{y} =
+    \kappa\left[
+    -  \sqrt{\frac{n+1}{2}} \chi_{n+1}({y})
+    +  \sqrt{\frac{n}{2}} \chi_{n - 1}({y})
+    \right],
+  \end{aligned}
+\end{equation}
+we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
+\begin{equation} \label{eq:d15}
+  \begin{aligned}
     \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
-    \frac{ie\hbar}{{m_e}}
+    \frac{ie\hbar\kappa}{{m_e}}
+    \delta_{k_x,k'_x} \\
+    & \times
+    \left(
+    \sqrt{\frac{n}{2}} \delta_{n',n-1}
+    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
+    \right),
+  \end{aligned}
+\end{equation}
+and
+\begin{equation} \label{eq:d15}
+  \begin{aligned}
+    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
+    \frac{ie\hbar}{{m_e}l_0}
     \delta_{k_x,k'_x} \\
@@
 \end{equation}
-%===============================================================================
-\end{appendix}
-
+}
 %===============================================================================
 % Bibliography
-%===============================================================================
-\bibliography{aps_article}
-%===============================================================================
+\bibliography{dressed_quantum_hall_res}
+%===============================================================================
+% Bibliography
+%===============================================================================
+%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
+%Control: key (0)
+%Control: author (72) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+
+%%%>>>>>>9294<<<<
+% \providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}%
+% \begin{thebibliography}{73}%
+% \makeatletter
+% \providecommand \@ifxundefined [1]{%
+%  \@ifx{#1\undefined}
+% }%
+% \providecommand \@ifnum [1]{%
+%  \ifnum #1\expandafter \@firstoftwo
+%  \else \expandafter \@secondoftwo
+%  \fi
+% }%
+% \providecommand \@ifx [1]{%
+%  \ifx #1\expandafter \@firstoftwo
+%  \else \expandafter \@secondoftwo
+%  \fi
+% }%
+% \providecommand \natexlab [1]{#1}%
+% \providecommand \enquote  [1]{``#1''}%
+% \providecommand \bibnamefont  [1]{#1}%
+% \providecommand \bibfnamefont [1]{#1}%
+% \providecommand \citenamefont [1]{#1}%
+% \providecommand \href@noop [0]{\@secondoftwo}%
+% \providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+% \providecommand \@href[1]{\@@startlink{#1}\@@href}%
+% \providecommand \@@href[1]{\endgroup#1\@@endlink}%
+% \providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+%   `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+% \providecommand \@@startlink[1]{}%
+% \providecommand \@@endlink[0]{}%
+% \providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+% \providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+% \providecommand \urlprefix  [0]{URL }%
+% \providecommand \Eprint [0]{\href }%
+% \providecommand \doibase [0]{https://doi.org/}%
+% \providecommand \selectlanguage [0]{\@gobble}%
+% \providecommand \bibinfo  [0]{\@secondoftwo}%
+% \providecommand \bibfield  [0]{\@secondoftwo}%
+% \providecommand \translation [1]{[#1]}%
+% \providecommand \BibitemOpen [0]{}%
+% \providecommand \bibitemStop [0]{}%
+% \providecommand \bibitemNoStop [0]{.\EOS\space}%
+% \providecommand \EOS [0]{\spacefactor3000\relax}%
+% \providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+% \let\auto@bib@innerbib\@empty
+% %</preamble>
+% \bibitem [{\citenamefont {Liu}\ \emph {et~al.}(2016)\citenamefont {Liu},
+%   \citenamefont {Weiss}, \citenamefont {Duan}, \citenamefont {Cheng},
+%   \citenamefont {Huang},\ and\ \citenamefont {Duan}}]{liu16}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+%   {Liu}}, \bibinfo {author} {\bibfnamefont {N.~O.}\ \bibnamefont {Weiss}},
+%   \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Duan}}, \bibinfo {author}
+%   {\bibfnamefont {H.~C.}\ \bibnamefont {Cheng}}, \bibinfo {author}
+%   {\bibfnamefont {Y.}~\bibnamefont {Huang}},\ and\ \bibinfo {author}
+%   {\bibfnamefont {X.}~\bibnamefont {Duan}},\ }\href
+%   {https://doi.org/10.1038/natrevmats.2016.42} {\bibfield  {journal} {\bibinfo
+%   {journal} {Nat. Rev. Mater.}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo
+%   {pages} {16042} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Wijesekara}\ \emph {et~al.}(2020)\citenamefont
+%   {Wijesekara}, \citenamefont {Gunapala}, \citenamefont {Stockman},\ and\
+%   \citenamefont {Premaratne}}]{wijesekara20}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~T.}\ \bibnamefont
+%   {Wijesekara}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+%   {Gunapala}}, \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont
+%   {Stockman}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Premaratne}},\ }\href {https://doi.org/10.1103/PhysRevB.101.245402}
+%   {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
+%   {volume} {101}},\ \bibinfo {pages} {245402} (\bibinfo {year}
+%   {2020})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Tao}\ \emph {et~al.}(2020)\citenamefont {Tao},
+%   \citenamefont {Chen}, \citenamefont {Li}, \citenamefont {Wang}, \citenamefont
+%   {Xu},\ and\ \citenamefont {Xu}}]{tao21}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+%   {Tao}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Chen}}, \bibinfo
+%   {author} {\bibfnamefont {Z.}~\bibnamefont {Li}}, \bibinfo {author}
+%   {\bibfnamefont {J.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont
+%   {X.}~\bibnamefont {Xu}},\ and\ \bibinfo {author} {\bibfnamefont {J.-B.}\
+%   \bibnamefont {Xu}},\ }\href {https://doi.org/10.1002/inf2.12148} {\bibfield
+%   {journal} {\bibinfo  {journal} {InfoMat}\ }\textbf {\bibinfo {volume} {3}},\
+%   \bibinfo {pages} {36} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Wijesekara}\ \emph {et~al.}(2021)\citenamefont
+%   {Wijesekara}, \citenamefont {Gunapala},\ and\ \citenamefont
+%   {Premaratne}}]{wijesekara21}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~T.}\ \bibnamefont
+%   {Wijesekara}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+%   {Gunapala}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Premaratne}},\ }\href {https://doi.org/10.1103/PhysRevB.104.045405}
+%   {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
+%   {volume} {104}},\ \bibinfo {pages} {045405} (\bibinfo {year}
+%   {2021})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Rodrigo}\ \emph {et~al.}(2015)\citenamefont
+%   {Rodrigo}, \citenamefont {Limaj}, \citenamefont {Janner}, \citenamefont
+%   {Etezadi}, \citenamefont {De~Abajo}, \citenamefont {Pruneri},\ and\
+%   \citenamefont {Altug}}]{rodrigo15}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+%   {Rodrigo}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Limaj}},
+%   \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Janner}}, \bibinfo
+%   {author} {\bibfnamefont {D.}~\bibnamefont {Etezadi}}, \bibinfo {author}
+%   {\bibfnamefont {F.~J.~G.}\ \bibnamefont {De~Abajo}}, \bibinfo {author}
+%   {\bibfnamefont {V.}~\bibnamefont {Pruneri}},\ and\ \bibinfo {author}
+%   {\bibfnamefont {H.}~\bibnamefont {Altug}},\ }\href
+%   {https://doi.org/10.1126/science.aab2051} {\bibfield  {journal} {\bibinfo
+%   {journal} {Science}\ }\textbf {\bibinfo {volume} {349}},\ \bibinfo {pages}
+%   {165} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Pirandola}\ \emph {et~al.}(2018)\citenamefont
+%   {Pirandola}, \citenamefont {Bardhan}, \citenamefont {Gehring}, \citenamefont
+%   {Weedbrook},\ and\ \citenamefont {Lloyd}}]{pirandola18}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+%   {Pirandola}}, \bibinfo {author} {\bibfnamefont {B.~R.}\ \bibnamefont
+%   {Bardhan}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Gehring}},
+%   \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Weedbrook}},\ and\
+%   \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Lloyd}},\ }\href
+%   {https://doi.org/10.1038/s41566-018-0301-6} {\bibfield  {journal} {\bibinfo
+%   {journal} {Nat. Photoics}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo
+%   {pages} {724} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Hapuarachchi}\ \emph {et~al.}(2018)\citenamefont
+%   {Hapuarachchi}, \citenamefont {Mallawaarachchi}, \citenamefont {Hattori},
+%   \citenamefont {Zhu},\ and\ \citenamefont {Premaratne}}]{hapuarachchi2018}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+%   {Hapuarachchi}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+%   {Mallawaarachchi}}, \bibinfo {author} {\bibfnamefont {H.~T.}\ \bibnamefont
+%   {Hattori}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Zhu}},\ and\
+%   \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Premaratne}},\ }\href
+%   {https://doi.org/10.1088/1361-648X/aaa46d} {\bibfield  {journal} {\bibinfo
+%   {journal} {J. Phys. Condens. Matter.}\ }\textbf {\bibinfo {volume} {30}},\
+%   \bibinfo {pages} {054006} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Weeraddana}\ \emph {et~al.}(2015)\citenamefont
+%   {Weeraddana}, \citenamefont {Premaratne},\ and\ \citenamefont
+%   {Andrews}}]{weeraddana15}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+%   {Weeraddana}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Premaratne}},\ and\ \bibinfo {author} {\bibfnamefont {D.~L.}\ \bibnamefont
+%   {Andrews}},\ }\href {https://10.1103/PhysRevB.92.035128} {\bibfield
+%   {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+%   {92}},\ \bibinfo {pages} {035128} (\bibinfo {year} {2015})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Yuan}\ \emph {et~al.}(2016)\citenamefont {Yuan},
+%   \citenamefont {Liu},\ and\ \citenamefont {Sargent}}]{yuan16}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Yuan}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}},\ and\
+%   \bibinfo {author} {\bibfnamefont {E.~H.}\ \bibnamefont {Sargent}},\ }\href
+%   {https://doi.org/10.1038/nenergy.2016.16} {\bibfield  {journal} {\bibinfo
+%   {journal} {Nature Energy}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo
+%   {pages} {16016} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Sun}\ \emph {et~al.}(2018)\citenamefont {Sun},
+%   \citenamefont {Ouellette}, \citenamefont {de~Arquer}, \citenamefont {Voznyy},
+%   \citenamefont {Kim}, \citenamefont {Wei}, \citenamefont {Proppe},
+%   \citenamefont {Saidaminov}, \citenamefont {Xu}, \citenamefont {Liu} \emph
+%   {et~al.}}]{sun18}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+%   {Sun}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Ouellette}},
+%   \bibinfo {author} {\bibfnamefont {F.~P.~G.}\ \bibnamefont {de~Arquer}},
+%   \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Voznyy}}, \bibinfo
+%   {author} {\bibfnamefont {Y.}~\bibnamefont {Kim}}, \bibinfo {author}
+%   {\bibfnamefont {M.}~\bibnamefont {Wei}}, \bibinfo {author} {\bibfnamefont
+%   {A.~H.}\ \bibnamefont {Proppe}}, \bibinfo {author} {\bibfnamefont {M.~I.}\
+%   \bibnamefont {Saidaminov}}, \bibinfo {author} {\bibfnamefont
+%   {J.}~\bibnamefont {Xu}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Liu}}, \emph {et~al.},\ }\href {https://doi.org/10.1038/s41467-018-06342-7}
+%   {\bibfield  {journal} {\bibinfo  {journal} {Nat. Commun.}\ }\textbf {\bibinfo
+%   {volume} {9}},\ \bibinfo {pages} {4003} (\bibinfo {year} {2018})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Huh}\ \emph {et~al.}(2015)\citenamefont {Huh},
+%   \citenamefont {Guerreschi}, \citenamefont {Peropadre}, \citenamefont
+%   {McClean},\ and\ \citenamefont {Aspuru-Guzik}}]{huh15}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+%   {Huh}}, \bibinfo {author} {\bibfnamefont {G.~G.}\ \bibnamefont {Guerreschi}},
+%   \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Peropadre}}, \bibinfo
+%   {author} {\bibfnamefont {J.~R.}\ \bibnamefont {McClean}},\ and\ \bibinfo
+%   {author} {\bibfnamefont {A.}~\bibnamefont {Aspuru-Guzik}},\ }\href
+%   {https://doi.org/10.1038/nphoton.2015.153} {\bibfield  {journal} {\bibinfo
+%   {journal} {Nat. Photonics}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo
+%   {pages} {615} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Slussarenko}\ and\ \citenamefont
+%   {Pryde}(2019)}]{slussarenko19}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+%   {Slussarenko}}\ and\ \bibinfo {author} {\bibfnamefont {G.~J.}\ \bibnamefont
+%   {Pryde}},\ }\href {https://doi.org/10.1063/1.5115814} {\bibfield  {journal}
+%   {\bibinfo  {journal} {Appl. Phys. Rev.}\ }\textbf {\bibinfo {volume} {6}},\
+%   \bibinfo {pages} {041303} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Andersen}(2021)}]{andersen21}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.~L.}\ \bibnamefont
+%   {Andersen}},\ }\href {https://doi.org/10.1038/d41586-021-00488-z} {\bibfield
+%   {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo {volume} {591}},\
+%   \bibinfo {pages} {40} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Marais}\ \emph {et~al.}(2018)\citenamefont {Marais},
+%   \citenamefont {Adams}, \citenamefont {Ringsmuth}, \citenamefont {Ferretti},
+%   \citenamefont {Gruber}, \citenamefont {Hendrikx}, \citenamefont {Schuld},
+%   \citenamefont {Smith}, \citenamefont {Sinayskiy}, \citenamefont {Kr{\"u}ger}
+%   \emph {et~al.}}]{marais18}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%   {Marais}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Adams}},
+%   \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont {Ringsmuth}}, \bibinfo
+%   {author} {\bibfnamefont {M.}~\bibnamefont {Ferretti}}, \bibinfo {author}
+%   {\bibfnamefont {J.~M.}\ \bibnamefont {Gruber}}, \bibinfo {author}
+%   {\bibfnamefont {R.}~\bibnamefont {Hendrikx}}, \bibinfo {author}
+%   {\bibfnamefont {M.}~\bibnamefont {Schuld}}, \bibinfo {author} {\bibfnamefont
+%   {S.~L.}\ \bibnamefont {Smith}}, \bibinfo {author} {\bibfnamefont
+%   {I.}~\bibnamefont {Sinayskiy}}, \bibinfo {author} {\bibfnamefont {T.~P.}\
+%   \bibnamefont {Kr{\"u}ger}}, \emph {et~al.},\ }\href
+%   {https://doi.org/10.1098/rsif.2018.0640} {\bibfield  {journal} {\bibinfo
+%   {journal} {J. R. Soc. Interface}\ }\textbf {\bibinfo {volume} {15}},\
+%   \bibinfo {pages} {20180640} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Bian}\ \emph {et~al.}(2020)\citenamefont {Bian},
+%   \citenamefont {Sun}, \citenamefont {Cai}, \citenamefont {Wang},\ and\
+%   \citenamefont {Zhao}}]{bian20}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+%   {Bian}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Sun}}, \bibinfo
+%   {author} {\bibfnamefont {L.}~\bibnamefont {Cai}}, \bibinfo {author}
+%   {\bibfnamefont {Y.}~\bibnamefont {Wang}},\ and\ \bibinfo {author}
+%   {\bibfnamefont {Y.}~\bibnamefont {Zhao}},\ }\href
+%   {https://doi.org/10.1073/pnas.2011660117} {\bibfield  {journal} {\bibinfo
+%   {journal} {Proc. Natl. Acad. Sci.}\ }\textbf {\bibinfo {volume} {117}},\
+%   \bibinfo {pages} {22736} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Rivera}\ and\ \citenamefont
+%   {Kaminer}(2020)}]{rivera20}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+%   {Rivera}}\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+%   {Kaminer}},\ }\href {https://doi.org/10.1038/s42254-020-0224-2} {\bibfield
+%   {journal} {\bibinfo  {journal} {Nat. Rev. Phys.}\ }\textbf {\bibinfo {volume}
+%   {2}},\ \bibinfo {pages} {538} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Shalaev}(2007)}]{shalaev07}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~M.}\ \bibnamefont
+%   {Shalaev}},\ }\href {https://doi.org/10.1038/nphoton.2006.49} {\bibfield
+%   {journal} {\bibinfo  {journal} {Nat. Photonics}\ }\textbf {\bibinfo {volume}
+%   {1}},\ \bibinfo {pages} {41} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Si}\ \emph {et~al.}(2014)\citenamefont {Si},
+%   \citenamefont {Sikdar}, \citenamefont {Chen}, \citenamefont {Eftekhari},
+%   \citenamefont {Xu}, \citenamefont {Tang}, \citenamefont {Xiong},
+%   \citenamefont {Guo}, \citenamefont {Zhang}, \citenamefont {Lu} \emph
+%   {et~al.}}]{si14}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~J.}\ \bibnamefont
+%   {Si}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Sikdar}}, \bibinfo
+%   {author} {\bibfnamefont {Y.}~\bibnamefont {Chen}}, \bibinfo {author}
+%   {\bibfnamefont {F.}~\bibnamefont {Eftekhari}}, \bibinfo {author}
+%   {\bibfnamefont {Z.}~\bibnamefont {Xu}}, \bibinfo {author} {\bibfnamefont
+%   {Y.}~\bibnamefont {Tang}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+%   {Xiong}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Guo}}, \bibinfo
+%   {author} {\bibfnamefont {S.}~\bibnamefont {Zhang}}, \bibinfo {author}
+%   {\bibfnamefont {Y.}~\bibnamefont {Lu}}, \emph {et~al.},\ }\href
+%   {https://doi.org/10.1021/nn504615a} {\bibfield  {journal} {\bibinfo
+%   {journal} {ACS Nano}\ }\textbf {\bibinfo {volume} {8}},\ \bibinfo {pages}
+%   {11086} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Hapuarachchi}\ \emph {et~al.}(2019)\citenamefont
+%   {Hapuarachchi}, \citenamefont {Gunapala},\ and\ \citenamefont
+%   {Premaratne}}]{hapuarachchi19}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+%   {Hapuarachchi}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+%   {Gunapala}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Premaratne}},\ }\href {https://doi.org/10.1088/1361-648X/ab1234} {\bibfield
+%   {journal} {\bibinfo  {journal} {J. Phys. Condens. Matter.}\ }\textbf
+%   {\bibinfo {volume} {31}},\ \bibinfo {pages} {325301} (\bibinfo {year}
+%   {2019})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Perera}\ \emph {et~al.}(2020)\citenamefont {Perera},
+%   \citenamefont {Gunapala}, \citenamefont {Stockman},\ and\ \citenamefont
+%   {Premaratne}}]{perera20}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%   {Perera}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+%   {Gunapala}}, \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont
+%   {Stockman}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Premaratne}},\ }\href {https://doi.org/10.1021/acs.jpcc.0c10507} {\bibfield
+%   {journal} {\bibinfo  {journal} {J. Phys. Chem. C}\ }\textbf {\bibinfo
+%   {volume} {124}},\ \bibinfo {pages} {27694} (\bibinfo {year}
+%   {2020})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Chow}\ and\ \citenamefont {Jahnke}(2013)}]{chow13}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~W.}\ \bibnamefont
+%   {Chow}}\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Jahnke}},\
+%   }\href {https://doi.org/10.1016/j.pquantelec.2013.04.001} {\bibfield
+%   {journal} {\bibinfo  {journal} {Prog. Quantum. Electron.}\ }\textbf {\bibinfo
+%   {volume} {37}},\ \bibinfo {pages} {109} (\bibinfo {year} {2013})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Jayasekara}\ \emph {et~al.}(2016)\citenamefont
+%   {Jayasekara}, \citenamefont {Premaratne}, \citenamefont {Gunapala},\ and\
+%   \citenamefont {Stockman}}]{jayasekara16}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+%   {Jayasekara}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Premaratne}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont
+%   {Gunapala}},\ and\ \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont
+%   {Stockman}},\ }\href {https://doi.org/10.1063/1.4945378} {\bibfield
+%   {journal} {\bibinfo  {journal} {J. Appl. Phys.}\ }\textbf {\bibinfo {volume}
+%   {119}},\ \bibinfo {pages} {133101} (\bibinfo {year} {2016})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Premaratne}\ and\ \citenamefont
+%   {Stockman}(2017)}]{premaratne17}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Premaratne}}\ and\ \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont
+%   {Stockman}},\ }\href {https://doi.org/10.1364/AOP.9.000079} {\bibfield
+%   {journal} {\bibinfo  {journal} {Adv. Opt. Photonics}\ }\textbf {\bibinfo
+%   {volume} {9}},\ \bibinfo {pages} {79} (\bibinfo {year} {2017})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Tsang}(2010)}]{tsang10}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Tsang}},\ }\href {https://doi.org/10.1103/PhysRevA.81.063837} {\bibfield
+%   {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+%   {81}},\ \bibinfo {pages} {063837} (\bibinfo {year} {2010})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Liu}\ \emph {et~al.}(2017)\citenamefont {Liu},
+%   \citenamefont {Zhu}, \citenamefont {Gunapala}, \citenamefont {Stockman},\
+%   and\ \citenamefont {Premaratne}}]{liu17}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+%   {Liu}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Zhu}}, \bibinfo
+%   {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Gunapala}}, \bibinfo {author}
+%   {\bibfnamefont {M.~I.}\ \bibnamefont {Stockman}},\ and\ \bibinfo {author}
+%   {\bibfnamefont {M.}~\bibnamefont {Premaratne}},\ }\href
+%   {https://doi.org/10.1021/acsnano.7b06735} {\bibfield  {journal} {\bibinfo
+%   {journal} {ACS Nano}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages}
+%   {12573} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Devi}\ \emph {et~al.}(2020)\citenamefont {Devi},
+%   \citenamefont {Gunapala}, \citenamefont {Stockman},\ and\ \citenamefont
+%   {Premaratne}}]{devi20}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%   {Devi}}, \bibinfo {author} {\bibfnamefont {S.~D.}\ \bibnamefont {Gunapala}},
+%   \bibinfo {author} {\bibfnamefont {M.~I.}\ \bibnamefont {Stockman}},\ and\
+%   \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Premaratne}},\ }\href
+%   {https://doi.org/10.1103/PhysRevA.102.013701} {\bibfield  {journal} {\bibinfo
+%    {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {102}},\ \bibinfo
+%   {pages} {013701} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Kitagawa}\ \emph {et~al.}(2011)\citenamefont
+%   {Kitagawa}, \citenamefont {Oka}, \citenamefont {Brataas}, \citenamefont
+%   {Fu},\ and\ \citenamefont {Demler}}]{kitagawa11}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%   {Kitagawa}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Oka}},
+%   \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Brataas}}, \bibinfo
+%   {author} {\bibfnamefont {L.}~\bibnamefont {Fu}},\ and\ \bibinfo {author}
+%   {\bibfnamefont {E.}~\bibnamefont {Demler}},\ }\href
+%   {https://doi.org/10.1103/PhysRevB.84.235108} {\bibfield  {journal} {\bibinfo
+%   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {84}},\ \bibinfo
+%   {pages} {235108} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Zhou}\ and\ \citenamefont {Wu}(2011)}]{zhou11}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+%   {Zhou}}\ and\ \bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont {Wu}},\
+%   }\href {https://doi.org/10.1103/PhysRevB.83.245436} {\bibfield  {journal}
+%   {\bibinfo  {journal} {Phys.Rev.B}\ }\textbf {\bibinfo {volume} {83}},\
+%   \bibinfo {pages} {245436} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Kibis}(2014)}]{kibis14}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.~V.}\ \bibnamefont
+%   {Kibis}},\ }\href {https://doi.org/10.1209/0295-5075/107/57003} {\bibfield
+%   {journal} {\bibinfo  {journal} {Europhys. Lett.}\ }\textbf {\bibinfo {volume}
+%   {107}},\ \bibinfo {pages} {57003} (\bibinfo {year} {2014})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Pervishko}\ \emph {et~al.}(2015)\citenamefont
+%   {Pervishko}, \citenamefont {Kibis}, \citenamefont {Morina},\ and\
+%   \citenamefont {Shelykh}}]{pervishko15}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont
+%   {Pervishko}}, \bibinfo {author} {\bibfnamefont {O.~V.}\ \bibnamefont
+%   {Kibis}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Morina}},\ and\
+%   \bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont {Shelykh}},\ }\href
+%   {https://doi.org/10.1103/PhysRevB.92.205403} {\bibfield  {journal} {\bibinfo
+%   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo
+%   {pages} {205403} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Morina}\ \emph {et~al.}(2015)\citenamefont {Morina},
+%   \citenamefont {Kibis}, \citenamefont {Pervishko},\ and\ \citenamefont
+%   {Shelykh}}]{morina15}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+%   {Morina}}, \bibinfo {author} {\bibfnamefont {O.~V.}\ \bibnamefont {Kibis}},
+%   \bibinfo {author} {\bibfnamefont {A.~A.}\ \bibnamefont {Pervishko}},\ and\
+%   \bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont {Shelykh}},\ }\href
+%   {https://doi.org/10.1103/PhysRevB.91.155312} {\bibfield  {journal} {\bibinfo
+%   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {91}},\ \bibinfo
+%   {pages} {155312} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Dehghani}\ \emph {et~al.}(2015)\citenamefont
+%   {Dehghani}, \citenamefont {Oka},\ and\ \citenamefont {Mitra}}]{dehghani15}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+%   {Dehghani}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Oka}},\ and\
+%   \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Mitra}},\ }\href
+%   {https://doi.org/10.1103/PhysRevB.91.155422} {\bibfield  {journal} {\bibinfo
+%   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {91}},\ \bibinfo
+%   {pages} {155422} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Dini}\ \emph {et~al.}(2016)\citenamefont {Dini},
+%   \citenamefont {Kibis},\ and\ \citenamefont {Shelykh}}]{dini16}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+%   {Dini}}, \bibinfo {author} {\bibfnamefont {O.~V.}\ \bibnamefont {Kibis}},\
+%   and\ \bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont {Shelykh}},\
+%   }\href {https://doi.org/10.1103/PhysRevB.93.235411} {\bibfield  {journal}
+%   {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {93}},\
+%   \bibinfo {pages} {235411} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Wackerl}\ \emph {et~al.}(2020)\citenamefont
+%   {Wackerl}, \citenamefont {Wenk},\ and\ \citenamefont
+%   {Schliemann}}]{wackerl20}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Wackerl}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Wenk}},\ and\
+%   \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Schliemann}},\ }\href
+%   {https://doi.org/10.1103/PhysRevB.101.184204} {\bibfield  {journal} {\bibinfo
+%    {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {101}},\ \bibinfo
+%   {pages} {184204} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Premaratne}\ and\ \citenamefont
+%   {Agrawal}(2021)}]{premaratne21}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Premaratne}}\ and\ \bibinfo {author} {\bibfnamefont {G.~P.}\ \bibnamefont
+%   {Agrawal}},\ }\href@noop {} {\emph {\bibinfo {title} {Theoretical Foundations
+%   of Nanoscale Quantum Devices}}}\ (\bibinfo  {publisher} {Cambridge University
+%   Press},\ \bibinfo {year} {2021})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Grifoni}\ and\ \citenamefont
+%   {Hänggi}(1998)}]{grifoni98}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Grifoni}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+%   {Hänggi}},\ }\href {https://doi.org/10.1016/S0370-1573(98)00022-2}
+%   {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rep.}\ }\textbf {\bibinfo
+%   {volume} {304}},\ \bibinfo {pages} {229} (\bibinfo {year}
+%   {1998})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Cohen-Tannoudji}\ \emph {et~al.}(1998)\citenamefont
+%   {Cohen-Tannoudji}, \citenamefont {Dupont-Roc},\ and\ \citenamefont
+%   {Grynberg}}]{cohen98}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+%   {Cohen-Tannoudji}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+%   {Dupont-Roc}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+%   {Grynberg}},\ }\href@noop {} {\emph {\bibinfo {title} {Atom—Photon
+%   Interactions}}}\ (\bibinfo  {publisher} {John Wiley \& Sons, Ltd},\ \bibinfo
+%   {year} {1998})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Scully}\ and\ \citenamefont
+%   {Zubairy}(2001)}]{scully01}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Scully}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Zubairy}},\ }\href@noop {} {\emph {\bibinfo {title} {Introduction to Quantum
+%   Optics}}}\ (\bibinfo  {publisher} {Cambridge University Press},\ \bibinfo
+%   {year} {2001})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Girvin}\ and\ \citenamefont
+%   {Prange}(1990)}]{girvin90}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+%   {Girvin}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+%   {Prange}},\ }\href@noop {} {\emph {\bibinfo {title} {The quantum Hall
+%   effect}}}\ (\bibinfo  {publisher} {Springer-Verlag, New York},\ \bibinfo
+%   {year} {1990})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Ando}\ \emph {et~al.}(1972)\citenamefont {Ando},
+%   \citenamefont {Matsumoto}, \citenamefont {Uemura}, \citenamefont
+%   {Kobayashi},\ and\ \citenamefont {Komatsubara}}]{ando72}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%   {Ando}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Matsumoto}},
+%   \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Uemura}}, \bibinfo
+%   {author} {\bibfnamefont {M.}~\bibnamefont {Kobayashi}},\ and\ \bibinfo
+%   {author} {\bibfnamefont {K.~F.}\ \bibnamefont {Komatsubara}},\ }\href
+%   {https://doi.org/10.1143/JPSJ.32.859} {\bibfield  {journal} {\bibinfo
+%   {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume} {32}},\ \bibinfo
+%   {pages} {859} (\bibinfo {year} {1972})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Ando}\ and\ \citenamefont
+%   {Uemura}(1974{\natexlab{a}})}]{ando74_1}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%   {Ando}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Uemura}},\
+%   }\href {https://doi.org/10.1143/JPSJ.36.959} {\bibfield  {journal} {\bibinfo
+%   {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume} {36}},\ \bibinfo
+%   {pages} {959} (\bibinfo {year} {1974}{\natexlab{a}})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Ando}(1974{\natexlab{a}})}]{ando74_2}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%   {Ando}},\ }\href {https://doi.org/10.1143/JPSJ.36.1521} {\bibfield  {journal}
+%   {\bibinfo  {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume}
+%   {36}},\ \bibinfo {pages} {1521} (\bibinfo {year}
+%   {1974}{\natexlab{a}})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Ando}(1974{\natexlab{b}})}]{ando74_3}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%   {Ando}},\ }\href {https://doi.org/10.1143/JPSJ.37.622} {\bibfield  {journal}
+%   {\bibinfo  {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume}
+%   {37}},\ \bibinfo {pages} {622} (\bibinfo {year}
+%   {1974}{\natexlab{b}})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Ando}\ and\ \citenamefont
+%   {Uemura}(1974{\natexlab{b}})}]{ando74_4}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%   {Ando}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Uemura}},\
+%   }\href {https://doi.org/10.1143/JPSJ.37.1233} {\bibfield  {journal} {\bibinfo
+%    {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo {volume} {37}},\ \bibinfo
+%   {pages} {1233} (\bibinfo {year} {1974}{\natexlab{b}})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Ando}\ \emph {et~al.}(1982)\citenamefont {Ando},
+%   \citenamefont {Fowler},\ and\ \citenamefont {Stern}}]{ando82}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%   {Ando}}, \bibinfo {author} {\bibfnamefont {A.~B.}\ \bibnamefont {Fowler}},\
+%   and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Stern}},\ }\href
+%   {https://doi.org/10.1103/RevModPhys.54.437} {\bibfield  {journal} {\bibinfo
+%   {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {54}},\ \bibinfo
+%   {pages} {437} (\bibinfo {year} {1982})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Endo}\ \emph {et~al.}(2009)\citenamefont {Endo},
+%   \citenamefont {Hatano}, \citenamefont {Nakamura},\ and\ \citenamefont
+%   {Shirasaki}}]{endo09}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%   {Endo}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Hatano}},
+%   \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Nakamura}},\ and\
+%   \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Shirasaki}},\ }\href
+%   {https://doi.org/10.1088/0953-8984/21/34/345803} {\bibfield  {journal}
+%   {\bibinfo  {journal} {J. Phys.: Condens. Matter}\ }\textbf {\bibinfo {volume}
+%   {21}},\ \bibinfo {pages} {345803} (\bibinfo {year} {2009})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Allerman}\ \emph {et~al.}(1995)\citenamefont
+%   {Allerman}, \citenamefont {Xu}, \citenamefont {Hauser},\ and\ \citenamefont
+%   {Jagadish}}]{allerman95}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%   {Allerman}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Xu}},
+%   \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Hauser}},\ and\ \bibinfo
+%   {author} {\bibfnamefont {C.}~\bibnamefont {Jagadish}},\ }\href
+%   {https://doi.org/10.1063/1.358844} {\bibfield  {journal} {\bibinfo  {journal}
+%   {J. Appl. Phys.}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo {pages} {2052}
+%   (\bibinfo {year} {1995})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Tieke}\ \emph {et~al.}(1997)\citenamefont {Tieke},
+%   \citenamefont {Fletcher}, \citenamefont {Zeitler}, \citenamefont {Geim},
+%   \citenamefont {Henini},\ and\ \citenamefont {Maan}}]{tieke97}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+%   {Tieke}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Fletcher}},
+%   \bibinfo {author} {\bibfnamefont {U.}~\bibnamefont {Zeitler}}, \bibinfo
+%   {author} {\bibfnamefont {A.~K.}~\bibnamefont {Geim}}, \bibinfo {author}
+%   {\bibfnamefont {M.}~\bibnamefont {Henini}},\ and\ \bibinfo {author}
+%   {\bibfnamefont {J.~C.}~\bibnamefont {Maan}},\ }\href
+%   {https://doi.org/10.1103/PhysRevLett.78.4621} {\bibfield  {journal} {\bibinfo
+%    {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {78}},\ \bibinfo
+%   {pages} {4621} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Pan}\ \emph {et~al.}(2005)\citenamefont {Pan},
+%   \citenamefont {Xia}, \citenamefont {Stormer}, \citenamefont {Tsui},
+%   \citenamefont {Vicente}, \citenamefont {Adams}, \citenamefont {Sullivan},
+%   \citenamefont {Pfeiffer}, \citenamefont {Baldwin},\ and\ \citenamefont
+%   {West}}]{pan05}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+%   {Pan}}, \bibinfo {author} {\bibfnamefont {J.~S.}~\bibnamefont {Xia}}, \bibinfo
+%   {author} {\bibfnamefont {H.~L.}~\bibnamefont {Stormer}}, \bibinfo {author}
+%   {\bibfnamefont {D.~C.}~\bibnamefont {Tsui}}, \bibinfo {author} {\bibfnamefont
+%   {C.~L.}~\bibnamefont {Vicente}}, \bibinfo {author} {\bibfnamefont
+%   {E.~D.}~\bibnamefont {Adams}}, \bibinfo {author} {\bibfnamefont
+%   {N.~S.}~\bibnamefont {Sullivan}}, \bibinfo {author} {\bibfnamefont
+%   {L.~N.}~\bibnamefont {Pfeiffer}}, \bibinfo {author} {\bibfnamefont
+%   {K.~W.}~\bibnamefont {Baldwin}},\ and\ \bibinfo {author} {\bibfnamefont
+%   {K.~W.}~\bibnamefont {West}},\ }\href
+%   {https://doi.org/10.1103/PhysRevLett.95.066808} {\bibfield  {journal}
+%   {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {95}},\
+%   \bibinfo {pages} {066808} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Landau}(1930)}]{landau30}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+%   {Landau}},\ }\href {https://doi.org/10.1007/BF01397213} {\bibfield  {journal}
+%   {\bibinfo  {journal} {Z. Physik}\ }\textbf {\bibinfo {volume} {64}},\
+%   \bibinfo {pages} {629} (\bibinfo {year} {1930})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Mahan}(2000)}]{mahan00}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~D.}\ \bibnamefont
+%   {Mahan}},\ }\href@noop {} {\emph {\bibinfo {title} {Many-particle physics}}}\
+%   (\bibinfo  {publisher} {Springer Science \& Business Media, New York},\
+%   \bibinfo {year} {2000})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Bruus}\ and\ \citenamefont
+%   {Flensberg}(2004)}]{bruus04}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+%   {Bruus}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+%   {Flensberg}},\ }\href@noop {} {\emph {\bibinfo {title} {Many-body quantum
+%   theory in condensed matter physics: an introduction}}}\ (\bibinfo
+%   {publisher} {Oxford University Press, New York},\ \bibinfo {year}
+%   {2004})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Husimi}(1953)}]{husimi53}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+%   {Husimi}},\ }\href {https://doi.org/10.1143/ptp/9.4.381} {\bibfield
+%   {journal} {\bibinfo  {journal} {Prog. Theor. Phys.}\ }\textbf {\bibinfo
+%   {volume} {9}},\ \bibinfo {pages} {381} (\bibinfo {year} {1953})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Dittrich}\ \emph {et~al.}(1998)\citenamefont
+%   {Dittrich}, \citenamefont {Hänggi}, \citenamefont {Ingold}, \citenamefont
+%   {Kramer}, \citenamefont {Schön},\ and\ \citenamefont {Zwerger}}]{ditt98}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+%   {Dittrich}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Hänggi}},
+%   \bibinfo {author} {\bibfnamefont {G.~L.}\ \bibnamefont {Ingold}}, \bibinfo
+%   {author} {\bibfnamefont {B.}~\bibnamefont {Kramer}}, \bibinfo {author}
+%   {\bibfnamefont {G.}~\bibnamefont {Schön}},\ and\ \bibinfo {author}
+%   {\bibfnamefont {W.}~\bibnamefont {Zwerger}},\ }\href@noop {} {\emph {\bibinfo
+%   {title} {Quantum Transport and Dissipation}}}\ (\bibinfo  {publisher}
+%   {Wiley-VCH, Weinheim},\ \bibinfo {year} {1998})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Floquet}(1883)}]{floquet83}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+%   {Floquet}},\ }\href {https://doi.org/10.24033/asens.220} {\bibfield
+%   {journal} {\bibinfo  {journal} {Scientific annals of the École Normale
+%   Supérieure}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {47}
+%   (\bibinfo {year} {1883})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Holthaus}(2015)}]{holthaus15}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Holthaus}},\ }\href {https://doi.org/10.1088/0953-4075/49/1/013001}
+%   {\bibfield  {journal} {\bibinfo  {journal} {J. Phys. B: At., Mol. Opt.
+%   Phys.}\ }\textbf {\bibinfo {volume} {49}},\ \bibinfo {pages} {013001}
+%   (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Popov}\ and\ \citenamefont
+%   {Perelomov}(1970)}]{popov70}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+%   {Popov}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%   {Perelomov}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J.
+%   Exp. Theor. Phys.}\ }\textbf {\bibinfo {volume} {30}},\ \bibinfo {pages}
+%   {910} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Sambe}(1975)}]{sambe75}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+%   {Sambe}},\ }\href {https://doi.org/10.1103/PhysRevA.7.2203} {\bibfield
+%   {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+%   {7}},\ \bibinfo {pages} {2203} (\bibinfo {year} {1975})}\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Peskin}\ \emph {et~al.}(1994)\citenamefont {Peskin},
+%   \citenamefont {Kosloff},\ and\ \citenamefont {Moiseyev}}]{peskin93}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
+%   {Peskin}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Kosloff}},\
+%   and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Moiseyev}},\ }\href
+%   {https://doi.org/10.1063/1.466739} {\bibfield  {journal} {\bibinfo  {journal}
+%   {J. Chem. Phys.}\ }\textbf {\bibinfo {volume} {100}},\ \bibinfo {pages}
+%   {8849} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Althorpe}\ \emph {et~al.}(1997)\citenamefont
+%   {Althorpe}, \citenamefont {Kouri}, \citenamefont {Hoffman},\ and\
+%   \citenamefont {Moiseyev}}]{althorpe97}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~C.}\ \bibnamefont
+%   {Althorpe}}, \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont {Kouri}},
+%   \bibinfo {author} {\bibfnamefont {D.~K.}\ \bibnamefont {Hoffman}},\ and\
+%   \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Moiseyev}},\ }\href
+%   {https://doi.org/10.1016/S0301-0104(97)00062-1} {\bibfield  {journal}
+%   {\bibinfo  {journal} {Chem. Phys.}\ }\textbf {\bibinfo {volume} {217}},\
+%   \bibinfo {pages} {289} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Winkler}(2003)}]{winkler03}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+%   {Winkler}},\ }\href@noop {} {\emph {\bibinfo {title} {Spin-orbit Coupling
+%   Effects in Two-Dimensional Electron and Hole Systems}}}\ (\bibinfo
+%   {publisher} {Springer, Berlin},\ \bibinfo {year} {2003})\BibitemShut
+%   {NoStop}%
+% \bibitem [{\citenamefont {Wackerl}(2020)}]{wackerlthesis20}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Wackerl}},\ }\emph {\bibinfo {title} {Transport in Periodically Driven
+%   Systems}},\ \href@noop {} {Ph.D. thesis},\ \bibinfo  {school} {University of
+%   Regensburg} (\bibinfo {year} {2020})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Tsuji}\ \emph {et~al.}(2008)\citenamefont {Tsuji},
+%   \citenamefont {Oka},\ and\ \citenamefont {Aoki}}]{tsuji08}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+%   {Tsuji}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Oka}},\ and\
+%   \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Aoki}},\ }\href
+%   {https://doi.org/10.1103/PhysRevB.78.235124} {\bibfield  {journal} {\bibinfo
+%   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {78}},\ \bibinfo
+%   {pages} {235124} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Griffiths}\ and\ \citenamefont
+%   {Schroeter}(2018)}]{griffiths18}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+%   {Griffiths}}\ and\ \bibinfo {author} {\bibfnamefont {D.~F.}\ \bibnamefont
+%   {Schroeter}},\ }\href@noop {} {\emph {\bibinfo {title} {Introduction to
+%   Quantum Mechanics}}}\ (\bibinfo  {publisher} {Cambridge University Press},\
+%   \bibinfo {year} {2018})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Shankar}(1994)}]{shankar94}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+%   {Shankar}},\ }\href@noop {} {\emph {\bibinfo {title} {Principles of Quantum
+%   Mechanics}}}\ (\bibinfo  {publisher} {Springer, New York},\ \bibinfo {year}
+%   {1994})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Celeghini}\ \emph {et~al.}(2021)\citenamefont
+%   {Celeghini}, \citenamefont {Gadella},\ and\ \citenamefont {del
+%   Olmo}}]{celeghini21}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+%   {Celeghini}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Gadella}},\
+%   and\ \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {del Olmo}},\
+%   }\href {https://doi.org/10.3390/sym13050853} {\bibfield  {journal} {\bibinfo
+%   {journal} {Symmetry}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo {pages}
+%   {853} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Akkermans}\ and\ \citenamefont
+%   {Montambaux}(2010)}]{akkermans10}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+%   {Akkermans}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+%   {Montambaux}},\ }\href@noop {} {\emph {\bibinfo {title} {Mesoscopic Physics
+%   of Electrons and Photons}}}\ (\bibinfo  {publisher} {Cambridge University
+%   Press},\ \bibinfo {year} {2010})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Arfken}(1985)}]{arfken85}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+%   {Arfken}},\ }\href@noop {} {\emph {\bibinfo {title} {Mathematical Methods for
+%   Physicists}}}\ (\bibinfo  {publisher} {Academic Press, Inc. , San Diego},\
+%   \bibinfo {year} {1985})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Bracewell}(1978)}]{bracewell78}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+%   {Bracewell}},\ }\href@noop {} {\emph {\bibinfo {title} {The Fourier Transform
+%   and Its Applications}}}\ (\bibinfo  {publisher} {McGraw-Hill, New York},\
+%   \bibinfo {year} {1978})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Cuyt}\ \emph {et~al.}(2008)\citenamefont {Cuyt},
+%   \citenamefont {Petersen}, \citenamefont {Verdonk}, \citenamefont
+%   {Waadeland},\ and\ \citenamefont {Jones}}]{cuyt08}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+%   {Cuyt}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Petersen}},
+%   \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Verdonk}}, \bibinfo
+%   {author} {\bibfnamefont {H.}~\bibnamefont {Waadeland}},\ and\ \bibinfo
+%   {author} {\bibfnamefont {W.}~\bibnamefont {Jones}},\ }\href@noop {} {\emph
+%   {\bibinfo {title} {Handbook of Continued Fractions for Special Functions}}}\
+%   (\bibinfo  {publisher} {Springer, Dordrecht},\ \bibinfo {year}
+%   {2008})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Abramowitz}\ and\ \citenamefont
+%   {Stegun}(1964)}]{abramowitz64}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+%   {Abramowitz}}\ and\ \bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont
+%   {Stegun}},\ }\href@noop {} {\emph {\bibinfo {title} {Handbook of Mathematical
+%   Functions with Formulas, Graphs, and Mathematical Tables}}}\ (\bibinfo
+%   {publisher} {Dover, New York},\ \bibinfo {year} {1964})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {V.Vedenyapin}\ \emph {et~al.}(2011)\citenamefont
+%   {V.Vedenyapin}, \citenamefont {Sinitsyn},\ and\ \citenamefont
+%   {Dulov}}]{vedenyapin11}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibnamefont {V.Vedenyapin}},
+%   \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Sinitsyn}},\ and\
+%   \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Dulov}},\ }\href@noop {}
+%   {\emph {\bibinfo {title} {Kinetic Boltzmann, Vlasov and Related Equations}}}\
+%   (\bibinfo  {publisher} {Elsevier, Amsterdam},\ \bibinfo {year}
+%   {2011})\BibitemShut {NoStop}%
+% \bibitem [{\citenamefont {Szegö}(1959)}]{szego59}%
+%   \BibitemOpen
+%   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+%   {Szegö}},\ }\href@noop {} {\emph {\bibinfo {title} {Orthogonal
+%   Polynomials}}}\ (\bibinfo  {publisher} {American Mathematical Society, New
+%   York},\ \bibinfo {year} {1959})\BibitemShut {NoStop}%
+% \end{thebibliography}%
+% %===============================================================================
 

### 2021-11-14 response/response.tex
restructure paper_res

@@
 
+We have made minor changes in language and presentation to improve clarity, and to match the rest of the manuscript better to the changes done to address the reviewer’s comments.
 \begin{itemize}
-    \item Introduction section details need to be changed.
-    \begin{itemize}
-        \item Section IV-A first paragraph - \\
-            {\color{Maroon} We prepare the thermal reservoirs $B_L$ and $B_R$ so that the temperature $T_L$ of $B_L$ is significantly higher than the temperature $T_R$ of $B_R$ \acrshort{tls}.}
-    \end{itemize}
-    \item Near Eq.37 $\sigma_0$ correction.
+    \item Section I - seventh paragraph (page 2): \\
+        {\color{Maroon} In Sec. VII, we discuss the physical significance of our theoretical results and their possible employments in future nanoelectronic devices.
+        Finally, we summarize our findings and present our conclusions in Sec. VIII.}
+    \item Section VIII - first paragraph (page 10): \\
+        {\color{Maroon} Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.}    
 \end{itemize}
@@
 Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, it is reasonable to extend our general derivation in given Eq.~[31] into a simple expression through a low-temperature limit.
-Furthermore, with the ability of adjusting Fermi level of the system through the applied gate voltage, we can achieve higher Fermi energies.
-This implies the condition $k_BT \ll \varepsilon_F$ and we can approximate that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
+Then we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
 This can be represented by the delta function \cite{endo09}
@@
   where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Under the above distribution in low-temperature conditions or $k_BT \ll \varepsilon_F$ condition, we can approximate that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
+Under the low-temperature conditions ($k_BT \ll \varepsilon_F$), we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
 This can be represented by the delta function \cite{endo09}

### 2021-11-14 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
restructure paper_res

@@
 {\color{Red}Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
-This inspired investigations on theoretical description of MIROs and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+This inspired investigations on theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
 These analytical formalisms provide a proper explanation for the experimental observations of MIROs.
@@
 The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism and it has escaped the researchers’ attention before.
-Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems for a high-frequency case.} However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
+Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system under high-frequency field.} However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
 {\color{Red}The authors of Ref.\cite{dini16} used the conductivity models from Refs.
@@
 \ref{sec:floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
-The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec:manipulate_conductivity}.
-In Sec. \ref{sec:conclusions}, we summarize our analysis and present our conclusions.
+The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec.
+\ref{sec:manipulate_conductivity}.
+{\color{Red}In Sec.
+\ref{sec:physical_significance}, we discuss the physical significance of our theoretical results and their possible employments in future nanoelectronic devices.
+Finally, we summarize our findings and present our conclusions in Sec. \ref{sec:conclusions}.}
 %===============================================================================
@@
 Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space.
-In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{T}$, which is pointed towards the $z$-axis.
+In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{\intercal}$, which is pointed towards the $z$-axis.
 In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface.
 We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field.
-Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field as given in Fig.~\ref{fig:1}.
+Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\intercal}$ for the linearly polarized dressing field as given in Fig.~\ref{fig:1}.
 \begin{figure}[b]
@@
 
-Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{T}$.
-Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E\cos(\omega t)]/\omega,0)^{T}$.
+Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{\intercal}$.
+Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E\cos(\omega t)]/\omega,0)^{\intercal}$.
 These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}.
@@
 \end{equation}
-where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{T}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{T}$.
+where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\intercal}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{\intercal}$.
 The exact solutions for the time-dependent Schrödinger equation $i\hbar \dv*{\psi}{t} = \hat{H}_e(t)\psi$ were already derived in Refs.
@@
 where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Under the above distribution in low-temperature conditions or $k_BT \ll \varepsilon_F$ condition, we can approximate that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
+Under the low-temperature conditions ($k_BT \ll \varepsilon_F$), we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
 This can be represented by the delta function \cite{endo09}
@@
 Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.
-
-On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.
-When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:6}.
-However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
-This demonstrates our ability to tune the width of the conductivity regions in these quantum Hall systems with the help of a dressing field.
-
-These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
-However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
-This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
-The semi-elliptical conductivity regions are  illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed data for Landau levels \cite{endo09}.
-In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the results depicted in Ref.
-\cite{endo09}.
-The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimentally observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
-However, they have not considered the tunability that can be achieved with a dressing field.
-In this analysis, we account for both the magnetic and dressing field effects that can affect the transport properties of 2DEG, leading to a more generalized theory.
-Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{fig_4_conductivity_with_fermi_level}
-\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:5}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{fig_5_conductivity_with_fermi_level_zoomed}
-\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:6}
-\end{figure}
 
@@
 This same behavior was also observed in the experimental observations presented in Ref.
-\cite{wakabayashi78} as well.
-However, in our analysis, we have analytically explained the controllability of these conductivity regions using a dressing field.
+\cite{wakabayashi78} as well.}
+
+{\color{Red}Considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.}
+When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:6}.
+However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
+This demonstrates our ability to tune the width of the conductivity regions in these quantum Hall systems with the help of a dressing field.
+
+\begin{figure}[t]
+\includegraphics[scale=0.54]{fig_4_conductivity_with_fermi_level}
+\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\label{fig:5}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[scale=0.54]{fig_5_conductivity_with_fermi_level_zoomed}
+\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\label{fig:6}
+\end{figure}
+
+These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
+However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
+The semi-elliptical conductivity regions are  illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed data for Landau levels \cite{endo09}.
+In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the results depicted in Ref.
+\cite{endo09}.
+The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimentally observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
+However, they have not considered the tunability that can be achieved with a dressing field.
+In this analysis, we account for both the magnetic and dressing field effects that can affect the transport properties of 2DEG, leading to a more generalized theory.
+Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.
+
+{\color{Red}
 Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
@@
 {\color{Red}
-We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within an order where we can neglect effects of the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions.} Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
+We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within an order where we can neglect effects of the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions.
+Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.}
 
@@
 and
-\begin{equation} \label{eq:d15}
+\begin{equation} \label{eq:d16}
   \begin{aligned}

### 2021-11-14 response/response.tex
Restructure res

@@
 Please note that in the following sections, the statements in {\color{RoyalBlue} \textbf{blue}} are the comments of the reviewers.
-Our responses are shown in black letters, and the modifications we have done to the manuscript are given in {\color{Maroon} red}.
+Our responses are shown in black letters, and the modifications we have done to the manuscript are given in {\color{Red} red}.
 
@@
     \item Section I - seventh paragraph (page 2): \\
-        {\color{Maroon} In Sec. VII, we discuss the physical significance of our theoretical results and their possible employments in future nanoelectronic devices.
+        {\color{Red} In Sec. VII, we discuss the physical significance of our theoretical results and their possible employments in future nanoelectronic devices.
         Finally, we summarize our findings and present our conclusions in Sec. VIII.}
+    \item Section VI - fourth paragraph (page 8): \\
+        {\color{Red} Considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.}
     \item Section VIII - first paragraph (page 10): \\
-        {\color{Maroon} Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.}    
+        {\color{Red} Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.}
 \end{itemize}
@@
 Therefore, we have made a discussion on the physical significance of our theoretical results and their possible employments in the optimization of nanoelectronic device performance.
-We have inserted a new section (Section VII) to incorporate the above discussion into the manuscript.
+First, we added a detailed comparison between our theoritical results and experiment observation for zero radiation case.
+Then, we inserted a new section (Section VII) to incorporate the above discussion into the manuscript.
 The total content of the section is given below,
@@
 \begin{itemize}
-  \item Section VII (page 8):\\
-  {\color{Maroon}
+  \item Section VI - third paragraph (page 8):\\
+  {\color{Red}
+  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.
+4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
+  As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
+  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
+  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
+  Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
+The  change of the gate voltage applied to the system will modify the Fermi level of the system.
+  Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
+  This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+By comparing these empirical observations with our results given in Fig.
+4, we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
+Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
+This will locate to the Fermi level on higher-order Landau levels.
+As illustrated in Fig.
+4, this will result in a higher conductivity peak value at the higher-order Landau levels.
+This same behavior was also observed in the experimental observations presented in Ref.
+\cite{wakabayashi78} as well.
+However, in our analysis, we have analytically explained the controllability of these conductivity regions using a dressing field.
+  }
+  \item Section VII (page 9):\\
+  {\color{Red}
   \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}
@@
 As illustrated in Fig.
-4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Ref.\cite{endo09,wakabayashi78} through our model.
+4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Refs.\cite{endo09,wakabayashi78} through our model.
 Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
@@
 This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
-  Furthermore, adopting the mechanism presented in Ref.\cite{hirakawa01}, we can utilize our manipulation of conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
+  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can utilize our manipulation of conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
   Based on these ready-to-use nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers the potential to realize advanced nanoelectronic devices.
@@
 To describe these behaviors Durst \textit{et al.} \cite{durst03} introduced a simple theoretical model assuming that the experimentally observed oscillations are a consequence of photoexcited disorder-scattered electrons.
-However, later a novel model was proposed in Ref. \cite{dmitriev03,dmitriev05,dmitriev09} considering the changes of the electron distribution function done by the microwave field.
+However, later a novel model was proposed in Refs. \cite{dmitriev03,dmitriev05,dmitriev09} considering the changes of the electron distribution function done by the microwave field.
 These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have successfully described the behavior of MIROs in experimentally relevant temperatures which were missed in the previous model \cite{durst03}.
@@
   The mentioned experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$).
-This leads to building the theoretical models presented in Ref.
+This leads to building the theoretical models presented in Refs.
 \cite{durst03,dmitriev03} by assuming that these oscillations are caused by photoexcited electrons.
@@
   \item
-  These fascinating MIROs are only observed under the weak magnetic fields ($B < \SI{0.2}{\tesla}$) in the experiments performed in Ref.
+  These fascinating MIROs are only observed under the weak magnetic fields ($B < \SI{0.2}{\tesla}$) in the experiments performed in Refs.
 \cite{zudov01,mani02,zudov03,mani04}.
@@
   \item Section I - fifth paragraph (page 1):\\
-  {\color{Maroon}
-  In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
-  Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
+  {\color{Red}
   Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
-  This inspired investigations on theoretical description of MIROs and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+  This inspired investigations on theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
 These analytical formalisms provide a proper explanation for the experimental observations of MIROs.
@@
   The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism and it has escaped the researchers’ attention before.
-  Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems for a high-frequency case.
-However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
-In their study, they used the conductivity models from Refs.
-\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
+  Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system under high-frequency field.
   }
-  \item Section VI - fifth paragraph (page 8):\\
-  {\color{Maroon}
-  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are a repetition of the Shubnikov–de Haas(SdH) oscillations.
-  As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
-  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
-  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
-  Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
-The  change of the gate voltage applied to the system will modify the Fermi level of the system.
-  Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
-  This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
-By comparing these empirical observations with our results given in Fig.
-[4], we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
-Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
-This will locate to the Fermi level on higher-order Landau levels.
-As illustrated in Fig.~[4], this will result in a higher conductivity peak value at the higher-order Landau levels.
-This same behavior was also observed in the experimental observations presented in Ref.
-\cite{wakabayashi78} as well.
-However, in our analysis, we have analytically explained the controllability of these conductivity regions using a dressing field.
+  \item Section VI - sixth paragraph (page 9):\\
+  {\color{Red}
   Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
@@
   \item Section VII (page 8):\\
-  {\color{Maroon}
+  {\color{Red}
   \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}
@@
 As illustrated in Fig.
-4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Ref.\cite{endo09,wakabayashi78} through our model.
+4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Refs.
+\cite{endo09,wakabayashi78} through our model.
 Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
@@
   \item Section IV - first paragraph (page 4):\\
-  {\color{Maroon}
-  The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
-  However, this theory has not been applied for a dressed quantum Hall system in the previous studies.
-In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
-  With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(14), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
-  \begin{equation} \label{eq:15}
-    \begin{aligned}
-      \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N =
-      \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N)
-      \int_{-\infty}^{\infty} &
-      J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
-      J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
-      \\
-      & \times
-      \left|
-      \int_{-\infty}^{\infty}
-      \chi_N \left( \frac{\hbar}{eB}k_2 \right)
-      \chi_N \bm{\left(} \frac{\hbar}{eB}
-      \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
-      dk_2 \right|^2 d k_1,
-    \end{aligned}
-  \end{equation}
-  where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
-  A more detailed derivation is given in Appendix C.
+  {\color{Red}
   We modeled the effect caused by impurities in the considered system as a single short-range perturbation potential.
@@
   \item Section V - second paragraph (page 7):\\
-  {\color{Maroon}
+  {\color{Red}
   Since we consider the dressed quantum Hall system under the off-resonant condition, the absorption of photons are avoided.
@@
 \begin{itemize}
-  \item Appendix D (page 14):\\
-  {\color{Maroon}
+  \item Appendix D (page 16):\\
+  {\color{Red}
   \subsection*{\label{appendix_d}Appendix D: Current operators for a dressed quantum Hall system}
@@
   }
-  \item Section V (page 7):\\
-  {\color{Maroon}
+  \item Section V - second paragraph (page 7):\\
+  {\color{Red}
   Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(31) leads to
-  \begin{equation} \label{eq:35}
+  \begin{equation} \tag{35}
     \begin{aligned}
@@
   Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
-  \begin{equation} \label{eq:36}
+  \begin{equation} \tag{36}
     \begin{aligned}
@@
 These will define the effect on the inverse scattering time matrix components.
-As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the considered system and creates novel states called Floquet states.
+As mentioned in Ref.
+\cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the considered system and creates novel states called Floquet states.
 The properties of these states depend on the characteristics of the applied dressing field.
@@
 \begin{itemize}
-  \item Section VI - fifth paragraph (page 8):\\
-  {\color{Maroon}
-  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are a repetition of the Shubnikov–de Haas(SdH) oscillations.
+  \item Section VI - third paragraph (page 8):\\
+  {\color{Red}
+  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.
+4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
   As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
@@
 By comparing these empirical observations with our results given in Fig.
-[4], we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
+4, we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
 Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
 This will locate to the Fermi level on higher-order Landau levels.
-As illustrated in Fig.~[4], this will result in a higher conductivity peak value at the higher-order Landau levels.
+As illustrated in Fig.
+4, this will result in a higher conductivity peak value at the higher-order Landau levels.
 This same behavior was also observed in the experimental observations presented in Ref.
@@
 However, in our analysis, we have analytically explained the controllability of these conductivity regions using a dressing field.
-  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
-However, these experiments and theoretical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
-  It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
-In our case, the applied dressing field is in the off-resonant range and that will only change the broadening of Landau levels and avoid any contribution towards the photon absorptions.
-This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
-Therefore our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
   }
@@
 We also followed the same theoretical derivation with given assumptions but with an additional dressing field.
-Our results for the undressed system give a adequate agreement with the results from Ref.\cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks.
+Our results for the undressed system give a adequate agreement with the results from Ref.
+\cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks.
 We have added this clarification in the manuscript.
@@
   \item Section I - sixth paragraph (page 2):\\
-  {\color{Maroon}
+  {\color{Red}
   It is important to note that, in this analysis, we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions can be neglected.
@@
   }
-  \item Section VIII - second paragraph (page 8):\\
-  {\color{Maroon}
+  \item Section VIII - first paragraph (page 10):\\
+  {\color{Red}
   We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within an order where we can neglect effects of the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions.
@@
 However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diagonal components of the conductivity tensor.
-As mentioned in Ref.~\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations
-\begin{equation} \nonumber
+As mentioned in Ref.
+\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations
+\begin{equation} \tag{1}
   \dv{\widetilde{\sigma}^{xy}(X_F,I)}{B} \approx
@@
 This will imply sudden Hall conductivity transitions between one plateau to another near a Landau level.
-As empirical observation shown in Ref.
+As empirical observation shown in Refs.
 \cite{klitzing80,gusynin06}, we can predict a staircase behavior for quantum Hall conductivity agaist the gate voltage.
@@
   \item Section VIII (page 8):\\
-  {\color{Maroon}
-  Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results do not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}.
-This is due to the fact that the authors of Ref.\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Ref.\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
+  {\color{Red}
+  Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results do not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.
+\cite{endo09}.
+This is due to the fact that the authors of Ref.
+\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Refs.
+\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
   However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
   }
-  \item Section III (page 3):\\
-  {\color{Maroon}
-  The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
+  \item Section III - first paragraph (page 3):\\
+  {\color{Red}
   In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.
@@
   }
-  \item Section I (page 2):\\
-  {\color{Maroon}
-  The authors of Ref.\cite{dini16} used the conductivity models from Refs.
+  \item Section I - fifth paragraph (page 2):\\
+  {\color{Red}
+  The authors of Ref.
+\cite{dini16} used the conductivity models from Refs.
 \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
   }
-  \item Section IV (page 5):\\
-  {\color{Maroon}
-  In the study presented in Ref.~\cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
+  \item Section IV - third paragraph (page 5):\\
+  {\color{Red}
+  In the study presented in Ref.
+\cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
   }

### 2021-11-15 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
Restructure res
Corrections

@@
 In contrast, near each Landau level, the conductivity achieves excessive values compared to other areas.
-Moreover, as illustrates in Fig.~\ref{fig:5}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.
+Moreover, as illustrates in Fig.~\ref{fig:4}, the peak value of the normalized longitudinal conductivity on each Landau level gets increased with the Landau level number.
 
 {\color{Red}
-By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~[4] are a repetition of the Shubnikov–de Haas(SdH) oscillations.
+By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
 As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
@@
 This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
-By comparing these empirical observations with our results given in Fig.
-[4], we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
+By comparing these empirical observations with our results given in Fig.~\ref{fig:4}, we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
 Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
 This will locate to the Fermi level on higher-order Landau levels.
-As illustrated in Fig.~[4], this will result in a higher conductivity peak value at the higher-order Landau levels.
+As illustrated in Fig.~\ref{fig:4}, this will result in a higher conductivity peak value at the higher-order Landau levels.
 This same behavior was also observed in the experimental observations presented in Ref.
@@
 {\color{Red}Considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.}
-When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:6}.
+When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:5}.
 However, the peak value of the conductivity at each Landau level has the same value as the undressed system.
@@
 These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
-However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:5} and Fig.~\ref{fig:6} are generally incompatible with the results reported in Ref.~\cite{dini16}.
+However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:4} and Fig.~\ref{fig:5} are generally incompatible with the results reported in Ref.~\cite{dini16}.
 This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}.
@@
 Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
-As illustrated in Fig.
-4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Ref.\cite{endo09,wakabayashi78} through our model.
+As illustrated in Fig.~\ref{fig:4}, we were also able to demonstrate the same SdH oscillations as experimental results observed in Ref.\cite{endo09,wakabayashi78} through our model.
 Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
-However, from our results given in Fig.
-5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+However, from our results given in Fig.~\ref{fig:5}, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
 In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.
@@
 In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures.
-Since the Fermi level of the system can be altered with the applied gate voltage, this behavior can be easily mapped into our results given in Fig.
-4.
+Since the Fermi level of the system can be altered with the applied gate voltage, this behavior can be easily mapped into our results given in Fig.~\ref{fig:4}.
 However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field.
@@
 Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59,boyd18}
-\begin{subequations} \label{eq:d8}
-  \begin{align}
+\begin{equation} \label{eq:d8}
+  \int \chi_{n}({y})
+  \chi_{n'}({y}) d{y} = \delta_{n',n},
+\end{equation}
+\begin{equation} \label{eq:d9}
     \int
-    \chi_{n}({y})
-    \chi_{n'}({y}) d{y} &=
-    \delta_{n',n}, \\
-    \int
-    y \chi_{n}({y})\chi_{n'}({y}) d{y} &=
+    y \chi_{n}({y})\chi_{n'}({y}) d{y} =
     \frac{1}{\kappa}
@@
     \delta_{n',n-1} \right),
-  \end{align}
-\end{subequations}
+\end{equation}
 we simplify the matrix elements of $x$-directional current operator to obtain
-\begin{equation} \label{eq:d9}
+\begin{equation} \label{eq:d10}
   \begin{aligned}
@@
 Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
-\begin{equation} \label{eq:d10}
+\begin{equation} \label{eq:d11}
   \begin{aligned}
@@
 For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
-\begin{equation} \label{eq:d11}
+\begin{equation} \label{eq:d12}
   \begin{aligned}
@@
 Moreover, we can identify the $y$-directional current operator component as
-\begin{equation} \label{eq:d12}
+\begin{equation} \label{eq:d13}
   \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
@@
 Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
-\begin{equation} \label{eq:d13}
+\begin{equation} \label{eq:d14}
   \left({j}_y \right)_{nm,n'm'} =
@@
 After following the same steps done for the $x$-directional current operator, and recursion relation of the first derivative of Gauss-Hermite functions \cite{boyd18}
-\begin{equation} \label{eq:d14}
+\begin{equation} \label{eq:d15}
   \begin{aligned}
@@
 we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
-\begin{equation} \label{eq:d15}
+\begin{equation} \label{eq:d16}
   \begin{aligned}
@@
 and
-\begin{equation} \label{eq:d16}
+\begin{equation} \label{eq:d17}
   \begin{aligned}

### 2021-11-18 response/response.tex
Corrections res
Edit to res

@@
 % Bibliography style
-\usepackage[numbers]{natbib}
+\usepackage[numbers,sort&compress]{natbib}
 \bibliographystyle{apsrev4-1}
@@
 
-We have made minor changes in language and presentation to improve clarity, and to match the rest of the manuscript better to the changes done to address the reviewer’s comments.
+We have made minor changes in language and presentation to improve clarity, and to match the rest of the manuscript better to the changes done to address the reviewers' comments.
 \begin{itemize}
@@
 
-We strongly agree with the reviewer that reasoning on our theoretical results and their application in current nanoelectronic devices would be essential to the reader.
-Therefore, we have made a discussion on the physical significance of our theoretical results and their possible employments in the optimization of nanoelectronic device performance.
-First, we added a detailed comparison between our theoritical results and experiment observation for zero radiation case.
-Then, we inserted a new section (Section VII) to incorporate the above discussion into the manuscript.
-The total content of the section is given below,
+We agree that our work has a theoretical bias, and the reader may benefit from some application perspective from our theoretical results to characterize or design nanoelectronic devices.
+Therefore, we have discussed the physical significance of our theoretical results and their possible use in optimizing nanoelectronic device performance.
+First, we added a detailed comparison between our theoretical results and experiment observation when no radiation is present.
+We also added a new section (Section VII) on this very aspect.
+,
 
@@
   {\color{Red}
-  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.
+  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.
 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
-  As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
-  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
-  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
+  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
+  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field amplitude for different types of 2DEGs.
+  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
   Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
-The  change of the gate voltage applied to the system will modify the Fermi level of the system.
-  Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
+  The applied gate voltage to the system modifies the Fermi level of the system.
+  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage chnages generates SdH oscillations.
   This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
-By comparing these empirical observations with our results given in Fig.
-4, we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
-Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
-This will locate to the Fermi level on higher-order Landau levels.
+  By comparing these observations with our results in Fig.
+4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
+  Furthermore, when we increase the gate voltage, the Fermi level rises.
 As illustrated in Fig.
@@
 This same behavior was also observed in the experimental observations presented in Ref.
-\cite{wakabayashi78} as well.
-However, in our analysis, we have analytically explained the controllability of these conductivity regions using a dressing field.
+\cite{wakabayashi78}.
+  In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
   }
@@
   However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low-temperatures is the disorders in materials \cite{ando85,dial07}.
-The broaden sequence of delta functions of density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
+The broaden sequence of delta functions of density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations.
 \cite{endo09,wakabayashi78}.
@@
   Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
-As illustrated in Fig.
-4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Refs.\cite{endo09,wakabayashi78} through our model.
-Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
-However, from our results given in Fig.
-5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
+  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}.
+Strikingly, we show in Fig.
+5 that we can manipulate the broadening of these conductivity peaks using an external dressing field.
 In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.
@@
 In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
-  The charge carrier concentration of a considering system is an imperative parameter that defines the conductivity properties of the system.
-We can manipulate that using the electrostatic field-effect mechanism and it is an ideal tool to control the conductivity in some specific systems.
-  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that the gate electric field can be used to manipulate the conductivity.
-A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the charge transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
-In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures.
-Since the Fermi level of the system can be altered with the applied gate voltage, this behavior can be easily mapped into our results given in Fig.
-4.
-However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field.
-Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general mathematical description to manipulate longitudinal conductivity broadening using only a high-intensity electromagnetic field.
+  The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
+  As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
+  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
+  We also observed that a considerable number of studies exists on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) in magnetic fields \cite{wakabayashi78,yang18,long20,li14}.
+Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures.
+Since the Fermi level of a system can be altered with the applied gate voltage, our Fig.
+4 depicts this result.
+  In particular, our analysisshoes that we can manipulate the broadening of the conductivity regions using an external dressing field.
+Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.
 
@@
 In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
-As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field.
+As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field.
 This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
-  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can utilize our manipulation of conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
-  Based on these ready-to-use nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers the potential to realize advanced nanoelectronic devices.
-Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
+  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
+  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
+  Furthermore, this theoretical model will aid for development of simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
   }

### 2021-11-18 response/response.tex
Edit to res

@@
 
-We thank the reviewer for pointing out that the necessity of comparison between our theoretical model and previous discussions on transport properties of quantum Hall systems.
-Among the mentioned studies we can identify that experimental researches \cite{zudov01,mani02,zudov03,mani04} are specifically aimed at the unusual oscillations of the magnetoresistance induced by the microwave (millimeter-wave) radiation in 2DEG quantum Hall systems.
+We agree with the reviewer that it is useful to have a discussion comparing  our theoretical model and previous work on transport properties of quantum Hall systems.
+Among the mentioned studies we can identify that experimental work reported in Refs.
+\cite{zudov01,mani02,zudov03,mani04} are specifically aimed at the unusual oscillations of the magnetoresistance induced by the microwave (millimeter-wave) radiation in 2DEG quantum Hall systems.
 These oscillations are known as \textit{microwave-induced resistance oscillations} (MIROs).
@@
 However, later a novel model was proposed in Refs. \cite{dmitriev03,dmitriev05,dmitriev09} considering the changes of the electron distribution function done by the microwave field.
-These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have successfully described the behavior of MIROs in experimentally relevant temperatures which were missed in the previous model \cite{durst03}.
-Furthermore, we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorption by an electron in the considering system.
-However, in our theoretical model, we take into account higher frequencies than microwaves as the dressing field.
-Therefore we can identify major dissimilarities between our system under the analysis and MIROs systems \cite{zudov01,mani02,zudov03,mani04,durst03,dmitriev03,dmitriev05,dmitriev09}.
-We listed these dissimilarities as follows for our comparison.
+These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have successfully described the behavior of MIROs at experimentally relevant temperatures that were missed in the previous model \cite{durst03}.
+Furthermore, we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorption by an electron in the associated system.
+In our theoretical model, we take into account higher frequencies than microwaves as the dressing field.
+Therefore we can identify and quantify significant dissimilarities between our system and MIROs systems \cite{zudov01,mani02,zudov03,mani04,durst03,dmitriev03,dmitriev05,dmitriev09}. They are:
 \begin{itemize}
   \item
-  The mentioned experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$).
+  in the experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$).
 This leads to building the theoretical models presented in Refs.

### 2021-11-18 response/response.tex
Edit res

@@
   \item
-  The applied microwave radiation power on the MIROs experiments \cite{mani02,zudov03} are varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
-However, in our analysis, we take the dressing field as a high-intensity field, where we can not address the dressing field as a perturbation to our considering system.
-This leads us to use recognize new Floquet states together with conventional Landau levels.
+  the applied microwave radiation power on the MIROs experiments \cite{mani02,zudov03} are varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
+However, in our analysis, we take the dressing field as a high-intensity electromagnetic field, where we can not consider the dressing field as a perturbation in our analysis.
+This leads us to recognize the formation of Floquet states together with conventional Landau levels.
 As we mentioned in our results, we used high-intensity dressing fields of magnitude around the $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.
   \item
-  These fascinating MIROs are only observed under the weak magnetic fields ($B < \SI{0.2}{\tesla}$) in the experiments performed in Refs.
+  these fascinating MIROs are only observed under the influence of weak magnetic fields ($B < \SI{0.2}{\tesla}$) in experiments performed in Refs.
 \cite{zudov01,mani02,zudov03,mani04}.
-In this range of weak magnetic fields,  we can only observe MIROs and Shubnikov–de Haas (SdH) oscillations reveal only on high-intensity magnetic fields.
+In this range of weak magnetic fields,  we can only observe MIROs as Shubnikov–de Haas (SdH) oscillations reveal only on high-intensity magnetic fields.
 In comparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics.
@@
   \item
-  In our work, we analyzed the 2DEG quantum Hall system with a high-intensity dressing field which does not contribute to a energy exchange between the high-frequency dressing field and electrons.
-Therefore we have assumed the applied electromagnetic radiation as a purely dressing field.
-There are two possible absorption mechanisms in a 2DEG quantum Hall system namely electron transitions between distinct Landau levels and electron transitions between distinct states of the same broadened Landau level.
-To avoid these absorptions we have tuned the dressing field into a high-frequency range in our system under the analysis.
+  in our work, we analyzed the 2DEG quantum Hall system with a dressing high-intensity electromagnetic field which does not contribute to a energy exchange between the high-frequency dressing field and electrons.
+Therefore we have assumed the applied electromagnetic radiation as a pure dressing field.
+There are two possible absorption mechanisms in a 2DEG quantum Hall system; namely electron transitions between distinct Landau levels, and electron transitions between distinct states of the same broadened Landau level.
+To avoid these absorptions, we have tuned the dressing field into a high-frequency range in our system under the analysis.
 Furthermore, due to the high-intensity dressing field, the entire electronic states of the conventional 2DEG quantum Hall system will be restructured.
@@
 
-Examining the above-mentioned points, we can identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two particular natures of magnetotransport properties.
-However, we identify that it is crucial to acknowledge these well-defined findings in MIROs and their relationship to our considered system. We have added this clarification in the manuscript.
+Based on the above discussion, we can identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two distinguishable magnetotransport scenarios.
 
@@
   This inspired investigations on theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
-These analytical formalisms provide a proper explanation for the experimental observations of MIROs.
+These formalisms provide a proper explanation for the experimental observations of MIROs.
 However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) fields.
-  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a purely dressing (nonabsorbable) field.
-  The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism and it has escaped the researchers’ attention before.
-  Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system under high-frequency field.
+  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
+  The influence of induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism, and it has escaped the researchers’ attention before.
+  Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
   }
@@
   It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
-In our case, the applied dressing field is in the off-resonant range and that will only change the broadening of Landau levels and avoid any contribution towards the photon absorptions.
+In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions.
 This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
@@
 
-We thank the reviewer for pointing out the importance of these facts that will help to elevate the value of our work.
-As we mentioned in comment 1, considering the importance of discussing the physical significance of our results, we added a new section (Section VII) to address these facts.
+This is a valid comment.
+As we mentioned in comment 1, considering the importance of discussing the physical significance of our results, we included a new section (Section VII) to address this comment.
 
@@
   Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
-As illustrated in Fig.
-4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Refs.
-\cite{endo09,wakabayashi78} through our model.
-Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
-However, from our results given in Fig.
-5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
+  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}.
+Strikingly, we show in Fig.
+5 that we can manipulate the broadening of these conductivity peaks using an external dressing field.
 In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.
@@
 In our previous manuscript, we have presented the detailed derivation of Eq.~[15] with a discussion on models of disorder under Appendix C.
-However we will discuss our selection of disorder model and approximations made to derive the Eq.~[15] here as well.
+However, here we again elucidate our disorder model and approximations made to derive the Eq.~[15] for clarity and to respond to this question.
 
-We modeled the effect caused by impurities in the considered system as a single perturbation potential.
+We modelled the effect caused by impurities in the considered system as a single perturbation potential.
 Analyzing the electric properties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
 Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
-In addition, we consider only our considering static disorder corresponds to the situation in which the electrons scatter elastically.
-First, we adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the considering system and we approximate this into a Gaussian white noise.
+In addition, we consider a static disorder corresponds only to elastic electron scattering processes.
+First, we adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the associated system and we approximate this into a Gaussian white noise.
 
-Since we are presenting the perturbation potential $V(\vb{r})$ by a group of randomly localized impurities, we take into account $N_{imp}$ number of identical single impurity potentials distributed randomly but in fixed positions $\vb{r}_i$.
-Thus, we can describe the scattering potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$
+Since we are presenting the perturbation potential $V(\vb{r})$ by a group of randomly localized impurities, we assume $N_{imp}$ number of identical single impurity potentials distributed randomly but in fixed positions $\vb{r}_i$.
+Thus, we can describe the perturbation potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$,
 \begin{equation} \label{eq:1}
@@
 \end{equation}
-Furthermore, we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
+Furthermore, we approximate this perturbation potential as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
 This model is characterized by the following two equations \cite{akkermans10}
@@
 \end{subequations}
-where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function depends only on $\vb{r}-\vb{r'}$.
-In addition, this model assumes that $\upsilon (\vb{r}-\vb{r'})$ only depends on the magnitude of the position difference $|\vb{r}-\vb{r'}|$, and it decays with a characteristic length $r_c$.
-Since this study considers the case where the wavelength of radiation or scattering electron is much greater than $r_c$, it is a better approximation to make a two-point correlation function be
+where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function which solely depends only on $\vb{r}-\vb{r'}$, and decays with a characteristic length $r_c$.
+Since this study considers the case where the wavelength of radiation or a scattering electron is much greater than $r_c$, it is a reasonable to approximation its two-point correlation function by
 \begin{equation} \label{eq:4}
@@
 \end{equation}
-where $\Upsilon_{imp}^2$ is a constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately model the total scattering potential as
+where $\Upsilon_{imp}^2$ is a positive constant.
+A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}.
+Then we can approximately write the total scattering potential as
 \begin{equation} \label{eq:5}
@@
 
-Then we calculate the Floquet-Fermi golden rule for a dressed quantum Hall system using this perturbative impurity potential.
-In the derivation, we have defined the $V_{imp}$ value which is constant in momentum space.
-It is a property of Gaussian white noise impurity distribution \cite{akkermans10,wackerl20}.
+Using this expression, we can evaluate the Floquet-Fermi golden rule for a dressed quantum Hall system.
+Furthermore, considering the properties of a Gaussian white noise impurity distribution \cite{wackerl20,akkermans10}, we assume $V_{imp}$ is a constant in the momentum space.
 However, throughout the derivation, we use only the first-order contribution (Born approximation) of the impurity potential.
@@
 
-Since previous studies on Floquet-Drude conductivity \cite{wackerl20}, and magnetotransport properties in undressed \cite{endo09} and dressed \cite{dini16} quantum Hall systems have used this particular Gaussian white noise potential, we also selected this pertucular impurity model to describe our system.
-This opens a path to compare our analytical outcomes with these previous models.
-As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the magnetotransport properties of dressed quantum Hall system would be an interesting future research possibility.
+Since previous studies on Floquet-Drude conductivity \cite{wackerl20}, and magneto-transport properties in undressed \cite{endo09} and dressed \cite{dini16} quantum Hall systems have used this particular Gaussian white noise potential, we also selected this pertucular impurity model to describe our system.
+Such a choise enables us to compare our analytical results with these previous models.
+As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the magnetotransport properties of dressed quantum Hall system would be an intriguing future research possibility.
 
-Since we have only mentioned the validity conditions we used to derive the Eq.~[15] in Appendix C and not in the main text of the previous manuscript, we have added these validity conditions to the main text of the new manuscript.
+Since we have only mentioned the validity conditions we used to derive the Eq.~[15] in Appendix C and not in the main text of the previous manuscript, we have added these validity conditions to the main text of the revised manuscript.
 
@@
   {\color{Red}
-  We modeled the effect caused by impurities in the considered system as a single short-range perturbation potential.
-Analyzing the electric properties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
+  We have modeled the effect caused by impurities as a single short-range perturbation potential.
+Analyzing the electric properties for a specific impurity distribution is a rather formidable task.
+We do not consider a simple impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
   Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
-  Furthermore, we assumed that our perturbation potential is formed by a group of randomly distributed impurities under the Edwards impurity model \cite{akkermans10,wackerl20}.
-  Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-Then we  approximate the impurity potential into a Gaussian white noise \cite{akkermans10,wackerl20}.
-  Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
+  Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
+  Essentially, all these assumptions means that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20},
+  where $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
   Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.

### 2021-11-18 response/response.tex
Edit to res

@@
 First, we discuss the validity of the Eq.~[33] and Eq.~[34].
-In our analysis, we have derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
-In contrast to the MIROs analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, where the absorption of photons are avoided.
-Therefore, we can select the Fermi-Dirac distribution as our particle distribution function on the general expression given in Eq.~[31]
+Our analysis derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
+In contrast to the MIROs analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, but photon absorption does not happen.
+Therefore, we can select the Fermi-Dirac distribution as our particle distribution function for Eq.~[31]
 \begin{equation} \tag{5}
@@
 \end{equation}
-Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Then we selected a special scenario where we assumed that the system is under a low-temperature limit or the condition $k_BT \ll \varepsilon_F$.
-Since previous theoretical studies \cite{wackerl20,dini16,endo09} on magnetotransport properties of 2DEG quantum Hall systems were derived under this assumption, we selected this condition to provide a better comparison with their outcomes.
+Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
+Then we consider a special scenario where the system operates at a low-temperature limit, i.e., the condition $k_BT \ll \varepsilon_F$.
+Since previous theoretical studies \cite{wackerl20,dini16,endo09} on magneto-transport properties of 2DEG quantum Hall systems were derived under this assumption, we also adopted the same conditions as it enables us to compare results with those studies.
 In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing temperature, we can identify the decaying behavior of SdH oscillations.
-Therefore, if we need to maintain a good oscillatory behavior we need to work in low temperatures.
-Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, it is reasonable to extend our general derivation in given Eq.~[31] into a simple expression through a low-temperature limit.
-Then we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
-This can be represented by the delta function \cite{endo09}
+Therefore, if we need to maintain a good oscillatory behavior, we need to operate in low temperatures.
+Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, it is reasonable to simplify our general derivation in given Eq.~[31] for low-temperature limit.
+Under these assumptions, the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy, and  can be represented by the delta function \cite{endo09}
 \begin{equation} \tag{6}
@@
   {\color{Red}
-  Since we consider the dressed quantum Hall system under the off-resonant condition, the absorption of photons are avoided.
-Therefore, we select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
+  We consider a dressed quantum Hall system under off-resonant condition, where photon absorption does not happen.
+Therefore, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
   \begin{equation} \tag{33}
@@
   \end{equation}
-  where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Under the low-temperature conditions ($k_BT \ll \varepsilon_F$), we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
-This can be represented by the delta function \cite{endo09}
+  where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
+At low-temperatures, i.e.
+$k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
   \begin{equation} \tag{34}
@@
 
-Yes, it is true that when we consider the experimental observations of a quantum Hall system a strong dressing field can increase the temperature of the sample.
-However, as mentioned in a previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low-temperature by applying narrow pulses of a strong dressing field to observe the discussed phenomena.
+Yes, indeed, experiments on quantum hall systems subject to a strong dressing field show elevated temperatures.
+However, as demonstrated in previous studies by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, it is possible to maintain low system temperature by limiting the dressing field to narrow pulses.
 
 Although we have extended our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoretical model into different types of particle distribution functions.
-As presented in the previous work done by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion needs to address the changes in distribution functions in our derived general longitudinal conductivity formula and this would be an noteworthy extension to our study.
+As presented in the previous work done by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion needs to address the changes in distribution functions in our derived general longitudinal conductivity formula, and this would be a noteworthy extension to our study.
 

### 2021-11-18 response/response.tex
Edit to res

@@
 
-We express our gratitude towards the reviewer for pointing out this inadvertent oversight done in the $yy$-component of the current operator calculation and this has led to an unexpected normalization factor in the yy-component of conductivity expression.
-Since we have only analyzed the normalized $xx$-component of the conductivity tensor, the remaining analysis is not affected by this change.
-After this change, we can predict that both xx-component and $yy$-component show the same conductivity behaviors.
+We express our gratitude towards the reviewer for pointing out this inadvertent oversight done in the $yy$-component of the current operator calculation.
+This has led to an unexpected normalization factor in the yy-component of the  conductivity expression.
+Since we have only used the normalized $xx$-component of the conductivity tensor for subsequent analysis, this oversight has no impact on the analysis reported in the  manuscsript.
+With this correction, we observe that both xx-component and $yy$-component show the same conductivity behaviors.
 We added these amendments to the current operator calculations done in Appendix D and the longitudinal conductivity calculation under Section V.
@@
   \end{equation}
-  Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
+  Let $[y - y_0 - \zeta(t)] = \bar{y}$, and we can obtain
   \begin{equation} \tag{D7}
@@
   \end{equation}
-  Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
+  Using the following integral identities of the Floquet modes that are made up of Gauss-Hermite functions \cite{vedenyapin11,szego59}
   \begin{equation} \tag{D8}
@@
   \end{equation}
-  Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
+  Due to high complexity of extract solution, in this study we only consider the constant contribution from the Fourier series components of the above expression.
+Therefore, we can identify the $0$-th component of the Fourier series as
   \begin{equation} \tag{D11}
@@
   \end{equation}
-  For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
+  To calculate the electric current operator, we substitute the electron's charge and effective mass to the above derived equation. This leads to
   \begin{equation} \tag{D12}
@@
 
-If we applied an arbitrary directional polarized dressing field, we can derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis.
+Suppose we applied an arbitrary directional polarized dressing field.
+In thay case, we could derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis.
 This would change the amplitude of the considering dressing field ($E$) in each direction.
-Now there will be a new component in parallel to the considering conductivity component and this will modify the time-dependent Hamiltonian given in Eq.~[2].
+There will be a new component in parallel to the considering conductivity component, which will modify the time-dependent Hamiltonian given in Eq.~[2].
 Then, we need to solve the Schrödinger equation with the modified Hamiltonian to find the new Floquet modes for the new system.
@@
 
-For analyzing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
-The Floquet-Drude conductivity formula was only developed for the diagonal components of the conductivity tensor of the considering system.
-In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analyzed the dressing field effect on two diagonal components of the conductivity tensor.
-Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these types of behaviors of dressed 2DEG quantum Hall systems.
+For analyzing our system, we mainly employ the diagonal components of the Floquet-Drude conductivity tensor introduced by Wackerl \textit{et al.} \cite{wackerl20}.
+As we mainly focus on SdH oscillations in longitudinal conductivity components, we limit our analysis to the dressing field on two diagonal components of the conductivity tensor.
+Therefore we are unable to predict the off-diagonal component behavior of the system.
 %

### 2021-11-18 response/response.tex
Edit to res

@@
     \item Section VIII - first paragraph (page 10): \\
-        {\color{Red} Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.}
+        {\color{Red} Finally, we derived analytical expressions for the diagonal components of the electric conductivity tensor concerning the 2DEG quantum Hall system operates at low temperatures.}
 \end{itemize}
@@
   This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
-  By comparing these observations with our results in Fig.
+  By comparing these observations against our results in Fig.
 4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
@@
 5 that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.
+In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
 
@@
   We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
-  Furthermore, this theoretical model will aid for development of simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
+  Furthermore, this theoretical model will aid for development of simulation tools that will design the quantum effects in
+magneto-transport properties of 2D nanostructures.
   }
@@
   the applied microwave radiation power on the MIROs experiments \cite{mani02,zudov03} are varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
-However, in our analysis, we take the dressing field as a high-intensity electromagnetic field, where we can not consider the dressing field as a perturbation in our analysis.
+However, in our analysis, we take the dressing field as a high-intensity electromagnetic field, where we cannot consider the dressing field as a perturbation in our analysis.
 This leads us to recognize the formation of Floquet states together with conventional Landau levels.
-As we mentioned in our results, we used high-intensity dressing fields of magnitude around the $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.
+As we mentioned in our results, we used dressing high-intensity electromagnetic fields of magnitude around the $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.
   \item
@@
 To avoid these absorptions, we have tuned the dressing field into a high-frequency range in our system under the analysis.
-Furthermore, due to the high-intensity dressing field, the entire electronic states of the conventional 2DEG quantum Hall system will be restructured.
+Furthermore, due to the dressing high-intensity electromagnetic field, the entire electronic states of the conventional 2DEG quantum Hall system will be restructured.
 We have addressed these modifications through the Floquet theory.
@@
 
-Based on the above discussion, we can identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two distinguishable magnetotransport scenarios.
+Based on the above discussion, we can identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two distinguishable
+magneto-transport scenarios.
 
@@
   In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
-  The influence of induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism, and it has escaped the researchers’ attention before.
+  The influence of induced by a pure dressing field on
+magneto-transport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism, and it has escaped the researchers’ attention before.
   Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
@@
   {\color{Red}
-  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
-However, these experiments and theoretical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
+  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
+magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems.
+However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
   It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
@@
 We modelled the effect caused by impurities in the considered system as a single perturbation potential.
-Analyzing the electric properties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
+Analyzing the electric properties for a specific impurity distribution is a rather formidable task.
+We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
 Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
-In addition, we consider a static disorder corresponds only to elastic electron scattering processes.
-First, we adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the associated system and we approximate this into a Gaussian white noise.
+We start our analysis by consider a static disorder that corresponds only to elastic electron scattering processes.
+We adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the associated system and we approximate this into a Gaussian white noise.
 
@@
 Such a choise enables us to compare our analytical results with these previous models.
-As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the magnetotransport properties of dressed quantum Hall system would be an intriguing future research possibility.
+As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the
+magneto-transport properties of dressed quantum Hall system would be an intriguing future research possibility.
 
@@
   {\color{Red}
-  We have modeled the effect caused by impurities as a single short-range perturbation potential.
+  We have modellfed the effect caused by impurities as a single short-range perturbation potential.
 Analyzing the electric properties for a specific impurity distribution is a rather formidable task.
-We do not consider a simple impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
+We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
   Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
@@
 Therefore, if we need to maintain a good oscillatory behavior, we need to operate in low temperatures.
-Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, it is reasonable to simplify our general derivation in given Eq.~[31] for low-temperature limit.
+Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, it is reasonable to simplify our general derivation given in  Eq.~[31] for low-temperature limit.
 Under these assumptions, the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy, and  can be represented by the delta function \cite{endo09}
@@
 \end{equation}
-Applying these adequate conditions, we can simplify our derivation into single expression that can be compared with previous studies \cite{wackerl20,dini16,endo09} on magnetotransport in dressed quantum Hall systems.
-We have added clarification on the above assumptions in the manuscript.
+Applying these adequate conditions, we can simplify our derivation into single expression that can be compared with previous studies \cite{wackerl20,dini16,endo09} on
+magneto-transport in dressed quantum Hall systems. We have added clarification on the above assumptions in the manuscript.
 \begin{itemize}
@@
   where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
-At low-temperatures, i.e.
-$k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
+At low-temperatures, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
   \begin{equation} \tag{34}
@@
 Although we have extended our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoretical model into different types of particle distribution functions.
-As presented in the previous work done by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion needs to address the changes in distribution functions in our derived general longitudinal conductivity formula, and this would be a noteworthy extension to our study.
+As presented in the previous work of Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion needs to address the changes in distribution functions in our derived general longitudinal conductivity formula, and this would be a noteworthy extension to our study.
 
@@
   \end{equation}
-  where $\widetilde{m}$ is the mass of the considering particle.
+  where $\widetilde{m}$ is the mass of the associated particle.
 
@@
 In thay case, we could derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis.
-This would change the amplitude of the considering dressing field ($E$) in each direction.
+This would change the amplitude of the associated dressing field ($E$) in each direction.
 There will be a new component in parallel to the considering conductivity component, which will modify the time-dependent Hamiltonian given in Eq.~[2].
@@
 For analyzing our system, we mainly employ the diagonal components of the Floquet-Drude conductivity tensor introduced by Wackerl \textit{et al.} \cite{wackerl20}.
-As we mainly focus on SdH oscillations in longitudinal conductivity components, we limit our analysis to the dressing field on two diagonal components of the conductivity tensor.
+As we mainly focus on SdH oscillations in longitudinal conductivity components, we limit our analysis to the dressing field influence on two diagonal components of the conductivity tensor.
 Therefore we are unable to predict the off-diagonal component behavior of the system.
@@
 
-\newpage
 \subsection*{Response to the comments of Reviewer 2}
 
-We would like to thank the reviewer for his/her insightful comments on our work.
+We want to thank the reviewer for his/her insightful comments on our work.
 To address your comments, we had to add new materials and reorganize our text.
-As a result, we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis.
-We hence believe that both the presentation and scientific content of this manuscript are of a much higher quality than our previous submission.
-We hope our response and the corresponding changes we incorporated into the manuscript would be sufficient to clarify the issues raised.
+As a result, we have able to considerably improved our discussion on the underlying assumptions and corresponding physical significance of our analysis.
+We hope our response and the corresponding changes we incorporated into the manuscript will be sufficient to clarify the issues raised.
 
@@
 We thank the reviewer for pointing out the importance of this fact.
-To overcome this shortage of discussion we made a detailed analysis of our results against the undressed 2DEG quantum Hall system behavior.
-We have inserted this discussion into our manuscript under Section VI.
+In the revised manuscript, we have included detailed analysis of our results against the undressed 2DEG quantum Hall system behavior.
 
@@
   {\color{Red}
-  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.
+  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.
 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
-  As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
-  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
-  The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
+  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
+  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field amplitude for different types of 2DEGs.
+  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
   Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
-The  change of the gate voltage applied to the system will modify the Fermi level of the system.
-  Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
+  The applied gate voltage to the system modifies the Fermi level of the system.
+  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage chnages generates SdH oscillations.
   This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
-By comparing these empirical observations with our results given in Fig.
-4, we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
-Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
-This will locate to the Fermi level on higher-order Landau levels.
+  By comparing these observations against our results in Fig.
+4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
+  Furthermore, when we increase the gate voltage, the Fermi level rises.
 As illustrated in Fig.
@@
 
-We agree with the reviewer that the discussion on the Anderson localization and topologically protected edge modes were missing from the previous manuscript.
-We would like to mention to the reviewer that while deriving Eq.~[31], we have assumed that the applied static magnetic field is placed in a lower intensity range where we can neglect several effects known to appear in a 2DEG quantum Hall system.
+We ommitted a discussion on the Anderson localization and topologically protected edge modes as we neglected them in our work.
+While deriving Eq.~[31], we have assumed that the applied static magnetic field is placed in a lower intensity range where we can neglect several effects known to appear in a 2DEG quantum Hall system.
 Under this condition, we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions, and the spin splitting as well.
-As mentioned in the work done by Endo \textit{et al.} \cite{endo09}, under the given magnetic field range, the undressed magnetotransport properties of GaAs/AlGaAs 2DEG quantum Hall system provide an excellent agreement between the experimental observations and theory that was developed by neglecting the above-mentioned effects.
-We also followed the same theoretical derivation with given assumptions but with an additional dressing field.
-Our results for the undressed system give a adequate agreement with the results from Ref.
+As mentioned in the work of Endo \textit{et al.} \cite{endo09}, within the magnetic field range of interest, the undressed
+magneto-transport properties of GaAs/AlGaAs 2DEG quantum Hall system provide an excellent agreement between the experimental observations and theory that was developed by neglecting the above-mentioned effects.
+Our work is very similar to theirs with an additional dressing field.
+Our results for the undressed system agrees with the results in Ref.
 \cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks.
@@
   {\color{Red}
-  It is important to note that, in this analysis, we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions can be neglected.
-The use of this assumption can also be found in the study done by Endo \textit{et al.} \cite{endo09}.
+  It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions.
+This is not an overly restrictive assumption and others have used similar assumption in their work e.g.
+see \textit{et al.} \cite{endo09}.
   }
@@
   {\color{Red}
-  We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within an order where we can neglect effects of the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions.
+  We modelled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.
   }
@@
 
-For analyzing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}.
-The Floquet-Drude conductivity formula was only developed for the diagonal components of the conductivity tensor of the considering system.
-In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analyzed the dressing field effect on two diagonal components of the conductivity tensor through the Floquet-Drude conductivity formula.
-Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these types of behaviors of dressed 2DEG quantum Hall systems.
+For analyzing our system, we mainly employ the diagonal components of the Floquet-Drude conductivity tensor introduced by Wackerl \textit{et al.} \cite{wackerl20}.
+As we mainly focus on SdH oscillations in longitudinal conductivity components, we limit our analysis to the dressing field influence on two diagonal components of the conductivity tensor.
+Therefore we cannot predict the off-diagonal component behavior of the system.
 However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diagonal components of the conductivity tensor.
 As mentioned in Ref.
-\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations
+\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly agree with  experiment observations
 \begin{equation} \tag{1}
@@
 By examining the connection between longitudinal and transverse conductivities in the 2DEG quantum Hall system, we can expect the same Hall conductivity behavior in a dressed quantum Hall system.
-However, using the dressing field we can squeeze the conductivity peaks on Landau levels.
-This will squeeze the region of longitudinal conductivity peaks placed near the Landau levels.
-This will imply sudden Hall conductivity transitions between one plateau to another near a Landau level.
-As empirical observation shown in Refs.
-\cite{klitzing80,gusynin06}, we can predict a staircase behavior for quantum Hall conductivity agaist the gate voltage.
-With a external dressing field we will be able to get rapid transitions than the undressed system.
-However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulated from the begin and it will be the subject of our future study.
+However, using the dressing field, we can squeeze the conductivity peaks on Landau levels, i.e., squeeze the region of longitudinal conductivity peaks placed near the Landau levels.
+This  imply sudden Hall conductivity transitions between one plateau to another near a Landau level.
+As in Refs.
+\cite{klitzing80,gusynin06}, we can also predict a staircase behavior of quantum Hall conductivity against the gate voltage.
+With an external dressing field, we will be able to get rapid transitions than the undressed system.
+However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulated from the beginning.
+It will be the subject of our future study.
 
@@
 
-We would like to thank the reviewer for pointing out the deficiencies in our manuscript and we have considered your recommendations seriously.
 We made the following changes in language and presentation to improve the clarity of our manuscript.
@@
   {\color{Red}
-  Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results do not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.
+  Despite this behavior being identified in previous work of Dini \textit{et al.}  \cite{dini16}, they cannot fully account for the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.
 \cite{endo09}.
-This is due to the fact that the authors of Ref.
-\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Refs.
-\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
+The authors of Ref.
+\cite{dini16} have used the conventinal expression of longitudinal conductivity from Refs.
+\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening for Landau level.
+These predictions significantly deviates from the experimentally observed Landau level broadening \cite{endo09}.
   However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
@@
   Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
-As illustrated in Fig.
-4, we were also able to demonstrate the same SdH oscillations as experimental results observed in Refs.
-\cite{endo09,wakabayashi78} through our model.
-Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
-However, from our results given in Fig.
-5, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.
+  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
+  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}.
+Strikingly, we show in Fig.
+5 that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
 
@@
 In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
-As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field.
+As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field.
 This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
-  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can utilize our manipulation of conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
-  Based on these ready-to-use nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers the potential to realize advanced nanoelectronic devices.
-Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
+  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
+  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
+  Furthermore, this theoretical model will aid for development of simulation tools that will design the quantum effects in
+  magneto-transport properties of 2D nanostructures.
   }

### 2021-11-18 response/response.tex
Edit to res
Corrections to res

@@
 Therefore, we have discussed the physical significance of our theoretical results and their possible use in optimizing nanoelectronic device performance.
-First, we added a detailed comparison between our theoretical results and experiment observation when no radiation is present.
+First, we added a detailed comparison between our theoretical results and experiment observations when no radiation is present.
 We also added a new section (Section VII) on this very aspect.
-,
 
@@
 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
-  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
-  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field amplitude for different types of 2DEGs.
+  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of the SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
+  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude for different types of 2DEGs.
   The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
-  Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
+  Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in a 2DEG quantum Hall system by changing the gate voltage.
   The applied gate voltage to the system modifies the Fermi level of the system.
-  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage chnages generates SdH oscillations.
+  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation generates SdH oscillations.
   This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
@@
 The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
-The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
+The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
 This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically.
 The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
-  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low-temperatures is the disorders in materials \cite{ando85,dial07}.
-The broaden sequence of delta functions of density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations.
-\cite{endo09,wakabayashi78}.
+  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}.
+The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.
 
-  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
+  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with gaussian impurity broadening assumptions.
   As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
@@
 5 that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
+At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering.
+Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
 
@@
   A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
-  We also observed that a considerable number of studies exists on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) in magnetic fields \cite{wakabayashi78,yang18,long20,li14}.
-Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures.
+  We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}.
+Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures.
 Since the Fermi level of a system can be altered with the applied gate voltage, our Fig.
 4 depicts this result.
-  In particular, our analysisshoes that we can manipulate the broadening of the conductivity regions using an external dressing field.
+  In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field.
 Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.
@@
   We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
-  Furthermore, this theoretical model will aid for development of simulation tools that will design the quantum effects in
+  Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
   magneto-transport properties of 2D nanostructures.
@@
 
-We agree with the reviewer that it is useful to have a discussion comparing  our theoretical model and previous work on transport properties of quantum Hall systems.
+We agree with the reviewer that it is useful to have a discussion comparing  our theoretical model and previous work on the transport properties of quantum Hall systems.
 Among the mentioned studies we can identify that experimental work reported in Refs.
@@
   \item
-  the applied microwave radiation power on the MIROs experiments \cite{mani02,zudov03} are varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
+  the applied microwave radiation power on the MIROs experiments \cite{mani02,zudov03} varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
 However, in our analysis, we take the dressing field as a high-intensity electromagnetic field, where we cannot consider the dressing field as a perturbation in our analysis.
@@
   \item
-  in our work, we analyzed the 2DEG quantum Hall system with a dressing high-intensity electromagnetic field which does not contribute to a energy exchange between the high-frequency dressing field and electrons.
+  in our work, we analyzed the 2DEG quantum Hall system with a dressing high-intensity electromagnetic field which does not contribute to energy exchange between the high-frequency dressing field and electrons.
 Therefore we have assumed the applied electromagnetic radiation as a pure dressing field.
-There are two possible absorption mechanisms in a 2DEG quantum Hall system; namely electron transitions between distinct Landau levels, and electron transitions between distinct states of the same broadened Landau level.
+There are two possible absorption mechanisms in a 2DEG quantum Hall system; namely electron transitions between distinct Landau levels and electron transitions between distinct states of the same broadened Landau level.
 To avoid these absorptions, we have tuned the dressing field into a high-frequency range in our system under the analysis.
@@
 We have addressed these modifications through the Floquet theory.
-However, the MIROs models \cite{durst03,dmitriev03} are based on low-frequency cases where the system is able to absorb low-frequency photons from the field.
+However, the MIROs models \cite{durst03,dmitriev03} are based on low-frequency cases where the system can absorb low-frequency photons from the field.
 \end{itemize}
@@
   Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
-  This inspired investigations on theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+  This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
 These formalisms provide a proper explanation for the experimental observations of MIROs.
@@
   The influence of induced by a pure dressing field on
-magneto-transport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism, and it has escaped the researchers’ attention before.
+  magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
   Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
@@
 
-We modelled the effect caused by impurities in the considered system as a single perturbation potential.
+We modeled the effect caused by impurities in the considered system as a single perturbation potential.
 Analyzing the electric properties for a specific impurity distribution is a rather formidable task.
@@
 Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
-We start our analysis by consider a static disorder that corresponds only to elastic electron scattering processes.
+We start our analysis by considering a static disorder that corresponds only to elastic electron scattering processes.
 We adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the associated system and we approximate this into a Gaussian white noise.
@@
 \end{subequations}
-where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function which solely depends only on $\vb{r}-\vb{r'}$, and decays with a characteristic length $r_c$.
-Since this study considers the case where the wavelength of radiation or a scattering electron is much greater than $r_c$, it is a reasonable to approximation its two-point correlation function by
+where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function that solely depends only on $\vb{r}-\vb{r'}$, and decays with a characteristic length $r_c$.
+Since this study considers the case where the wavelength of radiation or a scattering electron is much greater than $r_c$, it is reasonable to approximation its two-point correlation function by
 \begin{equation} \label{eq:4}
@@
 
-Since previous studies on Floquet-Drude conductivity \cite{wackerl20}, and magneto-transport properties in undressed \cite{endo09} and dressed \cite{dini16} quantum Hall systems have used this particular Gaussian white noise potential, we also selected this pertucular impurity model to describe our system.
-Such a choise enables us to compare our analytical results with these previous models.
+Since previous studies on Floquet-Drude conductivity \cite{wackerl20}, and magneto-transport properties in undressed \cite{endo09} and dressed \cite{dini16} quantum Hall systems have used this particular Gaussian white noise potential, we also selected this particular impurity model to describe our system.
+Such a choice enables us to compare our analytical results with these previous models.
 As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the
@@
   {\color{Red}
-  We have modellfed the effect caused by impurities as a single short-range perturbation potential.
+  We have modeled the effect caused by impurities as a single short-range perturbation potential.
 Analyzing the electric properties for a specific impurity distribution is a rather formidable task.
@@
   Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
-  Essentially, all these assumptions means that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+  Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
 This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20},
@@
 \end{equation}
-Applying these adequate conditions, we can simplify our derivation into single expression that can be compared with previous studies \cite{wackerl20,dini16,endo09} on
+Applying these adequate conditions, we can simplify our derivation into a single expression that can be compared with previous studies \cite{wackerl20,dini16,endo09} on
 magneto-transport in dressed quantum Hall systems. We have added clarification on the above assumptions in the manuscript.
@@
 This has led to an unexpected normalization factor in the yy-component of the  conductivity expression.
-Since we have only used the normalized $xx$-component of the conductivity tensor for subsequent analysis, this oversight has no impact on the analysis reported in the  manuscsript.
+Since we have only used the normalized $xx$-component of the conductivity tensor for subsequent analysis, this oversight has no impact on the analysis reported in the  manuscript.
 With this correction, we observe that both xx-component and $yy$-component show the same conductivity behaviors.
@@
 Suppose we applied an arbitrary directional polarized dressing field.
-In thay case, we could derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis.
+In that case, we could derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis.
 This would change the amplitude of the associated dressing field ($E$) in each direction.
@@
 To address your comments, we had to add new materials and reorganize our text.
-As a result, we have able to considerably improved our discussion on the underlying assumptions and corresponding physical significance of our analysis.
+As a result, we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis.
 We hope our response and the corresponding changes we incorporated into the manuscript will be sufficient to clarify the issues raised.
@@
 We thank the reviewer for pointing out the importance of this fact.
-In the revised manuscript, we have included detailed analysis of our results against the undressed 2DEG quantum Hall system behavior.
+In the revised manuscript, we have included a detailed analysis of our results against the undressed 2DEG quantum Hall system behavior.
 
@@
 
-We ommitted a discussion on the Anderson localization and topologically protected edge modes as we neglected them in our work.
+We omitted a discussion on the Anderson localization and topologically protected edge modes as we neglected them in our work.
 While deriving Eq.~[31], we have assumed that the applied static magnetic field is placed in a lower intensity range where we can neglect several effects known to appear in a 2DEG quantum Hall system.
@@
 Our work is very similar to theirs with an additional dressing field.
-Our results for the undressed system agrees with the results in Ref.
+Our results for the undressed system agree with the results in Ref.
 \cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks.
@@
   It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions.
-This is not an overly restrictive assumption and others have used similar assumption in their work e.g.
+This is not an overly restrictive assumption and others have used the same assumption in their work e.g.
 see \textit{et al.} \cite{endo09}.
@@
   {\color{Red}
-  We modelled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.
+  We modeled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.
   }
@@
 However, using the dressing field, we can squeeze the conductivity peaks on Landau levels, i.e., squeeze the region of longitudinal conductivity peaks placed near the Landau levels.
-This  imply sudden Hall conductivity transitions between one plateau to another near a Landau level.
+This  implies sudden Hall conductivity transitions between one plateau to another near a Landau level.
 As in Refs.
@@
   {\color{Red}
-  Despite this behavior being identified in previous work of Dini \textit{et al.}  \cite{dini16}, they cannot fully account for the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.
+  Despite this behavior being identified in the previous work of Dini \textit{et al.}  \cite{dini16}, they cannot fully account for the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.
 \cite{endo09}.
 The authors of Ref.
-\cite{dini16} have used the conventinal expression of longitudinal conductivity from Refs.
-\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening for Landau level.
-These predictions significantly deviates from the experimentally observed Landau level broadening \cite{endo09}.
-  However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
+\cite{dini16} have used the conventional expression of longitudinal conductivity from Refs.
+\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening for the Landau levels.
+These predictions significantly deviate from the experimentally observed Landau level broadening \cite{endo09}.
+  However, our generalized analysis on the conductivity of dressed quantum Hall systems provides a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
   }
@@
   In the study presented in Ref.
-\cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
+\cite{endo09}, the authors have assumed that the effective mass of an electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
   }

### 2021-11-18 response/response.tex
Update response paper until sec.Vi

@@
   It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions.
-This is not an overly restrictive assumption and others have used the same assumption in their work e.g.
+This is not an overly restrictive assumption and others have used the same assumption in their work, e.g.
 see \textit{et al.} \cite{endo09}.
@@
   In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.
-Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
   }

### 2021-11-18 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
Update response paper until sec.Vi

@@
 Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
-{\color{Red}Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
-This inspired investigations on theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
-These analytical formalisms provide a proper explanation for the experimental observations of MIROs.
+{\color{Red}
+Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
+This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+These formalisms provide a proper explanation for the experimental observations of MIROs.
 However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) fields.
-In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a purely dressing (nonabsorbable) field.
-The impacts induced by a purely dressing field on magnetotransport properties of 2DEG quantum Hall system need to be described by a non absorption mechanism and it has escaped the researchers’ attention before.
-Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system under high-frequency field.} However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
-{\color{Red}The authors of Ref.\cite{dini16} used the conductivity models from Refs.
+In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
+The influence of induced by a pure dressing field on
+magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
+Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.}
+However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
+{\color{Red}
+The authors of Ref.
+\cite{dini16} used the conductivity models from Refs.
 \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.}
@@
 {\color{Red}
-It is important to note that, in this analysis, we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions can be neglected.
-The use of this assumption can also be found in the study done by Endo \textit{et al.} \cite{endo09}.
+It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions.
+This is not an overly restrictive assumption and others have used the same assumption in their work, e.g.
+see \textit{et al.} \cite{endo09}.
 } In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
@@
 The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
-{\color{Red}In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.} Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
+{\color{Red}
+In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.} Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
 
@@
 {\color{Red}
-We modeled the effect caused by impurities in the considered system as a single short-range perturbation potential.
-Analyzing the electric properties for a specific impurity configuration is a rather formidable task and is not examined in this work since it is unlikely to have exactly the evaluated impurity configuration in an experiment.
+We have modeled the effect caused by impurities as a single short-range perturbation potential.
+Analyzing the electric properties for a specific impurity distribution is a rather formidable task.
+We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
 Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
-Furthermore, we assumed that our perturbation potential is formed by a group of randomly distributed impurities under the Edwards impurity model \cite{akkermans10,wackerl20}.
-Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-Then we  approximate the impurity potential into a Gaussian white noise \cite{akkermans10,wackerl20}.
-Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
+Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
+Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20},
+where $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
 Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
@@
 To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
-{\color{Red}In the study presented in Ref.~\cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.} In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
+{\color{Red}In the study presented in Ref.
+\cite{endo09}, the authors have assumed that the effective mass of an electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.} In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
 Therefore, in our calculations, we assumed that the natural least Landau level broadening also has this value: $\Gamma^{00}_{N=0}|_{E=0} = \SI{0.24}{\milli\eV}$.
@@
 {\color{Red}
-Since we consider the dressed quantum Hall system under the off-resonant condition, the absorption of photons are avoided.
-Therefore, we select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
+We consider a dressed quantum Hall system under off-resonant condition, where photon absorption does not happen.
+Therefore, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
 \begin{equation} \label{eq:33}
@@
 \end{equation}
-where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Under the low-temperature conditions ($k_BT \ll \varepsilon_F$), we can assume that the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy.
-This can be represented by the delta function \cite{endo09}
+where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
+At low-temperatures, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function
 \begin{equation} \label{eq:34}

### 2021-11-18 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
Update res paper

@@
 This is not an overly restrictive assumption and others have used the same assumption in their work, e.g.
-see \textit{et al.} \cite{endo09}.
-} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
+see \textit{et al.} \cite{endo09}.} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
 Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref.
@@
 \end{equation}
-Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(31) leads to
+Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
 \begin{equation} \label{eq:35}
@@
 $\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$, and $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$.
-Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
+Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
 \begin{equation} \label{eq:36}
@@
 {\color{Red}
-By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems under zero radiation with our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
-As observed in the experimental work done by Caviglia \textit{et al.} \cite{caviglia10}, the SdH oscillations period only depends on the perpendicular component of the applied magnetic field.
-Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} with a different type of 2DEG have been examined these SdH oscillations against the applied magnetic field amplitude.
-The magnetic field's perpendicular component amplitude defines the cyclotron frequency ($\omega_0$) of the considering system.
-Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in 2DEG quantum Hall system by changing the gate voltage.
-The  change of the gate voltage applied to the system will modify the Fermi level of the system.
-Since the Landau level energy is only dependent on the cyclotron frequency, this will generate the same SdH oscillations against gate voltage.
+By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
+As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of the SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
+Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude for different types of 2DEGs.
+The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
+Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in a 2DEG quantum Hall system by changing the gate voltage.
+The applied gate voltage to the system modifies the Fermi level of the system.
+Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation generates SdH oscillations.
 This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
-By comparing these empirical observations with our results given in Fig.~\ref{fig:4}, we can identify that our oscillations are also shown the same characteristic behavior with $\hbar\omega_0$ periodicity against Fermi level value.
-Furthermore, when we increase the gate voltage, the Fermi level of the system gets increased.
-This will locate to the Fermi level on higher-order Landau levels.
+By comparing these observations against our results in Fig.~\ref{fig:4}, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
+Furthermore, when we increase the gate voltage, the Fermi level rises.
 As illustrated in Fig.~\ref{fig:4}, this will result in a higher conductivity peak value at the higher-order Landau levels.
 This same behavior was also observed in the experimental observations presented in Ref.
-\cite{wakabayashi78} as well.}
+\cite{wakabayashi78}.
+In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.}
 
@@
 {\color{Red}
-Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable magnetotransport properties induced by microwave radiation on 2DEG quantum Hall systems.
-However, these experiments and theoretical models only examined the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
+Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
+magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems.
+However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
 It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
-In our case, the applied dressing field is in the off-resonant range and that will only change the broadening of Landau levels and avoid any contribution towards the photon absorptions.
+In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions.
 This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
@@
 The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
-The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneously peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
+The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
 This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically.
 The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
-However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening in low-temperatures is the disorders in materials \cite{ando85,dial07}.
-The broaden sequence of delta functions of density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as Shubnikov–de Haas (SdH) oscillations.
-\cite{endo09,wakabayashi78}.
-
-Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system developed by considering low-temperature limit with gaussian impurity broadening assumptions.
-As illustrated in Fig.~\ref{fig:4}, we were also able to demonstrate the same SdH oscillations as experimental results observed in Ref.\cite{endo09,wakabayashi78} through our model.
-Under the undressed condition, our results overlap with the conductivity measurement for quantum Hall systems \cite{endo09}.
-However, from our results given in Fig.~\ref{fig:5}, we demonstrate that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-In low-temperatures, the principal cause of broadening of these conductivity peaks is impurity scattering and using an external dressing field we can suppress the scattering which results in shrinkage of both the scattering-induced broadening and the longitudinal conductivity peaks.
+However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}.
+The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.
+
+Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with gaussian impurity broadening assumptions.
+As illustrated in Fig.~\ref{fig:4}, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
+Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}.
+Strikingly, we show in Fig.~\ref{fig:5} that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering.
+Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
 
@@
 In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
-The charge carrier concentration of a considering system is an imperative parameter that defines the conductivity properties of the system.
-We can manipulate that using the electrostatic field-effect mechanism and it is an ideal tool to control the conductivity in some specific systems.
-A 2DEG under static magnetic field with quantum Hall effects is an excellent example that the gate electric field can be used to manipulate the conductivity.
-A considerable number of researches have been performed using different types of 2D field-effect transistors (FETs) in magnetic fields to study the charge transport in the quantum limit \cite{wakabayashi78,yang18,long20,li14}.
-In the study done by Yang \textit{et al.} \cite{yang18}, the authors have observed quantized Hall plateaus and Shubnikov–de Haas oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields in low-temperatures.
-Since the Fermi level of the system can be altered with the applied gate voltage, this behavior can be easily mapped into our results given in Fig.~\ref{fig:4}.
-However, the specialty of our outcomes is we owned the capability of manipulating the broadening of the conductivity regions using an external dressing field.
-Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general mathematical description to manipulate longitudinal conductivity broadening using only a high-intensity electromagnetic field.
+The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
+As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
+A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
+We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}.
+Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures.
+Since the Fermi level of a system can be altered with the applied gate voltage, our Fig.~\ref{fig:4} depicts this result.
+In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field.
+Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.
 
@@
 In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
-As a result of manipulating the broadening of conductivity regions, we can shrink the broadening of conductivity peaks around Landau levels using a high-intensity dressing field.
+As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field.
 This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
-Furthermore, adopting the mechanism presented in Ref.\cite{hirakawa01}, we can utilize our manipulation of conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
-Based on these ready-to-use nanoelectronic devices and their feasible optimization, we believe that our mathematical description offers the potential to realize advanced nanoelectronic devices.
-Furthermore, this theoretical model will help to develop simulation tools that will design the quantum effects in magnetotransport properties of 2D nanostructures.
+Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
+We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
+Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
+magneto-transport properties of 2D nanostructures.
 }
@@
 {\color{Red}
-We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within an order where we can neglect effects of the Anderson localization, the formation of the edge states, the spin splitting, and the electron-electron interactions.
-Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.}
+We modeled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.} Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.
 
@@
 Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels.
-{\color{Red}Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results do not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}.
-This is due to the fact that the authors of Ref.\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Ref.\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
-However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.}
+{\color{Red}Despite this behavior being identified in the previous work of Dini \textit{et al.}  \cite{dini16}, they cannot fully account for the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.
+\cite{endo09}.
+The authors of Ref.
+\cite{dini16} have used the conventional expression of longitudinal conductivity from Refs.
+\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening for the Landau levels.
+These predictions significantly deviate from the experimentally observed Landau level broadening \cite{endo09}.
+However, our generalized analysis on the conductivity of dressed quantum Hall systems provides a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.}
 
@@
 \end{equation}
-Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
+Let $[y - y_0 - \zeta(t)] = \bar{y}$, and we can obtain
 \begin{equation} \label{eq:d7}
@@
 \end{equation}
-Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59,boyd18}
+Using the following integral identities of the Floquet modes that are made of Gauss-Hermite functions \cite{vedenyapin11,szego59,boyd18}
 \begin{equation} \label{eq:d8}
@@
 \end{equation}
-Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
+Due to high complexity of extract solution, in this study we only consider the constant contribution from the Fourier series components of the above expression.
+Therefore, we can identify the $0$-th component of the Fourier series as
 \begin{equation} \label{eq:d11}
@@
 \end{equation}
-For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
+To calculate the electric current operator, we substitute the electron’s charge and effective mass to the above derived equation. This leads to
 \begin{equation} \label{eq:d12}

### 2021-11-19 response/response.tex
Update res paper
Corrections to res

@@
 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
-  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of the SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
-  Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude for different types of 2DEGs.
+  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
+  Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
   The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
-  Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in a 2DEG quantum Hall system by changing the gate voltage.
   The applied gate voltage to the system modifies the Fermi level of the system.
-  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation generates SdH oscillations.
-  This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
+  This oscillatory behavior against applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
   By comparing these observations against our results in Fig.
@@
 To describe these behaviors Durst \textit{et al.} \cite{durst03} introduced a simple theoretical model assuming that the experimentally observed oscillations are a consequence of photoexcited disorder-scattered electrons.
-However, later a novel model was proposed in Refs. \cite{dmitriev03,dmitriev05,dmitriev09} considering the changes of the electron distribution function done by the microwave field.
+However, later Refs. \cite{dmitriev03,dmitriev05,dmitriev09} proposed a novel model considering the changes were made on
+the electron distribution function by the microwave field.
 These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have successfully described the behavior of MIROs at experimentally relevant temperatures that were missed in the previous model \cite{durst03}.
 Furthermore, we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorption by an electron in the associated system.
-In our theoretical model, we take into account higher frequencies than microwaves as the dressing field.
-Therefore we can identify and quantify significant dissimilarities between our system and MIROs systems \cite{zudov01,mani02,zudov03,mani04,durst03,dmitriev03,dmitriev05,dmitriev09}. They are:
+In our theoretical model, we take into account higher frequencies than microwaves as the dressing electromagnetic field.
+Therefore we can identify and quantify significant dissimilarities between our system and MIRO systems \cite{zudov01,mani02,zudov03,mani04,durst03,dmitriev03,dmitriev05,dmitriev09}. They are:
 \begin{itemize}
   \item
-  in the experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$).
+  the experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$).
 This leads to building the theoretical models presented in Refs.
 \cite{durst03,dmitriev03} by assuming that these oscillations are caused by photoexcited electrons.
-Since these models consider on relevant frequency range (microwave radiation), it will allow us to acknowledge the photon absorption by electrons.
+Since these models consider on a relevant frequency range (microwave radiation), it will allow us to acknowledge the photon absorption by electrons.
 In contrast to that, our consideration is only focused on the systems with high-frequency range dressing fields which will not be associated with any photon absorption.
   \item
-  the applied microwave radiation power on the MIROs experiments \cite{mani02,zudov03} varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
+  the applied microwave radiation power on the MIRO experiments \cite{mani02,zudov03} varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
 However, in our analysis, we take the dressing field as a high-intensity electromagnetic field, where we cannot consider the dressing field as a perturbation in our analysis.
@@
 In comparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics.
-Therefore in our analysis, we aim at the effects induced by high-intensity magnetic fields ($B \sim \SI{1}{\tesla}$).
+Therefore in our analysis, we aim at the effects induced by higher intensity magnetic fields ($B \sim \SI{1}{\tesla}$) than the MIRO experiments.
   \item
@@
 We have addressed these modifications through the Floquet theory.
-However, the MIROs models \cite{durst03,dmitriev03} are based on low-frequency cases where the system can absorb low-frequency photons from the field.
+However, the MIRO models \cite{durst03,dmitriev03} are based on low-frequency cases where the system can absorb low-frequency photons from the field.
 \end{itemize}
@@
   {\color{Red}
-  Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
+  Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
   This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
 These formalisms provide a proper explanation for the experimental observations of MIROs.
-However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) fields.
+However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
   In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
-  The influence of induced by a pure dressing field on
+  The influence induced by a pure dressing field on
   magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
@@
 In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions.
-This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
-Therefore our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
+This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems.
+Therefore, our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
   }
@@
 where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function that solely depends only on $\vb{r}-\vb{r'}$, and decays with a characteristic length $r_c$.
-Since this study considers the case where the wavelength of radiation or a scattering electron is much greater than $r_c$, it is reasonable to approximation its two-point correlation function by
+Since this study considers the case where the wavelength of radiation or a scattering electron is much greater than $r_c$, it is reasonable to approximate its two-point correlation function by
 \begin{equation} \label{eq:4}
@@
 Furthermore, considering the properties of a Gaussian white noise impurity distribution \cite{wackerl20,akkermans10}, we assume $V_{imp}$ is a constant in the momentum space.
+Here $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
+All the detailed steps for the derivation of the Floquet-Fermi golden rule for a dressed quantum Hall system are included in Appendix C.
 However, throughout the derivation, we use only the first-order contribution (Born approximation) of the impurity potential.
-All the detailed steps for the derivation of the Floquet-Fermi golden rule for a dressed quantum Hall system are included in Appendix C.
 
@@
   Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20},
-  where $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
+This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20}.
+  Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
   Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
@@
 Our analysis derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
-In contrast to the MIROs analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, but photon absorption does not happen.
+In contrast to the MIRO analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, but photon absorption does not happen.
 Therefore, we can select the Fermi-Dirac distribution as our particle distribution function for Eq.~[31]
@@
   \end{equation}
-  Using the following integral identities of the Floquet modes that are made up of Gauss-Hermite functions \cite{vedenyapin11,szego59}
+  Using the following integral identities of the Floquet modes that are made of Gauss-Hermite functions \cite{vedenyapin11,szego59}
   \begin{equation} \tag{D8}

### 2021-11-19 response/response.tex
Correction to res paper

@@
 Our analysis derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
-In contrast to the MIRO analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, but photon absorption does not happen.
+In contrast to the MIRO analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, where the photon absorption does not happen.
 Therefore, we can select the Fermi-Dirac distribution as our particle distribution function for Eq.~[31]
@@
 Applying these adequate conditions, we can simplify our derivation into a single expression that can be compared with previous studies \cite{wackerl20,dini16,endo09} on
-magneto-transport in dressed quantum Hall systems. We have added clarification on the above assumptions in the manuscript.
+magneto-transport in dressed quantum Hall systems. We have added clarification on the above assumptions in the revised manuscript.
 \begin{itemize}
@@
 \bibliography{response}
-
-\bigskip
-\bigskip
-
+\medskip
 Sincerely yours,

### 2021-11-19 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
Correction to res paper

@@
 {\color{Red}
-Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
+Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
 This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
 These formalisms provide a proper explanation for the experimental observations of MIROs.
-However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) fields.
+However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
 In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
-The influence of induced by a pure dressing field on
+The influence induced by a pure dressing field on
 magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
@@
 Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20},
-where $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
+This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20}.
+Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
 Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
@@
 By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
-As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of the SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
-Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude for different types of 2DEGs.
+As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
+Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
 The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
-Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in a 2DEG quantum Hall system by changing the gate voltage.
 The applied gate voltage to the system modifies the Fermi level of the system.
-Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation generates SdH oscillations.
-This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
+This oscillatory behavior against applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
 By comparing these observations against our results in Fig.~\ref{fig:4}, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
@@
 In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions.
-This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems.
-Therefore our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
+This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems.
+Therefore, our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
 }

### 2021-11-19 response/response.tex
final corrections

@@
 
-We have made minor changes in language and presentation to improve clarity, and to match the rest of the manuscript better to the changes done to address the reviewers' comments.
+We have made some minor changes in language and presentation to improve the clarity and organization of the manuscript.
 \begin{itemize}
     \item Section I - seventh paragraph (page 2): \\
-        {\color{Red} In Sec. VII, we discuss the physical significance of our theoretical results and their possible employments in future nanoelectronic devices.
+        {\color{Red} In Sec. VII, we discuss the physical significance of our theoretical results and their possible use in future nanoelectronic devices.
         Finally, we summarize our findings and present our conclusions in Sec. VIII.}
@@
   The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
-  The applied gate voltage to the system modifies the Fermi level of the system.
+  The gate voltage modifies the Fermi level of the system.
   Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
-  This oscillatory behavior against applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+  Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
   By comparing these observations against our results in Fig.
@@
 
-  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with gaussian impurity broadening assumptions.
+  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
   As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
@@
 \cite{zudov01,mani02,zudov03,mani04}.
-In this range of weak magnetic fields,  we can only observe MIROs as Shubnikov–de Haas (SdH) oscillations reveal only on high-intensity magnetic fields.
+In this range of weak magnetic fields,  we can only observe MIROs as Shubnikov–de Haas (SdH) oscillations reveal only with high-intensity magnetic fields.
 In comparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics.
@@
 
-Although we have extended our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoretical model into different types of particle distribution functions.
+Although we have restricted our general derivation given in Eq.~[31] into a particular instance for comparison, there is no fundemental restriction in extending our theoretical model into different types of particle distribution functions.
 As presented in the previous work of Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion needs to address the changes in distribution functions in our derived general longitudinal conductivity formula, and this would be a noteworthy extension to our study.
@@
 
-Suppose we applied an arbitrary directional polarized dressing field.
+Suppose we apply an arbitrary directional polarized dressing field.
 In that case, we could derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis.
 This would change the amplitude of the associated dressing field ($E$) in each direction.
-There will be a new component in parallel to the considering conductivity component, which will modify the time-dependent Hamiltonian given in Eq.~[2].
+There will be a new component in parallel to the conductivity component of interest, which will modify the time-dependent Hamiltonian given in Eq.~[2].
 Then, we need to solve the Schrödinger equation with the modified Hamiltonian to find the new Floquet modes for the new system.
@@
   {\color{Red}
-  It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions.
-This is not an overly restrictive assumption and others have used the same assumption in their work, e.g.
-see \textit{et al.} \cite{endo09}.
+  It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, and the electron-electron interactions.
+These are not overly restrictive assumptions, and other have successfully used same assumptions in their work, e.g see Endo \textit{et al.} \cite{endo09}.
   }

### 2021-11-19 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
final corrections to paper res

@@
 {\color{Red}
-It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, the electron-electron interactions.
-This is not an overly restrictive assumption and others have used the same assumption in their work, e.g.
-see \textit{et al.} \cite{endo09}.} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
+It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, and the electron-electron interactions.
+These are not overly restrictive assumptions, and other have successfully used same assumptions in their work, e.g.
+see Endo \textit{et al.} \cite{endo09}.} In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
 Finally, we demonstrate that our generalized model reproduces the results of the state-of-the-art conductivity model in Ref.
@@
 {\color{Red}In Sec.
-\ref{sec:physical_significance}, we discuss the physical significance of our theoretical results and their possible employments in future nanoelectronic devices.
+\ref{sec:physical_significance}, we discuss the physical significance of our theoretical results and their possible use in future nanoelectronic devices.
 Finally, we summarize our findings and present our conclusions in Sec. \ref{sec:conclusions}.}
@@
 The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
-The applied gate voltage to the system modifies the Fermi level of the system.
+The gate voltage modifies the Fermi level of the system.
 Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
-This oscillatory behavior against applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
 By comparing these observations against our results in Fig.~\ref{fig:4}, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
@@
 
-Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with gaussian impurity broadening assumptions.
+Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
 As illustrated in Fig.~\ref{fig:4}, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.

### 2021-11-19 paper/dressed_quantum_hall_sub2/dressed_quantum_hall_sub2.tex
Add submission 2 paper

--- 2021-11-09 paper/Submission/Manuscript/dressed_quantum_hall.tex
@@
 Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
-Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems.
+Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
+This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+These formalisms provide a proper explanation for the experimental observations of MIROs.
+However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
+In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
+The influence induced by a pure dressing field on
+magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
+Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
 However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
-In their study, they used the conductivity models from Refs.
+The authors of Ref.
+\cite{dini16} used the conductivity models from Refs.
 \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
@@
 This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
+It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, and the electron-electron interactions.
+These are not overly restrictive assumptions, and other have successfully used same assumptions in their work, e.g.
+see Endo \textit{et al.} \cite{endo09}.
 In this study, we explicitly calculate the longitudinal components ($\sigma^{xx},\sigma^{yy}$) of the conductivity tensor in a periodically driven quantum Hall system by developing a generalized analytical description using the Floquet-Drude conductivity \cite{wackerl20}.
@@
 \ref{sec:floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
-The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec:manipulate_conductivity}.
-In Sec. \ref{sec:conclusions}, we summarize our analysis and present our conclusions.
+The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec.
+\ref{sec:manipulate_conductivity}.
+In Sec.
+\ref{sec:physical_significance}, we discuss the physical significance of our theoretical results and their possible use in future nanoelectronic devices.
+Finally, we summarize our findings and present our conclusions in Sec. \ref{sec:conclusions}.
 %===============================================================================
@@
 The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
-In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field.
+In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.
 Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
@@
 A more detailed derivation is given in Appendix \ref{appendix_c}.
-We modeled the effect caused by impurities in the considered system as a single perturbation potential.
-Since random impurities in a disordered metal offer a better approximation for experimental conditions, we assumed that our perturbation potential is formed by a group of randomly distributed impurities.
-Thus, we represented the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+We have modeled the effect caused by impurities as a single short-range perturbation potential.
+Analyzing the electric properties for a specific impurity distribution is a rather formidable task.
+We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
+Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
+Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
+Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
+This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20}.
 Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
 Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
+In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
 
@@
 To make a comparison, we have selected the experiment parameters to match with analysis in Ref.~\cite{endo09}.
-In that study, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
+In the study presented in Ref.
+\cite{endo09}, the authors have assumed that the effective mass of an electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
 In addition, they used the broadening of the undressed $0$-th Landau level $\Gamma_0$ as $\SI{0.24}{\milli\eV}$.
@@
 \end{equation}
-We use the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
+We consider a dressed quantum Hall system under off-resonant condition, where photon absorption does not happen.
+Therefore, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
 \begin{equation} \label{eq:33}
@@
 \end{equation}
-where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system.
-Considering the above distribution for extremely low-temperature conditions, we can use the following approximation
+where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
+At low-temperatures, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function
 \begin{equation} \label{eq:34}
@@
 \end{equation}
-where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$
-and
-$\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$.
+where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$,
+$\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$, and $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$.
 Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix \ref{appendix_d}
@@
 \end{equation}
-with $\sigma^0 = \flatfrac{e^2}{(\pi \hbar A)}$, and we can express this as
+with $\sigma_0 = \flatfrac{e^2l_0^2}{(\pi \hbar A)}$, and we can express this as
 \begin{equation} \label{eq:38}
@@
 
-On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.
+By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
+As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
+Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
+The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
+The gate voltage modifies the Fermi level of the system.
+Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
+Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
+By comparing these observations against our results in Fig.~\ref{fig:4}, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
+Furthermore, when we increase the gate voltage, the Fermi level rises.
+As illustrated in Fig.~\ref{fig:4}, this will result in a higher conductivity peak value at the higher-order Landau levels.
+This same behavior was also observed in the experimental observations presented in Ref.
+\cite{wakabayashi78}.
+In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
+
+Considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.
 When we increase the intensity level of the dressing field, the conductivity regions get weakened as illustrated in the Fig.~\ref{fig:5}.
@@
 
+\begin{figure}[t]
+\includegraphics[scale=0.54]{fig_4_conductivity_with_fermi_level}
+\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\label{fig:4}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[scale=0.54]{fig_5_conductivity_with_fermi_level_zoomed}
+\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\label{fig:5}
+\end{figure}
+
 These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
-As the authors remarked in that publication, since the Fermi level of the system can be changed with the applied gate voltage of the material, this can be utilized as a 2D switch for nanoscale optoelectronics applications.
-Controlling  the external dressing field's intensity allows us to fine-tune this switching mechanism for optimized performance.
 However, we can distinguish that the shapes and behavior of the conductivity regions that illustrated in Fig.~\ref{fig:4} and Fig.~\ref{fig:5} are generally incompatible with the results reported in Ref.~\cite{dini16}.
@@
 
-\begin{figure}[t]
-\includegraphics[scale=0.54]{fig_4_conductivity_with_fermi_level}
-\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:4}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{fig_5_conductivity_with_fermi_level_zoomed}
-\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:5}
-\end{figure}
-%===============================================================================
-
-%===============================================================================
-% Section 07 : Conclusions
+Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
+magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems.
+However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
+It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
+In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions.
+This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems.
+Therefore, our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
+%===============================================================================
+
+%===============================================================================
+% Section 07 : Physical significance of the outcome
+%===============================================================================
+\section{\label{sec:physical_significance} Physical Significance of the Outcomes}
+With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
+The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
+The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
+This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically.
+The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
+However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}.
+The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.
+
+Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
+As illustrated in Fig.~\ref{fig:4}, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
+Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}.
+Strikingly, we show in Fig.~\ref{fig:5} that we can manipulate the broadening of these conductivity peaks using an external dressing field.
+At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering.
+Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
+
+Research on novel states of matter has driven the evolution of present-day nanoelectronic devices.
+In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
+The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
+As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
+A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
+We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}.
+Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures.
+Since the Fermi level of a system can be altered with the applied gate voltage, our Fig.~\ref{fig:4} depicts this result.
+In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field.
+Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.
+
+The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
+In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
+As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field.
+This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
+Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
+We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
+Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
+magneto-transport properties of 2D nanostructures.
+%===============================================================================
+
+%===============================================================================
+% Section 08 : Conclusions
 %===============================================================================
@@
 We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method.
-We assumed the impurities in the material as a Gaussian random scattering potential.
-Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.
+We modeled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.
+Finally, we derived analytical expressions for the diagonal components of electric conductivity tensor concerning the 2DEG quantum Hall system under low temperatures.
 
@@
 Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels.
-Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.
-However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.
+Despite this behavior being identified in the previous work of Dini \textit{et al.}  \cite{dini16}, they cannot fully account for the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.
+\cite{endo09}.
+The authors of Ref.
+\cite{dini16} have used the conventional expression of longitudinal conductivity from Refs.
+\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening for the Landau levels.
+These predictions significantly deviate from the experimentally observed Landau level broadening \cite{endo09}.
+However, our generalized analysis on the conductivity of dressed quantum Hall systems provides a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
 
@@
 \end{equation}
-Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
-\begin{subequations} \label{eq:d8}
-  \begin{align}
+Using the following integral identities of the Floquet modes that are made of Gauss-Hermite functions \cite{vedenyapin11,szego59,boyd18}
+\begin{equation} \label{eq:d8}
+  \int \chi_{n}({y})
+  \chi_{n'}({y}) d{y} = \delta_{n',n},
+\end{equation}
+\begin{equation} \label{eq:d9}
     \int
-    \chi_{n}({y})
-    \chi_{n'}({y}) d{y} &=
-    \delta_{n',n}, \\
-    \int
-    y \chi_{n}({y})\chi_{n'}({y}) d{y} &=
+    y \chi_{n}({y})\chi_{n'}({y}) d{y} =
+    \frac{1}{\kappa}
     \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
     \delta_{n',n-1} \right),
-  \end{align}
-\end{subequations}
+\end{equation}
 we simplify the matrix elements of $x$-directional current operator to obtain
-\begin{equation} \label{eq:d9}
+\begin{equation} \label{eq:d10}
   \begin{aligned}
     &\left({j}_x \right)_{nm,n'm'} =
-    \frac{eB}{{\widetilde{m}}}
+    \frac{eB}{{\widetilde{m}}\kappa}
     \delta_{k_x,k'_x} \\
@@
 \end{equation}
-Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
-\begin{equation} \label{eq:d10}
+Due to high complexity of extract solution, in this study we only consider the constant contribution from the Fourier series components of the above expression.
+Therefore, we can identify the $0$-th component of the Fourier series as
+\begin{equation} \label{eq:d11}
   \begin{aligned}
       \left({j}_x \right)_{nm,n'm'} =&
-      \frac{eB}{\widetilde{m}}
+      \frac{eB}{\widetilde{m}\kappa}
       \delta_{k_x,k'_x} \\
@@
 \end{equation}
-For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
-\begin{equation} \label{eq:d11}
+To calculate the electric current operator, we substitute the electron’s charge and effective mass to the above derived equation. This leads to
+\begin{equation} \label{eq:d12}
   \begin{aligned}
       \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
-      \frac{e^2B}{{m_e}}
+      \frac{e\hbar}{{m_e}l_0}
       \delta_{k_x,k'_x}\\
@@
       \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-      \delta_{n',n-1} \right).
-  \end{aligned}
-\end{equation}
+      \delta_{n',n-1} \right),
+  \end{aligned}
+\end{equation}
+where $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$ is the magnetic length.
 
 Moreover, we can identify the $y$-directional current operator component as
-\begin{equation} \label{eq:d12}
+\begin{equation} \label{eq:d13}
   \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
@@
 \end{equation}
-After following the same steps done for the $x$-directional current operator, we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
-\begin{equation} \label{eq:d14}
+After following the same steps done for the $x$-directional current operator, and recursion relation of the first derivative of Gauss-Hermite functions \cite{boyd18}
+\begin{equation} \label{eq:d15}
+  \begin{aligned}
+    \pdv{\chi_{n}({y})}{y} =
+    \kappa\left[
+    -  \sqrt{\frac{n+1}{2}} \chi_{n+1}({y})
+    +  \sqrt{\frac{n}{2}} \chi_{n - 1}({y})
+    \right],
+  \end{aligned}
+\end{equation}
+we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
+\begin{equation} \label{eq:d16}
   \begin{aligned}
     \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
-    \frac{ie\hbar}{{m_e}}
+    \frac{ie\hbar\kappa}{{m_e}}
+    \delta_{k_x,k'_x} \\
+    & \times
+    \left(
+    \sqrt{\frac{n}{2}} \delta_{n',n-1}
+    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
+    \right),
+  \end{aligned}
+\end{equation}
+and
+\begin{equation} \label{eq:d17}
+  \begin{aligned}
+    \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
+    \frac{ie\hbar}{{m_e}l_0}
     \delta_{k_x,k'_x} \\
@@
 \providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}%
-\begin{thebibliography}{73}%
+\begin{thebibliography}{98}%
 \makeatletter
@@
   {Premaratne}},\ and\ \bibinfo {author} {\bibfnamefont {D.~L.}\ \bibnamefont
-  {Andrews}},\ }\href {https://10.1103/PhysRevB.92.035128} {\bibfield
+  {Andrews}},\ }\href {https://doi.org/10.1103/PhysRevB.92.035128} {\bibfield
   {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
@@
   {https://doi.org/10.1088/0953-8984/21/34/345803} {\bibfield  {journal}
-  {\bibinfo  {journal} {J. Phys.: Condens. Matter}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {J. Phys. Condens. Matter}\ }\textbf {\bibinfo {volume}
   {21}},\ \bibinfo {pages} {345803} (\bibinfo {year} {2009})}\BibitemShut
@@
   \bibinfo {author} {\bibfnamefont {U.}~\bibnamefont {Zeitler}}, \bibinfo
-  {author} {\bibfnamefont {A.~K.}~\bibnamefont {Geim}}, \bibinfo {author}
+  {author} {\bibfnamefont {A.}~\bibnamefont {Geim}}, \bibinfo {author}
   {\bibfnamefont {M.}~\bibnamefont {Henini}},\ and\ \bibinfo {author}
-  {\bibfnamefont {J.~C.}~\bibnamefont {Maan}},\ }\href
+  {\bibfnamefont {J.}~\bibnamefont {Maan}},\ }\href
   {https://doi.org/10.1103/PhysRevLett.78.4621} {\bibfield  {journal} {\bibinfo
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-  {Pan}}, \bibinfo {author} {\bibfnamefont {J.~S.}~\bibnamefont {Xia}}, \bibinfo
-  {author} {\bibfnamefont {H.~L.}~\bibnamefont {Stormer}}, \bibinfo {author}
-  {\bibfnamefont {D.~C.}~\bibnamefont {Tsui}}, \bibinfo {author} {\bibfnamefont
-  {C.~L.}~\bibnamefont {Vicente}}, \bibinfo {author} {\bibfnamefont
-  {E.~D.}~\bibnamefont {Adams}}, \bibinfo {author} {\bibfnamefont
-  {N.~S.}~\bibnamefont {Sullivan}}, \bibinfo {author} {\bibfnamefont
-  {L.~N.}~\bibnamefont {Pfeiffer}}, \bibinfo {author} {\bibfnamefont
-  {K.~W.}~\bibnamefont {Baldwin}},\ and\ \bibinfo {author} {\bibfnamefont
-  {K.~W.}~\bibnamefont {West}},\ }\href
+  {Pan}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Xia}}, \bibinfo
+  {author} {\bibfnamefont {H.}~\bibnamefont {Stormer}}, \bibinfo {author}
+  {\bibfnamefont {D.}~\bibnamefont {Tsui}}, \bibinfo {author} {\bibfnamefont
+  {C.}~\bibnamefont {Vicente}}, \bibinfo {author} {\bibfnamefont
+  {E.}~\bibnamefont {Adams}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Sullivan}}, \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Pfeiffer}}, \bibinfo {author} {\bibfnamefont
+  {K.}~\bibnamefont {Baldwin}},\ and\ \bibinfo {author} {\bibfnamefont
+  {K.}~\bibnamefont {West}},\ }\href
   {https://doi.org/10.1103/PhysRevLett.95.066808} {\bibfield  {journal}
@@
   \bibinfo {pages} {066808} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zudov}\ \emph {et~al.}(2001)\citenamefont {Zudov},
+  \citenamefont {Du}, \citenamefont {Simmons},\ and\ \citenamefont
+  {Reno}}]{zudov01}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Zudov}}, \bibinfo {author} {\bibfnamefont {R.~R.}\ \bibnamefont {Du}},
+  \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont {Simmons}},\ and\
+  \bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont {Reno}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.64.201311} {\bibfield  {journal} {\bibinfo
+  {journal} {Phy. Rev. B}\ }\textbf {\bibinfo {volume} {64}},\ \bibinfo {pages}
+  {201311} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mani}\ \emph {et~al.}(2002)\citenamefont {Mani},
+  \citenamefont {Smet}, \citenamefont {von Klitzing}, \citenamefont
+  {Narayanamurti}, \citenamefont {Johnson},\ and\ \citenamefont
+  {Umansky}}]{mani02}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+  {Mani}}, \bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont {Smet}},
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {von Klitzing}}, \bibinfo
+  {author} {\bibfnamefont {V.}~\bibnamefont {Narayanamurti}}, \bibinfo {author}
+  {\bibfnamefont {W.~B.}\ \bibnamefont {Johnson}},\ and\ \bibinfo {author}
+  {\bibfnamefont {V.}~\bibnamefont {Umansky}},\ }\href
+  {https://doi.org/10.1038/nature01277} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature}\ }\textbf {\bibinfo {volume} {420}},\ \bibinfo {pages}
+  {646} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zudov}\ \emph {et~al.}(2003)\citenamefont {Zudov},
+  \citenamefont {Du}, \citenamefont {Pfeiffer},\ and\ \citenamefont
+  {West}}]{zudov03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Zudov}}, \bibinfo {author} {\bibfnamefont {R.~R.}\ \bibnamefont {Du}},
+  \bibinfo {author} {\bibfnamefont {L.~N.}\ \bibnamefont {Pfeiffer}},\ and\
+  \bibinfo {author} {\bibfnamefont {K.~W.}\ \bibnamefont {West}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.90.046807} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phy. Rev. Lett.}\ }\textbf {\bibinfo {volume} {90}},\
+  \bibinfo {pages} {046807} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mani}\ \emph {et~al.}(2004)\citenamefont {Mani},
+  \citenamefont {Smet}, \citenamefont {Von~Klitzing}, \citenamefont
+  {Narayanamurti}, \citenamefont {Johnson},\ and\ \citenamefont
+  {Umansky}}]{mani04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+  {Mani}}, \bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont {Smet}},
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Von~Klitzing}}, \bibinfo
+  {author} {\bibfnamefont {V.}~\bibnamefont {Narayanamurti}}, \bibinfo {author}
+  {\bibfnamefont {W.}~\bibnamefont {Johnson}},\ and\ \bibinfo {author}
+  {\bibfnamefont {V.}~\bibnamefont {Umansky}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.92.146801} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phy.Rev. Lett.}\ }\textbf {\bibinfo {volume} {92}},\
+  \bibinfo {pages} {146801} (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Durst}\ \emph {et~al.}(2003)\citenamefont {Durst},
+  \citenamefont {Sachdev}, \citenamefont {Read},\ and\ \citenamefont
+  {Girvin}}]{durst03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~C.}\ \bibnamefont
+  {Durst}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sachdev}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Read}},\ and\ \bibinfo
+  {author} {\bibfnamefont {S.~M.}\ \bibnamefont {Girvin}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.91.086803} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {91}},\
+  \bibinfo {pages} {086803} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dmitriev}\ \emph {et~al.}(2003)\citenamefont
+  {Dmitriev}, \citenamefont {Mirlin},\ and\ \citenamefont
+  {Polyakov}}]{dmitriev03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont
+  {Dmitriev}}, \bibinfo {author} {\bibfnamefont {A.~D.}\ \bibnamefont
+  {Mirlin}},\ and\ \bibinfo {author} {\bibfnamefont {D.~G.}\ \bibnamefont
+  {Polyakov}},\ }\href {https://doi.org/10.1103/PhysRevLett.91.226802}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {91}},\ \bibinfo {pages} {226802} (\bibinfo {year}
+  {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dmitriev}\ \emph {et~al.}(2005)\citenamefont
+  {Dmitriev}, \citenamefont {Vavilov}, \citenamefont {Aleiner}, \citenamefont
+  {Mirlin},\ and\ \citenamefont {Polyakov}}]{dmitriev05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont
+  {Dmitriev}}, \bibinfo {author} {\bibfnamefont {M.~G.}\ \bibnamefont
+  {Vavilov}}, \bibinfo {author} {\bibfnamefont {I.~L.}\ \bibnamefont
+  {Aleiner}}, \bibinfo {author} {\bibfnamefont {A.~D.}\ \bibnamefont
+  {Mirlin}},\ and\ \bibinfo {author} {\bibfnamefont {D.~G.}\ \bibnamefont
+  {Polyakov}},\ }\href {https://doi.org/10.1103/PhysRevB.71.115316} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {71}},\ \bibinfo {pages} {115316} (\bibinfo {year} {2005})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Dmitriev}\ \emph {et~al.}(2009)\citenamefont
+  {Dmitriev}, \citenamefont {Khodas}, \citenamefont {Mirlin}, \citenamefont
+  {Polyakov},\ and\ \citenamefont {Vavilov}}]{dmitriev09}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~A.}\ \bibnamefont
+  {Dmitriev}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Khodas}},
+  \bibinfo {author} {\bibfnamefont {A.~D.}\ \bibnamefont {Mirlin}}, \bibinfo
+  {author} {\bibfnamefont {D.~G.}\ \bibnamefont {Polyakov}},\ and\ \bibinfo
+  {author} {\bibfnamefont {M.~G.}\ \bibnamefont {Vavilov}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.80.165327} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {80}},\ \bibinfo
+  {pages} {165327} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Landau}(1930)}]{landau30}%
@@
   \bibinfo {pages} {289} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Akkermans}\ and\ \citenamefont
+  {Montambaux}(2010)}]{akkermans10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Akkermans}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Montambaux}},\ }\href@noop {} {\emph {\bibinfo {title} {Mesoscopic Physics
+  of Electrons and Photons}}}\ (\bibinfo  {publisher} {Cambridge University
+  Press},\ \bibinfo {year} {2010})\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Winkler}(2003)}]{winkler03}%
@@
   {pages} {235124} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wakabayashi}\ and\ \citenamefont
+  {Kawaji}(1978)}]{wakabayashi78}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Wakabayashi}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Kawaji}},\ }\href {https://doi.org/10.1143/JPSJ.44.1839} {\bibfield
+  {journal} {\bibinfo  {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo
+  {volume} {44}},\ \bibinfo {pages} {1839} (\bibinfo {year}
+  {1978})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ochiai}\ \emph {et~al.}(1990)\citenamefont {Ochiai},
+  \citenamefont {Mizuno}, \citenamefont {Kawabe}, \citenamefont {Ishibashi},
+  \citenamefont {Aoyagi}, \citenamefont {Gamo},\ and\ \citenamefont
+  {Namba}}]{ochiai190}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Ochiai}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Mizuno}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kawabe}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Ishibashi}}, \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Aoyagi}}, \bibinfo {author} {\bibfnamefont
+  {K.}~\bibnamefont {Gamo}},\ and\ \bibinfo {author} {\bibfnamefont
+  {S.}~\bibnamefont {Namba}},\ }\href {https://doi.org/10.1143/JJAP.29.L739}
+  {\bibfield  {journal} {\bibinfo  {journal} {Jpn. J. Appl. Phys.}\ }\textbf
+  {\bibinfo {volume} {29}},\ \bibinfo {pages} {L739} (\bibinfo {year}
+  {1990})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mancoff}\ \emph {et~al.}(1996)\citenamefont
+  {Mancoff}, \citenamefont {Zielinski}, \citenamefont {Marcus}, \citenamefont
+  {Campman},\ and\ \citenamefont {Gossard}}]{mancoff96}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Mancoff}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Zielinski}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Marcus}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Campman}},\ and\ \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Gossard}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.53.R7599} {\bibfield  {journal} {\bibinfo
+  {journal} {Phy. Rev. B}\ }\textbf {\bibinfo {volume} {53}},\ \bibinfo {pages}
+  {R7599} (\bibinfo {year} {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Arapov}\ \emph {et~al.}(2002)\citenamefont {Arapov},
+  \citenamefont {Alshanskii}, \citenamefont {Harus}, \citenamefont {Neverov},
+  \citenamefont {Shelushinina}, \citenamefont {Yakunin},\ and\ \citenamefont
+  {Kuznetsov}}]{arapov02}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.~G.}\ \bibnamefont
+  {Arapov}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Alshanskii}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Harus}}, \bibinfo
+  {author} {\bibfnamefont {V.}~\bibnamefont {Neverov}}, \bibinfo {author}
+  {\bibfnamefont {N.}~\bibnamefont {Shelushinina}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Yakunin}},\ and\ \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Kuznetsov}},\ }\href
+  {https://doi.org/10.1088/0957-4484/13/1/319} {\bibfield  {journal} {\bibinfo
+  {journal} {Nanotechnology}\ }\textbf {\bibinfo {volume} {13}},\ \bibinfo
+  {pages} {86} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Grbi{\'c}}\ \emph {et~al.}(2004)\citenamefont
+  {Grbi{\'c}}, \citenamefont {Ellenberger}, \citenamefont {Ihn}, \citenamefont
+  {Ensslin}, \citenamefont {Reuter},\ and\ \citenamefont {Wieck}}]{grbic04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Grbi{\'c}}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Ellenberger}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Ihn}},
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Ensslin}}, \bibinfo
+  {author} {\bibfnamefont {D.}~\bibnamefont {Reuter}},\ and\ \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Wieck}},\ }\href
+  {https://doi.org/10.1063/1.1781750} {\bibfield  {journal} {\bibinfo
+  {journal} {App. Phy.Lett.}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo
+  {pages} {2277} (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Caviglia}\ \emph {et~al.}(2010)\citenamefont
+  {Caviglia}, \citenamefont {Gariglio}, \citenamefont {Cancellieri},
+  \citenamefont {Sac{\'e}p{\'e}}, \citenamefont {Fete}, \citenamefont {Reyren},
+  \citenamefont {Gabay}, \citenamefont {Morpurgo},\ and\ \citenamefont
+  {Triscone}}]{caviglia10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Caviglia}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Gariglio}},
+  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Cancellieri}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Sac{\'e}p{\'e}}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Fete}}, \bibinfo {author}
+  {\bibfnamefont {N.}~\bibnamefont {Reyren}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Gabay}}, \bibinfo {author} {\bibfnamefont
+  {A.}~\bibnamefont {Morpurgo}},\ and\ \bibinfo {author} {\bibfnamefont
+  {J.-M.}\ \bibnamefont {Triscone}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.105.236802} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phy. Rev. Lett.}\ }\textbf {\bibinfo {volume} {105}},\
+  \bibinfo {pages} {236802} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fowler}\ \emph {et~al.}(1966)\citenamefont {Fowler},
+  \citenamefont {Fang}, \citenamefont {Howard},\ and\ \citenamefont
+  {Stiles}}]{fowler66}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~B.}\ \bibnamefont
+  {Fowler}}, \bibinfo {author} {\bibfnamefont {F.~F.}\ \bibnamefont {Fang}},
+  \bibinfo {author} {\bibfnamefont {W.~E.}\ \bibnamefont {Howard}},\ and\
+  \bibinfo {author} {\bibfnamefont {P.~J.}\ \bibnamefont {Stiles}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.16.901} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo
+  {pages} {901} (\bibinfo {year} {1966})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Klitzing}\ \emph {et~al.}(1980)\citenamefont
+  {Klitzing}, \citenamefont {Dorda},\ and\ \citenamefont
+  {Pepper}}]{klitzing80}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~V.}\ \bibnamefont
+  {Klitzing}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Dorda}},\
+  and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Pepper}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.45.494} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {45}},\ \bibinfo
+  {pages} {494} (\bibinfo {year} {1980})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ando}\ and\ \citenamefont {Murayama}(1985)}]{ando85}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Ando}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Murayama}},\ }\href {https://doi.org/10.1143/JPSJ.54.1519} {\bibfield
+  {journal} {\bibinfo  {journal} {J. Phys. Soc. Jpn.}\ }\textbf {\bibinfo
+  {volume} {54}},\ \bibinfo {pages} {1519} (\bibinfo {year}
+  {1985})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dial}\ \emph {et~al.}(2007)\citenamefont {Dial},
+  \citenamefont {Ashoori}, \citenamefont {Pfeiffer},\ and\ \citenamefont
+  {West}}]{dial07}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {O.~E.}\ \bibnamefont
+  {Dial}}, \bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont {Ashoori}},
+  \bibinfo {author} {\bibfnamefont {L.~N.}\ \bibnamefont {Pfeiffer}},\ and\
+  \bibinfo {author} {\bibfnamefont {K.~W.}\ \bibnamefont {West}},\ }\href
+  {https://doi.org/10.1038/nature05982} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature}\ }\textbf {\bibinfo {volume} {448}},\ \bibinfo {pages}
+  {176} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ahn}\ \emph {et~al.}(2003)\citenamefont {Ahn},
+  \citenamefont {Triscone},\ and\ \citenamefont {Mannhart}}]{ahn03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~H.}\ \bibnamefont
+  {Ahn}}, \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont {Triscone}},\
+  and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Mannhart}},\ }\href
+  {https://doi.org/10.1038/nature01878} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature}\ }\textbf {\bibinfo {volume} {424}},\ \bibinfo {pages}
+  {1015} (\bibinfo {year} {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Deng}\ \emph {et~al.}(2018)\citenamefont {Deng},
+  \citenamefont {Yu}, \citenamefont {Song}, \citenamefont {Zhang},
+  \citenamefont {Wang}, \citenamefont {Sun}, \citenamefont {Yi}, \citenamefont
+  {Wu}, \citenamefont {Wu}, \citenamefont {Zhu} \emph {et~al.}}]{deng18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Deng}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Yu}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Song}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
+  {N.~Z.}\ \bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont
+  {Z.}~\bibnamefont {Sun}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Yi}}, \bibinfo {author} {\bibfnamefont {Y.~Z.}\ \bibnamefont {Wu}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Wu}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Zhu}}, \emph {et~al.},\ }\href
+  {https://doi.org/10.1038/s41586-018-0626-9} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature}\ }\textbf {\bibinfo {volume} {563}},\ \bibinfo {pages}
+  {94} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yang}\ \emph {et~al.}(2018)\citenamefont {Yang},
+  \citenamefont {Zhang}, \citenamefont {Wang}, \citenamefont {Ye},
+  \citenamefont {Lou}, \citenamefont {Zhou}, \citenamefont {Watanabe},
+  \citenamefont {Taniguchi}, \citenamefont {Chang}, \citenamefont {Chen} \emph
+  {et~al.}}]{yang18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Yang}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Zhang}},
+  \bibinfo {author} {\bibfnamefont {N.~Z.}\ \bibnamefont {Wang}}, \bibinfo
+  {author} {\bibfnamefont {G.~J.}\ \bibnamefont {Ye}}, \bibinfo {author}
+  {\bibfnamefont {W.}~\bibnamefont {Lou}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Watanabe}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Taniguchi}},
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Chang}}, \bibinfo
+  {author} {\bibfnamefont {X.~H.}\ \bibnamefont {Chen}}, \emph {et~al.},\
+  }\href {https://doi.org/10.1021/acs.nanolett.8b03267} {\bibfield  {journal}
+  {\bibinfo  {journal} {Nano Lett.}\ }\textbf {\bibinfo {volume} {18}},\
+  \bibinfo {pages} {6611} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Long}\ \emph {et~al.}(2020)\citenamefont {Long},
+  \citenamefont {Chen}, \citenamefont {Xu},\ and\ \citenamefont
+  {Wang}}]{long20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Long}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Chen}}, \bibinfo
+  {author} {\bibfnamefont {S.}~\bibnamefont {Xu}},\ and\ \bibinfo {author}
+  {\bibfnamefont {N.}~\bibnamefont {Wang}},\ }in\ \href
+  {https://doi.org/10.5772/intechopen.89149} {\emph {\bibinfo {booktitle}
+  {Hybrid Nanomaterials-Flexible Electronics Materials}}}\ (\bibinfo
+  {publisher} {IntechOpen},\ \bibinfo {year} {2020})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Li}\ \emph {et~al.}(2014)\citenamefont {Li},
+  \citenamefont {Yu}, \citenamefont {Ye}, \citenamefont {Ge}, \citenamefont
+  {Ou}, \citenamefont {Wu}, \citenamefont {Feng}, \citenamefont {Chen},\ and\
+  \citenamefont {Zhang}}]{li14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Li}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Yu}}, \bibinfo
+  {author} {\bibfnamefont {G.~J.}\ \bibnamefont {Ye}}, \bibinfo {author}
+  {\bibfnamefont {Q.}~\bibnamefont {Ge}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Ou}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Wu}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Feng}}, \bibinfo
+  {author} {\bibfnamefont {X.~H.}\ \bibnamefont {Chen}},\ and\ \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Zhang}},\ }\href
+  {https://doi.org/10.1038/nnano.2014.35} {\bibfield  {journal} {\bibinfo
+  {journal} {Nat. Nanotechnol.}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo
+  {pages} {372} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hirakawa}\ \emph {et~al.}(2001)\citenamefont
+  {Hirakawa}, \citenamefont {Yamanaka}, \citenamefont {Kawaguchi},
+  \citenamefont {Endo}, \citenamefont {Saeki},\ and\ \citenamefont
+  {Komiyama}}]{hirakawa01}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Hirakawa}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Yamanaka}},
+  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Kawaguchi}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Endo}}, \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Saeki}},\ and\ \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Komiyama}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.63.085320} {\bibfield  {journal} {\bibinfo
+  {journal} {Phy. Rev. B}\ }\textbf {\bibinfo {volume} {63}},\ \bibinfo {pages}
+  {085320} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Griffiths}\ and\ \citenamefont
@@
   {853} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Akkermans}\ and\ \citenamefont
-  {Montambaux}(2010)}]{akkermans10}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Akkermans}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Montambaux}},\ }\href@noop {} {\emph {\bibinfo {title} {Mesoscopic Physics
-  of Electrons and Photons}}}\ (\bibinfo  {publisher} {Cambridge University
-  Press},\ \bibinfo {year} {2010})\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Arfken}(1985)}]{arfken85}%
@@
   York},\ \bibinfo {year} {1959})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Boyd}(2018)}]{boyd18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
+  {Boyd}},\ }\href@noop {} {\emph {\bibinfo {title} {Dynamics of the equatorial
+  ocean}}}\ (\bibinfo  {publisher} {Springer},\ \bibinfo {year}
+  {2018})\BibitemShut {NoStop}%
 \end{thebibliography}%

### 2021-11-20 paper/submission2/manuscript/dressed_quantum_hall_sub2.tex
Finilize paper

--- 2021-11-19 paper/dressed_quantum_hall_sub2/dressed_quantum_hall_sub2.tex
@@
 \begin{acknowledgments}
-K.H wish to acknowledge the members of A$\chi$L at Monash University for their encouragement and support and specially T.N.
-Perera and R.T.Wijesekara for insightful discussions.
+K.H wish to acknowledge the members of A$\chi$L at Monash University for their encouragement and support and specially T.
+Perera and R.
+Wijesekara for insightful discussions.
 The work of K.H is supported by the Australian Government Research Training Program (RTP) Scholarship and the Monash University Institute of Graduate Research.
@@
   {journal} {Phy. Rev. B}\ }\textbf {\bibinfo {volume} {64}},\ \bibinfo {pages}
-  {201311} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+  {201311(R)} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Mani}\ \emph {et~al.}(2002)\citenamefont {Mani},
@@
   {Mani}}, \bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont {Smet}},
-  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Von~Klitzing}}, \bibinfo
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {von~Klitzing}}, \bibinfo
   {author} {\bibfnamefont {V.}~\bibnamefont {Narayanamurti}}, \bibinfo {author}
-  {\bibfnamefont {W.}~\bibnamefont {Johnson}},\ and\ \bibinfo {author}
+  {\bibfnamefont {W.~B.}~\bibnamefont {Johnson}},\ and\ \bibinfo {author}
   {\bibfnamefont {V.}~\bibnamefont {Umansky}},\ }\href
@@
   \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Mancoff}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Zielinski}},
-  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Marcus}}, \bibinfo
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.~B.}~\bibnamefont
+  {Mancoff}}, \bibinfo {author} {\bibfnamefont {L.~J.}~\bibnamefont {Zielinski}},
+  \bibinfo {author} {\bibfnamefont {C.~M.}~\bibnamefont {Marcus}}, \bibinfo
   {author} {\bibfnamefont {K.}~\bibnamefont {Campman}},\ and\ \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Gossard}},\ }\href
+  {\bibfnamefont {A.~C.}~\bibnamefont {Gossard}},\ }\href
   {https://doi.org/10.1103/PhysRevB.53.R7599} {\bibfield  {journal} {\bibinfo
@@
   \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~D.}~\bibnamefont
   {Caviglia}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Gariglio}},
@@
   {M.}~\bibnamefont {Gabay}}, \bibinfo {author} {\bibfnamefont
-  {A.}~\bibnamefont {Morpurgo}},\ and\ \bibinfo {author} {\bibfnamefont
+  {A.~F.}~\bibnamefont {Morpurgo}},\ and\ \bibinfo {author} {\bibfnamefont
   {J.-M.}\ \bibnamefont {Triscone}},\ }\href
@@
   {Hirakawa}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Yamanaka}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Kawaguchi}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Endo}}, \bibinfo {author}
+  , \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Endo}}, \bibinfo {author}
   {\bibfnamefont {M.}~\bibnamefont {Saeki}},\ and\ \bibinfo {author}

### 2022-01-12 response2/response2.tex
Add response2 directory

% ****** Start of file response2.tex ****** %
\documentclass{article}

%===============================================================================
% Import packages
%===============================================================================

\usepackage[top=0.8in,bottom=1in,left=1in,right=1in]{geometry}
% Physics package
\usepackage{physics}
% Paragraph skip package
\usepackage[parfill]{parskip}
% AMS packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
% Color package
\usepackage[dvipsnames]{xcolor}
% Acronym package
\usepackage[acronym]{glossaries}
% SI units package
\usepackage{siunitx}
% Hypertext package
\usepackage[hidelinks]{hyperref}
% Bold math
\usepackage{bm}
% Other packages
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float}
\usepackage{cite}
\usepackage{multicol}
\usepackage{multirow}
% \usepackage{kpfonts}

% Bibliography style
\usepackage[numbers,sort&compress]{natbib}
\bibliographystyle{apsrev4-1}

\begin{document}

% Define acronyms
\newacronym{tls}{TLS}{two-level system}

%===============================================================================
% Add date
%===============================================================================
\today\\

Ashot Melikyan,\\
Associate Editor,\\
Physical Review B.\\

Dear Professor Melikyan,

Thank you very much for your effort in managing the review process of our manuscript. We are also thankful for the reviewer comments, and believe the second version of the manuscript we submit herewith has been significantly improved by the constructive criticism we received. Additionally, the subsequent sections of this document discuss the reviewer comments and our responses to them.

Please note that in the following sections, the statements in {\color{RoyalBlue} \textbf{blue}} are the comments of the reviewers. Our responses are shown in black letters, and the modifications we have done to the manuscript are given in {\color{Red} red}.

\subsection*{General changes to the manuscript}

We have made some minor changes in language and presentation to improve the clarity and organization of the manuscript.
\begin{itemize}
    \item Section I - seventh paragraph (page 2): \\
        {\color{Red} In Sec. VII, we discuss the physical significance of our theoretical results and their possible use in future nanoelectronic devices.
        Finally, we summarize our findings and present our conclusions in Sec. VIII.}
    \item Section VI - fourth paragraph (page 8): \\
        {\color{Red} Considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.}
    \item Section VIII - first paragraph (page 10): \\
        {\color{Red} Finally, we derived analytical expressions for the diagonal components of the electric conductivity tensor concerning the 2DEG quantum Hall system operates at low temperatures.}
\end{itemize}

\subsection*{Response to the comments of Reviewer 1}

We would like to thank the reviewer for bringing the deficiencies of our manuscript to our attention and providing constructive feedback to improve the quality of our work. We have considered all of your suggestions seriously and revised our manuscript as described below.

\subsubsection*{Comment 1 -
\color{RoyalBlue} My concern is that the manuscript is heavily skewed towards a purely mathematical formulation of the problem. It has a minimal connection to realistic two-dimensional electron systems. The manuscript does not discuss how the results can be applied to understanding mechanisms of charge transport in nanoelectronic devices and can be used to optimize device performance. Without such discussion, the manuscript will have a minimal impact on the community working on developing nanoelectronics.}

We agree that our work has a theoretical bias, and the reader may benefit from some application perspective from our theoretical results to characterize or design nanoelectronic devices. Therefore, we have discussed the physical significance of our theoretical results and their possible use in optimizing nanoelectronic device performance. First, we added a detailed comparison between our theoretical results and experiment observations when no radiation is present.  We also added a new section (Section VII) on this very aspect.

\begin{itemize}
  \item Section VI - third paragraph (page 8):\\
  {\color{Red}
  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig. 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
  Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
  The gate voltage modifies the Fermi level of the system.
  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
  Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
  By comparing these observations against our results in Fig. 4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
  Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig. 4, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
  In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
  }
  \item Section VII (page 9):\\
  {\color{Red}
  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}

  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect. The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems. The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}. This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically. The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}. The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.

  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}. Strikingly, we show in Fig. 5 that we can manipulate the broadening of these conductivity peaks using an external dressing field. At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering. Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.

  Research on novel states of matter has driven the evolution of present-day nanoelectronic devices. In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
  The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
  As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
  We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}. Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures. Since the Fermi level of a system can be altered with the applied gate voltage, our Fig. 4 depicts this result.
  In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field. Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.

  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications. In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage. As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field. This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
  Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
  magneto-transport properties of 2D nanostructures.
  }
\end{itemize}

\subsubsection*{Comment 2 -
\color{RoyalBlue} Moreover, this current research direction has a significant overlap with previous experimental and theoretical studies of quantum Hall systems that started with the observation of zero-resistance states in high mobility systems [Zudov et al, Phys. Rev. B 64, 201311 (2001), Mani et al, Phys. Rev. Lett. 92, 146801 (2004)] and gave rise to theoretical models for the phenomenon [Durst et al, Phys. Rev. Lett. 91, 086803 (2003), Dmitriev et al., Phys. Rev. B 71, 115316 (2005), Dmitriev et al, Phys. Rev. B 80, 165327 (2009)]. The present manuscript needs to connect to various known phenomena discussed earlier in the literature on quantum Hall systems.}

We agree with the reviewer that it is useful to have a discussion comparing  our theoretical model and previous work on the transport properties of quantum Hall systems.
Among the mentioned studies we can identify that experimental work reported in Refs. \cite{zudov01,mani02,zudov03,mani04} are specifically aimed at the unusual oscillations of the magnetoresistance induced by the microwave (millimeter-wave) radiation in 2DEG quantum Hall systems.
These oscillations are known as \textit{microwave-induced resistance oscillations} (MIROs).
To describe these behaviors Durst \textit{et al.} \cite{durst03} introduced a simple theoretical model assuming that the experimentally observed oscillations are a consequence of photoexcited disorder-scattered electrons.
However, later Refs. \cite{dmitriev03,dmitriev05,dmitriev09} proposed a novel model considering the changes were made on
the electron distribution function by the microwave field.
These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have successfully described the behavior of MIROs at experimentally relevant temperatures that were missed in the previous model \cite{durst03}.
Furthermore, we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorption by an electron in the associated system. In our theoretical model, we take into account higher frequencies than microwaves as the dressing electromagnetic field.
Therefore we can identify and quantify significant dissimilarities between our system and MIRO systems \cite{zudov01,mani02,zudov03,mani04,durst03,dmitriev03,dmitriev05,dmitriev09}. They are:
\begin{itemize}
  \item
  the experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$). This leads to building the theoretical models presented in Refs. \cite{durst03,dmitriev03} by assuming that these oscillations are caused by photoexcited electrons. Since these models consider on a relevant frequency range (microwave radiation), it will allow us to acknowledge the photon absorption by electrons. In contrast to that, our consideration is only focused on the systems with high-frequency range dressing fields which will not be associated with any photon absorption.
  \item
  the applied microwave radiation power on the MIRO experiments \cite{mani02,zudov03} varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range. However, in our analysis, we take the dressing field as a high-intensity electromagnetic field, where we cannot consider the dressing field as a perturbation in our analysis. This leads us to recognize the formation of Floquet states together with conventional Landau levels. As we mentioned in our results, we used dressing high-intensity electromagnetic fields of magnitude around the $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.
  \item
  these fascinating MIROs are only observed under the influence of weak magnetic fields ($B < \SI{0.2}{\tesla}$) in experiments performed in Refs. \cite{zudov01,mani02,zudov03,mani04}. In this range of weak magnetic fields,  we can only observe MIROs as Shubnikov–de Haas (SdH) oscillations reveal only with high-intensity magnetic fields. In comparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics. Therefore in our analysis, we aim at the effects induced by higher intensity magnetic fields ($B \sim \SI{1}{\tesla}$) than the MIRO experiments.
  \item
  in our work, we analyzed the 2DEG quantum Hall system with a dressing high-intensity electromagnetic field which does not contribute to energy exchange between the high-frequency dressing field and electrons. Therefore we have assumed the applied electromagnetic radiation as a pure dressing field. There are two possible absorption mechanisms in a 2DEG quantum Hall system; namely electron transitions between distinct Landau levels and electron transitions between distinct states of the same broadened Landau level. To avoid these absorptions, we have tuned the dressing field into a high-frequency range in our system under the analysis. Furthermore, due to the dressing high-intensity electromagnetic field, the entire electronic states of the conventional 2DEG quantum Hall system will be restructured. We have addressed these modifications through the Floquet theory. However, the MIRO models \cite{durst03,dmitriev03} are based on low-frequency cases where the system can absorb low-frequency photons from the field.
\end{itemize}

Based on the above discussion, we can identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two distinguishable
magneto-transport scenarios.

\begin{itemize}
  \item Section I - fifth paragraph (page 1):\\
  {\color{Red}
  Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
  This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
  The influence induced by a pure dressing field on
  magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
  Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
  }
  \item Section VI - sixth paragraph (page 9):\\
  {\color{Red}
  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
  magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems. However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
  It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field. In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions. This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems. Therefore, our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
  }
\end{itemize}

\subsubsection*{Comment 3 -
\color{RoyalBlue} The manuscript will also provide more impact if it demonstrates how the new results can help to improve the future development of nanoelectronic devices. After these questions are addressed, the manuscript will be suitable for publication in Physical Review B. Otherwise, it will fit better to a more mathematically oriented journal.
}

This is a valid comment. As we mentioned in comment 1, considering the importance of discussing the physical significance of our results, we included a new section (Section VII) to address this comment.

\begin{itemize}
  \item Section VII (page 8):\\
  {\color{Red}
  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}

  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect. The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems. The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}. This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically. The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}. The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.

  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}. Strikingly, we show in Fig. 5 that we can manipulate the broadening of these conductivity peaks using an external dressing field. At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering. Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.

  Research on novel states of matter has driven the evolution of present-day nanoelectronic devices. In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
  The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
  As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
  We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}. Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures. Since the Fermi level of a system can be altered with the applied gate voltage, our Fig. 4 depicts this result.
  In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field. Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.

  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications. In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage. As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field. This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
  Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
  magneto-transport properties of 2D nanostructures.
  }
\end{itemize}

\subsubsection*{Comment 4 -
\color{RoyalBlue} The quantum Quantum Hall effect requires high mobility samples. In these samples, the structure of the disorder is usually complicated and combines both short-length potentials of impurities and long-length electrostatic inhomogeneities. The interplay of these components of disorder opens exciting questions about the transport properties of 2DEGs. What is the structure of disorder considered in the present manuscript and hidden in the notations for Vimp? What are the conditions for validity of eq. (15)?
}

We thank the reviewer for raising this important question. In our previous manuscript, we have presented the detailed derivation of Eq.~[15] with a discussion on models of disorder under Appendix C. However, here we again elucidate our disorder model and approximations made to derive the Eq.~[15] for clarity and to respond to this question.

We modeled the effect caused by impurities in the considered system as a single perturbation potential. Analyzing the electric properties for a specific impurity distribution is a rather formidable task. We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment. Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
We start our analysis by considering a static disorder that corresponds only to elastic electron scattering processes.
We adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the associated system and we approximate this into a Gaussian white noise.

Since we are presenting the perturbation potential $V(\vb{r})$ by a group of randomly localized impurities, we assume $N_{imp}$ number of identical single impurity potentials distributed randomly but in fixed positions $\vb{r}_i$. Thus, we can describe the perturbation potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$,
\begin{equation} \label{eq:1}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \upsilon (\vb{r}-\vb{r}_i).
\end{equation}
Furthermore, we approximate this perturbation potential as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average. This model is characterized by the following two equations \cite{akkermans10}
\begin{subequations}
\begin{equation} \label{eq:2}
  \expval{\upsilon(\vb{r})}_{imp} =0,
\end{equation}
\begin{equation} \label{eq:3}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
\end{equation}
\end{subequations}
where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function that solely depends only on $\vb{r}-\vb{r'}$, and decays with a characteristic length $r_c$. Since this study considers the case where the wavelength of radiation or a scattering electron is much greater than $r_c$, it is reasonable to approximate its two-point correlation function by
\begin{equation} \label{eq:4}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
\end{equation}
where $\Upsilon_{imp}^2$ is a positive constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately write the total scattering potential as
\begin{equation} \label{eq:5}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
\end{equation}

Using this expression, we can evaluate the Floquet-Fermi golden rule for a dressed quantum Hall system. Furthermore, considering the properties of a Gaussian white noise impurity distribution \cite{wackerl20,akkermans10}, we assume $V_{imp}$ is a constant in the momentum space.
Here $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
All the detailed steps for the derivation of the Floquet-Fermi golden rule for a dressed quantum Hall system are included in Appendix C.
However, throughout the derivation, we use only the first-order contribution (Born approximation) of the impurity potential.

Since previous studies on Floquet-Drude conductivity \cite{wackerl20}, and magneto-transport properties in undressed \cite{endo09} and dressed \cite{dini16} quantum Hall systems have used this particular Gaussian white noise potential, we also selected this particular impurity model to describe our system. Such a choice enables us to compare our analytical results with these previous models. As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the
magneto-transport properties of dressed quantum Hall system would be an intriguing future research possibility.

Since we have only mentioned the validity conditions we used to derive the Eq.~[15] in Appendix C and not in the main text of the previous manuscript, we have added these validity conditions to the main text of the revised manuscript.

\begin{itemize}
  \item Section IV - first paragraph (page 4):\\
  {\color{Red}
  We have modeled the effect caused by impurities as a single short-range perturbation potential. Analyzing the electric properties for a specific impurity distribution is a rather formidable task. We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
  Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
  Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
  Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20}.
  Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
  Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder. In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
  }
\end{itemize}

\subsubsection*{Comment 5 -
\color{RoyalBlue} If continuous illumination is applied to an electron system, the system will heat indefinitely. The distribution function is stabilized when the electron-electron and electron-phonon scattering mechanisms are included. What are the conditions of validity for eqs. (33-34)? The deviations of the distribution function from its equilibrium result in effects that can significantly overcome the equilibrium contributions, see Dmitriev et al, Phys. Rev. B 80, 165327 (2009). However, to capture these effects, a treatment within Floquet-Drude formalism is insufficient and a complete quantum kinetic equation has to be analyzed. Can the authors argue why their results still present some interest to the community even if they potentially disregard more significant contributions?
}

This is a good, valid question. First, we discuss the validity of the Eq.~[33] and Eq.~[34]. Our analysis derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
In contrast to the MIRO analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, where the photon absorption does not happen. Therefore, we can select the Fermi-Dirac distribution as our particle distribution function for Eq.~[31]
\begin{equation} \tag{5}
  f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1}.
\end{equation}
Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
Then we consider a special scenario where the system operates at a low-temperature limit, i.e., the condition $k_BT \ll \varepsilon_F$.
Since previous theoretical studies \cite{wackerl20,dini16,endo09} on magneto-transport properties of 2DEG quantum Hall systems were derived under this assumption, we also adopted the same conditions as it enables us to compare results with those studies.
In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing temperature, we can identify the decaying behavior of SdH oscillations.
Therefore, if we need to maintain a good oscillatory behavior, we need to operate in low temperatures.
Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, it is reasonable to simplify our general derivation given in  Eq.~[31] for low-temperature limit. Under these assumptions, the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy, and  can be represented by the delta function \cite{endo09}
\begin{equation} \tag{6}
  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
\end{equation}
Applying these adequate conditions, we can simplify our derivation into a single expression that can be compared with previous studies \cite{wackerl20,dini16,endo09} on
magneto-transport in dressed quantum Hall systems. We have added clarification on the above assumptions in the revised manuscript.
\begin{itemize}
  \item Section V - second paragraph (page 7):\\
  {\color{Red}
  We consider a dressed quantum Hall system under off-resonant condition, where photon absorption does not happen. Therefore, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
  \begin{equation} \tag{33}
    f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
  \end{equation}
  where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system. At low-temperatures, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
  \begin{equation} \tag{34}
    - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
  \end{equation}
  }
\end{itemize}

Yes, indeed, experiments on quantum hall systems subject to a strong dressing field show elevated temperatures. However, as demonstrated in previous studies by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, it is possible to maintain low system temperature by limiting the dressing field to narrow pulses.

Although we have restricted our general derivation given in Eq.~[31] into a particular instance for comparison, there is no fundemental restriction in extending our theoretical model into different types of particle distribution functions. As presented in the previous work of Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion needs to address the changes in distribution functions in our derived general longitudinal conductivity formula, and this would be a noteworthy extension to our study.

\subsubsection*{Comment 6 -
\color{RoyalBlue} The authors presented the results for the conductivity tensor's xx- and yy-components. They seem to be identical, apart of a dimensional factor $(eB)^2$ in the denominator. The equality of these two components is expected for isotropic systems. Does the polarization of the electromagnetic field break the isotropy? Do the two components of the conductivity remain equal even for an arbitrary direction of a linearly polarized field? Is there a non-Hall contribution to the xy-component?
}

We express our gratitude towards the reviewer for pointing out this inadvertent oversight done in the $yy$-component of the current operator calculation. This has led to an unexpected normalization factor in the yy-component of the  conductivity expression. Since we have only used the normalized $xx$-component of the conductivity tensor for subsequent analysis, this oversight has no impact on the analysis reported in the  manuscript. With this correction, we observe that both xx-component and $yy$-component show the same conductivity behaviors. We added these amendments to the current operator calculations done in Appendix D and the longitudinal conductivity calculation under Section V.

\begin{itemize}
  \item Appendix D (page 16):\\
  {\color{Red}
  \subsection*{\label{appendix_d}Appendix D: Current operators for a dressed quantum Hall system}

  In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system. We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(1) and we identified them as the Floquet states in Eq.~(14). For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(10) as quantum states using their corresponding quantum numbers as follows
  \begin{equation} \tag{D1}
    \ket{\phi_{n,m}} = \ket{n,k_x}.
  \end{equation}
  Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
  \begin{equation} \tag{D2}
    \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
  \end{equation}
  Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
  \begin{equation} \tag{D3}
    \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
  \end{equation}
  where $\widetilde{m}$ is the mass of the associated particle.

  First, we consider the $x$-directional particle current operator component, and we can identify that as
  \begin{equation} \tag{D4}
    \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
  \end{equation}
  Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
  \begin{equation} \tag{D5}
    \left({j}_x \right)_{nm,n'm'} =
    \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
  \end{equation}
  and we evaluate these using the Floquet modes derived in Eq.~(7) as follows
  \begin{equation} \tag{D6}
    \begin{aligned}
      \left({j}_x \right)_{nm,n'm'} = &
      \frac{1}{{\widetilde{m}}}
      \delta_{k_x,k'_x}
      \int
      \left(\hbar k'_x + eBy\right) \\
      & \times
       \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
      \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
      dy.
    \end{aligned}
  \end{equation}
  Let $[y - y_0 - \zeta(t)] = \bar{y}$, and we can obtain
  \begin{equation} \tag{D7}
    \begin{aligned}
      \left({j}_x \right)_{nm,n'm'} =
      \frac{1}{{\widetilde{m}}}
      \delta_{k_x,k'_x}
      \int &
      \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right]
      \chi_{n}(\bar{y})
      \chi_{n'}(\bar{y})
      d\bar{y}.
    \end{aligned}
  \end{equation}
  Using the following integral identities of the Floquet modes that are made of Gauss-Hermite functions \cite{vedenyapin11,szego59}
  \begin{equation} \tag{D8}
    \int
    \chi_{n}({y})
    \chi_{n'}({y}) d{y} =
    \delta_{n',n},
  \end{equation}
  \begin{equation} \tag{D9}
    \int
    y \chi_{n}({y})\chi_{n'}({y}) d{y} =
    \frac{1}{\kappa}
    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1} \right),
  \end{equation}
  we simplify the matrix elements of $x$-directional current operator to obtain
  \begin{equation} \tag{D10}
    \begin{aligned}
      &\left({j}_x \right)_{nm,n'm'} =
      \frac{eB}{{\widetilde{m}\kappa}}
      \delta_{k_x,k'_x}
      \left[
      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1}\right)
      + \zeta(t) \delta_{n',n}
      \right].
    \end{aligned}
  \end{equation}
  Due to high complexity of extract solution, in this study we only consider the constant contribution from the Fourier series components of the above expression. Therefore, we can identify the $0$-th component of the Fourier series as
  \begin{equation} \tag{D11}
    \begin{aligned}
        \left({j}_x \right)_{nm,n'm'} =&
        \frac{eB}{\widetilde{m}\kappa}
        \delta_{k_x,k'_x}
        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
        \delta_{n',n-1} \right).
    \end{aligned}
  \end{equation}
  To calculate the electric current operator, we substitute the electron's charge and effective mass to the above derived equation. This leads to
  \begin{equation} \tag{D12}
    \begin{aligned}
        \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
        \frac{e\hbar}{{m_e}l_0}
        \delta_{k_x,k'_x}
        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
        \delta_{n',n-1} \right).
    \end{aligned}
  \end{equation}
  where $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$ is the magnetic length.

  Moreover, we can identify the $y$-directional current operator component as
  \begin{equation} \tag{D13}
    \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
  \end{equation}
  Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
  \begin{equation} \tag{D14}
    \left({j}_y \right)_{nm,n'm'} =
    \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
  \end{equation}
  After following the same steps done for the $x$-directional current operator, and recursion relation of the first derivative of Gauss-Hermite functions
  \begin{equation} \tag{D15}
    \begin{aligned}
      \pdv{\chi_{n}({y})}{y} =
      \kappa\left[
      -  \sqrt{\frac{n+1}{2}} \chi_{n+1}({y})
      +  \sqrt{\frac{n}{2}} \chi_{n - 1}({y})
      \right],
    \end{aligned}
  \end{equation}
  we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
  \begin{equation} \tag{D16}
    \begin{aligned}
      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
      \frac{ie\hbar\kappa}{m_e}
      \delta_{k_x,k'_x}
      \left(
      \sqrt{\frac{n}{2}} \delta_{n',n-1}
      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
      \right).
    \end{aligned}
  \end{equation}
  \begin{equation} \tag{D17}
    \begin{aligned}
      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
      \frac{ie \hbar}{m_e l_0}
      \delta_{k_x,k'_x}
      \left(
      \sqrt{\frac{n}{2}} \delta_{n',n-1}
      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
      \right).
    \end{aligned}
  \end{equation}
  }
  \item Section V - second paragraph (page 7):\\
  {\color{Red}
  Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(31) leads to
  \begin{equation} \tag{35}
    \begin{aligned}
      \sigma^{xx}  =
      \frac{e^2l_0^2}{\pi\hbar A}
      \sum_{n}
      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
        }
      \right]
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
        }
      \right],
    \end{aligned}
  \end{equation}
  where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$,
  $\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$, and $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$.
  Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
  \begin{equation} \tag{36}
    \begin{aligned}
      {\sigma}^{yy} =
      \frac{e^2l_0^2}{\pi\hbar A}
      \sum_{n}
      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
        }
      \right]
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
        }
      \right].
    \end{aligned}
  \end{equation}
  }
\end{itemize}

Suppose we apply an arbitrary directional polarized dressing field. In that case, we could derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis. This would change the amplitude of the associated dressing field ($E$) in each direction. There will be a new component in parallel to the conductivity component of interest, which will modify the time-dependent Hamiltonian given in Eq.~[2]. Then, we need to solve the Schrödinger equation with the modified Hamiltonian to find the new Floquet modes for the new system. These will define the effect on the inverse scattering time matrix components. As mentioned in Ref. \cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the considered system and creates novel states called Floquet states. The properties of these states depend on the characteristics of the applied dressing field. Therefore, the polarization method also changes the behavior of the Floquet states. These polarization-dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields. However, in a dressed quantum Hall system with a $y$-directional linear polarized field, we predict the same longitudinal conductivity behaviors in diagonal components of the conductivity tensor.

For analyzing our system, we mainly employ the diagonal components of the Floquet-Drude conductivity tensor introduced by Wackerl \textit{et al.} \cite{wackerl20}. As we mainly focus on SdH oscillations in longitudinal conductivity components, we limit our analysis to the dressing field influence on two diagonal components of the conductivity tensor. Therefore we are unable to predict the off-diagonal component behavior of the system.
%
% As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the consideirng system and creates novel states called Floquet states. The properties of these states are depends on the characteristics of applied dressing field. Therefore, the polarization method also change the behavior of the Floquet states.
% These polarization dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields. In addition, they have mentioned the impact on the direction of the linearly polarization dressing field and this will break the isotropy behavior of the longitudinal conductivities in the consideirng system.
%
% We also followed the same formalism of Floquet states for 2DEG quantum Hall systems. In our work also we were able to identify that the applied dressing field's polarization direction can be effect the magnitude of the longitudinal conductivity component. A detailed derivation of these two longitudinal conductivity component's current operators are given in Appendix D. If we applied a arbitary directional polarized dressing field, we can derive a expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with same steps in this analysis. This would change the amplitude of the considering dressing field ($E$) in each direction. However, now there will be a new conponent in parallel to the considering conductivity component and we need to solve the Schrödinger equation with the modified Hamiltonian in Eq.~[2] for the new system with these changes.
% However in our analysis, our main objective was to identify the manipulation capabilities of SdH oscillations using dressing field intensity. In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diagonal components in conductivity tensor. Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quantum Hall systems.

\subsection*{Response to the comments of Reviewer 2}

We want to thank the reviewer for his/her insightful comments on our work. To address your comments, we had to add new materials and reorganize our text. As a result, we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis. We hope our response and the corresponding changes we incorporated into the manuscript will be sufficient to clarify the issues raised.

\subsubsection*{Comment 1 -
\color{RoyalBlue} The paper is very low on comparison with experiments, for which there is a large amount of data available for the zero radiation case. I would like to see detailed analysis of how Figs 4 and 5 compare with available
experimental data. Without this addition, physical relevance of such
detailed calculations is questionable.
}

We thank the reviewer for pointing out the importance of this fact. In the revised manuscript, we have included a detailed analysis of our results against the undressed 2DEG quantum Hall system behavior.

\begin{itemize}
  \item Section VI - third paragraph (page 8):\\
  {\color{Red}
  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig. 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
  Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
  The gate voltage modifies the Fermi level of the system.
  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
  Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
  By comparing these observations against our results in Fig. 4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
  Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig. 4, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
  In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
  }
\end{itemize}

\subsubsection*{Comment 2 -
\color{RoyalBlue} In the presence of disorder, Anderson localization and topologically protected edge modes are dominant considerations when calculating DC transport coefficients. How are these factors taken into account?
}

We omitted a discussion on the Anderson localization and topologically protected edge modes as we neglected them in our work.
While deriving Eq.~[31], we have assumed that the applied static magnetic field is placed in a lower intensity range where we can neglect several effects known to appear in a 2DEG quantum Hall system. Under this condition, we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions, and the spin splitting as well. As mentioned in the work of Endo \textit{et al.} \cite{endo09}, within the magnetic field range of interest, the undressed
magneto-transport properties of GaAs/AlGaAs 2DEG quantum Hall system provide an excellent agreement between the experimental observations and theory that was developed by neglecting the above-mentioned effects. Our work is very similar to theirs with an additional dressing field. Our results for the undressed system agree with the results in Ref. \cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks. We have added this clarification in the manuscript.

\begin{itemize}
  \item Section I - sixth paragraph (page 2):\\
  {\color{Red}
  It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, and the electron-electron interactions. These are not overly restrictive assumptions, and other have successfully used same assumptions in their work, e.g see Endo \textit{et al.} \cite{endo09}.
  }
  \item Section VIII - first paragraph (page 10):\\
  {\color{Red}
  We modeled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.
  }
\end{itemize}

\subsubsection*{Comment 3 -
\color{RoyalBlue} Can the authors reproduce the quantized Hall conductance of filled Landau levels in the presence of disorder? Please discuss.
}

For analyzing our system, we mainly employ the diagonal components of the Floquet-Drude conductivity tensor introduced by Wackerl \textit{et al.} \cite{wackerl20}. As we mainly focus on SdH oscillations in longitudinal conductivity components, we limit our analysis to the dressing field influence on two diagonal components of the conductivity tensor.
Therefore we cannot predict the off-diagonal component behavior of the system. However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diagonal components of the conductivity tensor. As mentioned in Ref. \cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly agree with  experiment observations
\begin{equation} \tag{1}
  \dv{\widetilde{\sigma}^{xy}(X_F,I)}{B} \approx
    \pi\mu \frac{\hbar \omega_0}{\varepsilon_F} [\widetilde{\sigma}^{xx}(X_F,I)]^2.
\end{equation}
By examining the connection between longitudinal and transverse conductivities in the 2DEG quantum Hall system, we can expect the same Hall conductivity behavior in a dressed quantum Hall system. However, using the dressing field, we can squeeze the conductivity peaks on Landau levels, i.e., squeeze the region of longitudinal conductivity peaks placed near the Landau levels. This  implies sudden Hall conductivity transitions between one plateau to another near a Landau level. As in Refs.  \cite{klitzing80,gusynin06}, we can also predict a staircase behavior of quantum Hall conductivity against the gate voltage. With an external dressing field, we will be able to get rapid transitions than the undressed system. However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulated from the beginning. It will be the subject of our future study.

\subsubsection*{Comment 4 -
\color{RoyalBlue} The way some previous works are cited is disappointing. Example from page 8: “Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.” This is not informative. Where, specifically, did results from earlier works fall short of reality, which have been better addressed in this work?
}

We made the following changes in language and presentation to improve the clarity of our manuscript.

\begin{itemize}
  \item Section VIII (page 8):\\
  {\color{Red}
  Despite this behavior being identified in the previous work of Dini \textit{et al.}  \cite{dini16}, they cannot fully account for the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref. \cite{endo09}. The authors of Ref. \cite{dini16} have used the conventional expression of longitudinal conductivity from Refs. \cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening for the Landau levels. These predictions significantly deviate from the experimentally observed Landau level broadening \cite{endo09}.
  However, our generalized analysis on the conductivity of dressed quantum Hall systems provides a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
  }
  \item Section III - first paragraph (page 3):\\
  {\color{Red}
  In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.
  }
  \item Section I - fifth paragraph (page 2):\\
  {\color{Red}
  The authors of Ref. \cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
  }
  \item Section IV - third paragraph (page 5):\\
  {\color{Red}
  In the study presented in Ref. \cite{endo09}, the authors have assumed that the effective mass of an electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
  }
\end{itemize}

\subsubsection*{Comment 5 -
\color{RoyalBlue} Adding some physical insight into the remarkable observation of radiation-induced narrowing of lineshapes (Figs 4, 5) will help elevate
this work.
}

We agree with the reviewer that a discussion on our theoretical results and their physical significance in modern nanoelectronic devices is a vital requirement. We have added a new Section VII to overcome the above-mentioned deficiency of our manuscript. The total content of the section is given below,

\begin{itemize}
  \item Section VII (page 8):\\
  {\color{Red}
  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}

  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect. The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems. The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}. This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically. The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}. The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.

  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}. Strikingly, we show in Fig. 5 that we can manipulate the broadening of these conductivity peaks using an external dressing field. At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering. Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.

  Research on novel states of matter has driven the evolution of present-day nanoelectronic devices. In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
  The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
  As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
  We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}. Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures. Since the Fermi level of a system can be altered with the applied gate voltage, our Fig. 4 depicts this result.
  In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field. Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.

  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications. In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage. As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field. This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
  Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
  magneto-transport properties of 2D nanostructures.
  }
\end{itemize}

\bibliography{response2}
\medskip
Sincerely yours,

\def\s#1#2#3{\vbox{\hsize=4.5cm
		\kern2cm
		\hrule\kern1ex
		\hbox to \hsize{\strut\hfil #1 \hfil}
		\hbox to \hsize{\strut\hfil #2 \hfil}
		\hbox to \hsize{\strut\hfil #3 \hfil}}}

\hbox to \hsize{\s{Malin Premaratne}{(Corresponding Author)}{\href{malin.premaratne@monash.edu}{malin.premaratne@monash.edu}}}

\end{document}

% ****** End of file dressed_quantum_hall.tex ****** %

### 2022-01-13 response2/response2.tex
Add reviewer 1 comment

@@
 
-Thank you very much for your effort in managing the review process of our manuscript.
-We are also thankful for the reviewer comments, and believe the second version of the manuscript we submit herewith has been significantly improved by the constructive criticism we received.
-Additionally, the subsequent sections of this document discuss the reviewer comments and our responses to them.
+Thank you very much for your efforts in managing the review process for our manuscript.
+We are grateful for the comments of the reviewers and we believe the manuscript we submit now has been significantly improved by the constructive criticism we received.
+Please find herewith, the reviewer comments and our responses with the changes highlighted.
 
@@
         Finally, we summarize our findings and present our conclusions in Sec. VIII.}
-    \item Section VI - fourth paragraph (page 8): \\
-        {\color{Red} Considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpened the conductivity peaks.}
-    \item Section VIII - first paragraph (page 10): \\
-        {\color{Red} Finally, we derived analytical expressions for the diagonal components of the electric conductivity tensor concerning the 2DEG quantum Hall system operates at low temperatures.}
 \end{itemize}
@@
 
-We would like to thank the reviewer for bringing the deficiencies of our manuscript to our attention and providing constructive feedback to improve the quality of our work.
-We have considered all of your suggestions seriously and revised our manuscript as described below.
+We would like to thank the reviewer for his/her insightful comments on the theoretical foundations of our model.
+Accordingly, we have been able to significantly refine our discussion on the underlying assumptions and corresponding physical conditions of our system.
+We hence believe that our response, and the corresponding changes we incorporated to the manuscript would be sufficient to clarify the issues raised.
 
 \subsubsection*{Comment 1 -
-\color{RoyalBlue} My concern is that the manuscript is heavily skewed towards a purely mathematical formulation of the problem.
-It has a minimal connection to realistic two-dimensional electron systems.
-The manuscript does not discuss how the results can be applied to understanding mechanisms of charge transport in nanoelectronic devices and can be used to optimize device performance.
-Without such discussion, the manuscript will have a minimal impact on the community working on developing nanoelectronics.}
+\color{RoyalBlue} I still find that the justification of approximation in Eq.
+(34) is sketchy and likely misses some essential effects related to the impact of the radiation on the distribution function in microwave fields.}
 
-We agree that our work has a theoretical bias, and the reader may benefit from some application perspective from our theoretical results to characterize or design nanoelectronic devices.
-Therefore, we have discussed the physical significance of our theoretical results and their possible use in optimizing nanoelectronic device performance.
-First, we added a detailed comparison between our theoretical results and experiment observations when no radiation is present.
-We also added a new section (Section VII) on this very aspect.
-
-\begin{itemize}
-  \item Section VI - third paragraph (page 8):\\
-  {\color{Red}
-  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.
-4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
-  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
-  Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
-  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
-  The gate voltage modifies the Fermi level of the system.
-  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
-  Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
-  By comparing these observations against our results in Fig.
-4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
-  Furthermore, when we increase the gate voltage, the Fermi level rises.
-As illustrated in Fig.
-4, this will result in a higher conductivity peak value at the higher-order Landau levels.
-This same behavior was also observed in the experimental observations presented in Ref.
-\cite{wakabayashi78}.
-  In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
-  }
-  \item Section VII (page 9):\\
-  {\color{Red}
-  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}
-
-  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
-The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
-The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
-This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically.
-The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
-  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}.
-The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.
-
-  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
-  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
-  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}.
-Strikingly, we show in Fig.
-5 that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering.
-Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
-
-  Research on novel states of matter has driven the evolution of present-day nanoelectronic devices.
-In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
-  The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
-  As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
-  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
-  We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}.
-Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures.
-Since the Fermi level of a system can be altered with the applied gate voltage, our Fig.
-4 depicts this result.
-  In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field.
-Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.
-
-  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
-In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
-As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field.
-This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
-  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
-  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
-  Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
-  magneto-transport properties of 2D nanostructures.
-  }
-\end{itemize}
-
-\subsubsection*{Comment 2 -
-\color{RoyalBlue} Moreover, this current research direction has a significant overlap with previous experimental and theoretical studies of quantum Hall systems that started with the observation of zero-resistance states in high mobility systems [Zudov et al, Phys.
-Rev.
-B 64, 201311 (2001), Mani et al, Phys.
-Rev.
-Lett.
-92, 146801 (2004)] and gave rise to theoretical models for the phenomenon [Durst et al, Phys.
-Rev.
-Lett.
-91, 086803 (2003), Dmitriev et al., Phys.
-Rev.
-B 71, 115316 (2005), Dmitriev et al, Phys.
-Rev.
-B 80, 165327 (2009)].
-The present manuscript needs to connect to various known phenomena discussed earlier in the literature on quantum Hall systems.}
-
-We agree with the reviewer that it is useful to have a discussion comparing  our theoretical model and previous work on the transport properties of quantum Hall systems.
-Among the mentioned studies we can identify that experimental work reported in Refs.
-\cite{zudov01,mani02,zudov03,mani04} are specifically aimed at the unusual oscillations of the magnetoresistance induced by the microwave (millimeter-wave) radiation in 2DEG quantum Hall systems.
-These oscillations are known as \textit{microwave-induced resistance oscillations} (MIROs).
-To describe these behaviors Durst \textit{et al.} \cite{durst03} introduced a simple theoretical model assuming that the experimentally observed oscillations are a consequence of photoexcited disorder-scattered electrons.
-However, later Refs. \cite{dmitriev03,dmitriev05,dmitriev09} proposed a novel model considering the changes were made on
-the electron distribution function by the microwave field.
-These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have successfully described the behavior of MIROs at experimentally relevant temperatures that were missed in the previous model \cite{durst03}.
-Furthermore, we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorption by an electron in the associated system.
-In our theoretical model, we take into account higher frequencies than microwaves as the dressing electromagnetic field.
-Therefore we can identify and quantify significant dissimilarities between our system and MIRO systems \cite{zudov01,mani02,zudov03,mani04,durst03,dmitriev03,dmitriev05,dmitriev09}. They are:
-\begin{itemize}
-  \item
-  the experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$).
-This leads to building the theoretical models presented in Refs.
-\cite{durst03,dmitriev03} by assuming that these oscillations are caused by photoexcited electrons.
-Since these models consider on a relevant frequency range (microwave radiation), it will allow us to acknowledge the photon absorption by electrons.
-In contrast to that, our consideration is only focused on the systems with high-frequency range dressing fields which will not be associated with any photon absorption.
-  \item
-  the applied microwave radiation power on the MIRO experiments \cite{mani02,zudov03} varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range.
-However, in our analysis, we take the dressing field as a high-intensity electromagnetic field, where we cannot consider the dressing field as a perturbation in our analysis.
-This leads us to recognize the formation of Floquet states together with conventional Landau levels.
-As we mentioned in our results, we used dressing high-intensity electromagnetic fields of magnitude around the $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.
-  \item
-  these fascinating MIROs are only observed under the influence of weak magnetic fields ($B < \SI{0.2}{\tesla}$) in experiments performed in Refs.
-\cite{zudov01,mani02,zudov03,mani04}.
-In this range of weak magnetic fields,  we can only observe MIROs as Shubnikov–de Haas (SdH) oscillations reveal only with high-intensity magnetic fields.
-In comparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics.
-Therefore in our analysis, we aim at the effects induced by higher intensity magnetic fields ($B \sim \SI{1}{\tesla}$) than the MIRO experiments.
-  \item
-  in our work, we analyzed the 2DEG quantum Hall system with a dressing high-intensity electromagnetic field which does not contribute to energy exchange between the high-frequency dressing field and electrons.
-Therefore we have assumed the applied electromagnetic radiation as a pure dressing field.
-There are two possible absorption mechanisms in a 2DEG quantum Hall system; namely electron transitions between distinct Landau levels and electron transitions between distinct states of the same broadened Landau level.
-To avoid these absorptions, we have tuned the dressing field into a high-frequency range in our system under the analysis.
-Furthermore, due to the dressing high-intensity electromagnetic field, the entire electronic states of the conventional 2DEG quantum Hall system will be restructured.
-We have addressed these modifications through the Floquet theory.
-However, the MIRO models \cite{durst03,dmitriev03} are based on low-frequency cases where the system can absorb low-frequency photons from the field.
-\end{itemize}
-
-Based on the above discussion, we can identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two distinguishable
-magneto-transport scenarios.
-
-\begin{itemize}
-  \item Section I - fifth paragraph (page 1):\\
-  {\color{Red}
-  Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
-  This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
-These formalisms provide a proper explanation for the experimental observations of MIROs.
-However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
-  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
-  The influence induced by a pure dressing field on
-  magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
-  Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
-  }
-  \item Section VI - sixth paragraph (page 9):\\
-  {\color{Red}
-  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
-  magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems.
-However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
-  It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
-In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions.
-This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems.
-Therefore, our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
-  }
-\end{itemize}
-
-\subsubsection*{Comment 3 -
-\color{RoyalBlue} The manuscript will also provide more impact if it demonstrates how the new results can help to improve the future development of nanoelectronic devices.
-After these questions are addressed, the manuscript will be suitable for publication in Physical Review B.
-Otherwise, it will fit better to a more mathematically oriented journal.
-}
-
-This is a valid comment.
-As we mentioned in comment 1, considering the importance of discussing the physical significance of our results, we included a new section (Section VII) to address this comment.
-
-\begin{itemize}
-  \item Section VII (page 8):\\
-  {\color{Red}
-  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}
-
-  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
-The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
-The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
-This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically.
-The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
-  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}.
-The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.
-
-  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
-  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
-  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}.
-Strikingly, we show in Fig.
-5 that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering.
-Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
-
-  Research on novel states of matter has driven the evolution of present-day nanoelectronic devices.
-In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
-  The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
-  As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
-  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
-  We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}.
-Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures.
-Since the Fermi level of a system can be altered with the applied gate voltage, our Fig.
-4 depicts this result.
-  In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field.
-Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.
-
-  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
-In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
-As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field.
-This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
-  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
-  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
-  Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
-  magneto-transport properties of 2D nanostructures.
-  }
-\end{itemize}
-
-\subsubsection*{Comment 4 -
-\color{RoyalBlue} The quantum Quantum Hall effect requires high mobility samples.
-In these samples, the structure of the disorder is usually complicated and combines both short-length potentials of impurities and long-length electrostatic inhomogeneities.
-The interplay of these components of disorder opens exciting questions about the transport properties of 2DEGs.
-What is the structure of disorder considered in the present manuscript and hidden in the notations for Vimp?
-What are the conditions for validity of eq.
-(15)?
-}
-
-We thank the reviewer for raising this important question.
-In our previous manuscript, we have presented the detailed derivation of Eq.~[15] with a discussion on models of disorder under Appendix C.
-However, here we again elucidate our disorder model and approximations made to derive the Eq.~[15] for clarity and to respond to this question.
-
-We modeled the effect caused by impurities in the considered system as a single perturbation potential.
-Analyzing the electric properties for a specific impurity distribution is a rather formidable task.
-We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
-Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
-We start our analysis by considering a static disorder that corresponds only to elastic electron scattering processes.
-We adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the associated system and we approximate this into a Gaussian white noise.
-
-Since we are presenting the perturbation potential $V(\vb{r})$ by a group of randomly localized impurities, we assume $N_{imp}$ number of identical single impurity potentials distributed randomly but in fixed positions $\vb{r}_i$.
-Thus, we can describe the perturbation potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$,
-\begin{equation} \label{eq:1}
-  V(\vb{r}) =
-  \sum_{i=1}^{N_{imp}}
-  \upsilon (\vb{r}-\vb{r}_i).
-\end{equation}
-Furthermore, we approximate this perturbation potential as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average.
-This model is characterized by the following two equations \cite{akkermans10}
-\begin{subequations}
-\begin{equation} \label{eq:2}
-  \expval{\upsilon(\vb{r})}_{imp} =0,
-\end{equation}
-\begin{equation} \label{eq:3}
-  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
-\end{equation}
-\end{subequations}
-where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function that solely depends only on $\vb{r}-\vb{r'}$, and decays with a characteristic length $r_c$.
-Since this study considers the case where the wavelength of radiation or a scattering electron is much greater than $r_c$, it is reasonable to approximate its two-point correlation function by
-\begin{equation} \label{eq:4}
-  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
-\end{equation}
-where $\Upsilon_{imp}^2$ is a positive constant.
-A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}.
-Then we can approximately write the total scattering potential as
-\begin{equation} \label{eq:5}
-  V(\vb{r}) =
-  \sum_{i=1}^{N_{imp}}
-  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
-\end{equation}
-
-Using this expression, we can evaluate the Floquet-Fermi golden rule for a dressed quantum Hall system.
-Furthermore, considering the properties of a Gaussian white noise impurity distribution \cite{wackerl20,akkermans10}, we assume $V_{imp}$ is a constant in the momentum space.
-Here $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
-All the detailed steps for the derivation of the Floquet-Fermi golden rule for a dressed quantum Hall system are included in Appendix C.
-However, throughout the derivation, we use only the first-order contribution (Born approximation) of the impurity potential.
-
-Since previous studies on Floquet-Drude conductivity \cite{wackerl20}, and magneto-transport properties in undressed \cite{endo09} and dressed \cite{dini16} quantum Hall systems have used this particular Gaussian white noise potential, we also selected this particular impurity model to describe our system.
-Such a choice enables us to compare our analytical results with these previous models.
-As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the
-magneto-transport properties of dressed quantum Hall system would be an intriguing future research possibility.
-
-Since we have only mentioned the validity conditions we used to derive the Eq.~[15] in Appendix C and not in the main text of the previous manuscript, we have added these validity conditions to the main text of the revised manuscript.
-
-\begin{itemize}
-  \item Section IV - first paragraph (page 4):\\
-  {\color{Red}
-  We have modeled the effect caused by impurities as a single short-range perturbation potential.
-Analyzing the electric properties for a specific impurity distribution is a rather formidable task.
-We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
-  Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
-  Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
-  Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$.
-This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20}.
-  Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
-  Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder.
-In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
-  }
-\end{itemize}
-
-\subsubsection*{Comment 5 -
-\color{RoyalBlue} If continuous illumination is applied to an electron system, the system will heat indefinitely.
-The distribution function is stabilized when the electron-electron and electron-phonon scattering mechanisms are included.
-What are the conditions of validity for eqs.
-(33-34)?
-The deviations of the distribution function from its equilibrium result in effects that can significantly overcome the equilibrium contributions, see Dmitriev et al, Phys.
-Rev.
-B 80, 165327 (2009).
-However, to capture these effects, a treatment within Floquet-Drude formalism is insufficient and a complete quantum kinetic equation has to be analyzed.
-Can the authors argue why their results still present some interest to the community even if they potentially disregard more significant contributions?
-}
-
-This is a good, valid question.
-First, we discuss the validity of the Eq.~[33] and Eq.~[34].
-Our analysis derived the longitudinal conductivity of a dressed quantum Hall system without any partial distribution function specification until Eq.~[31].
-In contrast to the MIRO analysis \cite{dmitriev03,dmitriev05,dmitriev09}, we consider the dressed quantum Hall system under the off-resonant condition, where the photon absorption does not happen.
-Therefore, we can select the Fermi-Dirac distribution as our particle distribution function for Eq.~[31]
-\begin{equation} \tag{5}
-  f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1}.
-\end{equation}
-Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
-Then we consider a special scenario where the system operates at a low-temperature limit, i.e., the condition $k_BT \ll \varepsilon_F$.
-Since previous theoretical studies \cite{wackerl20,dini16,endo09} on magneto-transport properties of 2DEG quantum Hall systems were derived under this assumption, we also adopted the same conditions as it enables us to compare results with those studies.
-In addition, as mentioned in previous experimental studies on SdH oscillations \cite{zudov03,mani02,arapov02} in 2DEG undressed quantum Hall systems with increasing temperature, we can identify the decaying behavior of SdH oscillations.
-Therefore, if we need to maintain a good oscillatory behavior, we need to operate in low temperatures.
-Since in our analysis, we study the manipulation of SdH oscillations using a dressing field, it is reasonable to simplify our general derivation given in  Eq.~[31] for low-temperature limit.
-Under these assumptions, the derivative of the Fermi-Dirac distribution is sharply peaked around the Fermi energy, and  can be represented by the delta function \cite{endo09}
-\begin{equation} \tag{6}
-  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
-\end{equation}
-Applying these adequate conditions, we can simplify our derivation into a single expression that can be compared with previous studies \cite{wackerl20,dini16,endo09} on
-magneto-transport in dressed quantum Hall systems. We have added clarification on the above assumptions in the revised manuscript.
-\begin{itemize}
-  \item Section V - second paragraph (page 7):\\
-  {\color{Red}
-  We consider a dressed quantum Hall system under off-resonant condition, where photon absorption does not happen.
-Therefore, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
-  \begin{equation} \tag{33}
-    f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
-  \end{equation}
-  where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
-At low-temperatures, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
-  \begin{equation} \tag{34}
-    - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
-  \end{equation}
-  }
-\end{itemize}
-
-Yes, indeed, experiments on quantum hall systems subject to a strong dressing field show elevated temperatures.
-However, as demonstrated in previous studies by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, it is possible to maintain low system temperature by limiting the dressing field to narrow pulses.
-
-Although we have restricted our general derivation given in Eq.~[31] into a particular instance for comparison, there is no fundemental restriction in extending our theoretical model into different types of particle distribution functions.
-As presented in the previous work of Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion needs to address the changes in distribution functions in our derived general longitudinal conductivity formula, and this would be a noteworthy extension to our study.
-
-\subsubsection*{Comment 6 -
-\color{RoyalBlue} The authors presented the results for the conductivity tensor's xx- and yy-components.
-They seem to be identical, apart of a dimensional factor $(eB)^2$ in the denominator.
-The equality of these two components is expected for isotropic systems.
-Does the polarization of the electromagnetic field break the isotropy?
-Do the two components of the conductivity remain equal even for an arbitrary direction of a linearly polarized field?
-Is there a non-Hall contribution to the xy-component?
-}
-
-We express our gratitude towards the reviewer for pointing out this inadvertent oversight done in the $yy$-component of the current operator calculation.
-This has led to an unexpected normalization factor in the yy-component of the  conductivity expression.
-Since we have only used the normalized $xx$-component of the conductivity tensor for subsequent analysis, this oversight has no impact on the analysis reported in the  manuscript.
-With this correction, we observe that both xx-component and $yy$-component show the same conductivity behaviors.
-We added these amendments to the current operator calculations done in Appendix D and the longitudinal conductivity calculation under Section V.
-
-\begin{itemize}
-  \item Appendix D (page 16):\\
-  {\color{Red}
-  \subsection*{\label{appendix_d}Appendix D: Current operators for a dressed quantum Hall system}
-
-  In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system.
-We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(1) and we identified them as the Floquet states in Eq.~(14).
-For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(10) as quantum states using their corresponding quantum numbers as follows
-  \begin{equation} \tag{D1}
-    \ket{\phi_{n,m}} = \ket{n,k_x}.
-  \end{equation}
-  Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
-  \begin{equation} \tag{D2}
-    \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
-  \end{equation}
-  Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
-  \begin{equation} \tag{D3}
-    \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
-  \end{equation}
-  where $\widetilde{m}$ is the mass of the associated particle.
-
-  First, we consider the $x$-directional particle current operator component, and we can identify that as
-  \begin{equation} \tag{D4}
-    \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
-  \end{equation}
-  Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
-  \begin{equation} \tag{D5}
-    \left({j}_x \right)_{nm,n'm'} =
-    \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
-  \end{equation}
-  and we evaluate these using the Floquet modes derived in Eq.~(7) as follows
-  \begin{equation} \tag{D6}
-    \begin{aligned}
-      \left({j}_x \right)_{nm,n'm'} = &
-      \frac{1}{{\widetilde{m}}}
-      \delta_{k_x,k'_x}
-      \int
-      \left(\hbar k'_x + eBy\right) \\
-      & \times
-       \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
-      \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
-      dy.
-    \end{aligned}
-  \end{equation}
-  Let $[y - y_0 - \zeta(t)] = \bar{y}$, and we can obtain
-  \begin{equation} \tag{D7}
-    \begin{aligned}
-      \left({j}_x \right)_{nm,n'm'} =
-      \frac{1}{{\widetilde{m}}}
-      \delta_{k_x,k'_x}
-      \int &
-      \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right]
-      \chi_{n}(\bar{y})
-      \chi_{n'}(\bar{y})
-      d\bar{y}.
-    \end{aligned}
-  \end{equation}
-  Using the following integral identities of the Floquet modes that are made of Gauss-Hermite functions \cite{vedenyapin11,szego59}
-  \begin{equation} \tag{D8}
-    \int
-    \chi_{n}({y})
-    \chi_{n'}({y}) d{y} =
-    \delta_{n',n},
-  \end{equation}
-  \begin{equation} \tag{D9}
-    \int
-    y \chi_{n}({y})\chi_{n'}({y}) d{y} =
-    \frac{1}{\kappa}
-    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-    \delta_{n',n-1} \right),
-  \end{equation}
-  we simplify the matrix elements of $x$-directional current operator to obtain
-  \begin{equation} \tag{D10}
-    \begin{aligned}
-      &\left({j}_x \right)_{nm,n'm'} =
-      \frac{eB}{{\widetilde{m}\kappa}}
-      \delta_{k_x,k'_x}
-      \left[
-      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-      \delta_{n',n-1}\right)
-      + \zeta(t) \delta_{n',n}
-      \right].
-    \end{aligned}
-  \end{equation}
-  Due to high complexity of extract solution, in this study we only consider the constant contribution from the Fourier series components of the above expression.
-Therefore, we can identify the $0$-th component of the Fourier series as
-  \begin{equation} \tag{D11}
-    \begin{aligned}
-        \left({j}_x \right)_{nm,n'm'} =&
-        \frac{eB}{\widetilde{m}\kappa}
-        \delta_{k_x,k'_x}
-        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-        \delta_{n',n-1} \right).
-    \end{aligned}
-  \end{equation}
-  To calculate the electric current operator, we substitute the electron's charge and effective mass to the above derived equation. This leads to
-  \begin{equation} \tag{D12}
-    \begin{aligned}
-        \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
-        \frac{e\hbar}{{m_e}l_0}
-        \delta_{k_x,k'_x}
-        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
-        \delta_{n',n-1} \right).
-    \end{aligned}
-  \end{equation}
-  where $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$ is the magnetic length.
-
-  Moreover, we can identify the $y$-directional current operator component as
-  \begin{equation} \tag{D13}
-    \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
-  \end{equation}
-  Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
-  \begin{equation} \tag{D14}
-    \left({j}_y \right)_{nm,n'm'} =
-    \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
-  \end{equation}
-  After following the same steps done for the $x$-directional current operator, and recursion relation of the first derivative of Gauss-Hermite functions
-  \begin{equation} \tag{D15}
-    \begin{aligned}
-      \pdv{\chi_{n}({y})}{y} =
-      \kappa\left[
-      -  \sqrt{\frac{n+1}{2}} \chi_{n+1}({y})
-      +  \sqrt{\frac{n}{2}} \chi_{n - 1}({y})
-      \right],
-    \end{aligned}
-  \end{equation}
-  we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
-  \begin{equation} \tag{D16}
-    \begin{aligned}
-      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
-      \frac{ie\hbar\kappa}{m_e}
-      \delta_{k_x,k'_x}
-      \left(
-      \sqrt{\frac{n}{2}} \delta_{n',n-1}
-      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
-      \right).
-    \end{aligned}
-  \end{equation}
-  \begin{equation} \tag{D17}
-    \begin{aligned}
-      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
-      \frac{ie \hbar}{m_e l_0}
-      \delta_{k_x,k'_x}
-      \left(
-      \sqrt{\frac{n}{2}} \delta_{n',n-1}
-      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
-      \right).
-    \end{aligned}
-  \end{equation}
-  }
-  \item Section V - second paragraph (page 7):\\
-  {\color{Red}
-  Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(31) leads to
-  \begin{equation} \tag{35}
-    \begin{aligned}
-      \sigma^{xx}  =
-      \frac{e^2l_0^2}{\pi\hbar A}
-      \sum_{n}
-      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
-      \left[
-        \frac{1}
-        {
-          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
-        }
-      \right]
-      \left[
-        \frac{1}
-        {
-          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
-        }
-      \right],
-    \end{aligned}
-  \end{equation}
-  where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$,
-  $\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$, and $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$.
-  Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
-  \begin{equation} \tag{36}
-    \begin{aligned}
-      {\sigma}^{yy} =
-      \frac{e^2l_0^2}{\pi\hbar A}
-      \sum_{n}
-      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
-      \left[
-        \frac{1}
-        {
-          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
-        }
-      \right]
-      \left[
-        \frac{1}
-        {
-          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
-        }
-      \right].
-    \end{aligned}
-  \end{equation}
-  }
-\end{itemize}
-
-Suppose we apply an arbitrary directional polarized dressing field.
-In that case, we could derive an expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with the same steps presented in our analysis.
-This would change the amplitude of the associated dressing field ($E$) in each direction.
-There will be a new component in parallel to the conductivity component of interest, which will modify the time-dependent Hamiltonian given in Eq.~[2].
-Then, we need to solve the Schrödinger equation with the modified Hamiltonian to find the new Floquet modes for the new system.
-These will define the effect on the inverse scattering time matrix components.
-As mentioned in Ref.
-\cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the considered system and creates novel states called Floquet states.
-The properties of these states depend on the characteristics of the applied dressing field.
-Therefore, the polarization method also changes the behavior of the Floquet states.
-These polarization-dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields.
-However, in a dressed quantum Hall system with a $y$-directional linear polarized field, we predict the same longitudinal conductivity behaviors in diagonal components of the conductivity tensor.
-
-For analyzing our system, we mainly employ the diagonal components of the Floquet-Drude conductivity tensor introduced by Wackerl \textit{et al.} \cite{wackerl20}.
-As we mainly focus on SdH oscillations in longitudinal conductivity components, we limit our analysis to the dressing field influence on two diagonal components of the conductivity tensor.
-Therefore we are unable to predict the off-diagonal component behavior of the system.
-%
-% As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the quantum state of the consideirng system and creates novel states called Floquet states.
-The properties of these states are depends on the characteristics of applied dressing field.
-Therefore, the polarization method also change the behavior of the Floquet states.
-% These polarization dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields.
-In addition, they have mentioned the impact on the direction of the linearly polarization dressing field and this will break the isotropy behavior of the longitudinal conductivities in the consideirng system.
-%
-% We also followed the same formalism of Floquet states for 2DEG quantum Hall systems.
-In our work also we were able to identify that the applied dressing field's polarization direction can be effect the magnitude of the longitudinal conductivity component.
-A detailed derivation of these two longitudinal conductivity component's current operators are given in Appendix D.
-If we applied a arbitary directional polarized dressing field, we can derive a expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with same steps in this analysis.
-This would change the amplitude of the considering dressing field ($E$) in each direction.
-However, now there will be a new conponent in parallel to the considering conductivity component and we need to solve the Schrödinger equation with the modified Hamiltonian in Eq.~[2] for the new system with these changes.
-% However in our analysis, our main objective was to identify the manipulation capabilities of SdH oscillations using dressing field intensity.
-In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diagonal components in conductivity tensor.
-Therefore we are unable to predict the off-diagonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quantum Hall systems.
-
-\subsection*{Response to the comments of Reviewer 2}
-
-We want to thank the reviewer for his/her insightful comments on our work.
-To address your comments, we had to add new materials and reorganize our text.
-As a result, we have been able to considerably improve our discussion on the underlying assumptions and corresponding physical significance of our analysis.
-We hope our response and the corresponding changes we incorporated into the manuscript will be sufficient to clarify the issues raised.
-
-\subsubsection*{Comment 1 -
-\color{RoyalBlue} The paper is very low on comparison with experiments, for which there is a large amount of data available for the zero radiation case.
-I would like to see detailed analysis of how Figs 4 and 5 compare with available
-experimental data. Without this addition, physical relevance of such
-detailed calculations is questionable.
-}
-
-We thank the reviewer for pointing out the importance of this fact.
-In the revised manuscript, we have included a detailed analysis of our results against the undressed 2DEG quantum Hall system behavior.
-
-\begin{itemize}
-  \item Section VI - third paragraph (page 8):\\
-  {\color{Red}
-  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.
-4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
-  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
-  Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
-  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
-  The gate voltage modifies the Fermi level of the system.
-  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
-  Interestingly, this oscillatory behavior against applied gate voltage has been observed experimentally by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
-  By comparing these observations against our results in Fig.
-4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
-  Furthermore, when we increase the gate voltage, the Fermi level rises.
-As illustrated in Fig.
-4, this will result in a higher conductivity peak value at the higher-order Landau levels.
-This same behavior was also observed in the experimental observations presented in Ref.
-\cite{wakabayashi78}.
-  In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
-  }
-\end{itemize}
-
-\subsubsection*{Comment 2 -
-\color{RoyalBlue} In the presence of disorder, Anderson localization and topologically protected edge modes are dominant considerations when calculating DC transport coefficients.
-How are these factors taken into account?
-}
-
-We omitted a discussion on the Anderson localization and topologically protected edge modes as we neglected them in our work.
-While deriving Eq.~[31], we have assumed that the applied static magnetic field is placed in a lower intensity range where we can neglect several effects known to appear in a 2DEG quantum Hall system.
-Under this condition, we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions, and the spin splitting as well.
-As mentioned in the work of Endo \textit{et al.} \cite{endo09}, within the magnetic field range of interest, the undressed
-magneto-transport properties of GaAs/AlGaAs 2DEG quantum Hall system provide an excellent agreement between the experimental observations and theory that was developed by neglecting the above-mentioned effects.
-Our work is very similar to theirs with an additional dressing field.
-Our results for the undressed system agree with the results in Ref.
-\cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks.
-We have added this clarification in the manuscript.
-
-\begin{itemize}
-  \item Section I - sixth paragraph (page 2):\\
-  {\color{Red}
-  It is important to note that, we limit the applied magnetic field to a range where we can neglect effects such as Anderson localization, formation of the edge states, spin splitting, and the electron-electron interactions.
-These are not overly restrictive assumptions, and other have successfully used same assumptions in their work, e.g see Endo \textit{et al.} \cite{endo09}.
-  }
-  \item Section VIII - first paragraph (page 10):\\
-  {\color{Red}
-  We modeled the impurities in the material as a Gaussian random scattering potential, and restricted the applied magnetic field to a range where we can neglect effects of Anderson localization, formation of the edge states, spin splitting, and electron-electron interactions.
-  }
-\end{itemize}
-
-\subsubsection*{Comment 3 -
-\color{RoyalBlue} Can the authors reproduce the quantized Hall conductance of filled Landau levels in the presence of disorder? Please discuss.
-}
-
-For analyzing our system, we mainly employ the diagonal components of the Floquet-Drude conductivity tensor introduced by Wackerl \textit{et al.} \cite{wackerl20}.
-As we mainly focus on SdH oscillations in longitudinal conductivity components, we limit our analysis to the dressing field influence on two diagonal components of the conductivity tensor.
-Therefore we cannot predict the off-diagonal component behavior of the system.
-However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behavior of off-diagonal components of the conductivity tensor.
-As mentioned in Ref.
-\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly agree with  experiment observations
-\begin{equation} \tag{1}
-  \dv{\widetilde{\sigma}^{xy}(X_F,I)}{B} \approx
-    \pi\mu \frac{\hbar \omega_0}{\varepsilon_F} [\widetilde{\sigma}^{xx}(X_F,I)]^2.
-\end{equation}
-By examining the connection between longitudinal and transverse conductivities in the 2DEG quantum Hall system, we can expect the same Hall conductivity behavior in a dressed quantum Hall system.
-However, using the dressing field, we can squeeze the conductivity peaks on Landau levels, i.e., squeeze the region of longitudinal conductivity peaks placed near the Landau levels.
-This  implies sudden Hall conductivity transitions between one plateau to another near a Landau level.
-As in Refs.
-\cite{klitzing80,gusynin06}, we can also predict a staircase behavior of quantum Hall conductivity against the gate voltage.
-With an external dressing field, we will be able to get rapid transitions than the undressed system.
-However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulated from the beginning.
-It will be the subject of our future study.
-
-\subsubsection*{Comment 4 -
-\color{RoyalBlue} The way some previous works are cited is disappointing.
-Example from page 8: “Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.” This is not informative.
-Where, specifically, did results from earlier works fall short of reality, which have been better addressed in this work?
-}
-
-We made the following changes in language and presentation to improve the clarity of our manuscript.
-
-\begin{itemize}
-  \item Section VIII (page 8):\\
-  {\color{Red}
-  Despite this behavior being identified in the previous work of Dini \textit{et al.}  \cite{dini16}, they cannot fully account for the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.
-\cite{endo09}.
-The authors of Ref.
-\cite{dini16} have used the conventional expression of longitudinal conductivity from Refs.
-\cite{ando74_1,ando82} and this theory yields a semi-elliptical broadening for the Landau levels.
-These predictions significantly deviate from the experimentally observed Landau level broadening \cite{endo09}.
-  However, our generalized analysis on the conductivity of dressed quantum Hall systems provides a well-suited description for empirically observed behaviors of undressed quantum Hall systems as well.
-  }
-  \item Section III - first paragraph (page 3):\\
-  {\color{Red}
-  In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field.
-  }
-  \item Section I - fifth paragraph (page 2):\\
-  {\color{Red}
-  The authors of Ref.
-\cite{dini16} used the conductivity models from Refs.
-\cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
-  }
-  \item Section IV - third paragraph (page 5):\\
-  {\color{Red}
-  In the study presented in Ref.
-\cite{endo09}, the authors have assumed that the effective mass of an electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
-  }
-\end{itemize}
-
-\subsubsection*{Comment 5 -
-\color{RoyalBlue} Adding some physical insight into the remarkable observation of radiation-induced narrowing of lineshapes (Figs 4, 5) will help elevate
-this work.
-}
-
-We agree with the reviewer that a discussion on our theoretical results and their physical significance in modern nanoelectronic devices is a vital requirement.
-We have added a new Section VII to overcome the above-mentioned deficiency of our manuscript.
-The total content of the section is given below,
-
-\begin{itemize}
-  \item Section VII (page 8):\\
-  {\color{Red}
-  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}
-
-  With the realization of 2DEGs in Si-MOSFETs (Metal Oxide Semiconductor Field Effect Transistors) \citep{fowler66}, Klitzing \textit{et al.} \cite{klitzing80} made the first transport measurements on such systems to reveal the quantum Hall effect.
-The empirical discovery of these unusual properties marked the beginning of a whole new realm in condensed matter physics that continues to produce phenomenal advancements in electronic systems.
-The quantum Hall effects in a 2DEG under a static magnetic field are described by plateaus quantized to integer values of the conductivity quantum ($\flatfrac{e^2}{\hbar}$) in the off-diagonal conductivity, with simultaneous peaks at inter-plateau transition for the diagonal conductivity \cite{endo09}.
-This is due to the applied magnetic field and it changes the energy spectrum of 2DEG dramatically.
-The magnetic field causes the density of states in 2DEG to split up into a sequence of delta functions, separated by an energy $\hbar\omega_0$, with $\omega_0$ the cyclotron frequency which depends on the applied magnetic field.
-  However, experimental results demonstrate that these Landau levels are broadened and the main source of these broadening at low temperatures is the disorders in materials \cite{ando85,dial07}.
-The broaden sequence of delta functions of the density of states implies the oscillating behavior in the experimental measurements of longitudinal conductivity which is known as SdH oscillations \cite{endo09,wakabayashi78}.
-
-  Our theoretical analysis on longitudinal conductivity behavior of dressed quantum Hall system was developed by considering low-temperature limit with Gaussian impurity broadening assumptions.
-  As illustrated in Fig. 4, we can describe the experimentally observed SdH oscillation results in Refs.\cite{endo09,wakabayashi78} through our model.
-  Under the undressed condition, our results overlap with the conductivity measurement of quantum Hall systems \cite{endo09}.
-Strikingly, we show in Fig.
-5 that we can manipulate the broadening of these conductivity peaks using an external dressing field.
-At low temperatures, the principal cause of broadening of these conductivity peaks is impurity-induced scattering.
-Using an external dressing field, we can suppress the impurity-induced scattering and this results a reduction of both the scattering-induced broadening and the longitudinal conductivity peaks.
-
-  Research on novel states of matter has driven the evolution of present-day nanoelectronic devices.
-In particular, controllable manipulation of material properties through a gate electric field has revolutionized the development of material science and technology \cite{ahn03,deng18}.
-  The charge carrier concentration of a system is an imperative parameter that defines its conductivity properties.
-  As we can manipulate the charge carrier concentration using an electrostatic field-effect, we exert significant control over the conductivity externally.
-  A 2DEG under static magnetic field with quantum Hall effects is an excellent example that illustrates how the gate electric field controls conductivity.
-  We also observed that a considerable number of studies exist on charge transport in the quantum limit that employed different types of 2D field-effect transistors (FETs) subjected to magnetic fields \cite{wakabayashi78,yang18,long20,li14}.
-Yang \textit{et al.} \cite{yang18} study shows quantized Hall plateaus and SdH oscillations for longitudinal conductivity against gate voltage in black phosphorus FET under static magnetic fields at low temperatures.
-Since the Fermi level of a system can be altered with the applied gate voltage, our Fig.
-4 depicts this result.
-  In particular, our analysis shows that we can manipulate the broadening of the conductivity regions using an external dressing field.
-Although Yang \textit{et al.} \cite{yang18}, achieved broadening in longitudinal conductivity peaks by changing the temperature in a low range, in this study we presented a general theory on manipulating longitudinal conductivity broadening using a high-intensity electromagnetic field.
-
-  The realization of the underlying mechanism of 2D FETs in the quantum realm promises its potential in next-generation nanoelectronic applications.
-In a particular application that uses the switching mechanism of the above-discussed FETs with quantum Hall effects, we can achieve high and low output conductivities by changing the input gate voltage.
-As a result of manipulating the broadening of conductivity regions, we can limit the broadening of conductivity peaks around Landau levels using a dressing high-intensity electromagnetic field.
-This will enhance the sensitivity of FETs which provides the ability to observe narrow changes in gate voltage.
-  Furthermore, adopting the mechanism presented in Ref. \cite{hirakawa01}, we can manipulate conductivity peaks into very sensitive, narrowband high-frequency radiation detectors.
-  We envision these advances in nanoelectronics from our theoretical model and knowledge generated from the insight it provides to the underlying dependencies.
-  Furthermore, this theoretical model will aid in the development of simulation tools that will design the quantum effects in
-  magneto-transport properties of 2D nanostructures.
-  }
-\end{itemize}
+We agree with the reviewer that the issue was not addressed properly. Therefore, we have made an extensive discussion on the underlying validity of approximation in Eq.~[34].
 

### 2022-01-13 response2/response2.tex
Add res to q1

@@
 
-We agree with the reviewer that the issue was not addressed properly. Therefore, we have made an extensive discussion on the underlying validity of approximation in Eq.~[34].
+We agree with the reviewer that the issue was not addressed properly.
+Therefore, we have made an extensive discussion on the underlying validity of approximation in Eq.~[34].
+Fisrt, we discuss about the complications we have to face when we are trying to derive a full description of a realistic periodically driven system.
+Thus, we assume the particle distribution function is stationary under external driving field.
+Later, we clarify the actual conditions and requirements for the a stationary particle distribution function for driven system.
+
+The accessibility of coherent driving fields such as laser opens many interesting potential for manupulating quantum systems.
+This leads to Floquet engineeting of solid-state, atomic, and photonic systems with the bais of Floquet states.
+However, the powerful thermodynamic rules that related to the static systems in thermal equilibrium in general cannot be apply into the nonequilibrium regime where Floquet states are defined \cite{seetharam2015}.
+Therefore, in order to achieve the viability of Floquet engineering in fermion systems, it is crucial to undestand the conditions for a steady state partical distribution and it is one of the major challenge in the field.
+Among previous studies on this topic, a main point of inestigation is time-scales.
+As an example, if the switch-on of the driving field is not far from the past, the distribution function of a qunatum system will highly depend on the switching-on protocal of the periodic driving \cite{dehghani2014}.
+Although we can consider the intermediate timescales, there would be many physical processes causing the heating of the quantum system.
+A variety of approches for stabilizing the quantum system under this condition has been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}.
+When the applied driving field get stronger the heating caused by the field gets increase.
+Thus, the cooloing system needs to be much stronger and this leads to a non-perturbative inclusion of the bath to the system.
+In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasiparticles and their scattering processes have addressed semi-classically using the Boltzmann approch.
+However, a fully microscopic description of heating of a driven system is a rather challenging task due to the multiple processes that need to be investigate.
+It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging.
+In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}.
+This leads towards to a featureless state at long times.
 

### 2022-01-14 response2/response2.tex
Add to res of q1

@@
 Fisrt, we discuss about the complications we have to face when we are trying to derive a full description of a realistic periodically driven system.
-Thus, we assume the particle distribution function is stationary under external driving field.
-Later, we clarify the actual conditions and requirements for the a stationary particle distribution function for driven system.
+Later, we clarify the actual conditions and requirements to approximate a stationary particle distribution function for driven system.
 
-The accessibility of coherent driving fields such as laser opens many interesting potential for manupulating quantum systems.
-This leads to Floquet engineeting of solid-state, atomic, and photonic systems with the bais of Floquet states.
+The accessibility of coherent driving fields such as laser opens many interesting capabilities for manupulating quantum systems.
+This leads to Floquet engineeting of solid-state, atomic, and photonic systems with the basic of Floquet states.
 However, the powerful thermodynamic rules that related to the static systems in thermal equilibrium in general cannot be apply into the nonequilibrium regime where Floquet states are defined \cite{seetharam2015}.
@@
 This leads towards to a featureless state at long times.
+All these concludes that undestanding of heating processes in any timescale and adress them to describe relastic driven system needs the treatment of very rich physics.
+However, under proper parameter regimes to be discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.
+
+Since there exist a novel regime of closed Floquet systems with quas-isteady state that persists for an exponentially long time \cite{lindner2017}, we assumed that the distribution is to be a time-independent through out our paper.
+The main reason behind the heating of a driven quantum system is absorbtion of photons from the applied field.
+Thus, to suppress the heating rating we require to control the absorption processes.
+We can achieve this by fine-tuning the driving field.
+Before discuss further, first we need to introduce few energy scales mentioned in the Rudner \textit{et al.} work \cite{rudner2020}, such as photon energy of the driving field $\hbar\omega$, the single-particle bandwidth of the low-lying bands $W$, the local interaction energy scale $U$, and the size of a gap in the spectrum $\Delta$.
+Here, $\omega$ is the frequency of the driving field.
+As mentioned in Rudner \textit{et al.} work \cite{rudner2020}, there are two promising regimes where the heating rate can be suppressed in a closed Floquet system.
+First regimes is the limit where the applied field's photon energy is larger than the bandwidth of the low-lying bands ($\hbar\omega \gg W$).
+In this case, absorption process only can take place through high-order processes that involve many-particle rearrangements known as many-body resonances \cite{bukov2016,lindner2017,rudner2020}.
+Therefore, these absorptions are heavily suppressed and this leads the system to a equilibrium-like
+state.
+This regime has been enabled many researches on driven quantum systems \cite{kitagawa2011,lopez2015,pervishko2015,bukov2015,yudin2016}.
+Under the high frequency illumination, the systems becomes nearly time-independent where the external driving only renormalize the system's parameters rather than manipulating the distribution \cite{wackerlthesis20}.
 

### 2022-01-17 response2/response2.tex
Finalize res to q1

@@
 However, the powerful thermodynamic rules that related to the static systems in thermal equilibrium in general cannot be apply into the nonequilibrium regime where Floquet states are defined \cite{seetharam2015}.
-Therefore, in order to achieve the viability of Floquet engineering in fermion systems, it is crucial to undestand the conditions for a steady state partical distribution and it is one of the major challenge in the field.
+Therefore, in order to achieve the viability of Floquet engineering in fermion systems, it is crucial to undestand the conditions for a steady state particle distribution and it is one of the major challenge in the field.
 Among previous studies on this topic, a main point of inestigation is time-scales.
@@
 Therefore, these absorptions are heavily suppressed and this leads the system to a equilibrium-like
-state.
+state. Now, the system becomes nearly time-independent where the external driving only renormalize the system's parameters rather than manipulating the distribution \cite{wackerlthesis20}.
 This regime has been enabled many researches on driven quantum systems \cite{kitagawa2011,lopez2015,pervishko2015,bukov2015,yudin2016}.
-Under the high frequency illumination, the systems becomes nearly time-independent where the external driving only renormalize the system's parameters rather than manipulating the distribution \cite{wackerlthesis20}.
+The next possible regime can be identified in gapped systems.
+When the high-lying energy bands are significantly seperated from a set of low-lying bands ($\hbar\omega \ll \Delta$), many photons must be absorbed for a single excitation across the energy gap $\Delta$.
+This results a significant suppression of energy absorbtion processes and heating rates \cite{rudner2020}.
+However, if the local interaction strength $U$ is a dominating energy scale, the interactions make hige impact on particle states in the system.
+This makes the study more complicated.
+Thus, to neglect the interactions, the interaction strength should be smaller than the both the bandwidth and the photon energy.
+Connecting the above discussed energy scales and their unique requirements, we can identify a most promising regime for a driven system with steady particle distribution with an increasing energ scale hierarchy: $U \ll W \ll \hbar\omega \ll \Delta$ \cite{wackerlthesis20}.
+This will allow us to consider a quantum system with time-independent paricle distribution function under a driven field in our work.
+
+Next, it is important to note that, the studies \cite{wackerl20,wackerlthesis20,dini16,endo09} inspire our work have been used this steady state particle distribution function assumption with very low temperature conditions $k_B T \ll \varepsilon_F$.
+Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy level.
+Our main aim was to use a new approch namely Floquet-Drude conductivity \cite{wackerl20} to build our theoritical analysis on the dressed quantum Hall system.
+Since, we expected to compare our theoritical description on the charge transport properties of dressed quantum Hall system with the previous discussions \cite{dini16,endo09}, we used the same assumtions and conditions through out our work as well.
+This allowed us to identify the differences of our numerical results with previous outcomes from Refs.
+\cite{dini16,endo09} and seperate the actural effects of the dressing field on quantum Hall systems.
+
+It is true that the consideration of impacts on a particle distribution function of a quantum system under microwave fields is essential.
+Nevertheless, as discussed above we can treat the driving field as a pure dressing field with the proper energy and time scale conditions.
+In our study we are not rescticted to microwave field radiation.
+Since we can  employ the above mentioned conditions in our study, we assume that the driving field only renormalize the systems's parameters rather than changing the particle distribution.
+
+We agree with the reviwer that a more generalized analysis on this topic is required.
+However, the complexity related to the photon absorbtion processes is beyond the scope of the present study, and we plan to address them in our future work.
+We have now clearly mentioned these conditions related to steady particle distribution function in the revised manuscript.
+We included the following text in the revised manuscript.
+
+\begin{itemize}
+  \item Section V - second paragraph (page 7):\\
+  {\color{Red}
+  To further evaluate the conductivity expression, we must specify the distribution function.
+Generic interacting Floquet systems absorb photons from the radiation and tend to heat up \cite{seetharam2019,rudner2020}.
+  However, a full description of a common dressed system requires a proper treatment of photon interactions.
+The complexity attach to these interactions are very high.
+There are various strategies \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020} for overcoming this challenge of heating and for achieving nonequilibrium steady state distribution.
+Working in regimes where heating rates are stongly suppressed enables steady particle distribution function in driven isolated quantum systems.
+  As mentioned in Rudner \textit{et al.} \cite{rudner2020}, placing proper conditions on energy and time scales, the distribution function of a Floquet system can be assumed to be steady.
+By properly selecting the frequency of the radiation, we can ensure that the interband electron transitions are controlled.
+This leads to significantly suppressed heating rates.
+  Let's consider our dressed quantum Hall system under off-resonant conditions \cite{rudner2020,wackerlthesis20}, where photon absorption does not happen.
+Thus, we can assume that the driving field only renormalize the systems's parameters rather than changing the particle distribution function.
+  Additionaly, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our Floquet system
+  \begin{equation} \tag{33}
+    f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
+  \end{equation}
+  where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
+With the aim of compare our results with the outcomes already known in literature \cite{dini16,endo09}, we enfore the low-temperature conditions to the Fermi-Dirac distribution.
+  At low-temperatures conditions, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
+  \begin{equation} \tag{34}
+    - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
+  \end{equation}
+  }
+\end{itemize}
 

### 2022-01-17 response2/response2.tex
Add res to q2

@@
 
+\subsubsection*{Comment 2 -
+\color{RoyalBlue} Moreover, the authors are misinterpreting the results of earlier theoretical works.
+In particular, Ref.
+[31] demonstrates both the effect of photo excitations of electrons and the dressing of electronic states.}
+
+We thank the reviewer for mention this deficiency.
+We believe this comment from the reviewer comes mainly from our statement “Lately, several experimental [50–53] and theoreti- cal [54–57] studies have uncovered various remarkable magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems.
+However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
+It is important to state that the difference between our SdH oscillations and MIROs [50–53] by considering the frequency range of the applied electromagnetic field.” in the Section IV (page 9) in the manuscript.
+On a re-reading the manuscript, we see that the language we had used here is ambiguous and admit that the statement gives a meaning that is quite different to what we were trying to convey.
+
+What we meant to say here is that, once TM is fixed to the particular value we use in the simulations (i.e TM = TR), we can neglect the bath BM afterwards when analysing how the optical field affects the heat flows within the system.
+We never meant to say that the bath BM should be removed from the system at the beginning.
+
 \bibliography{response2}

### 2022-01-17 response2/response2.tex
Finalize res to q2

--- 2022-01-17 response2/response2.tex
@@
 Our responses are shown in black letters, and the modifications we have done to the manuscript are given in {\color{Red} red}.
-
-\subsection*{General changes to the manuscript}
-
-We have made some minor changes in language and presentation to improve the clarity and organization of the manuscript.
-\begin{itemize}
-    \item Section I - seventh paragraph (page 2): \\
-        {\color{Red} In Sec. VII, we discuss the physical significance of our theoretical results and their possible use in future nanoelectronic devices.
-        Finally, we summarize our findings and present our conclusions in Sec. VIII.}
-\end{itemize}
 
@@
 
+\subsubsection*{Comment 2 -
+\color{RoyalBlue} Moreover, the authors are misinterpreting the results of earlier theoretical works.
+In particular, Ref.
+[31] demonstrates both the effect of photo excitations of electrons and the dressing of electronic states.}
+
+We thank the reviewer for mention this deficiency. We believe this comment from the reviewer comes mainly from our statement
+
+{\color{CadetBlue} “This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs [54-57].
+These formalisms provide a proper explanation for the experimental observations of MIROs.
+However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
+In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
+The influence induced by a pure dressing field on
+magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.”}
+
+in the Section I (page 1 and page 2) in the manuscript. It is important to note that the Ref. [31] in our previous response to reviewer comments represents the the
+following study:
+
+\textit{I. A. Dmitriev, M. Khodas, A. D. Mirlin, D. G. Polyakov, and M. G. Vavilov, Phys. Rev. B 80, 165327 (2009).}
+
+In our previous manuscript we have represented it as Ref. [57]. In the present response we refer it as \cite{dmitriev09}.
+On a re-reading the previous manuscript, we see that the language we had used here is ambiguous and admit that the statement gives a meaning that is quite different to what we were trying to convey.
+
+What we meant to say here is that, work presented in Dmitriev \textit{et al.} \cite{dmitriev09} related to the microwave induced resistance oscillations (MIROs) which can be observed in 2DEG subjected to both magnetic field and low-frequency (microwave) radiation.
+As mentioned by the reviewer, Ref.
+\cite{dmitriev09} have properly described the magnto-trasnport properties using the dressed states of electrons as well as the photon interactions.
+On the other hand, if the driving field is in high-frequency regime, we can neglect the photon interactions as mentioned in the response to the first comment.
+In addition, we can identify that the high-frequency and low-frequency radiation lead to two different behaviors of the magnto-trasnport characteristics of dressed quantum Hall systems \cite{dini16}.
+With the low-frequency illumination, particular effects can be observed known as ``zero resistance states" where we can observe increased longitudinal conductivity.
+However, under high-frequency radiation decrease both the broadening of Landau levels and the longitudinal conductivity.
+Our analysis is focused on high-frequency regime where we can significantly suppress the photon interactions in the Floquet system.
+Therefore, we meant to mention this difference between the our study and the Ref.
+\cite{dmitriev09}.
+We never meant to say that Dmitriev \textit{et al.} \cite{dmitriev09} only consider the effects of photon excitations.
+
+To incorporate your comment to the manuscript, we removed the above mentioned statement and replaced it with wording which hopefully would convey our meaning better.
+
+\begin{itemize}
+  \item Section I - second paragraph (page 5):\\
+  {\color{Red}
+  This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+These formalisms provide a proper explanation for the experimental observations of MIROs.
+However, these experimental and theoretical works have been linked to effects of low-frequency (microwave) electromagnetic fields which results an increase of longitudinal conductivity.
+  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduce the longitudinal conductivity \cite{dini16}.
+  Since high-frequency radiation only contribute to the suppression of electron scattering, the driving field can be treated as a pure dressing (nonabsorbable) field \cite{dini16}.
+  Thus, the influence induced by a high-frequency pure dressing field on
+  magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
+  }
+\end{itemize}
+
+In addition, we have made the following minor change in language and presentation to match the rest of the manuscript better to the changes done to address the reviewer’s comments.
+
+\begin{itemize}
+  \item Section VI - sixth paragraph (page 9):\\
+  {\color{Red}
+  However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on low-frequency fields.
+  }
+  \item Section VI - sixth paragraph (page 9):\\
+  {\color{Red} In our case, the applied dressing field is in the high-frequency regime where we can neglect the photon interactions.
+The only influence of the electromagnetic field is the suppression of electron scattering.}
+\end{itemize}
+
 \bibliography{response2}

### 2022-01-17 response2/response2.tex
Finalize res to q3

@@
 
+\subsubsection*{Comment 3 -
+\color{RoyalBlue} This paper also discusses the importance of the disorder structure and that the large parameter r\_c often characterizes the high mobility electron gas.
+The latter is considered short in the present manuscript.
+However, since the authors clarified specific assumptions in their theoretical model, I believe the paper can be published in its current form.
+Analyzing the system beyond the approximations made here can be done later.}
+
+While we admit that including an analytical description for the effect of long-range impurity potentials is valuable, we need to mentioned about the previous studies \cite{dini16,endo09} influence our work.
+In these studies the transport properties of quantum Hall syatems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
+The main focus of the present study is to utilize the novel Floquet-Drude conductivity method \cite{wackerl20,wackerlthesis20} to describe dressed quantum Hall systems.
+Since it is required to compare our novel theoritical description of charge transport properties with the previous studies \cite{dini16,endo09} of dressed quantum Hall systems, we adopted the same assumptions and conditions used in previous studies.
+In addition, analysis of long-range needs the proper treatment of interections.
+These interactions are a different topic and these effects are not discussed in this work and left as future study.
+
 \bibliography{response2}

### 2022-01-19 response2/response2.tex
Change res to q3

@@
 Accordingly, we have been able to significantly refine our discussion on the underlying assumptions and corresponding physical conditions of our system.
-We hence believe that our response, and the corresponding changes we incorporated to the manuscript would be sufficient to clarify the issues raised.
+We hence believe that our response and the corresponding changes we incorporated into the manuscript would be sufficient to clarify the issues raised.
 
@@
 Therefore, we have made an extensive discussion on the underlying validity of approximation in Eq.~[34].
-Fisrt, we discuss about the complications we have to face when we are trying to derive a full description of a realistic periodically driven system.
-Later, we clarify the actual conditions and requirements to approximate a stationary particle distribution function for driven system.
+First, we discuss the complications we have to face when we are trying to derive a full description of a realistic periodically driven system.
+Later, we clarify the actual conditions and requirements to approximate a stationary particle distribution function for a driven system.
 
-The accessibility of coherent driving fields such as laser opens many interesting capabilities for manupulating quantum systems.
-This leads to Floquet engineeting of solid-state, atomic, and photonic systems with the basic of Floquet states.
-However, the powerful thermodynamic rules that related to the static systems in thermal equilibrium in general cannot be apply into the nonequilibrium regime where Floquet states are defined \cite{seetharam2015}.
-Therefore, in order to achieve the viability of Floquet engineering in fermion systems, it is crucial to undestand the conditions for a steady state particle distribution and it is one of the major challenge in the field.
-Among previous studies on this topic, a main point of inestigation is time-scales.
-As an example, if the switch-on of the driving field is not far from the past, the distribution function of a qunatum system will highly depend on the switching-on protocal of the periodic driving \cite{dehghani2014}.
+The accessibility of coherent driving fields such as laser opens many interesting capabilities for manipulating quantum systems.
+This leads to the Floquet engineering of solid-state, atomic, and photonic systems with the basics of Floquet states.
+In general, the powerful thermodynamic rules related to the static systems in thermal equilibrium, cannot be applied to the nonequilibrium regime where Floquet states are defined \cite{seetharam2015}.
+Therefore, to achieve the viability of Floquet engineering in fermion systems, it is crucial to understand the conditions for a steady-state particle distribution and it is one of the main challenges in the field.
+Among previous studies on this topic, a major point of investigation is time scales.
+As an example, if the switch-on of the driving field is not far from the past, the distribution function of a quantum system will highly depend on the switching-on protocol of the periodic driving \cite{dehghani2014}.
 Although we can consider the intermediate timescales, there would be many physical processes causing the heating of the quantum system.
-A variety of approches for stabilizing the quantum system under this condition has been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}.
-When the applied driving field get stronger the heating caused by the field gets increase.
-Thus, the cooloing system needs to be much stronger and this leads to a non-perturbative inclusion of the bath to the system.
-In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasiparticles and their scattering processes have addressed semi-classically using the Boltzmann approch.
-However, a fully microscopic description of heating of a driven system is a rather challenging task due to the multiple processes that need to be investigate.
+A variety of approaches for stabilizing the quantum system under this condition have been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}.
+When the applied driving field gets more powerful the heating caused by the field gets increases.
+Thus, the cooling system needs to be much stronger and this leads to a non-perturbative inclusion of the bath in the system.
+In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasiparticles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
+> However, a fully microscopic description of heating of a driven system is a rather challenging task due to the multiple processes that need to be investigate.
 It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging.
@@
 The main focus of the present study is to utilize the novel Floquet-Drude conductivity method \cite{wackerl20,wackerlthesis20} to describe dressed quantum Hall systems.
-Since it is required to compare our novel theoritical description of charge transport properties with the previous studies \cite{dini16,endo09} of dressed quantum Hall systems, we adopted the same assumptions and conditions used in previous studies.
-In addition, analysis of long-range needs the proper treatment of interections.
-These interactions are a different topic and these effects are not discussed in this work and left as future study.
+Since it is required to compare our novel theoritical description of charge transport properties with the previous charge transport studies \cite{dini16,endo09} of quantum Hall systems, we adopted the same assumptions and conditions.
+In addition, Wackel \textit{et al.} \cite{wackerl20} have developed the Floquet-Drude conductivity theory through the short-range impurity potential assumptions.
+Thus, first we need to improve  Floquet-Drude conductivity theory before use it on the dressed quantum Hall system.
+The analysis of the implications from long-range impurity potentials needs a proper treatment of high-order interections.
+The discussion of these interactions through Floquet theory is a different topic.
+Thus, it is not discussed in this work.
+However, following the reviewer’s suggestion, we are planning to discuss these effects through our future study.
 

### 2022-01-19 response2/response2.tex
Corrections spellings

@@
 In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasiparticles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
-> However, a fully microscopic description of heating of a driven system is a rather challenging task due to the multiple processes that need to be investigate.
+However, a fully microscopic description of the heating of a driven system is a rather challenging task due to the multiple processes that need to be investigated.
 It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging.
-In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}.
-This leads towards to a featureless state at long times.
-All these concludes that undestanding of heating processes in any timescale and adress them to describe relastic driven system needs the treatment of very rich physics.
+In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy densty \cite{rudner2020}.
+This leads towards a featureless state at long times.
+All these conclude that understanding heating processes in any timescale and addressing them to describe a realistic driven system needs the treatment of very rich physics.
 However, under proper parameter regimes to be discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.
 
-Since there exist a novel regime of closed Floquet systems with quas-isteady state that persists for an exponentially long time \cite{lindner2017}, we assumed that the distribution is to be a time-independent through out our paper.
-The main reason behind the heating of a driven quantum system is absorbtion of photons from the applied field.
+Since there exists a novel regime of closed Floquet systems with a quasi-steady-state that persists for an exponentially long time \cite{lindner2017}, we assumed that the distribution is to be time-independent throughout our paper.
+The main reason behind the heating of a driven quantum system is the absorption of photons from the applied field.
 Thus, to suppress the heating rating we require to control the absorption processes.
 We can achieve this by fine-tuning the driving field.
-Before discuss further, first we need to introduce few energy scales mentioned in the Rudner \textit{et al.} work \cite{rudner2020}, such as photon energy of the driving field $\hbar\omega$, the single-particle bandwidth of the low-lying bands $W$, the local interaction energy scale $U$, and the size of a gap in the spectrum $\Delta$.
+Before discussing further, first, we need to introduce a few energy scales mentioned in the Rudner \textit{et al.} work \cite{rudner2020}, such as the photon energy of the driving field $\hbar\omega$, the single-particle bandwidth of the low-lying bands $W$, the local interaction energy scale $U$, and the size of a gap in the spectrum $\Delta$.
 Here, $\omega$ is the frequency of the driving field.
 As mentioned in Rudner \textit{et al.} work \cite{rudner2020}, there are two promising regimes where the heating rate can be suppressed in a closed Floquet system.
-First regimes is the limit where the applied field's photon energy is larger than the bandwidth of the low-lying bands ($\hbar\omega \gg W$).
-In this case, absorption process only can take place through high-order processes that involve many-particle rearrangements known as many-body resonances \cite{bukov2016,lindner2017,rudner2020}.
-Therefore, these absorptions are heavily suppressed and this leads the system to a equilibrium-like
+The first regime is the limit where the applied field's photon energy is larger than the bandwidth of the low-lying bands ($\hbar\omega \gg W$).
+In this case, the absorption process only can take place through high-order processes that involve many-particle rearrangements known as many-body resonances  \cite{bukov2016,lindner2017,rudner2020}.
+Therefore, these absorptions are heavily suppressed and this leads the system to an equilibrium-like
 state. Now, the system becomes nearly time-independent where the external driving only renormalize the system's parameters rather than manipulating the distribution \cite{wackerlthesis20}.
-This regime has been enabled many researches on driven quantum systems \cite{kitagawa2011,lopez2015,pervishko2015,bukov2015,yudin2016}.
+This regime has been enabled many kinds of research on driven quantum systems \cite{kitagawa2011,lopez2015,pervishko2015,bukov2015,yudin2016}.
 The next possible regime can be identified in gapped systems.
-When the high-lying energy bands are significantly seperated from a set of low-lying bands ($\hbar\omega \ll \Delta$), many photons must be absorbed for a single excitation across the energy gap $\Delta$.
-This results a significant suppression of energy absorbtion processes and heating rates \cite{rudner2020}.
-However, if the local interaction strength $U$ is a dominating energy scale, the interactions make hige impact on particle states in the system.
+When the high-lying energy bands are significantly separated from a set of low-lying bands ($\hbar\omega \ll \Delta$), many photons must be absorbed for a single excitation across the energy gap $\Delta$.
+This results in significant suppression of energy absorption processes and heating rates \cite{rudner2020}.
+However, if the local interaction strength $U$ is a dominating energy scale, the interactions make a huge impact on particle states in the system.
 This makes the study more complicated.
-Thus, to neglect the interactions, the interaction strength should be smaller than the both the bandwidth and the photon energy.
-Connecting the above discussed energy scales and their unique requirements, we can identify a most promising regime for a driven system with steady particle distribution with an increasing energ scale hierarchy: $U \ll W \ll \hbar\omega \ll \Delta$ \cite{wackerlthesis20}.
-This will allow us to consider a quantum system with time-independent paricle distribution function under a driven field in our work.
+Thus, to neglect the interactions, the interaction strength should be smaller than both the bandwidth and the photon energy.
+Connecting the above-discussed energy scales and their unique requirements, we can identify a most promising regime for a driven system with steady particle distribution with an increasing energy scale hierarchy: $U \ll W \ll \hbar\omega \ll \Delta$ \cite{wackerlthesis20}.
+This will allow us to consider a quantum system with a time-independent particle distribution function under a driven field in our work.
 
-Next, it is important to note that, the studies \cite{wackerl20,wackerlthesis20,dini16,endo09} inspire our work have been used this steady state particle distribution function assumption with very low temperature conditions $k_B T \ll \varepsilon_F$.
+Next, it is important to note that, the studies \cite{wackerl20,wackerlthesis20,dini16,endo09} that inspire our work have been used this steady-state particle distribution function assumption with very low-temperature conditions $k_B T \ll \varepsilon_F$.
 Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy level.
-Our main aim was to use a new approch namely Floquet-Drude conductivity \cite{wackerl20} to build our theoritical analysis on the dressed quantum Hall system.
-Since, we expected to compare our theoritical description on the charge transport properties of dressed quantum Hall system with the previous discussions \cite{dini16,endo09}, we used the same assumtions and conditions through out our work as well.
+Our main aim was to use a new approach namely Floquet-Drude conductivity \cite{wackerl20} to build our theoretical analysis on the dressed quantum Hall system.
+In our current work, we expected to compare our theoretical description of the charge transport properties of dressed quantum Hall system with the previous discussions \cite{dini16,endo09}.
+Thus, we used the same assumptions and conditions throughout our work.
 This allowed us to identify the differences of our numerical results with previous outcomes from Refs.
-\cite{dini16,endo09} and seperate the actural effects of the dressing field on quantum Hall systems.
+\cite{dini16,endo09} and separate the actual effects of the dressing field on quantum Hall systems.
 
-It is true that the consideration of impacts on a particle distribution function of a quantum system under microwave fields is essential.
+Indeed, the consideration of impacts on a particle distribution function of a quantum system under microwave fields is essential.
 Nevertheless, as discussed above we can treat the driving field as a pure dressing field with the proper energy and time scale conditions.
-In our study we are not rescticted to microwave field radiation.
-Since we can  employ the above mentioned conditions in our study, we assume that the driving field only renormalize the systems's parameters rather than changing the particle distribution.
+In our study, we are not restricted to microwave field radiation.
+Since we can employ the above-mentioned conditions in our study, we assume that the driving field only renormalizes the Floquet system's parameters rather than changing the particle distribution.
 
-We agree with the reviwer that a more generalized analysis on this topic is required.
-However, the complexity related to the photon absorbtion processes is beyond the scope of the present study, and we plan to address them in our future work.
-We have now clearly mentioned these conditions related to steady particle distribution function in the revised manuscript.
+We agree with the reviewer that a more generalized analysis of this topic is required.
+However, the complexity related to the photon absorption processes is beyond the scope of the present study, and we plan to address them in our future work.
+We have now clearly mentioned these conditions related to the stable particle distribution function in the revised manuscript.
 We included the following text in the revised manuscript.
@@
   However, a full description of a common dressed system requires a proper treatment of photon interactions.
-The complexity attach to these interactions are very high.
-There are various strategies \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020} for overcoming this challenge of heating and for achieving nonequilibrium steady state distribution.
-Working in regimes where heating rates are stongly suppressed enables steady particle distribution function in driven isolated quantum systems.
+The complexity attached to these interactions is very high.
+There are various strategies \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020} for overcoming this challenge of heating and for achieving nonequilibrium steady-state distribution.
+Working in regimes where heating rates are strongly suppressed enables steady particle distribution function in driven isolated quantum systems.
+However, a full description of a common dressed system requires a proper treatment of photon interactions.
+The complexity attached to these interactions is very high.
   As mentioned in Rudner \textit{et al.} \cite{rudner2020}, placing proper conditions on energy and time scales, the distribution function of a Floquet system can be assumed to be steady.
@@
   Let's consider our dressed quantum Hall system under off-resonant conditions \cite{rudner2020,wackerlthesis20}, where photon absorption does not happen.
-Thus, we can assume that the driving field only renormalize the systems's parameters rather than changing the particle distribution function.
-  Additionaly, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our Floquet system
+Thus, we can assume that the driving field only renormalizes the system's parameters rather than changing the particle distribution function.
+  Additionally, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our Floquet system
   \begin{equation} \tag{33}
@@
   where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
-With the aim of compare our results with the outcomes already known in literature \cite{dini16,endo09}, we enfore the low-temperature conditions to the Fermi-Dirac distribution.
+To compare our results with the outcomes already known in the literature \cite{dini16,endo09}, we enforce the low-temperature conditions to the Fermi-Dirac distribution.
   At low-temperatures conditions, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
@@
 
-We thank the reviewer for mention this deficiency. We believe this comment from the reviewer comes mainly from our statement
+We thank the reviewer for mentioning this deficiency. We believe this comment from the reviewer comes mainly from our statement
 
@@
 
-in the Section I (page 1 and page 2) in the manuscript. It is important to note that the Ref. [31] in our previous response to reviewer comments represents the the
-following study:
+in Section I (page 1 and page 2) in the manuscript. It is important to note that the Ref. [31] in our previous response to reviewer comments represents the following study:
 
@@
 
-In our previous manuscript we have represented it as Ref. [57]. In the present response we refer it as \cite{dmitriev09}.
-On a re-reading the previous manuscript, we see that the language we had used here is ambiguous and admit that the statement gives a meaning that is quite different to what we were trying to convey.
+In our previous manuscript, we have represented it as Ref. [57]. In the present response, we refer to it as \cite{dmitriev09}.
+On a re-reading the previous manuscript, we see that the language we had used here is ambiguous and admit that the statement gives a meaning that is quite different from what we were trying to convey.
 
-What we meant to say here is that, work presented in Dmitriev \textit{et al.} \cite{dmitriev09} related to the microwave induced resistance oscillations (MIROs) which can be observed in 2DEG subjected to both magnetic field and low-frequency (microwave) radiation.
+What we meant to say here is that work presented in Dmitriev \textit{et al.} \cite{dmitriev09} related to the microwave-induced resistance oscillations (MIROs) that can be observed in 2DEG subjected to both magnetic field and low-frequency (microwave) radiation.
 As mentioned by the reviewer, Ref.
-\cite{dmitriev09} have properly described the magnto-trasnport properties using the dressed states of electrons as well as the photon interactions.
-On the other hand, if the driving field is in high-frequency regime, we can neglect the photon interactions as mentioned in the response to the first comment.
-In addition, we can identify that the high-frequency and low-frequency radiation lead to two different behaviors of the magnto-trasnport characteristics of dressed quantum Hall systems \cite{dini16}.
+\cite{dmitriev09} have appropriately described the magneto-transport properties using the dressed states of electrons as well as the photon interactions.
+On the other hand, if the driving field is in a high-frequency regime, we can neglect the photon interactions as mentioned in the response to the first comment.
+In addition, we can identify that the high-frequency and low-frequency radiation lead to two different behaviors of the magneto-transport characteristics of dressed quantum Hall systems \cite{dini16}.
 With the low-frequency illumination, particular effects can be observed known as ``zero resistance states" where we can observe increased longitudinal conductivity.
-However, under high-frequency radiation decrease both the broadening of Landau levels and the longitudinal conductivity.
-Our analysis is focused on high-frequency regime where we can significantly suppress the photon interactions in the Floquet system.
-Therefore, we meant to mention this difference between the our study and the Ref.
+However, we can predict a depletion of both the broadening of Landau levels and the longitudinal conductivity under high-frequency radiation.
+Our analysis is focused on a high-frequency regime where we can significantly suppress the photon interactions in the Floquet system.
+Therefore, we meant to mention this difference between our study and the Ref.
 \cite{dmitriev09}.
@@
 
-To incorporate your comment to the manuscript, we removed the above mentioned statement and replaced it with wording which hopefully would convey our meaning better.
+To incorporate your comment into the manuscript, we removed the above-mentioned statement and replaced it with wording which hopefully would convey our meaning better.
 
@@
 These formalisms provide a proper explanation for the experimental observations of MIROs.
-However, these experimental and theoretical works have been linked to effects of low-frequency (microwave) electromagnetic fields which results an increase of longitudinal conductivity.
-  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduce the longitudinal conductivity \cite{dini16}.
-  Since high-frequency radiation only contribute to the suppression of electron scattering, the driving field can be treated as a pure dressing (nonabsorbable) field \cite{dini16}.
+However, these experimental and theoretical works have been linked to the effects of low-frequency (microwave) electromagnetic fields that increase the longitudinal conductivity.
+  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduces the longitudinal conductivity \cite{dini16}.
+  Since high-frequency radiation only contributes to the suppression of electron scattering, the driving field can be treated as a pure dressing (nonabsorbable) field \cite{dini16}.
   Thus, the influence induced by a high-frequency pure dressing field on
-  magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
+  magneto-transport properties of 2DEG quantum Hall system need to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
   }
@@
 
-While we admit that including an analytical description for the effect of long-range impurity potentials is valuable, we need to mentioned about the previous studies \cite{dini16,endo09} influence our work.
-In these studies the transport properties of quantum Hall syatems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
+While we admit that including an analytical description for the effect of long-range impurity potentials is valuable, we need to mention about the previous studies \cite{dini16,endo09} influence our work.
+In these studies, the transport properties of quantum Hall systems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
 The main focus of the present study is to utilize the novel Floquet-Drude conductivity method \cite{wackerl20,wackerlthesis20} to describe dressed quantum Hall systems.
-Since it is required to compare our novel theoritical description of charge transport properties with the previous charge transport studies \cite{dini16,endo09} of quantum Hall systems, we adopted the same assumptions and conditions.
+Since it is required to compare our novel theoretical description of charge transport properties with the previous charge transport studies \cite{dini16,endo09} of quantum Hall systems, we adopted the same assumptions and conditions.
 In addition, Wackel \textit{et al.} \cite{wackerl20} have developed the Floquet-Drude conductivity theory through the short-range impurity potential assumptions.
-Thus, first we need to improve  Floquet-Drude conductivity theory before use it on the dressed quantum Hall system.
-The analysis of the implications from long-range impurity potentials needs a proper treatment of high-order interections.
+Thus, first, we need to improve the Floquet-Drude conductivity theory before using it on the dressed quantum Hall system.
+The analysis of the implications from long-range impurity potentials needs a proper treatment of high-order interactions.
 The discussion of these interactions through Floquet theory is a different topic.
 Thus, it is not discussed in this work.
-However, following the reviewer’s suggestion, we are planning to discuss these effects through our future study.
+However, following the reviewer’s suggestion, we hope to discuss these effects in our future study.
 

### 2022-01-19 response2/response2.tex
Corrections

@@
 This leads to the Floquet engineering of solid-state, atomic, and photonic systems with the basics of Floquet states.
-In general, the powerful thermodynamic rules related to the static systems in thermal equilibrium, cannot be applied to the nonequilibrium regime where Floquet states are defined \cite{seetharam2015}.
+In general, the powerful thermodynamic rules related to the static systems in thermal equilibrium, cannot be applied to the non-equilibrium regime where Floquet states are defined \cite{seetharam2015}.
 Therefore, to achieve the viability of Floquet engineering in fermion systems, it is crucial to understand the conditions for a steady-state particle distribution and it is one of the main challenges in the field.
@@
 Thus, the cooling system needs to be much stronger and this leads to a non-perturbative inclusion of the bath in the system.
-In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasiparticles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
+In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasi-particles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
 However, a fully microscopic description of the heating of a driven system is a rather challenging task due to the multiple processes that need to be investigated.
 It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging.
-In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy densty \cite{rudner2020}.
+In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}.
 This leads towards a featureless state at long times.
@@
 The complexity attached to these interactions is very high.
-There are various strategies \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020} for overcoming this challenge of heating and for achieving nonequilibrium steady-state distribution.
+There are various strategies \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020} for overcoming this challenge of heating and for achieving non-equilibrium steady-state distribution.
 Working in regimes where heating rates are strongly suppressed enables steady particle distribution function in driven isolated quantum systems.
@@
   As mentioned in Rudner \textit{et al.} \cite{rudner2020}, placing proper conditions on energy and time scales, the distribution function of a Floquet system can be assumed to be steady.
-By properly selecting the frequency of the radiation, we can ensure that the interband electron transitions are controlled.
+By properly selecting the frequency of the radiation, we can ensure that the inter-band electron transitions are controlled.
 This leads to significantly suppressed heating rates.
@@
 In particular, Ref.
-[31] demonstrates both the effect of photo excitations of electrons and the dressing of electronic states.}
+[31] demonstrates both the effect of photo excitation of electrons and the dressing of electronic states.}
 
@@
 
-{\color{CadetBlue} “This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs [54-57].
+{\color{CadetBlue} “This inspired investigations on the theoretical description of MIROs, and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs [54-57].
 These formalisms provide a proper explanation for the experimental observations of MIROs.
 However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
-In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
+In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (non-absorbable) field.
 The influence induced by a pure dressing field on
@@
 \cite{dmitriev09}.
-We never meant to say that Dmitriev \textit{et al.} \cite{dmitriev09} only consider the effects of photon excitations.
+We never meant to say that Dmitriev \textit{et al.} \cite{dmitriev09} only consider the effects of photon excitation.
 
@@
   {\color{Red}
-  This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+  This inspired investigations on the theoretical description of MIROs, and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
 These formalisms provide a proper explanation for the experimental observations of MIROs.
@@
   In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduces the longitudinal conductivity \cite{dini16}.
-  Since high-frequency radiation only contributes to the suppression of electron scattering, the driving field can be treated as a pure dressing (nonabsorbable) field \cite{dini16}.
+  Since high-frequency radiation only contributes to the suppression of electron scattering, the driving field can be treated as a pure dressing (non-absorbable) field \cite{dini16}.
   Thus, the influence induced by a high-frequency pure dressing field on

### 2022-01-19 response2/response2.tex
Corrections

@@
 
-We agree with the reviewer that the issue was not addressed properly.
-Therefore, we have made an extensive discussion on the underlying validity of approximation in Eq.~[34].
-First, we discuss the complications we have to face when we are trying to derive a full description of a realistic periodically driven system.
-Later, we clarify the actual conditions and requirements to approximate a stationary particle distribution function for a driven system.
+We agree with the reviewer that the issue was not addressed comprehensively.
+Therefore, we made an extensive discussion on the underlying validity of the approximation in Eq.~[34].
+First, we discuss the complications related to the derivation of full analytical expression for a realistic periodically driven system.
+Later, we clarify the actual conditions and requirements to approximate a stationary particle distribution function for a periodically driven system.
 
-The accessibility of coherent driving fields such as laser opens many interesting capabilities for manipulating quantum systems.
-This leads to the Floquet engineering of solid-state, atomic, and photonic systems with the basics of Floquet states.
+The accessibility of coherent driving fields such as lasers unlock many significant potentials to manipulate quantum systems.
+This leads to the Floquet engineering of solid-state, atomic, and photonic systems with the basis of Floquet states.
 In general, the powerful thermodynamic rules related to the static systems in thermal equilibrium, cannot be applied to the non-equilibrium regime where Floquet states are defined \cite{seetharam2015}.
-Therefore, to achieve the viability of Floquet engineering in fermion systems, it is crucial to understand the conditions for a steady-state particle distribution and it is one of the main challenges in the field.
+Therefore, to achieve the viability of the Floquet engineering in fermion systems, it is crucial to understand the conditions for a steady-state particle distribution.
+Nevertheless, it is one of the main challenges in the field.
 Among previous studies on this topic, a major point of investigation is time scales.
@@
 Although we can consider the intermediate timescales, there would be many physical processes causing the heating of the quantum system.
-A variety of approaches for stabilizing the quantum system under this condition have been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}.
-When the applied driving field gets more powerful the heating caused by the field gets increases.
+A variety of approaches for stabilizing the driven quantum system under this time scales have been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}.
+When the applied driving field gets more powerful, the heating caused by the field gets increases.
 Thus, the cooling system needs to be much stronger and this leads to a non-perturbative inclusion of the bath in the system.
 In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasi-particles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
-However, a fully microscopic description of the heating of a driven system is a rather challenging task due to the multiple processes that need to be investigated.
+However, a complete microscopic description of the heating of a driven system is a rather challenging task due to the multiple processes that need to be investigated.
 It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging.
@@
 
-Since there exists a novel regime of closed Floquet systems with a quasi-steady-state that persists for an exponentially long time \cite{lindner2017}, we assumed that the distribution is to be time-independent throughout our paper.
+Since there exists a novel regime of closed Floquet systems with a quasi-steady-state that persists for an considerably long time \cite{lindner2017}, we assumed that the distribution is to be time-independent throughout our paper.
 The main reason behind the heating of a driven quantum system is the absorption of photons from the applied field.
@@
 This makes the study more complicated.
-Thus, to neglect the interactions, the interaction strength should be smaller than both the bandwidth and the photon energy.
-Connecting the above-discussed energy scales and their unique requirements, we can identify a most promising regime for a driven system with steady particle distribution with an increasing energy scale hierarchy: $U \ll W \ll \hbar\omega \ll \Delta$ \cite{wackerlthesis20}.
+Thus, to neglect the interactions, the interaction strength $U$ should be smaller than both the bandwidth $W$ and the photon energy $\hbar\omega$.
+Connecting the above-discussed energy scales and their unique requirements, we can identify a most promising regime for a driven system with steady particle distribution with an increasing energy scale hierarchy: $U \ll W \ll \hbar\omega \ll \Delta$ \cite{rudner2020,wackerlthesis20}.
 This will allow us to consider a quantum system with a time-independent particle distribution function under a driven field in our work.
 
-Next, it is important to note that, the studies \cite{wackerl20,wackerlthesis20,dini16,endo09} that inspire our work have been used this steady-state particle distribution function assumption with very low-temperature conditions $k_B T \ll \varepsilon_F$.
+Next, it is important to note that, the studies \cite{wackerl20,wackerlthesis20,dini16,endo09} that inspired our work have been used this steady-state particle distribution function assumption with very low-temperature conditions $k_B T \ll \varepsilon_F$.
 Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy level.
 Our main aim was to use a new approach namely Floquet-Drude conductivity \cite{wackerl20} to build our theoretical analysis on the dressed quantum Hall system.
-In our current work, we expected to compare our theoretical description of the charge transport properties of dressed quantum Hall system with the previous discussions \cite{dini16,endo09}.
-Thus, we used the same assumptions and conditions throughout our work.
+Moreover, we expected to compare our theoretical description of the charge transport properties of dressed quantum Hall system with the previous discussions \cite{dini16,endo09}.
+Thus, we used the same steady-state particle distribution assumptions and conditions throughout our work.
 This allowed us to identify the differences of our numerical results with previous outcomes from Refs.
@@
 There are various strategies \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020} for overcoming this challenge of heating and for achieving non-equilibrium steady-state distribution.
-Working in regimes where heating rates are strongly suppressed enables steady particle distribution function in driven isolated quantum systems.
-However, a full description of a common dressed system requires a proper treatment of photon interactions.
-The complexity attached to these interactions is very high.
+Working in regimes where heating rates are strongly suppressed enables steady particle distribution function in the driven isolated quantum systems.
   As mentioned in Rudner \textit{et al.} \cite{rudner2020}, placing proper conditions on energy and time scales, the distribution function of a Floquet system can be assumed to be steady.
@@
 
-{\color{CadetBlue} “This inspired investigations on the theoretical description of MIROs, and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs [54-57].
+“This inspired investigations on the theoretical description of MIROs, and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs [54-57].
 These formalisms provide a proper explanation for the experimental observations of MIROs.
@@
 The influence induced by a pure dressing field on
-magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.”}
+magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.”
 
-in Section I (page 1 and page 2) in the manuscript. It is important to note that the Ref. [31] in our previous response to reviewer comments represents the following study:
+in Section I (page 1 and page 2) in the manuscript. It is important to note that the ``Ref.~[31]'' in our previous response to reviewer comments represents the following study:
 
@@
 
-In our previous manuscript, we have represented it as Ref. [57]. In the present response, we refer to it as \cite{dmitriev09}.
+In our previous manuscript, we have represented it as ``Ref.~[57]''. In the present response, we refer to it as Ref.~\cite{dmitriev09}.
 On a re-reading the previous manuscript, we see that the language we had used here is ambiguous and admit that the statement gives a meaning that is quite different from what we were trying to convey.
@@
 In addition, we can identify that the high-frequency and low-frequency radiation lead to two different behaviors of the magneto-transport characteristics of dressed quantum Hall systems \cite{dini16}.
-With the low-frequency illumination, particular effects can be observed known as ``zero resistance states" where we can observe increased longitudinal conductivity.
+With the low-frequency illumination, particular effects can be observed known as ``zero resistance states" where we can identify a increased longitudinal conductivity.
 However, we can predict a depletion of both the broadening of Landau levels and the longitudinal conductivity under high-frequency radiation.
@@
 
-In addition, we have made the following minor change in language and presentation to match the rest of the manuscript better to the changes done to address the reviewer’s comments.
+In addition, we have made the following minor change in language and presentation to match the rest of the manuscript better to the changes done to address the reviewer’s comment.
 
@@
 
-While we admit that including an analytical description for the effect of long-range impurity potentials is valuable, we need to mention about the previous studies \cite{dini16,endo09} influence our work.
+While we admit that including an analytical description for the effect of long-range impurity potentials is valuable, we need to mention about the previous studies \cite{dini16,endo09} that influenced our work.
 In these studies, the transport properties of quantum Hall systems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
@@
 Since it is required to compare our novel theoretical description of charge transport properties with the previous charge transport studies \cite{dini16,endo09} of quantum Hall systems, we adopted the same assumptions and conditions.
-In addition, Wackel \textit{et al.} \cite{wackerl20} have developed the Floquet-Drude conductivity theory through the short-range impurity potential assumptions.
-Thus, first, we need to improve the Floquet-Drude conductivity theory before using it on the dressed quantum Hall system.
+In addition, Wackel \textit{et al.} \cite{wackerl20} have derived the Floquet-Drude conductivity theory with the short-range impurity potential assumption.
+Thus, we need to improve the Floquet-Drude conductivity theory before we using it on the dressed quantum Hall system with long-range impurity conditions.
 The analysis of the implications from long-range impurity potentials needs a proper treatment of high-order interactions.
-The discussion of these interactions through Floquet theory is a different topic.
+The discussion of these interactions through the Floquet theory is a different topic.
 Thus, it is not discussed in this work.

### 2022-01-19 paper/dressed_quantum_hall_sub3/dressed_quantum_hall_sub3.tex
Add new submission and correct the response

--- 2021-11-19 paper/dressed_quantum_hall_sub2/dressed_quantum_hall_sub2.tex
@@
 \end{equation}
-We consider a dressed quantum Hall system under off-resonant condition, where photon absorption does not happen.
-Therefore, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our system
-\begin{equation} \label{eq:33}
+{\color{Red} To further evaluate the conductivity expression, we must specify the distribution function.
+Generic interacting Floquet systems absorb photons from the radiation and tend to heat up \cite{seetharam2019,rudner2020}.
+However, a full description of a common dressed system requires a proper treatment of photon interactions.
+The complexity attached to these interactions is very high.
+There are various strategies \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020} for overcoming this challenge of heating and for achieving non-equilibrium steady-state distribution.
+Working in regimes where heating rates are strongly suppressed enables steady particle distribution function in the driven isolated quantum systems.
+As mentioned in Rudner \textit{et al.} \cite{rudner2020}, placing proper conditions on energy and time scales, the distribution function of a Floquet system can be assumed to be steady.
+By properly selecting the frequency of the radiation, we can ensure that the inter-band electron transitions are controlled.
+This leads to significantly suppressed heating rates.
+Let's consider our dressed quantum Hall system under off-resonant conditions \cite{rudner2020,wackerlthesis20}, where photon absorption does not happen.
+Thus, we can assume that the driving field only renormalizes the system's parameters rather than changing the particle distribution function.
+Additionally, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our Floquet system
+\begin{equation} \tag{33}
   f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
@@
 where $k_B$ is the Boltzmann constant, $T$ is the absolute temperature, and $\varepsilon_F$ is the Fermi energy of the system.
-At low-temperatures, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function
-\begin{equation} \label{eq:34}
+To compare our results with the outcomes already known in the literature \cite{dini16,endo09}, we enforce the low-temperature conditions to the Fermi-Dirac distribution.
+At low-temperatures conditions, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
+\begin{equation} \tag{34}
   - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
 \end{equation}
+}
 Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
@@
 K.H wish to acknowledge the members of A$\chi$L at Monash University for their encouragement and support and specially T.N.
-Perera and R.T.Wijesekara for insightful discussions.
+Perera and R.T.
+Wijesekara for insightful discussions.
 The work of K.H is supported by the Australian Government Research Training Program (RTP) Scholarship and the Monash University Institute of Graduate Research.
@@
 %Control: production of eprint (0) enabled
+
 \providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}%

### 2022-01-19 response2/response2.tex
Add new submission and correct the response

@@
 A variety of approaches for stabilizing the driven quantum system under this time scales have been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}.
-When the applied driving field gets more powerful, the heating caused by the field gets increases.
+When the applied driving field gets more powerful, the heating caused by the field increases.
 Thus, the cooling system needs to be much stronger and this leads to a non-perturbative inclusion of the bath in the system.
@@
 It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging.
-In the absence of interaction to an external environment, many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}.
-This leads towards a featureless state at long times.
+In the absence of interaction to an external environment, a many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}.
+This leads towards a featureless state at long time scales.
 All these conclude that understanding heating processes in any timescale and addressing them to describe a realistic driven system needs the treatment of very rich physics.
-However, under proper parameter regimes to be discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.
+However, under proper parameter regimes discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.
 
-Since there exists a novel regime of closed Floquet systems with a quasi-steady-state that persists for an considerably long time \cite{lindner2017}, we assumed that the distribution is to be time-independent throughout our paper.
+Since there exists a novel regime of closed Floquet systems with a quasi-steady-state that persists for an considerably long time \cite{lindner2017}, we assume that the distribution is time-independent throughout our paper.
 The main reason behind the heating of a driven quantum system is the absorption of photons from the applied field.
@@
 
-Next, it is important to note that, the studies \cite{wackerl20,wackerlthesis20,dini16,endo09} that inspired our work have been used this steady-state particle distribution function assumption with very low-temperature conditions $k_B T \ll \varepsilon_F$.
+Next, it is important to note that, the studies \cite{wackerl20,wackerlthesis20,dini16,endo09} which inspired our work have  used the steady-state particle distribution function assumption with very low-temperature conditions $k_B T \ll \varepsilon_F$.
 Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy level.
@@
 In our previous manuscript, we have represented it as ``Ref.~[57]''. In the present response, we refer to it as Ref.~\cite{dmitriev09}.
-On a re-reading the previous manuscript, we see that the language we had used here is ambiguous and admit that the statement gives a meaning that is quite different from what we were trying to convey.
+On re-reading the previous manuscript, we see that the language we had used here is ambiguous and admit that the statement gives a meaning that is quite different from what we were trying to convey.
 
-What we meant to say here is that work presented in Dmitriev \textit{et al.} \cite{dmitriev09} related to the microwave-induced resistance oscillations (MIROs) that can be observed in 2DEG subjected to both magnetic field and low-frequency (microwave) radiation.
+What we meant to say here is that work presented in Dmitriev \textit{et al.} \cite{dmitriev09} only relates to the effects induced from a low-frequency (microwave) radiation, specially the microwave-induced resistance oscillations (MIROs).
+The MIROs can be observed in 2DEG subjected to both magnetic field and low-frequency (microwave) radiation.
 As mentioned by the reviewer, Ref.
@@
 
-To incorporate your comment into the manuscript, we removed the above-mentioned statement and replaced it with wording which hopefully would convey our meaning better.
+To incorporate your comment into the manuscript, we removed the above-mentioned statement and replaced it with wordings which hopefully would convey our meaning better.
 
@@
 
-While we admit that including an analytical description for the effect of long-range impurity potentials is valuable, we need to mention about the previous studies \cite{dini16,endo09} that influenced our work.
-In these studies, the transport properties of quantum Hall systems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
+We admit that including an analytical description for the effect of long-range impurity potentials is valuable.
+However, in the studies \cite{dini16,endo09} that influenced our work, the transport properties of quantum Hall systems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
 The main focus of the present study is to utilize the novel Floquet-Drude conductivity method \cite{wackerl20,wackerlthesis20} to describe dressed quantum Hall systems.
@@
 In addition, Wackel \textit{et al.} \cite{wackerl20} have derived the Floquet-Drude conductivity theory with the short-range impurity potential assumption.
-Thus, we need to improve the Floquet-Drude conductivity theory before we using it on the dressed quantum Hall system with long-range impurity conditions.
+Thus, we need to improve the Floquet-Drude conductivity theory before using it on the dressed quantum Hall system with long-range impurity conditions.
 The analysis of the implications from long-range impurity potentials needs a proper treatment of high-order interactions.

### 2022-01-19 paper/dressed_quantum_hall_sub3/dressed_quantum_hall_sub3.tex
Finalize the paper with red text

@@
 Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
-This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+{\color{Red}
+This inspired investigations on the theoretical description of MIROs, and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
 These formalisms provide a proper explanation for the experimental observations of MIROs.
-However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
-In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
-The influence induced by a pure dressing field on
-magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
+However, these experimental and theoretical works have been linked to the effects of low-frequency (microwave) electromagnetic fields that increase the longitudinal conductivity.
+In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system leads to different behavior that reduces the longitudinal conductivity \cite{dini16}.
+Since high-frequency radiation only contributes to the suppression of electron scattering, the driving field can be treated as a pure dressing (non-absorbable) field \cite{dini16}.
+Thus, the influence induced by a high-frequency pure dressing field on
+magneto-transport properties of 2DEG quantum Hall system need to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.}
 Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
@@
 Additionally, we can select the Fermi-Dirac distribution as our partial distribution function ($f$) for our Floquet system
-\begin{equation} \tag{33}
+\begin{equation} \label{eq:33}
   f(\varepsilon) = \frac{1}{\exp[(\varepsilon - \varepsilon_F)/k_B T]+1},
@@
 At low-temperatures conditions, i.e., $k_BT \ll \varepsilon_F$, the derivative of this distribution is sharply peaked around the Fermi energy, and can be approximated by a delta function \cite{endo09}
-\begin{equation} \tag{34}
+\begin{equation} \label{eq:34}
   - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
@@
 
+\begin{figure}[t]
+\includegraphics[scale=0.54]{fig_4_conductivity_with_fermi_level}
+\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\label{fig:4}
+\end{figure}
+
+\begin{figure}[t]
+\includegraphics[scale=0.54]{fig_5_conductivity_with_fermi_level_zoomed}
+\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
+In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
+\label{fig:5}
+\end{figure}
+
 By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
@@
 
-\begin{figure}[t]
-\includegraphics[scale=0.54]{fig_4_conductivity_with_fermi_level}
-\caption{ Normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a  frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:4}
-\end{figure}
-
-\begin{figure}[t]
-\includegraphics[scale=0.54]{fig_5_conductivity_with_fermi_level_zoomed}
-\caption{$3$rd Landau level’s normalized longitudinal conductivity $\widetilde{\sigma}^{xx}$ against Fermi level $X_F$ with different intensities $I$ of the external dressing field in a GaAs-based quantum well under a nonoscillating magnetic field with $B = \SI{1.2}{\tesla}$, dressing field with a frequency of $\omega =\SI{2e12}{\radian\per\second}$ and $I_0 =\SI{100}{\watt\per\square\centi\metre}$.
-In this calculation, we have assumed that the natural  broadening of $0$-th Landau level $\Gamma_0$ is $\SI{0.24}{\milli\eV}$.}
-\label{fig:5}
-\end{figure}
-
 These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.
@@
 magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems.
-However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
+{\color{Red}
+However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on low-frequency fields.}
 It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
-In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions.
+{\color{Red}
+In our case, the applied dressing field is in the high-frequency regime where we can neglect the photon interactions.
+The only influence of the electromagnetic field is the suppression of electron scattering.}
 This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems.
@@
   {2018})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Seetharam}\ \emph {et~al.}(2019)\citenamefont
+  {Seetharam}, \citenamefont {Bardyn}, \citenamefont {Lindner}, \citenamefont
+  {Rudner},\ and\ \citenamefont {Refael}}]{seetharam2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~I.}\ \bibnamefont
+  {Seetharam}}, \bibinfo {author} {\bibfnamefont {C.-E.}\ \bibnamefont
+  {Bardyn}}, \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont {Lindner}},
+  \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}}, \ and\
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Refael}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev.B}\ }\textbf {\bibinfo
+  {volume} {99}},\ \bibinfo {pages} {014307} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rudner}\ and\ \citenamefont
+  {Lindner}(2020)}]{rudner2020}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
+  {Rudner}}\ and\ \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont
+  {Lindner}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nat.
+  Rev. Phys.}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {229}
+  (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lindner}\ \emph {et~al.}(2017)\citenamefont
+  {Lindner}, \citenamefont {Berg},\ and\ \citenamefont {Rudner}}]{lindner2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont
+  {Lindner}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Berg}}, \
+  and\ \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
+  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {011018} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bukov}\ \emph {et~al.}(2015)\citenamefont {Bukov},
+  \citenamefont {D'Alessio},\ and\ \citenamefont {Polkovnikov}}]{bukov2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Bukov}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {D'Alessio}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Polkovnikov}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Adv. Phys.}\
+  }\textbf {\bibinfo {volume} {64}},\ \bibinfo {pages} {139} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Eckardt}\ and\ \citenamefont
+  {Anisimovas}(2015)}]{eckardt2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Eckardt}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Anisimovas}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {New J. Phys.}\ }\textbf {\bibinfo {volume} {17}},\ \bibinfo {pages} {093039}
+  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kuwahara}\ \emph {et~al.}(2016)\citenamefont
+  {Kuwahara}, \citenamefont {Mori},\ and\ \citenamefont
+  {Saito}}]{kuwahara2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Kuwahara}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Mori}}, \
+  and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Saito}},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Ann. Phys.}\
+  }\textbf {\bibinfo {volume} {367}},\ \bibinfo {pages} {96} (\bibinfo {year}
+  {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Abanin}\ \emph {et~al.}(2017)\citenamefont {Abanin},
+  \citenamefont {De~Roeck}, \citenamefont {Ho},\ and\ \citenamefont
+  {Huveneers}}]{abanin2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+  {Abanin}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {De~Roeck}},
+  \bibinfo {author} {\bibfnamefont {W.~W.}\ \bibnamefont {Ho}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Huveneers}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys.Rev. B}\ }\textbf {\bibinfo
+  {volume} {95}},\ \bibinfo {pages} {014112} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mori}\ \emph {et~al.}(2018)\citenamefont {Mori},
+  \citenamefont {Ikeda}, \citenamefont {Kaminishi},\ and\ \citenamefont
+  {Ueda}}]{mori2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Mori}}, \bibinfo {author} {\bibfnamefont {T.~N.}\ \bibnamefont {Ikeda}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Kaminishi}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ueda}},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {J. Phys. B: At. Mol. Opt. Phys}\
+  }\textbf {\bibinfo {volume} {51}},\ \bibinfo {pages} {112001} (\bibinfo
+  {year} {2018})}\BibitemShut {NoStop}%
 \end{thebibliography}%

### 2022-01-20 paper/dressed_quantum_hall_sub3/dressed_quantum_hall_sub3.tex
Correction references
Finalize paper and response for sub3

@@
 {\color{Red}
-This inspired investigations on the theoretical description of MIROs, and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+This inspired investigations on the theoretical description of MIROs and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
 These formalisms provide a proper explanation for the experimental observations of MIROs.
@@
 \end{figure}
-
 Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~\ref{fig:2} and Fig.~\ref{fig:3}.
@@
 {\color{Red} To further evaluate the conductivity expression, we must specify the distribution function.
-Generic interacting Floquet systems absorb photons from the radiation and tend to heat up \cite{seetharam2019,rudner2020}.
-However, a full description of a common dressed system requires a proper treatment of photon interactions.
+Generic interacting Floquet systems absorb photons from the radiation and tend to heat \cite{seetharam2019,rudner2020}.
+However, a complete description of a common dressed system requires a proper treatment of photon interactions.
 The complexity attached to these interactions is very high.
@@
   - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
-\end{equation}
-}
-Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
+\end{equation}}Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
 \begin{equation} \label{eq:35}
@@
 %Control: production of eprint (0) enabled
-
 \providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}%
-\begin{thebibliography}{98}%
+\begin{thebibliography}{106}%
 \makeatletter
@@
   {pages} {235124} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Seetharam}\ \emph {et~al.}(2019)\citenamefont
+  {Seetharam}, \citenamefont {Bardyn}, \citenamefont {Lindner}, \citenamefont
+  {Rudner},\ and\ \citenamefont {Refael}}]{seetharam2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~I.}\ \bibnamefont
+  {Seetharam}}, \bibinfo {author} {\bibfnamefont {C.-E.}\ \bibnamefont
+  {Bardyn}}, \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont {Lindner}},
+  \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}},\ and\
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Refael}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.99.014307} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev.B}\ }\textbf {\bibinfo {volume} {99}},\ \bibinfo {pages}
+  {014307} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rudner}\ and\ \citenamefont
+  {Lindner}(2020)}]{rudner2020}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
+  {Rudner}}\ and\ \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont
+  {Lindner}},\ }\href {https://doi.org/10.1038/s42254-020-0170-z} {\bibfield
+  {journal} {\bibinfo  {journal} {Nat. Rev. Phys.}\ }\textbf {\bibinfo {volume}
+  {2}},\ \bibinfo {pages} {229} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lindner}\ \emph {et~al.}(2017)\citenamefont
+  {Lindner}, \citenamefont {Berg},\ and\ \citenamefont {Rudner}}]{lindner2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont
+  {Lindner}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Berg}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}},\ }\href
+  {https://doi.org/10.1103/PhysRevX.7.011018} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages}
+  {011018} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bukov}\ \emph {et~al.}(2015)\citenamefont {Bukov},
+  \citenamefont {D'Alessio},\ and\ \citenamefont {Polkovnikov}}]{bukov2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Bukov}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {D'Alessio}},\
+  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Polkovnikov}},\
+  }\href {https://doi.org/10.1080/00018732.2015.1055918} {\bibfield  {journal}
+  {\bibinfo  {journal} {Adv. Phys.}\ }\textbf {\bibinfo {volume} {64}},\
+  \bibinfo {pages} {139} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Eckardt}\ and\ \citenamefont
+  {Anisimovas}(2015)}]{eckardt2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Eckardt}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Anisimovas}},\ }\href {https://doi.org/10.1088/1367-2630/17/9/093039}
+  {\bibfield  {journal} {\bibinfo  {journal} {New J. Phys.}\ }\textbf {\bibinfo
+  {volume} {17}},\ \bibinfo {pages} {093039} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kuwahara}\ \emph {et~al.}(2016)\citenamefont
+  {Kuwahara}, \citenamefont {Mori},\ and\ \citenamefont
+  {Saito}}]{kuwahara2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Kuwahara}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Mori}},\
+  and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Saito}},\ }\href
+  {https://doi.org/10.1016/j.aop.2016.01.012} {\bibfield  {journal} {\bibinfo
+  {journal} {Ann. Phys.}\ }\textbf {\bibinfo {volume} {367}},\ \bibinfo {pages}
+  {96} (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Abanin}\ \emph {et~al.}(2017)\citenamefont {Abanin},
+  \citenamefont {De~Roeck}, \citenamefont {Ho},\ and\ \citenamefont
+  {Huveneers}}]{abanin2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+  {Abanin}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {De~Roeck}},
+  \bibinfo {author} {\bibfnamefont {W.~W.}\ \bibnamefont {Ho}},\ and\ \bibinfo
+  {author} {\bibfnamefont {F.}~\bibnamefont {Huveneers}},\ }\href
+  {https://doi.org/10.1103/PhysRevB.95.014112} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys.Rev. B}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages}
+  {014112} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Mori}\ \emph {et~al.}(2018)\citenamefont {Mori},
+  \citenamefont {Ikeda}, \citenamefont {Kaminishi},\ and\ \citenamefont
+  {Ueda}}]{mori2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Mori}}, \bibinfo {author} {\bibfnamefont {T.~N.}\ \bibnamefont {Ikeda}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Kaminishi}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ueda}},\ }\href
+  {https://doi.org/10.1088/1361-6455/aabcdf} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Phys. B: At. Mol. Opt. Phys}\ }\textbf {\bibinfo {volume}
+  {51}},\ \bibinfo {pages} {112001} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Wakabayashi}\ and\ \citenamefont
@@
   {2018})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Seetharam}\ \emph {et~al.}(2019)\citenamefont
-  {Seetharam}, \citenamefont {Bardyn}, \citenamefont {Lindner}, \citenamefont
-  {Rudner},\ and\ \citenamefont {Refael}}]{seetharam2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~I.}\ \bibnamefont
-  {Seetharam}}, \bibinfo {author} {\bibfnamefont {C.-E.}\ \bibnamefont
-  {Bardyn}}, \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont {Lindner}},
-  \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}}, \ and\
-  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Refael}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev.B}\ }\textbf {\bibinfo
-  {volume} {99}},\ \bibinfo {pages} {014307} (\bibinfo {year}
-  {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rudner}\ and\ \citenamefont
-  {Lindner}(2020)}]{rudner2020}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
-  {Rudner}}\ and\ \bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont
-  {Lindner}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nat.
-  Rev. Phys.}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {229}
-  (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lindner}\ \emph {et~al.}(2017)\citenamefont
-  {Lindner}, \citenamefont {Berg},\ and\ \citenamefont {Rudner}}]{lindner2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~H.}\ \bibnamefont
-  {Lindner}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Berg}}, \
-  and\ \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont {Rudner}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\
-  }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {011018} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bukov}\ \emph {et~al.}(2015)\citenamefont {Bukov},
-  \citenamefont {D'Alessio},\ and\ \citenamefont {Polkovnikov}}]{bukov2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Bukov}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {D'Alessio}}, \
-  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Polkovnikov}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Adv. Phys.}\
-  }\textbf {\bibinfo {volume} {64}},\ \bibinfo {pages} {139} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Eckardt}\ and\ \citenamefont
-  {Anisimovas}(2015)}]{eckardt2015}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Eckardt}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Anisimovas}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {New J. Phys.}\ }\textbf {\bibinfo {volume} {17}},\ \bibinfo {pages} {093039}
-  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kuwahara}\ \emph {et~al.}(2016)\citenamefont
-  {Kuwahara}, \citenamefont {Mori},\ and\ \citenamefont
-  {Saito}}]{kuwahara2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Kuwahara}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Mori}}, \
-  and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Saito}},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Ann. Phys.}\
-  }\textbf {\bibinfo {volume} {367}},\ \bibinfo {pages} {96} (\bibinfo {year}
-  {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Abanin}\ \emph {et~al.}(2017)\citenamefont {Abanin},
-  \citenamefont {De~Roeck}, \citenamefont {Ho},\ and\ \citenamefont
-  {Huveneers}}]{abanin2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
-  {Abanin}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {De~Roeck}},
-  \bibinfo {author} {\bibfnamefont {W.~W.}\ \bibnamefont {Ho}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {F.}~\bibnamefont {Huveneers}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys.Rev. B}\ }\textbf {\bibinfo
-  {volume} {95}},\ \bibinfo {pages} {014112} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Mori}\ \emph {et~al.}(2018)\citenamefont {Mori},
-  \citenamefont {Ikeda}, \citenamefont {Kaminishi},\ and\ \citenamefont
-  {Ueda}}]{mori2018}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Mori}}, \bibinfo {author} {\bibfnamefont {T.~N.}\ \bibnamefont {Ikeda}},
-  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Kaminishi}}, \ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Ueda}},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {J. Phys. B: At. Mol. Opt. Phys}\
-  }\textbf {\bibinfo {volume} {51}},\ \bibinfo {pages} {112001} (\bibinfo
-  {year} {2018})}\BibitemShut {NoStop}%
 \end{thebibliography}%

### 2022-01-20 response2/response2.tex
Finalize paper and response for sub3

@@
 We would like to thank the reviewer for his/her insightful comments on the theoretical foundations of our model.
-Accordingly, we have been able to significantly refine our discussion on the underlying assumptions and corresponding physical conditions of our system.
+Accordingly, we have been able to significantly refine our discussion on our system's underlying assumptions and corresponding physical conditions.
 We hence believe that our response and the corresponding changes we incorporated into the manuscript would be sufficient to clarify the issues raised.
@@
 
-We agree with the reviewer that the issue was not addressed comprehensively.
-Therefore, we made an extensive discussion on the underlying validity of the approximation in Eq.~[34].
-First, we discuss the complications related to the derivation of full analytical expression for a realistic periodically driven system.
+We agree with the reviewer that we did not address the issue comprehensively.
+Therefore, we extensively discussed the underlying validity of the approximation in Eq.~[34].
+First, we discuss the complications related to deriving a full analytical expression for a realistic periodically driven system.
 Later, we clarify the actual conditions and requirements to approximate a stationary particle distribution function for a periodically driven system.
 
-The accessibility of coherent driving fields such as lasers unlock many significant potentials to manipulate quantum systems.
+The accessibility of coherent driving fields such as lasers unlocks many significant potentials to manipulate quantum systems.
 This leads to the Floquet engineering of solid-state, atomic, and photonic systems with the basis of Floquet states.
-In general, the powerful thermodynamic rules related to the static systems in thermal equilibrium, cannot be applied to the non-equilibrium regime where Floquet states are defined \cite{seetharam2015}.
-Therefore, to achieve the viability of the Floquet engineering in fermion systems, it is crucial to understand the conditions for a steady-state particle distribution.
+The powerful thermodynamic rules related to the static systems in thermal equilibrium cannot be applied to the non-equilibrium regime where Floquet states are defined \cite{seetharam2015}.
+Therefore, to achieve the viability of the Floquet engineering in fermion systems, it is crucial to understand the conditions for steady-state particle distribution.
 Nevertheless, it is one of the main challenges in the field.
-Among previous studies on this topic, a major point of investigation is time scales.
-As an example, if the switch-on of the driving field is not far from the past, the distribution function of a quantum system will highly depend on the switching-on protocol of the periodic driving \cite{dehghani2014}.
+Among previous studies on this topic, a significant point of investigation is time scales.
+For example, if the switch-on of the driving field is not far from the past, the distribution function of a quantum system will highly depend on the switching-on protocol of the periodic driving \cite{dehghani2014}.
 Although we can consider the intermediate timescales, there would be many physical processes causing the heating of the quantum system.
-A variety of approaches for stabilizing the driven quantum system under this time scales have been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}.
+Various of approaches for stabilizing the driven quantum system under this time scale have been investigated using bath engineering methods \cite{seetharam2015,weidinger2017,seetharam2019,rudner2020}.
 When the applied driving field gets more powerful, the heating caused by the field increases.
-Thus, the cooling system needs to be much stronger and this leads to a non-perturbative inclusion of the bath in the system.
-In addition, in the previous work of Genske \textit{et al.} \cite{genske2015}, the dynamics of the Floquet quasi-particles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
+Thus, the cooling system needs to be much more rubust, leading to a non-perturbative inclusion of the bath in the system.
+In addition, Genske \textit{et al.}'s previous work \cite{genske2015}, the dynamics of the Floquet quasi-particles and their scattering processes have been addressed semi-classically using the Boltzmann approach.
 However, a complete microscopic description of the heating of a driven system is a rather challenging task due to the multiple processes that need to be investigated.
 It is important to notice that, the behavior of Floquet states under the long timescale conditions are even more challenging.
-In the absence of interaction to an external environment, a many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}.
+Without interaction with an external environment, a many-body driven quantum system will absorb energy from the driving field and increase the local entropy density \cite{rudner2020}.
 This leads towards a featureless state at long time scales.
 All these conclude that understanding heating processes in any timescale and addressing them to describe a realistic driven system needs the treatment of very rich physics.
-However, under proper parameter regimes discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.
+However, under the proper parameter regimes discussed below, we can achieve a nearly quasi-steady state in isolated quantum systems on short to intermediate timescales \cite{lindner2017,bukov2015,eckardt2015,kuwahara2016,abanin2017,mori2018,rudner2020}.
 
-Since there exists a novel regime of closed Floquet systems with a quasi-steady-state that persists for an considerably long time \cite{lindner2017}, we assume that the distribution is time-independent throughout our paper.
-The main reason behind the heating of a driven quantum system is the absorption of photons from the applied field.
-Thus, to suppress the heating rating we require to control the absorption processes.
+Since a novel regime of closed Floquet systems with a quasi-steady-state that persists for a considerably long time \cite{lindner2017}, we assume that the distribution is time-independent throughout our paper.
+The main reason for  heating of a driven quantum system is the absorption of photons from the applied field.
+Thus, to suppress the heating rating, we must control the absorption processes.
 We can achieve this by fine-tuning the driving field.
@@
 The first regime is the limit where the applied field's photon energy is larger than the bandwidth of the low-lying bands ($\hbar\omega \gg W$).
-In this case, the absorption process only can take place through high-order processes that involve many-particle rearrangements known as many-body resonances  \cite{bukov2016,lindner2017,rudner2020}.
-Therefore, these absorptions are heavily suppressed and this leads the system to an equilibrium-like
+In this case, the absorption process can only occur through high-order processes that involve many-particle rearrangements known as many-body resonances  \cite{bukov2016,lindner2017,rudner2020}.
+Therefore, these absorptions are heavily suppressed, leading the system to an equilibrium-like
 state. Now, the system becomes nearly time-independent where the external driving only renormalize the system's parameters rather than manipulating the distribution \cite{wackerlthesis20}.
@@
 The next possible regime can be identified in gapped systems.
-When the high-lying energy bands are significantly separated from a set of low-lying bands ($\hbar\omega \ll \Delta$), many photons must be absorbed for a single excitation across the energy gap $\Delta$.
-This results in significant suppression of energy absorption processes and heating rates \cite{rudner2020}.
-However, if the local interaction strength $U$ is a dominating energy scale, the interactions make a huge impact on particle states in the system.
+When the high lying energy bands are significantly separated from a set of low-lying bands ($\hbar\omega \ll \Delta$), many photons must be absorbed for a single excitation across the energy gap $\Delta$.
+This significantly depletes energy absorption processes and heating rates \cite{rudner2020}.
+However, if the local interaction strength $U$ is a dominating energy scale, the interactions impact particle states in the system.
 This makes the study more complicated.
-Thus, to neglect the interactions, the interaction strength $U$ should be smaller than both the bandwidth $W$ and the photon energy $\hbar\omega$.
+Thus, to neglect the interactions, the interaction strength $U$ should be smaller than  the bandwidth $W$ and the photon energy $\hbar\omega$.
 Connecting the above-discussed energy scales and their unique requirements, we can identify a most promising regime for a driven system with steady particle distribution with an increasing energy scale hierarchy: $U \ll W \ll \hbar\omega \ll \Delta$ \cite{rudner2020,wackerlthesis20}.
@@
 
-Next, it is important to note that, the studies \cite{wackerl20,wackerlthesis20,dini16,endo09} which inspired our work have  used the steady-state particle distribution function assumption with very low-temperature conditions $k_B T \ll \varepsilon_F$.
+Next, it is important to note that the studies \cite{wackerl20,wackerlthesis20,dini16,endo09} which inspired our work have  used the steady-state particle distribution function assumption with very low-temperature conditions $k_B T \ll \varepsilon_F$.
 Here, $k_B$ is the Boltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy level.
-Our main aim was to use a new approach namely Floquet-Drude conductivity \cite{wackerl20} to build our theoretical analysis on the dressed quantum Hall system.
+Our main aim was to use a new approach, namely Floquet-Drude conductivity \cite{wackerl20} to build our theoretical analysis on the dressed quantum Hall system.
 Moreover, we expected to compare our theoretical description of the charge transport properties of dressed quantum Hall system with the previous discussions \cite{dini16,endo09}.
@@
 
-Indeed, the consideration of impacts on a particle distribution function of a quantum system under microwave fields is essential.
-Nevertheless, as discussed above we can treat the driving field as a pure dressing field with the proper energy and time scale conditions.
+Indeed, considering impacts on a particle distribution function of a quantum system under microwave fields is essential.
+Nevertheless, as discussed above, we can treat the driving field as a pure dressing field with the proper energy and time scale conditions.
 In our study, we are not restricted to microwave field radiation.
@@
 However, the complexity related to the photon absorption processes is beyond the scope of the present study, and we plan to address them in our future work.
-We have now clearly mentioned these conditions related to the stable particle distribution function in the revised manuscript.
+We have now clearly mentioned these conditions related to the revised manuscript`s stable particle distribution function.
 We included the following text in the revised manuscript.
@@
   To further evaluate the conductivity expression, we must specify the distribution function.
-Generic interacting Floquet systems absorb photons from the radiation and tend to heat up \cite{seetharam2019,rudner2020}.
-  However, a full description of a common dressed system requires a proper treatment of photon interactions.
+Generic interacting Floquet systems absorb photons from the radiation and tend to heat \cite{seetharam2019,rudner2020}.
+  However, a complete description of a common dressed system requires a proper treatment of photon interactions.
 The complexity attached to these interactions is very high.
@@
 
-What we meant to say here is that work presented in Dmitriev \textit{et al.} \cite{dmitriev09} only relates to the effects induced from a low-frequency (microwave) radiation, specially the microwave-induced resistance oscillations (MIROs).
+What we meant to say here is that work presented in Dmitriev \textit{et al.} \cite{dmitriev09} only relates to the effects induced from a low-frequency (microwave) radiation, especially the microwave-induced resistance oscillations (MIROs).
 The MIROs can be observed in 2DEG subjected to both magnetic field and low-frequency (microwave) radiation.
@@
 In addition, we can identify that the high-frequency and low-frequency radiation lead to two different behaviors of the magneto-transport characteristics of dressed quantum Hall systems \cite{dini16}.
-With the low-frequency illumination, particular effects can be observed known as ``zero resistance states" where we can identify a increased longitudinal conductivity.
+With the low-frequency illumination, particular effects can be observed known as ``zero resistance states" where we can identify an increased longitudinal conductivity.
 However, we can predict a depletion of both the broadening of Landau levels and the longitudinal conductivity under high-frequency radiation.
@@
 
-To incorporate your comment into the manuscript, we removed the above-mentioned statement and replaced it with wordings which hopefully would convey our meaning better.
+To incorporate your comment into the manuscript, we removed the statement as mentioned above and replaced it with wordings which hopefully would convey our meaning better.
 
@@
   {\color{Red}
-  This inspired investigations on the theoretical description of MIROs, and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
+  This inspired investigations on the theoretical description of MIROs and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
 These formalisms provide a proper explanation for the experimental observations of MIROs.
@@
 We admit that including an analytical description for the effect of long-range impurity potentials is valuable.
-However, in the studies \cite{dini16,endo09} that influenced our work, the transport properties of quantum Hall systems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
+In the studies \cite{dini16,endo09} that influenced our work, the transport properties of quantum Hall systems and dressed quantum Hall systems have been investigated with the assumption of short-range impurity potentials.
 The main focus of the present study is to utilize the novel Floquet-Drude conductivity method \cite{wackerl20,wackerlthesis20} to describe dressed quantum Hall systems.
@@
 The analysis of the implications from long-range impurity potentials needs a proper treatment of high-order interactions.
-The discussion of these interactions through the Floquet theory is a different topic.
-Thus, it is not discussed in this work.
-However, following the reviewer’s suggestion, we hope to discuss these effects in our future study.
+The discussion of these interactions through the Floquet theory is a different topic, and beyond the scope of the present study.
+Given the importance of this topic, we will certainly revisit it in our future studies.
 

### 2022-01-21 paper/submission3/manuscript/dressed_quantum_hall_sub3.tex
Finalize paper

--- 2022-01-20 paper/dressed_quantum_hall_sub3/dressed_quantum_hall_sub3.tex
@@
 Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
-{\color{Red}
 This inspired investigations on the theoretical description of MIROs and several semi-classical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}.
@@
 Thus, the influence induced by a high-frequency pure dressing field on
-magneto-transport properties of 2DEG quantum Hall system need to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.}
+magneto-transport properties of 2DEG quantum Hall system need to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
 Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
@@
 \end{equation}
-{\color{Red} To further evaluate the conductivity expression, we must specify the distribution function.
+To further evaluate the conductivity expression, we must specify the distribution function.
 Generic interacting Floquet systems absorb photons from the radiation and tend to heat \cite{seetharam2019,rudner2020}.
@@
   - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).
-\end{equation}}Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
+\end{equation}
+Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(\ref{eq:31}) leads to
 \begin{equation} \label{eq:35}
@@
 magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems.
-{\color{Red}
-However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on low-frequency fields.}
+However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on low-frequency fields.
 It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field.
-{\color{Red}
 In our case, the applied dressing field is in the high-frequency regime where we can neglect the photon interactions.
-The only influence of the electromagnetic field is the suppression of electron scattering.}
+The only influence of the electromagnetic field is the suppression of electron scattering.
 This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems.
@@
   {journal} {Phy. Rev. B}\ }\textbf {\bibinfo {volume} {64}},\ \bibinfo {pages}
-  {201311} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+  {201311(R)} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Mani}\ \emph {et~al.}(2002)\citenamefont {Mani},
-  \citenamefont {Smet}, \citenamefont {von Klitzing}, \citenamefont
+  \citenamefont {Smet}, \citenamefont {vonKlitzing}, \citenamefont
   {Narayanamurti}, \citenamefont {Johnson},\ and\ \citenamefont
@@
   {Mani}}, \bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont {Smet}},
-  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {von Klitzing}}, \bibinfo
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {vonKlitzing}}, \bibinfo
   {author} {\bibfnamefont {V.}~\bibnamefont {Narayanamurti}}, \bibinfo {author}
@@
 \bibitem [{\citenamefont {Mani}\ \emph {et~al.}(2004)\citenamefont {Mani},
-  \citenamefont {Smet}, \citenamefont {Von~Klitzing}, \citenamefont
+  \citenamefont {Smet}, \citenamefont {von~Klitzing}, \citenamefont
   {Narayanamurti}, \citenamefont {Johnson},\ and\ \citenamefont
@@
   {Hirakawa}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Yamanaka}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Kawaguchi}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Endo}}, \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Saeki}},\ and\ \bibinfo {author}
+  , \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Endo}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Saeki}},\ and\ \bibinfo {author}
   {\bibfnamefont {S.}~\bibnamefont {Komiyama}},\ }\href

### 2022-01-21 paper/submission4/manuscript/dressed_quantum_hall_sub4.tex
Add new reference for supplemental materials

--- 2022-01-21 paper/submission3/manuscript/dressed_quantum_hall_sub3.tex
@@
 \end{equation}
-where $\varsigma = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$. Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.
+where $\varsigma = \flatfrac{\Gamma_0}{(2\hbar \omega_0)}$.
+Here, $\Gamma_0$ is the natural energy broadening of the least Landau level.
+The derived analytical expression is further analyzed numerically using empirical system parameters to compare with the results from previous charge transport studies on quantum Hall systems.
+For the interested reader, the full \textsc{mathematica} codes for the simulations are available in Ref.~\cite{supplemental1}.
 
@@
 \providecommand{\noopsort}[1]{}\providecommand{\singleletter}[1]{#1}%
-\begin{thebibliography}{106}%
+\begin{thebibliography}{107}%
 \makeatletter
@@
   {NoStop}%
+\bibitem [{sup()}]{supplemental1}%
+  \BibitemOpen
+  \href@noop {} {}\bibinfo {howpublished} {See Supplemental Material at
+  \url{URL} for complete numerical simulations of the longitudinal conductivity
+  in dressed quantum Hall system}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Wakabayashi}\ and\ \citenamefont
